### 2021-08-05 paper.tex
Initial Overleaf Import

% ****** Start of file apssamp.tex ******
%
%   This file is part of the APS files in the REVTeX 4.2 distribution.
%   Version 4.2a of REVTeX, December 2014
%
%   Copyright (c) 2014 The American Physical Society.
%
%   See the REVTeX 4 README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.2
%
% See the REVTeX 4 README file
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex apssamp.tex
%  2)  bibtex apssamp
%  3)  latex apssamp.tex
%  4)  latex apssamp.tex
%
\documentclass[superscriptaddress,unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{physics}
\usepackage{lipsum}
\usepackage{subfig}
% \usepackage{braket}

%\newcommand\abs[1]{\left|#1\right|}
%\newcommand\bra[1]{\left| #1 \right \rangle}
%\newcommand\ket[1]{\left \langle #1 \right |}

\begin{document}

\title{Predicting Solid State Qubit Candidates}

\author{Oliver Lerstøl Hebnes}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Marianne Etzelm\"uller Bathen}
\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
\author{Øyvind Sigmundson Schøyen}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Sebastian G. Winther-Larsen}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Morten Hjorth-Jensen}
\affiliation{Facility for Rare Ion Beams and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
\author{Lasse Vines}
\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}

\begin{abstract}

Semiconductor materials provide a compelling platform for quantum
technology, and a vast amount of materials and their properties can be
found in high-throughput databases.  However, filtering among these
materials in order to find novel candidates for quantum technology is
a challenge. Therefore, we provide a framework for the automatic
discovery of promising solid-state material hosts using machine
learning methods.

We have developed data extraction tools for numerous material science
databases, and constructed over $4800$ physics-informed features for a
dataset consisting of more than $25000$ materials.  Furthermore, we
have developed and implemented three data mining approaches, termed
\textit{the Ferrenti approach}, \textit{the augmented Ferrenti
  approach} and \textit{the insightful approach} for defining three
distinct training sets for the supervised machine learning algorithms
logistic regression, decision tree, random forest and gradient boost
to be trained on.

We find a lack of consistent results for the Ferrenti approach and the
augmented Ferrenti approach due to an overly broad formulation of the
training set, whereas the restrictions set in the insightful approach
proved suitable. All models agreed on $214$ predicted candidates, with
examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP,
and InAs. All approaches and all models agreed on a subset of $47$
eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary
compounds.

\end{abstract}

\pacs{02.70.Ss, 31.15.A-, 31.15.bw, 71.15.-m, 73.21.La}

\maketitle

\section{Introduction}

\section{Theoretical Background and Experimental Data}

\section{Results and Discussions}

\section{Conclusions and Perspectives}

\begin{acknowledgments}

The work of MHJ is supported by the U.S. Department of Energy,
Office of Science, office of Nuclear Physics under grant
No. DE-SC0021152 and U.S. National Science Foundation Grants
No. PHY-1404159 and PHY-2013047.

\end{acknowledgments}

\bibliography{apssamp}% Produces the bibliography via BibTeX.
\end{document}

### 2021-08-09 paper.tex
Updates from Overleaf

@@
 \author{Marianne Etzelm\"uller Bathen}
+\affiliation{Advanced Power Semiconductor Laboratory,ETH Zürich,  8092  Zürich,  Switzerland}
 \affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
@@
 No. PHY-1404159 and PHY-2013047. 
+The work of MEB and LV was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
+%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
+MEB acknowledges support by an ETH Zurich Postdoctoral Fellowship.
 

### 2021-08-10 paper.tex
Updates from Overleaf

@@
 
+%Where to submit? 
+% npj Quantum Information  or npj Computational Materials are options I am familiar with 
+%
+
 \section{Introduction}
+To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored.
+The quantum computer, together with the complementary quantum technologies of sensing and communication, is becoming a frontrunner in the race for solutions.
+Discuss recent benchmarks for quantum computing \cite{Arute_2019}.
+
+Limitations of quantum computing and technology building blocks. Drawbacks of superconductors. Semiconductors are a promising platform. Example of NV center in diamond \cite{Doherty_2013}.
+
+%From thesis - rewrite 
+Unfortunately, there are substantial challenges associated with the modern quantum platforms simultaneously as the selection of quantum platforms are slim.
+The majority of discoveries of potential quantum platforms have so far happened by serendipity, and there is an urgent need for new and better materials that can escalate the effort for a sustainable future.
+
+The fourth science paradigm introduces the potential of targeted search for promising material systems to act as qubit hosts. 
+Herein, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods. 
+Initial database building similar to Ferrenti et al [].
 
 \section{Theoretical Background and Experimental Data} 
+%subsections are potential topics, not necessarily subsections we will actually include
 
-\section{Results and Discussions}
+\subsection{Quantum host material requirements}
+%What parameters are we looking for?
+
+\subsection{The semiconductor platform}
+%Experimental findings
+
+\subsection{Introduction to DFT} 
+%Data formats
+
+\subsection{Databases} 
+%Materials project, AFLOW, Open Quantum, JARVIS
+
+\section{Methodology}
+\subsection{Materials informatics} 
+Mining
+
+Screening
+
+\subsection{Machine learning}
+
+\section{Results and Discussion}
+\subsection{}
 

### 2021-08-13 paper.tex
Updates from Overleaf

@@
 \author{Marianne Etzelm\"uller Bathen}
-\affiliation{Advanced Power Semiconductor Laboratory,ETH Zürich,  8092  Zürich,  Switzerland}
+\affiliation{Advanced Power Semiconductor Laboratory, ETH Zürich, 8092  Zürich,  Switzerland}
 \affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
@@
 
+%Main message 1: develop methodology for data mining and machine learning for materials properties 
 We have developed data extraction tools for numerous material science
@@
 
+% Main message 2: Use method to propose new materials that are promising quantum hosts 
 We find a lack of consistent results for the Ferrenti approach and the
@@
 
-%Where to submit? 
-% npj Quantum Information  or npj Computational Materials are options I am familiar with 
-%
+%Submit to npj Computational Materials
 
-\section{Introduction}
+%Marianne: I have now structured the paper according to other papers in this journal 
+%I think we can make a supplementary material if we see that we need it, it is quite common for the journal
+
+\section*{Introduction}%Oliver and Morten and Marianne (semiconductor portion)
 To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored.
@@
 Herein, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods. 
-Initial database building similar to Ferrenti et al [].
+Initial database building similar to Ferrenti et al \cite{Ferrenti2020}.
 
-\section{Theoretical Background and Experimental Data} 
-%subsections are potential topics, not necessarily subsections we will actually include
+\begin{figure}
+    \centering
+    \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
+    \caption{Placeholder for workflow.
+Morten: can you please add the other schematic figure we discussed as placeholder?
+Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
+}
+    \label{fig:ht-workflow}
+\end{figure}
 
-\subsection{Quantum host material requirements}
+\section*{Theoretical Background and Experimental Data} 
+%Subsections are potential topics, not necessarily subsections we will actually include. 
+%We can probably merge a few of the subsections in the end, or even move some theory to the supplementary
+
+%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics.
+
+\subsection*{Quantum Host Material Requirements} %Marianne and Lasse 
 %What parameters are we looking for? 
+Discuss experimental data and the semiconductor platform.
 
-\subsection{The semiconductor platform}
+%\subsection*{The semiconductor platform} %Marianne and Lasse 
 %Experimental findings
 
-\subsection{Introduction to DFT} 
-%Data formats
+\subsection*{Density Functional Theory Output} %Marianne 
+Data formats, limitations etc.
 
-\subsection{Databases} 
+\subsection*{Material Informatics} %Øyvind (Oliver)    
+%Data mining, screening
+
+\subsection*{Machine Learning} % Morten
+
+\section*{Results}
+Includes discussion of results.
+
+\subsection*{Information Flow}  %Sebastian/Oyvind (Marianne) 
+Includes results from data mining and description of the three approaches. 
+%MEB: Since Methods are at the end, I propose to put part of this discussion in the Results section. 
+%This is because it is an important result of the work, and also because it is important to understand the rest of the paper
+
+\subsection*{Optimization of Machine Learning Models} %Morten (Oliver input in round 2)
+
+\subsection*{Predicting Novel Material Hosts for Quantum Technology} %Oyvind (Oliver input in round 2) 
+\subsubsection*{The Ferrenti approach} 
+\subsubsection*{The augmented Ferrenti approach} 
+\subsubsection*{The insightful approach} 
+\subsubsection*{Comparing the approaches}
+
+\section*{Discussion} % All - last thing we write  
+Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
+
+\section*{Methods}
+%Methodology comes after concluding remarks, and is structured into subsections
+
+\subsection*{Databases} %Oliver and Øyvind 
 %Materials project, AFLOW, Open Quantum, JARVIS 
+Mining.
 
-\section{Methodology}
-\subsection{Materials informatics} 
-Mining
+\subsection*{Material Informatics} %Oliver and Øyvind 
+Screening and workflow and approaches.
 
-Screening
+\subsection*{Machine Learning} %Sebastian/Morten   
+Insight gaining.
 
-\subsection{Machine learning}
+\section*{Data availability} 
+%We can put something else, standard text 
+The data that support the plots within this paper and other findings of this study are
+available from the corresponding authors upon reasonable request.
 
-\section{Results and Discussion}
-\subsection{}
+\section*{Code availability} 
+The codes developed in this study are available from the authors upon reasonable
+request.
 
-\section{Conclusions and Perspectives}
+\bibliography{apssamp}% Produces the bibliography via BibTeX.
 
@@
 
-\bibliography{apssamp}% Produces the bibliography via BibTeX.
+\section*{Author contributions} 
+%Copied in from another paper 
+S.-M.J. conceived the idea and developed the simulation model. T.H.L. performed
+computer simulation. S.Y.B. and S.D.H. fabricated devices. D.-W.S., S.L., H.W.C. and
+J.-W.J. supported measurement of device performances. Y.-H.S. and X.-B.F.
+synthesised QD materials. S.Z. and J.Y. supported experiments. C.S. and Y.K.
+supported computer simulation. L.G.O. and G.A. supported data analysis. J.M.K.
+guided this work. S.-M.J., T.H.L. and S.Y.B. contributed equally. 
+All the authors
+contributed to the preparation of the manuscript.
+
+\section*{Competing interests}
+The authors declare no competing interests.
+
 \end{document}

### 2021-08-18 paper.tex
Updates from Overleaf

@@
 \section*{Theoretical Background and Experimental Data}
-%Subsections are potential topics, not necessarily subsections we will actually include. 
-%We can probably merge a few of the subsections in the end, or even move some theory to the supplementary
 
@@
 Data formats, limitations etc.
+
+Density functional theory is a versatile and powerful theoretical approach, enabling targeted study of semiconductor materials with many atoms. 
+Proven successful for material properties such as thermal stability, lattice parameters and band gap.
 
@@
 %Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
-MEB acknowledges support by an ETH Zurich Postdoctoral Fellowship.
+The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship.
 
@@
 guided this work. S.-M.J., T.H.L. and S.Y.B. contributed equally. 
-All the authors
-contributed to the preparation of the manuscript.
+All the authors contributed to the preparation of the manuscript.
 

### 2021-08-21 paper.tex
Updates from Overleaf

@@
 \section*{Theoretical Background and Experimental Data} 
+%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics. 
+Quantum technologies, including sensing, communication and computing, 
+are intriguing because of the new capabilities they offer. 
+However, realization of large-scale fabrication for these techniques requires further technological development. 
+The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale. 
+Instead, recent developments have seen/heralded the rise of semiconductors as host materials for a variety of quantum devices.
+Much easier to combine with existing devices, and RT operation has been shown.
+However, the ideal host has yet to be identified, and the requirements for acting as a good host remain unclear. 
+Different methods are needed.
 
-%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics.
+\subsection*{Semiconductors as a Quantum Host} %Marianne and Lasse 
+The key feature when considering a quantum object for application is coherence, which is again tightly connected to the concept of coherence. 
+For all applications, the basic requirement is a two-level quantum system which is quite isolated so the levels remain stable. 
+Also need to control the qubit state via initialization, manipulation and read-out. 
+Requirements \cite{DiVincenzo2000,Weber2010}: 
+\begin{itemize}
+    \item A scalable physical system with well-characterized qubits
+    \item Reliable qubit initialization protocols 
+    \item Need quantum gates to operate on qubits 
+    \item Qubit state coherence time must exceed gate operation time 
+    \item Need to read out qubit state after operation. 
+\end{itemize}
 
-\subsection*{Quantum Host Material Requirements} %Marianne and Lasse 
+%Discuss experimental data and the semiconductor platform. 
+Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap. 
+Importantly, such deep levels can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT. 
+A prime example is the nitrogen-vacancy center in diamond, which has been proposed 
+as a contender for both qubit, sensing and communication applications \cite{Doherty_2013}. 
+The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, exhibiting entangled photons that have been separated by ... km []. 
+Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence of 1 ms []. 
+Qubit operations and entanglement have been demonstrated []. 
+However, emission wavelength is not ideally compatible with fiber optic technology (need telecom range), spin coherence is good but could be better, and sensing is good.
+
+\begin{table}[t]
+    \centering
+    \begin{tabular}{c|c|c|c}
+    Material & Band gap (eV) & Defect candidates & Reference \\
+    \hline
+    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\  
+    4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\ 
+    Si & $1.1$ & P, G, unidentified & \cite{Muhonen_2014,Durand_2020,Redjem2020} \\ 
+    (2D) \textit{h}-BN & $6.0$ & Unidentified defects & \cite{Tran_2016,Tran_2016b,Hayee_2020} \\ 
+    ZnO & $3.4$ & Unidentified defects & \cite{Morfa2012} \\ 
+    ZnS & $3.6$ (zincblende) & Unidentified defects & \cite{Stewart2019} \\ 
+    GaAs & $1.4$ & Quantum dots & \cite{Bluhm2010} \\ 
+    GaN & $3.4$ & Quantum dots, unidentified defects & \cite{Roux2017,Berhane2018} \\
+    AlN & $6.0$ & Unidentified defects & \cite{Xue2020}\\
+    \end{tabular}
+    \caption{Overview of materials and defects that have been demonstrated to exhibit QT-compatible characteristics such as single-photon emission and coherent spin manipulation.}
+    \label{tab:qt-materials}
+\end{table}
+
+ ZnS [74], GaAs [75],
+GaN [76, 77 , 80] and AlN [78, 79],  [81].
+
+%QT requirements. 
 %What parameters are we looking for? 
-Discuss experimental data and the semiconductor platform.
+Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics. 
+Not all defects are identified, and challenges due 
+to the specific materials complicate the implementation of defects for QT. 
+There are some common denominators for the materials: 
+\begin{itemize}
+    \item Wide band gap to facilitate localized deep levels (physical)
+    \item Low spin orbit coupling to extend spin coherence times (physical) 
+    \item Low el-phonon coupling for sharp ZPLs (physical) 
+    \item Availability as high-quality, bulk, or thin-film single crystals (practical)
+    \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
+\end{itemize}
+Note the division between physical and practical requirements in the list above. 
+The physical ones refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to some more external influence that provides more easy measurement and detection of said properties.
+It is the former that we are interested in.
 
-%\subsection*{The semiconductor platform} %Marianne and Lasse 
-%Experimental findings
+Different defect and material types may suit different needs. 
+Therefore, we need a bigger bank of candidates. 
+Also, we do not fully understand exactly what constitutes a good quantum host material. 
+So far, detection of QT compatibility has been slow, as a signal is detected and then identified in a specific material. 
+We are looking for a top-down approach to instead predict promising materials, and guide experiments. 
+For this, we first need a large dataset.
 
 \subsection*{Density Functional Theory Output} %Marianne 
+Density functional theory has been exceptionally successful in predicting solid-state material properties 
+such as
+
 Data formats, limitations etc.

### 2021-08-24 paper.tex
Updates from Overleaf

--- 2021-08-18 paper.tex
@@
 % \usepackage{braket}
+\usepackage{siunitx}
+\sisetup{separate-uncertainty}
 
@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Marianne Etzelm\"uller Bathen}
@@
 \affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Øyvind Sigmundson Schøyen}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Sebastian G. Winther-Larsen}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Morten Hjorth-Jensen}
@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Lasse Vines}
@@
 
-\begin{figure}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/paradigms.png}
+    \caption{[PLACEHOLDER] Schematic over paradigms in science.}
+    \label{fig:paradigm}
+\end{figure}
+
+\section*{Theoretical Background and Experimental Data} 
+%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics.
+
+%Some of this can also be copied into the introduction
+
+Quantum technologies, including sensing, communication and computing, 
+are intriguing because of the new capabilities they offer. 
+However, realization of large-scale fabrication for these techniques requires further technological development. 
+The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale. 
+Instead, recent developments have seen/heralded the rise of semiconductors as possible host materials for a variety of quantum devices.
+Semiconductor quantum dots or point defects could prove easier to combine with existing devices, and room temperature operation of prototype communication and computing devices has been shown.
+However, this technology is still in the early stages, and the issues left to address include scalable and reproducible device fabrication, identification of ideally suited host candidates, and, importantly, understanding the requirements for a material to act as a good host remain unclear.
+%Different methods are needed.
+
+\subsection*{Semiconductors as a Quantum Host} %Marianne and Lasse
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/qubit.png}
+    \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
+    \label{fig:qt}
+\end{figure}
+
+Quantum tehcnologies commonly rely on a quantum bit or qubit as the basis for operation. 
+For all applications, the basic requirement is a two-level quantum system which is quite isolated from the environment, ensuring long-term stability between operations.
+In other words, we search for systems which exhibit a high degree of coherence.
+However, stability is not enough. The qubit state must be controlled via repeatable initialization, manipulation and read-out. 
+A set of requirements were formulated by DiVincenzo for the case of qubits and quantum computing \cite{DiVincenzo2000}.
+Below, these are rephrased to encompass qubit requirements for all three QT application areas:
+\begin{itemize}
+    \item A scalable physical system with well-characterized qubits
+    \item Reliable qubit initialization protocols 
+    \item Quantum gates and protocols to operate on and control qubit states  
+    \item Qubit state coherence time must exceed gate operation time 
+    \item Qubit state read-out after operation, preferably optically.  
+\end{itemize}
+
+%Discuss experimental data and the semiconductor platform. 
+Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap. 
+Importantly, deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT. 
+A prime example is the nitrogen-vacancy (NV) center in diamond, which has been proposed 
+as a contender for both computing, sensing and communication applications \cite{Doherty_2013}. 
+The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for optical imaging of living cells \cite{Lesage_2013}.  
+Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second},
+leading to demonstrations of entanglement and teleportation of two NV center spins \cite{Bernien2013,Pfaff_2014}. 
+However, despite these promising discoveries, diamond may not be the ideal candidate host.
+The NV center, for instance, emits in the visible, which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology, and the poor scalability of diamond devices may prove non-competitive in the long run.
+
+\begin{table}[h]
+    \centering
+    \begin{tabular}{c|c|c|c}
+    Material & Band gap (eV) & Defect candidates & References \\
+    \hline
+    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\  
+    4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\ 
+    Si & $1.1$ & P, G, unidentified & \cite{Muhonen_2014,Durand_2020,Redjem2020} \\ 
+    (2D) \textit{h}-BN & $6.0$ & Unidentified defects & \cite{Tran_2016,Tran_2016b,Hayee_2020} \\ 
+    ZnO & $3.4$ & Unidentified defects & \cite{Morfa2012} \\ 
+    ZnS & $3.6$ (zincblende) & Unidentified defects & \cite{Stewart2019} \\ 
+    GaAs & $1.4$ & Quantum dots & \cite{Bluhm2010} \\ 
+    GaN & $3.4$ & Quantum dots, unidentified defects & \cite{Roux2017,Berhane2018} \\
+    AlN & $6.0$ & Unidentified defects & \cite{Xue2020}\\
+    \end{tabular}
+    \caption{Overview of materials and defects that have been demonstrated to exhibit QT-compatible characteristics such as single-photon emission and coherent spin manipulation.}
+    \label{tab:qt-materials}
+\end{table}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/NV.png}
+    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
+    \label{fig:defects-dft}
+\end{figure}
+
+%QT requirements. 
+%What parameters are we looking for? 
+Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
+In this context we consider single-photon emission and coherent spin manipulation for systems related to point defects primarily, but also self-assembled or lithographically structured quantum dots.
+Most of the defects in the table have yet to be identified, and different materials challenges complicate the implementation of defects for QT. 
+A set of common denominators for materials that contain quantum emitters was summarized by Weber et al \cite{Weber2010}: 
+\begin{itemize}
+    \item Wide band gap to facilitate localized deep levels (physical)
+    \item Low spin orbit coupling to extend spin coherence times (physical) 
+    \item Low el-phonon coupling for sharp emission lines (physical) 
+    \item Availability as high-quality, bulk, or thin-film single crystals (practical)
+    \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
+\end{itemize}
+Note the division between physical and practical requirements in the list above. 
+The physical criteria refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to the external influences that simplify measurement and detection of the interesting properties.
+In this work, we will focus most on the former set of criteria, as understanding them better may give further insights into the makings of a solid QT platform.
+
+In addition to obtaining greater understanding of  exactly what constitutes a good quantum host material, we must recognize that different defect and material types may suit different needs.
+Therefore, we aim to develop a bigger bank of candidate defects and materials.
+So far, detection of QT compatibility in semiconductors has been slow going, as a signal is detected and then identified in a specific material.  
+Instead, we are looking for a top-down approach to  \textit{predict} promising materials, enabling a guiding of experimental efforts. 
+%For this, we first need a large dataset.
+
+\subsection*{Density Functional Theory Output} %Marianne 
+Density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
+Using DFT calculations we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
+
+DFT is based on the Hohenberg-Kohn \cite{Hohenberg1964} and Kohn-Sham \cite{Kohn1965} theorems and provides a method for iteratively solving the Schrodinger equation based on initial guesses for the atomic potentials.
+The foundation for DFT centers around the electronic density providing all ground-state properties of the system, provided that the external potential can be exactly described. 
+The fundamental challenge of DFT calculations is that this potential, as expressed by the exchange-correlation functional, can be exactly computed for only very few and simple systems.
+
+In the case of solid state materials the XC functional is not known and must instead be approximated. 
+Herein, we will consider three classes of functionals based on different fundamental assumptions.
+The local density approximation (LDA) takes the homogeneous electron gas as a starting point, while the more advanced general gradient approximation (GGA) includes also the gradient in local electron gas variations.
+These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron can interact with itself).
+More recent developments have seen the widespread use of hybrid functionals such as the HSE06 incorporating a portion of Hartree-Fock exact exchange \cite{Heyd2003},  albeit at a much greater computational cost.
+See, e.g., this review \cite{Freysoldt2014} for further details on different functionals for semiconductor and defect calculations.
+
+Despite the limitations imposed by the approximate nature of the XC functional, and the band gap error of LDA and GGA level functionals, 
+DFT can be a powerful tool when predicting, designing and interpreting experiments. 
+Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict novel candidate QT hosts.
+The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}, which can underestimate the band gap of semiconductor materials.  
+Nonetheless, a larger data set is available than for, e.g., HSE06, and many trends are conserved also with PBE. 
+The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the elctronegativity, the electron-phonon coupling and magnetic properties.
+
+\subsection*{Material Informatics} %Øyvind (Oliver)    
+%Data mining, screening
+
+\begin{figure}[t]
     \centering
     \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
-    \caption{Placeholder for workflow.
-Morten: can you please add the other schematic figure we discussed as placeholder?
+    \caption{[PLACEHOLDER for workflow] Morten: can you please add the other schematic figure we discussed as placeholder?
 Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
@@
 \end{figure}
-
-\section*{Theoretical Background and Experimental Data}
-
-%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics.
-
-\subsection*{Quantum Host Material Requirements} %Marianne and Lasse 
-%What parameters are we looking for? 
-Discuss experimental data and the semiconductor platform.
-
-%\subsection*{The semiconductor platform} %Marianne and Lasse 
-%Experimental findings
-
-\subsection*{Density Functional Theory Output} %Marianne 
-Data formats, limitations etc.
-
-Density functional theory is a versatile and powerful theoretical approach, enabling targeted study of semiconductor materials with many atoms. 
-Proven successful for material properties such as thermal stability, lattice parameters and band gap.
-
-\subsection*{Material Informatics} %Øyvind (Oliver)    
-%Data mining, screening
 

### 2021-09-24 paper.tex
Updates from Overleaf

@@
 \usepackage{siunitx}
+\usepackage{color}
 \sisetup{separate-uncertainty}
@@
 %\newcommand\ket[1]{\left \langle #1 \right |}
+
+\newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
+\newcommand{\morten}[1]{\textcolor{green}{#1}}
+\newcommand{\sebastian}[1]{\textcolor{cyan}{#1}}
+\newcommand{\marianne}[1]{\textcolor{blue}{#1}}
+\newcommand{\oyvind}[1]{\textcolor{maroon}{#1}}
+\newcommand{\lasse}[1]{\textcolor{red}{#1}}
 
@@
 \section*{Introduction}%Oliver and Morten and Marianne (semiconductor portion)
-To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored.
-The quantum computer, together with the complementary quantum technologies of sensing and communication, is becoming a frontrunner in the race for solutions.
-Discuss recent benchmarks for quantum computing \cite{Arute_2019}.
+The second quantum revolution is heralding the development of new solutions and devices based on quantum technology \cite{Acin2018}.
+Among the promising prototypes that are already available we find in vivo sensing of magnetic fields in cells [], secure communication over large distances by separation of entangled photons, and finally the demonstration of quantum computers [].
+Quantum computers in particular are in high demand to sate the continued demand for computing power strong enough to solve increasingly complex problems. 
+Recently, the potential of such machines to outperform classical systems was proven when a 53-qubit quantum computer based on superconductor electronics solved a computational problem that was beyond the capabilities of a 200'000 core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
 
-Limitations of quantum computing and technology building blocks. Drawbacks of superconductors. Semiconductors are a promising platform. Example of NV center in diamond \cite{Doherty_2013}.
+Quantum platforms are available but both the materials and fabrication technologies are far less mature than those for, e.g., classical computers and sensors. 
+An important concern in this context is that of scalability. 
+For example, the best performing quantum computer prototypes rely on either superconducting electronics or trapped ions.
+Both technologies require millikelvin temperatures to operate, fabrication is challenging, and the stability of interactions is an issue.
+Instead, semiconductors are emerging as a promising alternative platform, offering competitive characteristics combined with the possibility of room temperature operation and mature and scalable material processing and fabrication.
+
+Quantum technologies based on semiconductors rely on either defects or quantum dots, where the latter kind can be of the self-assembled or the fabricated type.
 
@@
 \subsection*{Semiconductors as a Quantum Host} %Marianne and Lasse 
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/qubit.png}
-    \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
-    \label{fig:qt}
-\end{figure}
-
-Quantum tehcnologies commonly rely on a quantum bit or qubit as the basis for operation. 
-For all applications, the basic requirement is a two-level quantum system which is quite isolated from the environment, ensuring long-term stability between operations.
+Quantum technologies commonly rely on a quantum bit or qubit as the basis for operation. 
+\marianne{Some schematic is shown in Figure~\ref{fig:qt}}. 
+For all applications, the basic requirement is a two-level quantum system which is essentially isolated from its environment, ensuring sufficient stability to perform various operation.
 In other words, we search for systems which exhibit a high degree of coherence.
-However, stability is not enough. The qubit state must be controlled via repeatable initialization, manipulation and read-out. 
+Additionally, the qubit state must be controlable via repeatable initialization, manipulation and read-out protocols.
 A set of requirements were formulated by DiVincenzo for the case of qubits and quantum computing \cite{DiVincenzo2000}.
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/qubit.png}
+    \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
+    \label{fig:qt}
+\end{figure}
+
 %Discuss experimental data and the semiconductor platform. 
@@
 as a contender for both computing, sensing and communication applications \cite{Doherty_2013}. 
-The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for optical imaging of living cells \cite{Lesage_2013}.  
-Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second},
+The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for, e.g., stress tensor mapping \cite{Broadway2019} and optical imaging of living cells \cite{Lesage_2013}.
+Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second} \cite{Doherty_2013},
 leading to demonstrations of entanglement and teleportation of two NV center spins \cite{Bernien2013,Pfaff_2014}. 
-However, despite these promising discoveries, diamond may not be the ideal candidate host.
-The NV center, for instance, emits in the visible, which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology, and the poor scalability of diamond devices may prove non-competitive in the long run.
+However, despite these promising discoveries, diamond  as a quantum platform comes with several important drawbacks.
+The relevant defects therein, such as the NV center, emit in the visible region of the spectrum which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology.
+Additionally, diamond is expensive, device fabrication is challenging and scalability is poor, leading to concerns in whether quantum technology device development will be realizable on this platform.
+Hence, we search among the plethora of available semiconductors for a platform that can deliver on the necessary parameters for QT applications while also, ideally, providing availability and scalable fabrication.
+In this context, the material properties that facilitate quantum compatible characteristics such as single-photon emission and coherent spin manipulation to manifest must be identified.
 
@@
     \centering
+    \caption{Overview of materials and defects that have been demonstrated to exhibit QT compatible characteristics such as single-photon emission and coherent spin manipulation.}
     \begin{tabular}{c|c|c|c}
@@
     \hline
-    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\  
-    4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\ 
+    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\ 4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\
     Si & $1.1$ & P, G, unidentified & \cite{Muhonen_2014,Durand_2020,Redjem2020} \\ 
@@
     \end{tabular}
-    \caption{Overview of materials and defects that have been demonstrated to exhibit QT-compatible characteristics such as single-photon emission and coherent spin manipulation.}
     \label{tab:qt-materials}
@@
 
+%\begin{figure}[t]
+%    \centering
+%    \includegraphics[width=0.5\textwidth]{figures/NV.png}
+%    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
+%    \label{fig:defects-dft}
+%\end{figure}
+
 \begin{figure}[t]
     \centering
-    \includegraphics[width=0.5\textwidth]{figures/NV.png}
-    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
-    \label{fig:defects-dft}
+    \includegraphics[width=0.5\textwidth]{figures/defects-sic.pdf}
+    \caption{[PLACEHOLDER] Schematic representation of different quantum compatible defects in SiC and the energy levels they introduce into the band gap, from Ref.\cite{Bathen2021}.} 
+    \label{fig:defects-sic}
 \end{figure}
@@
 In this context we consider single-photon emission and coherent spin manipulation for systems related to point defects primarily, but also self-assembled or lithographically structured quantum dots.
-Most of the defects in the table have yet to be identified, and different materials challenges complicate the implementation of defects for QT. 
-A set of common denominators for materials that contain quantum emitters was summarized by Weber et al \cite{Weber2010}: 
+\marianne{A (placeholder) schematic of quantum compatible defects and the energy levels they introduce into the band gap of 4H-SiC is shown in Figure~\ref{fig:defects-sic}.}
+Most of the defects in the table have yet to be identified, and different material related challenges complicate the implementation of defects for QT. 
+A set of common denominators for materials that contain qubit defects was summarized by Weber et al. \cite{Weber2010}: 
 \begin{itemize}
@@
 The physical criteria refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to the external influences that simplify measurement and detection of the interesting properties.
-In this work, we will focus most on the former set of criteria, as understanding them better may give further insights into the makings of a solid QT platform.
+In this work, we will focus primarily on the former set of criteria, as understanding them better may give further insights into the makings of a reliable QT platform.
 
@@
 Therefore, we aim to develop a bigger bank of candidate defects and materials.
-So far, detection of QT compatibility in semiconductors has been slow going, as a signal is detected and then identified in a specific material.  
+So far, detection of QT compatibility in semiconductors has been rather slow, depending on signal detection and later identification in each specific material. 
 Instead, we are looking for a top-down approach to \textit{predict} promising materials, enabling a guiding of experimental efforts. 
@@
 \subsection*{Density Functional Theory Output} %Marianne 
-Density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
-Using DFT calculations we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
+The density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
+DFT provides a method for iteratively solving the Schr{\"o}dinger equation based on initial guesses for the atomic potentials. 
+Using DFT calculations, we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
 
-DFT is based on the Hohenberg-Kohn \cite{Hohenberg1964} and Kohn-Sham \cite{Kohn1965} theorems and provides a method for iteratively solving the Schrodinger equation based on initial guesses for the atomic potentials.
-The foundation for DFT centers around the electronic density providing all ground-state properties of the system, provided that the external potential can be exactly described. 
-The fundamental challenge of DFT calculations is that this potential, as expressed by the exchange-correlation functional, can be exactly computed for only very few and simple systems.
+%DFT is based on the Hohenberg-Kohn \cite{Hohenberg1964} and Kohn-Sham \cite{Kohn1965} theorems and provides a method for iteratively solving the Schrodinger equation based on initial guesses for the atomic potentials.
+%The foundation for DFT centers around the electronic density providing all ground-state properties of the system, provided that the external potential can be exactly described. 
+%The fundamental challenge of DFT calculations is that this potential, as expressed by the exchange-correlation functional, can be exactly computed for only very few and simple systems.
 
-In the case of solid state materials the XC functional is not known and must instead be approximated. 
-Herein, we will consider three classes of functionals based on different fundamental assumptions.
+The fundamental challenge of the DFT is that the calculations rely on approximations to the potential function of a system as expressed by the exchange-correlation (XC) functional, which is not known for bulk materials.
+The XC functional is usually grouped into three categories based on the level of theory.
 The local density approximation (LDA) takes the homogeneous electron gas as a starting point, while the more advanced general gradient approximation (GGA) includes also the gradient in local electron gas variations.
-These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron can interact with itself).
+These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron is allowed to interact with itself) [Ref SchollSteckel] \cite{Freysoldt2014}.
 More recent developments have seen the widespread use of hybrid functionals such as the HSE06 incorporating a portion of Hartree-Fock exact exchange \cite{Heyd2003},  albeit at a much greater computational cost.
-See, e.g., this review \cite{Freysoldt2014} for further details on different functionals for semiconductor and defect calculations.
+%See, e.g., this review \cite{Freysoldt2014} for further details on different functionals for semiconductor and defect calculations.
 
@@
 DFT can be a powerful tool when predicting, designing and interpreting experiments. 
-Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict novel candidate QT hosts.
-The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}, which can underestimate the band gap of semiconductor materials.  
+Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict new candidate QT hosts.
+The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}. 
+Note that the PBE functional tends to underestimate the band gap of semiconductor materials.  
 Nonetheless, a larger data set is available than for, e.g., HSE06, and many trends are conserved also with PBE. 
-The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the elctronegativity, the electron-phonon coupling and magnetic properties.
+The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the electronegativity, the electron-phonon coupling and magnetic properties.
 
@@
 \subsection*{Information Flow}  %Sebastian/Oyvind (Marianne) 
-Includes results from data mining and description of the three approaches. 
-%MEB: Since Methods are at the end, I propose to put part of this discussion in the Results section. 
-%This is because it is an important result of the work, and also because it is important to understand the rest of the paper
+% MEB: Since Methods are at the end, I propose to put part of this
+% discussion in the Results section. 
+% This is because it is an important result of the work, and also
+% because it is important to understand the rest of the paper
 
-\subsection*{Optimization of Machine Learning Models} %Morten (Oliver input in round 2)
+The information stream of this project can be regarded as many
+modular parts connected in logical pieces. The initial step for
+gathering and building features is visualized by the
+the flowchart in [INSERT FIGURE!!]. 
+Initially, we start by extracting all entries in
+the Materials Project that matches a specific query. 
+Thereafter, we apply Matminer’s\cite{Ward2018}
+featurization tools to make thousands
+of features of the data. The conditions on this initial query are that the
+materials must
+derive from experimental data, and have a band gap wider than $0.1$ eV.
+In a parallel step, entries that are deemed
+similar to the entries from the initial query
+are extracted from AFLOW\cite{Curtarolo2012, Curtarolo2012a, Calderon2015},
+AFLOW-ML\cite{Isayev2017},
+JARVIS-DFT, % \cite{Choudhary2020},
+OQMD\cite{Saal2013,Kirklin2015}
+and
+Citrine Informatics. The results of these steps are combined into
+a data set for further analysis.
 
-\subsection*{Predicting Novel Material Hosts for Quantum Technology} %Oyvind (Oliver input in round 2) 
+% \subsection*{Optimization of Machine Learning Models} %Morten (Oliver input in round 2)
+
+\subsection*{Data Mining}
+
+After compiling a dataset from the procedure outlined above, we 
+face a challenge in terms of defining a training set that we can 
+train data on. This is not only challenging due to the lack of known
+suitable candidates (1), but also due to the intricacy of defining
+materials as unsuitable candidates (0). We follow three separate
+procedures to this end.
+
 \subsubsection*{The Ferrenti approach}
+
+The first approach to defining a training set is based on the criteria
+from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+They suggest a data mining process consisting of four stages by 
+systematically evaluating the suitability of host materials from
+the Materials Project.
+
+We label \textbf{suitable} candidates by the following steps.
+
+\begin{enumerate}
+    \item Include materials that;
+    \begin{itemize}
+        \item contain elements with more than $50\%$ natural abundance of 
+            zero spin isotopes,
+        \item crystallize in nonpolar space groups,
+        \item is present in the ICSD database, and
+        \item is calculated nonmagnetic
+    \end{itemize}
+    \item Pragmatically remove toxic, radioactive and otherwise 
+        ``difficult'' materials;
+    \begin{itemize}
+        \item exclude Th, U, Cd and Hg,
+        \item exclude any rare-earth metals and noble gases,
+        \item exclude Ru, Os, Fe or Ni.
+    \end{itemize}
+    \item Include only materials with a band gap larger than $0.5$eV by MP
+        PBE-GGA.
+    \item Ensure energy above hull is less than $0.2$ eV per atom.
+\end{enumerate}
+
+We then label \textbf{un}-suitable candidates amongst materials in 
+the ICSD database that crystallize in polar space groups, are calculated
+to be magnetic and have a band gap larger than $0.1$ eV by MP PBE-GGA.
+
 \subsubsection*{The augmented Ferrenti approach}
+In the second approach, we adjust the first approach in order to
+improve the dataset. This approach is therefore named
+\emph{the augmented Ferrenti Approach}.
+
+In the first approach we included critera that were not motivated by physically 
+motivated, but from a purely practical perspective, like excluding toxic and
+radioactive elements. Such criteria is not necessarily related to what makes 
+a material suitable for quantum technology - eventually it is up to the 
+experimentalist to decide the practicability of the employed material.
+Consequently, we remove stage two from the approach above. What is more, we will
+include a few more elements that has shown promising properties (REF??), but were
+initially excluded due to the lack of spin-zero isotopes.
+
+The following steps make up the process of choosing \textbf{suitable} candidates 
+in the \emph{augmented Ferrenti approach},
+\begin{enumerate}
+    \item Include materials that,
+    \begin{itemize}
+        \item contain elements where more than half have a natural abundance of zero spin
+            isotopes, except Al, P, Ga, As, B and N.
+        \item crystallize in non-polar space groups,
+        \item is present in the ICSD database,
+        \item is calculated nonmagnetic.
+    \end{itemize}
+    \item Only keep materials that have a band gap larger than 1.5 eV as
+        calculated by MP PBE-GGA,
+    \item Ensure energy above hull is less than 0.2 eV per atom. 
+\end{enumerate}
+
+For \textbf{unsuitable} candidates, we implement the same strategy as the non-augmented
+Ferrenti approach. The result is a somewhat unbalanced dataset, with up to 75 \% of the 
+materials found in the suitable group. However, the dataset is 78 \% larger than in
+approach 1.
+
 \subsubsection*{The insightful approach}
+The third approach is vastly different from the two first approaches in terms
+of labeling, as we apply knowledge from the field (REFS!!) 
+to pick our promising material host candidates. We therefore name this scheme 
+\emph{the insightful approach}.
+Due to the concern of having a too-small dataset, we will include
+materials that are promising and have shown suitable properties to
+accommodate deep defects that potentially can exhibit quantum effects.
+The approach to pick \textbf{suitable} candidates can be summed up as,
+\begin{enumerate}
+    \item Pick candidates that match the formulas [A BUNCH OF MATERIALS AND REFERENCES HERE] and are present in the ICSD database.  
+    \item Perform a manual screening for correct structures.
+\end{enumerate}
+
+After the first stage of picking candidates we are left with a list of 202 matching formulas which include 12 entries that have a band gap of less than $0.4$~eV.
+These structures are unstable in terms of energy above hull calculations, and will decompose other materials in the list with a band gap that is substantially above 0.5 eV.
+We include all except C (mp-568410),
+with MP-computed band gap of 0.12 eV - a metal according to AFLOW-ML and therefore 
+labeled as unsuitable instead.
+
+MORE ON MANUAL SCREENING....
+
+Since the dataset constituting suitable candidates are few, we add 400 \emph{unsuitable}
+candidates. These are picked at random from the pool of unsuitable candidates 
+from the two previous approaches, in addition to those that are marked unsuitable through
+the manual screening process.
+
 \subsubsection*{Comparing the approaches}
+
+Figure 5.3 would be nice to have here :) Also figure 5.4.
+
+\subsection*{Predicting Novel Material Hosts for Quantum Technology} %Sebastian / Oyvind (Oliver input in round 2)
 
@@
 \section*{Methods}
-%Methodology comes after concluding remarks, and is structured into subsections
+Should be rather short. Details can be included in a Supplementary Material.
 
-\subsection*{Databases} %Oliver and Øyvind 
+\subsection*{Information Flow}
+
+\subsection*{Databases} %Sebastian, Oliver and Øyvind 
+The Materials Project (REF) is an open-source project based on the Vienna Ab Initio Package (VASP) (REF).
+The functional GGA is used to calculate band structures, while for transition metals, a $+U$ correction is applied to correct for correlation effects (REF).
+The project is known as the initiator of materials genomics and offers a variety of calculated properties of over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
+
+The AFLOW (REF) repository is an automatic software framework that utilize the GGA-PBE functional within VASP.
+
 %Materials project, AFLOW, Open Quantum, JARVIS 
@@
 The data that support the plots within this paper and other findings of this study are
-available from the corresponding authors upon reasonable request.
+available from the corresponding authors upon reasonable request. [Marianne: I assume you want to add the Github link here?]
 
@@
 The codes developed in this study are available from the authors upon reasonable
-request.
+request. [Marianne: I assume you want to add the Github link here?]
 

### 2021-11-25 appendix/featurizerTable.tex
Updates from Overleaf

\begin{center}
\begin{longtable}{M{3.5cm} M{6.5cm} M{2.0cm}}
\caption{This work's chosen 39 featurizers from matminer. Descriptions are either found from Ref. \cite{Ward2018} or from the project's Github page. For entries lacking references, we refer to Ref.~\cite{Ward2018}.}
\label{table:featurizers} 
\hline 
Features & Description & Reference \\ 
\hline 
  \textbf{Composition features} & & \\ 
  AtomicOrbitals & Highest occupied molecular orbital (HOMO) & \cite{Kotochigova1997}  \\   
   & and lowest unoccupied molecular orbital (LUMO) &  \\   
  AtomicPacking-Efficiency & Packing efficiency & \cite{Laws2015}  \\   
  BandCenter & Estimate absolute position of band center  & \cite{Butler1978} \\   
   & using geometric mean of electronegativity &  \\  
  ElementFraction & Fraction of each element in a composition &    \\   
  ElementProperty & Statistics of various element properties & \cite{Ong2013,Ward2016, Deml2016}  \\   
  IonProperty & Maximum and average ionic character & \cite{Ward2016} \\   
  Miedema & Formation enthalpies of intermetallic compounds, solid solutions, & \cite{Weeber1987} \\   
   & and amorphous phases using semi-empirical Miedema model &  \\   
  Stoichiometry & $L^p$ norm-based stoichiometric attributes & \cite{Ward2016} \\   
  TMetalFraction & Fraction of magnetic transition metals & \cite{Deml2016}  \\   
  ValenceOrbital & Valence orbital attributes such as & \cite{Ward2016}  \\   
   &  the mean number of electrons in each shell &   \\   
  YangSolid-Solution & Mixing thermochemistry and size mismatch terms & \cite{Yang2012} \\
    \hline 
  \textbf{Oxide composition features} &  &  \\
  Electronegativity-Diff & Statistics on electronegativity difference & \cite{Deml2016} \\   
   &  between anions and cations & \\ 
  OxidationStates & Statistics of oxidation states & \cite{Deml2016}  \\   
\hline 
  \textbf{Structure features} & & \\   
  DensityFeatures & Calculate density, volume per atom and packing fraction & - \\   
  GlobalSymmetry-Features & Determines spacegroup number, crystal system  & - \\   
   & (1-7) and inversion symmetry & \\ 
  RadialDistribution-Function & Calculates the radial distribution  & - \\   
   & function of a crystal system & \\ 
  CoulombMatrix & Generate the Coulomb matrix for nuclear interactions  & \cite{Rupp2012}  \\    
  %CoulombMatrix & Generate the Coulomb matrix, which is a representation of the nuclear coulombic interaction of the input structure. & \cite{Rupp2012}  \\      
  PartialRadial-Distribution-Function & Compute the partial radial distribution  & \cite{Schuett2014}  \\   
   & function of a crystal structure & \\ 
  SineCoulomb-Matrix & Computes a variant of the coulomb matrix & \cite{Faber2015}  \\   
   & developed for periodic crystals & \\ 
  EwaldEnergy & Computes the energy from Coulombic interactions  & \cite{Ewald1921}  \\   
   & based on charge states of each site & \\ 
  BondFractions & Compute the fraction of each bond in a  & \cite{Hansen2015}  \\   
   & structure, based on nearest neighbors & \\ 
  Structural Heterogeneity & Calculates the variance in bond lengths and  & \cite{Ward2017}  \\   
   & atomic volumes in a structure & \\ 
  MaximumPacking-Efficiency & Calculates the maximum packing efficiency of a structure & \cite{Ward2017} \\   
  Chemical-Ordering & Computes how much the ordering of species  & \cite{Ward2017}  \\   
   & differs from random in a structure & \\ 
  XRDPowder-Pattern & 1D array representing normalized powder diffraction & \cite{Ong2013} \\ 
   &of a structure as calculated by pymatgen  & \\ 
    \hline 
  \textbf{Site features} & & \\
  AGNI-Fingerprints & Calculates the product integral of RDF & \cite{Botu2014}  \\    
   & and Gaussian window function  & \\ 
  AverageBond- Agle & Determines the average bond angle of a specific  & \cite{Jong2016}  \\
   & site with its nearest neighbors  & \\ 
  AverageBond-Length & Determines the average bond length between one specific site & \cite{Jong2016}  \\ 
   & and all its nearest neighbors  & \\ 
  BondOrientational-Parameter & Calculates the averages of spherical  & \cite{Seko2017, Steinhardt1983}  \\ 
   & harmonics of local neighbors & \\ 
  ChemEnvSite-Fingerprint & Calculates the resemblance of given sites to ideal & \cite{Waroquiers2017, Zimmermann2017}  \\   
   & environment using pymatgens ChemEnv package  & \\ 
  Coordination-Number & The number of first nearest neighbors of a site & \cite{Zimmermann2017}  \\
  CrystalNN-Fingerprint & A local order parameter fingerprint for periodic crystals & -  \\   
  GaussianSymm-Func & Calculates the gaussian radial and angular symmetry functions  & \cite{Behler2011,Khorshidi2016}  \\   
   & originally suggested for fitting machine learning potentials &  \\ 
  GeneralizedRadial-Distribution-Function & Computes the general radial distribution function for a site & \cite{Seko2017}  \\   
  LocalProperty-Difference & Computes the difference in elemental properties  & \cite{Ward2017, Jong2016} \\   
   & between a site and its neighboring sites & \\ 
  OPSite-Fingerprint & Computes the local structure order parameters & \cite{Zimmermann2017} \\   
   & from a site's neighbor environment  & \\ 
  Voronoi-Fingerprint & Calculates the Voronoi tessellation-based  & \cite{Peng2011,Wang2019} \\
   & features around a target site & \\ 
\hline     
  \textbf{Density of state features} & & \\
  DOSFeaturizer & Computes top contributors to the density of  & \cite{Dylla2020} \\ 
  & states at the VBM and CBM  & \\ 
  %DOSFeaturizer & Computes top contributors to the density of states at the valence and conduction band edges. Thus includes chemical species, orbital character, and orbital location information. & \cite{Dylla2020} \\
  \hline  
  \textbf{Band structure features} & & \\
  BandFeaturizer & Converts a complex electronic band  & - \\ 
   &structure into discrete quantities  & \\ 
%BandFeaturizer & Converts a complex electronic band structure into quantities such as band gap and the norm of k point coordinates at which the conduction band minimum and valence band maximum occur. & - \\
\hline 
\end{longtable}
\end{center}

### 2021-11-25 figures/tikz-plots/augmented-ferrenti-approach.tex
Updates from Overleaf

\begin{figure}[!ht]
  \centering
  \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$22550$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$7557$]
      [$14993$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$8143$]
      [$14407$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$7199$]
      [$15351$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$8762$]
      [$13788$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
\vspace*{-95mm}
\caption{Visualization of the predicted material candidates from the augmented Ferrenti approach. The green nodes display the number of predicted suitable candidates while unsuitable ones are marked in red.} 
\label{fig:02-predictions}
\end{figure}

### 2021-11-25 figures/tikz-plots/ferrenti-approach.tex
Updates from Overleaf

\begin{figure}[t]
  \centering
  \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$23623$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$11243$]
      [$12380$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$12308$]
      [$11315$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$9345$]
      [$14278$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$11835$]
      [$11788$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
\vspace*{-95mm}
\caption{Visualization of the predicted material candidates from the Ferrenti approach. The green nodes display the number of predicted suitable candidates while unsuitable ones are marked in red.}
\label{fig:01-predictions}
\end{figure}

### 2021-11-25 figures/tikz-plots/insightful-approach.tex
Updates from Overleaf

\begin{figure}[!ht]
  \centering
  \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$24544$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$23702$]
      [$842$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$23347$]
      [$1197$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$24001$]
      [$543$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$23948$]
      [$596$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
\vspace*{-95mm}
\caption{Visualization of the predicted material candidates from the insightful approach. The green nodes display the number of predicted suitable candidates while unsuitable ones are marked in red.} 
\label{fig:03-predictions}
\end{figure}

### 2021-11-25 figures/tikz-plots/prediction-fig.tex
Updates from Overleaf

\begin{figure}[t]
  \centering
  \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$23623$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$11243$]
      [$12380$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$12308$]
      [$11315$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$9345$]
      [$14278$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$11835$]
      [$11788$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
%\vspace*{-95mm}
\begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$22550$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$7557$]
      [$14993$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$8143$]
      [$14407$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$7199$]
      [$15351$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$8762$]
      [$13788$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
%\vspace*{20mm}
 \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$24544$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$23702$]
      [$842$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Decision tree,node box,alias=a1
      [$23347$]
      [$1197$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Random forest,node box,alias=a1
      [$24001$]
      [$543$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$23948$]
      [$596$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
      ]
    ]
    ]
  \end{forest}
\vspace*{-95mm}
\caption{Visualization of the predicted material candidates from the (a) Ferrenti, (b) augemented Ferrenti and (c) insightful approaches. The green nodes display the number of predicted suitable candidates while unsuitable ones are marked in red.}
\label{fig:predictions}
\end{figure}

### 2021-11-25 figures/tikz-plots/validation-tree.tex
Updates from Overleaf

\begin{figure}[!ht]
  \centering
  \begin{forest}
    for tree={l sep=1em, s sep=1em, anchor=center, inner sep=0.3em, fill=red!50, circle}
    [$625$ ABO$_3$ compounds, node box, alias=bagging, above=1em
    [Logistic regression,node box,alias=a1
      [$414$]
      [$211$,fill=yellow!50,edge label={node[above=1ex,yellow arrow]{}}
        [$195$]
        [$16$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
        ]
      ]
    ]
    [Decision tree,node box,alias=a1
      [$382$]
      [$243$,fill=yellow!50,edge label={node[above=1ex,yellow arrow]{}}
        [$212$]
        [$31$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
        ]
      ]
    ]
    [Random forest,node box,alias=a1
      [$438$]
      [$187$,fill=yellow!50,edge label={node[above=1ex,yellow arrow]{}}
        [$157$]
        [$30$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
        ]
      ]
    ]
    [Gradient boost,node box,alias=a1
      [$419$]
      [$206$,fill=yellow!50,edge label={node[above=1ex,yellow arrow]{}}
        [$198$]
        [$8$,fill=green!50,edge label={node[above=1ex,green arrow]{}}
        ]
      ]
    ]
    ]
  \end{forest}
\vspace*{-95mm}
\caption{A figure visualizing the top-down workflow of predicting new ABO$_3$ cubic perovskites for all models. First layer of predictions display the number of predicted perovskites in yellow, while nonperovskites in red. Thereafter follows the prediction of perovskites into cubic perovskites in green, while only perovskites as red.}
\label{fig:workflow}
\end{figure}

### 2021-11-25 paper.tex
Updates from Overleaf

--- 2021-08-21 paper.tex
@@
 \usepackage{lipsum}
-\usepackage{subfig}
+% \usepackage{subfig} %not compatible with subcaption
 % \usepackage{braket}
+\usepackage{siunitx}
+\usepackage{color}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{tikz,pgfplots}
+\usepackage{makecell}
+\captionsetup[table]{skip=10pt}
+\pgfplotsset{compat=1.17}
+\sisetup{separate-uncertainty}
+\usepackage{hyperref} 
+\usepackage{longtable}
+
+\usepackage{forest}
+\forestset{
+    .style={
+        for tree={
+            base=bottom,
+            child anchor=north,
+            align=center,
+            s sep+=1cm,
+    straight edge/.style={
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -- (.child anchor);}
+    },
+    if n children={0}
+        {tier=word, draw, thick, rectangle}
+        {draw, diamond, thick, aspect=2},
+    if n=1{%
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {Y};}
+        }{
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {N};}
+        }
+        }
+    }
+}
+\tikzset{
+  green arrow/.style={
+    midway,green,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
+    allow upside down
+  },
+  yellow arrow/.style={
+    midway,yellow,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
+    allow upside down
+  },
+  black arrow/.style 2 args={-stealth, shorten >=#1, shorten <=#2},
+  black arrow/.default={1mm}{1mm},
+  tree box/.style={draw, rounded corners, inner sep=1em},
+  node box/.style={white, draw=white, text=black, rectangle, rounded corners},
+}
 
@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+\affiliation{Sopra Steria, N-0185 Oslo, Norway}
+
 \author{Marianne Etzelm\"uller Bathen}
@@
 \affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
+
+\author{Sebastian G. Winther-Larsen}
+\affiliation{Menon Economics, N-0369 Oslo, Norway}
+\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Øyvind Sigmundson Schøyen}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
-\author{Sebastian G. Winther-Larsen}
+
+\author{Morten Hjorth-Jensen}
+\affiliation{Department of Physics and Astronomy and Facility for Rare Ion Beams, Michigan State University, East Lansing, MI 48824, USA}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
-\author{Morten Hjorth-Jensen}
-\affiliation{Facility for Rare Ion Beams and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
-\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Lasse Vines}
@@
 
-Semiconductor materials provide a compelling platform for quantum
-technology, and a vast amount of materials and their properties can be
-found in high-throughput databases.  However, filtering among these
-materials in order to find novel candidates for quantum technology is
-a challenge. Therefore, we provide a framework for the automatic
-discovery of promising solid-state material hosts using machine
-learning methods.
+Semiconductor materials provide a compelling platform for quantum technology, and a vast amount of materials and their properties can be found in high-throughput databases.
+However, filtering among these materials in order to find novel candidates for quantum technology is a challenge.
+Therefore, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods.
 
 %Main message 1: develop methodology for data mining and machine learning for materials properties 
-We have developed data extraction tools for numerous material science
-databases, and constructed over $4800$ physics-informed features for a
-dataset consisting of more than $25000$ materials.  Furthermore, we
-have developed and implemented three data mining approaches, termed
-\textit{the Ferrenti approach}, \textit{the augmented Ferrenti
-  approach} and \textit{the insightful approach} for defining three
-distinct training sets for the supervised machine learning algorithms
-logistic regression, decision tree, random forest and gradient boost
-to be trained on.
+We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25000$ materials.
+Furthermore, we
+have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the insightful approach} for defining three distinct training sets for the supervised machine learning algorithms
+logistic regression, decision tree, random forest and gradient boost to be trained on.
 
 % Main message 2: Use method to propose new materials that are promising quantum hosts 
-We find a lack of consistent results for the Ferrenti approach and the
-augmented Ferrenti approach due to an overly broad formulation of the
-training set, whereas the restrictions set in the insightful approach
-proved suitable. All models agreed on $214$ predicted candidates, with
-examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP,
-and InAs. All approaches and all models agreed on a subset of $47$
-eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary
-compounds.
+We find a lack of consistent results for the Ferrenti approach and the augmented
+Ferrenti approach due to an overly broad formulation of the training
+set, whereas the restrictions set in the insightful approach proved suitable. All
+models for the insightful approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, 
+MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs. All three approaches and all ML
+models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary,
+and $10$ tertiary compounds.
 
@@
 \section*{Introduction}%Oliver and Morten and Marianne (semiconductor portion)
-To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored.
-The quantum computer, together with the complementary quantum technologies of sensing and communication, is becoming a frontrunner in the race for solutions.
-Discuss recent benchmarks for quantum computing \cite{Arute_2019}.
+The second quantum revolution is heralding the development of new solutions and devices based on quantum technology \cite{Acin2018}.
+Among the promising prototypes that are already available we find in vivo sensing of magnetic fields in cells [], secure communication over large distances by separation of entangled photons [], and finally the demonstration of quantum computing [].
+Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
+Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as the quantum internet. 
+Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a 200'000 core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
+And IBM announced recently its 127 qubit quantum processor.
 
-Limitations of quantum computing and technology building blocks. Drawbacks of superconductors. Semiconductors are a promising platform. Example of NV center in diamond \cite{Doherty_2013}.
+%Figure 1 introduction schematic 
+\begin{figure}[t]
+    \centering
+    %\includegraphics[width=0.6\textwidth]{figures/paradigms.png}
+    \includegraphics[width=0.9\textwidth]{figures/ht-workflow.jpg}
+    \caption{[PLACEHOLDER] Schematic of an example workflow in material informatics. 
+    %\marianne{Morten: can you please add the other schematic figure we discussed as placeholder?
+Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
+We should have just one figure I think, perhaps even combining the paradigms and explaining the material informatics worklow.}
+    }
+    \label{fig:paradigm}
+\end{figure}
 
-%From thesis - rewrite 
-Unfortunately, there are substantial challenges associated with the modern quantum platforms simultaneously as the selection of quantum platforms are slim.
-The majority of discoveries of potential quantum platforms have so far happened by serendipity, and there is an urgent need for new and better materials that can escalate the effort for a sustainable future.
+Several platforms are available for the development of quantum technologies (QT) but the materials and fabrication technologies are less mature than those for, e.g., classical computers and sensors. 
+An important concern in this context is that of scalability. 
+For example, the best performing quantum computer prototypes available today rely on superconducting electronics or trapped ions.
+Both technologies require millikelvin temperatures to operate, fabrication is challenging, and the stability of interactions between qubits is an issue.
+Instead, semiconductors are emerging as a promising alternative platform, offering competitive characteristics combined with the possibility of room temperature operation and mature and scalable material processing and fabrication.
 
-The fourth science paradigm introduces the potential of targeted search for promising material systems to act as qubit hosts. 
-Herein, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods. 
-Initial database building similar to Ferrenti et al \cite{Ferrenti2020}.
+Quantum technologies based on semiconductors rely on either defects or quantum dots where the latter kind can be of the self-assembled or fabricated type. 
+Semiconductor defects can act as single-photon emitters or spin centers and are compatible with the three main QT categories of computing, communication and sensing.  
+These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap.
+So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliable single-photon emission and long spin coherence times.
+The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared and telecom coupled with more mature material processing and fabrication  \cite{Bathen2021}.
+However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
+Another important issue is that the understanding of the requirements for a material to enable quantum compatible properties to manifest remains lacking,
+%The plethora of possible emitters and spin centers formed by semiconductor defects or nanostructures come with different characteristics that are compatible with specific applications.  
+%Additionally, the understanding of what exactly makes a semiconductor based quantum platform suitable for QT is scarce, 
+and the selection of quantum compatible semiconductor host materials is slim.
 
-\begin{figure}
-    \centering
-    \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
-    \caption{Placeholder for workflow.
-Morten: can you please add the other schematic figure we discussed as placeholder?
+The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for 
+%new and better materials that can escalate the effort for a sustainable future. 
+a better understanding of how different materials properties manifest. 
+In this context, a framework for dedicated materials search and analysis is needed. 
+The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
+The fourth paradigm
+%, as illustrated by the schematic in Figure~\ref{fig:paradigm}(a), 
+introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.  
+Instead of searching through a host of signals for the one that matches our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies. 
+This is made feasible by the availability of databases containing material properties for a wide range of different systems.
+In this work, the data in question is provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
+Combined with machine learning algorithms we provide a path towards precise classification of qubit candidates.
+The inclusions of machine learning methods follows recent trends in applications of
+statistics, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
+
+In this work we provide a framework for the data mining and automated discovery of promising solid-state material hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
+The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical or experimental data is available.
+The method that was developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+Matminer \cite{Ward2018} is then used for material analysis to featurize the extracted data. 
+An important feature of the work is the database building and development of the training sets for the machine learning models.
+We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020}  \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the insightful approach}.
+We find that the former two methodologies base their data extraction protocols on practical considerations, such as experimental availability in specific forms or the toxicity of the materials, leading to few observable trends in the materials predicted by well-tested machine learning algorithms, such as logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{mehta2019,hastie2009}.
+The third approach, on the other hand, relies on materials with experimentally proven advantageous characteristics in the training set.
+This more restricted approach proved more suitable than the other two and yielded $214$ predicted candidates with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
+%\begin{itemize}
+ %   \item Data was extracted from databases materials project ... 
+ %   \item Featurization using matminer 
+ %   \item Initial database building similar to Ferrenti et al \cite{Ferrenti2020}, but method is expanded to focus mainly on physical aspects. 
+ %   \item Machine learning on top.  
+%\end{itemize}
+
+%\section*{Theoretical Background and Experimental Data}
+
+%Quantum technologies, including sensing, communication and computing, are intriguing because of the new capabilities they offer.
+However, realization of large-scale fabrication for these techniques requires further technological development.
+The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale.
+Instead, recent developments have seen/heralded the rise of semiconductors as possible host materials for a variety of quantum devices.
+Semiconductor quantum dots or point defects could prove easier to combine with existing devices, and room temperature operation of prototype communication and computing devices has been shown.
+However, this technology is still in the early stages, and the issues left to address include scalable and reproducible device fabrication, identification of ideally suited host candidates, and, importantly, understanding the requirements for a material to act as a good host remain unclear.
+
+%\subsection*{Semiconductors as a Quantum Host} 
+%Quantum technologies commonly rely on a quantum bit or qubit as the basis for operation.
+\marianne{Some schematic is shown in Figure~\ref{fig:qt}}.
+For all applications, the basic requirement is a two-level quantum system which is essentially isolated from its environment, ensuring sufficient stability to perform various operation.
+In other words, we search for systems which exhibit a high degree of coherence.
+Additionally, the qubit state must be controlable via repeatable initialization, manipulation and read-out protocols.
+A set of requirements were formulated by DiVincenzo for the case of qubits and quantum computing \cite{DiVincenzo2000}.
+Below, these are rephrased to encompass qubit requirements for all three QT application areas:
+%\begin{itemize}
+ %   \item A scalable physical system with well-characterized qubits
+ %  \item Reliable qubit initialization protocols 
+ %   \item Quantum gates and protocols to operate on and control qubit states  
+ %   \item Qubit state coherence time must exceed gate operation time 
+ %   \item Qubit state read-out after operation, preferably optically.  
+%\end{itemize}
+
+%\begin{figure}[t]
+ %   \centering
+ %   \includegraphics[width=0.3\textwidth]{figures/qubit.png}
+ %   \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
+ %   \label{fig:qt}
+%\end{figure}
+
+%Discuss experimental data and the semiconductor platform. 
+%Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap.
+Importantly, deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT.
+A prime example is the nitrogen-vacancy (NV) center in diamond, which has been proposed as a contender for both computing, sensing and communication applications \cite{Doherty_2013}.
+The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for, e.g., stress tensor mapping \cite{Broadway2019} and optical imaging of living cells \cite{Lesage_2013}.
+Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second} \cite{Doherty_2013}, leading to demonstrations of entanglement and teleportation of two NV center spins \cite{Bernien2013,Pfaff_2014}.
+However, despite these promising discoveries, diamond  as a quantum platform comes with several important drawbacks.
+The relevant defects therein, such as the NV center, emit in the visible region of the spectrum which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology.
+Additionally, diamond is expensive, device fabrication is challenging and scalability is poor, leading to concerns in whether quantum technology device development will be realizable on this platform.
+Hence, we search among the plethora of available semiconductors for a platform that can deliver on the necessary parameters for QT applications while also, ideally, providing availability and scalable fabrication.
+In this context, the material properties that facilitate quantum compatible characteristics such as single-photon emission and coherent spin manipulation to manifest must be identified.
+
+%\begin{figure}[t]
+%    \centering
+%    \includegraphics[width=0.5\textwidth]{figures/NV.png}
+%    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
+%    \label{fig:defects-dft}
+%\end{figure}
+
+%\begin{figure}[t]
+ %   \centering
+ %   \includegraphics[width=0.5\textwidth]{figures/defects-sic.pdf}
+ %   \caption{[PLACEHOLDER] Schematic representation of different quantum compatible defects in SiC and the energy levels they introduce into the band gap, from Ref.\cite{Bathen2021}.} 
+ %   \label{fig:defects-sic}
+%\end{figure}
+
+%Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
+In this context we consider single-photon emission and coherent spin manipulation for systems related to point defects primarily, but also self-assembled or lithographically structured quantum dots.
+\marianne{A (placeholder) schematic of quantum compatible defects and the energy levels they introduce into the band gap of 4H-SiC is shown in Figure~\ref{fig:defects-sic}.} Most of the defects in the table have yet to be identified, and different material related challenges complicate the implementation of defects for QT.
+A set of common denominators for materials that contain qubit defects was summarized by Weber et al.
+\cite{Weber2010}:
+%\begin{itemize}
+ %   \item Wide band gap to facilitate localized deep levels (physical)
+ %    \item Low spin orbit coupling to extend spin coherence times (physical) 
+ %   \item Low el-phonon coupling for sharp emission lines (physical) 
+ %   \item Availability as high-quality, bulk, or thin-film single crystals (practical)
+ %   \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
+%\end{itemize}
+%Note the division between physical and practical requirements in the list above.
+The physical criteria refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to the external influences that simplify measurement and detection of the interesting properties.
+In this work, we will focus primarily on the former set of criteria, as understanding them better may give further insights into the makings of a reliable QT platform.
+
+%In addition to obtaining greater understanding of  exactly what constitutes a good quantum host material, we must recognize that different defect and material types may suit different needs.
+Therefore, we aim to develop a bigger bank of candidate defects and materials.
+So far, detection of QT compatibility in semiconductors has been rather slow, depending on signal detection and later identification in each specific material.
+Instead, we are looking for a top-down approach to \textit{predict} promising materials, enabling a guiding of experimental efforts.
+
+%\subsection*{Density Functional Theory Output} %Marianne 
+%The density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
+DFT provides a method for iteratively solving the Schr{\"o}dinger equation based on initial guesses for the atomic potentials.
+Using DFT calculations, we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
+
+%The fundamental challenge of the DFT is that the calculations rely on approximations to the potential function of a system as expressed by the exchange-correlation (XC) functional, which is not known for bulk materials.
+The XC functional is usually grouped into three categories based on the level of theory.
+The local density approximation (LDA) takes the homogeneous electron gas as a starting point, while the more advanced general gradient approximation (GGA) includes also the gradient in local electron gas variations.
+These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron is allowed to interact with itself) [Ref SchollSteckel] \cite{Freysoldt2014}.
+More recent developments have seen the widespread use of hybrid functionals such as the HSE06 incorporating a portion of Hartree-Fock exact exchange \cite{Heyd2003},  albeit at a much greater computational cost.
+
+%Despite the limitations imposed by the approximate nature of the XC functional, and the band gap error of LDA and GGA level functionals, DFT can be a powerful tool when predicting, designing and interpreting experiments.
+Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict new candidate QT hosts.
+The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}.
+Note that the PBE functional tends to underestimate the band gap of semiconductor materials.
+Nonetheless, a larger data set is available than for, e.g., HSE06, and many trends are conserved also with PBE.
+The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the electronegativity, the electron-phonon coupling and magnetic properties.
+
+%\begin{figure}[t]
+%    \centering
+%    \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
+%    \caption{[PLACEHOLDER for workflow] Morten: can you please add the other schematic figure we discussed as placeholder?
 Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
 }
-    \label{fig:ht-workflow}
-\end{figure}
+%    \label{fig:ht-workflow}
+%\end{figure}
 
-\section*{Theoretical Background and Experimental Data} 
-%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics. 
-Quantum technologies, including sensing, communication and computing, 
-are intriguing because of the new capabilities they offer. 
-However, realization of large-scale fabrication for these techniques requires further technological development. 
-The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale. 
-Instead, recent developments have seen/heralded the rise of semiconductors as host materials for a variety of quantum devices.
-Much easier to combine with existing devices, and RT operation has been shown.
-However, the ideal host has yet to be identified, and the requirements for acting as a good host remain unclear. 
-Different methods are needed.
+%\subsection*{Machine Learning}
 
-\subsection*{Semiconductors as a Quantum Host} %Marianne and Lasse 
-The key feature when considering a quantum object for application is coherence, which is again tightly connected to the concept of coherence. 
-For all applications, the basic requirement is a two-level quantum system which is quite isolated so the levels remain stable. 
-Also need to control the qubit state via initialization, manipulation and read-out. 
-Requirements \cite{DiVincenzo2000,Weber2010}: 
+%Should contain a brief description of the four ``algorithms'':
+%\begin{itemize}
+ %   \item Logistic regression
+ %   \item Decision trees
+ %   \item Random forest
+ %   \item Gradient boost
+%\end{itemize}
+
+%Why these? Works well out of the box, I guess. Readily available in scikit-learn.
+
+\section*{Results and discussion}
+%Includes discussion of results.
+
+\subsection*{Information Flow}  %Sebastian/Oliver (Marianne) 
+% MEB: Since Methods are at the end, I propose to put part of this
+% discussion in the Results section. 
+% This is because it is an important result of the work, and also
+% because it is important to understand the rest of the paper
+
+The information stream in this work can be regarded as many
+modular parts connected in logical pieces. The initial step for
+gathering material data and building features is visualized by the
+the flowchart in Figure~\ref{fig:flowchart-makedata}. 
+Initially, we start by extracting all entries in
+the Materials Project that matches a specific query.
+
+\input{figures/tikz-plots/flow-chart-data-extraction.tex}
+
+\input{figures/tikz-plots/flow-chart-featurization.tex}
+
+Thereafter, we apply Matminer’s \cite{Ward2018}
+featurization tools to make thousands of features of the data.
+The conditions for this initial query are that the materials must derive from experimental data, and have a band gap wider than $0.1$~eV.
+In a parallel step, entries that are deemed
+similar to the entries from the initial query
+are extracted from 
+OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, 
+AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, 
+AFLOW-ML \cite{Isayev2017},
+and
+Citrine Informatics REF!??. The results of these steps are combined into
+a data set for further analysis.
+
+A schematic describing the featurization process in Matminer is shown in Figure~\ref{fig:flowchart-featurization}. 
+\textbf{[Describe it and say something about which features we choose.]}  
+The 39 features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
+
+\subsection*{Data Mining}
+
+After compiling a dataset from the procedure outlined above, we 
+face a challenge in terms of defining a training set that %we can train data on. 
+can be used to train an ML algorithm. 
+This is challenging for two reasons. 
+Firstly, although defects like the NV center in diamond and emitters in SiC are becoming
+increasingly well studied, few candidate materials are known. An additional consideration
+is that the physical mechanisms promoting favorable defect properties are not fully understood. 
+Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly
+intricate. 
+%This is not only challenging due to the lack of known suitable candidates (1),  but also due to the intricacy of defining materials as unsuitable candidates (0). 
+We follow three separate procedures to define a training set consisting of both suitable and unsuitable material candidates for QT.
+
+\subsubsection*{The Ferrenti approach}
+
+The first approach to defining a training set is based on the criteria
+from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+They suggest a data mining process consisting of four stages by 
+systematically evaluating the suitability of host materials from
+the Materials Project.
+
+In this framework, we label \textbf{suitable} candidates by the following steps. 
+\begin{enumerate}
+    \item Include materials that;
     \begin{itemize}
-    \item A scalable physical system with well-characterized qubits
-    \item Reliable qubit initialization protocols 
-    \item Need quantum gates to operate on qubits 
-    \item Qubit state coherence time must exceed gate operation time 
-    \item Need to read out qubit state after operation. 
+        \item contain elements with more than $50\%$ natural abundance of 
+            zero spin isotopes,
+        \item crystallize in non-polar space groups,
+        \item are present in the ICSD database, and
+        \item are calculated to be nonmagnetic. 
     \end{itemize}
+    \item Pragmatically remove toxic, radioactive and otherwise 
+        ``difficult'' materials;
+    \begin{itemize}
+        \item exclude Th, U, Cd and Hg,
+        \item exclude any rare-earth metals and noble gases,
+        \item exclude Ru, Os, Fe or Ni.
+    \end{itemize}
+    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional. 
+    \item Ensure that energy above hull is less than $0.2$~eV per atom.
+\end{enumerate}
 
-%Discuss experimental data and the semiconductor platform. 
-Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap. 
-Importantly, such deep levels can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT. 
-A prime example is the nitrogen-vacancy center in diamond, which has been proposed 
-as a contender for both qubit, sensing and communication applications \cite{Doherty_2013}. 
-The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, exhibiting entangled photons that have been separated by ... km []. 
-Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence of 1 ms []. 
-Qubit operations and entanglement have been demonstrated []. 
-However, emission wavelength is not ideally compatible with fiber optic technology (need telecom range), spin coherence is good but could be better, and sensing is good.
+We then label \textbf{unsuitable} candidates as materials in the ICSD database that crystallize in polar space groups, are calculated 
+to be magnetic and have a band gap larger than $0.1$~eV as calculated by PBE-GGA.
 
-\begin{table}[t]
+\subsubsection*{The augmented Ferrenti approach}
+In the second approach, we adjust the first approach in order to 
+improve the dataset. This approach is therefore named
+\emph{the augmented Ferrenti approach}.
+
+In the first approach we included criteria that were not physically motivated, but instead based on a purely practical perspective, like excluding toxic and
+radioactive elements. Such criteria are not necessarily related to what makes 
+a material suitable for quantum technology - eventually it is up to the 
+experimentalist to decide the practicality of the material to be employed. 
+Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
+What is more, we will include a few additional elements that have shown promising properties, but were initially excluded due to the lack of spin zero isotopes.
+
+The following steps make up the process of choosing \textbf{suitable} candidates 
+in the \emph{augmented Ferrenti approach},
+\begin{enumerate}
+    \item Include materials that; 
+    \begin{itemize}
+        \item contain elements where more than half have a natural abundance of zero spin isotopes, except Al, P, Ga, As, B and N, 
+        \item crystallize in non-polar space groups,
+        \item are present in the ICSD database,
+        \item are calculated to be nonmagnetic. 
+    \end{itemize}
+    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA,
+    \item Ensure energy above hull is less than $0.2$~eV per atom. 
+\end{enumerate}
+
+For \textbf{unsuitable} candidates, we implement the same strategy as the non-augmented
+Ferrenti approach. The result is a somewhat unbalanced dataset, with up to $75 \ \%$ of the 
+materials found in the suitable group. However, the dataset is $78 \ \%$ larger than for
+the Ferrenti approach.
+
+\subsubsection*{The insightful approach}
+The third approach differs substantially from the first two approaches in terms 
+of labeling, as we apply knowledge from the field (see, e.g., Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)   
+to pick our promising material host candidates. We therefore name this scheme 
+\emph{the insightful approach}. 
+Due to the concern of having a too-small dataset, we will include
+materials that are promising and have shown suitable properties to 
+accommodate deep defects that potentially can exhibit quantum effects. 
+Materials where properties like single-photon emission and spin manipulation are attributed to quantum dot self-assembled formation or lithographic structuring will also be included in this context.  
+The approach to pick \textbf{suitable} candidates can be summed up as;   
+\begin{enumerate}
+    \item Pick candidates that match the formulas in Table~\ref{tab:qt-materials}, or the formulas ZnSe,  AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} or SiGe \cite{Hardy2019}. 
+    \item Make sure the candidates are present in the ICSD database.  
+    \item Perform a manual screening for correct structures.
+\end{enumerate}
+
+\begin{table}[b]
     \centering 
+    \caption{Overview of materials and defects that have been demonstrated to exhibit QT compatible characteristics such as single-photon emission and coherent spin manipulation.}
     \begin{tabular}{c|c|c|c}
-    Material & Band gap (eV) & Defect candidates & Reference \\
+    Material & Band gap (eV) & Defect candidates & References \\
     \hline
-    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\  
-    4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\ 
+    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Taylor2008,Balasubramanian_2009,Barclay2011,Gordon2013,Rogers_2014,Bhaskar_2018} \\
+    SiC & $2.2$-$3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018}  \cite{Weber2010, Son2020, Falk2013} \\
     Si & $1.1$ & P, G, unidentified & \cite{Muhonen_2014,Durand_2020,Redjem2020} \\ 
     (2D) \textit{h}-BN & $6.0$ & Unidentified defects & \cite{Tran_2016,Tran_2016b,Hayee_2020} \\ 
+    (2D) MoS$_2$, WSe$_2$, WS$_2$ & $<2.5$~eV & Bound excitons & \cite{Toth2019} \\
     ZnO & $3.4$ & Unidentified defects & \cite{Morfa2012} \\ 
@@
 
- ZnS [74], GaAs [75],
-GaN [76, 77 , 80] and AlN [78, 79],  [81].
+Table~\ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
+In this context, we consider single-photon emission and coherent spin manipulation.
+The table forms the basis for picking suitable candidates for the insightful approach. 
+The properties being studied arise from mechanisms related to, e.g., point defects, excitons, and both self-assembled and lithographically structures quantum dots. 
+Quantum emission signatures have been assigned to specific defects in diamond and SiC, but for most other materials, identification of the responsible defects still remains. 
+In the insightful approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set, but also the materials ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe that have been predicted to act as good quantum hosts based on favorable properties such as wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
 
-%QT requirements. 
-%What parameters are we looking for? 
-Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics. 
-Not all defects are identified, and challenges due 
-to the specific materials complicate the implementation of defects for QT. 
-There are some common denominators for the materials: 
-\begin{itemize}
-    \item Wide band gap to facilitate localized deep levels (physical)
-    \item Low spin orbit coupling to extend spin coherence times (physical) 
-    \item Low el-phonon coupling for sharp ZPLs (physical) 
-    \item Availability as high-quality, bulk, or thin-film single crystals (practical)
-    \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
-\end{itemize}
-Note the division between physical and practical requirements in the list above. 
-The physical ones refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to some more external influence that provides more easy measurement and detection of said properties.
-It is the former that we are interested in.
+After the first stage of picking candidates we are left with a list of 202 matching formulas which include 12 entries that have a band gap of less than $0.4$~eV.
+These structures are unstable in terms of energy above hull calculations, and will decompose into other materials in the list with a band gap that is substantially above $0.5$~eV.
+We include all of these structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
 
-Different defect and material types may suit different needs. 
-Therefore, we need a bigger bank of candidates. 
-Also, we do not fully understand exactly what constitutes a good quantum host material. 
-So far, detection of QT compatibility has been slow, as a signal is detected and then identified in a specific material. 
-We are looking for a top-down approach to instead predict promising materials, and guide experiments. 
-For this, we first need a large dataset.
+MORE ON MANUAL SCREENING....
+%% OH: Dirty details about suitable materials:
+Entries matching the formula C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier.
+%OH: Is discussed earlier in thesis but maybe neccessary to mention here?
+For C, we admit three-dimensional diamond-like structures as explicitly stated in the column tags at Materials Project.
+Additionally, we find many two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
+We add these as suitable candidates.
+Complex structures (eg.
+C$_{28}$, C$_{48}$, C$_{60}$) were moved to the test set.
+For SiC, we admitted all entries, which involved $2$H, $3$C, $4$H, $6$H and $15$R.
+Concerning BN, MoS$_2$, WSe$_2$ and  WS$_2$, we only admit two-dimensional structures.
+For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted suitable or not by the models in a later step.
 
-\subsection*{Density Functional Theory Output} %Marianne 
-Density functional theory has been exceptionally successful in predicting solid-state material properties 
-such as
+The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} has identified them as potentially promising candidates due to acceptable properties defined in requirements (H1-H4) in \autoref{ssec:qubit-material-host-requirements}.
+We note that only tetrahedrally coordinated structures of the given formulas were present after the band gap restriction of $0.5eV$.
 
-Data formats, limitations etc.
+The suitable candidates contain only compounds that are either elementary (unary) or binary.
+We do not want to discriminate based on the number of elements in a compound, therefore we remove the feature that describes the number of elements in a compound.
+After three stages, a total of $187$ entries were labeled as suitable candidates.
+%% OH: Stop details suitable materials
 
-Density functional theory is a versatile and powerful theoretical approach, enabling targeted study of semiconductor materials with many atoms. 
-Proven successful for material properties such as thermal stability, lattice parameters and band gap.
+Since the dataset constituting suitable candidates in the third approach contains few entries, we add 400 \emph{unsuitable}
+candidates. These are picked at random from the pool of unsuitable candidates 
+from the two previous approaches, in addition to those that are marked as unsuitable through
+the manual screening process. 
+See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the insightful approach.
 
-\subsection*{Material Informatics} %Øyvind (Oliver)    
-%Data mining, screening
-
-\subsection*{Machine Learning} % Morten
-
-\section*{Results}
-Includes discussion of results.
-
-\subsection*{Information Flow}  %Sebastian/Oyvind (Marianne) 
-Includes results from data mining and description of the three approaches. 
-%MEB: Since Methods are at the end, I propose to put part of this discussion in the Results section. 
-%This is because it is an important result of the work, and also because it is important to understand the rest of the paper
-
-\subsection*{Optimization of Machine Learning Models} %Morten (Oliver input in round 2)
-
-\subsection*{Predicting Novel Material Hosts for Quantum Technology} %Oyvind (Oliver input in round 2) 
-\subsubsection*{The Ferrenti approach} 
-\subsubsection*{The augmented Ferrenti approach}
-\subsubsection*{The insightful approach}
 \subsubsection*{Comparing the approaches}
 
-\section*{Discussion} % All - last thing we write  
-Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
+The three different methods for data mining place a particular emphasis on each of their particular goals.
+The Ferrenti approach depends on choosing only elements with zero spin isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding elements.
+Thus, the first approach targets a more narrow prediction space than the second approach does.
+However, perhaps the most restricted approach is the insightful approach.
+Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the insightful approach to provide an even narrower prediction space.
+\textbf{[Are there any pros or cons we could mention on narrow prediction spaces?]}
+
+%\marianne{Short paragraph here (or somewhere else) highlighting the potential issues with the two first approaches in terms of actually identifying any trends.}
+
+We provide a visualization of each approach's training data as a parallel coordinate plot for a few selected features in Figure~\ref{fig:parallel-coordinates-approaches}.
+Parallel coordinate schemes \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
+The selected features are found on the x-axis, while the y-axis shows the value of the data present.
+Thus, parallel coordinate plots can turn many-dimensional data into a compact two-dimensional representation.
+Due to possible data cluttering, the figure visualizes a random sample of each class with an upper limit of $250$ per class with transparent lines.
+The green and red polylines represent suitable and unsuitable candidates, respectively.
+
+The Ferrenti approach and the augmented Ferrenti approach share similarities; 
+for example, all unsuitable candidates exhibit polar space groups, and their upper limits for both ionic character and covalent range are equal for suitable candidates.  
+%such as having only unsuitable candidates with polar space groups and having an equal amount of upper limit for both ionic character and covalent range for suitable characters. 
+Additionally, the two approaches share that suitable candidates can consist of up to five different elements. 
+Interestingly, we observe that
+the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former. 
+%even if the augmented Ferrenti approach is less restricted, it appears that the entries span the same dimensions.
+
+The biggest difference is found for the insightful approach.
+The entries selected as suitable candidates do not exhibit any magnetization, even though there are both polar and non-polar space groups present.
+Additionally, the range of covalent radius and maximum ionic character span a substantially smaller space than the Ferrenti-based approaches.
+\textbf{This can be interpreted as ... }
+
+\begin{figure}[t] %!htp
+    \centering
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \input{figures/parallel-coordinates-plots/01-ferrenti-approach.pgf}
+    \end{subfigure}
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \input{figures/parallel-coordinates-plots/02-augmented-ferrenti-approach.pgf}
+    \end{subfigure}
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \input{figures/parallel-coordinates-plots/03-insightful-approach.pgf}
+    \end{subfigure}
+    \vspace*{-95mm}
+    \caption{Parallel coordinate plots for the different approaches.
+To limit the data cluttering, we have randomly collected up to $250$ entries for each class and made the lines transparent.
+For the insightful approach, we have used all the $187$ suitable candidates.
+The axes show total magnetization (mag) taken from the Mateirals Project (MP) database, space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) extracted from MP.}
+    \label{fig:parallel-coordinates-approaches}
+\end{figure}
+
+To visualize the complexity of the training sets, we have found the two largest eigenvalues of the covariance matrix of the initial data from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
+The resulting scatter plots are found in Figure~\ref{fig:2dscatterplotpca}.
+Green squares display suitable candidates and red triangles represent unsuitable candidates. 
+Due to the 
+%simplicity 
+complexity 
+of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are overlapping. 
+Hence, using these approaches to data mining could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT. 
+\textbf{Nonetheless, the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further. This could indicate ... } 
+In the case of the insightful approach, on the other hand, we can already start to see a trend where the upper left part of the figure is dominated by suitable candidates.
+Therefore, we can expect that the two Ferrenti approaches would need either supplementary dimensions for further distinguishing, or that it could prove challenging to find a generalized model.
+
+\begin{figure}[h] %!tbp
+    \centering
+    \begin{subfigure}{0.3\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
+    \end{subfigure}%
+    \begin{subfigure}{0.3\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.3\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
+    \end{subfigure}
+    \vspace*{-95mm}
+    \caption{Two-dimensional scatter plots for the three different approaches.
+We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components (PC1 and PC2) of the initial data from the Materials Project query.
+Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots.
+Green squares display suitable candidates and red triangles represent unsuitable candidates.}
+    \label{fig:2dscatterplotpca}
+\end{figure}
+
+%\marianne{Return here to the basic issues with the two first approaches, in that they perhaps rely too much on practicalities. }  
+It seems likely that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
+Where the insightful approach takes advantage of the experimental knowledge that is already available in the literature, the Ferrenti and augmented Ferrenti schemes
+%procedures 
+rely on assumptions of which material properties are responsible for the observed effect. 
+An additional factor to consider is the use of practical considerations when restricting the parameter space for material choice. 
+In short, a much clearer separation is observed for the insightful approach as compared to the others. 
+These observations constitute an important finding of the work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT. 
+The manual approach of selecting suitable candidates based on experimental findings yields strong indication that a trend does exist and thus is possible to identify. 
+Importantly, the presented methodology for selecting candidates as presented in the insightful approach can be adapted also to other material systems where a specific set of properties are desired but the specific mechanisms behind them are unknown.
+
+The constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
+We note that this complexity is not necessarily reflected in the descriptors.
+%Additionally, we acknowledge that many compositions deemed as suitable candidates consist of either rare or dangerous elements.
+By utilizing an enormously large database as Materials Project, we have to account for their ultimate goal - to model all possible materials and their properties.
+%The automated process of adding an entry to their database does not necessarily contain all relevant information about a respective material. This is information that needs to be added manually.
+Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
+Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
+Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
+Therefore, we are dependent on that the Materials Project has obtained data with high quality, and we note that it is likely that there are some errors present in our data sets.
+
+\subsection*{Predicting Suitable Material Hosts for Quantum Technology}
+
+Using the four algorithms, optimized at each of the three approaches, and applying them to the case of predicting materials as suitable material hosts for QT, yields 12 sets of results.
+In this chapter, we present sets of representative results for each approach.
+
+\subsubsection*{The Ferrenti Approach}
+%Should we include materials in training set? Or keep it, but move into data mining discussion?
+We first consider the machine learning classification of the test set based on the Ferrenti approach. 
+Notably we find that carbon in diamond-like structure is classified as a suitable candidate from the training set in the Ferrenti approach. 
+This is in agreement with the suitable candidates that were defined manually for the insightful approach. 
+Interestingly, from the training set of the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures are labeled as suitable. 
+%Out of the known suitable candidates defined for the insightful approach, we find carbon in diamond-like structures, but we also find two-dimensional carbon in graphite-like structures labeled as suitable.
+All structures of silicon are also labeled as suitable together with one entry of silicon carbide. 
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present.
+
+%\input{figures/tikz-plots/ferrenti-approach.tex}
+%\input{figures/tikz-plots/augmented-ferrenti-approach.tex} 
+%\input{figures/tikz-plots/insightful-approach.tex}
+
+\input{figures/tikz-plots/prediction-fig.tex}
+
+The number of candidates predicted by each of the four machine learning algorithms 'Logistic regression', 'Decision tree', 'Random forest' and 'Gradient boost' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach.
+From the training set of $23623$ materials, the four models consistently predict at least $11.000$ materials as promising candidates.
+All of the models agree on $6804$ suitable candidates, however, many of the materials are predicted with the probability similar to a coin-flip.
+If we were to raise the minimum bar of a prediction to
+$0.7$ instead of $0.5$, the models would only agree on around $3000$ suitable candidates. 
+Of the known suitable materials that were present in the training set, we find that all four models admit almost all materials with a chemical formula matching the known candidates.
+This can allow materials with unfortunate structures to be labeled as suitable candidates by all models.
+Consequently, the models do not recognize the strict band gap restriction, which makes it challenging to facilitate deep defects.
+Ideally, we would expect that the models would have probabilities lower than $0.5$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all models.
+
+\subsubsection*{The augmented Ferrenti Approach}
+
+%Should we include materials in training set? Or keep it, but move into data mining disc
+%MB I think it's fine here also 
+Next, we turn to the more liberal augmented Ferrenti approach.
+In the training set, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs, AlP, carbon in both diamond- and graphite-like structures, and AlN in three different structures.
+The training set includes a larger variety of known suitable candidates compared to the Ferrenti approach due to admitting more elements in the initial restriction.
+However, since we also included a larger band gap restriction of $1.5$~eV, we find a more sparse representation of each known chemical formula present in the training set.
+
+The four models predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the test set, where they all agree on a set of $9227$ predicted suitable candidates.
+Comparing to the training set reveals that all of the unlabeled known suitable candidates are, in fact, predicted as suitable candidates.
+Unfortunately, the models also yield predictions that do not match with what one would expect from physical considerations.
+All four machine learning models confidently predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl. 
+At least, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
+Furthermore, despite enforcing a larger band gap restriction of $1.5$~eV for the training set, we find that all models are predicting suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the models are not taking this important property into account when classifying the materials.
+
+\subsubsection*{The insightful approach}
+The ML models that were trained on the data set defined from the insightful approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
+%Trained on the training set defined as the insightful approach, the models are able to predict radically fewer suitable candidates compared to the two latter approaches. 
+A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision tree, random forest and gradient boost, respectively.
+All the four ML models agree on a total of $214$ suitable candidates.
+However, $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
+
+%Cut down the amount of information given on perhaps not so suitable candidates, while rather emphasis the good predicted suitable candidates?
+
+Initially, we consider the materials that were classified as suitable with a probability of $85 \ \%$ or higher by all the models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+The compound BN (mp-$1639$) is already present in the training data as a suitable candidate, and therefore we believe the models recognize this as a suitable candidate with high probability.
+Furthermore, two compositions of CdSe (mp-$2691$ and mp-$1070$) have been predicted as suitable, possibly as a consequence of CdS being present as a suitable candidate in the training set.
+The element S resides in the same group as Se, and the data shows that the two compounds of CdSe are associated with a calculated band gap of $0.5$ eV and $0.55$ eV, respectively, in the MP database.
+Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$~eV \cite{CelebiSerdar2007SaCo, BanerjeeR2000Eots}.
+%Unfortunately, Cd is a toxic metal which could make large scale fabrication challenging.
+
+We also find two compositions with the same chemical formula, the orthorhombic coordinated (mp-$629458$) and the chalcopyrite structured BC$_2$N (mp-$1008523$) where the first structure is in a polar space group while the latter is not.
+The band gaps are in MP calculated as $1.85$ eV and $1.65$ eV, respectively.
+BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN.
+Both structures have, as expected, strong covalent character and have been studied for application as nanostructures \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020} in ab-initio calculations.
+Of similar compounds, it has been predicted that the diamond-like structure of BC$_3$N can be a prominent spin qubit material host \cite{Wang2020SpinQB}.
+By creating a boron (B) vacancy, it will immediately lead to an NV center with similar properties as found in the NV center in diamond.
+If this is also possible for BC$_2$N, remains to be seen.
+We note that BC$_3$N is not present in MP, and therefore not present in our dataset.
+
+The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) show some similar properties in the data, and have band gaps of $0.30$, $1.18$ and $1.73$~eV, respectively.
+Single self-assembled InAs quantum dots have already been demonstrated \cite{Liu2018}, and is therefore an exciting possible material to use in quantum technology.
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized and contains the toxic element Cd, which could prove an obstacle for large scale utilization.
+CuI, however, has recently been synthesized and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
+Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the dataset than, e.g., the more covalent materials of Si, SiC and diamond.
+It seems that ionic character alone is not an obstacle, but it is unknown at this time whether CuI has higher potential for hosting single-photon emitters, spin-manipulation or QT operation via nanostructuring.
+Note that NaCl was not predicted as suitable for QT in the insightful approach.
+
+Lowering the probability requirement from $85 \ \%$ to $75 \ \%$ for all models results in $66$ materials. 
+The full list is contained in the Supplementary Material at \cite{supplementary}. 
+The list of predicted suitable candidates now includes ternary compounds of the formula ABC$_2$.
+The elements Ga, Cd and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Te, P or As may reside at the C site.
+Most of the formed compounds include toxic elements with one exception.
+This exception is ZnGeP$_2$ (mp-$4524$), which takes the chalcopyrite-like structure, with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database and an experimentally reported band gap of $1.99$~eV \cite{Xing1989}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, has strong covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
+We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains unknown  
+whether the candidate can facilitate the isolated deep energy levels often associated with defects showing quantum compatible properties. 
+%if the candidate can provide isolation and shelter to experimentally facilitate a deep defect with quantum effects.
+
+Among the $66$ materials that all models in the insightful approach agreed on with more than $75 \ \%$ probability, we emphasize the presence of Ge, GeC, BP and InP.
+Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
+%In fact, the first transistors were made in germanium due to their appealing electrical properties, but silicon took over as the material of choice for microelectronics due to the outstanding quality of silicon dioxide.
+%, which allowed the fabrication and integration of increasingly smaller transistors \cite{Scappucci2020, Pillarisetty2011}. 
+Ge has the highest hole mobility of semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization  \cite{Scappucci2020}.
+Furthermore, like SiC, Ge can take advantage of the mature large-scale fabrication of silicon due to their similar properties.
+Similar considerations could be made for the case of GeC. 
+Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalent material having a band gap of $1.8$~eV. 
+Interestingly, as SiC is widely known as highly suitable host material for QT compatible defects, we encourage further research on GeC due to its comparable properties with SiC.
+
+The compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures.
+The indirect band gaps of the different structures are calculated at $1.46$~eV and $1.1$~eV, respectively, as reported in the MP database.
+They are both nonmagnetic and share several properties with the entries mentioned above; including ...
+The compound is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
+
+Lastly, we will mention the prediction of InP (mp-$966800$) as a suitable candidate.
+The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
+InP is reported in the Materials Project to have a direct band gap of $0.51$~eV, and is considered as one of the most promising candidates
+to compete with 
+Cd- or Pb- based QDs for, e.g., display and lighting applications \cite{Zhang2020a, Won2019}.
+
+It is worth to mention that all models agree on several oxides being potential candidates when the probability cut-off is set low enough (but still above $50 \ \%$).
+However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list defining the $66$ suitable candidates in the Supplementary Material.
+Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
+Removing ZnO from the training set for the insightful approach might result in fewer or even no oxide compounts being predicted above the suitability limit.
+
+The work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020} suggests a list of $541$ viable hosts after the data mining procedure.  
+Of these, we find only a single material present in our list of $66$ candidates (see the Supplementary Material at \cite{supplementary}).
+This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
+Its band gap is $1.98$~eV in the MP database with the experimental value being $5.6$~eV  \cite{SaumGeorge1959}.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by the of Ref.~\cite{Ferrenti2020}.
+We believe that these criteria favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
+%\oliver{Maybe also see if other compounds that were present in training set are present in their 541 hosts. }
+
+%Supplementary information: List displaying the 66 predicted candidates that all models in the insightful approach agreed on with more than 75\% probability. %appendix/listof66materials
+
+\subsubsection*{Comparison of the approaches}
+
+Out of the three approaches, we find that the augmented Ferrenti approach is the least restricted approach and admits the most entries.
+The Ferrenti approach also admits a large number of entries, but is otherwise not very different from the augmented version.
+Importantly, by applying the four ML models to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
+Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the insightful approach predicts fewer suitable candidates where manually verification is achievable.
+Manual verification through a literature survey will often not be available, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics.
+
+It is important to note that the insightfull approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
+Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
+%We believe there are three reasons for this.  
+It is known that the GGA functional Materials Project applies is known to underestimate the band gap of many semiconductors. 
+%underestimating the band gap severely, and therefore there is a chance that the models consider the band gap as noise and not useful information. 
+It is therefore possible that the band gap is not considered an important parameter by the ML models. 
+%Understanding the motivation behind the classification of the models will be an important step towards understanding ... 
+Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
+Thus, one can argue that the models find other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
+
+We find that $119$ of the $214$ candidates predicted as suitable by the insightful approach (when the probability cut-off is set to [X]) were also selected by all models in the augmented Ferrenti approach.
+%Of the $214$ suitable candidates predicted by all models in the insightful approach, we find $119$ of them also predicted as suitable by all models in the augmented Ferrenti approach. 
+Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
+All approaches and their corresponding models agree on a $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+\textbf{The list of the $47$ materials agreed on by all models and all three approaches as suitable candidates with a probability $> X \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
+
+%\section*{Discussion} 
+% Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
+
+%\oliver{The following paragraphs are "disclaimers" where we list possible pitfalls and weaknesses of this experiment.
+Could also be incorporated in the discussion instead?} MB I moved it up to data mining
+
+%SHORT SUMMARY FIRST HERE.
+
+%Motivated by our findings, we believe that further computational, experimental, or theoretical verification after a prediction of a possible promising material remains an important step in this work.
+This step is part of the workflow for novel materials discovery, which is visualized in \autoref{fig:ht-workflow}.
+Nevertheless, we have provided an exploratory analysis for the discovery of novel materials to be used in QT.
+Considering the number of materials predicted as suitable candidates by our models and approaches, we hope it encouragesfurther studies and identification of possible new material hosts.
+
+%We find that including toxic materials etc in the training set is vital for reliable predictions.
+They can then later be excluded when planning experiments, but the practical considerations should be saved for last and not included in the initial criteria.
 
 \section*{Methods}
-%Methodology comes after concluding remarks, and is structured into subsections
+%Should be rather short. Details can be included in a Supplementary Material.
 
-\subsection*{Databases} %Oliver and Øyvind 
-%Materials project, AFLOW, Open Quantum, JARVIS 
-Mining.
+\subsection*{Information Flow}
 
-\subsection*{Material Informatics} %Oliver and Øyvind 
+\subsection*{Databases} %Sebastian and Oliver 
+The Materials Project \cite{Jain2013, Jain2018} is an open-source project based on the Vienna Ab Initio Package (VASP) \cite{Kresse1996}.
+The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional is used to calculate band structures, while for transition metals, a $+U$ correction is applied to correct for correlation effects \cite{Wang2006}.
+The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
+
+The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than 600.000 materials.
+The calculations are performed with the VASP software whereas the electron exchange and correlation are described with the PBE functional.
+The $+U$ extension is included for several calculations considering specific elements \cite{Stevanovic2012}.
+
+JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly 40.000 3D materials using the vdW-DF-OptB88 functional \cite{Thonhauser2007, Klimes2011}.
+Structures included in the database are originally taken from the Materials Project, and then re-optimized using the OPT-functional.
+Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap of each structure \cite{Choudhary2018a}.
+
+The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
+They utilize the PBE functional within VASP
+%with projector-augmented wave (PAW) potentials 
+to relax twice and optimize the ICSD-structure.
+
+AFLOW-ML \cite{Isayev2017} is an API that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which they denote as \textit{fragment descriptors}.
+Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression model to predict the band gap width.
+The accuracy is validated by a five-fold cross-validation process for each model, where they report a $93 \ \%$ prediction success of their initial binary classification model.
+
+Matminer \cite{Ward2018} is an open-source toolkit for material analysis written in Python.
+Matminer provides modules to extract information from a wide variety of databases.
+Additionally, they provide the tools to construct possibly thousands of features from calculations based on a material's composition, structure and electronic properties from DFT calculations, and have frameworks for visualization and automatic machine learning.
+
+\subsection*{Material Informatics}  
 Screening and workflow and approaches.
 
-\subsection*{Machine Learning} %Sebastian/Morten   
-Insight gaining.
+\subsection*{Machine Learning}
+
+Machine learning  represents the science of giving computers the ability to learn without being explicitly programmed.
+The idea is that there exist generic algorithms which can be used to find patterns in a broad class of data sets without having to write code specifically for each problem.
+The algorithm builds its own logic based on the data.
+
+\begin{itemize}
+    \item Logistic regression
+    \item Decision trees
+    \item Random forests
+    \item Gradient boosting
+\end{itemize}
 
@@
 %We can put something else, standard text 
-The data that support the plots within this paper and other findings of this study are
-available from the corresponding authors upon reasonable request.
+%The data that support the plots within this paper and other findings of this study are available from the corresponding authors upon reasonable request.
+[Marianne: I assume you want to add the Github link here?]
+
+The data that support the findings of this study are available from the corresponding author, and the datasets used to generate the ML models are available online at [Github link].
 
 \section*{Code availability} 
-The codes developed in this study are available from the authors upon reasonable
-request.
+%The codes developed in this study are available from the authors upon reasonable request. [Marianne: I assume you want to add the Github link here?] 
+The codes employed to develop the ML models are available online at [Github link].
 
@@
 
-\section*{Author contributions} 
+%\section*{Author contributions} 
 %Copied in from another paper 
-S.-M.J. conceived the idea and developed the simulation model. T.H.L. performed
-computer simulation. S.Y.B. and S.D.H. fabricated devices. D.-W.S., S.L., H.W.C. and
-J.-W.J. supported measurement of device performances. Y.-H.S. and X.-B.F.
-synthesised QD materials. S.Z. and J.Y. supported experiments. C.S. and Y.K.
-supported computer simulation. L.G.O. and G.A. supported data analysis. J.M.K.
-guided this work. S.-M.J., T.H.L. and S.Y.B. contributed equally. 
+%S.-M.J.
+conceived the idea and developed the simulation model.
+T.H.L.
+performed computer simulation.
+S.Y.B.
+and S.D.H.
+fabricated devices.
+D.-W.S., S.L., H.W.C.
+and J.-W.J.
+supported measurement of device performances.
+Y.-H.S.
+and X.-B.F.
+synthesised QD materials.
+S.Z.
+and J.Y.
+supported experiments.
+C.S.
+and Y.K.
+supported computer simulation.
+L.G.O.
+and G.A.
+supported data analysis.
+J.M.K.
+guided this work.
+S.-M.J., T.H.L.
+and S.Y.B.
+contributed equally.
 All the authors contributed to the preparation of the manuscript.

### 2021-11-25 supplementary.tex
Updates from Overleaf

--- 2021-08-24 paper.tex
@@
 \usepackage{siunitx}
+\usepackage{color}
+\usepackage{longtable}
 \sisetup{separate-uncertainty}
-
 %\newcommand\abs[1]{\left|#1\right|}
@@
 
+\newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
+\newcommand{\morten}[1]{\textcolor{green}{#1}}
+\newcommand{\sebastian}[1]{\textcolor{cyan}{#1}}
+\newcommand{\marianne}[1]{\textcolor{blue}{#1}}
+\newcommand{\oyvind}[1]{\textcolor{maroon}{#1}}
+\newcommand{\lasse}[1]{\textcolor{red}{#1}}
+
 \begin{document}
 
-\title{Predicting Solid State Qubit Candidates}
+\title{Supplementary Material \\ 
+Predicting Solid State Qubit Candidates}
 
@@
 
-\author{Øyvind Sigmundson Schøyen}
+\author{Sebastian G. Winther-Larsen}
+\affiliation{Menon Economics, N-0369 Oslo, Norway}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
 
-\author{Sebastian G. Winther-Larsen}
+\author{Øyvind Sigmundson Schøyen}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 
-\begin{abstract}
-
-Semiconductor materials provide a compelling platform for quantum
-technology, and a vast amount of materials and their properties can be
-found in high-throughput databases.  However, filtering among these
-materials in order to find novel candidates for quantum technology is
-a challenge. Therefore, we provide a framework for the automatic
-discovery of promising solid-state material hosts using machine
-learning methods.
-
-%Main message 1: develop methodology for data mining and machine learning for materials properties 
-We have developed data extraction tools for numerous material science
-databases, and constructed over $4800$ physics-informed features for a
-dataset consisting of more than $25000$ materials.  Furthermore, we
-have developed and implemented three data mining approaches, termed
-\textit{the Ferrenti approach}, \textit{the augmented Ferrenti
-  approach} and \textit{the insightful approach} for defining three
-distinct training sets for the supervised machine learning algorithms
-logistic regression, decision tree, random forest and gradient boost
-to be trained on.
-
-% Main message 2: Use method to propose new materials that are promising quantum hosts 
-We find a lack of consistent results for the Ferrenti approach and the
-augmented Ferrenti approach due to an overly broad formulation of the
-training set, whereas the restrictions set in the insightful approach
-proved suitable. All models agreed on $214$ predicted candidates, with
-examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP,
-and InAs. All approaches and all models agreed on a subset of $47$
-eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary
-compounds.
-
-\end{abstract}
-
 \pacs{02.70.Ss, 31.15.A-, 31.15.bw, 71.15.-m, 73.21.La}
@@
 
-%Submit to npj Computational Materials
+Contents: \\ 
+Supplementary methods --- information on machine learning approaches and the featurization process. \\ 
+Supplementary results --- tables of resulting materials from the different approaches and models used.  \\ 
+Supplementary references.
 
-%Marianne: I have now structured the paper according to other papers in this journal 
-%I think we can make a supplementary material if we see that we need it, it is quite common for the journal
+\newpage
 
-\section*{Introduction}%Oliver and Morten and Marianne (semiconductor portion)
-To sustain the digital world’s increasing computational demand, alternatives to the classical computer must be explored.
-The quantum computer, together with the complementary quantum technologies of sensing and communication, is becoming a frontrunner in the race for solutions.
-Discuss recent benchmarks for quantum computing \cite{Arute_2019}.
+\section*{Supplementary methods}
+\subsection*{Featurization}
+Table~\ref{table:featurizers} contains an overview of this work's chosen 39 features from matminer. The features were selected based on ...
 
-Limitations of quantum computing and technology building blocks. Drawbacks of superconductors. Semiconductors are a promising platform. Example of NV center in diamond \cite{Doherty_2013}.
+\input{appendix/featurizerTable.tex}
 
-%From thesis - rewrite 
-Unfortunately, there are substantial challenges associated with the modern quantum platforms simultaneously as the selection of quantum platforms are slim.
-The majority of discoveries of potential quantum platforms have so far happened by serendipity, and there is an urgent need for new and better materials that can escalate the effort for a sustainable future.
+\subsection*{Optimization of machine learning models}
+Something important to add here??
 
-The fourth science paradigm introduces the potential of targeted search for promising material systems to act as qubit hosts. 
-Herein, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods. 
-Initial database building similar to Ferrenti et al \cite{Ferrenti2020}.
+\section*{Supplementary results}
+Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all models in the insightful approach agreed on with more than $75 \ \%$ probability.
+All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
+Note that materials can appear several times  on  the  list  due  to  different  structures of the same composition.
+The  list  contains five  elementary (unary), 46  binary and  15 ternary compounds.
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/paradigms.png}
-    \caption{[PLACEHOLDER] Schematic over paradigms in science.}
-    \label{fig:paradigm}
-\end{figure}
-
-\section*{Theoretical Background and Experimental Data} 
-%Not all papers have a theory chapter, but since we are speaking to two quite different communities, it might be nice to include some basics.
-
-%Some of this can also be copied into the introduction
-
-Quantum technologies, including sensing, communication and computing, 
-are intriguing because of the new capabilities they offer. 
-However, realization of large-scale fabrication for these techniques requires further technological development. 
-The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale. 
-Instead, recent developments have seen/heralded the rise of semiconductors as possible host materials for a variety of quantum devices.
-Semiconductor quantum dots or point defects could prove easier to combine with existing devices, and room temperature operation of prototype communication and computing devices has been shown.
-However, this technology is still in the early stages, and the issues left to address include scalable and reproducible device fabrication, identification of ideally suited host candidates, and, importantly, understanding the requirements for a material to act as a good host remain unclear.
-%Different methods are needed.
-
-\subsection*{Semiconductors as a Quantum Host} %Marianne and Lasse
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/qubit.png}
-    \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
-    \label{fig:qt}
-\end{figure}
-
-Quantum tehcnologies commonly rely on a quantum bit or qubit as the basis for operation. 
-For all applications, the basic requirement is a two-level quantum system which is quite isolated from the environment, ensuring long-term stability between operations.
-In other words, we search for systems which exhibit a high degree of coherence.
-However, stability is not enough. The qubit state must be controlled via repeatable initialization, manipulation and read-out. 
-A set of requirements were formulated by DiVincenzo for the case of qubits and quantum computing \cite{DiVincenzo2000}.
-Below, these are rephrased to encompass qubit requirements for all three QT application areas:
-\begin{itemize}
-    \item A scalable physical system with well-characterized qubits
-    \item Reliable qubit initialization protocols 
-    \item Quantum gates and protocols to operate on and control qubit states  
-    \item Qubit state coherence time must exceed gate operation time 
-    \item Qubit state read-out after operation, preferably optically.  
-\end{itemize}
-
-%Discuss experimental data and the semiconductor platform. 
-Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap. 
-Importantly, deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT. 
-A prime example is the nitrogen-vacancy (NV) center in diamond, which has been proposed 
-as a contender for both computing, sensing and communication applications \cite{Doherty_2013}. 
-The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for optical imaging of living cells \cite{Lesage_2013}.  
-Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second},
-leading to demonstrations of entanglement and teleportation of two NV center spins \cite{Bernien2013,Pfaff_2014}. 
-However, despite these promising discoveries, diamond may not be the ideal candidate host.
-The NV center, for instance, emits in the visible, which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology, and the poor scalability of diamond devices may prove non-competitive in the long run.
-
-\begin{table}[h]
-    \centering
-    \begin{tabular}{c|c|c|c}
-    Material & Band gap (eV) & Defect candidates & References \\
-    \hline
-    Diamond  & $5.5$  & N$_\mathrm{C}V_\mathrm{C}$, Si$_\mathrm{C}V_\mathrm{C}$, Ge$_\mathrm{C}V_\mathrm{C}$ & \cite{Balasubramanian_2009,Rogers_2014,Bhaskar_2018} \\  
-    4H-SiC & $3.3$ & $V_\mathrm{Si}$, $V_\mathrm{Si}V_\mathrm{C}$, C$_\mathrm{Si}V_\mathrm{C}$, N$_\mathrm{C}V_\mathrm{Si}$ & \cite{Widmann2014,Christle_2015,Castelletto_2014,Zargaleh_2018} \\ 
-    Si & $1.1$ & P, G, unidentified & \cite{Muhonen_2014,Durand_2020,Redjem2020} \\ 
-    (2D) \textit{h}-BN & $6.0$ & Unidentified defects & \cite{Tran_2016,Tran_2016b,Hayee_2020} \\ 
-    ZnO & $3.4$ & Unidentified defects & \cite{Morfa2012} \\ 
-    ZnS & $3.6$ (zincblende) & Unidentified defects & \cite{Stewart2019} \\ 
-    GaAs & $1.4$ & Quantum dots & \cite{Bluhm2010} \\ 
-    GaN & $3.4$ & Quantum dots, unidentified defects & \cite{Roux2017,Berhane2018} \\
-    AlN & $6.0$ & Unidentified defects & \cite{Xue2020}\\
-    \end{tabular}
-    \caption{Overview of materials and defects that have been demonstrated to exhibit QT-compatible characteristics such as single-photon emission and coherent spin manipulation.}
-    \label{tab:qt-materials}
-\end{table}
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.5\textwidth]{figures/NV.png}
-    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
-    \label{fig:defects-dft}
-\end{figure}
-
-%QT requirements. 
-%What parameters are we looking for? 
-Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
-In this context we consider single-photon emission and coherent spin manipulation for systems related to point defects primarily, but also self-assembled or lithographically structured quantum dots.
-Most of the defects in the table have yet to be identified, and different materials challenges complicate the implementation of defects for QT. 
-A set of common denominators for materials that contain quantum emitters was summarized by Weber et al \cite{Weber2010}: 
-\begin{itemize}
-    \item Wide band gap to facilitate localized deep levels (physical)
-    \item Low spin orbit coupling to extend spin coherence times (physical) 
-    \item Low el-phonon coupling for sharp emission lines (physical) 
-    \item Availability as high-quality, bulk, or thin-film single crystals (practical)
-    \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
-\end{itemize}
-Note the division between physical and practical requirements in the list above. 
-The physical criteria refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to the external influences that simplify measurement and detection of the interesting properties.
-In this work, we will focus most on the former set of criteria, as understanding them better may give further insights into the makings of a solid QT platform.
-
-In addition to obtaining greater understanding of  exactly what constitutes a good quantum host material, we must recognize that different defect and material types may suit different needs.
-Therefore, we aim to develop a bigger bank of candidate defects and materials.
-So far, detection of QT compatibility in semiconductors has been slow going, as a signal is detected and then identified in a specific material.  
-Instead, we are looking for a top-down approach to  \textit{predict} promising materials, enabling a guiding of experimental efforts. 
-%For this, we first need a large dataset.
-
-\subsection*{Density Functional Theory Output} %Marianne 
-Density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
-Using DFT calculations we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
-
-DFT is based on the Hohenberg-Kohn \cite{Hohenberg1964} and Kohn-Sham \cite{Kohn1965} theorems and provides a method for iteratively solving the Schrodinger equation based on initial guesses for the atomic potentials.
-The foundation for DFT centers around the electronic density providing all ground-state properties of the system, provided that the external potential can be exactly described. 
-The fundamental challenge of DFT calculations is that this potential, as expressed by the exchange-correlation functional, can be exactly computed for only very few and simple systems.
-
-In the case of solid state materials the XC functional is not known and must instead be approximated. 
-Herein, we will consider three classes of functionals based on different fundamental assumptions.
-The local density approximation (LDA) takes the homogeneous electron gas as a starting point, while the more advanced general gradient approximation (GGA) includes also the gradient in local electron gas variations.
-These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron can interact with itself).
-More recent developments have seen the widespread use of hybrid functionals such as the HSE06 incorporating a portion of Hartree-Fock exact exchange \cite{Heyd2003},  albeit at a much greater computational cost.
-See, e.g., this review \cite{Freysoldt2014} for further details on different functionals for semiconductor and defect calculations.
-
-Despite the limitations imposed by the approximate nature of the XC functional, and the band gap error of LDA and GGA level functionals, 
-DFT can be a powerful tool when predicting, designing and interpreting experiments. 
-Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict novel candidate QT hosts.
-The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}, which can underestimate the band gap of semiconductor materials.  
-Nonetheless, a larger data set is available than for, e.g., HSE06, and many trends are conserved also with PBE. 
-The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the elctronegativity, the electron-phonon coupling and magnetic properties.
-
-\subsection*{Material Informatics} %Øyvind (Oliver)    
-%Data mining, screening
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
-    \caption{[PLACEHOLDER for workflow] Morten: can you please add the other schematic figure we discussed as placeholder?
-Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
-}
-    \label{fig:ht-workflow}
-\end{figure}
-
-\subsection*{Machine Learning} % Morten
-
-\section*{Results}
-Includes discussion of results.
-
-\subsection*{Information Flow}  %Sebastian/Oyvind (Marianne) 
-Includes results from data mining and description of the three approaches. 
-%MEB: Since Methods are at the end, I propose to put part of this discussion in the Results section. 
-%This is because it is an important result of the work, and also because it is important to understand the rest of the paper
-
-\subsection*{Optimization of Machine Learning Models} %Morten (Oliver input in round 2)
-
-\subsection*{Predicting Novel Material Hosts for Quantum Technology} %Oyvind (Oliver input in round 2) 
-\subsubsection*{The Ferrenti approach} 
-\subsubsection*{The augmented Ferrenti approach}
-\subsubsection*{The insightful approach}
-\subsubsection*{Comparing the approaches}
-
-\section*{Discussion} % All - last thing we write  
-Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
-
-\section*{Methods}
-%Methodology comes after concluding remarks, and is structured into subsections
-
-\subsection*{Databases} %Oliver and Øyvind 
-%Materials project, AFLOW, Open Quantum, JARVIS 
-Mining.
-
-\subsection*{Material Informatics} %Oliver and Øyvind 
-Screening and workflow and approaches.
-
-\subsection*{Machine Learning} %Sebastian/Morten   
-Insight gaining.
-
-\section*{Data availability} 
-%We can put something else, standard text 
-The data that support the plots within this paper and other findings of this study are
-available from the corresponding authors upon reasonable request.
-
-\section*{Code availability} 
-The codes developed in this study are available from the authors upon reasonable
-request.
+\input{appendix/tablesof66materials.tex}
 
@@
 
-\begin{acknowledgments}
-
-The work of MHJ is supported by the U.S. Department of Energy,
-Office of Science, office of Nuclear Physics under grant
-No. DE-SC0021152 and U.S. National Science Foundation Grants
-No. PHY-1404159 and PHY-2013047. 
-The work of MEB and LV was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
-%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
-The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship.
-
-\end{acknowledgments}
-
-\section*{Author contributions} 
-%Copied in from another paper 
-S.-M.J. conceived the idea and developed the simulation model. T.H.L. performed
-computer simulation. S.Y.B. and S.D.H. fabricated devices. D.-W.S., S.L., H.W.C. and
-J.-W.J. supported measurement of device performances. Y.-H.S. and X.-B.F.
-synthesised QD materials. S.Z. and J.Y. supported experiments. C.S. and Y.K.
-supported computer simulation. L.G.O. and G.A. supported data analysis. J.M.K.
-guided this work. S.-M.J., T.H.L. and S.Y.B. contributed equally. 
-All the authors contributed to the preparation of the manuscript.
-
-\section*{Competing interests}
-The authors declare no competing interests.
-
 \end{document}

### 2021-11-26 paper.tex
Updates from Overleaf

@@
 Semiconductor materials provide a compelling platform for quantum technology, and a vast amount of materials and their properties can be found in high-throughput databases.
-However, filtering among these materials in order to find novel candidates for quantum technology is a challenge.
+However, sifting through tens of thousands of these materials in order to find novel candidates for quantum technology is a challenge.
 Therefore, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods.
@@
 The second quantum revolution is heralding the development of new solutions and devices based on quantum technology \cite{Acin2018}.
-Among the promising prototypes that are already available we find in vivo sensing of magnetic fields in cells [], secure communication over large distances by separation of entangled photons [], and finally the demonstration of quantum computing [].
+Among the promising prototypes that are already available we find in vivo sensing of magnetic fields in cells [REF!], secure communication over large distances by separation of entangled photons [REF!], and finally the demonstration of quantum computing [REF!].
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
@@
 Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a 200'000 core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
-And IBM announced recently its 127 qubit quantum processor.
+Most recently, IBM announced its 127 qubit quantum processor~\cite{IBM2021}.
 
@@
 These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap.
-So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliable single-photon emission and long spin coherence times.
+So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliabl single-photon emission and long spin coherence times.
 The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared and telecom coupled with more mature material processing and fabrication  \cite{Bathen2021}.
@@
 The third approach differs substantially from the first two approaches in terms 
-of labeling, as we apply knowledge from the field (see, e.g., Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)   
+of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)   
 to pick our promising material host candidates. We therefore name this scheme 
 \emph{the insightful approach}. 
-Due to the concern of having a too-small dataset, we will include
+Due to the concern of having an insufficient dataset, we will include
 materials that are promising and have shown suitable properties to 
@@
 
-MORE ON MANUAL SCREENING....
 %% OH: Dirty details about suitable materials:

### 2021-11-26 paper.tex
Updates from Overleaf

@@
 
-\author{Oliver Lerstøl Hebnes}
+\author{Oliver Lerst{\o}l Hebnes}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 
-\author{Øyvind Sigmundson Schøyen}
+\author{{\O}yvind Sigmundson Sch{\o}yen}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap.
-So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliabl single-photon emission and long spin coherence times.
+So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliable single-photon emission and long spin coherence times.
 The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared and telecom coupled with more mature material processing and fabrication  \cite{Bathen2021}.
@@
 
-\begin{itemize}
-    \item Logistic regression
-    \item Decision trees
-    \item Random forests
-    \item Gradient boosting
-\end{itemize}
+The approaches to ML are many, but are often split into two main categories, supervised and unsupervised.
+In supervised learning we know the answer to a problem, and let the computer deduce the logic behind it.
+On the other hand, unsupervised learning is a method for finding patterns and relationship in data sets without any prior knowledge of the system.
+Many researchers also operate with a third category, namely reinforcement learning.
+This is a paradigm of learning inspired by behavioral psychology, where learning is achieved by trial-and-error, solely from rewards and punishment.
+In this work our focus is on supervised learning only with labeled data.
+Our main focus is on classification problems.
+
+In this work we have applied four well-known and tested machine learning methods for classification problems, these are (see for example \cite{Hastie2009,Mehta2019} for discussions and applications):
+\begin{enumerate}
+    \item Logistic regression,
+    \item Decision trees,
+    \item Random forests,
+    \item Gradient boosting.
+\end{enumerate}
+Logistic regression \cite{Hastie2009} is a simple and frequently used method for binary and multi-category classification problems.
+In addition to logistic regression, we have also applied and tested the predictions made by decision trees and ensemble methods like random forests and gradient boosting, the latter through the application of the computationally efficient  XGBoost library \cite{xgboost2016}.
+Gradient boosting and random forests use decision trees as weak learners and improve their predictability, through either collections of randomized decision trees (a subset of the features in the data sets are selected randomly en building a decision tree for classification)  in random forests or by using a decision tree as a weak learner and improve upon this model by iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
+Pure decision trees can easily lead to overfitting of the data under
+ study, leading to a model that exhibits a high variance.
+Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Ref.~\cite{Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning applied to physics problems.
+Gradient boosting implemented through the  XGBoost library, is used widely by data scientists to achieve state-of-the-art results on many machine learning challenges.
 

### 2021-11-26 paper.tex
Updates from Overleaf

@@
 
-The approaches to ML are many, but are often split into two main categories, supervised and unsupervised.
+The approaches to machine learning are many, but are often split into two main categories, supervised and unsupervised.
 In supervised learning we know the answer to a problem, and let the computer deduce the logic behind it.
@@
 This is a paradigm of learning inspired by behavioral psychology, where learning is achieved by trial-and-error, solely from rewards and punishment.
-In this work our focus is on supervised learning only with labeled data.
-Our main focus is on classification problems.
+In this work our focus is on supervised learning only with labeled data for classification problems.
 
@@
 In addition to logistic regression, we have also applied and tested the predictions made by decision trees and ensemble methods like random forests and gradient boosting, the latter through the application of the computationally efficient  XGBoost library \cite{xgboost2016}.
-Gradient boosting and random forests use decision trees as weak learners and improve their predictability, through either collections of randomized decision trees (a subset of the features in the data sets are selected randomly en building a decision tree for classification)  in random forests or by using a decision tree as a weak learner and improve upon this model by iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under
- study, leading to a model that exhibits a high variance.
-Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Ref.~\cite{Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning applied to physics problems.
-Gradient boosting implemented through the  XGBoost library, is used widely by data scientists to achieve state-of-the-art results on many machine learning challenges.
+Gradient boosting and random forests use decision trees as weak learners and improve their predictability.
+For random forests this is implemented through a collection of randomized decision trees where a  subset of the features in the data sets are selected randomly when building a decision tree.
+Boosting methods like gradient boosting use decision trees as  weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
+Pure decision trees can easily lead to overfitting of the data under study, leading to a model that exhibits a high variance.
+Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Ref.~\cite{Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
+Gradient boosting implemented through the  XGBoost library, is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
 

### 2021-12-10 paper.tex
Updates from Overleaf

@@
 
-\title{Predicting Solid State Qubit Candidates}
+%\title{Predicting Solid State Qubit Candidates}
+\title{Predicting Solid State Material Platforms for Quantum Technologies}
 
@@
 \author{Marianne Etzelm\"uller Bathen}
-\affiliation{Advanced Power Semiconductor Laboratory, ETH Zürich, 8092  Zürich,  Switzerland}
+\affiliation{Advanced Power Semiconductor Laboratory, ETH Z{\"u}rich, 8092  Z{\"u}rich,  Switzerland}
 \affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
@@
 
-Semiconductor materials provide a compelling platform for quantum technology, and a vast amount of materials and their properties can be found in high-throughput databases.
+%Rewrite to avoid plagiarism complaints, original is commented out
+
+%Semiconductor materials provide a compelling platform for quantum technology, and a vast amount of materials and their properties can be found in high-throughput databases.
 However, sifting through tens of thousands of these materials in order to find novel candidates for quantum technology is a challenge.
 Therefore, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods.
+Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
+However, scouring these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using materials informatics and machine learning methods.
 
-%Main message 1: develop methodology for data mining and machine learning for materials properties 
-We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25000$ materials.
-Furthermore, we
-have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the insightful approach} for defining three distinct training sets for the supervised machine learning algorithms
-logistic regression, decision tree, random forest and gradient boost to be trained on.
+%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25000$ materials.
+Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the insightful approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
+Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25'000$ materials.
+The information from the databases was converted into nearly $5'000$ physics-informed features.
+Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}.
+%Rename insightful approach! To what? 
+%Options include stringent, strict, cherry-picked, informed and intuitive. 
+The three approaches define distinct training sets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
 
-% Main message 2: Use method to propose new materials that are promising quantum hosts 
-We find a lack of consistent results for the Ferrenti approach and the augmented
-Ferrenti approach due to an overly broad formulation of the training
-set, whereas the restrictions set in the insightful approach proved suitable. All
-models for the insightful approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, 
-MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs. All three approaches and all ML
-models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary,
-and $10$ tertiary compounds.
+%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the insightful approach proved suitable.
+All models for the insightful approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs.
+All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
+We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set.
+The restrictions set in the intuitive approach, on the other hand, which relies exclusively on findings from the literature, proved more suitable.
+All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>XX \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
 
@@
 
-%Submit to npj Computational Materials
-
-%Marianne: I have now structured the paper according to other papers in this journal 
-%I think we can make a supplementary material if we see that we need it, it is quite common for the journal
-
-\section*{Introduction}%Oliver and Morten and Marianne (semiconductor portion)
-The second quantum revolution is heralding the development of new solutions and devices based on quantum technology \cite{Acin2018}.
-Among the promising prototypes that are already available we find in vivo sensing of magnetic fields in cells [REF!], secure communication over large distances by separation of entangled photons [REF!], and finally the demonstration of quantum computing [REF!].
+\section*{Introduction}
+The second quantum revolution is heralding the development of new solutions and devices based on principles from quantum mechanics \cite{Acin2018}.
+Among the promising technologies that are already available we find in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum computer architectures and prototypes.
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
-Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as the quantum internet. 
+Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as quantum cryptography and the quantum internet.  
 Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a 200'000 core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
@@
     \centering
-    %\includegraphics[width=0.6\textwidth]{figures/paradigms.png}
-    \includegraphics[width=0.9\textwidth]{figures/ht-workflow.jpg}
+%    \includegraphics[width=0.9\textwidth]{figures/ht-workflow.jpg}
+    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new.png}
     \caption{[PLACEHOLDER] Schematic of an example workflow in material informatics. 
-    %\marianne{Morten: can you please add the other schematic figure we discussed as placeholder?
-Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
-We should have just one figure I think, perhaps even combining the paradigms and explaining the material informatics worklow.}
+    %\marianne{Sebastian makes simplified figure.}
     }
-    \label{fig:paradigm}
+    \label{fig:ht-workflow}
 \end{figure}
@@
 These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap.
-So-called deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., reliable single-photon emission and long spin coherence times.
-The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared and telecom coupled with more mature material processing and fabrication  \cite{Bathen2021}.
+So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
+The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
 However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
-Another important issue is that the understanding of the requirements for a material to enable quantum compatible properties to manifest remains lacking,
-%The plethora of possible emitters and spin centers formed by semiconductor defects or nanostructures come with different characteristics that are compatible with specific applications.  
-%Additionally, the understanding of what exactly makes a semiconductor based quantum platform suitable for QT is scarce, 
-and the selection of quantum compatible semiconductor host materials is slim.
+Importantly, we are lacking a complete understanding of the requirements for a material to manifest quantum compatible properties,  
+and the selection of known quantum compatible semiconductor host materials is slim.
 
 The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for 
-%new and better materials that can escalate the effort for a sustainable future. 
-a better understanding of how different materials properties manifest. 
+a better understanding of how the QT compatible materials properties manifest. 
 In this context, a framework for dedicated materials search and analysis is needed. 
 The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
-The fourth paradigm
-%, as illustrated by the schematic in Figure~\ref{fig:paradigm}(a), 
-introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.  
+The fourth paradigm instead introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.
 Instead of searching through a host of signals for the one that matches our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies. 
-This is made feasible by the availability of databases containing material properties for a wide range of different systems.
+This is made feasible by the availability of databases containing materials properties for a wide range of different systems.
 In this work, the data in question is provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
-Combined with machine learning algorithms we provide a path towards precise classification of qubit candidates.
-The inclusions of machine learning methods follows recent trends in applications of
-statistics, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
+Combined with machine learning methods we provide a path towards precise classification of qubit candidates.
+The inclusion of machine learning methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
 
-In this work we provide a framework for the data mining and automated discovery of promising solid-state material hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
+In this work we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
 The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical or experimental data is available.
-The method that was developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
-Matminer \cite{Ward2018} is then used for material analysis to featurize the extracted data. 
-An important feature of the work is the database building and development of the training sets for the machine learning models.
-We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020}  \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the insightful approach}.
-We find that the former two methodologies base their data extraction protocols on practical considerations, such as experimental availability in specific forms or the toxicity of the materials, leading to few observable trends in the materials predicted by well-tested machine learning algorithms, such as logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{mehta2019,hastie2009}.
-The third approach, on the other hand, relies on materials with experimentally proven advantageous characteristics in the training set.
-This more restricted approach proved more suitable than the other two and yielded $214$ predicted candidates with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
-%\begin{itemize}
- %   \item Data was extracted from databases materials project ... 
- %   \item Featurization using matminer 
- %   \item Initial database building similar to Ferrenti et al \cite{Ferrenti2020}, but method is expanded to focus mainly on physical aspects. 
- %   \item Machine learning on top.  
-%\end{itemize}
+The method that was developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+Matminer \cite{Ward2018} was then used for material analysis to featurize the extracted data.
+An important feature of our work is the database building and development of the training sets for machine learning methods.
+We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020}  \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the intuitive approach}.
+We find that the former two methodologies base their data extraction protocols on practical considerations, such as experimental availability in specific forms or the toxicity of the materials, leading to few observable trends in the materials predicted by well-tested machine learning algorithms, such as logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
+The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set.
+This more restricted approach proved more suitable than the other two and yielded $214$ predicted candidates (to a probability of $>50 \ \%$) with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
 
-%\section*{Theoretical Background and Experimental Data}
+\section*{Results}
 
-%Quantum technologies, including sensing, communication and computing, are intriguing because of the new capabilities they offer.
-However, realization of large-scale fabrication for these techniques requires further technological development.
-The superconducting electronics platform that is currently employed for quantum computers necessitates millikelvin temperatures and may prove challenging to scale.
-Instead, recent developments have seen/heralded the rise of semiconductors as possible host materials for a variety of quantum devices.
-Semiconductor quantum dots or point defects could prove easier to combine with existing devices, and room temperature operation of prototype communication and computing devices has been shown.
-However, this technology is still in the early stages, and the issues left to address include scalable and reproducible device fabrication, identification of ideally suited host candidates, and, importantly, understanding the requirements for a material to act as a good host remain unclear.
+\subsection*{Information Flow}
 
-%\subsection*{Semiconductors as a Quantum Host} 
-%Quantum technologies commonly rely on a quantum bit or qubit as the basis for operation.
-\marianne{Some schematic is shown in Figure~\ref{fig:qt}}.
-For all applications, the basic requirement is a two-level quantum system which is essentially isolated from its environment, ensuring sufficient stability to perform various operation.
-In other words, we search for systems which exhibit a high degree of coherence.
-Additionally, the qubit state must be controlable via repeatable initialization, manipulation and read-out protocols.
-A set of requirements were formulated by DiVincenzo for the case of qubits and quantum computing \cite{DiVincenzo2000}.
-Below, these are rephrased to encompass qubit requirements for all three QT application areas:
-%\begin{itemize}
- %   \item A scalable physical system with well-characterized qubits
- %  \item Reliable qubit initialization protocols 
- %   \item Quantum gates and protocols to operate on and control qubit states  
- %   \item Qubit state coherence time must exceed gate operation time 
- %   \item Qubit state read-out after operation, preferably optically.  
-%\end{itemize}
-
-%\begin{figure}[t]
- %   \centering
- %   \includegraphics[width=0.3\textwidth]{figures/qubit.png}
- %   \caption{[PLACEHOLDER] Schematic of classical versus quantum bits. }
- %   \label{fig:qt}
-%\end{figure}
-
-%Discuss experimental data and the semiconductor platform. 
-%Semiconductors embody point defects that may trap charge carriers, causing deep energy levels to appear within the fundamental band gap.
-Importantly, deep level defects can trap carriers in localized states that are essentially isolated from the surroundings, making them suitable for QT.
-A prime example is the nitrogen-vacancy (NV) center in diamond, which has been proposed as a contender for both computing, sensing and communication applications \cite{Doherty_2013}.
-The NV center is a room temperature single-photon source emitting in the visible portion of the spectrum, and has been employed for, e.g., stress tensor mapping \cite{Broadway2019} and optical imaging of living cells \cite{Lesage_2013}.
-Moreover, the NV center in its negative charge state traps an electron in a localized and high-spin $S=1$ state that can be coherently controlled and with RT spin coherence times above \SI{1}{\milli\second} \cite{Doherty_2013}, leading to demonstrations of entanglement and teleportation of two NV center spins \cite{Bernien2013,Pfaff_2014}.
-However, despite these promising discoveries, diamond  as a quantum platform comes with several important drawbacks.
-The relevant defects therein, such as the NV center, emit in the visible region of the spectrum which is not compatible with the telecom wavelengths needed to integrate with optical fiber technology.
-Additionally, diamond is expensive, device fabrication is challenging and scalability is poor, leading to concerns in whether quantum technology device development will be realizable on this platform.
-Hence, we search among the plethora of available semiconductors for a platform that can deliver on the necessary parameters for QT applications while also, ideally, providing availability and scalable fabrication.
-In this context, the material properties that facilitate quantum compatible characteristics such as single-photon emission and coherent spin manipulation to manifest must be identified.
-
-%\begin{figure}[t]
-%    \centering
-%    \includegraphics[width=0.5\textwidth]{figures/NV.png}
-%    \caption{[PLACEHOLDER] Schematic representation of the electronic structure of the NV center in diamond.}
-%    \label{fig:defects-dft}
-%\end{figure}
-
-%\begin{figure}[t]
- %   \centering
- %   \includegraphics[width=0.5\textwidth]{figures/defects-sic.pdf}
- %   \caption{[PLACEHOLDER] Schematic representation of different quantum compatible defects in SiC and the energy levels they introduce into the band gap, from Ref.\cite{Bathen2021}.} 
- %   \label{fig:defects-sic}
-%\end{figure}
-
-%Table \ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
-In this context we consider single-photon emission and coherent spin manipulation for systems related to point defects primarily, but also self-assembled or lithographically structured quantum dots.
-\marianne{A (placeholder) schematic of quantum compatible defects and the energy levels they introduce into the band gap of 4H-SiC is shown in Figure~\ref{fig:defects-sic}.} Most of the defects in the table have yet to be identified, and different material related challenges complicate the implementation of defects for QT.
-A set of common denominators for materials that contain qubit defects was summarized by Weber et al.
-\cite{Weber2010}:
-%\begin{itemize}
- %   \item Wide band gap to facilitate localized deep levels (physical)
- %    \item Low spin orbit coupling to extend spin coherence times (physical) 
- %   \item Low el-phonon coupling for sharp emission lines (physical) 
- %   \item Availability as high-quality, bulk, or thin-film single crystals (practical)
- %   \item Constituent elements with naturally occurring isotopes of zero nuclear spin (practical). 
-%\end{itemize}
-%Note the division between physical and practical requirements in the list above.
-The physical criteria refer to some fundamental aspect of the material that permits specific properties to manifest, while practical refers to the external influences that simplify measurement and detection of the interesting properties.
-In this work, we will focus primarily on the former set of criteria, as understanding them better may give further insights into the makings of a reliable QT platform.
-
-%In addition to obtaining greater understanding of  exactly what constitutes a good quantum host material, we must recognize that different defect and material types may suit different needs.
-Therefore, we aim to develop a bigger bank of candidate defects and materials.
-So far, detection of QT compatibility in semiconductors has been rather slow, depending on signal detection and later identification in each specific material.
-Instead, we are looking for a top-down approach to \textit{predict} promising materials, enabling a guiding of experimental efforts.
-
-%\subsection*{Density Functional Theory Output} %Marianne 
-%The density functional theory (DFT) is a versatile and powerful theoretical approach that has been exceptionally successful in predicting solid-state material properties such as stability of different phases, lattice parameters and band gaps.
-DFT provides a method for iteratively solving the Schr{\"o}dinger equation based on initial guesses for the atomic potentials.
-Using DFT calculations, we are able to accurately investigate semiconductor materials with many atoms while keeping efficiency and cost in mind.
-
-%The fundamental challenge of the DFT is that the calculations rely on approximations to the potential function of a system as expressed by the exchange-correlation (XC) functional, which is not known for bulk materials.
-The XC functional is usually grouped into three categories based on the level of theory.
-The local density approximation (LDA) takes the homogeneous electron gas as a starting point, while the more advanced general gradient approximation (GGA) includes also the gradient in local electron gas variations.
-These local or semi-local functionals yield satisfactory results on geometrical concerns but tend to underestimate energies such as the band gap or defect energy levels due to a self-interaction error (i.e., an electron is allowed to interact with itself) [Ref SchollSteckel] \cite{Freysoldt2014}.
-More recent developments have seen the widespread use of hybrid functionals such as the HSE06 incorporating a portion of Hartree-Fock exact exchange \cite{Heyd2003},  albeit at a much greater computational cost.
-
-%Despite the limitations imposed by the approximate nature of the XC functional, and the band gap error of LDA and GGA level functionals, DFT can be a powerful tool when predicting, designing and interpreting experiments.
-Herein, we employ databases containing DFT calculations of material properties to gain insight into the fundamental mechanisms behind observed quantum characteristics, and predict new candidate QT hosts.
-The calculations we employ were performed using the GGA-level Perdew-Burke-Erznerhof (PBE) functional \cite{Perdew1996}.
-Note that the PBE functional tends to underestimate the band gap of semiconductor materials.
-Nonetheless, a larger data set is available than for, e.g., HSE06, and many trends are conserved also with PBE.
-The ground-state (and $0$~K) parameters that can be extracted from this type of data set include the total energy (translates into stability), the band gap, the electronegativity, the electron-phonon coupling and magnetic properties.
-
-%\begin{figure}[t]
-%    \centering
-%    \includegraphics[width=\textwidth]{figures/ht-workflow.jpg}
-%    \caption{[PLACEHOLDER for workflow] Morten: can you please add the other schematic figure we discussed as placeholder?
-Sebastian makes our own versions of these schematic figures (I can make some VESTA files with materials).
-}
-%    \label{fig:ht-workflow}
-%\end{figure}
-
-%\subsection*{Machine Learning}
-
-%Should contain a brief description of the four ``algorithms'':
-%\begin{itemize}
- %   \item Logistic regression
- %   \item Decision trees
- %   \item Random forest
- %   \item Gradient boost
-%\end{itemize}
-
-%Why these? Works well out of the box, I guess. Readily available in scikit-learn.
-
-\section*{Results and discussion}
-%Includes discussion of results.
-
-\subsection*{Information Flow}  %Sebastian/Oliver (Marianne) 
-% MEB: Since Methods are at the end, I propose to put part of this
-% discussion in the Results section. 
-% This is because it is an important result of the work, and also
-% because it is important to understand the rest of the paper
-
-The information stream in this work can be regarded as many
-modular parts connected in logical pieces. The initial step for
-gathering material data and building features is visualized by the
-the flowchart in Figure~\ref{fig:flowchart-makedata}. 
+The information stream in this work can be regarded as many modular parts connected in logical pieces.
+The initial step for gathering material data and building features is visualized by the the flowchart in Figure~\ref{fig:flowchart-makedata}.
 Initially, we start by extracting all entries in
-the Materials Project that matches a specific query.
+the Materials Project (MP) that matches a specific query. 
+The data in MP is calculated using density functional theory (DFT) as implemented in the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and using the The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
 
@@
 featurization tools to make thousands of features of the data.
-The conditions for this initial query are that the materials must derive from experimental data, and have a band gap wider than $0.1$~eV.
+The conditions for this initial query are that the materials must derive from experimental data and have a band gap wider than $0.1$~eV to exclude metallic compounds.
 In a parallel step, entries that are deemed
 similar to the entries from the initial query
-are extracted from 
-OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, 
-AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, 
-AFLOW-ML \cite{Isayev2017},
-and
-Citrine Informatics REF!??. The results of these steps are combined into
-a data set for further analysis.
+are extracted from the databases OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017}, and the Citrination platform \cite{OMaraJordan2016MDIA}.
+The results of these steps are combined into a data set for further analysis.
 
-A schematic describing the featurization process in Matminer is shown in Figure~\ref{fig:flowchart-featurization}. 
-\textbf{[Describe it and say something about which features we choose.]}  
+%Marianne: I got some stuff from the thesis 
+Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
+This transformation is known as generating descriptors
+or features, however, we will in this work adapt the name featurization.
+The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project.
+A schematic describing the  featurization process in Matminer is shown in Figure~\ref{fig:flowchart-featurization} 
+and focus on a material's composition, structure, atomic sites, density of states and band structure. 
+%\textbf{[Describe it and say something about which features we choose.]}  
 The 39 features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
+The selection of features was kept rather wide as we do not precisely know which features best describe a suitable  host material.
 
@@
 
-After compiling a dataset from the procedure outlined above, we 
-face a challenge in terms of defining a training set that %we can train data on. 
-can be used to train an ML algorithm. 
-This is challenging for two reasons. 
+After compiling a dataset from the procedure outlined above, we face an obstacle in terms of defining a training set for the machine learning algorithms. This is challenging for two reasons. 
 Firstly, although defects like the NV center in diamond and emitters in SiC are becoming
 increasingly well studied, few candidate materials are known. An additional consideration
-is that the physical mechanisms promoting favorable defect properties are not fully understood. 
-Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly
-intricate. 
+is that the physical mechanisms promoting favorable defect properties are not fully understood. Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
 %This is not only challenging due to the lack of known suitable candidates (1),  but also due to the intricacy of defining materials as unsuitable candidates (0). 
-We follow three separate procedures to define a training set consisting of both suitable and unsuitable material candidates for QT.
+We follow three separate procedures to define a training set consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
 
 \subsubsection*{The Ferrenti approach}
-
-The first approach to defining a training set is based on the criteria
-from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
-They suggest a data mining process consisting of four stages by 
-systematically evaluating the suitability of host materials from
-the Materials Project.
-
+The first approach to defining a training set is based on the criteria from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project.
 In this framework, we label \textbf{suitable} candidates by the following steps.
@@
     \begin{itemize}
-        \item contain elements with more than $50\%$ natural abundance of 
-            zero spin isotopes,
+        \item contain elements with more than $50 \ \%$ natural abundance of spin zero  isotopes,
         \item crystallize in non-polar space groups,
@@
     \end{itemize}
-    \item Pragmatically remove toxic, radioactive and otherwise 
-        ``difficult'' materials;
+    \item Pragmatically remove toxic, radioactive and otherwise ``difficult'' materials;
     \begin{itemize}
-        \item exclude Th, U, Cd and Hg,
-        \item exclude any rare-earth metals and noble gases,
-        \item exclude Ru, Os, Fe or Ni.
+        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
+        \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
+        \item exclude transition metal elements with unpaired electrons like Ru, Os, Fe or Ni because of their paramagnetism.
     \end{itemize}
@@
 
-We then label \textbf{unsuitable} candidates as materials in the ICSD database that crystallize in polar space groups, are calculated 
-to be magnetic and have a band gap larger than $0.1$~eV as calculated by PBE-GGA.
+Transition metal elements are eliminated in this approach if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
+In this context, also the symmetry of the crystalline host may be important.
+Therefore, only phases which take on non polar space groups are considered in this approach.
+The energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
+
+We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database that crystallize in polar space groups, are calculated 
+to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional.
+The resulting complete dataset contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
 
 \subsubsection*{The augmented Ferrenti approach}
-In the second approach, we adjust the first approach in order to 
-improve the dataset. This approach is therefore named
-\emph{the augmented Ferrenti approach}.
+In the second approach, we adjust the first approach in order to improve the dataset. This approach is therefore named \emph{the augmented Ferrenti approach}.
 
-In the first approach we included criteria that were not physically motivated, but instead based on a purely practical perspective, like excluding toxic and
-radioactive elements. Such criteria are not necessarily related to what makes 
-a material suitable for quantum technology - eventually it is up to the 
-experimentalist to decide the practicality of the material to be employed. 
+In the first approach we included criteria that were not physically motivated, but instead based on a purely practical perspective, like excluding toxic and radioactive elements.
+Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the practicality of the material to be employed.
 Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
-What is more, we will include a few additional elements that have shown promising properties, but were initially excluded due to the lack of spin zero isotopes.
+Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
 
-The following steps make up the process of choosing \textbf{suitable} candidates 
-in the \emph{augmented Ferrenti approach},
+The following steps constitute the process of choosing \textbf{suitable} candidates 
+in the \emph{augmented Ferrenti approach}. 
 \begin{enumerate}
@@
     \end{itemize}
-    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA,
-    \item Ensure energy above hull is less than $0.2$~eV per atom. 
+    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA.
+The higher band gap requirement is included here to avoid including an unfeasible number of candidate materials.
+    \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
 \end{enumerate}
 
-For \textbf{unsuitable} candidates, we implement the same strategy as the non-augmented
-Ferrenti approach. The result is a somewhat unbalanced dataset, with up to $75 \ \%$ of the 
-materials found in the suitable group. However, the dataset is $78 \ \%$ larger than for
-the Ferrenti approach.
+For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach. The result is a somewhat unbalanced dataset, with up to $75 \ \%$ of the 
+materials found in the suitable group. However, the dataset is $78 \ \%$ larger than for the Ferrenti approach.
 
-\subsubsection*{The insightful approach}
-The third approach differs substantially from the first two approaches in terms 
-of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)   
-to pick our promising material host candidates. We therefore name this scheme 
-\emph{the insightful approach}. 
-Due to the concern of having an insufficient dataset, we will include
-materials that are promising and have shown suitable properties to 
-accommodate deep defects that potentially can exhibit quantum effects. 
-Materials where properties like single-photon emission and spin manipulation are attributed to quantum dot self-assembled formation or lithographic structuring will also be included in this context.  
+\subsubsection*{The intuitive approach}
+The third approach differs substantially from the first two approaches in terms of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)
+to pick our promising material host candidates. 
+In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
+We therefore name this scheme \emph{the intuitive approach}.
+Due to the concern of having a dataset that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating  deep defects that potentially can exhibit quantum effects - even though such effects may not yet have been shown.
+Materials where properties like single-photon emission and spin manipulation are attributed to quantum dots (formed by self-assembly or lithographic structuring) will also be included in this context.
 The approach to pick \textbf{suitable} candidates can be summed up as;   
@@
     \item Pick candidates that match the formulas in Table~\ref{tab:qt-materials}, or the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} or SiGe \cite{Hardy2019}. 
-    \item Make sure the candidates are present in the ICSD database.  
+    \item Make sure that the candidates are present in the ICSD database.  
     \item Perform a manual screening for correct structures. 
@@
 In this context, we consider single-photon emission and coherent spin manipulation.
-The table forms the basis for picking suitable candidates for the insightful approach. 
+The table forms the basis for picking suitable candidates for the intuitive approach. 
 The properties being studied arise from mechanisms related to, e.g., point defects, excitons, and both self-assembled and lithographically structures quantum dots. 
-Quantum emission signatures have been assigned to specific defects in diamond and SiC, but for most other materials, identification of the responsible defects still remains. 
-In the insightful approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set, but also the materials ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe that have been predicted to act as good quantum hosts based on favorable properties such as wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
+Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects still remains. 
+In the intuitive approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
+Additionally, we also include materials matching the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
 
-After the first stage of picking candidates we are left with a list of 202 matching formulas which include 12 entries that have a band gap of less than $0.4$~eV.
-These structures are unstable in terms of energy above hull calculations, and will decompose into other materials in the list with a band gap that is substantially above $0.5$~eV.
-We include all of these structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
+After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
+These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
+We include all of the $202$ structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
 
 %% OH: Dirty details about suitable materials:
-Entries matching the formula C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier.
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
 %OH: Is discussed earlier in thesis but maybe neccessary to mention here? 
-For C, we admit three-dimensional diamond-like structures as explicitly stated in the column tags at Materials Project.
+For C, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from Materials Project.
 Additionally, we find many two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
@@
 C$_{28}$, C$_{48}$, C$_{60}$) were moved to the test set.
-For SiC, we admitted all entries, which involved $2$H, $3$C, $4$H, $6$H and $15$R.
+For SiC, we admitted all entries, which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
 Concerning BN, MoS$_2$, WSe$_2$ and  WS$_2$, we only admit two-dimensional structures.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted suitable or not by the models in a later step.
+For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML models in a later step.
 
-The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} has identified them as potentially promising candidates due to acceptable properties defined in requirements (H1-H4) in \autoref{ssec:qubit-material-host-requirements}.
-We note that only tetrahedrally coordinated structures of the given formulas were present after the band gap restriction of $0.5eV$.
+The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010}  identified them as potentially promising candidates due to suitable material properties.
+%acceptable properties defined in requirements (H1-H4) in \autoref{ssec:qubit-material-host-requirements}. 
+We note that only tetrahedrally coordinated structures of the given formulas were present after applying the band gap restriction of $0.5$~eV.
 
-The suitable candidates contain only compounds that are either elementary (unary) or binary.
+The suitable candidates in the intuitive approach contain only compounds that are either elementary (unary) or binary.
 We do not want to discriminate based on the number of elements in a compound, therefore we remove the feature that describes the number of elements in a compound.
-After three stages, a total of $187$ entries were labeled as suitable candidates.
-%% OH: Stop details suitable materials
-
-Since the dataset constituting suitable candidates in the third approach contains few entries, we add 400 \emph{unsuitable}
-candidates. These are picked at random from the pool of unsuitable candidates 
-from the two previous approaches, in addition to those that are marked as unsuitable through
-the manual screening process. 
+After the three stages, a total of $187$ entries were labeled as suitable candidates.
 See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the insightful approach.
 
+Since the dataset constituting suitable candidates in the third approach contains few entries, we add $400$ \emph{unsuitable} candidates.
+These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable through the manual screening process.
+
 \subsubsection*{Comparing the approaches}
-
 The three different methods for data mining place a particular emphasis on each of their particular goals.
-The Ferrenti approach depends on choosing only elements with zero spin isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding elements.
+The Ferrenti approach depends on choosing only elements with spin zero isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
 Thus, the first approach targets a more narrow prediction space than the second approach does.
@@
 Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the insightful approach to provide an even narrower prediction space.
-\textbf{[Are there any pros or cons we could mention on narrow prediction spaces?]}
 
@@
 
-The Ferrenti approach and the augmented Ferrenti approach share similarities; 
-for example, all unsuitable candidates exhibit polar space groups, and their upper limits for both ionic character and covalent range are equal for suitable candidates.  
+The Ferrenti approach and the augmented Ferrenti approach share several similarities; 
+for example, all unsuitable candidates exhibit polar space groups (follows from the definition of the data sets), and their upper limits for both ionic character and covalent range are equal for suitable candidates.
 %such as having only unsuitable candidates with polar space groups and having an equal amount of upper limit for both ionic character and covalent range for suitable characters. 
@@
 Interestingly, we observe that
-the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former. 
+the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former. 
 %even if the augmented Ferrenti approach is less restricted, it appears that the entries span the same dimensions.
@@
 The biggest difference is found for the insightful approach.
-The entries selected as suitable candidates do not exhibit any magnetization, even though there are both polar and non-polar space groups present.
-Additionally, the range of covalent radius and maximum ionic character span a substantially smaller space than the Ferrenti-based approaches.
-\textbf{This can be interpreted as ... }
+The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups.
+Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller space in the case of the insightful approach than for the Ferrenti-based approaches.
+Here, we can begin to deduce some trends, if the findings from the insightful approach are taken as guidance.
+Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range appear more important.
+Identification of the features that promote quantum compatible characteristics could be crucial for targeted quantum device design based on defect engineering.
 
@@
         \centering
-          \input{figures/parallel-coordinates-plots/01-ferrenti-approach.pgf}
+          \input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}
     \end{subfigure}
@@
         \centering
-          \input{figures/parallel-coordinates-plots/02-augmented-ferrenti-approach.pgf}
+          \input{figures/parallel-coordinates-plots/02-augmented-ferrenti-approach-v2.pgf}
     \end{subfigure}
@@
         \centering
-          \input{figures/parallel-coordinates-plots/03-insightful-approach.pgf}
+          \input{figures/parallel-coordinates-plots/03-insightful-approach-v2.pgf}
     \end{subfigure}
@@
 To limit the data cluttering, we have randomly collected up to $250$ entries for each class and made the lines transparent.
-For the insightful approach, we have used all the $187$ suitable candidates.
-The axes show total magnetization (mag) taken from the Mateirals Project (MP) database, space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) extracted from MP.}
+For the intuitive approach, we have used all the $187$ suitable candidates.
+The axes show total magnetization (mag) taken from the Materials Project (MP) database along with the space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) extracted from MP.}
     \label{fig:parallel-coordinates-approaches}
@@
 Green squares display suitable candidates and red triangles represent unsuitable candidates. 
-Due to the 
-%simplicity 
-complexity 
-of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are overlapping. 
-Hence, using these approaches to data mining could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT. 
-\textbf{Nonetheless, the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further. This could indicate ... } 
-In the case of the insightful approach, on the other hand, we can already start to see a trend where the upper left part of the figure is dominated by suitable candidates.
-Therefore, we can expect that the two Ferrenti approaches would need either supplementary dimensions for further distinguishing, or that it could prove challenging to find a generalized model.
+Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are largely overlapping.
+Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
+%Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
+Therefore, we can expect that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available datasets.
+
+In the case of the intuitive approach, on the other hand, we can already start to see a trend where the upper left part of the figure is dominated by suitable candidates.
+The unsuitable candidates are similarly restricted to the lower right corner and there appears to be a clear barrier between the two, albeit with some exceptions.
+This indicates that the intuitive approach may be capable of separating materials based on their underlying properties.
 
@@
 
-%\marianne{Return here to the basic issues with the two first approaches, in that they perhaps rely too much on practicalities. }  
 It seems likely that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
@@
 %procedures 
-rely on assumptions of which material properties are responsible for the observed effect. 
+rely on previous assumptions for which material properties are responsible for the desired quantum effects.   
 An additional factor to consider is the use of practical considerations when restricting the parameter space for material choice. 
-In short, a much clearer separation is observed for the insightful approach as compared to the others. 
+In short, a much clearer separation is observed for the intuitive approach as compared to the others. 
 These observations constitute an important finding of the work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT. 
-The manual approach of selecting suitable candidates based on experimental findings yields strong indication that a trend does exist and thus is possible to identify. 
-Importantly, the presented methodology for selecting candidates as presented in the insightful approach can be adapted also to other material systems where a specific set of properties are desired but the specific mechanisms behind them are unknown.
+The manual approach for selecting suitable candidates based on experimental findings yields strong indication that a trend does exist and thus is possible to identify. 
+Importantly, the presented methodology for selecting candidates as presented in the intuitive approach can be adapted also to other material systems where a specific set of properties are desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
 
-The constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
+It is important to note that the constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
 We note that this complexity is not necessarily reflected in the descriptors.
@@
 
+Another potential source of uncertainty which should be mentioned is the use of the PBE functional for computing the information in the databases employed herein.
+Despite being immensely successful in describing a number of material properties, PBE is widely known for underestimating the band gap of semiconductors \cite{Freysoldt2014}.
+Therefore, not all properties predicted using the PBE functional are reliable.
+Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput.
+
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology}
 
-Using the four algorithms, optimized at each of the three approaches, and applying them to the case of predicting materials as suitable material hosts for QT, yields 12 sets of results.
-In this chapter, we present sets of representative results for each approach.
+Taking the four machine learning algorithms outlined above and applying them to the datasets optimized using each of the three approaches yields 12 sets of results for predicting  materials as suitable material hosts for QT.
+In this section, we present representative ML results based on each of the three data mining approaches.
 
@@
 Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the insightful approach predicts fewer suitable candidates where manually verification is achievable.
-Manual verification through a literature survey will often not be available, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics.
+Manual verification through a literature survey will often not be available, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
@@
 
-%\section*{Discussion} 
+\section*{Discussion} 
 % Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
@@
 
-%Motivated by our findings, we believe that further computational, experimental, or theoretical verification after a prediction of a possible promising material remains an important step in this work.
-This step is part of the workflow for novel materials discovery, which is visualized in \autoref{fig:ht-workflow}.
+Motivated by our findings, we believe that further computational, experimental, or theoretical verification after a prediction of a possible promising material remains an important step in this work.
+This step is part of the workflow for novel materials discovery, which is visualized in Fig.~\ref{fig:ht-workflow}.
 Nevertheless, we have provided an exploratory analysis for the discovery of novel materials to be used in QT.
-Considering the number of materials predicted as suitable candidates by our models and approaches, we hope it encouragesfurther studies and identification of possible new material hosts.
+Considering the number of materials predicted as suitable candidates by our models and approaches, we hope it encourages further studies and identification of possible new material hosts.
 
-%We find that including toxic materials etc in the training set is vital for reliable predictions.
+We find that including toxic materials etc in the training set is vital for reliable predictions.
 They can then later be excluded when planning experiments, but the practical considerations should be saved for last and not included in the initial criteria.
@@
 \subsection*{Material Informatics}  
-Screening and workflow and approaches.
+Screening and workflow and approaches. Technicalities of featurization if necessary.
 
@@
 %The codes developed in this study are available from the authors upon reasonable request. [Marianne: I assume you want to add the Github link here?] 
-The codes employed to develop the ML models are available online at [Github link].
+The codes employed to develop the ML models are available online at https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts (DOI: 10.5281/zenodo.4633959 - Update with new release later).
+%This DOI refers to an release of a Github Repository.
 
@@
 
-The work of MHJ is supported by the U.S. Department of Energy,
+The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
+%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
+The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship. 
+The work of MHJ is partially supported by the U.S. Department of Energy,
 Office of Science, office of Nuclear Physics under grant
@@
 No. PHY-1404159 and PHY-2013047.
-The work of MEB and LV was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
-%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
-The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship.
 

### 2021-12-10 paper.tex
Updates from Overleaf

@@
 
-%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25000$ materials.
+%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials.
 Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the insightful approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
-Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25'000$ materials.
+Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25'000$ materials.
 The information from the databases was converted into nearly $5'000$ physics-informed features.
@@
 
-After compiling a dataset from the procedure outlined above, we face an obstacle in terms of defining a training set for the machine learning algorithms. This is challenging for two reasons. 
+After compiling a data set from the procedure outlined above, we face an obstacle in terms of defining a training set for the machine learning algorithms. This is challenging for two reasons. 
 Firstly, although defects like the NV center in diamond and emitters in SiC are becoming
@@
 to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional.
-The resulting complete dataset contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
+The resulting complete data set contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
 
 \subsubsection*{The augmented Ferrenti approach}
-In the second approach, we adjust the first approach in order to improve the dataset. This approach is therefore named \emph{the augmented Ferrenti approach}.
+In the second approach, we adjust the first approach in order to improve the data set. This approach is therefore named \emph{the augmented Ferrenti approach}.
 
@@
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach. The result is a somewhat unbalanced dataset, with up to $75 \ \%$ of the 
-materials found in the suitable group. However, the dataset is $78 \ \%$ larger than for the Ferrenti approach.
+For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach. The result is a somewhat unbalanced data set, with up to $75 \ \%$ of the 
+materials found in the suitable group. However, the data set is $78 \ \%$ larger than for the Ferrenti approach.
 
@@
 We therefore name this scheme \emph{the intuitive approach}.
-Due to the concern of having a dataset that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating  deep defects that potentially can exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of having a data set that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating  deep defects that potentially can exhibit quantum effects - even though such effects may not yet have been shown.
 Materials where properties like single-photon emission and spin manipulation are attributed to quantum dots (formed by self-assembly or lithographic structuring) will also be included in this context.
@@
 
-Since the dataset constituting suitable candidates in the third approach contains few entries, we add $400$ \emph{unsuitable} candidates.
+Since the data set constituting suitable candidates in the third approach contains few entries, we add $400$ \emph{unsuitable} candidates.
 These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable through the manual screening process.
@@
 %Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
-Therefore, we can expect that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available datasets.
+Therefore, we can expect that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available data sets.
 
@@
 
-It is important to note that the constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
+It is important to note that the constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
 We note that this complexity is not necessarily reflected in the descriptors.
@@
 
-Taking the four machine learning algorithms outlined above and applying them to the datasets optimized using each of the three approaches yields 12 sets of results for predicting  materials as suitable material hosts for QT.
+Taking the four machine learning algorithms outlined above and applying them to the data sets optimized using each of the three approaches yields 12 sets of results for predicting  materials as suitable material hosts for QT.
 In this section, we present representative ML results based on each of the three data mining approaches.
@@
 If this is also possible for BC$_2$N, remains to be seen.
-We note that BC$_3$N is not present in MP, and therefore not present in our dataset.
+We note that BC$_3$N is not present in MP, and therefore not present in our data set.
 
@@
 CuI, however, has recently been synthesized and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the dataset than, e.g., the more covalent materials of Si, SiC and diamond.
+Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the data set than, e.g., the more covalent materials of Si, SiC and diamond.
 It seems that ionic character alone is not an obstacle, but it is unknown at this time whether CuI has higher potential for hosting single-photon emitters, spin-manipulation or QT operation via nanostructuring.
@@
 Pure decision trees can easily lead to overfitting of the data under study, leading to a model that exhibits a high variance.
-Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Ref.~\cite{Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
-Gradient boosting implemented through the  XGBoost library, is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
+Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
+Gradient boosting implemented through the  XGBoost library \cite{xgboost2016}, is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
 
@@
 
-The data that support the findings of this study are available from the corresponding author, and the datasets used to generate the ML models are available online at [Github link].
+The data sets that support the findings of this study are available from the corresponding author, and the data sets used to generate the ML models are available online at [Github link].
 

### 2021-12-10 figures/tikz-plots/prediction-fig.tex
Updates from Overleaf

@@
     \centering
+    (a)
+    \\
     \begin{forest}
@@
         ]
-    [Decision tree,node box,alias=a1
+        [Decision trees,node box,alias=a1
           [$12308$]
@@
         ]
-    [Random forest,node box,alias=a1
+        [Random forests,node box,alias=a1
           [$9345$]
@@
         ]
-    [Gradient boost,node box,alias=a1
+        [Gradient boosting,node box,alias=a1
           [$11835$]
@@
 %\vspace*{-95mm}
+    \\
+    (b)
+    \\
 \begin{forest}
@@
     ]
-    [Decision tree,node box,alias=a1
+    [Decision trees,node box,alias=a1
       [$8143$]
@@
     ]
-    [Random forest,node box,alias=a1
+    [Random forests,node box,alias=a1
       [$7199$]
@@
     ]
-    [Gradient boost,node box,alias=a1
+    [Gradient boosting,node box,alias=a1
       [$8762$]
@@
 %\vspace*{20mm}
+    \\
+    (c)
+    \\
  \begin{forest}
@@
     ]
-    [Decision tree,node box,alias=a1
+    [Decision trees,node box,alias=a1
       [$23347$]
@@
     ]
-    [Random forest,node box,alias=a1
+    [Random forests,node box,alias=a1
       [$24001$]
@@
     ]
-    [Gradient boost,node box,alias=a1
+    [Gradient boosting,node box,alias=a1
       [$23948$]

### 2021-12-10 paper.tex
Updates from Overleaf

@@
 %OH: Is discussed earlier in thesis but maybe neccessary to mention here? 
-For C, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from Materials Project.
+For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
 Additionally, we find many two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
@@
 Concerning BN, MoS$_2$, WSe$_2$ and  WS$_2$, we only admit two-dimensional structures.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML models in a later step.
+For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by machine learning methods  in a later step.
 
@@
 
-Taking the four machine learning algorithms outlined above and applying them to the data sets optimized using each of the three approaches yields 12 sets of results for predicting  materials as suitable material hosts for QT.
+Taking the four machine learning algorithms outlined above and applying them to the data sets optimized using each of the three approaches yields twelve sets of results for predicting  materials as suitable material hosts for QT.
 In this section, we present representative ML results based on each of the three data mining approaches.
@@
 We first consider the machine learning classification of the test set based on the Ferrenti approach. 
-Notably we find that carbon in diamond-like structure is classified as a suitable candidate from the training set in the Ferrenti approach. 
+Notably we find that carbon in a diamond-like structure is classified as a suitable candidate from the training set in the Ferrenti approach. 
 This is in agreement with the suitable candidates that were defined manually for the insightful approach. 
-Interestingly, from the training set of the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures are labeled as suitable. 
+Interestingly, from the training set of the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures is labeled as suitable. 
 %Out of the known suitable candidates defined for the insightful approach, we find carbon in diamond-like structures, but we also find two-dimensional carbon in graphite-like structures labeled as suitable.
@@
 
-The number of candidates predicted by each of the four machine learning algorithms 'Logistic regression', 'Decision tree', 'Random forest' and 'Gradient boost' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach.
-From the training set of $23623$ materials, the four models consistently predict at least $11.000$ materials as promising candidates.
-All of the models agree on $6804$ suitable candidates, however, many of the materials are predicted with the probability similar to a coin-flip.
+The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach.
+From the training set of $23623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates.
+All four methods agree on $6804$ suitable candidates, however, many of the materials are predicted with the probability similar to a coin flip.
 If we were to raise the minimum bar of a prediction to
-$0.7$ instead of $0.5$, the models would only agree on around $3000$ suitable candidates. 
-Of the known suitable materials that were present in the training set, we find that all four models admit almost all materials with a chemical formula matching the known candidates.
-This can allow materials with unfortunate structures to be labeled as suitable candidates by all models.
-Consequently, the models do not recognize the strict band gap restriction, which makes it challenging to facilitate deep defects.
-Ideally, we would expect that the models would have probabilities lower than $0.5$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all models.
+$0.7$ instead of $0.5$, the above ML approaches would only agree on around $3000$ suitable candidates. 
+Of the known suitable materials that were present in the training set, we find that all four methods admit almost all materials with a chemical formula matching the known candidates.
+This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods.
+Consequently, the ML methods do not recognize the strict band gap restriction, which makes it challenging to facilitate deep defects.
+Ideally, we would expect that the ML methods would have probabilities lower than $0.5$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all ML methods studied here.
 
@@
 
-The four models predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the test set, where they all agree on a set of $9227$ predicted suitable candidates.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the test set, where they all agree on a set of $9227$ predicted suitable candidates.
 Comparing to the training set reveals that all of the unlabeled known suitable candidates are, in fact, predicted as suitable candidates.
-Unfortunately, the models also yield predictions that do not match with what one would expect from physical considerations.
-All four machine learning models confidently predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl. 
+Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physical considerations.
+All four ML methods confidently predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl. 
 At least, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Furthermore, despite enforcing a larger band gap restriction of $1.5$~eV for the training set, we find that all models are predicting suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the models are not taking this important property into account when classifying the materials.
+Furthermore, despite enforcing a larger band gap restriction of $1.5$~eV for the training set, we find that all our implemented ML methods  predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the methods are not taking this important property into account when classifying the materials.
 
 \subsubsection*{The insightful approach}
-The ML models that were trained on the data set defined from the insightful approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
+The ML methods that were trained on the data set defined from the insightful approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
 %Trained on the training set defined as the insightful approach, the models are able to predict radically fewer suitable candidates compared to the two latter approaches. 
-A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision tree, random forest and gradient boost, respectively.
-All the four ML models agree on a total of $214$ suitable candidates.
+A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
+All the four ML methods agree on a total of $214$ suitable candidates.
 However, $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
@@
 Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
-Removing ZnO from the training set for the insightful approach might result in fewer or even no oxide compounts being predicted above the suitability limit.
+Removing ZnO from the training set for the insightful approach might result in fewer or even no oxide compounds being predicted above the suitability limit.
 
@@
 The Ferrenti approach also admits a large number of entries, but is otherwise not very different from the augmented version.
-Importantly, by applying the four ML models to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
+Importantly, by applying the four ML methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
 Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the insightful approach predicts fewer suitable candidates where manually verification is achievable.
@@
 
-It is important to note that the insightfull approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
+It is important to note that the insightful approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
 Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
@@
 %underestimating the band gap severely, and therefore there is a chance that the models consider the band gap as noise and not useful information. 
-It is therefore possible that the band gap is not considered an important parameter by the ML models. 
+It is therefore possible that the band gap is not considered an important parameter by the ML methods. 
 %Understanding the motivation behind the classification of the models will be an important step towards understanding ... 
 Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
-Thus, one can argue that the models find other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
+Thus, one can argue that the ML methods find other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
 
-We find that $119$ of the $214$ candidates predicted as suitable by the insightful approach (when the probability cut-off is set to [X]) were also selected by all models in the augmented Ferrenti approach.
+We find that $119$ of the $214$ candidates predicted as suitable by the insightful approach (when the probability cut-off is set to [X]) were also selected by all ML methods in the augmented Ferrenti approach.
 %Of the $214$ suitable candidates predicted by all models in the insightful approach, we find $119$ of them also predicted as suitable by all models in the augmented Ferrenti approach. 
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding models agree on a $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
-\textbf{The list of the $47$ materials agreed on by all models and all three approaches as suitable candidates with a probability $> X \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
+All approaches and their corresponding methods agree on a $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+\textbf{The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a probability $> X \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
 
@@
 Nevertheless, we have provided an exploratory analysis for the discovery of novel materials to be used in QT.
-Considering the number of materials predicted as suitable candidates by our models and approaches, we hope it encourages further studies and identification of possible new material hosts.
+Considering the number of materials predicted as suitable candidates by our machine learning methods and approaches, we hope it encourages further studies and identification of possible new material hosts.
 
@@
 AFLOW-ML \cite{Isayev2017} is an API that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which they denote as \textit{fragment descriptors}.
-Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression model to predict the band gap width.
-The accuracy is validated by a five-fold cross-validation process for each model, where they report a $93 \ \%$ prediction success of their initial binary classification model.
+Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap width.
+The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
 
@@
 Boosting methods like gradient boosting use decision trees as  weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under study, leading to a model that exhibits a high variance.
-Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the model employed, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
+Pure decision trees can easily lead to overfitting of the data under study, leading to a machine learning method that exhibits a high variance.
+Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
 Gradient boosting implemented through the  XGBoost library \cite{xgboost2016}, is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
@@
 
-The data sets that support the findings of this study are available from the corresponding author, and the data sets used to generate the ML models are available online at [Github link].
+The data sets that support the findings of this study are available from the corresponding author, and the data sets used in our  machine learning studies are available online at [Github link].
 
@@
 %The codes developed in this study are available from the authors upon reasonable request. [Marianne: I assume you want to add the Github link here?] 
-The codes employed to develop the ML models are available online at https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts (DOI: 10.5281/zenodo.4633959 - Update with new release later).
+The codes employed to develop the machine learning results are available online at https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts (DOI: 10.5281/zenodo.4633959 - Update with new release later).
 %This DOI refers to an release of a Github Repository.
@@
 The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship. 
-The work of MHJ is partially supported by the U.S. Department of Energy,
+The work of MHJ was supported by the U.S. Department of Energy,
 Office of Science, office of Nuclear Physics under grant

### 2021-12-11 paper.tex
Updates from Overleaf

@@
 %We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials.
-Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the insightful approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
-Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25'000$ materials.
-The information from the databases was converted into nearly $5'000$ physics-informed features.
+Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the intuitive approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
+Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25.000$ materials.
+The information from the databases was converted into nearly $5000$ physics-informed features.
 Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}.
-%Rename insightful approach! To what? 
+%Rename intuitive approach! To what? 
 %Options include stringent, strict, cherry-picked, informed and intuitive. 
@@
 
-%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the insightful approach proved suitable.
-All models for the insightful approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs.
+%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the intuitive approach proved suitable.
+All models for the intuitive approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs.
 All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
@@
 Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as quantum cryptography and the quantum internet.  
-Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a 200'000 core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
-Most recently, IBM announced its 127 qubit quantum processor~\cite{IBM2021}.
+Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
+Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
 
@@
     \centering
-%    \includegraphics[width=0.9\textwidth]{figures/ht-workflow.jpg}
     \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new.png}
-    \caption{[PLACEHOLDER] Schematic of an example workflow in material informatics. 
-    %\marianne{Sebastian makes simplified figure.}
+    \caption{Schematic of an example workflow in material informatics: results from theory, experiment and computation are fed into material databases.
+A cycle involving material screening, machine learning and predictions leads to knowledge gain and ultimately applications in fields such as clean energy and quantum technology.
     }
@@
 The fourth paradigm instead introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.
-Instead of searching through a host of signals for the one that matches our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies. 
+Instead of searching through a host of signals for the one that matches our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing materials properties for a wide range of different systems.
@@
 the Materials Project (MP) that matches a specific query. 
-The data in MP is calculated using density functional theory (DFT) as implemented in the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and using the The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
+The MP database contains ground state properties of different materials that are calculated using density functional theory (DFT) as implemented in the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and using the The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
 
@@
 
-%Marianne: I got some stuff from the thesis 
 Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
@@
 is that the physical mechanisms promoting favorable defect properties are not fully understood. Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
-%This is not only challenging due to the lack of known suitable candidates (1),  but also due to the intricacy of defining materials as unsuitable candidates (0). 
 We follow three separate procedures to define a training set consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
@@
     \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional.
+The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations.
     \item Ensure that energy above hull is less than $0.2$~eV per atom.
@@
     \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA.
-The higher band gap requirement is included here to avoid including an unfeasible number of candidate materials.
+The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials.
     \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
@@
 \subsubsection*{The intuitive approach}
-The third approach differs substantially from the first two approaches in terms of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview)
-to pick our promising material host candidates. 
+The third approach differs substantially from the first two approaches in terms of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview) to pick our promising material host candidates.
 In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
@@
 After the three stages, a total of $187$ entries were labeled as suitable candidates.
-See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the insightful approach.
+See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the intuitive approach.
 
-Since the data set constituting suitable candidates in the third approach contains few entries, we add $400$ \emph{unsuitable} candidates.
+Since the data set constituting suitable candidates in the third approach contains few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
 These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable through the manual screening process.
@@
 \subsubsection*{Comparing the approaches}
-The three different methods for data mining place a particular emphasis on each of their particular goals.
+The three different approached to data mining place a particular emphasis on each of their particular goals.
 The Ferrenti approach depends on choosing only elements with spin zero isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
 Thus, the first approach targets a more narrow prediction space than the second approach does.
-However, perhaps the most restricted approach is the insightful approach.
-Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the insightful approach to provide an even narrower prediction space.
-
-%\marianne{Short paragraph here (or somewhere else) highlighting the potential issues with the two first approaches in terms of actually identifying any trends.}
+However, perhaps the most restricted approach is the intuitive one.
+Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the intuitive approach to provide an even narrower prediction space.
+Here, one should keep in mind that ...
 
@@
 Thus, parallel coordinate plots can turn many-dimensional data into a compact two-dimensional representation.
-Due to possible data cluttering, the figure visualizes a random sample of each class with an upper limit of $250$ per class with transparent lines.
+Due to possible data cluttering, the figure visualizes a random sample of each class (suitable or unsuitable) with an upper limit of $250$ per class with transparent lines.
 The green and red polylines represent suitable and unsuitable candidates, respectively.
 
-The Ferrenti approach and the augmented Ferrenti approach share several similarities; 
-for example, all unsuitable candidates exhibit polar space groups (follows from the definition of the data sets), and their upper limits for both ionic character and covalent range are equal for suitable candidates.
-%such as having only unsuitable candidates with polar space groups and having an equal amount of upper limit for both ionic character and covalent range for suitable characters. 
-Additionally, the two approaches share that suitable candidates can consist of up to five different elements. 
-Interestingly, we observe that
-the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former. 
-%even if the augmented Ferrenti approach is less restricted, it appears that the entries span the same dimensions.
+The Ferrenti approach and the augmented Ferrenti approach share several similarities. 
+Interestingly, we observe that the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former.
+The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
+Moreover, all candidates that were labeled unsuitable exhibit polar space groups (follows from the definition of the data sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
 
-The biggest difference is found for the insightful approach.
-The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller space in the case of the insightful approach than for the Ferrenti-based approaches.
-Here, we can begin to deduce some trends, if the findings from the insightful approach are taken as guidance.
+The biggest difference is found for the intuitive approach.
+The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups - contrarily to the two Ferrenti-based approaches.
+Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller space in the case of the intuitive approach than for the two former ones.
+Here, we can begin to deduce some trends, if the findings from the intuitive approach are taken as guidance.
 Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range appear more important.
@@
 Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are largely overlapping.
+The logic behind categorizing materials in the two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca}.
 Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
@@
 This indicates that the intuitive approach may be capable of separating materials based on their underlying properties.
+Thus, devising a sound framework for the data mining process is paramount to obtain a suitable training set for the machine learning methods.
 
@@
 It seems likely that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
-Where the insightful approach takes advantage of the experimental knowledge that is already available in the literature, the Ferrenti and augmented Ferrenti schemes
-%procedures 
-rely on previous assumptions for which material properties are responsible for the desired quantum effects.   
-An additional factor to consider is the use of practical considerations when restricting the parameter space for material choice. 
-In short, a much clearer separation is observed for the intuitive approach as compared to the others. 
+Where the intuitive approach takes advantage of the experimental knowledge that is available in the literature, the Ferrenti and augmented Ferrenti schemes rely on assumptions for which material properties are responsible for the desired quantum effects.
+An additional factor to consider is the use of practical considerations (e.g., toxic materials or the availability of spin zero isotopes) when restricting the parameter space for material choice. 
+Intriguingly, a much clearer separation is observed for the intuitive approach, where no restrictions were imposed in terms of specific characteristics for the materials, as compared to the two others.
 These observations constitute an important finding of the work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT.
-The manual approach for selecting suitable candidates based on experimental findings yields strong indication that a trend does exist and thus is possible to identify. 
-Importantly, the presented methodology for selecting candidates as presented in the intuitive approach can be adapted also to other material systems where a specific set of properties are desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
+The manual approach for selecting suitable candidates based on experimental findings yields strong indications that a trend does exist and thus is possible to identify.
+Importantly, the methodology for selecting candidates as implemented in the intuitive approach can be adapted also to other material systems where a specific set of properties is desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
 
@@
 We note that this complexity is not necessarily reflected in the descriptors.
-%Additionally, we acknowledge that many compositions deemed as suitable candidates consist of either rare or dangerous elements.
-By utilizing an enormously large database as Materials Project, we have to account for their ultimate goal - to model all possible materials and their properties.
-%The automated process of adding an entry to their database does not necessarily contain all relevant information about a respective material. This is information that needs to be added manually.
 Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
@@
 
-Another potential source of uncertainty which should be mentioned is the use of the PBE functional for computing the information in the databases employed herein.
+Another potential source of uncertainty that should be mentioned is the use of the PBE functional for computing the information in the databases employed herein.
 Despite being immensely successful in describing a number of material properties, PBE is widely known for underestimating the band gap of semiconductors \cite{Freysoldt2014}.
-Therefore, not all properties predicted using the PBE functional are reliable.
-Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput.
+Therefore, not all properties predicted using the PBE functional are reliable, and the band gaps in particular cannot be trusted in absolute terms.
+Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor properties.
 
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology}
+Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
+These four machine learning methods were applied to the data sets that were optimized using each of the three approaches (Ferrenti, augmented Ferrenti and intuitive) outlined above.
+This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+In this section, we present representative results after applying machine learning methods to the datasets resulting from each of the three data mining approaches.
 
-Taking the four machine learning algorithms outlined above and applying them to the data sets optimized using each of the three approaches yields twelve sets of results for predicting  materials as suitable material hosts for QT.
-In this section, we present representative ML results based on each of the three data mining approaches.
-
-\subsubsection*{The Ferrenti Approach}
-%Should we include materials in training set? Or keep it, but move into data mining discussion?
-We first consider the machine learning classification of the test set based on the Ferrenti approach. 
-Notably we find that carbon in a diamond-like structure is classified as a suitable candidate from the training set in the Ferrenti approach. 
-This is in agreement with the suitable candidates that were defined manually for the insightful approach. 
-Interestingly, from the training set of the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures is labeled as suitable. 
-%Out of the known suitable candidates defined for the insightful approach, we find carbon in diamond-like structures, but we also find two-dimensional carbon in graphite-like structures labeled as suitable.
+\subsubsection*{The Ferrenti approach}
+We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
+Taking a closer look at the training set from the Ferrenti approach, we find that carbon in a diamond-like structure is classified as a suitable candidate. 
+This is in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also the candidates that were manually defined as suitable in the intuitive approach.  
+Interestingly, in the training set from the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures are labeled as suitable. 
 All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present.
-
-%\input{figures/tikz-plots/ferrenti-approach.tex}
-%\input{figures/tikz-plots/augmented-ferrenti-approach.tex} 
-%\input{figures/tikz-plots/insightful-approach.tex}
+Note that this is the 3C polytype of SiC, meaning that the most quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
 
@@
 The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach.
-From the training set of $23623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates.
-All four methods agree on $6804$ suitable candidates, however, many of the materials are predicted with the probability similar to a coin flip.
-If we were to raise the minimum bar of a prediction to
-$0.7$ instead of $0.5$, the above ML approaches would only agree on around $3000$ suitable candidates. 
-Of the known suitable materials that were present in the training set, we find that all four methods admit almost all materials with a chemical formula matching the known candidates.
+From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates.
+All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with the probability similar to a coin flip.
+If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on around $3000$ suitable candidates. 
+We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the training set. 
 This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods. 
-Consequently, the ML methods do not recognize the strict band gap restriction, which makes it challenging to facilitate deep defects.
-Ideally, we would expect that the ML methods would have probabilities lower than $0.5$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all ML methods studied here.
+%Be careful here - PBE is known for underestimating band gaps. 
+For example, the ML methods do not maintain the band gap restriction from the training set definition. 
+Ideally, we would expect that the ML methods would have probabilities lower than $50 \ \%$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein, 
+indicating that the band gap restriction is not recognized as important by the machine learning algorithms. 
+Small band gaps could make it challenging to facilitate deep level defects. 
+On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for some of the materials.
 
-\subsubsection*{The augmented Ferrenti Approach}
+\subsubsection*{The augmented Ferrenti approach}
+Next, we turn to the more liberal augmented Ferrenti approach containing a $78 \ \%$ larger amount of materials than the former one.
+In the training set, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The training set includes a larger variety of
+known 
+%classified 
+suitable candidates compared to the Ferrenti approach due to admitting more elements in the initial restriction.
+However, since we also included a larger band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known
+chemical formula present in the training set.
 
-%Should we include materials in training set? Or keep it, but move into data mining disc
-%MB I think it's fine here also 
-Next, we turn to the more liberal augmented Ferrenti approach.
-In the training set, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs, AlP, carbon in both diamond- and graphite-like structures, and AlN in three different structures.
-The training set includes a larger variety of known suitable candidates compared to the Ferrenti approach due to admitting more elements in the initial restriction.
-However, since we also included a larger band gap restriction of $1.5$~eV, we find a more sparse representation of each known chemical formula present in the training set.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a set of $9227$ predicted suitable candidates.
+Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
+Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physical considerations.
+All four ML algorithms confidently (to probabilities of $83 \ \%$ and $60 \ \%$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of the bonding (see, e.g., Ref.~\cite{Weber2010}).
+Indeed, single-photon emitters with sharp and bright zero phonon lines are uncommon in materials with a strong ionic character. 
+Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the ML methods are not adhering rigidly to the band gap restriction when classifying the materials.
 
-The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the test set, where they all agree on a set of $9227$ predicted suitable candidates.
-Comparing to the training set reveals that all of the unlabeled known suitable candidates are, in fact, predicted as suitable candidates.
-Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physical considerations.
-All four ML methods confidently predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl. 
-At least, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Furthermore, despite enforcing a larger band gap restriction of $1.5$~eV for the training set, we find that all our implemented ML methods  predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the methods are not taking this important property into account when classifying the materials.
-
-\subsubsection*{The insightful approach}
-The ML methods that were trained on the data set defined from the insightful approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
-%Trained on the training set defined as the insightful approach, the models are able to predict radically fewer suitable candidates compared to the two latter approaches. 
+\subsubsection*{The intuitive approach}
+The ML methods that were trained on the data set defined in the intuitive approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four ML methods agree on a total of $214$ suitable candidates.
-However, $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
+All the four ML methods agree on a total of $214$ suitable candidates to a probability above $50 \ \%$.
+Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
+Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
 
@@
 
-Initially, we consider the materials that were classified as suitable with a probability of $85 \ \%$ or higher by all the models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+Initially, we consider the materials that were classified as suitable with a probability of $85 \ \%$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
 The compound BN (mp-$1639$) is already present in the training data as a suitable candidate, and therefore we believe the models recognize this as a suitable candidate with high probability.
 Furthermore, two compositions of CdSe (mp-$2691$ and mp-$1070$) have been predicted as suitable, possibly as a consequence of CdS being present as a suitable candidate in the training set.
-The element S resides in the same group as Se, and the data shows that the two compounds of CdSe are associated with a calculated band gap of $0.5$ eV and $0.55$ eV, respectively, in the MP database.
+The element S resides in the same group as Se, and the data shows that the two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.55$~eV, respectively, in the MP database.
 Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$~eV \cite{CelebiSerdar2007SaCo, BanerjeeR2000Eots}.
@@
 
-We also find two compositions with the same chemical formula, the orthorhombic coordinated (mp-$629458$) and the chalcopyrite structured BC$_2$N (mp-$1008523$) where the first structure is in a polar space group while the latter is not.
-The band gaps are in MP calculated as $1.85$ eV and $1.65$ eV, respectively.
+In the case of BC$_2$N we find two compositions with the same chemical formula, the orthorhombic coordinated (mp-$629458$) and the chalcopyrite structured (mp-$1008523$) BC$_2$N, where the first takes on a polar space group while the latter does not.
+The band gaps are listed as $1.85$~eV and $1.65$~eV, respectively, in the MP database.
 BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN.
-Both structures have, as expected, strong covalent character and have been studied for application as nanostructures \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020} in ab-initio calculations.
-Of similar compounds, it has been predicted that the diamond-like structure of BC$_3$N can be a prominent spin qubit material host \cite{Wang2020SpinQB}.
-By creating a boron (B) vacancy, it will immediately lead to an NV center with similar properties as found in the NV center in diamond.
-If this is also possible for BC$_2$N, remains to be seen.
-We note that BC$_3$N is not present in MP, and therefore not present in our data set.
+Both structures have, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+It has similarly been predicted that the diamond-like structure of BC$_3$N can be a prominent spin qubit material host \cite{Wang2020SpinQB}.
+By creating a boron (B) vacancy one can obtain a nitrogen-vacancy center with similar properties to those found for the NV center in diamond.
+Whether this is also possible for BC$_2$N remains to be seen.
+We note that BC$_3$N is not present in the MP database and therefore not included in our dataset.
 
-The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) show some similar properties in the data, and have band gaps of $0.30$, $1.18$ and $1.73$~eV, respectively.
+The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) exhibit some comparable properties, and have band gaps of $0.30$, $1.18$ and $1.73$~eV, respectively.
 Single self-assembled InAs quantum dots have already been demonstrated \cite{Liu2018}, and is therefore an exciting possible material to use in quantum technology.
@@
 It seems that ionic character alone is not an obstacle, but it is unknown at this time whether CuI has higher potential for hosting single-photon emitters, spin-manipulation or QT operation via nanostructuring.
-Note that NaCl was not predicted as suitable for QT in the insightful approach.
+Note that NaCl was not predicted as suitable for QT in the intuitive approach.
 
 Lowering the probability requirement from $85 \ \%$ to $75 \ \%$ for all models results in $66$ materials. 
-The full list is contained in the Supplementary Material at \cite{supplementary}. 
+The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
 The list of predicted suitable candidates now includes ternary compounds of the formula ABC$_2$.
@@
 
-Among the $66$ materials that all models in the insightful approach agreed on with more than $75 \ \%$ probability, we emphasize the presence of Ge, GeC, BP and InP.
+Among the $66$ materials that all models in the intuitive approach agreed on with more than $75 \ \%$ probability, we emphasize the presence of Ge, GeC, BP and InP.
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
@@
 Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
-Removing ZnO from the training set for the insightful approach might result in fewer or even no oxide compounds being predicted above the suitability limit.
+Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above the suitability limit.
 
@@
 
-%Supplementary information: List displaying the 66 predicted candidates that all models in the insightful approach agreed on with more than 75\% probability. %appendix/listof66materials
+%Supplementary information: List displaying the 66 predicted candidates that all models in the intuitive approach agreed on with more than 75\% probability. %appendix/listof66materials
 
-\subsubsection*{Comparison of the approaches}
+\subsubsection*{Comparing the approaches}
 
@@
 Importantly, by applying the four ML methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
-Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the insightful approach predicts fewer suitable candidates where manually verification is achievable.
+Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
 Manual verification through a literature survey will often not be available, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
-It is important to note that the insightful approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
+It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
 Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
@@
 
-We find that $119$ of the $214$ candidates predicted as suitable by the insightful approach (when the probability cut-off is set to [X]) were also selected by all ML methods in the augmented Ferrenti approach.
-%Of the $214$ suitable candidates predicted by all models in the insightful approach, we find $119$ of them also predicted as suitable by all models in the augmented Ferrenti approach. 
+We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the probability cut-off is set to [X]) were also selected by all ML methods in the augmented Ferrenti approach.
+%Of the $214$ suitable candidates predicted by all models in the intuitive approach, we find $119$ of them also predicted as suitable by all models in the augmented Ferrenti approach. 
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.

### 2021-12-11 supplementary.tex
Updates from Overleaf

@@
 Contents: \\ 
-Supplementary methods --- information on machine learning approaches and the featurization process. \\ 
-Supplementary results --- tables of resulting materials from the different approaches and models used.  \\ 
+Supplementary methods --- additional information on the featurization process and implementation of the machine learning models. \\ 
+Supplementary results --- tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches. \\ 
 Supplementary references.
@@
 \subsection*{Optimization of machine learning models}
-Something important to add here??
+Morten/Oliver please add details.
 
 \section*{Supplementary results}
-Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all models in the insightful approach agreed on with more than $75 \ \%$ probability.
+Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with more than $75 \ \%$ probability.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.

### 2021-12-13 paper.tex
Updates from Overleaf

@@
 Furthermore, two compositions of CdSe (mp-$2691$ and mp-$1070$) have been predicted as suitable, possibly as a consequence of CdS being present as a suitable candidate in the training set.
-The element S resides in the same group as Se, and the data shows that the two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.55$~eV, respectively, in the MP database.
+The element S resides in the same group as Se, and the data shows that the two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.6$~eV, respectively, in the MP database.
 Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$~eV \cite{CelebiSerdar2007SaCo, BanerjeeR2000Eots}.
-%Unfortunately, Cd is a toxic metal which could make large scale fabrication challenging.
 
 In the case of BC$_2$N we find two compositions with the same chemical formula, the orthorhombic coordinated (mp-$629458$) and the chalcopyrite structured (mp-$1008523$) BC$_2$N, where the first takes on a polar space group while the latter does not.
-The band gaps are listed as $1.85$~eV and $1.65$~eV, respectively, in the MP database.
+The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
 BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN.
@@
 
-The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) exhibit some comparable properties, and have band gaps of $0.30$, $1.18$ and $1.73$~eV, respectively.
-Single self-assembled InAs quantum dots have already been demonstrated \cite{Liu2018}, and is therefore an exciting possible material to use in quantum technology.
+The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) have band gaps of $0.3$, $1.2$ and $1.7$~eV, respectively, and exhibit comparable properties.
+Self-assembled InAs quantum dots, for example, are an exciting possible material to use in quantum technology \cite{Liu2018}.
 To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized and contains the toxic element Cd, which could prove an obstacle for large scale utilization.
-CuI, however, has recently been synthesized and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
+CuI, however, has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
 Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the data set than, e.g., the more covalent materials of Si, SiC and diamond.
-It seems that ionic character alone is not an obstacle, but it is unknown at this time whether CuI has higher potential for hosting single-photon emitters, spin-manipulation or QT operation via nanostructuring.
+It seems that ionic character alone is not an obstacle, but it is unknown at this time whether, if CuI in fact does have potential for hosting single-photon emitters and spin centers, these properties would result from deep level defects or nanostructuring.
 Note that NaCl was not predicted as suitable for QT in the intuitive approach.
@@
 The elements Ga, Cd and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Te, P or As may reside at the C site.
-Most of the formed compounds include toxic elements with one exception.
-This exception is ZnGeP$_2$ (mp-$4524$), which takes the chalcopyrite-like structure, with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database and an experimentally reported band gap of $1.99$~eV \cite{Xing1989}.
-ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, has strong covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+Most of the predicted compounds include toxic elements with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
+In comparison, the experimentally reported band gap is larger at $2.0$~eV \cite{Xing1989}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains unknown  
-whether the candidate can facilitate the isolated deep energy levels often associated with defects showing quantum compatible properties. 
-%if the candidate can provide isolation and shelter to experimentally facilitate a deep defect with quantum effects.
+We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains to be seen whether the candidate can facilitate the isolated deep energy levels often associated with defects showing quantum compatible properties.
 
@@
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
-%In fact, the first transistors were made in germanium due to their appealing electrical properties, but silicon took over as the material of choice for microelectronics due to the outstanding quality of silicon dioxide.
-%, which allowed the fabrication and integration of increasingly smaller transistors \cite{Scappucci2020, Pillarisetty2011}. 
-Ge has the highest hole mobility of semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization  \cite{Scappucci2020}.
-Furthermore, like SiC, Ge can take advantage of the mature large-scale fabrication of silicon due to their similar properties.
+Ge has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
+Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
 Similar considerations could be made for the case of GeC. 
-Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalent material having a band gap of $1.8$~eV. 
-Interestingly, as SiC is widely known as highly suitable host material for QT compatible defects, we encourage further research on GeC due to its comparable properties with SiC.
+Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
+Consequently, as SiC is widely known as highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
 
 The compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures.
-The indirect band gaps of the different structures are calculated at $1.46$~eV and $1.1$~eV, respectively, as reported in the MP database.
-They are both nonmagnetic and share several properties with the entries mentioned above; including ...
+The indirect band gaps of the different structures are calculated at $1.5$~eV and $1.1$~eV, respectively, as reported in the MP database.
+Both configurations of PB are nonmagnetic and share several properties with the entries mentioned above; including ...
 The compound is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
@@
 The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
-InP is reported in the Materials Project to have a direct band gap of $0.51$~eV, and is considered as one of the most promising candidates
-to compete with 
+InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with
 Cd- or Pb- based QDs for, e.g., display and lighting applications \cite{Zhang2020a, Won2019}. 
+We note the possibility of using InP-based quantum dots for QT application.
 
@@
 Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above the suitability limit. 
-
 The work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020} suggests a list of $541$ viable hosts after the data mining procedure.  
-Of these, we find only a single material present in our list of $66$ candidates (see the Supplementary Material at \cite{supplementary}).
+Among these these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the dataset resulting from the intuitive approach (see the Supplementary Material at \cite{supplementary}).
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
-Its band gap is $1.98$~eV in the MP database with the experimental value being $5.6$~eV  \cite{SaumGeorge1959}.
+Its band gap is $2.0$~eV in the MP database with the experimental value being reported as much larger at $5.6$~eV  \cite{SaumGeorge1959}.
 MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by the of Ref.~\cite{Ferrenti2020}.
-We believe that these criteria favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
+We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
 %\oliver{Maybe also see if other compounds that were present in training set are present in their 541 hosts. }
-
-%Supplementary information: List displaying the 66 predicted candidates that all models in the intuitive approach agreed on with more than 75\% probability. %appendix/listof66materials
 
@@
 Out of the three approaches, we find that the augmented Ferrenti approach is the least restricted approach and admits the most entries.
-The Ferrenti approach also admits a large number of entries, but is otherwise not very different from the augmented version.
+The Ferrenti approach also admits a large number of materials into the training set, but the resulting data is otherwise not very different from the augmented version.
 Importantly, by applying the four ML methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
 Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
-Manual verification through a literature survey will often not be available, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
-It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but less compared to that of the other two approaches.
+It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but to a lesser extent as compared to the other two approaches.
 Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
-%We believe there are three reasons for this.  
-It is known that the GGA functional Materials Project applies is known to underestimate the band gap of many semiconductors. 
-%underestimating the band gap severely, and therefore there is a chance that the models consider the band gap as noise and not useful information. 
+Firstly, as mentioned above, it is known that the PBE functional that the Materials Project applies is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
 It is therefore possible that the band gap is not considered an important parameter by the ML methods. 
-%Understanding the motivation behind the classification of the models will be an important step towards understanding ... 
 Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
-Thus, one can argue that the ML methods find other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
+Thus, one can argue that the ML methods are finding  other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
+\textbf{In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
+Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
+However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive)  through to the predictions indicates that at least some of the intended parameters are being recognized as important.
+Among the three approaches to data mining we find that the intuitive one conforms to expectation most closely. }
 
-We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the probability cut-off is set to [X]) were also selected by all ML methods in the augmented Ferrenti approach.
-%Of the $214$ suitable candidates predicted by all models in the intuitive approach, we find $119$ of them also predicted as suitable by all models in the augmented Ferrenti approach. 
+\textbf{I am missing a discussion, here or below, on the different ML methods and their different results.
+Which of the four algorithms is best or makes the most sense?
+Please compare either here, or for each of the approaches in the Predictions sections.}
+
+We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the probability cut-off is set to $50 \ \%$) were also selected by all ML methods in the augmented Ferrenti approach.
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding methods agree on a $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
-\textbf{The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a probability $> X \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
+All approaches and their corresponding methods agree on a total of $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+\textbf{The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a probability $> 50 \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
 
 \section*{Discussion} 
-% Shorter section, includes summary, concluding remarks and is quite heavy on outlook.
+We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials.
+Furthermore, three approaches to data mining for QT applications were developed; the Ferrenti, augmented Ferrenti and augmented approaches.
+Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision tree, random forest and gradient boost).
 
-%\oliver{The following paragraphs are "disclaimers" where we list possible pitfalls and weaknesses of this experiment.
-Could also be incorporated in the discussion instead?} MB I moved it up to data mining
+We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was overly broad with a lack of clear distinction between the materials labeled suitable and unsuitable for QT in the two training sets.
+The stringent restrictions set for the intuitive approach on the other hand proved more suitable basing on the much clearer distinction between suitable and unsuitable candidates.
 
-%SHORT SUMMARY FIRST HERE.
+Notably, our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
+\textbf{This manifests in the ML predictions as ...} 
+Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with ideal conditions to divine physics based trends.
 
-Motivated by our findings, we believe that further computational, experimental, or theoretical verification after a prediction of a possible promising material remains an important step in this work.
-This step is part of the workflow for novel materials discovery, which is visualized in Fig.~\ref{fig:ht-workflow}.
-Nevertheless, we have provided an exploratory analysis for the discovery of novel materials to be used in QT.
-Considering the number of materials predicted as suitable candidates by our machine learning methods and approaches, we hope it encourages further studies and identification of possible new material hosts.
-
-We find that including toxic materials etc in the training set is vital for reliable predictions.
-They can then later be excluded when planning experiments, but the practical considerations should be saved for last and not included in the initial criteria.
+In short, the findings presented herein firmly establish that material informatics via data mining to machine learning predictions is a both viable and important route to new discoveries in important fields.
+Herein, we focus on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
+Two main routes can be followed to exploit the results.
+One aspect is the pursuit of experimental verification of quantum technology compatible effect in the materials predicted as suitable by the four ML methods.
+Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest.
+Thus can new discoveries in the field of quantum technologies be made.
 
 \section*{Methods}
-%Should be rather short. Details can be included in a Supplementary Material.
 
-\subsection*{Information Flow}
-
-\subsection*{Databases} %Sebastian and Oliver 
+\subsection*{Databases} 
 The Materials Project \cite{Jain2013, Jain2018} is an open-source project based on the Vienna Ab Initio Package (VASP) \cite{Kresse1996}.
@@
 
-The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than 600.000 materials.
+The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than $600.000$  materials.
 The calculations are performed with the VASP software whereas the electron exchange and correlation are described with the PBE functional.
@@
 
-JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly 40.000 3D materials using the vdW-DF-OptB88 functional \cite{Thonhauser2007, Klimes2011}.
-Structures included in the database are originally taken from the Materials Project, and then re-optimized using the OPT-functional.
-Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap of each structure \cite{Choudhary2018a}.
+JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly $40.000$ 3D materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
+Structures included in the database are originally taken from the Materials Project, and then re-optimized using the OPT functional.
+Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
 
@@
 
-AFLOW-ML \cite{Isayev2017} is an API that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which they denote as \textit{fragment descriptors}.
+AFLOW-ML \cite{Isayev2017} is an API that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which are denoted as \textit{fragment descriptors}.
 Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap width.
@@
 
-Matminer \cite{Ward2018} is an open-source toolkit for material analysis written in Python.
+\subsection*{Material Informatics}  
+Matminer \cite{Ward2018} is an open source toolkit for material analysis written in Python.
 Matminer provides modules to extract information from a wide variety of databases.
 Additionally, they provide the tools to construct possibly thousands of features from calculations based on a material's composition, structure and electronic properties from DFT calculations, and have frameworks for visualization and automatic machine learning.
-
-\subsection*{Material Informatics}  
-Screening and workflow and approaches. Technicalities of featurization if necessary.
+The features selected for featurization herein are summarized in the Supplementary Material at \cite{supplementary}.
 
@@
 Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
-Gradient boosting implemented through the  XGBoost library \cite{xgboost2016}, is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
+Gradient boosting implemented through the  XGBoost library \cite{xgboost2016} is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
 
 \section*{Data availability} 
-%We can put something else, standard text 
-%The data that support the plots within this paper and other findings of this study are available from the corresponding authors upon reasonable request.
-[Marianne: I assume you want to add the Github link here?]
-
-The data sets that support the findings of this study are available from the corresponding author, and the data sets used in our  machine learning studies are available online at [Github link].
+The data sets that support the findings of this study are available online at DOI: 10.5281/zenodo.4633959.
 
 \section*{Code availability} 
-%The codes developed in this study are available from the authors upon reasonable request. [Marianne: I assume you want to add the Github link here?] 
-The codes employed to develop the machine learning results are available online at https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts (DOI: 10.5281/zenodo.4633959 - Update with new release later).
-%This DOI refers to an release of a Github Repository.
+The codes employed to develop the machine learning results are available online at 
+%https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts 
+DOI: 10.5281/zenodo.4633959. 
+%Update with new release later).
 
-\bibliography{apssamp}% Produces the bibliography via BibTeX.
+\bibliography{apssamp}
 

### 2021-12-15 paper.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new.png}
+    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
     \caption{Schematic of an example workflow in material informatics: results from theory, experiment and computation are fed into material databases.
@@
 The information stream in this work can be regarded as many modular parts connected in logical pieces.
-The initial step for gathering material data and building features is visualized by the the flowchart in Figure~\ref{fig:flowchart-makedata}.
+The initial step for gathering material data and building features is visualized by the the flowchart in Figure~\ref{fig:flowchart}.
 Initially, we start by extracting all entries in
@@
 
-\input{figures/tikz-plots/flow-chart-data-extraction.tex}
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.9\textwidth]{figures/flow_chart.png}
+    \caption{
+        The data flow of the main project, starting from an initial MP-query, and ending with a featurized dataset
+        with entries from several other databases. To limit the memory and computational usage, the data is
+        partitioned into smaller subsets where the respective pymatgen objects are obtained through a query to be used in
+        the following featurization steps. This process is repeated iteratively until all the data has been featurized.
+        Abbreviations used are Materials Project (MP), density of states (DOS) and electronic band structure (band).
+    }
+    \label{fig:flowchart}
+\end{figure}
 
-\input{figures/tikz-plots/flow-chart-featurization.tex}
+% \input{figures/tikz-plots/flow-chart-data-extraction.tex}
+
+% \input{figures/tikz-plots/flow-chart-featurization.tex}
 
@@
 The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project.
-A schematic describing the  featurization process in Matminer is shown in Figure~\ref{fig:flowchart-featurization} 
+A schematic describing the  featurization process in Matminer is shown as a step in Figure~\ref{fig:flowchart} 
 and focus on a material's composition, structure, atomic sites, density of states and band structure. 
@@
     \end{subfigure}
-    \vspace*{-95mm}
+    %\vspace*{10mm}
     \caption{Parallel coordinate plots for the different approaches.
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v2.pdf}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v2.pdf}
     \end{subfigure}
-    \vspace*{-95mm}
+    %\vspace*{-95mm}
     \caption{Two-dimensional scatter plots for the three different approaches.

### 2021-12-16 paper.tex
Updates from Overleaf

@@
 All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
-All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>XX \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>50 \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
 
@@
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
-        \item exclude transition metal elements with unpaired electrons like Ru, Os, Fe or Ni because of their paramagnetism.
+        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism.
+Ru and Os are also removed because they only exist in the data as complex cluster structures.
     \end{itemize}
@@
 
-We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database that crystallize in polar space groups, are calculated 
-to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional.
+We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional.
 The resulting complete data set contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
@@
     \begin{itemize}
-        \item contain elements where more than half have a natural abundance of zero spin isotopes, except Al, P, Ga, As, B and N, 
+        \item contain elements where more than half have a natural abundance of zero spin isotopes, including Al, P, Ga, As, B and N, 
         \item crystallize in non-polar space groups,
@@
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach. The result is a somewhat unbalanced data set, with up to $75 \ \%$ of the 
-materials found in the suitable group. However, the data set is $78 \ \%$ larger than for the Ferrenti approach.
+For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach.
+The result is a somewhat unbalanced data set, with up to $75 \ \%$ of the materials found in the suitable group.
+However, the data set is $78 \ \%$ larger than for the Ferrenti approach.
 
@@
 All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with the probability similar to a coin flip.
-If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on around $3000$ suitable candidates. 
+If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on $1784$ suitable candidates. 
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the training set. 
@@
 
+\begin{figure}[h] %!tbp
+    \centering
+    \begin{subfigure}{1\textwidth}
+        \centering
+        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
+        \input{figures/histograms/summary-01-02-histogram-.tex}
+    \end{subfigure}%
+
+    \begin{subfigure}{1\textwidth}
+        \centering
+        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
+        \input{figures/histograms/summary-03-histogram-.tex}
+    \end{subfigure}
+    \caption{Histograms of predicted materials as a function of band gaps, where all models in an approach agree with at least the probability of $50\%$.
+The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}
+    \label{fig:histogram}
+\end{figure}
+
 \subsubsection*{Comparing the approaches}
+
+\begin{table}[b]
+    \centering 
+    \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
+A probability of $50 \ \%$ represents the confidence of a coin flip, while $100 \ \%$ is a fully confident prediction.}
+    \begin{tabular}{c|c|c|c}
+      & $50 \ \%$ & $75 \ \%$ & $85 \ \%$ \\
+     \hline
+     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
+     Augmented Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
+     Intuitive approach & $214$ & $66$ & $9$ \\
+     \hline
+     All approaches together & $47$ & $6$ & 0 \\
+    \end{tabular}
+    \label{tab:probabilites}
+\end{table}
 

### 2021-12-16 supplementary.tex
Updates from Overleaf

@@
 \title{Supplementary Material \\ 
-Predicting Solid State Qubit Candidates}
+%Predicting Solid State Qubit Candidates}
+Predicting Solid State Material Platforms for Quantum Technologies}
 
@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+\affiliation{Sopra Steria, N-0185 Oslo, Norway}
 
@@
 \subsection*{Optimization of machine learning models}
-Morten/Oliver please add details.
 
@@
 Note that materials can appear several times  on  the  list due  to  different  structures of the same composition.
-The  list  contains five elementary (unary), 46  binary and  15 ternary compounds.
+The  list  contains $5$ elementary (unary), $46$  binary and  $15$ ternary compounds.
 
 \input{appendix/tablesof66materials.tex}
+
+Still missing.
 

### 2021-12-17 paper.tex
Updates from Overleaf

@@
 However, scouring these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using materials informatics and machine learning methods.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using materials informatics \cite{rickman2019} and machine learning methods.
 
@@
 We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set.
-The restrictions set in the intuitive approach, on the other hand, which relies exclusively on findings from the literature, proved more suitable.
+The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, proved on the other hand more suitable.
 All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
@@
     \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
-    \caption{Schematic of an example workflow in material informatics: results from theory, experiment and computation are fed into material databases.
+    \caption{Schematic of an example workflow in material informatics: results from theory, experiment and computation are fed into material databases (arrow pointing to the center).
 A cycle involving material screening, machine learning and predictions leads to knowledge gain and ultimately applications in fields such as clean energy and quantum technology.
@@
 
-Several platforms are available for the development of quantum technologies (QT) but the materials and fabrication technologies are less mature than those for, e.g., classical computers and sensors. 
+Several platforms are available for the development of quantum technologies (QT), but the materials and fabrication technologies are less mature than those for, e.g., classical computers and sensors. 
 An important concern in this context is that of scalability. 
@@
 So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
-The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to out-compete diamond in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
+The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to outcompete diamond in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
 However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
-Importantly, we are lacking a complete understanding of the requirements for a material to manifest quantum compatible properties,  
+Furthermore, we lack a complete understanding of the requirements for a material to manifest quantum compatible properties,  
 and the selection of known quantum compatible semiconductor host materials is slim.
@@
 The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for 
-a better understanding of how the QT compatible materials properties manifest. 
+a better and more systematic understanding of how the QT compatible materials properties manifest. 
 In this context, a framework for dedicated materials search and analysis is needed.
+
 The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
-The fourth paradigm instead introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.
-Instead of searching through a host of signals for the one that matches our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
+Instead, the fourth paradigm  introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.
+Rather than searching through a host of signals for those that match our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing materials properties for a wide range of different systems.
-In this work, the data in question is provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
+In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
 Combined with machine learning methods we provide a path towards precise classification of qubit candidates.
@@
 In this work we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
-The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical or experimental data is available.
-The method that was developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
-Matminer \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important feature of our work is the database building and development of the training sets for machine learning methods.
+The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical and/or experimental data are available.
+
+The approach we have developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+The Python library for data mining Matminer \cite{Ward2018} was then used for material analysis to featurize the extracted data.
+An important aspect of our work is the database building and pertinent development of the training sets for machine learning methods.
 We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020}  \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the intuitive approach}.
@@
 The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set.
-This more restricted approach proved more suitable than the other two and yielded $214$ predicted candidates (to a probability of $>50 \ \%$) with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
+These training sets where then analyzed with the above mentioned machine learning methods.
+This approach proved more suitable than the other two and yielded $214$ predicted candidates (to a probability of $>50 \ \%$) with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
 
@@
 
+%MHJ what do we mean with logical pieces?
 The information stream in this work can be regarded as many modular parts connected in logical pieces.
-The initial step for gathering material data and building features is visualized by the the flowchart in Figure~\ref{fig:flowchart}.
+The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}.
 Initially, we start by extracting all entries in
-the Materials Project (MP) that matches a specific query. 
-The MP database contains ground state properties of different materials that are calculated using density functional theory (DFT) as implemented in the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and using the The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
+the Materials Project (MP) that match a specific query. 
+The MP database contains ground state properties of different materials that are calculated using density functional theory (DFT).
+The DFT simulations are effectively implemented using the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and the  Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
 
@@
         The data flow of the main project, starting from an initial MP-query, and ending with a featurized dataset
-        with entries from several other databases. To limit the memory and computational usage, the data is
-        partitioned into smaller subsets where the respective pymatgen objects are obtained through a query to be used in
-        the following featurization steps. This process is repeated iteratively until all the data has been featurized.
+        with entries from several other databases. To limit the memory and computational usage, the data are
+        partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in
+        the following featurization steps. This process is repeated iteratively until all the data have been featurized.
         Abbreviations used are Materials Project (MP), density of states (DOS) and electronic band structure (band).
@@
 
-Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
+Before applying any machine learning algorithm, the data were transformed into a numerical representation that reflects the relationship between the input and output data.
 This transformation is known as generating descriptors
@@
 \subsubsection*{The Ferrenti approach}
-The first approach to defining a training set is based on the criteria from the paper by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+The first approach to defining a training set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project.
-In this framework, we label \textbf{suitable} candidates by the following steps.
+In this framework, we label \textbf{suitable} candidates by the following steps:
+%MHJ how do we cite the  ICSD data? No ref as of now
 \begin{enumerate}
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database, and
+        \item are present in the ICSD database (the world's largest database for completely identified inorganic crystal structures), and
         \item are calculated to be nonmagnetic. 
@@
 
-We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional.
+We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database %MHJ need ref here
+that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional, as discussed above.
 The resulting complete data set contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
@@
 Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
-Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
+Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of total spin zero isotopes.
 
 The following steps constitute the process of choosing \textbf{suitable} candidates 
-in the \emph{augmented Ferrenti approach}. 
+in the \emph{augmented Ferrenti approach}:
 \begin{enumerate}
@@
 After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
-These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
+These $12$ entries are calculated to be thermodynamically
+unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
 We include all of the $202$ structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
@@
 Complex structures (eg.
-C$_{28}$, C$_{48}$, C$_{60}$) were moved to the test set.
+C$_{28}$, C$_{48}$, C$_{60}$) were moved to the test set in our machine learning studies, see discussion below.
 For SiC, we admitted all entries, which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
@@
 
-The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010}  identified them as potentially promising candidates due to suitable material properties.
+The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedral coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010}  identified them as potentially promising candidates due to suitable material properties.
 %acceptable properties defined in requirements (H1-H4) in \autoref{ssec:qubit-material-host-requirements}. 
-We note that only tetrahedrally coordinated structures of the given formulas were present after applying the band gap restriction of $0.5$~eV.
+We note that only tetrahedral coordinated structures of the given formulas were present after applying the band gap restriction of $0.5$~eV.
 
@@
 Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the intuitive approach to provide an even narrower prediction space.
-Here, one should keep in mind that ...
+%Here, one should keep in mind that ...
 
@@
 
-To visualize the complexity of the training sets, we have found the two largest eigenvalues of the covariance matrix of the initial data from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
+To visualize the complexity of the training sets, we have found the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
 The resulting scatter plots are found in Figure~\ref{fig:2dscatterplotpca}.
@@
 Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are largely overlapping.
-The logic behind categorizing materials in the two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca}.
+The logic behind categorizing materials in  two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca}.
 Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
 %Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
-Therefore, we can expect that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available data sets.
+We expect therefore that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available data sets.
 
@@
 Out of the three approaches, we find that the augmented Ferrenti approach is the least restricted approach and admits the most entries.
-The Ferrenti approach also admits a large number of materials into the training set, but the resulting data is otherwise not very different from the augmented version.
-Importantly, by applying the four ML methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
+The Ferrenti approach also admits a large number of materials into the training set, but the resulting data are otherwise not very different from the augmented version.
+Importantly, by applying the four machine learning methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
 Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
@@
 Notably, our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
-\textbf{This manifests in the ML predictions as ...} 
+% MHJ paragraph not concluded \textbf{This manifests in the ML predictions as ...} 
 Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with ideal conditions to divine physics based trends.
@@
 
-JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly $40.000$ 3D materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
-Structures included in the database are originally taken from the Materials Project, and then re-optimized using the OPT functional.
+JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly $40.000$ three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
+Structures included in the database are originally taken from the Materials
+%mhj: ref to materials project is missing
+Project, and then re-optimized using the OPT functional.
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
@@
 
-AFLOW-ML \cite{Isayev2017} is an API that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which are denoted as \textit{fragment descriptors}.
+AFLOW-ML \cite{Isayev2017} is an application programming interface (API) that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which are denoted as \textit{fragment descriptors}.
 Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap width.
@@
 Additionally, they provide the tools to construct possibly thousands of features from calculations based on a material's composition, structure and electronic properties from DFT calculations, and have frameworks for visualization and automatic machine learning.
+Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}.
 The features selected for featurization herein are summarized in the Supplementary Material at \cite{supplementary}.

### 2021-12-17 paper.tex
Updates from Overleaf

@@
 
+In summary, using various
+data extraction tools for a number of materials science databases, we have obtained databases consisting of over 25.000 materials.
+The information from the databases has then been converted into nearly 5000 physics-informed features.
+After these steps with fine-tuning and selection of entries  for our data sets we are now ready to apply machine learning methods in order to classify materials as potential candidates for quantum technologies.
+
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology}

### 2021-12-17 paper.tex
Updates from Overleaf

@@
 \usepackage{color}
-\usepackage{caption}
+% \usepackage{caption}
 \usepackage{subcaption}
@@
 \usepackage{hyperref} 
-\usepackage{longtable}
+% \usepackage{longtable}
 
@@
 Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}.
-%Rename intuitive approach! To what? 
+%Rename insightful approach! To what? 
 %Options include stringent, strict, cherry-picked, informed and intuitive. 
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database (the world's largest database for completely identified inorganic crystal structures), and
+        \item are present in the ICSD database~\cite{Allen1987} (the world's largest database for completely identified inorganic crystal structures), and
         \item are calculated to be nonmagnetic. 
@@
 
-\begin{figure}[h] %!tbp
+\begin{figure}%[h] %!tbp
     \centering
@@
 \section*{Data availability} 
-The data sets that support the findings of this study are available online at DOI: 10.5281/zenodo.4633959.
+The data sets that support the findings of this study are available online at \cite{Ohebbi2021}.
 
@@
 %https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts 
-DOI: 10.5281/zenodo.4633959. 
+\cite{Ohebbi2021}.
 %Update with new release later).

### 2021-12-18 paper.tex
Updates from Overleaf

@@
 \usepackage{tikz,pgfplots}
+\usepgfplotslibrary{groupplots,dateplot}
+\usetikzlibrary{patterns,shapes.arrows}
 \usepackage{makecell}
@@
         %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
-        \input{figures/histograms/summary-01-02-histogram-.tex}
+        \input{figures/histograms/summary-01-02-03-histogram-bg.tex}
+        \subcaption[]{}
     \end{subfigure}%
@@
         %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
-        \input{figures/histograms/summary-03-histogram-.tex}
+        \input{figures/histograms/summary-01-02-03-histogram-cov.tex}
+        \subcaption[]{}
     \end{subfigure}
-    \caption{Histograms of predicted materials as a function of band gaps, where all models in an approach agree with at least the probability of $50\%$.
+
+    \begin{subfigure}{1\textwidth}
+        \centering
+        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
+        \input{figures/histograms/summary-01-02-03-histogram-ionic.tex}
+        \subcaption[]{}
+    \end{subfigure}
+
+    \caption{Histograms of predicted suitable materials as a function of (a) PBE-calculated band gap from Materials Project, (b) covalent range (Cov range) and (c) maximum ionic character (Ionic char).
 The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}

### 2021-12-19 paper.tex
Updates from Overleaf

@@
 The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project.
-A schematic describing the  featurization process in Matminer is shown as a step in Figure~\ref{fig:flowchart} 
+
+%\textbf{[Describe it and say something about which features we choose.]}
+To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}, which were used to generate a supervised mcahine learning framework called the MODnet.
+Their implementation provides featurization for a material's composition, structure and atomic sites.
+However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure, therefore, we extend their implementation to facilitate such featurizations.
+A schematic figure visualizing the featurization process in Matminer is shown in Figure~\ref{fig:flowchart}
 and focus on a material's composition, structure, atomic sites, density of states and band structure. 
-%\textbf{[Describe it and say something about which features we choose.]}  
 The 39 features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
-The selection of features was kept rather wide as we do not precisely know which features best describe a suitable  host material.
+The selection of features was kept rather wide as we do not precisely know which features best describe a solid state material platform for quantum technology.
 
@@
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
+Data extracted from Materials Project was done
 

### 2021-12-21 paper.tex
Updates from Overleaf

--- 2021-12-18 paper.tex
@@
 
+\author{{\O}yvind Sigmundson Sch{\o}yen}
+\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+
 \author{Sebastian G. Winther-Larsen}
@@
 
-\author{{\O}yvind Sigmundson Sch{\o}yen}
-\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+\author{Lasse Vines}
+\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
-
-\author{Lasse Vines}
-\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
@@
 However, scouring these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using materials informatics \cite{rickman2019} and machine learning methods.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics %\cite{rickman2019}
+and machine learning methods.
 
@@
 The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, proved on the other hand more suitable.
-All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials to a probability of $>50 \ \%$. 
-All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates (to a probability of $>50 \ \%$) of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
+All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.   
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
+of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
 
@@
 
-The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for 
-a better and more systematic understanding of how the QT compatible materials properties manifest. 
+The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of how the QT compatible materials properties manifest.
 In this context, a framework for dedicated materials search and analysis is needed.
@@
 These training sets where then analyzed with the above mentioned machine learning methods.
-This approach proved more suitable than the other two and yielded $214$ predicted candidates (to a probability of $>50 \ \%$) with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
+This approach proved more suitable than the other two and yielded $214$ predicted candidates
+%(to a $0.5$ cut-off)  
+with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs.
 
@@
 
-%MHJ what do we mean with logical pieces?
 The information stream in this work can be regarded as many modular parts connected in logical pieces.
 The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}.
-Initially, we start by extracting all entries in
-the Materials Project (MP) that match a specific query. 
+Initially, we start by extracting all entries in the Materials Project (MP) that match a specific query. 
 The MP database contains ground state properties of different materials that are calculated using density functional theory (DFT).
-The DFT simulations are effectively implemented using the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and the  Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional to calculate the electronic structure of the materials.
+The DFT simulations are effectively implemented using the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and the  Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996}  functional to calculate the electronic structure of the materials.
 
@@
     \includegraphics[width=0.9\textwidth]{figures/flow_chart.png}
-    \caption{
-        The data flow of the main project, starting from an initial MP-query, and ending with a featurized dataset
-        with entries from several other databases. To limit the memory and computational usage, the data are
+    \caption{The data flow of the main project, starting from an initial MP-query, and ending with a featurized dataset with entries from several other databases.
+To limit the memory and computational usage, the data are
     partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in
-        the following featurization steps. This process is repeated iteratively until all the data have been featurized.
+    the following featurization steps. This process is repeated iteratively until all the data has been featurized.
     Abbreviations used are Materials Project (MP), density of states (DOS) and electronic band structure (band).
@@
 
-% \input{figures/tikz-plots/flow-chart-data-extraction.tex}
-
-% \input{figures/tikz-plots/flow-chart-featurization.tex}
-
-Thereafter, we apply Matminer’s \cite{Ward2018}
-featurization tools to make thousands of features of the data.
-The conditions for this initial query are that the materials must derive from experimental data and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+The conditions for this initial query are that the materials must derive from 
+%experimental data 
+the ICSD database 
+and have a band gap wider than $0.1$~eV to exclude metallic compounds. 
+The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Levin2020}.  
 In a parallel step, entries that are deemed
@@
 
-Before applying any machine learning algorithm, the data were transformed into a numerical representation that reflects the relationship between the input and output data.
+Thereafter, we apply Matminer’s \cite{Ward2018} featurization tools to generate thousands of features from the data. 
+Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
 This transformation is known as generating descriptors
@@
 The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project. 
-A schematic describing the  featurization process in Matminer is shown as a step in Figure~\ref{fig:flowchart} 
-and focus on a material's composition, structure, atomic sites, density of states and band structure. 
-%\textbf{[Describe it and say something about which features we choose.]}  
-The 39 features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
-The selection of features was kept rather wide as we do not precisely know which features best describe a suitable  host material.
+%To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}, which were used to generate a supervised machine learning framework called the MODnet.
+Their implementation provides featurization for a material's composition, structure and atomic sites.
+However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure, therefore, we extend their implementation to facilitate such featurizations.
+A schematic visualizing the featurization process in Matminer is contained in Figure~\ref{fig:flowchart} 
+and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
+The $39$ features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
+The selection of features was kept rather wide as we do not precisely know which features best describe a solid state material platform for quantum technology.
 
@@
     \begin{itemize}
-        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in most stable forms,
+        \item exclude Th, U, Cd and Hg because they are radioactive and/or toxic in the most stable forms,
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
@@
 
-In the first approach we included criteria that were not physically motivated, but instead based on a purely practical perspective, like excluding toxic and radioactive elements.
+In the first approach we included criteria that were not physically motivated, but instead to some extent based on a  practical perspective, like excluding toxic and radioactive elements.
 Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the practicality of the material to be employed.
 Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
-Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of total spin zero isotopes.
+Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
 
@@
 We therefore name this scheme \emph{the intuitive approach}.
-Due to the concern of having a data set that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating  deep defects that potentially can exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of having a data set that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 Materials where properties like single-photon emission and spin manipulation are attributed to quantum dots (formed by self-assembly or lithographic structuring) will also be included in this context.
@@
     \item Make sure that the candidates are present in the ICSD database.  
-    \item Perform a manual screening for correct structures. 
+    \item Perform a manual screening for appropriate crystallographic structures. 
 \end{enumerate}
@@
 The table forms the basis for picking suitable candidates for the intuitive approach. 
-The properties being studied arise from mechanisms related to, e.g., point defects, excitons, and both self-assembled and lithographically structures quantum dots. 
-Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects still remains. 
+The properties being studied arise from mechanisms related to, e.g., point defects, excitons, and both self-assembled and lithographically structured quantum dots. 
+Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects is still lacking. 
 In the intuitive approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
@@
 After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
-These $12$ entries are calculated to be thermodynamically
-unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
+These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
 We include all of the $202$ structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
@@
 %% OH: Dirty details about suitable materials:
-Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
-%OH: Is discussed earlier in thesis but maybe neccessary to mention here? 
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
 For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
-Additionally, we find many two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
+Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
 We add these as suitable candidates.
@@
 
-The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedral coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010}  identified them as potentially promising candidates due to suitable material properties.
-%acceptable properties defined in requirements (H1-H4) in \autoref{ssec:qubit-material-host-requirements}. 
-We note that only tetrahedral coordinated structures of the given formulas were present after applying the band gap restriction of $0.5$~eV.
+The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
+We note that only tetrahedrally coordinated structures of the given formulas were present after imposing the band gap restriction of $0.5$~eV.
 
-The suitable candidates in the intuitive approach contain only compounds that are either elementary (unary) or binary.
+The candidates labeled as suitable in the intuitive approach contain only compounds that are either elementary (unary) or binary.
 We do not want to discriminate based on the number of elements in a compound, therefore we remove the feature that describes the number of elements in a compound.
 After the three stages, a total of $187$ entries were labeled as suitable candidates.
-See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the intuitive approach.
+%See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the intuitive approach.
 
@@
 \subsubsection*{Comparing the approaches}
-The three different approached to data mining place a particular emphasis on each of their particular goals.
-The Ferrenti approach depends on choosing only elements with spin zero isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
+The three different approaches to data mining place a particular emphasis on each of their specific goals.
+The Ferrenti approach relies on choosing only elements with spin zero isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
 Thus, the first approach targets a more narrow prediction space than the second approach does.
@@
 The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-Moreover, all candidates that were labeled unsuitable exhibit polar space groups (follows from the definition of the data sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
+Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the data sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
 
@@
 The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups - contrarily to the two Ferrenti-based approaches.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller space in the case of the intuitive approach than for the two former ones.
+Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the intuitive approach than for the two former ones.
 Here, we can begin to deduce some trends, if the findings from the intuitive approach are taken as guidance.
@@
 This indicates that the intuitive approach may be capable of separating materials based on their underlying properties.
-Thus, devising a sound framework for the data mining process is paramount to obtain a suitable training set for the machine learning methods.
+Thus, devising a sound framework for the data mining process is paramount to obtaining a suitable training set for the machine learning methods.
 
@@
 In summary, using various
-data extraction tools for a number of materials science databases, we have obtained databases consisting of over 25.000 materials.
-The information from the databases has then been converted into nearly 5000 physics-informed features.
+data extraction tools for a number of materials science databases, we have obtained databases consisting of over $25.000$ materials.
+The information from the databases has then been converted into nearly $5000$ physics-informed features.
 After these steps with fine-tuning and selection of entries for our data sets we are now ready to apply machine learning methods in order to classify materials as potential candidates for quantum technologies.
@@
 In this section, we present representative results after applying machine learning methods to the datasets resulting from each of the three data mining approaches.
+
+Explain the distinction between and definitions of the test and training sets here.
 
@@
 From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates.
-All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with the probability similar to a coin flip.
-If we were to raise the minimum bar of a prediction to $70 \ \%$ instead of $50 \ \%$, the above ML algorithms would only agree on $1784$ suitable candidates. 
+All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum cut-off of a prediction to $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates. 
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the training set. 
@@
 %Be careful here - PBE is known for underestimating band gaps. 
-For example, the ML methods do not maintain the band gap restriction from the training set definition. 
-Ideally, we would expect that the ML methods would have probabilities lower than $50 \ \%$ for all materials with band gaps lower than $0.5$~eV, which would be expected behavior based on the training set, but this is not the case.
+For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
+Ideally, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated for a cut-off set to above $0.5$ after applying the ML algorithms.  
+Although this is expected behavior based on the training set, it is not the case. 
 We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein, 
@@
 \subsubsection*{The intuitive approach}
-The ML methods that were trained on the data set defined in the intuitive approach to data mining predict substantially fewer candidates as compared to the two other approaches. 
+The ML methods that were trained on the data set defined in the intuitive approach predict substantially fewer candidates as compared to the two other approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four ML methods agree on a total of $214$ suitable candidates to a probability above $50 \ \%$.
+All the four ML methods agree on a total of $214$ suitable candidates for a $0.5$ cut-off restriction.
 Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
@@
 
-Initially, we consider the materials that were classified as suitable with a probability of $85 \ \%$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+Initially, we consider the materials that were classified as suitable to a degree of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
 The compound BN (mp-$1639$) is already present in the training data as a suitable candidate, and therefore we believe the models recognize this as a suitable candidate with high probability.
@@
 The element S resides in the same group as Se, and the data shows that the two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.6$~eV, respectively, in the MP database.
-Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$~eV \cite{CelebiSerdar2007SaCo, BanerjeeR2000Eots}.
+Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}, while bulk CdSe has a slightly lower reported band gap of $2.4$~eV \cite{Qutub2012}.
 
-In the case of BC$_2$N we find two compositions with the same chemical formula, the orthorhombic coordinated (mp-$629458$) and the chalcopyrite structured (mp-$1008523$) BC$_2$N, where the first takes on a polar space group while the latter does not.
+In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the chalcopyrite structured (mp-$1008523$) BC$_2$N.
+The former takes on a polar space group while the latter does not.
 The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
 BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN.
-Both structures have, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
 It has similarly been predicted that the diamond-like structure of BC$_3$N can be a prominent spin qubit material host \cite{Wang2020SpinQB}.
-By creating a boron (B) vacancy one can obtain a nitrogen-vacancy center with similar properties to those found for the NV center in diamond.
+By creating a boron (B) vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N is not present in the MP database and therefore not included in our dataset.
+We note that BC$_3$N is not represented in the MP database and therefore not included in our dataset.
 
@@
 Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the data set than, e.g., the more covalent materials of Si, SiC and  diamond.
-It seems that ionic character alone is not an obstacle, but it is unknown at this time whether, if CuI in fact does have potential for hosting single-photon emitters and spin centers, these properties would result from deep level defects or nanostructuring.
+It seems that ionic character alone is not an obstacle if the prediction of CuI proves to be merited.
+It is unknown at this time whether an potential quantum compatible properties of CuI would originate from deep level defects or nanostructuring (quantum dots).
 Note that NaCl was not predicted as suitable for QT in the intuitive approach.
 
-Lowering the probability requirement from $85 \ \%$ to $75 \ \%$ for all models results in $66$ materials. 
+Lowering the requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials. 
 The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
@@
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$  \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains to be seen whether the candidate can facilitate the isolated deep energy levels often associated with defects showing quantum compatible properties.
+We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains to be seen whether the candidate can facilitate the isolated deep energy levels often associated with defects exhibiting quantum compatible properties.
 
-Among the $66$ materials that all models in the intuitive approach agreed on with more than $75 \ \%$ probability, we emphasize the presence of Ge, GeC, BP and InP.
+Among the $66$ materials that all models in the intuitive approach agreed on to above $0.75$, we emphasize the presence of Ge, GeC, BP and InP.
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
@@
 The indirect band gaps of the different structures are calculated at $1.5$~eV and $1.1$~eV,  respectively, as reported in the MP database.
-Both configurations of PB are nonmagnetic and share several properties with the entries mentioned above; including ...
+Both configurations of BP are nonmagnetic and share several properties with the entries mentioned above; including ...
 The compound is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
@@
 The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
-InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with
-Cd- or Pb- based QDs for, e.g., display and lighting applications \cite{Zhang2020a, Won2019}. 
-We note the possibility of using InP-based quantum dots for QT application.
+InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
+We underline the possibility of using InP-based quantum dots for QT application as well.
 
-It is worth to mention that all models agree on several oxides being potential candidates when the probability cut-off is set low enough (but still above $50 \ \%$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list defining the $66$ suitable candidates in the Supplementary Material.
+It is worth mentioning that all models agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list defining the $66$ suitable candidates ($0.75$ cut-off) in the Supplementary Material.
 Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
-Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above the suitability limit. 
-The work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020} suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the dataset resulting from the intuitive approach (see the Supplementary Material at \cite{supplementary}).
+Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above the suitability limit and could be an interesting future pathway for investigation.
+
+In comparison, the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020} suggests a list of $541$ viable hosts after the data mining procedure.  
+Among these these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the dataset resulting from the intuitive approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
 Its band gap is $2.0$~eV in the MP database with the experimental value being reported as much larger at $5.6$~eV  \cite{SaumGeorge1959}.
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by the of Ref.~\cite{Ferrenti2020}.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Ferrenti2020} Ref.~\cite{Ferrenti2020}.
 We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
@@
     \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
-A probability of $50 \ \%$ represents the confidence of a coin flip, while $100 \ \%$ is a fully confident prediction.}
+A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
     \begin{tabular}{c|c|c|c}
-      & $50 \ \%$ & $75 \ \%$ & $85 \ \%$ \\
+      & $0.50$ & $0.75$ & $0.85$ \\
      \hline
@@
 
+Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates for each of the three approaches as a function of ML model confidence when the four models in an approach agree.
+%A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.
 Out of the three approaches, we find that the augmented Ferrenti approach is the least restricted approach and admits the most entries.
@@
 Importantly, by applying the four machine learning methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
-Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approach is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
+Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approaches is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 Firstly, as mentioned above, it is known that the PBE functional that the Materials Project applies is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
-It is therefore possible that the band gap is not considered an important parameter by the ML methods. 
+It is therefore possible that the band gap is erroneously not considered an important parameter by the ML methods - or, we may be overestimating the importance of this criterion. 
 Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
 Thus, one can argue that the ML methods are finding other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
-\textbf{In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
+In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
 Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
 However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
-Among the three approaches to data mining we find that the intuitive one conforms to expectation most closely. }
+We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the augmented Ferrenti approach. 
+Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
+All approaches and their corresponding methods agree on a total of $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a $0.5$ cut-off can be found in the Supplementary Material at \cite{supplementary}.
 
@@
 Which of the four algorithms is best or makes the most sense?
-Please compare either here, or for each of the approaches in the Predictions sections.}
+Please compare either here, or for each of the approaches in the Predictions subsections.
+Data can go in Supplemental.}
 
-We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the probability cut-off is set to $50 \ \%$) were also selected by all ML methods in the augmented Ferrenti approach.
-Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding methods agree on a total of $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
-\textbf{The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a probability $> 50 \ \%$ can be found in the Supplementary Material at \cite{supplementary}.}
+Among the three approaches to data mining, we find that the materials predicted based on the training set defined in the intuitive approach conform to expectation most closely.
+Figure~\ref{fig:histogram} displays the number of predicted candidate materials as a function of (a) band gap, (b) covalent range and (c) ionic character.
+We observe ...
 
 \section*{Discussion} 
-We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials.
-Furthermore, three approaches to data mining for QT applications were developed; the Ferrenti, augmented Ferrenti and augmented approaches.
+We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25.000$ materials.
+Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach,  (ii) the augmented Ferrenti approach, and (iii) the intuitive approach.
 Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision tree, random forest and gradient boost).
@@
 We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was overly broad with a lack of clear distinction between the materials labeled suitable and unsuitable for QT in the two training sets.
-The stringent restrictions set for the intuitive approach on the other hand proved more suitable basing on the much clearer distinction between suitable and unsuitable candidates.
+The stringent restrictions set for the intuitive approach, on the other hand, proved more suitable basing on the much clearer distinction between suitable and unsuitable candidates.
 
@@
 % MHJ paragraph not concluded \textbf{This manifests in the ML predictions as ...} 
-Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with ideal conditions to divine physics based trends.
+Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with optimal conditions to divine physics based trends.
 
-In short, the findings presented herein firmly establish that material informatics via data mining to machine learning predictions is a both viable and important route to new discoveries in important fields.
+In short, the findings presented herein firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
 Herein, we focus on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
@@
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
+Data extraction from Materials Project was performed ...
 
@@
 Additionally, they provide the tools to construct possibly thousands of features from calculations based on a material's composition, structure and electronic properties from DFT calculations, and have frameworks for visualization and automatic machine learning.
-Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}.
+To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}, which was used to generate a supervised machine learning framework called the MODnet.
+The implementation by \citeauthor{Breuck2021} provides featurization for a material's composition, structure and atomic sites.
+However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure.
+Therefore, we extend their implementation to facilitate such featurizations.
 The features selected for featurization herein are summarized in the Supplementary Material at \cite{supplementary}.
+
+Pymatgen, a robust, open-source Python library for materials analysis \cite{pymatgen}, was also employed.
 
@@
 
-%\section*{Author contributions} 
-%Copied in from another paper 
-%S.-M.J.
-conceived the idea and developed the simulation model.
-T.H.L.
-performed computer simulation.
-S.Y.B.
-and S.D.H.
-fabricated devices.
-D.-W.S., S.L., H.W.C.
-and J.-W.J.
-supported measurement of device performances.
-Y.-H.S.
-and X.-B.F.
-synthesised QD materials.
-S.Z.
-and J.Y.
-supported experiments.
-C.S.
-and Y.K.
-supported computer simulation.
-L.G.O.
-and G.A.
-supported data analysis.
-J.M.K.
-guided this work.
-S.-M.J., T.H.L.
-and S.Y.B.
-contributed equally.
-All the authors contributed to the preparation of the manuscript.
+\section*{Author contributions}
+Add! 
+%M.I.K.
+and M.v.S.
+conceived the main theme of the work.
+S.A., D.P., and M.v.S.
+have carried out the calculations.
+All authors have contributed to the writing of the paper and the analysis of the data.
 
@@
 
+\section*{Additional information}
+Correspondence and requests for materials should be addressed to ?
+
 \end{document}

### 2021-12-21 supplementary.tex
Updates from Overleaf

@@
 
-\author{{\O}yvind Sigmundson Sch{\o}yen}
-\affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
+\author{Lasse Vines}
+\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
 \author{Morten Hjorth-Jensen}
-\affiliation{Facility for Rare Ion Beams and Department of Physics and Astronomy, Michigan State University, East Lansing, MI 48824, USA}
+\affiliation{Department of Physics and Astronomy and Facility for Rare Ion Beams, Michigan State University, East Lansing, MI 48824, USA}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
-
-\author{Lasse Vines}
-\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
@@
 \section*{Supplementary results}
-Table~\ref{tab:03-probability-candidates}  displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with more than $75 \ \%$ probability.
+Table~\ref{tab:03-probability-candidates} displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with a cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
@@
 
-Still missing.
+Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning models and all three approaches agreed upon.
+The list contains $8$ elemental, $29$ binary, and $10$ tertiary compounds.
+
+\input{appendix/tablesof47materials.tex}
 

### 2021-12-31 paper.tex
Updates from Overleaf

@@
 and have a band gap wider than $0.1$~eV to exclude metallic compounds. 
-The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Levin2020}.  
+The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.%
+%OH: corrected icsd citation to german one (different from nist)
 In a parallel step, entries that are deemed
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database~\cite{Allen1987} (the world's largest database for completely identified inorganic crystal structures), and
+        \item are present in the ICSD database~\cite{Allen1987,Zagorac2019} (the world's largest database for completely identified inorganic crystal structures), and
         \item are calculated to be nonmagnetic. 
@@
 
-We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database %MHJ need ref here
+We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} %MHJ need ref here
 that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional, as discussed above.
-The resulting complete data set contains materials where $56 \ \%$ are labeled as unsuitable and $44 \ \%$ as suitable for QT applications.
+The resulting complete data set contains $1581$ materials where %$56 \ \%$ 
+$35 \ \%$
+are labeled as unsuitable and 
+%$44 \ \%$
+$65 \ \%$
+as suitable for QT applications.
 
@@
 We observe ...
+%
 
@@
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
-Data extraction from Materials Project was performed ...
+Data extraction from Materials Project was performed in december of $2020$ for the Ferrenti and Augmented Ferrenti approach, while in march $2021$ for the intuitive approach.
+Therefore, the two former approaches includes $77$ more materials due to deprecated entries in the Materials Project database.
 
@@
 The $+U$ extension is included for several calculations considering specific elements \cite{Stevanovic2012}.
+Data extraction from OQMD was done in february of $2021$.
 
@@
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
+Data extraction from JARVIS-DFT was done in january of $2021$, were we utilized the version made available 30.04.2021 at \url{figshare.com}.
 
@@
 %with projector-augmented wave (PAW) potentials 
-to relax twice and optimize the ICSD-structure.
+to relax twice and optimize the ICSD-structure. Data-extraction was done in the period of january-february of $2021$.
 
@@
 The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
+This work utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
+We extract the crystallographic information file (CIF) of the crystals from Materials Project, and then use this as input to AFLOW-ML, which then returns an anticipated band gap.
+The process was done during january of $2021$.
 

### 2021-12-31 supplementary.tex
Updates from Overleaf

@@
 \usepackage{lipsum}
-\usepackage{subfig}
+%\usepackage{subfig}
 % \usepackage{braket}
@@
 \usepackage{longtable}
+\usepackage{subfigure}
+\usepackage{tikz,pgfplots}
+\usepgfplotslibrary{groupplots,dateplot}
+\usetikzlibrary{patterns,shapes.arrows}
 \sisetup{separate-uncertainty}
@@
 %\newcommand\ket[1]{\left \langle #1 \right |}
+\pgfplotsset{%samples=101,
+axis lines = left,
+every axis plot/.append style={line width=2pt},
+}
+
+\pgfplotsset{compat=1.17}
 
@@
 \subsection*{Optimization of machine learning models}
+\begin{figure}[ht!]
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/01-ferrenti-approach-176-LOG}
+    \caption{}
+    \label{fig:q1-LOG}
+  \end{subfigure}%
+    \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/01-ferrenti-approach-176-DT}
+    \caption{}
+    \label{fig:q1-DT}
+  \end{subfigure}
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/01-ferrenti-approach-176-RF.tex}
+    \caption{}
+    \label{fig:q1-RF}
+  \end{subfigure}%
+   \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/01-ferrenti-approach-176-GB.tex}
+    \caption{}
+    \label{fig:q1-GB}
+  \end{subfigure}
+  \caption{{Four figures displaying hyperparameter search for the Ferrenti approach.
+The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
+Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
+Precision, recall, and F1 scores are based on the test set.
+The number of principal components that explain the $95\%$ accumulated variance is $144$, while the optimal model is found using the F1-score.}}
+  \label{fig:01-pca}
+\end{figure}
 

### 2022-01-02 supplementary.tex
Updates from Overleaf

@@
 
-\usepackage{graphicx}% Include figure files
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{amssymb}
+\usepackage[top=4cm,bottom=4cm,left=2.8cm,right=3.75cm,asymmetric,twoside]{geometry}
+\usepackage{graphicx}
+\usepackage{fancyhdr}
+\usepackage{comment}
+\usepackage{tikzorbital}
+\usepackage{array} % center tables + 2 next lines
+\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
+\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
+\usepackage{multirow} % confusion matrix
+\newcommand\MyBox[2]{
+  \fbox{\lower0.75cm
+    \vbox to 2.0cm{\vfil
+      \hbox to 2.0cm{\hfil\parbox{1.4cm}{#1\\#2}\hfil}
+      \vfil}%
+  }%
+}
+\usepackage{grffile}
+\usepackage{epigraph} % quote
+\usepackage{wrapfig} %wrapping text to fig
+\usepackage{tikz} %draw figures
+
+\usepackage{subcaption} %subcaption
+\usepackage[font=small,labelfont=bf,width=0.9\textwidth]{caption}
+\captionsetup[table]{skip=10pt}
+\usepackage[T1]{fontenc}
+\usepackage[sc, osf]{mathpazo}
+\usepackage[euler-digits]{eulervm}
+\usepackage{booktabs}
+\usepackage{enumerate}
+\usepackage{commath}
+\usepackage{mathtools}
+\usepackage[utf8]{inputenc}
+\usepackage{pgfplots}
+\usepgfplotslibrary{groupplots,dateplot}
+\usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
+\pgfplotsset{compat=newest}
+
+\usepackage{sansmath}
+\tikzset{>=stealth,
+OptimumStyle/.style={align=center,anchor=east,rotate=90,font=\scriptsize}
+}
+\pgfplotsset{%samples=101,
+axis lines = left,
+every axis plot/.append style={line width=2pt},
+}
+% Include font for the identity operator
+\usepackage{dsfont}
+\usepackage[binary-units=true]{siunitx}
+\usepackage{makecell}
+\usepackage{longtable}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 \usepackage{lipsum}
-%\usepackage{subfig}
-% \usepackage{braket}
 \usepackage{siunitx}
 \usepackage{color}
-\usepackage{longtable}
-\usepackage{subfigure}
-\usepackage{tikz,pgfplots}
-\usepgfplotslibrary{groupplots,dateplot}
-\usetikzlibrary{patterns,shapes.arrows}
 \sisetup{separate-uncertainty}
-%\newcommand\abs[1]{\left|#1\right|}
-%\newcommand\bra[1]{\left| #1 \right \rangle}
-%\newcommand\ket[1]{\left \langle #1 \right |}
 \pgfplotsset{%samples=101,
@@
 }
-
-\pgfplotsset{compat=1.17}
 
@@
 \subsection*{Featurization}
-Table~\ref{table:featurizers} contains an overview of this work's chosen 39 features from matminer. The features were selected based on ...
+Table~\ref{table:featurizers} contains an overview of this work's chosen 39 features from matminer. The features were selected based on
+the work of
 
@@
 \subsection*{Optimization of machine learning models}
+
+In the evaluation of the approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
+Four different evaluation metrics are applied to each of the four algorithms for each approach.
+
+For random forest, gradient boost, and decision tree, we found that by adjusting most of the available parameters responded to severe overfitting.
+Therefore, most parameters are the default values defined by Scikit-learn.
+The only parameter that we found that could potentially improve the evaluation metric F$1$ was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$.
+For logistic regression, we chose to adjust the regularization strength with seven logarithmical adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
+
+When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95\%$ from the principal component analysis.
+Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totalling up to $30800$ individual models, just for logisitic regression for one approach.
+
+%Ferrenti 
+We visualize the grid search for the optimal number of principal components for the Ferrenti approach in figure \ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
+For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.
+
+In table \ref{tab:01-pc}, we find the precise measurements for each evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in \ref{fig:01-pca}.
+The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$.
+For random forest and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boost.
+We find the best performing model is logistic regression, but is dependent on a large amount of principal components.
+
+%Augmented ferrenti (to be continued)
+%Intuitive (to be continued)
+
+\begin{table}[!ht]
+\centering
+\caption{A table of the optimal number of principal components and the respective scores (standard deviation) for the Ferrenti approach, as visualized in the dash-dotted line in figure \ref{fig:01-pca}.}
+\label{tab:01-pc}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Model & PC & Mean test &  Mean precision & Mean recall & mean F1\\
+  \hline
+  LOG & $171$ & $0.98(0.012)$ & $0.98(0.011)$ & $0.99(0.007)$ & $0.99(0.007)$ \\
+  DT & $37$   & $0.77(0.034)$ & $0.84(0.034)$ & $0.85(0.044)$ & $0.84(0.022)$ \\
+  RF & $53$   & $0.87(0.027)$ & $0.88(0.022)$ & $0.98(0.010)$ & $0.93(0.014)$ \\
+  GB & $107$  & $0.92(0.016)$ & $0.92(0.015)$ & $0.98(0.010)$ & $0.95(0.009)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
 \begin{figure}[ht!]
+\begin{subfigure}[b]{1.0\textwidth}
+    \centering
+    \input{figures/optimizing-parameters/label.tex}
+  \end{subfigure}
+  \par\bigskip
   \begin{subfigure}[b]{0.5\textwidth}
@@
 
+\clearpage
+
 \section*{Supplementary results}

### 2022-01-03 paper.tex
Updates from Overleaf

@@
 All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
-We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set.
+%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set.
 The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, proved on the other hand more suitable.
+We find that the Ferrenti approach and the augmented Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
+The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, but provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
 All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
-of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
+of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for futher material explorations towards quantum technology.
 
@@
 So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
-The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are poised to outcompete diamond in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
+The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
 However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
@@
 We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020}  \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the intuitive approach}.
-We find that the former two methodologies base their data extraction protocols on practical considerations, such as experimental availability in specific forms or the toxicity of the materials, leading to few observable trends in the materials predicted by well-tested machine learning algorithms, such as logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
+We find that the former two methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set.
-These training sets where then analyzed with the above mentioned machine learning methods.
-This approach proved more suitable than the other two and yielded $214$ predicted candidates
+These training sets where then analyzed with the above mentioned machine learning methods, and yielded $214$ predicted candidates
 %(to a $0.5$ cut-off)  
@@
 
-The information stream in this work can be regarded as many modular parts connected in logical pieces.
+The information stream in this work can be regarded as many modular parts 
+%connected in logical pieces. 
+that are connected. 
 The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}. 
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database~\cite{Allen1987,Zagorac2019} (the world's largest database for completely identified inorganic crystal structures), and
+        \item are present in the ICSD database,  %\cite{Allen1987,Zagorac2019} 
+        %(the world's largest database for completely identified inorganic crystal structures), 
+        and
         \item are calculated to be nonmagnetic. 
@@
 Intriguingly, a much clearer separation is observed for the intuitive approach, where no restrictions were imposed in terms of specific characteristics for the materials, as compared to the two others.
-These observations constitute an important finding of the work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT.
+These observations constitute an important finding of our work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT.
 The manual approach for selecting suitable candidates based on experimental findings yields strong indications that a trend does exist and thus is possible to identify.
@@
 The information from the databases has then been converted into nearly $5000$ physics-informed features.
-After these steps with fine-tuning and selection of entries for our data sets we are now ready to apply machine learning methods in order to classify materials as potential candidates for quantum technologies.
+After these steps with fine-tuning and selection of entries for our data sets we are now ready to apply machine learning methods on the test set in order to classify materials as potential candidates for quantum technologies.
 
@@
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
-Its band gap is $2.0$~eV in the MP database with the experimental value being reported as much larger at $5.6$~eV  \cite{SaumGeorge1959}.
+Its band gap is $2.0$~eV in the MP database with the experimental value being reported as large as $5.6$~eV  \cite{SaumGeorge1959}.
 MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Ferrenti2020} Ref.~\cite{Ferrenti2020}.
@@
 Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
-However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
+%However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
+However, the large overlap of predicted materials between the three approaches (Ferrenti, augmented Ferrenti and intuitive) indicates that at least some of the intended parameters are being recognized as important.
 We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the augmented Ferrenti approach. 
@@
 
-We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was overly broad with a lack of clear distinction between the materials labeled suitable and unsuitable for QT in the two training sets.
+We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad with a lack of clear distinction between the materials labeled suitable and unsuitable for QT in the two training sets.
 The stringent restrictions set for the intuitive approach, on the other hand, proved more suitable basing on the much clearer distinction between suitable and unsuitable candidates.
@@
 AFLOW-ML \cite{Isayev2017} is an application programming interface (API) that uses machine learning to predict thermo-mechanical and electronic properties based on the chemical composition and atomic structure alone, which are denoted as \textit{fragment descriptors}.
-Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap width.
+Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap.
 The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.

### 2022-01-04 paper.tex
Updates from Overleaf

@@
 We find that the Ferrenti approach and the augmented Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, but provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
 All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.
@@
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
-Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as quantum cryptography and the quantum internet.  
-Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}, spurring further investigations into competitive quantum technology platforms.
+Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
+Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as quantum cryptography and the quantum internet, spurring further investigations into technologies based on quantum mechanics.
 
@@
 
-We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad with a lack of clear distinction between the materials labeled suitable and unsuitable for QT in the two training sets.
-The stringent restrictions set for the intuitive approach, on the other hand, proved more suitable basing on the much clearer distinction between suitable and unsuitable candidates.
+We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled suitable and unsuitable for QT in the two training sets.
+The stringent restrictions set for the intuitive approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
 

### 2022-01-04 supplementary.tex
Updates from Overleaf

@@
 The only parameter that we found that could potentially improve the evaluation metric F$1$ was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$.
-For logistic regression, we chose to adjust the regularization strength with seven logarithmical adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
+For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
 
-When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95\%$ from the principal component analysis.
-Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totalling up to $30800$ individual models, just for logisitic regression for one approach.
+When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
+Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models, just for logistic regression for one approach.
 
 %Ferrenti 
-We visualize the grid search for the optimal number of principal components for the Ferrenti approach in figure \ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
+We visualize the grid search for the optimal number of principal components for the Ferrenti approach in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
 For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.
 
-In table \ref{tab:01-pc}, we find the precise measurements for each evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in \ref{fig:01-pca}.
+In Table~\ref{tab:01-pc}, we find the precise measurements for each of the evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
 The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$.

### 2022-01-07 figures/feature-importance/01-ferrenti-approachDT-final.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.296093145959793,
ytick style={color=black},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.0602126647764764);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.110963188395912);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0240371193898026);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0221547131912102);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.246093145959793);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0188217883182872);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0105015974384699);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00699136294394965);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.00853041123767904);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.00934264373238672);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0201245026439328);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.00803736953390133);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0201541360551478);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0180446021881651);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0132118462234375);
\draw[draw=none,fill=color0] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0181046069828721);
\draw[draw=none,fill=color0] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0309174582001746);
\draw[draw=none,fill=color0] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0359878148351983);
\draw[draw=none,fill=color0] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0271294275084838);
\draw[draw=none,fill=color0] (axis cs:19.6,0) rectangle (axis cs:20.4,0.012494436624754);
\draw[draw=none,fill=color0] (axis cs:20.6,0) rectangle (axis cs:21.4,0.0167371542524648);
\draw[draw=none,fill=color0] (axis cs:21.6,0) rectangle (axis cs:22.4,0.0172798021408093);
\draw[draw=none,fill=color0] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00542141841736881);
\draw[draw=none,fill=color0] (axis cs:23.6,0) rectangle (axis cs:24.4,0.0402418644282019);
\draw[draw=none,fill=color0] (axis cs:24.6,0) rectangle (axis cs:25.4,0.0227346258367308);
\path [draw=color0, semithick]
(axis cs:1,5.12811391574566e-05)
--(axis cs:1,0.120374048413795);

\path [draw=color0, semithick]
(axis cs:2,0.0688908846055959)
--(axis cs:2,0.153035492186228);

\path [draw=color0, semithick]
(axis cs:3,0.000443281753072355)
--(axis cs:3,0.0476309570265328);

\path [draw=color0, semithick]
(axis cs:4,0.000463808547678048)
--(axis cs:4,0.0438456178347424);

\path [draw=color0, semithick]
(axis cs:5,0.201175759797789)
--(axis cs:5,0.291010532121796);

\path [draw=color0, semithick]
(axis cs:6,-0.00207540963664902)
--(axis cs:6,0.0397189862732235);

\path [draw=color0, semithick]
(axis cs:7,-0.000261197656391885)
--(axis cs:7,0.0212643925333317);

\path [draw=color0, semithick]
(axis cs:8,-0.00523656669530865)
--(axis cs:8,0.0192192925832079);

\path [draw=color0, semithick]
(axis cs:9,-0.00108881158485408)
--(axis cs:9,0.0181496340602122);

\path [draw=color0, semithick]
(axis cs:10,-0.00317148697566561)
--(axis cs:10,0.0218567744404391);

\path [draw=color0, semithick]
(axis cs:11,0.00759809291557517)
--(axis cs:11,0.0326509123722904);

\path [draw=color0, semithick]
(axis cs:12,-0.00126897867798911)
--(axis cs:12,0.0173437177457918);

\path [draw=color0, semithick]
(axis cs:13,0.00435547873601669)
--(axis cs:13,0.035952793374279);

\path [draw=color0, semithick]
(axis cs:14,-0.000431492489608061)
--(axis cs:14,0.0365206968659383);

\path [draw=color0, semithick]
(axis cs:15,-0.00810189470153616)
--(axis cs:15,0.0345255871484112);

\path [draw=color0, semithick]
(axis cs:16,-0.00758733165253984)
--(axis cs:16,0.0437965456182841);

\path [draw=color0, semithick]
(axis cs:17,-0.000304997596235309)
--(axis cs:17,0.0621399139965845);

\path [draw=color0, semithick]
(axis cs:18,0.00670250518936169)
--(axis cs:18,0.0652731244810349);

\path [draw=color0, semithick]
(axis cs:19,0.00234124172436161)
--(axis cs:19,0.0519176132926061);

\path [draw=color0, semithick]
(axis cs:20,-0.0107608268316967)
--(axis cs:20,0.0357497000812046);

\path [draw=color0, semithick]
(axis cs:21,-0.00616044853556576)
--(axis cs:21,0.0396347570404953);

\path [draw=color0, semithick]
(axis cs:22,-0.00878787812034752)
--(axis cs:22,0.0433474824019661);

\path [draw=color0, semithick]
(axis cs:23,-0.00371385025428554)
--(axis cs:23,0.0145566870890232);

\path [draw=color0, semithick]
(axis cs:24,-0.00489403909324856)
--(axis cs:24,0.0853777679496524);

\path [draw=color0, semithick]
(axis cs:25,-0.0140804363436156)
--(axis cs:25,0.0595496880170773);
\addlegendimage{semithick, color=color0};
\addlegendentry{Decision tree};
\addplot [semithick, color0, mark=-, mark size=0, mark options={solid}, only marks]
table {%
1 5.12811391574566e-05
2 0.0688908846055959
3 0.000443281753072355
4 0.000463808547678048
5 0.201175759797789
6 -0.00207540963664902
7 -0.000261197656391885
8 -0.00523656669530865
9 -0.00108881158485408
10 -0.00317148697566561
11 0.00759809291557517
12 -0.00126897867798911
13 0.00435547873601669
14 -0.000431492489608061
15 -0.00810189470153616
16 -0.00758733165253984
17 -0.000304997596235309
18 0.00670250518936169
19 0.00234124172436161
20 -0.0107608268316967
21 -0.00616044853556576
22 -0.00878787812034752
23 -0.00371385025428554
24 -0.00489403909324856
25 -0.0140804363436156
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.120374048413795
2 0.153035492186228
3 0.0476309570265328
4 0.0438456178347424
5 0.291010532121796
6 0.0397189862732235
7 0.0212643925333317
8 0.0192192925832079
9 0.0181496340602122
10 0.0218567744404391
11 0.0326509123722904
12 0.0173437177457918
13 0.035952793374279
14 0.0365206968659383
15 0.0345255871484112
16 0.0437965456182841
17 0.0621399139965845
18 0.0652731244810349
19 0.0519176132926061
20 0.0357497000812046
21 0.0396347570404953
22 0.0433474824019661
23 0.0145566870890232
24 0.0853777679496524
25 0.0595496880170773
};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/01-ferrenti-approachGB-final.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.0666666666666667,0.466666666666667,0.2}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.241504672452706,
ytick style={color=black},
yticklabels={,0, 0.1,0.2},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.0939219294354606);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.128717126999015);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0213938886864563);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.00888144685168664);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.191504672452706);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.00724897098092836);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.00450287540874152);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00389892865504545);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.00328938623970718);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.00607634168998537);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0075927359484662);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.00246964434307127);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0113273434472604);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0215526621032538);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,0.00889067969625317);
\draw[draw=none,fill=color0] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0112833024636162);
\draw[draw=none,fill=color0] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0331145663678211);
\draw[draw=none,fill=color0] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0265656605925389);
\draw[draw=none,fill=color0] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0412663962030667);
\draw[draw=none,fill=color0] (axis cs:19.6,0) rectangle (axis cs:20.4,0.00893277229511404);
\draw[draw=none,fill=color0] (axis cs:20.6,0) rectangle (axis cs:21.4,0.00638009737027819);
\draw[draw=none,fill=color0] (axis cs:21.6,0) rectangle (axis cs:22.4,0.0110083486001703);
\draw[draw=none,fill=color0] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00396903870317716);
\draw[draw=none,fill=color0] (axis cs:23.6,0) rectangle (axis cs:24.4,0.0182603050195842);
\draw[draw=none,fill=color0] (axis cs:24.6,0) rectangle (axis cs:25.4,0.0400563256690563);
\path [draw=color0, semithick]
(axis cs:1,0.0728244166732798)
--(axis cs:1,0.115019442197641);

\path [draw=color0, semithick]
(axis cs:2,0.102746647015722)
--(axis cs:2,0.154687606982308);

\path [draw=color0, semithick]
(axis cs:3,0.0096504157614985)
--(axis cs:3,0.0331373616114142);

\path [draw=color0, semithick]
(axis cs:4,0.00120429954877644)
--(axis cs:4,0.0165585941545968);

\path [draw=color0, semithick]
(axis cs:5,0.164674846558901)
--(axis cs:5,0.218334498346511);

\path [draw=color0, semithick]
(axis cs:6,0.00131865659765555)
--(axis cs:6,0.0131792853642012);

\path [draw=color0, semithick]
(axis cs:7,0.00089826602034204)
--(axis cs:7,0.008107484797141);

\path [draw=color0, semithick]
(axis cs:8,-0.000515167535189504)
--(axis cs:8,0.00831302484528041);

\path [draw=color0, semithick]
(axis cs:9,0.000577548695504199)
--(axis cs:9,0.00600122378391017);

\path [draw=color0, semithick]
(axis cs:10,-0.00123032392384619)
--(axis cs:10,0.0133830073038169);

\path [draw=color0, semithick]
(axis cs:11,0.00341822410793035)
--(axis cs:11,0.0117672477890021);

\path [draw=color0, semithick]
(axis cs:12,0.000427923119383559)
--(axis cs:12,0.00451136556675897);

\path [draw=color0, semithick]
(axis cs:13,-0.000894751232806041)
--(axis cs:13,0.0235494381273268);

\path [draw=color0, semithick]
(axis cs:14,-0.00534323462302397)
--(axis cs:14,0.0484485588295317);

\path [draw=color0, semithick]
(axis cs:15,-0.00580574316011168)
--(axis cs:15,0.023587102552618);

\path [draw=color0, semithick]
(axis cs:16,-0.0063295986999169)
--(axis cs:16,0.0288962036271493);

\path [draw=color0, semithick]
(axis cs:17,-0.000960237853350046)
--(axis cs:17,0.0671893705889922);

\path [draw=color0, semithick]
(axis cs:18,-0.00343303381845922)
--(axis cs:18,0.056564355003537);

\path [draw=color0, semithick]
(axis cs:19,0.00206699809958492)
--(axis cs:19,0.0804657943065485);

\path [draw=color0, semithick]
(axis cs:20,-0.00625580047143954)
--(axis cs:20,0.0241213450616676);

\path [draw=color0, semithick]
(axis cs:21,-0.00190515682114497)
--(axis cs:21,0.0146653515617014);

\path [draw=color0, semithick]
(axis cs:22,-0.00451438685233842)
--(axis cs:22,0.0265310840526791);

\path [draw=color0, semithick]
(axis cs:23,-0.000399848870586143)
--(axis cs:23,0.00833792627694046);

\path [draw=color0, semithick]
(axis cs:24,-0.0070765748506951)
--(axis cs:24,0.0435971848898635);

\path [draw=color0, semithick]
(axis cs:25,-0.00342720675075281)
--(axis cs:25,0.0835398580888655);
\addlegendimage{semithick, color=color0};
\addlegendentry{Gradient boost};
\addplot [semithick, color0, mark=-, mark size=0, mark options={solid}, only marks]
table {%
1 0.0728244166732798
2 0.102746647015722
3 0.0096504157614985
4 0.00120429954877644
5 0.164674846558901
6 0.00131865659765555
7 0.00089826602034204
8 -0.000515167535189504
9 0.000577548695504199
10 -0.00123032392384619
11 0.00341822410793035
12 0.000427923119383559
13 -0.000894751232806041
14 -0.00534323462302397
15 -0.00580574316011168
16 -0.0063295986999169
17 -0.000960237853350046
18 -0.00343303381845922
19 0.00206699809958492
20 -0.00625580047143954
21 -0.00190515682114497
22 -0.00451438685233842
23 -0.000399848870586143
24 -0.0070765748506951
25 -0.00342720675075281
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.115019442197641
2 0.154687606982308
3 0.0331373616114142
4 0.0165585941545968
5 0.218334498346511
6 0.0131792853642012
7 0.008107484797141
8 0.00831302484528041
9 0.00600122378391017
10 0.0133830073038169
11 0.0117672477890021
12 0.00451136556675897
13 0.0235494381273268
14 0.0484485588295317
15 0.023587102552618
16 0.0288962036271493
17 0.0671893705889922
18 0.056564355003537
19 0.0804657943065485
20 0.0241213450616676
21 0.0146653515617014
22 0.0265310840526791
23 0.00833792627694046
24 0.0435971848898635
25 0.0835398580888655
};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/01-ferrenti-approachLOG-final.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.533333333333333,0.8,0.933333333333333}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
xticklabels={,,},
ymin=-0.476544751038715, ymax=0.454074936965614,
ytick style={color=black},
yticklabels={-0.4,,0,,0.4},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,-0.123064253300487);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.254074936965614);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0637383003312674);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.010153582132699);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,-0.426544751038715);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0732655250272369);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0708059658830058);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0083798167350135);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0258456453297823);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0225188188581133);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,-0.00133413758881279);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,-0.00287012168215015);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,-0.131874778892413);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,-0.142790669765573);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,-0.0405779810634156);
\draw[draw=none,fill=color0] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0350731860669815);
\draw[draw=none,fill=color0] (axis cs:16.6,0) rectangle (axis cs:17.4,-0.0311000025985934);
\draw[draw=none,fill=color0] (axis cs:17.6,0) rectangle (axis cs:18.4,-0.14448078918333);
\draw[draw=none,fill=color0] (axis cs:18.6,0) rectangle (axis cs:19.4,0.033212744542326);
\draw[draw=none,fill=color0] (axis cs:19.6,0) rectangle (axis cs:20.4,-0.00593839297518309);
\draw[draw=none,fill=color0] (axis cs:20.6,0) rectangle (axis cs:21.4,-0.0387638090286288);
\draw[draw=none,fill=color0] (axis cs:21.6,0) rectangle (axis cs:22.4,-0.0546645306377975);
\draw[draw=none,fill=color0] (axis cs:22.6,0) rectangle (axis cs:23.4,-0.057269839782401);
\draw[draw=none,fill=color0] (axis cs:23.6,0) rectangle (axis cs:24.4,-0.0041084420499987);
\draw[draw=none,fill=color0] (axis cs:24.6,0) rectangle (axis cs:25.4,-0.0334022639069669);
\path [draw=color0, semithick]
(axis cs:1,-0.229417488366355)
--(axis cs:1,-0.0167110182346182);

\path [draw=color0, semithick]
(axis cs:2,0.23592009450898)
--(axis cs:2,0.272229779422249);

\path [draw=color0, semithick]
(axis cs:3,-0.0305441203965614)
--(axis cs:3,0.158020721059096);

\path [draw=color0, semithick]
(axis cs:4,-0.0595627687059507)
--(axis cs:4,0.0798699329713486);

\path [draw=color0, semithick]
(axis cs:5,-0.436113887749494)
--(axis cs:5,-0.416975614327935);

\path [draw=color0, semithick]
(axis cs:6,0.00255054819934573)
--(axis cs:6,0.143980501855128);

\path [draw=color0, semithick]
(axis cs:7,0.0465056999066113)
--(axis cs:7,0.0951062318594004);

\path [draw=color0, semithick]
(axis cs:8,-0.0409018572150964)
--(axis cs:8,0.0576614906851234);

\path [draw=color0, semithick]
(axis cs:9,-0.0224725241932268)
--(axis cs:9,0.0741638148527915);

\path [draw=color0, semithick]
(axis cs:10,-0.0756353873903538)
--(axis cs:10,0.12067302510658);

\path [draw=color0, semithick]
(axis cs:11,-0.0502658861107364)
--(axis cs:11,0.0475976109331108);

\path [draw=color0, semithick]
(axis cs:12,-0.0580334518860479)
--(axis cs:12,0.0522932085217476);

\path [draw=color0, semithick]
(axis cs:13,-0.250619578161296)
--(axis cs:13,-0.0131299796235295);

\path [draw=color0, semithick]
(axis cs:14,-0.270974675652396)
--(axis cs:14,-0.0146066638787493);

\path [draw=color0, semithick]
(axis cs:15,-0.137679517728949)
--(axis cs:15,0.0565235556021181);

\path [draw=color0, semithick]
(axis cs:16,-0.0895883476180547)
--(axis cs:16,0.159734719752018);

\path [draw=color0, semithick]
(axis cs:17,-0.293950085783651)
--(axis cs:17,0.231750080586464);

\path [draw=color0, semithick]
(axis cs:18,-0.319655037072536)
--(axis cs:18,0.0306934587058758);

\path [draw=color0, semithick]
(axis cs:19,-0.236206876473511)
--(axis cs:19,0.302632365558163);

\path [draw=color0, semithick]
(axis cs:20,-0.155739313287969)
--(axis cs:20,0.143862527337602);

\path [draw=color0, semithick]
(axis cs:21,-0.192747588063431)
--(axis cs:21,0.115219970006173);

\path [draw=color0, semithick]
(axis cs:22,-0.235981974229328)
--(axis cs:22,0.126652912953733);

\path [draw=color0, semithick]
(axis cs:23,-0.16625366350342)
--(axis cs:23,0.0517139839386183);

\path [draw=color0, semithick]
(axis cs:24,-0.235550284144142)
--(axis cs:24,0.227333400044145);

\path [draw=color0, semithick]
(axis cs:25,-0.315874390637381)
--(axis cs:25,0.249069862823448);

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 -0.229417488366355
2 0.23592009450898
3 -0.0305441203965614
4 -0.0595627687059507
5 -0.436113887749494
6 0.00255054819934573
7 0.0465056999066113
8 -0.0409018572150964
9 -0.0224725241932268
10 -0.0756353873903538
11 -0.0502658861107364
12 -0.0580334518860479
13 -0.250619578161296
14 -0.270974675652396
15 -0.137679517728949
16 -0.0895883476180547
17 -0.293950085783651
18 -0.319655037072536
19 -0.236206876473511
20 -0.155739313287969
21 -0.192747588063431
22 -0.235981974229328
23 -0.16625366350342
24 -0.235550284144142
25 -0.315874390637381
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 -0.0167110182346182
2 0.272229779422249
3 0.158020721059096
4 0.0798699329713486
5 -0.416975614327935
6 0.143980501855128
7 0.0951062318594004
8 0.0576614906851234
9 0.0741638148527915
10 0.12067302510658
11 0.0475976109331108
12 0.0522932085217476
13 -0.0131299796235295
14 -0.0146066638787493
15 0.0565235556021181
16 0.159734719752018
17 0.231750080586464
18 0.0306934587058758
19 0.302632365558163
20 0.143862527337602
21 0.115219970006173
22 0.126652912953733
23 0.0517139839386183
24 0.227333400044145
25 0.249069862823448
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Logistic regression};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/01-ferrenti-approachPC-final.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=1.4222438079424382in,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xlabel={Principal components},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.133808014644924,
ytick style={color=black},
yticklabels={, 0, , 0.1},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:1.4,0.123808014644924);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0779020383908885);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0690715494994265);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0448634890553009);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0396017649392185);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0309892340254588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0286471759268761);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0241373022722755);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0219387724823991);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0191941500093896);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0170987447716404);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0163324377943715);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0142479118996461);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0139471831901937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0125561362477749);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0122752355665442);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0117377683648439);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0108124054147357);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0105912984624588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:19.6,0) rectangle (axis cs:20.4,0.00987028371434172);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:20.6,0) rectangle (axis cs:21.4,0.00946157777094173);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:21.6,0) rectangle (axis cs:22.4,0.00932051055389097);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00851928669553865);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:23.6,0) rectangle (axis cs:24.4,0.00821174057436937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:24.6,0) rectangle (axis cs:25.4,0.00796122578616887);
\addlegendimage{semithick, color=white!53.3333333333333!black};
\addlegendentry{Explained variance};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/01-ferrenti-approachRF-final.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.163961791193378,
ytick style={color=black},
yticklabels={,0,,0.1,,0.2},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.0630557431105419);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0831193744181552);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.022912143158908);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0195487261065447);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.113961791193378);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0166845058106126);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0111880865301946);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0109815412799707);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.013418791526676);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0148028536779526);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0131608319701371);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.00838039909198669);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0148854194402229);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0203640215741575);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0147922332160194);
\draw[draw=none,fill=color0] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0167058216702408);
\draw[draw=none,fill=color0] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0285684173665608);
\draw[draw=none,fill=color0] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0251819365387591);
\draw[draw=none,fill=color0] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0342442655954786);
\draw[draw=none,fill=color0] (axis cs:19.6,0) rectangle (axis cs:20.4,0.0138513854588785);
\draw[draw=none,fill=color0] (axis cs:20.6,0) rectangle (axis cs:21.4,0.0135559278428533);
\draw[draw=none,fill=color0] (axis cs:21.6,0) rectangle (axis cs:22.4,0.0150237331161702);
\draw[draw=none,fill=color0] (axis cs:22.6,0) rectangle (axis cs:23.4,0.0096270211737359);
\draw[draw=none,fill=color0] (axis cs:23.6,0) rectangle (axis cs:24.4,0.0206136662393266);
\draw[draw=none,fill=color0] (axis cs:24.6,0) rectangle (axis cs:25.4,0.0335101355200213);
\path [draw=color0, semithick]
(axis cs:1,0.0573010303012627)
--(axis cs:1,0.0688104559198211);

\path [draw=color0, semithick]
(axis cs:2,0.0715458523831103)
--(axis cs:2,0.0946928964532001);

\path [draw=color0, semithick]
(axis cs:3,0.0162325617369429)
--(axis cs:3,0.0295917245808731);

\path [draw=color0, semithick]
(axis cs:4,0.0151929284504258)
--(axis cs:4,0.0239045237626635);

\path [draw=color0, semithick]
(axis cs:5,0.103650391870818)
--(axis cs:5,0.124273190515939);

\path [draw=color0, semithick]
(axis cs:6,0.0127466082846881)
--(axis cs:6,0.0206224033365371);

\path [draw=color0, semithick]
(axis cs:7,0.00938556140819314)
--(axis cs:7,0.012990611652196);

\path [draw=color0, semithick]
(axis cs:8,0.00854307516043412)
--(axis cs:8,0.0134200073995072);

\path [draw=color0, semithick]
(axis cs:9,0.0116751719811282)
--(axis cs:9,0.0151624110722239);

\path [draw=color0, semithick]
(axis cs:10,0.0103717999049377)
--(axis cs:10,0.0192339074509675);

\path [draw=color0, semithick]
(axis cs:11,0.00968301823796202)
--(axis cs:11,0.0166386457023121);

\path [draw=color0, semithick]
(axis cs:12,0.0064665824303152)
--(axis cs:12,0.0102942157536582);

\path [draw=color0, semithick]
(axis cs:13,0.00834089792296834)
--(axis cs:13,0.0214299409574775);

\path [draw=color0, semithick]
(axis cs:14,0.005070824077227)
--(axis cs:14,0.0356572190710881);

\path [draw=color0, semithick]
(axis cs:15,0.00706511442570956)
--(axis cs:15,0.0225193520063292);

\path [draw=color0, semithick]
(axis cs:16,0.00601575858602535)
--(axis cs:16,0.0273958847544562);

\path [draw=color0, semithick]
(axis cs:17,0.0113173620435266)
--(axis cs:17,0.045819472689595);

\path [draw=color0, semithick]
(axis cs:18,0.0103353119352383)
--(axis cs:18,0.0400285611422799);

\path [draw=color0, semithick]
(axis cs:19,0.011625254341459)
--(axis cs:19,0.0568632768494982);

\path [draw=color0, semithick]
(axis cs:20,0.00342679873482929)
--(axis cs:20,0.0242759721829277);

\path [draw=color0, semithick]
(axis cs:21,0.00673116906011602)
--(axis cs:21,0.0203806866255907);

\path [draw=color0, semithick]
(axis cs:22,0.00496948896783449)
--(axis cs:22,0.0250779772645059);

\path [draw=color0, semithick]
(axis cs:23,0.00660725108889622)
--(axis cs:23,0.0126467912585756);

\path [draw=color0, semithick]
(axis cs:24,0.00380908046748388)
--(axis cs:24,0.0374182520111692);

\path [draw=color0, semithick]
(axis cs:25,0.00587721747702246)
--(axis cs:25,0.0611430535630202);
\addlegendimage{semithick, color=color0};
\addlegendentry{Random forest};
\addplot [semithick, color0, mark=-, mark size=0, mark options={solid}, only marks]
table {%
1 0.0573010303012627
2 0.0715458523831103
3 0.0162325617369429
4 0.0151929284504258
5 0.103650391870818
6 0.0127466082846881
7 0.00938556140819314
8 0.00854307516043412
9 0.0116751719811282
10 0.0103717999049377
11 0.00968301823796202
12 0.0064665824303152
13 0.00834089792296834
14 0.005070824077227
15 0.00706511442570956
16 0.00601575858602535
17 0.0113173620435266
18 0.0103353119352383
19 0.011625254341459
20 0.00342679873482929
21 0.00673116906011602
22 0.00496948896783449
23 0.00660725108889622
24 0.00380908046748388
25 0.00587721747702246
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.0688104559198211
2 0.0946928964532001
3 0.0295917245808731
4 0.0239045237626635
5 0.124273190515939
6 0.0206224033365371
7 0.012990611652196
8 0.0134200073995072
9 0.0151624110722239
10 0.0192339074509675
11 0.0166386457023121
12 0.0102942157536582
13 0.0214299409574775
14 0.0356572190710881
15 0.0225193520063292
16 0.0273958847544562
17 0.045819472689595
18 0.0400285611422799
19 0.0568632768494982
20 0.0242759721829277
21 0.0203806866255907
22 0.0250779772645059
23 0.0126467912585756
24 0.0374182520111692
25 0.0611430535630202
};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/03-insightful-approachDT-final-2.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.8,0.4,0.466666666666667}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.84619547527771,
ytick style={color=black},
yticklabels={,0,, 0.4,,0.8},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.731619547527771);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.18113983898672);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.00345402728374034);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0208705310819208);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0155739365467582);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0237724911651494);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.003003922613769);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00923425403456265);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0113314507596083);
\path [draw=color0, semithick]
(axis cs:1,0.709690218797472)
--(axis cs:1,0.753548876258071);

\path [draw=color0, semithick]
(axis cs:2,0.159795728748012)
--(axis cs:2,0.202483949225428);

\path [draw=color0, semithick]
(axis cs:3,-0.00265218119467417)
--(axis cs:3,0.00956023576215485);

\path [draw=color0, semithick]
(axis cs:4,0.00724021662950192)
--(axis cs:4,0.0345008455343396);

\path [draw=color0, semithick]
(axis cs:5,-0.00216067805943182)
--(axis cs:5,0.0333085511529482);

\path [draw=color0, semithick]
(axis cs:6,0.00816087621620421)
--(axis cs:6,0.0393841061140945);

\path [draw=color0, semithick]
(axis cs:7,-0.00231674240297224)
--(axis cs:7,0.00832458763051024);

\path [draw=color0, semithick]
(axis cs:8,-0.002629967814537)
--(axis cs:8,0.0210984758836623);

\path [draw=color0, semithick]
(axis cs:9,-0.00405574281778054)
--(axis cs:9,0.0267186443369972);

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.709690218797472
2 0.159795728748012
3 -0.00265218119467417
4 0.00724021662950192
5 -0.00216067805943182
6 0.00816087621620421
7 -0.00231674240297224
8 -0.002629967814537
9 -0.00405574281778054
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.753548876258071
2 0.202483949225428
3 0.00956023576215485
4 0.0345008455343396
5 0.0333085511529482
6 0.0393841061140945
7 0.00832458763051024
8 0.0210984758836623
9 0.0267186443369972
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Decision tree};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/03-insightful-approachGB-final-2.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.0666666666666667,0.466666666666667,0.2}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.941178662009005,
yticklabels={,0,, 0.4,,0.8},
ytick style={color=black},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.871178662009005);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0217568511840037);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.00253604996390695);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0192708196133984);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0198922275506549);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0260375424696281);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0063356815006726);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00319869517406271);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.00540195176007804);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.00695771640251456);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.00312270971606427);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0030932299465922);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0112178627094187);
\path [draw=color0, semithick]
(axis cs:1,0.854956014167526)
--(axis cs:1,0.887401309850484);

\path [draw=color0, semithick]
(axis cs:2,0.00907965200713417)
--(axis cs:2,0.0344340503608733);

\path [draw=color0, semithick]
(axis cs:3,-0.000182654889842383)
--(axis cs:3,0.00525475481765629);

\path [draw=color0, semithick]
(axis cs:4,0.00923661909617688)
--(axis cs:4,0.0293050201306199);

\path [draw=color0, semithick]
(axis cs:5,-0.00820788248180509)
--(axis cs:5,0.0479923375831149);

\path [draw=color0, semithick]
(axis cs:6,0.00143690786973603)
--(axis cs:6,0.0506381770695201);

\path [draw=color0, semithick]
(axis cs:7,-0.00149882818592621)
--(axis cs:7,0.0141701911872714);

\path [draw=color0, semithick]
(axis cs:8,-0.00213482608794717)
--(axis cs:8,0.00853221643607259);

\path [draw=color0, semithick]
(axis cs:9,-0.00260933890414728)
--(axis cs:9,0.0134132424243034);

\path [draw=color0, semithick]
(axis cs:10,-0.0038254976017747)
--(axis cs:10,0.0177409304068038);

\path [draw=color0, semithick]
(axis cs:11,-0.0044786262895489)
--(axis cs:11,0.0107240457216774);

\path [draw=color0, semithick]
(axis cs:12,-0.000395131606741384)
--(axis cs:12,0.00658159149992578);

\path [draw=color0, semithick]
(axis cs:13,-0.00413997684116445)
--(axis cs:13,0.0265757022600018);

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.854956014167526
2 0.00907965200713417
3 -0.000182654889842383
4 0.00923661909617688
5 -0.00820788248180509
6 0.00143690786973603
7 -0.00149882818592621
8 -0.00213482608794717
9 -0.00260933890414728
10 -0.0038254976017747
11 -0.0044786262895489
12 -0.000395131606741384
13 -0.00413997684116445
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.887401309850484
2 0.0344340503608733
3 0.00525475481765629
4 0.0293050201306199
5 0.0479923375831149
6 0.0506381770695201
7 0.0141701911872714
8 0.00853221643607259
9 0.0134132424243034
10 0.0177409304068038
11 0.0107240457216774
12 0.00658159149992578
13 0.0265757022600018
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Gradient boost};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/03-insightful-approachLOG-final-2.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.533333333333333,0.8,0.933333333333333}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=-0.623461141126395, ymax=0.530741648814479,
ytick style={color=black},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,-0.253461141126395);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0901171486976447);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0863947483049856);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,-0.0772968684905453);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0300554413526054);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0644447825923199);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.000906315046421985);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0527024964515279);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,-0.0642484568407123);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,-0.111007430848113);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0148183210539744);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,-0.000553836590813862);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.100741648814479);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0378766308558455);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0181014244362775);
\path [draw=color0, semithick]
(axis cs:1,-0.587142604409583)
--(axis cs:1,0.0802203221567937);

\path [draw=color0, semithick]
(axis cs:2,0.0731623861401247)
--(axis cs:2,0.107071911255165);

\path [draw=color0, semithick]
(axis cs:3,0.0687951204204073)
--(axis cs:3,0.103994376189564);

\path [draw=color0, semithick]
(axis cs:4,-0.146499644473957)
--(axis cs:4,-0.0080940925071333);

\path [draw=color0, semithick]
(axis cs:5,-0.0313238410576597)
--(axis cs:5,0.0914347237628705);

\path [draw=color0, semithick]
(axis cs:6,0.0198594131562677)
--(axis cs:6,0.109030152028372);

\path [draw=color0, semithick]
(axis cs:7,-0.0499168743976032)
--(axis cs:7,0.0517295044904472);

\path [draw=color0, semithick]
(axis cs:8,0.00179966720486961)
--(axis cs:8,0.103605325698186);

\path [draw=color0, semithick]
(axis cs:9,-0.124803037939885)
--(axis cs:9,-0.00369387574154015);

\path [draw=color0, semithick]
(axis cs:10,-0.178052830807337)
--(axis cs:10,-0.0439620308888901);

\path [draw=color0, semithick]
(axis cs:11,-0.0315422676418746)
--(axis cs:11,0.0611789097498233);

\path [draw=color0, semithick]
(axis cs:12,-0.0592218306178204)
--(axis cs:12,0.0581141574361927);

\path [draw=color0, semithick]
(axis cs:13,0.0576301597775916)
--(axis cs:13,0.143853137851366);

\path [draw=color0, semithick]
(axis cs:14,-0.0196357412360911)
--(axis cs:14,0.0953890029477821);

\path [draw=color0, semithick]
(axis cs:15,-0.0217054681168758)
--(axis cs:15,0.0579083169894307);

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 -0.587142604409583
2 0.0731623861401247
3 0.0687951204204073
4 -0.146499644473957
5 -0.0313238410576597
6 0.0198594131562677
7 -0.0499168743976032
8 0.00179966720486961
9 -0.124803037939885
10 -0.178052830807337
11 -0.0315422676418746
12 -0.0592218306178204
13 0.0576301597775916
14 -0.0196357412360911
15 -0.0217054681168758
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.0802203221567937
2 0.107071911255165
3 0.103994376189564
4 -0.0080940925071333
5 0.0914347237628705
6 0.109030152028372
7 0.0517295044904472
8 0.103605325698186
9 -0.00369387574154015
10 -0.0439620308888901
11 0.0611789097498233
12 0.0581141574361927
13 0.143853137851366
14 0.0953890029477821
15 0.0579083169894307
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Logistic regression};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/03-insightful-approachPC-final-2.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\begin{axis}[
height=1.4222438079424382in,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xlabel={Principal components},
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.227659111193136,
ytick style={color=black},
yticklabels={,0,, 0.2},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:1.4,0.207659111193136);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:1.6,0) rectangle (axis cs:2.4,0.100931286761405);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0552189869141694);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0393144279067069);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0359175173728584);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0352100230844184);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0281116402524651);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0255858301182614);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:8.6,0) rectangle (axis cs:9.4,0.020895147833239);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:9.6,0) rectangle (axis cs:10.4,0.020208986578298);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0173851755021279);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0170402398481309);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0150421767580223);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0135123051552189);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0123812036773514);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0121461292946794);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0113049221584044);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0105679286164572);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0099240637848415);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:19.6,0) rectangle (axis cs:20.4,0.00947939547970391);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:20.6,0) rectangle (axis cs:21.4,0.00880748003307345);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:21.6,0) rectangle (axis cs:22.4,0.00854299753930025);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00819923337711622);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:23.6,0) rectangle (axis cs:24.4,0.00783441956089457);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:24.6,0) rectangle (axis cs:25.4,0.00725436756435554);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:25.6,0) rectangle (axis cs:26.4,0.00706748361834891);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:26.6,0) rectangle (axis cs:27.4,0.0067946334120975);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:27.6,0) rectangle (axis cs:28.4,0.00649269621923748);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:28.6,0) rectangle (axis cs:29.4,0.00631012021109268);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:29.6,0) rectangle (axis cs:30.4,0.0059935965924482);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:30.6,0) rectangle (axis cs:31.4,0.00591276082294336);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:31.6,0) rectangle (axis cs:32.4,0.00563442172532614);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:32.6,0) rectangle (axis cs:33.4,0.00539612814948874);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:33.6,0) rectangle (axis cs:34.4,0.00529456870611715);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:34.6,0) rectangle (axis cs:35.4,0.0052012922431412);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:35.6,0) rectangle (axis cs:36.4,0.00496741617032561);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:36.6,0) rectangle (axis cs:37.4,0.00483584771153227);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:37.6,0) rectangle (axis cs:38.4,0.00475069774706768);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:38.6,0) rectangle (axis cs:39.4,0.00453755427803973);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:39.6,0) rectangle (axis cs:40.4,0.00431289524873035);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:40.6,0) rectangle (axis cs:41.4,0.00413291864955501);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:41.6,0) rectangle (axis cs:42.4,0.00404009691245206);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:42.6,0) rectangle (axis cs:43.4,0.00384707175639724);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:43.6,0) rectangle (axis cs:44.4,0.00370794252319461);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:44.6,0) rectangle (axis cs:45.4,0.00360347785161737);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:45.6,0) rectangle (axis cs:46.4,0.00350293803678438);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:46.6,0) rectangle (axis cs:47.4,0.00335377406642866);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:47.6,0) rectangle (axis cs:48.4,0.00332782254644005);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:48.6,0) rectangle (axis cs:49.4,0.00325065460225723);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:49.6,0) rectangle (axis cs:50.4,0.00312401268859448);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:50.6,0) rectangle (axis cs:51.4,0.00307409451814868);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:51.6,0) rectangle (axis cs:52.4,0.00295493366839609);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:52.6,0) rectangle (axis cs:53.4,0.00283452933734321);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:53.6,0) rectangle (axis cs:54.4,0.00281415629292076);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:54.6,0) rectangle (axis cs:55.4,0.00277164449537654);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:55.6,0) rectangle (axis cs:56.4,0.0027301380386249);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:56.6,0) rectangle (axis cs:57.4,0.00269085035745271);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:57.6,0) rectangle (axis cs:58.4,0.00256884319342844);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:58.6,0) rectangle (axis cs:59.4,0.00252762617436217);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:59.6,0) rectangle (axis cs:60.4,0.00237101574205109);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:60.6,0) rectangle (axis cs:61.4,0.0023429271914207);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:61.6,0) rectangle (axis cs:62.4,0.00230359137012767);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:62.6,0) rectangle (axis cs:63.4,0.00221364734281885);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:63.6,0) rectangle (axis cs:64.4,0.0021462360088001);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:64.6,0) rectangle (axis cs:65.4,0.00211833683255068);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:65.6,0) rectangle (axis cs:66.4,0.00205592806762017);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:66.6,0) rectangle (axis cs:67.4,0.00203631661765791);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:67.6,0) rectangle (axis cs:68.4,0.00200913992503488);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:68.6,0) rectangle (axis cs:69.4,0.00198860732256562);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:69.6,0) rectangle (axis cs:70.4,0.00191877504746405);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:70.6,0) rectangle (axis cs:71.4,0.00183983787651402);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:71.6,0) rectangle (axis cs:72.4,0.00178967267072127);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:72.6,0) rectangle (axis cs:73.4,0.00176113054018146);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:73.6,0) rectangle (axis cs:74.4,0.00175587755437847);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:74.6,0) rectangle (axis cs:75.4,0.00166568926296783);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:75.6,0) rectangle (axis cs:76.4,0.00164865674220492);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:76.6,0) rectangle (axis cs:77.4,0.00163963642273892);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:77.6,0) rectangle (axis cs:78.4,0.00152246485297179);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:78.6,0) rectangle (axis cs:79.4,0.00150671318108692);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:79.6,0) rectangle (axis cs:80.4,0.00146762230969936);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:80.6,0) rectangle (axis cs:81.4,0.00144254604987905);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:81.6,0) rectangle (axis cs:82.4,0.00142852516970499);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:82.6,0) rectangle (axis cs:83.4,0.00140797817653715);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:83.6,0) rectangle (axis cs:84.4,0.00137907370730369);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:84.6,0) rectangle (axis cs:85.4,0.00137189411391102);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:85.6,0) rectangle (axis cs:86.4,0.00134894755604915);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:86.6,0) rectangle (axis cs:87.4,0.00131887269241828);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:87.6,0) rectangle (axis cs:88.4,0.00125161529911504);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:88.6,0) rectangle (axis cs:89.4,0.00123038981331776);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:89.6,0) rectangle (axis cs:90.4,0.00120293547721247);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:90.6,0) rectangle (axis cs:91.4,0.00118929296627723);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:91.6,0) rectangle (axis cs:92.4,0.00115421686183217);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:92.6,0) rectangle (axis cs:93.4,0.00113288923394035);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:93.6,0) rectangle (axis cs:94.4,0.00108899958168978);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:94.6,0) rectangle (axis cs:95.4,0.00107268732150737);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:95.6,0) rectangle (axis cs:96.4,0.00104142782755626);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:96.6,0) rectangle (axis cs:97.4,0.00101906762512476);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:97.6,0) rectangle (axis cs:98.4,0.00101077830297021);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:98.6,0) rectangle (axis cs:99.4,0.000989640667068959);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:99.6,0) rectangle (axis cs:100.4,0.000984439118691105);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:100.6,0) rectangle (axis cs:101.4,0.000960734989790538);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:101.6,0) rectangle (axis cs:102.4,0.000941461336335633);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:102.6,0) rectangle (axis cs:103.4,0.000928355012563315);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:103.6,0) rectangle (axis cs:104.4,0.000913315342059004);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:104.6,0) rectangle (axis cs:105.4,0.000897708116603778);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:105.6,0) rectangle (axis cs:106.4,0.000874661763686027);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:106.6,0) rectangle (axis cs:107.4,0.000854349918034593);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:107.6,0) rectangle (axis cs:108.4,0.000841201883286582);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:108.6,0) rectangle (axis cs:109.4,0.000819094760963474);
\addlegendimage{semithick, color=white!53.3333333333333!black};
\addlegendentry{Explained variance};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/feature-importance/03-insightful-approachRF-final-2.tex
Updates from Overleaf

% This file was created by tikzplotlib v0.9.8.
\begin{tikzpicture}

\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.455941102264594,
ytick style={color=black},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.405941102264594);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0980875027579887);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.048776110224331);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0307695146020032);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0225284912793522);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0376912406521808);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0408639729682783);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0453356735282065);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0258685047848363);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0341199103889856);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0225669600689547);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0197271830187896);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0294260599312947);
\draw[draw=none,fill=color0] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0100732082030255);
\draw[draw=none,fill=color0] (axis cs:14.6,0) rectangle (axis cs:15.4,0.00768012576296064);
\path [draw=color0, semithick]
(axis cs:1,0.38913349982482)
--(axis cs:1,0.422748704704367);

\path [draw=color0, semithick]
(axis cs:2,0.0842715544768568)
--(axis cs:2,0.111903451039121);

\path [draw=color0, semithick]
(axis cs:3,0.0397491095240302)
--(axis cs:3,0.0578031109246318);

\path [draw=color0, semithick]
(axis cs:4,0.0174838367514499)
--(axis cs:4,0.0440551924525565);

\path [draw=color0, semithick]
(axis cs:5,0.00917160744440918)
--(axis cs:5,0.0358853751142952);

\path [draw=color0, semithick]
(axis cs:6,0.0246759311379229)
--(axis cs:6,0.0507065501664387);

\path [draw=color0, semithick]
(axis cs:7,0.0296874637992993)
--(axis cs:7,0.0520404821372574);

\path [draw=color0, semithick]
(axis cs:8,0.0303547427614151)
--(axis cs:8,0.0603166042949978);

\path [draw=color0, semithick]
(axis cs:9,0.0147923986315111)
--(axis cs:9,0.0369446109381616);

\path [draw=color0, semithick]
(axis cs:10,0.0226833594028516)
--(axis cs:10,0.0455564613751197);

\path [draw=color0, semithick]
(axis cs:11,0.0134546981738569)
--(axis cs:11,0.0316792219640525);

\path [draw=color0, semithick]
(axis cs:12,0.0115712020878138)
--(axis cs:12,0.0278831639497654);

\path [draw=color0, semithick]
(axis cs:13,0.0188115961460041)
--(axis cs:13,0.0400405237165853);

\path [draw=color0, semithick]
(axis cs:14,0.00377725683628826)
--(axis cs:14,0.0163691595697627);

\path [draw=color0, semithick]
(axis cs:15,0.00393722295943178)
--(axis cs:15,0.0114230285664895);

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.38913349982482
2 0.0842715544768568
3 0.0397491095240302
4 0.0174838367514499
5 0.00917160744440918
6 0.0246759311379229
7 0.0296874637992993
8 0.0303547427614151
9 0.0147923986315111
10 0.0226833594028516
11 0.0134546981738569
12 0.0115712020878138
13 0.0188115961460041
14 0.00377725683628826
15 0.00393722295943178
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.422748704704367
2 0.111903451039121
3 0.0578031109246318
4 0.0440551924525565
5 0.0358853751142952
6 0.0507065501664387
7 0.0520404821372574
8 0.0603166042949978
9 0.0369446109381616
10 0.0455564613751197
11 0.0316792219640525
12 0.0278831639497654
13 0.0400405237165853
14 0.0163691595697627
15 0.0114230285664895
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Random forest};
\end{axis}

\end{tikzpicture}

### 2022-01-07 figures/tikz-plots/prediction-fig.tex
Updates from Overleaf

@@
     \centering
-    (a)
+    (a) Ferrenti approach
     \\
@@
     \\
-    (b)
+    (b) Augmented Ferrenti approach 
     \\
@@
     \\
-    (c)
+    (c) Intuitive approach
     \\
@@
   \end{forest}
-\vspace*{-95mm}
-\caption{Visualization of the predicted material candidates from the (a) Ferrenti, (b) augemented Ferrenti and (c) insightful approaches.
-The green nodes display the number of predicted suitable candidates while unsuitable ones are marked in red.}
+%\vspace*{-95mm}
+\caption{Visualization of the predicted material candidates from the (a) Ferrenti, (b) augmented Ferrenti and (c) intuitive approaches.
+Green and red nodes represent suitable and unsuitable candidates, respectively.
+}
 \label{fig:predictions}

### 2022-01-07 paper.tex
Updates from Overleaf

@@
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
-\affiliation{Sopra Steria, N-0185 Oslo, Norway}
 
@@
 However, scouring these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics %\cite{rickman2019}
-and machine learning methods.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods.
 
@@
 Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}.
-%Rename insightful approach! To what? 
+%Rename insightful approach! To what? Restricted? Experience-based?  
 %Options include stringent, strict, cherry-picked, informed and intuitive. 
@@
 The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-All four machine learning (ML) methods applied to the data set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.
+All four machine learning (ML) methods applied to the training set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
@@
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
-Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a 53-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
+Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a $53$-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
@@
     \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
-    \caption{Schematic of an example workflow in material informatics: results from theory, experiment and computation are fed into material databases (arrow pointing to the center).
+    \caption{Schematic of an example workflow in material informatics.
+Results from theory, experiment and computation are fed into material databases (arrow pointing to the center).
 A cycle involving material screening, machine learning and predictions leads to knowledge gain and ultimately applications in fields such as clean energy and quantum technology.
@@
 So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
-The most well-known QT defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
+The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
 However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
@@
 
-The majority of discoveries of quantum emitters in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of how the QT compatible materials properties manifest.
+The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of how the QT compatible materials properties manifest.
 In this context, a framework for dedicated materials search and analysis is needed.
@@
 The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
-Instead, the fourth paradigm  introduces the potential of targeted search for promising material systems to act as hosts for qubit and single-photon emitter defects.
+Instead, the fourth paradigm  introduces the potential of targeted search for promising material systems to enable properties such as coherent and isolated spin states and indistinguishable single-photon emission to manifest.
 Rather than searching through a host of signals for those that match our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
-This is made feasible by the availability of databases containing materials properties for a wide range of different systems.
+This is made feasible by the availability of databases containing material properties for a wide range of different systems.
 In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
@@
 In this work we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
+In this context, we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
 The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical and/or experimental data are available.
@@
 We find that the former two methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
-The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set.
-These training sets where then analyzed with the above mentioned machine learning methods, and yielded $214$ predicted candidates
+The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
+The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates
 %(to a $0.5$ cut-off)  
 with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs. 
+Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
 
@@
 %connected in logical pieces. 
+%MHJ What do we mean with logical pieces? 
 that are connected. 
 The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}. 
-Initially, we start by extracting all entries in the Materials Project (MP) that match a specific query. 
-The MP database contains ground state properties of different materials that are calculated using density functional theory (DFT).
-The DFT simulations are effectively implemented using the Vienna Ab Initio Package (VASP) \cite{Kresse1996} and the  Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996}  functional to calculate the electronic structure of the materials.
+Initially, we start by extracting all entries in the Materials Project (MP) database that match a specific query. 
+The MP database contains ground state properties of different materials that are computed using density functional theory (DFT).
+The DFT calculations in the database were performed using the Vienna ab initio simulation package (VASP) \cite{Kresse1996} and the Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996} exchange-correlation functional to calculate the electronic structure of the materials.
 
@@
     \includegraphics[width=0.9\textwidth]{figures/flow_chart.png}
-    \caption{The data flow of the main project, starting from an initial MP-query, and ending with a featurized dataset with entries from several other databases.
-To limit the memory and computational usage, the data are
-    partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in
-    the following featurization steps. This process is repeated iteratively until all the data has been featurized.
+    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized dataset with entries from several other databases.
+To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects
+    (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) 
+    are obtained through a query to be used in the following featurization steps.
+This process is repeated iteratively until all the data has been featurized.
 Abbreviations used are Materials Project (MP), density of states (DOS) and electronic band structure (band).
@@
 
-The conditions for this initial query are that the materials must derive from 
+The conditions for the initial MP query are that the materials must derive from 
 %experimental data 
-the ICSD database 
-and have a band gap wider than $0.1$~eV to exclude metallic compounds. 
-The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.%
+the ICSD database and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.
 %OH: corrected icsd citation to german one (different from nist)
-In a parallel step, entries that are deemed
-similar to the entries from the initial query
-are extracted from the databases OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017}, and the Citrination platform \cite{OMaraJordan2016MDIA}.
+In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the databases OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
 The results of these steps are combined into a data set for further analysis.
@@
 The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project. 
+%MB I moved the below to methods 
 %To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}, which were used to generate a supervised machine learning framework called the MODnet.
@@
 However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure, therefore, we extend their implementation to facilitate such featurizations.
-A schematic visualizing the featurization process in Matminer is contained in Figure~\ref{fig:flowchart} 
+A schematic visualizing the featurization process in Matminer is contained in Fig.~\ref{fig:flowchart} 
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ features selected in this work are summarized in the Supplementary Material at \cite{supplementary}.
+The $39$ features selected as material descriptors in this work can be found in the Supplementary Material at \cite{supplementary}.
 The selection of features was kept rather wide as we do not precisely know which features best describe a solid state material platform for quantum technology.
@@
 After compiling a data set from the procedure outlined above, we face an obstacle in terms of defining a training set for the machine learning algorithms. This is challenging for two reasons.  
-Firstly, although defects like the NV center in diamond and emitters in SiC are becoming
-increasingly well studied, few candidate materials are known. An additional consideration 
-is that the physical mechanisms promoting favorable defect properties are not fully understood. Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
+Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures, few candidate materials are known.
+An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technology.
+Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
 We follow three separate procedures to define a training set consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
@@
 In this framework, we label \textbf{suitable} candidates by the following steps:
-%MHJ how do we cite the  ICSD data? No ref as of now
 \begin{enumerate}
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database,  %\cite{Allen1987,Zagorac2019} 
-        %(the world's largest database for completely identified inorganic crystal structures), 
+        \item are present in the ICSD database, 
         and
@@
 
+The inclusion criteria are targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
+In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
+Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable photon emission, non-polar materials are assumed to be preferable.
+The inclusion criteria listed above are based on the work of \citeauthor{Weber2010} \cite{Weber2010}.
+
 Transition metal elements are eliminated in this approach if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
@@
 that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional, as discussed above.
-The resulting complete data set contains $1581$ materials where %$56 \ \%$ 
+The resulting complete training set contains $1581$ materials where %$56 \ \%$ 
 $35 \ \%$
@@
 \subsubsection*{The augmented Ferrenti approach}
-In the second approach, we adjust the first approach in order to improve the data set. This approach is therefore named \emph{the augmented Ferrenti approach}.
+In the second approach, we adjust the former one in order to expand the training set beyond practical considerations. This approach is therefore named \emph{the augmented Ferrenti approach}.
 
-In the first approach we included criteria that were not physically motivated, but instead to some extent based on a  practical perspective, like excluding toxic and radioactive elements.
-Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the practicality of the material to be employed.
+In the first approach we included criteria that were not physically motivated, but instead to some extent based on a practical perspective, such as excluding toxic and radioactive elements.
+Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the feasibility of the material to be employed.
 Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
@@
 
-The following steps constitute the process of choosing \textbf{suitable} candidates 
-in the \emph{augmented Ferrenti approach}:
+The following steps constitute the process of choosing \textbf{suitable} candidates in the \emph{augmented Ferrenti approach}:
 \begin{enumerate}
@@
     \begin{itemize}
-        \item contain elements where more than half have a natural abundance of zero spin isotopes, including Al, P, Ga, As, B and N, 
+        \item contain elements where more than half have a natural abundance of spin zero isotopes, including Al, P, Ga, As, B and N, 
         \item crystallize in non-polar space groups,
@@
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the non-augmented Ferrenti approach.
-The result is a somewhat unbalanced data set, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the data set is $78 \ \%$ larger than for the Ferrenti approach.
+For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
+The result is a somewhat unbalanced training set, with up to $75 \ \%$ of the materials found in the suitable group.
+However, the training set is $78 \ \%$ larger than for the Ferrenti approach with $2141$ suitable and $684$ unsuitable materials.
 
 \subsubsection*{The intuitive approach}
-The third approach differs substantially from the first two approaches in terms of labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview) to pick our promising material host candidates.
+The third approach differs substantially from the first two approaches in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview) to pick our promising material host candidates.
 In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
 We therefore name this scheme \emph{the intuitive approach}.
-Due to the concern of having a data set that is too narrow, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
-Materials where properties like single-photon emission and spin manipulation are attributed to quantum dots (formed by self-assembly or lithographic structuring) will also be included in this context.
+Due to the concern of having a training set that is too narrow in scope, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
+Materials where properties like single-photon emission and spin manipulation have been observed but attributed to quantum dots (formed by self-assembly or lithographic structuring) rather than being directly  defect related will also be included in this context.
 The approach to pick \textbf{suitable} candidates can be summed up as;   
@@
     \item Pick candidates that match the formulas in Table~\ref{tab:qt-materials}, or the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} or SiGe \cite{Hardy2019}. 
-    \item Make sure that the candidates are present in the ICSD database.  
+    \item Ensure that the candidates are present in the ICSD database.  
     \item Perform a manual screening for appropriate crystallographic structures. 
@@
 The table forms the basis for picking suitable candidates for the intuitive approach.
-The properties being studied arise from mechanisms related to, e.g., point defects, excitons, and both self-assembled and lithographically structured quantum dots. 
-Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects is still lacking. 
+The properties being studied arise from mechanisms related to, e.g., point defects, bound excitons, and both self-assembled and lithographically structured quantum dots and nanostructures such as 2D materials.
+Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects or structure related mechanism is still lacking.
 In the intuitive approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
@@
 These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
-We include all of the $202$ structures except for C (mp-568410) having a PBE-computed band gap of $0.12$~eV - a metal according to AFLOW-ML and therefore labeled as an unsuitable candidate.
+We include all of the $202$ structures except for C (mp-568410) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
 
@@
 For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
-Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$ eV) in the data.
+Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$~eV) among the data.
 We add these as suitable candidates.
-Complex structures (eg.
-C$_{28}$, C$_{48}$, C$_{60}$) were moved to the test set in our machine learning studies, see discussion below.
-For SiC, we admitted all entries, which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
+Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies, see discussion below.
+For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
 Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, we only admit two-dimensional structures.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by machine learning methods in a later step.
+For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the machine learning methods that are applied in a later stage.
 
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-We note that only tetrahedrally coordinated structures of the given formulas were present after imposing the band gap restriction of $0.5$~eV.
+We note that only tetrahedrally coordinated structures of the given formulas were included in the training set after imposing the band gap restriction of $0.5$~eV.
 
-The candidates labeled as suitable in the intuitive approach contain only compounds that are either elementary (unary) or binary.
-We do not want to discriminate based on the number of elements in a compound, therefore we remove the feature that describes the number of elements in a compound.
-After the three stages, a total of $187$ entries were labeled as suitable candidates.
+After the three screening steps in the intuitive approach, a total of $187$ entries were labeled as suitable candidates for the training set. 
+Notably, the candidates labeled as suitable in the intuitive approach contain only compounds that are either elementary (unary) or binary. 
+We want to avoid discriminating based on the number of elements in a compound, and therefore we remove the feature that describes the number of elements in a compound. 
 %See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the intuitive approach. 
-
-Since the data set constituting suitable candidates in the third approach contains few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
+Since the training set constituting suitable candidates in the third approach contains rather few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
 These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable through the manual screening process.
@@
 The three different approaches to data mining place a particular emphasis on each of their specific goals.
-The Ferrenti approach relies on choosing only elements with spin zero isotopes together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
+The Ferrenti approach relies on choosing only elements with spin zero isotopes and compounds that crystallize in nonpolar spacegroups together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
 Thus, the first approach targets a more narrow prediction space than the second approach does.
@@
 
+Taking a closer look at the training set from the Ferrenti approach, we find that carbon in a diamond-like structure is classified as a suitable candidate.
+This is in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the intuitive approach.
+Interestingly, in the training set from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are labeled as suitable as well.
+All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
+Note that this is the 3C polytype of SiC, meaning that the most quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
+
+In the training set of the Augmented Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The training set includes a larger variety of
+materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
+
 We provide a visualization of each approach's training data as a parallel coordinate plot for a few selected features in Figure~\ref{fig:parallel-coordinates-approaches}.
 Parallel coordinate schemes \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
-The selected features are found on the x-axis, while the y-axis shows the value of the data present.
+The selected features are found on the x-axis, while the y-axis shows the value of the data.
 Thus, parallel coordinate plots can turn many-dimensional data into a compact  two-dimensional representation.
@@
 The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the data sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
+Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
 
@@
 Here, we can begin to deduce some trends, if the findings from the intuitive approach are taken as guidance.
-Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range appear more important.
-Identification of the features that promote quantum compatible characteristics could be crucial for targeted quantum device design based on defect engineering.
+Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
+Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
 
@@
 
-To visualize the complexity of the training sets, we have found the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
-The resulting scatter plots are found in Figure~\ref{fig:2dscatterplotpca}.
-Green squares display suitable candidates and red triangles represent unsuitable candidates.
+To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
+The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca}.
+Green squares and red triangles represent suitable and unsuitable candidates, respectively.
 Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are largely overlapping.
@@
 %Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
-We expect therefore that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the available data sets.
+We expect therefore that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
 
-In the case of the intuitive approach, on the other hand, we can already start to see a trend where the upper left part of the figure is dominated by suitable candidates.
+In the case of the intuitive approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates.
 The unsuitable candidates are similarly restricted to the lower right corner and there appears to be a clear barrier between the two, albeit with some exceptions.
 This indicates that the intuitive approach may be capable of separating materials based on their underlying properties.
-Thus, devising a sound framework for the data mining process is paramount to obtaining a suitable training set for the machine learning methods.
+Thus, devising a logical framework for the data mining process is likely important to obtain a suitable training set for the machine learning methods.
 
@@
     \centering
-    \begin{subfigure}{0.3\textwidth}
+    \begin{subfigure}{0.4\textwidth}
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v2.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v3.pdf}
     \end{subfigure}%
-    \begin{subfigure}{0.3\textwidth}
+    \begin{subfigure}{0.4\textwidth}
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach-v2.pdf}
     \end{subfigure}
-    \begin{subfigure}{0.3\textwidth}
+
+    \begin{subfigure}{0.5\textwidth}
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v2.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v3.pdf}
     \end{subfigure}
@@
 The manual approach for selecting suitable candidates based on experimental findings yields strong indications that a trend does exist and thus is possible to identify.
+This will be an important goal of a future work.
 Importantly, the methodology for selecting candidates as implemented in the intuitive approach can be adapted also to other material systems where a specific set of properties is desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
 
-It is important to note that the constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
+%It is important to note that 
+The constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
 We note that this complexity is not necessarily reflected in the descriptors.
@@
 Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Therefore, we are dependent on that the Materials Project has obtained data with high quality, and we note that it is likely that there are some errors present in our data sets.
+Therefore, we are dependent on that the Materials Project database contains data with high quality, and we note that it is likely that there are some errors present in our data sets.
 
@@
 
-In summary, using various
-data extraction tools for a number of materials science databases, we have obtained databases consisting of over $25.000$ materials.
-The information from the databases has then been converted into nearly $5000$ physics-informed features.
-After these steps with fine-tuning and selection of entries for our data sets we are now ready to apply machine learning methods on the test set in order to classify materials as potential candidates for quantum technologies.
+In summary, using various data extraction tools for a number of materials science databases, we have obtained data sets consisting of over $25.000$ materials.
+The information from these data sets has then been converted into nearly $5000$ physics-informed features.
+After these steps with fine-tuning and selection of entries for our training sets we are now ready to apply machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
 
@@
 Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
-These four machine learning methods were applied to the data sets that were optimized using each of the three approaches (Ferrenti, augmented Ferrenti and intuitive) outlined above.
+These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, augmented Ferrenti and intuitive) outlined above.
 This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
-In this section, we present representative results after applying machine learning methods to the datasets resulting from each of the three data mining approaches.
+In this section, we present representative results after applying machine learning methods to the training sets resulting from each of the three data mining approaches.
 
-Explain the distinction between and definitions of the test and training sets here.
+%MB Here or further down? 
+%I moved it up here from the Comparing the approaches section below, 
+%because I moved the then Fig 5 (the predictions for each model and approach) into the Supplementary 
+\begin{table}[b]
+    \centering 
+    \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
+A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
+    \begin{tabular}{c|c|c|c}
+      & $0.50$ & $0.75$ & $0.85$ \\
+     \hline
+     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
+     Augmented Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
+     Intuitive approach & $214$ & $66$ & $9$ \\
+     \hline
+     All approaches together & $47$ & $6$ & 0 \\
+    \end{tabular}
+    \label{tab:probabilites}
+\end{table}
 
 \subsubsection*{The Ferrenti approach}
+
 We first consider the machine learning classification of the test set derived in the Ferrenti approach.
-Taking a closer look at the training set from the Ferrenti approach, we find that carbon in a diamond-like structure is classified as a suitable candidate. 
-This is in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also the candidates that were manually defined as suitable in the intuitive approach.  
-Interestingly, in the training set from the Ferrenti approach, we also find that carbon in two-dimensional graphite-like structures are labeled as suitable. 
-All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the 3C polytype of SiC, meaning that the most quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
+The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is contained in Figure~6 of the Supplementary Material at \cite{supplementary} for each of the three approaches.
+Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
 
-\input{figures/tikz-plots/prediction-fig.tex}
-
-The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is labeled in Figure~\ref{fig:predictions}(a) for the Ferrenti approach.
-From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates.
-All four methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum cut-off of a prediction to $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates. 
+%MEB We can take this out, I suppose, if we need more space, and put it in Supplementary (I put fig 5 there) 
+From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
+All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off of a prediction to (e.g.) $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see  Table~\ref{tab:qt-materials}) that were present in the training set. 
@@
 For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
-Ideally, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated for a cut-off set to above $0.5$ after applying the ML algorithms.  
-Although this is expected behavior based on the training set, it is not the case. 
+Based on the restrictions we defined initially, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated 
+%for a cut-off set to above $0.5$ 
+after applying the ML algorithms.  
+Although this is expected behavior based on the training set, the trend is not carried over to the predicted data.
 We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
-indicating that the band gap restriction is not recognized as important by the machine learning algorithms. 
-Small band gaps could make it challenging to facilitate deep level defects. 
-On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for some of the materials.
+indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms. 
+This cut-off value was imposed on the training data because small band gaps could make it challenging to facilitate deep level defects \cite{Weber2010}. 
+On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
 
@@
 Next, we turn to the more liberal augmented Ferrenti approach containing a $78 \ \%$ larger amount of materials than the former one. 
-In the training set, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The training set includes a larger variety of
-known 
-%classified 
-suitable candidates compared to the Ferrenti approach due to admitting more elements in the initial restriction.
-However, since we also included a larger band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known
-chemical formula present in the training set.
-
-The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a set of $9227$ predicted suitable candidates.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
 Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physical considerations.
-All four ML algorithms confidently (to probabilities of $83 \ \%$ and $60 \ \%$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of the bonding (see, e.g., Ref.~\cite{Weber2010}).
-Indeed, single-photon emitters with sharp and bright zero phonon lines are uncommon in materials with a strong ionic character. 
+All four ML algorithms confidently (to probabilities of $83 \ \%$ and $60 \ \%$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
 Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the ML methods are not adhering rigidly to the band gap restriction when classifying the materials.
+Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
+As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we are not aware of.
 
 \subsubsection*{The intuitive approach}
-The ML methods that were trained on the data set defined in the intuitive approach predict substantially fewer candidates as compared to the two other approaches. 
+The ML methods that were trained on the data extracted in the intuitive approach predict substantially fewer candidates as compared to the other two approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
@@
 
-%Cut down the amount of information given on perhaps not so suitable candidates, while rather emphasis the good predicted suitable candidates?
+%Cut down the amount of information given on perhaps not so suitable candidates, while rather emphasize the good predicted suitable candidates?
 
-Initially, we consider the materials that were classified as suitable to a degree of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
-The compound BN (mp-$1639$) is already present in the training data as a suitable candidate, and therefore we believe the models recognize this as a suitable candidate with high probability.
-Furthermore, two compositions of CdSe (mp-$2691$ and mp-$1070$) have been predicted as suitable, possibly as a consequence of CdS being present as a suitable candidate in the training set.
-The element S resides in the same group as Se, and the data shows that the two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.6$~eV, respectively, in the MP database.
-Comparing to experiment, high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}, while bulk CdSe has a slightly lower reported band gap of $2.4$~eV \cite{Qutub2012}.
+Initially, we consider the materials that were classified as suitable to a confidence of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+The compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, we believe this is a reason why the models recognize BN  as a suitable candidate with high probability.
+Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
+%The element S resides in the same group as Se, and 
+The two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.6$~eV, respectively, in the MP database.  
+Comparing to experiment, ... 
+%high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}.
+%Bulk CdS has a slightly lower reported band gap of $2.4$~eV \cite{Qutub2012}.
 
@@
 The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
-BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN.
+%BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN. 
 Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
@@
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N is not represented in the MP database and therefore not included in our dataset.
+We note that BC$_3$N was not represented in the MP database at the time of downloading and is therefore not included in our dataset.
 
-The compounds InAs (mp-$20305$), CuI (mp-$22895$ and mp-$569346$) and ZnCd$_3$Se$_4$ (mp-$1078597$) have band gaps of $0.3$, $1.2$ and $1.7$~eV, respectively, and exhibit comparable properties.
-Self-assembled InAs quantum dots, for example, are an exciting possible material to use in quantum technology \cite{Liu2018}.
-To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized and contains the toxic element Cd, which could prove an obstacle for large scale utilization.
-CuI, however, has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to other oxides in the data set than, e.g., the more covalent materials of Si, SiC and  diamond.
-It seems that ionic character alone is not an obstacle if the prediction of CuI proves to be merited.
-It is unknown at this time whether an potential quantum compatible properties of CuI would originate from deep level defects or nanostructuring (quantum dots).
+The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$ and $1.7$~eV, respectively.
+%, and exhibit comparable properties. 
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized. 
+Self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
+CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
+Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the data set than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
+It seems that ionic character alone is not an obstacle for a material to be quantum compatible if the prediction of CuI proves to be merited.
+It is unknown at this time whether any potential quantum compatible properties of CuI would originate from deep level defects or nanostructuring (e.g., quantum dots).
 Note that NaCl was not predicted as suitable for QT in the intuitive approach.
+%and contains the toxic element Cd, which could prove an obstacle for large scale utilization.
 
-Lowering the requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials. 
+Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials. 
 The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
-The list of predicted suitable candidates now includes ternary compounds of the formula ABC$_2$.
-The elements Ga, Cd and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Te, P or As may reside at the C site.
-Most of the predicted compounds include toxic elements with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
-In comparison, the experimentally reported band gap is larger at $2.0$~eV \cite{Xing1989}.
+The list of predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$, in addition to elemental and binary semiconductors, and the nine materials listed above.
+For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
+Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
+In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
 ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate, but it remains to be seen whether the candidate can facilitate the isolated deep energy levels often associated with defects exhibiting quantum compatible properties.
+We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or perhaps be a candidate for nanostructure based QT.
 
-Among the $66$ materials that all models in the intuitive approach agreed on to above $0.75$, we emphasize the presence of Ge, GeC, BP and InP.
+Among the $66$ materials that all models in the intuitive approach agreed on to a $0.75$ confidence level, we emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
@@
 Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
-Consequently, as SiC is widely known as highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
+Consequently, as SiC is widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
 
@@
 Both configurations of BP are nonmagnetic and share several properties with the entries mentioned above; including ...
-The compound is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
+BP is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
 
-Lastly, we will mention the prediction of InP (mp-$966800$) as a suitable candidate.
+Lastly, we will discuss the prediction of InP (mp-$966800$) as a suitable candidate.
 The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
 InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-We underline the possibility of using InP-based quantum dots for QT application as well.
+We underline the possibility of using InP-based quantum dots for QT applications as well.
 
 It is worth mentioning that all models agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list defining the $66$ suitable candidates ($0.75$ cut-off) in the Supplementary Material.
+However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates ($0.75$ cut-off) in the Supplementary Material.
 Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
-Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above the suitability limit and could be an interesting future pathway for investigation.
+Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above a suitability limit of $0.5$ and could be an interesting future pathway for investigation.
 
@@
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
-Its band gap is $2.0$~eV in the MP database with the experimental value being reported as large as $5.6$~eV  \cite{SaumGeorge1959}.
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Ferrenti2020} Ref.~\cite{Ferrenti2020}.
+Its band gap is $2.0$~eV in the MP database with the experimental value being reported from $2.45$~eV (optical band gap) \cite{Ubale2014} up to as large as $5.6$~eV \cite{SaumGeorge1959}.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} Ref.~\cite{Ferrenti2020}.
 We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
@@
 
-\begin{table}[b]
-    \centering 
-    \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
-A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
-    \begin{tabular}{c|c|c|c}
-      & $0.50$ & $0.75$ & $0.85$ \\
-     \hline
-     Ferrenti approach &  $6804$ & $1784$ & $258$  \\
-     Augmented Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
-     Intuitive approach & $214$ & $66$ & $9$ \\
-     \hline
-     All approaches together & $47$ & $6$ & 0 \\
-    \end{tabular}
-    \label{tab:probabilites}
-\end{table}
+As mentioned above, Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates for each of the three approaches as a function of ML model confidence when the four models in an approach agree.
+%A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.
+Comparing the three approaches, we again find that the augmented Ferrenti approach is the least restricted and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
+The Ferrenti approach also admits a large amount of materials through from the training set as compared to the intuitive approach, but the resulting data are otherwise not very different from the augmented version.
+Importantly, by applying the four machine learning methods to the data extracted using the two approaches, we are unable to exactly reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
+This may indicate that the machine learning methods did not recognize the criteria, or that the criteria we set are not, in fact, the most important for QT compatibility.
 
-Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates for each of the three approaches as a function of ML model confidence when the four models in an approach agree.
-%A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.
-Out of the three approaches, we find that the augmented Ferrenti approach is the least restricted approach and admits the most entries.
-The Ferrenti approach also admits a large number of materials into the training set, but the resulting data are otherwise not very different from the augmented version.
-Importantly, by applying the four machine learning methods to the data extracted using the two approaches, we are unable to reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
-Of course, the list of materials proposed by the Ferrenti and augmented Ferrenti approaches is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
+The list of materials predicted by the Ferrenti and augmented Ferrenti approaches is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
-It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but to a lesser extent as compared to the other two approaches.
+It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but to a lesser extent comparing to the other two approaches.
 Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
-Firstly, as mentioned above, it is known that the PBE functional that the Materials Project applies is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
+Firstly, as mentioned above, it is known that the PBE functional employed by the Materials Project calculations is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
 It is therefore possible that the band gap is erroneously not considered an important parameter by the ML methods - or, we may be overestimating the importance of this criterion. 
@@
 %However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
-However, the large overlap of predicted materials between the three approaches (Ferrenti, augmented Ferrenti and intuitive) indicates that at least some of the intended parameters are being recognized as important.
+However, the overlap of predicted materials between the three approaches (Ferrenti, augmented Ferrenti and intuitive) indicates that at least some of the intended parameters are being recognized as important.
 We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the augmented Ferrenti approach. 
@@
 All approaches and their corresponding methods agree on a total of $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+
 The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a $0.5$ cut-off can be found in the Supplementary Material at \cite{supplementary}. 
+Several interesting materials that were also discussed above for the predictions by the intuitive approach are present in this list, including BP, CdSe, BP, GeC, InP and Ge.
+However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
+We note that none of these were admitted through for the intuitive approach for higher confidence cut-offs above $0.75$.
+
+Importantly, there are six materials that all approaches and methods agree on to a $0.75$ confidence level.
+These are ZnGeAs$_2$ (mp-$4008$), CdSnP$_2$ (mp-$5213$), GeSe ($mp-10759$), InP (mp-20351), InP (mp-$966800$) and SiSn (mp-$1009813$).
+We highlight these six compounds, along with the nine predicted by the intuitive approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
 
@@
 
-Among the three approaches to data mining, we find that the materials predicted based on the training set defined in the intuitive approach conform to expectation most closely.
-Figure~\ref{fig:histogram} displays the number of predicted candidate materials as a function of (a) band gap, (b) covalent range and (c) ionic character.
-We observe ...
-%
+Figure~\ref{fig:histogram} displays the number of predicted candidate materials as a function of (a) band gap, (b) covalent range and (c) ionic character. We observe ...
 
@@
 Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the augmented Ferrenti approach, and (iii) the intuitive approach.
-Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision tree, random forest and gradient boost).
+Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision trees, random forests and gradient boosting).
 
-We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled suitable and unsuitable for QT in the two training sets.
+We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
 The stringent restrictions set for the intuitive approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
-
-Notably, our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
+Moreover, the smaller number of materials predicted for the intuitive approach permits manual verification. 
+%Our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
 % MHJ paragraph not concluded \textbf{This manifests in the ML predictions as ...} 
-Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with optimal conditions to divine physics based trends.
+%Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with optimal conditions to divine physics based trends.
 
@@
 Two main routes can be followed to exploit the results.
-One aspect is the pursuit of experimental verification of quantum technology compatible effect in the materials predicted as suitable by the four ML methods.
+One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four ML methods.
 Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest.
@@
 The $+U$ extension is included for several calculations considering specific elements \cite{Stevanovic2012}.
-Data extraction from OQMD was done in february of $2021$.
+Data extraction from OQMD was done in February of $2021$.
 
@@
 %with projector-augmented wave (PAW) potentials 
-to relax twice and optimize the ICSD-structure. Data-extraction was done in the period of january-february of $2021$.
+to relax twice and optimize the ICSD-structure. Data-extraction was done in the period of January-February of $2021$.
 
@@
 We extract the crystallographic information file (CIF) of the crystals from Materials Project, and then use this as input to AFLOW-ML, which then returns an anticipated band gap.
-The process was done during january of $2021$.
+The process was done during January of $2021$.
 
@@
 Add! 
-%M.I.K.
-and M.v.S.
-conceived the main theme of the work.
-S.A., D.P., and M.v.S.
-have carried out the calculations.
-All authors have contributed to the writing of the paper and the analysis of the data.
+%MEB, LV and MHJ conceived the main theme of the work.
+OH developed the programs and performed the bulk of the work.
+All authors have contributed to the writing of the paper and the discussion and analysis of the data.
 

### 2022-01-07 supplementary.tex
Updates from Overleaf

@@
 
+\usepackage{forest}
+\forestset{
+    .style={
+        for tree={
+            base=bottom,
+            child anchor=north,
+            align=center,
+            s sep+=1cm,
+    straight edge/.style={
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -- (.child anchor);}
+    },
+    if n children={0}
+        {tier=word, draw, thick, rectangle}
+        {draw, diamond, thick, aspect=2},
+    if n=1{%
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {Y};}
+        }{
+        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
+        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {N};}
+        }
+        }
+    }
+}
+\tikzset{
+  green arrow/.style={
+    midway,green,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
+    allow upside down
+  },
+  yellow arrow/.style={
+    midway,yellow,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
+    allow upside down
+  },
+  black arrow/.style 2 args={-stealth, shorten >=#1, shorten <=#2},
+  black arrow/.default={1mm}{1mm},
+  tree box/.style={draw, rounded corners, inner sep=1em},
+  node box/.style={white, draw=white, text=black, rectangle, rounded corners},
+}
+
 \newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
@@
 Contents: \\ 
-Supplementary methods --- additional information on the featurization process and implementation of the machine learning models. \\ 
-Supplementary results --- tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches. \\ 
+Supplementary methods --- additional information on the featurization process and optimization of the machine learning models. \\ 
+Supplementary results --- statistics and tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches.
+\\
 Supplementary references.
@@
 
-In the evaluation of the approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
+In the evaluation of the machine learning models for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
 Four different evaluation metrics are applied to each of the four algorithms for each approach.
 
-For random forest, gradient boost, and decision tree, we found that by adjusting most of the available parameters responded to severe overfitting.
+For random forests, gradient boosting, and decision trees, we found that by adjusting most of the available parameters, X responded to severe overfitting.
 Therefore, most parameters are the default values defined by Scikit-learn.
@@
 When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
-Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models, just for logistic regression for one approach.
+Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models, just for one arbitrary machine learning algorithm like logistic regression.
 
+\subsubsection*{Ferrenti approach}
 %Ferrenti 
-We visualize the grid search for the optimal number of principal components for the Ferrenti approach in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
 For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.
-
-In Table~\ref{tab:01-pc}, we find the precise measurements for each of the evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
-The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$.
-For random forest and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boost.
-We find the best performing model is logistic regression, but is dependent on a large amount of principal components.
-
-%Augmented ferrenti (to be continued)
-%Intuitive (to be continued)
-
-\begin{table}[!ht]
-\centering
-\caption{A table of the optimal number of principal components and the respective scores (standard deviation) for the Ferrenti approach, as visualized in the dash-dotted line in figure \ref{fig:01-pca}.}
-\label{tab:01-pc}
-\noindent\makebox[\textwidth]{
-\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
-  \hline
-  \hline
-   Model & PC & Mean test &  Mean precision & Mean recall & mean F1\\
-  \hline
-  LOG & $171$ & $0.98(0.012)$ & $0.98(0.011)$ & $0.99(0.007)$ & $0.99(0.007)$ \\
-  DT & $37$   & $0.77(0.034)$ & $0.84(0.034)$ & $0.85(0.044)$ & $0.84(0.022)$ \\
-  RF & $53$   & $0.87(0.027)$ & $0.88(0.022)$ & $0.98(0.010)$ & $0.93(0.014)$ \\
-  GB & $107$  & $0.92(0.016)$ & $0.92(0.015)$ & $0.98(0.010)$ & $0.95(0.009)$ \\
-  \hline
-\end{tabular}
-}
-\end{table}
 
@@
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall, and F1 scores are based on the test set.
-The number of principal components that explain the $95\%$ accumulated variance is $144$, while the optimal model is found using the F1-score.}}
+Precision, recall, and F$1$ scores are based on the test set.
+The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}}
   \label{fig:01-pca}
@@
 
-\clearpage
+\begin{table}[b]
+\centering
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:01-pca}.}
+\label{tab:01-pc}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Model & PC & Mean test &  Mean precision & Mean recall & mean F1\\
+  \hline
+  LOG & $171$ & $0.98(0.012)$ & $0.98(0.011)$ & $0.99(0.007)$ & $0.99(0.007)$ \\
+  DT & $37$   & $0.77(0.034)$ & $0.84(0.034)$ & $0.85(0.044)$ & $0.84(0.022)$ \\
+  RF & $53$   & $0.87(0.027)$ & $0.88(0.022)$ & $0.98(0.010)$ & $0.93(0.014)$ \\
+  GB & $107$  & $0.92(0.016)$ & $0.92(0.015)$ & $0.98(0.010)$ & $0.95(0.009)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
+In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
+The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$.
+For random forests and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boosting.
+We find the best performing model is logistic regression, but this model is dependent on a large number of principal components.
+
+In Figure~\ref{fig:01-fi}, we visualize how the models interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation.
+To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components needs to be involved.
+We have visualized the first $25$ since this captures the most important information, and we note that most of the important features are found within the first five principal components.
+
+\begin{figure}[ht!]
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/01-ferrenti-approachLOG-final.tex}
+    \label{fig:01-fi-a}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/01-ferrenti-approachDT-final.tex}
+    \label{fig:01-fi-b}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/01-ferrenti-approachRF-final.tex}
+    \label{fig:01-fi-c}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/01-ferrenti-approachGB-final.tex}
+    \label{fig:01-fi-d}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/01-ferrenti-approachPC-final.tex}
+    \label{fig:01-fi-e}
+  \end{subfigure}%
+
+  \caption{Five figures visualizing different parameters for the $25$ most principal components ranked in descending order by the explained variance for the Ferrenti approach.
+The panels show the logistic regression coefficients, decision trees feature importance, random forests feature importance, gradient boosting feature importance, and explained variance that is retained by choosing each of the eigenvectors.
+}
+  \label{fig:01-fi}
+\end{figure}
+
+For logistic regression, we have visualized the mean fitted coefficients and the standard variation in the top panel of Fig.~\ref{fig:01-fi}.
+Large positive or negative coefficients can be considered increasingly important, where positive (negative) coefficients will contribute to making positive (negative) predictions.
+In the three next panels, namely for the models decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
+Importantly, we observe that the single most important feature for all models is the fifth principal component.
+Interestingly, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the
+compound 
+% composition 
+as calculated by OQMD.
+
+After the first ten principal components, we observe that the models adapt the other principal components with varying degrees.
+The coefficients for the case of logistic regression experience large fluctuations, but the three remaining models find the first and second principal components important in addition to the fifth.
+In order of importance, we observe that the second component's largest values correspond to the electronegativity, ionic property, and covalence radius among the elements in the composition.
+The aggregations are either calculated as minimum, mean, standard deviation, or maximum.
+While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
+
+%While the first principal component has by far the largest explained variance, it does not provide any specific information of which features it represents.
+Some of the features represent the period in the periodic table, structural packing efficiency, and atomic weights of the components.
+However, we are unable to confirm the prominent features due to no significant .
+
+%a variety of features are represented, such as the rows that a composition in the periodic table represents, structural packing efficiency and atomic weights of the components, but we are unable to confirm the prominent features due to small variations.
+
+%We note that looking at feature importance can be regarded as misleading for data involving correlated features, but we consider the analysis safe due to the projection of the original data to orthogonal vectors, known as principal components, which results in uncorrelated features.
+%OH: Seb or Oyv, is it correct to say uncorrelated?
+
+\subsubsection*{Augmented Ferrenti approach}
+
+For the augmented Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
+All models experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which is a ratio of $75:25 \ \%$.
+This result comes as a consequence of the models being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
+On the other hand, we find a small precision for the first component since the model predicts many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
+This trend is revealed when looking at the balanced accuracy score.
+For all figures, it remains the lowest score of the evaluation metrics largely due to the inaccuracy of true negatives for the cross-validations.
+%Therefore, one can argue that we should use the balanced accuracy score for evaluation and not the F1 score, but the choice is independent of the evaluation metric since the optimal F1 score is also the optimal balanced accuracy score for all figures.
+
+\begin{table}[b]
+\centering
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the augmented Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
+\label{tab:02-pc}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Model & PC & Mean test &  Mean precision & Mean recall & mean F1\\
+  \hline
+  LOG & $175$ & $0.98(0.008)$ & $0.99(0.004)$ & $0.99(0.004)$ & $0.99(0.003)$ \\
+  DT & $25$   & $0.69(0.034)$ & $0.86(0.015)$ & $0.93(0.021)$ & $0.90(0.008)$ \\
+  RF & $25$   & $0.70(0.028)$ & $0.86(0.011)$ & $1.00(0.003)$ & $0.93(0.006)$ \\
+  GB & $93$   & $0.85(0.025)$ & $0.93(0.011)$ & $0.99(0.004)$ & $0.96(0.007)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
+Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the augmented Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
+Logistic regression performs optimally for many principal components, and is the only model that continues to improve with an increasing number of components.
+The decision trees model exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
+Random forests exhibits fewer fluctuations compared to the decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve after around $100$ principal components.
+
+The optimal hyperparameters are summarized in Table~\ref{tab:02-pc}.
+We find that the logistic regression model with $175$ principal components performs more or less like a perfect classifier with overall high scores.
+The decision trees and random forests models have similar balanced accuracy scores with $0.69$ and $0.70$, respectively, due to challenges associated with predicting true negative labels for $25$ principal components.
+Lastly, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
+
+\begin{figure}[ht!]
+  \begin{subfigure}[b]{1.0\textwidth}
+    \centering
+    \input{figures/optimizing-parameters/label.tex}
+  \end{subfigure}
+\par\bigskip
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/02-augmented-ferrenti-approach-176-LOG.tex}
+    \caption{}
+    \label{fig:q2-LOG}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/02-augmented-ferrenti-approach-176-DT.tex}
+    \caption{}
+    \label{fig:q2-DT}
+  \end{subfigure}
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/02-augmented-ferrenti-approach-176-RF.tex}
+    \caption{}
+    \label{fig:q2-RF}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/02-augmented-ferrenti-approach-176-GB.tex}
+    \caption{}
+    \label{fig:q2-GB}
+  \end{subfigure}
+  \caption{{Four figures displaying hyperparameter search for the augmented Ferrenti approach.
+The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
+Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
+Precision, recall, and F$1$ scores are based on the test set.
+The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}}
+  \label{fig:02-pca}
+\end{figure}
+
+The relevant hyperparameters for the logistic regression model were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
+Smaller regularization values resulted in worse scores, while increasing values did not notably alter the results.
+The decision trees and random forests found an optimal maximum depth of $7$, where smaller values resulted in low precision but high recall.
+Therefore, the choice was made to facilitate a compromise between precision and recall.
+For gradient boosting, we find the optimal maximum depth as $4$ due to a decline in overall metrics for increasing depth except for training accuracy, which could potentially result in overfitting.
+
+The interpretation of feature importance for the augmented Ferrenti approach is substantially more difficult than in the Ferrenti approach.
+We find for logistic regression and decision trees that no feature is different than any other in the cross-validation due to a large variety of accuracy.
+However, we find that random forests and gradient boosting experience the fifth principal component as important.
+Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates the DFT band gap of the elemental solids among the elements in the composition.
+
+\subsubsection*{Intuitive approach}
+
+Lastly, we turn to the intuitive approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set, which was again somewhat imbalanced.
+However, in contrast to the two training sets discussaed above, the majority of the entries was in this case labeled as unsuitable candidates.
+
+The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca}.
+Interestingly, we find that all models experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
+%This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
+
+Logistic regression experiences improvement of all scores for an increasing number of principal components, yet only up $5 \ \%$ in scores compared to the one-dimensional representation of one principal component.
+Thus, one can argue whether the increase in performance is worthwhile, considering a one-dimensional representation with just a few percentage losses of performance.
+However, with multiple principal components, we find the largest increase in precision, which is a sign that the one-dimensional representation tends to wrongly predict candidates as suitable when they are in fact unsuitable.
+The decision trees and the random forests models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger values.
+Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for a few principal components.
+
+\begin{table}[b]
+\centering
+\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the intuitive approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
+\label{tab:03-pca}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Model & PC & Mean test & Mean precision & Mean recall  & mean F1\\
+  \hline
+  LOG & $61$  & $0.99(0.011)$ & $0.97(0.032)$ & $0.99(0.016)$ & $0.98(0.018)$ \\
+  DT & $9$    & $0.96(0.019)$ & $0.95(0.040)$ & $0.95(0.033)$ & $0.95(0.026)$ \\
+  RF & $27$   & $0.98(0.020)$ & $0.97(0.033)$ & $0.97(0.031)$ & $0.97(0.026)$ \\
+  GB & $13$   & $0.97(0.016)$ & $0.96(0.036)$ & $0.97(0.029)$ & $0.96(0.022)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
+\begin{figure}[ht!]
+  \begin{subfigure}[b]{1.0\textwidth}
+    \centering
+    \input{figures/optimizing-parameters/label.tex}
+  \end{subfigure}
+  \par\bigskip
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/03-insightful-approach-176-LOG.tex}
+    \caption{}
+    \label{fig:q3-LOG}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/03-insightful-approach-176-DT.tex}
+    \caption{}
+    \label{fig:q3-DT}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/03-insightful-approach-176-RF.tex}
+    \caption{}
+    \label{fig:q3-RF}
+  \end{subfigure}%
+  \hfill
+  \begin{subfigure}[b]{0.5\textwidth}
+    \input{figures/optimizing-parameters/03-insightful-approach-176-GB.tex}
+    \caption{}
+    \label{fig:q3-GB}
+  \end{subfigure}
+
+  \caption{{Four figures displaying hyperparameter search for the intuitive approach.
+The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
+Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
+Precision, recall, and F$1$-scores are based on the test set.
+The number of principal components that explain the $95 \ \%$ accumulated variance is $103$, while the optimal model is found using the F$1$-score.}}
+  \label{fig:03-pca}
+\end{figure}
+
+The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all models exhibit high evaluation metrics.
+Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with the F$1$-score of $0.98$.
+The decision trees model uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
+
+\begin{figure}[ht!]
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/03-insightful-approachLOG-final-2.tex}
+    \label{fig:03-fi-a}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/03-insightful-approachDT-final-2.tex}
+    \label{fig:03-fi-b}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/03-insightful-approachRF-final-2.tex}
+    \label{fig:03-fi-c}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/03-insightful-approachGB-final-2.tex}
+    \label{fig:03-fi-d}
+  \end{subfigure}%
+
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \input{figures/feature-importance/03-insightful-approachPC-final-2.tex}
+    \label{fig:03-fi-e}
+  \end{subfigure}%
+
+  \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the intuitive approach.
+The panels show the logistic regression coefficients, decision trees feature importance, random forests feature importance, gradient boosting feature importance, and explained variance that is retained by including each of the eigenvectors.
+}
+  \label{fig:03-fi}
+\end{figure}
+
+Lastly, gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$.
+The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations as $400$.
+The decision trees uses a maximum depth of $6$, where larger values increased the training accuracy but not any other metric.
+The maximum depth for the random forests model was set to $6$, and gradient boosting was given a value of $4$.
+
+The intuitive approach differs in many aspects from the Ferrenti and augmented Ferrenti approaches.
+Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and augmented Ferrenti approach, respectively.
+Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
+
+Secondly, we find that the first principal component is by far the most important feature for all models, as visualized in Figure~\ref{fig:03-fi}.
+This is part of the reason why we experience a large accuracy for only a single feature, as seen in Figure~\ref{fig:03-pca}.
+The first principal component's corresponding features are challenging to explain due to small variations of values.
+However, it differs when it comes to which top features the first principal component describes, which includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+
+Thirdly, the intuitive approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the augmented Ferrenti approach.
+We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
+
+\input{figures/tikz-plots/prediction-fig.tex}
 
 \section*{Supplementary results}
-Table~\ref{tab:03-probability-candidates} displays the 66 predicted candidates that all four machine learning models, using the data set derived in the intuitive approach, agreed on with a cut-off set to $0.75$.
+
+\subsection*{Prediction statistics}
+
+Figure~\ref{fig:predictions} provides a visualization of the number of predicted material candidates from the (a) Ferrenti, (b) augmented Ferrenti and (c) intuitive approaches.
+Suitable and unsuitable candidates are marked in green and red, respectively.
+We observe that the number of predicted suitable candidates is similar for the Ferrenti and augmented Ferrenti approaches, albeit higher in the case of the latter, for all four ML models, while the intuitive approach results in a substantially narrower selection of contender materials.
+Note that the confidence cut-off was set to $0.5$.
+
+For the Ferrenti approach, logistic regression finds a total of $12.380$ suitable candidates, while decision trees is the most conservative with $11.315$.
+random forests has the most optimistic estimate with $14.278$, while gradient boosting finds $11.835$ suitable candidates.
+The four ML models agree on $6804$ suitable candidates, however, many of the materials
+are predicted with a confidence similar to that of a coin-flip.
+If we were to raise the minimum bar of a prediction to
+$0.7$, the models would only agree on $3000$ suitable candidates
+
+The perhaps more liberal augmented Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
+Due to the less stringent restrictions compared to the Ferrenti approach, we find the large amount of $9227$ entries that the four models agree on.
+
+The four models predict radically fewer suitable candidates for the intuitive approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The large majority of the unsuitable candidates are predicted with high probability except for the random forests model due to the ensemble of trees.
+All models, however, agree on $214$ suitable candidates.
+
+\subsection*{Predicted materials}
+
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning models, using the training set derived in the intuitive approach, agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
@@
 Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning models and all three approaches agreed upon. 
+%To 0.5 cutoff 
 The list contains $8$ elemental, $29$ binary, and $10$ tertiary compounds.

### 2022-01-17 paper_v2.tex
Updates from Overleaf

--- 2022-01-07 paper.tex
@@
 \author{Oliver Lerst{\o}l Hebnes}
+\affiliation{Your new job} 
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 \begin{abstract}
-
-%Rewrite to avoid plagiarism complaints, original is commented out
-
-%Semiconductor materials provide a compelling platform for quantum technology, and a vast amount of materials and their properties can be found in high-throughput databases.
-However, sifting through tens of thousands of these materials in order to find novel candidates for quantum technology is a challenge.
-Therefore, we provide a framework for the automatic discovery of promising solid-state material hosts using machine learning methods.
 Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
@@
 
-%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25000$ materials.
-Furthermore, we have developed and implemented three data mining approaches, termed \textit{the Ferrenti approach}, \textit{the augmented Ferrenti approach} and \textit{the intuitive approach} for defining three distinct training sets for the supervised machine learning algorithms logistic regression, decision tree, random forest and gradient boost to be trained on.
 Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25.000$ materials.
 The information from the databases was converted into nearly $5000$ physics-informed features.
-Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the augmented Ferrenti approach}, and \textit{the intuitive approach}.
-%Rename insightful approach! To what? Restricted? Experience-based?  
-%Options include stringent, strict, cherry-picked, informed and intuitive. 
+Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
 The three approaches define distinct training sets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
 
-%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set, whereas the restrictions set in the intuitive approach proved suitable.
-All models for the intuitive approach agreed on $214$ predicted candidates, with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC2N, BP, Ge, GeC, InP, and InAs.
-All three approaches and all ML models agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds.
-%We find a lack of consistent results for the Ferrenti approach and the augmented Ferrenti approach due to an overly broad formulation of the training set.
-The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, proved on the other hand more suitable.
-We find that the Ferrenti approach and the augmented Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the intuitive approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-All four machine learning (ML) methods applied to the training set derived using the intuitive approach agreed on a set of $214$ predicted candidate materials.
+We find that the Ferrenti approach and the extended Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
+The restrictions set in the empirical approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+All four machine learning (ML) methods applied to the training set derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
@@
 \section*{Introduction}
-The second quantum revolution is heralding the development of new solutions and devices based on principles from quantum mechanics \cite{Acin2018}.
-Among the promising technologies that are already available we find in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum computer architectures and prototypes.
+Quantum technologies (QT) based on solid state platforms are rapidly gaining in both success and notoriety. 
+Among the promising applications that are already available we find important breakthroughs  such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures.
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
-Recent advances have highlighted the potential of quantum computer architectures to outperform classical systems as a $53$-qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
+Recent advances have highlighted the potential of quantum information processors to outperform classical systems.
+Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
-Simultaneously, the concepts of entanglement and teleportation may enable advanced quantum communication protocols such as quantum cryptography and the quantum internet, spurring further investigations into technologies based on quantum mechanics.
+Simultaneously, the concepts of entanglement and teleportation may eventually facilitate advanced quantum communication protocols such as quantum cryptography and the quantum internet, spurring further investigations into technologies based on quantum mechanics.
 
@@
 
-Several platforms are available for the development of quantum technologies (QT), but the materials and fabrication technologies are less mature than those for, e.g., classical computers and sensors. 
+Several platforms are available for the development of quantum technologies, but the materials and fabrication technologies are less mature than those for, e.g., classical computers and sensors. 
 An important concern in this context is that of scalability. 
-For example, the best performing quantum computer prototypes available today rely on superconducting electronics or trapped ions.
-Both technologies require millikelvin temperatures to operate, fabrication is challenging, and the stability of interactions between qubits is an issue.
+For example, the best performing quantum computer prototypes available today rely on superconducting electronics, requiring millikelvin temperatures to operate, with challenging fabrication and the stability of interactions between qubits is an issue.
 Instead, semiconductors are emerging as a promising alternative platform, offering competitive characteristics combined with the possibility of room temperature operation and mature and scalable material processing and fabrication.
@@
 So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
-The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders in certain areas due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
+The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders especially for quantum communication purposes due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
 However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
-Furthermore, we lack a complete understanding of the requirements for a material to manifest quantum compatible properties,  
-and the selection of known quantum compatible semiconductor host materials is slim.
+Furthermore, we lack a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties,  
+and the selection of known quantum compatible host materials is slim.
 
-The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of how the QT compatible materials properties manifest.
+The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of which material requirements must be met for QT compatible characteristics (e.g.
+single-photon emission and manipulable spin states) to manifest.
 In this context, a framework for dedicated materials search and analysis is needed.
@@
 The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
-Instead, the fourth paradigm  introduces the potential of targeted search for promising material systems to enable properties such as coherent and isolated spin states and indistinguishable single-photon emission to manifest.
+Instead, the fourth paradigm introduces the potential of targeted search for promising material systems in which to expect QT compatible properties.
 Rather than searching through a host of signals for those that match our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
@@
 In this context, we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
-The methodology developed herein can be modified for other material types and application areas provided that a large enough database with relevant theoretical and/or experimental data are available.
+The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data are available.
 
 The approach we have developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
-The Python library for data mining Matminer \cite{Ward2018} was then used for material analysis to featurize the extracted data.
+The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
 An important aspect of our work is the database building and pertinent development of the training sets for machine learning methods.
-We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the augmented Ferrenti approach} and (iii) \emph{the intuitive approach}.
+We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii)
+%Marianne I have now changed augmented Ferrenti to extended Ferrenti 
+\emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
 We find that the former two methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates
+The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and ML methods.
 %(to a $0.5$ cut-off)  
-with examples such as ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs. 
+Example materials include ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs. 
 Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
@@
 The DFT calculations in the database were performed using the Vienna ab initio simulation package (VASP) \cite{Kresse1996} and the Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996} exchange-correlation functional to calculate the electronic structure of the materials.
+We note that despite being immensely successful in describing a number of material properties, PBE is widely known for underestimating the band gap of semiconductors \cite{Freysoldt2014}.
+Therefore, not all properties predicted using the PBE functional are reliable, and the band gaps in particular cannot be trusted in absolute terms.
+Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor properties.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/flow_chart.png}
-    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized dataset with entries from several other databases.
+    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
+    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized data set with entries from several other databases.
 To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects
@@
 %experimental data 
-the ICSD database and have a band gap wider than $0.1$~eV to exclude metallic compounds.
-The Inorganic Crystal Structure Database (ICSD) is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.
+the Inorganic Crystal Structure Database (ICSD) database and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+The ICSD is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.
 %OH: corrected icsd citation to german one (different from nist)
@@
 
-Thereafter, we apply Matminer’s \cite{Ward2018} featurization tools to generate thousands of features from the data. 
+Thereafter, we apply Matminer’s \cite{Ward2018} tools to generate thousands of features from the data. 
 Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
 This transformation is known as generating descriptors
-or features, however, we will in this work adapt the name featurization. 
+or features, however, we will in this work adopt the name featurization. 
 The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project. 
@@
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ features selected as material descriptors in this work can be found in the Supplementary Material at \cite{supplementary}.
+The $39$ featurizers selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
 The selection of features was kept rather wide as we do not precisely know which features best describe a solid state material platform for quantum technology.
+
+%It is important to note that 
+The constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
+Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
+Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
+Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
+Therefore, we are dependent on that the Materials Project database contains data with high quality, but we note that some errors are likely present in our data set.
 
@@
 
-After compiling a data set from the procedure outlined above, we face an obstacle in terms of defining a training set for the machine learning algorithms. This is challenging for two reasons.  
-Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures, few candidate materials are known.
-An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technology.
+After compiling a data set from the procedure outlined above, we must define a training set for the machine learning algorithms. This is challenging for two reasons.  
+Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures, relatively few candidate materials are known to be suitable.
+An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
 Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
-We follow three separate procedures to define a training set consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
+We follow three separate procedures for defining training sets consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
 
@@
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
-        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism.
-Ru and Os are also removed because they only exist in the data as complex cluster structures.
+        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism, Ru and Os are also removed because they only exist in the data as complex cluster structures.
     \end{itemize}
@@
 The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations.
-    \item Ensure that energy above hull is less than $0.2$~eV per atom.
+    \item Ensure that the energy above hull is less than $0.2$~eV per atom.
 \end{enumerate}
 
-The inclusion criteria are targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
+These inclusion criteria are based on the work of \citeauthor{Weber2010} \cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
 In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
-Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable photon emission, non-polar materials are assumed to be preferable.
-The inclusion criteria listed above are based on the work of \citeauthor{Weber2010} \cite{Weber2010}.
+Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon photon emission, non-polar materials are assumed to be preferable.
+%The inclusion criteria listed above are based on the work of \citeauthor{Weber2010} \cite{Weber2010}.
 
@@
 In this context, also the symmetry of the crystalline host may be important.
-Therefore, only phases which take on non polar space groups are considered in this approach.
+Therefore, only phases which take on non-polar space groups are considered in this approach.
 The energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
 
-We then label \textbf{unsuitable} candidates according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} %MHJ need ref here
-that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV (to exclude metals but include lower-band gap semiconductors) as calculated by DFT using the PBE functional, as discussed above.
-The resulting complete training set contains $1581$ materials where %$56 \ \%$ 
-$35 \ \%$
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
+that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
+The resulting complete training set contains $1581$ materials where $35 \ \%$
 are labeled as unsuitable and 
-%$44 \ \%$
-$65 \ \%$
-as suitable for QT applications.
+$65 \ \%$ as suitable for QT applications.
 
-\subsubsection*{The augmented Ferrenti approach}
-In the second approach, we adjust the former one in order to expand the training set beyond practical considerations. This approach is therefore named \emph{the augmented Ferrenti approach}.
+%The training set from the Ferrenti approach reveal that carbon in a diamond-like structure is classified as a suitable candidate, in good agreement with experimental observations, (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
+Interestingly, in the training set from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are labeled as suitable as well.
+All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
+Note that this is the 3C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
 
-In the first approach we included criteria that were not physically motivated, but instead to some extent based on a practical perspective, such as excluding toxic and radioactive elements.
+\subsubsection*{The extended Ferrenti approach}
+In the second approach, we adjust the former one in order to expand the training set beyond practical considerations. This approach is therefore named \emph{the extended Ferrenti approach}.
+
+In the first approach we included criteria that were 
+%not physically motivated, but instead 
+to some extent based on a practical perspective, such as excluding toxic and radioactive elements.
 Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the feasibility of the material to be employed.
-Consequently, in the augmented Ferrenti approach, we remove stage two from the approach above.
+Consequently, in the extended Ferrenti approach, we remove stage two from the approach above.
 Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
 
-The following steps constitute the process of choosing \textbf{suitable} candidates in the \emph{augmented Ferrenti approach}:
+The following steps constitute the process of choosing \textbf{suitable} candidates in the \emph{extended Ferrenti approach}:
 \begin{enumerate}
@@
     \end{itemize}
-    \item Only keep materials that have a band gap larger than $1.5$~eV as calculated by PBE-GGA.
-The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials.
+    \item Only keep materials that have a band gap larger than $1.5$~eV in the MP database.
+The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials in the training set.
     \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
@@
 The result is a somewhat unbalanced training set, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the training set is $78 \ \%$ larger than for the Ferrenti approach with $2141$ suitable and $684$ unsuitable materials.
+However, the training set is $78 \ \%$ larger than for the Ferrenti approach consisting of  $2141$ suitable and $684$ unsuitable materials.
 
-\subsubsection*{The intuitive approach}
+%MB I moved this down to not confuse the order of information 
+% 
+% In the training set of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The training set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
+
+\subsubsection*{The empirical approach}
 The third approach differs substantially from the first two approaches in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview) to pick our promising material host candidates.
 In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
-We therefore name this scheme \emph{the intuitive approach}.
-Due to the concern of having a training set that is too narrow in scope, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+We therefore name this scheme \emph{the empirical approach}.
+Due to the concern of having a training set that is too narrow in scope, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
-Materials where properties like single-photon emission and spin manipulation have been observed but attributed to quantum dots (formed by self-assembly or lithographic structuring) rather than being directly  defect related will also be included in this context.
-The approach to pick \textbf{suitable} candidates can be summed up as;   
+Materials where properties like single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related will also be included in this context.
+
+Table~\ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics (e.g., single-photon emission and coherent spin manipulation).
+The table forms the basis for picking suitable candidates for the empirical approach.
+The properties being studied arise from mechanisms related to, e.g., point defects, bound excitons, and both self-assembled and lithographically structured quantum dots and  nanostructures such as 2D materials.
+Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects or structure related mechanism is still lacking.
+
+%In the empirical approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
+Additionally, we also include materials matching the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
+
+The strategy for picking \textbf{suitable} candidates in the empirical approach can be summed up as;  
 \begin{enumerate}
-    \item Pick candidates that match the formulas in Table~\ref{tab:qt-materials}, or the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} or SiGe \cite{Hardy2019}. 
+    \item Select candidate materials that match the formulas in  Table~\ref{tab:qt-materials}, or the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} and SiGe \cite{Hardy2019}, as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling.
     \item Ensure that the candidates are present in the ICSD database.  
@@
 
-Table~\ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
-In this context, we consider single-photon emission and coherent spin manipulation.
-The table forms the basis for picking suitable candidates for the intuitive approach.
-The properties being studied arise from mechanisms related to, e.g., point defects, bound excitons, and both self-assembled and lithographically structured quantum dots and nanostructures such as 2D materials.
-Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects or structure related mechanism is still lacking.
-In the intuitive approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
-Additionally, we also include materials matching the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
-
 After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
 These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
-We include all of the $202$ structures except for C (mp-568410) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
+We include all of the $202$ structures except for C (mp-$568410$) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
 
 %% OH: Dirty details about suitable materials:
-Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see if the entries have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
 For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
@@
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-We note that only tetrahedrally coordinated structures of the given formulas were included in the training set after imposing the band gap restriction of $0.5$~eV.
+We note that only tetrahedrally coordinated structures of the given formulas were included in the training set after imposing a band gap restriction of $0.5$~eV.
 
-After the three screening steps in the intuitive approach, a total of $187$ entries were labeled as suitable candidates for the training set. 
-Notably, the candidates labeled as suitable in the intuitive approach contain only compounds that are either elementary (unary) or binary. 
+After the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set. 
+Notably, the candidates labeled as suitable in the empirical approach contain only compounds that are either elementary (unary) or binary. 
 We want to avoid discriminating based on the number of elements in a compound, and therefore we remove the feature that describes the number of elements in a compound. 
-%See the Supplementary Material at \cite{supplementary} for a table containing the manually screened materials that were labeled as suitable candidates in the training set for the intuitive approach. 
 Since the training set constituting suitable candidates in the third approach contains rather few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
-These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable through the manual screening process.
+These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
 
@@
 The three different approaches to data mining place a particular emphasis on each of their specific goals.
-The Ferrenti approach relies on choosing only elements with spin zero isotopes and compounds that crystallize in nonpolar spacegroups together with practical filters, while the augmented Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
+The Ferrenti approach relies on choosing only elements with spin zero isotopes and compounds that crystallize in nonpolar spacegroups together with practical filters, while the extended Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
 Thus, the first approach targets a more narrow prediction space than the second approach does.
-However, perhaps the most restricted approach is the intuitive one.
-Since the variety of known suitable materials is substantially more restricted than for the two other approaches, we would expect the intuitive approach to provide an even narrower prediction space.
+However, perhaps the most restricted approach is the empirical one.
+Since the variety of known suitable materials is substantially smaller than for the two other approaches, we would expect the empirical approach to provide an even narrower prediction space.
 %Here, one should keep in mind that ...
 
-Taking a closer look at the training set from the Ferrenti approach, we find that carbon in a diamond-like structure is classified as a suitable candidate.
-This is in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the intuitive approach.
+%MB copied from above  
+Considering the materials present in the training sets of the first two approaches more closely, we find that  carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
 Interestingly, in the training set from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are labeled as suitable as well.
 All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the 3C polytype of SiC, meaning that the most quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
+Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing from the training set.
 Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
+%Extended Ferrenti 
+In the training set of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The training set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
 
-In the training set of the Augmented Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The training set includes a larger variety of
-materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
-
-We provide a visualization of each approach's training data as a parallel coordinate plot for a few selected features in Figure~\ref{fig:parallel-coordinates-approaches}.
+The training data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
 The selected features are found on the x-axis, while the y-axis shows the value of the data.
-Thus, parallel coordinate plots can turn many-dimensional data into a compact  two-dimensional representation.
+Thus, parallel coordinate plots can turn complex many-dimensional data into a compact  two-dimensional representation.
 Due to possible data cluttering, the figure visualizes a random sample of each class (suitable or unsuitable) with an upper limit of $250$ per class with transparent lines.
@@
 
-The Ferrenti approach and the augmented Ferrenti approach share several similarities. 
-Interestingly, we observe that the entries in Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and augmented Ferrenti approaches, despite the more restricted nature of the former.
+The Ferrenti approach and the extended Ferrenti approach share several similarities. 
+Interestingly, we observe that the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
 The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
@@
 
-The biggest difference is found for the intuitive approach.
-The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups - contrarily to the two Ferrenti-based approaches.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the intuitive approach than for the two former ones.
-Here, we can begin to deduce some trends, if the findings from the intuitive approach are taken as guidance.
+The most striking difference is found for the empirical approach.
+The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti-based approaches.
+Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
+Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
 Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
@@
     \centering
-    \begin{subfigure}{1\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{1\textwidth}
+    \begin{subfigure}{0.7\textwidth}
         \centering
@@
 To limit the data cluttering, we have randomly collected up to $250$ entries for each class and made the lines transparent.
-For the intuitive approach, we have used all the $187$ suitable candidates.
+For the empirical approach, we have used all the $187$ suitable candidates.
 The axes show total magnetization (mag) taken from the Materials Project (MP) database along with the space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) extracted from MP.}
@@
 
-To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
-The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca}.
-Green squares and red triangles represent suitable and unsuitable candidates, respectively.
-Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the augmented Ferrenti approaches are largely overlapping.
-The logic behind categorizing materials in  two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca}.
-Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-%Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
-We expect therefore that the two Ferrenti approaches would need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it could prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
-
-In the case of the intuitive approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates.
-The unsuitable candidates are similarly restricted to the lower right corner and there appears to be a clear barrier between the two, albeit with some exceptions.
-This indicates that the intuitive approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important to obtain a suitable training set for the machine learning methods.
-
 \begin{figure}%[h] %!tbp
     \centering
-    \begin{subfigure}{0.4\textwidth}
+    \begin{subfigure}{0.3\textwidth}
         \centering
@@
     \end{subfigure}%
-    \begin{subfigure}{0.4\textwidth}
+    \begin{subfigure}{0.3\textwidth}
         \centering
@@
 
-    \begin{subfigure}{0.5\textwidth}
+    \begin{subfigure}{0.4\textwidth}
         \centering
@@
 Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots.
-Green squares display suitable candidates and red triangles represent unsuitable candidates.}
+Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
     \label{fig:2dscatterplotpca}
@@
 
-It seems likely that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
-Where the intuitive approach takes advantage of the experimental knowledge that is available in the literature, the Ferrenti and augmented Ferrenti schemes rely on assumptions for which material properties are responsible for the desired quantum effects.
+%MB !! Keep this here or move below??  !!
+To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
+The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca}.
+Green squares and red triangles represent suitable and unsuitable candidates, respectively.
+Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the extended Ferrenti approaches are largely overlapping.
+The logic behind categorizing materials in  two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti and extended Ferrenti approaches.
+Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
+%Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
+We expect therefore that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
+
+In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates (green, blue, yellow and black symbols). 
+Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue symbols), silicon carbide (black symbols) and silicon (yellow symbols) are grouped together but each material class is separated in its own region.
+The unsuitable candidates (red squares) are similarly restricted to the lower right corner and there appears to be a clear barrier between the two (suitable and unsuitable), albeit with some exceptions.
+This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
+Thus, devising a logical framework for the data mining process is likely important in order to obtain a suitable training set for the machine learning methods.
+
+%This paragraph is very diffuse and do not really say anything. I propsoe we remove it.
+%It seems probable that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
+Where the empirical approach takes advantage of the experimental and theoretical knowledge that is available in the literature, the Ferrenti and extended Ferrenti schemes rely on assumptions for which material properties are responsible for the desired quantum effects.
 An additional factor to consider is the use of practical considerations (e.g., toxic materials or the availability of spin zero isotopes) when restricting the parameter space for material choice.
-Intriguingly, a much clearer separation is observed for the intuitive approach, where no restrictions were imposed in terms of specific characteristics for the materials, as compared to the two others.
-These observations constitute an important finding of our work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT.
+%Intriguingly, a much clearer separation is observed for the empirical approach, where no restrictions were imposed in terms of specific characteristics for the materials, as compared to the two others.
+%These observations constitute an important finding of our work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT based on a principal components analysis.
 The manual approach for selecting suitable candidates based on experimental findings yields strong indications that a trend does exist and thus is possible to identify.
-This will be an important goal of a future work.
-Importantly, the methodology for selecting candidates as implemented in the intuitive approach can be adapted also to other material systems where a specific set of properties is desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
+%This will be an important goal of a future work. 
+%Importantly, the methodology for selecting candidates as implemented in the empirical approach can be adapted also to other material systems where a specific set of properties is desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
 
-%It is important to note that 
-The constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures.
-We note that this complexity is not necessarily reflected in the descriptors.
-Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
-Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
-Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Therefore, we are dependent on that the Materials Project database contains data with high quality, and we note that it is likely that there are some errors present in our data sets.
+%summary - do we need this? 
+In summary, using various data extraction tools for a number of materials science databases, we have obtained a data set consisting of over $25.000$ materials.
+The information from this data set has then been converted into nearly $5000$ physics-informed features.
+After these steps with fine-tuning and selection of entries for our training sets we are now ready to apply the machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
 
-Another potential source of uncertainty that should be mentioned is the use of the PBE functional for computing the information in the databases employed herein.
-Despite being immensely successful in describing a number of material properties, PBE is widely known for underestimating the band gap of semiconductors \cite{Freysoldt2014}.
-Therefore, not all properties predicted using the PBE functional are reliable, and the band gaps in particular cannot be trusted in absolute terms.
-Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor properties.
+\subsection*{Machine learning and principal component analysis}
 
-In summary, using various data extraction tools for a number of materials science databases, we have obtained data sets consisting of over $25.000$ materials.
-The information from these data sets has then been converted into nearly $5000$ physics-informed features.
-After these steps with fine-tuning and selection of entries for our training sets we are now ready to apply machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
+Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
+These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above.
+This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter  combinations. 
+\textbf{Principal components were found by ...} 
+The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents}. 
+Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four ML models are shown in the Supplementary Material at \cite{supplementary}.
+
+Fig.~\ref{fig:PComponents} displays the principal components as they are sorted in descending order by the explained variance.
+For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
+Importantly, we observe that the single most important feature for all models in the Ferrenti approach is the fifth principal component.
+Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
+The second component's largest values correspond to the
+%electronegativity, ionic property, and covalence radius 
+covalent radius, ionic character and packing efficiency 
+among the elements in the composition. 
+The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
+While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
+
+\begin{figure}[t]
+    \centering
+    %\includegraphics[width=0.9\textwidth]{figures/PC_Ferrenti_intuitive.png}
+    \includegraphics[width=0.9\textwidth]{figures/PCcomponents.pdf}
+    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by the explained variance for (a) the Ferrenti approach and (b) the empirical approach.
+Upper panels show the gradient boosting coefficients and the lower panels show the explained variance that is retained by choosing each of the eigenvectors.
+%\textit{Placeholder figure.}
+    }
+    \label{fig:PComponents}
+\end{figure}
+
+%extended Ferrenti 
+For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
+The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
+We find, for logistic regression and decision trees, that no feature is different than any other in the cross-validation due to a large variety of accuracy.
+However, we find that random forests and gradient boosting experience the fifth principal component as important.
+Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
+
+%empirical approach
+In the case of the empirical approach, in contrast to the Ferrenti based ones, the decision trees and random forests models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger PC values.
+Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components.
+
+The gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$.
+The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches.
+Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
+Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
+Secondly, we find that the first principal component is by far the most important feature for all models in the empirical approach, as visualized in Fig.~\ref{fig:PComponents}(b).
+This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} fur further details).
+The first principal component's corresponding features are challenging to explain due to small variations of values, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+The standard deviation of the radial distribution function appears multiple times in the list of features and appears to be of particular importance. 
+Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti  and $11 \ \%$ for the extended Ferrenti approach.
+We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
+
+Considering the principal components that are deemed important by the three approaches, we find several intriguing differences.
+The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding to matter.
+This is interesting as these features were used as guidance in the initial selection process when forming the training sets.
+The machine learning models appear to recognize at least some of the expected features as important.
+Intriguingly, for the empirical approach, other properties dominate.
+While, e.g., the band gap may still be important, the ML models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In this case, we did not guide the selection process in terms of specific properties, as was done in the Ferrenti based approaches.
+Instead, the ML models appear to be inferring that the common trend among the materials that are empirically known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology} 
-Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
-These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, augmented Ferrenti and intuitive) outlined above.
-This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
-In this section, we present representative results after applying machine learning methods to the training sets resulting from each of the three data mining approaches.
+%In this section, 
+After training the machine learning models using the three data mining approaches the models were employed on the test sets.
+An overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree is summarized in Table~\ref{tab:probabilites}.
 
-%MB Here or further down? 
-%I moved it up here from the Comparing the approaches section below, 
-%because I moved the then Fig 5 (the predictions for each model and approach) into the Supplementary 
 \begin{table}[b]
@@
      Ferrenti approach &  $6804$ & $1784$ & $258$  \\
-     Augmented Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
-     Intuitive approach & $214$ & $66$ & $9$ \\
+     Extended Ferrenti approach &  $9227$ & $4735$  & $2001$  \\ 
+     Empirical approach & $214$ & $66$ & $9$ \\
      \hline
@@
 We first consider the machine learning classification of the test set derived in the Ferrenti approach.
-The number of candidates predicted by each of the four machine learning methods 'Logistic regression', 'Decision trees', 'Random forests' and 'Gradient boosting' is contained in Figure~6 of the Supplementary Material at \cite{supplementary} for each of the three approaches.
-Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
-
+The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is contained in Figure~6 of the Supplementary Material at \cite{supplementary} for each of the three approaches.
 %MEB We can take this out, I suppose, if we need more space, and put it in Supplementary (I put fig 5 there) 
@@
 This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods. 
-%Be careful here - PBE is known for underestimating band gaps. 
 For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
@@
 We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
-indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms. 
-This cut-off value was imposed on the training data because small band gaps could make it challenging to facilitate deep level defects \cite{Weber2010}. 
+indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the PC analysis revealing the band gap as an important feature for the ML classification in the Ferrenti approach.
+%This cut-off value was imposed on the training data because small band gaps could make it challenging to facilitate deep level defects \cite{Weber2010}. 
 On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
 
-\subsubsection*{The augmented Ferrenti approach}
-Next, we turn to the more liberal augmented Ferrenti approach containing a $78 \ \%$ larger amount of materials than the former one. 
+\subsubsection*{The extended Ferrenti approach}
+Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger 
+%amount of materials 
+data set 
+than the Ferrenti approach.  
 The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
-Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physical considerations.
-All four ML algorithms confidently (to probabilities of $83 \ \%$ and $60 \ \%$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physics informed  considerations.
+All four ML algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
@@
 
-\subsubsection*{The intuitive approach}
-The ML methods that were trained on the data extracted in the intuitive approach predict substantially fewer candidates as compared to the other two approaches. 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.50\textwidth]{figures/vesta-images/cubic-5-structures.png}
+    \includegraphics[width=0.23\textwidth]{figures/vesta-images/hex-CdSe-CuI.png}
+    \includegraphics[width=0.16\textwidth]{figures/vesta-images/BC2N.png}
+    \caption{Illustrations of the crystal structures of the $9$ materials predicted by the empirical approach to $0.85$ confidence.
+Three different symmetry categories are clearly observable: (a) cubic, (b) hexagonal and (c) \textit{weird} (orthorombic top, chalcopyrite bottom).
+}
+    \label{fig:vesta-empirical-0p85}
+\end{figure}
+
+\subsubsection*{The empirical approach}
+The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four ML methods agree on a total of $214$ suitable candidates for a $0.5$ cut-off restriction.
+All the four ML methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
 Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
@@
 
-%Cut down the amount of information given on perhaps not so suitable candidates, while rather emphasize the good predicted suitable candidates?
-
-Initially, we consider the materials that were classified as suitable to a confidence of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
-The compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, we believe this is a reason why the models recognize BN  as a suitable candidate with high probability.
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+%include this? 
+The crystal structures of these materials are schematically drawn in Figure~\ref{fig:vesta-empirical-0p85} and grouped into three categories according to whether they are (a) cubic, (b) hexagonal or (c) other.
+%  
+The compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this a partial explanation for why the models recognize BN  as a suitable candidate with high probability.
 Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
 %The element S resides in the same group as Se, and 
-The two compounds of CdSe share similar properties with calculated band gaps of $0.5$~eV and $0.6$~eV, respectively, in the MP database.  
+The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.  
 Comparing to experiment, ... 
@@
 Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-It has similarly been predicted that the diamond-like structure of BC$_3$N can be a prominent spin qubit material host \cite{Wang2020SpinQB}.
+Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.
 By creating a boron (B) vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of downloading and is therefore not included in our dataset.
+We note that BC$_3$N was not represented in the MP database at the time of downloading and is therefore not included in our data set.
 
-The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$ and $1.7$~eV, respectively.
+The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
 %, and exhibit comparable properties. 
@@
 It is unknown at this time whether any potential quantum compatible properties of CuI would originate from deep level defects or nanostructuring (e.g., quantum dots).
-Note that NaCl was not predicted as suitable for QT in the intuitive approach.
-%and contains the toxic element Cd, which could prove an obstacle for large scale utilization.
+Note that NaCl was not predicted as suitable for QT in the empirical approach.
 
-Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials. 
-The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
+Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials for the empirical approach.  
+The full list of these $66$ listings is contained in the Supplementary Material at \cite{supplementary}. 
 The list of predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$, in addition to elemental and binary semiconductors, and the nine materials listed above.
@@
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or perhaps be a candidate for nanostructure based QT.
+We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
 
-Among the $66$ materials that all models in the intuitive approach agreed on to a $0.75$ confidence level, we emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
+Among the $66$ materials that all models in the empirical approach agreed on to a $0.75$ confidence level, we emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
@@
 Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
-Consequently, as SiC is widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
+Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
 
@@
 However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates ($0.75$ cut-off) in the Supplementary Material.
-Due to the labeling of ZnO as a suitable candidate, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
-Removing ZnO from the training set for the intuitive approach might result in fewer or even no oxide compounds being predicted above a suitability limit of $0.5$ and could be an interesting future pathway for investigation.
+Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
+Removing ZnO from the training set for the empirical approach might result in fewer or even no oxide compounds being predicted above a suitability limit of $0.5$ and could be an interesting future pathway for investigation.
 
-In comparison, the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020} suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the dataset resulting from the intuitive approach.
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figures/vesta-images/all-together-vesta-6-mat-all.png}
+    \caption{Illustrations of the crystal structure of the $6$ materials predicted by all approaches to $0.75$ confidence.
+Three different symmetry categories are clearly observable: (a) cubic, (b) hexagonal and (c) tetragonal.
+}
+    \label{fig:vesta-all-0p75}
+\end{figure}
+
+Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the data set resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 
-\begin{figure}%[h] %!tbp
-    \centering
-    \begin{subfigure}{1\textwidth}
-        \centering
-        %\includegraphics[width=1\textwidth]{figures/histograms/01-02-histogram-.pdf}
-        \input{figures/histograms/summary-01-02-03-histogram-bg.tex}
-        \subcaption[]{}
-    \end{subfigure}%
+\subsubsection*{Comparing the approaches}
+Comparing the three approaches (see Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
+The Ferrenti approach also admits a large amount of materials through from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manually verification is achievable.
+Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
-    \begin{subfigure}{1\textwidth}
-        \centering
-        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
-        \input{figures/histograms/summary-01-02-03-histogram-cov.tex}
-        \subcaption[]{}
-    \end{subfigure}
+Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
+We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
+Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
+All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where eight are elementary (unary), $29$ binary, and $10$ tertiary
+(see the Supplementary Material at \cite{supplementary} for the full list). 
+Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, BP, GeC, InP and Ge.
+However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
+We note that none of these were admitted through for the empirical approach when the confidence cut-off was set to $0.75$ or higher.
 
-    \begin{subfigure}{1\textwidth}
-        \centering
-        %\includegraphics[width=1\textwidth]{figures/histograms/03-histogram-.pdf}
-        \input{figures/histograms/summary-01-02-03-histogram-ionic.tex}
-        \subcaption[]{}
-    \end{subfigure}
+Importantly, there are six materials that all approaches and methods agree on to a $0.75$ confidence level.
+These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$), and their crystal structures are visualized in Figure~\ref{fig:vesta-all-0p75}.
+Again, we can distinguish three groupings in crystal structure; cubic, hexagonal and tetragonal. 
+We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
 
-    \caption{Histograms of predicted suitable materials as a function of (a) PBE-calculated band gap from Materials Project, (b) covalent range (Cov range) and (c) maximum ionic character (Ionic char).
-The number of predicted materials are $6804$ for the Ferrenti approach, $9227$ for the augmented Ferrenti approach, and $214$ for the intuitive approach.}
-    \label{fig:histogram}
+\subsection*{Important features for QT}
+
+%histograms 
+\begin{figure}[t]
+    \includegraphics[width=0.45\textwidth]{figures/histograms/new/MP_Eg_count_075.pdf}
+    \includegraphics[width=0.45\textwidth]{figures/histograms/new/IonProperty_max ionic char_count_075.pdf}
+    \includegraphics[width=0.45\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.pdf}
+    \includegraphics[width=0.45\textwidth]{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.pdf}
+    \caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function and (d) standard deviation of the average bond length.
+The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
+The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right.
+}
+    \label{fig:histogram_new}
 \end{figure}
 
-\subsubsection*{Comparing the approaches}
+%Turning to why the specific materials were chosen ... 
+The analysis of the principal components extracted from the ML models revealed that principal component number five was dominant for both the Ferrenti and extended Ferrenti approach.
+This PC includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
+On the other hand, the band gap related features were not important in the dominant PC in the empirical approach, i.e., PC number 1.
+However, Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of MP band gap, and reveals that all approaches predicted a substantial amount of materials with a low band gap.
+Moreover, the distribution of materials that was identified as suitable is broader with respect to the band gap for the Ferrenti approaches as compared to that of the empirical approach; the empirical approach exhibits a sharper peak around $2.5$~eV.
+Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV at the PBE level.
 
-As mentioned above, Table~\ref{tab:probabilites} contains an overview of the number of predicted suitable candidates for each of the three approaches as a function of ML model confidence when the four models in an approach agree.
-%A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.
-Comparing the three approaches, we again find that the augmented Ferrenti approach is the least restricted and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
-The Ferrenti approach also admits a large amount of materials through from the training set as compared to the intuitive approach, but the resulting data are otherwise not very different from the augmented version.
-Importantly, by applying the four machine learning methods to the data extracted using the two approaches, we are unable to exactly reproduce the criteria the approaches are based on, such as band gap restriction or polar space group.
-This may indicate that the machine learning methods did not recognize the criteria, or that the criteria we set are not, in fact, the most important for QT compatibility.
+%Took this out, not correct
+%As mentioned above, the PBE functional employed by the Materials Project calculations is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
+%It is therefore possible that the band gap is erroneously not considered an important parameter by the ML methods - or, we may be overestimating the importance of this criterion. 
+%Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
+%Thus, one can argue that the ML methods are finding other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
+%In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
+Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
+%However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, extended Ferrenti and empirical) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
 
-The list of materials predicted by the Ferrenti and augmented Ferrenti approaches is extensive, whereas the intuitive approach predicts fewer suitable candidates where manually verification is achievable.
-Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+The secondmost important principal component in the Ferrenti approach, PC nr.
+2, encompasses properties such as the covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of these features).
+The maximum ionic character is also deemed an important part of PC2.
+Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionicities for all three approaches - even peaking at a relatively high ionic character of $0.8$.
 
-It is important to note that the intuitive approach also proposed candidates with band gap energies lower than $0.5$~eV, but to a lesser extent comparing to the other two approaches.
-Thus, all three approaches predicted suitable candidates with band gaps lower than the lowest in the training sets.
-Firstly, as mentioned above, it is known that the PBE functional employed by the Materials Project calculations is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
-It is therefore possible that the band gap is erroneously not considered an important parameter by the ML methods - or, we may be overestimating the importance of this criterion. 
-Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
-Thus, one can argue that the ML methods are finding other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
-In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
-Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
-%However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, augmented Ferrenti and intuitive) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
-However, the overlap of predicted materials between the three approaches (Ferrenti, augmented Ferrenti and intuitive) indicates that at least some of the intended parameters are being recognized as important.
-We find that $119$ of the $214$ candidates predicted as suitable by the intuitive approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the augmented Ferrenti approach. 
-Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding methods agree on a total of $47$ potential candidates, where eight are elementary (unary), $29$ binary, and $10$ tertiary.
+The machine learning models in the empirical approach consistently identified the first PC as the predominant one.
+Identifying the single most important feature in this PC proved challenging as it is the combined impact of several features that is important in PC1.
+Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact, as it appears four times in different forms in the top ten list over dominating features.
+One configuration of the standard deviation of the RDF is demonstrated in  Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
+Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
-The list of the $47$ materials agreed on by all ML methods and all three approaches as suitable candidates with a $0.5$ cut-off can be found in the Supplementary Material at \cite{supplementary}. 
-Several interesting materials that were also discussed above for the predictions by the intuitive approach are present in this list, including BP, CdSe, BP, GeC, InP and Ge.
-However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
-We note that none of these were admitted through for the intuitive approach for higher confidence cut-offs above $0.75$.
+The standard deviation (std) of the RDF and average bond length for the three approaches reveals important information about the criteria followed by the ML methods when selecting suitable QT candidates.
+We interpret this feature such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
+Similarly, zero std in the average bond length would mean that all bonds are identical throughout the crystal.
+Intriguingly, the peaks in the distributions of the predicted materials are not found for perfectly symmetric materials with identical bond lengths; instead, some variation in the bond and wavefunction distributions is found to be optimal for a material to be suitable for QT.
+We note that the peaks seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
+The exact degree and type of symmetry is still open to debate and should be studied further.
 
-Importantly, there are six materials that all approaches and methods agree on to a $0.75$ confidence level.
-These are ZnGeAs$_2$ (mp-$4008$), CdSnP$_2$ (mp-$5213$), GeSe ($mp-10759$), InP (mp-20351), InP (mp-$966800$) and SiSn (mp-$1009813$).
-We highlight these six compounds, along with the nine predicted by the intuitive approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
+We note that out of all the feature distributions visualized herein, the largest difference between the Ferrenti approaches and the empirical approach is found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
+This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.
+For the empirical approach, there is a clear peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
 
-\textbf{I am missing a discussion, here or below, on the different ML methods and their different results.
-Which of the four algorithms is best or makes the most sense?
-Please compare either here, or for each of the approaches in the Predictions subsections.
-Data can go in Supplemental.}
+Returning to the predicted materials above, an interesting observation can be made.
+None of the nine materials predicted by the empirical approach with $0.85$ confidence, nor of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
+At most three different elements are present, but the emphasis is clearly on binary compounds.
+This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists, where some variations throughout the crystal in (e.g.) bond length and symmetry, for a material to manifest QT compatible properties.
+Indeed, this is in contrast to the expectations that guided the formulation of the training sets in the Ferrenti and extended Ferrenti approaches.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered instead.
 
-Figure~\ref{fig:histogram} displays the number of predicted candidate materials as a function of (a) band gap, (b) covalent range and (c) ionic character. We observe ...
+Considering our findings in light of the specific defect centers we know to be quantum compatible, we find a fascinating agreement.
+None of the known quantum emitters or spin centers appear in completely uniform systems.
+For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond have exhibited single-photon emission or controllable spin coherence.
+Instead, we find that QT effects often appear after impurities are introduced, as evidenced by the phosphorous impurity in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy an lead-vacancy centers in diamond [REF].
+For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
+While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT  compatible properties to manifest in a semiconductor host.
+
+%NB
 
@@
 We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25.000$ materials.
-Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the augmented Ferrenti approach, and (iii) the intuitive approach.
+Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
 Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision trees, random forests and gradient boosting).
 
-We find that the formulation of the training sets for the Ferrenti and augmented Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
-The stringent restrictions set for the intuitive approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
-Moreover, the smaller number of materials predicted for the intuitive approach permits manual verification. 
+We find that the formulation of the training sets for the Ferrenti and extended Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
+The stringent restrictions set for the empirical approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
+Moreover, the smaller number of materials predicted for the empirical approach permits manual verification. 
 %Our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
@@
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
-Data extraction from Materials Project was performed in december of $2020$ for the Ferrenti and Augmented Ferrenti approach, while in march $2021$ for the intuitive approach.
+Data extraction from Materials Project was performed in december of $2020$ for the Ferrenti and extended Ferrenti approach, while in march $2021$ for the empirical approach.
 Therefore, the two former approaches includes $77$ more materials due to deprecated entries in the Materials Project database.
@@
 They utilize the PBE functional within VASP
-%with projector-augmented wave (PAW) potentials 
+%with projector-extended wave (PAW) potentials 
 to relax twice and optimize the ICSD-structure. Data-extraction was done in the period of January-February of $2021$.

### 2022-01-17 supplementary.tex
Updates from Overleaf

@@
 
-Contents: \\ 
-Supplementary methods --- additional information on the featurization process and optimization of the machine learning models. \\ 
-Supplementary results --- statistics and tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches.
-\\
-Supplementary references.
+\noindent \textbf{Contents:} 
+\begin{itemize}
+    \item \textit{Supplementary methods.} \\   Additional information on the featurization process and optimization of the machine learning models. 
+    \item \textit{Supplementary results.} \\  Statistics and tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches.
+    \item \textit{Supplementary references.}  
+\end{itemize}
 
@@
 \subsection*{Featurization}
-Table~\ref{table:featurizers} contains an overview of this work's chosen 39 features from matminer. The features were selected based on
-the work of
+To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}. 
+Table~\ref{table:featurizers} contains an overview of this work's chosen 39 featurizers from Matminer. The featurization process results in $4876$ descriptors.
+
+The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable potential host.
+Therefore, we strive to collect an achievable quantity of descriptors with the hope of getting wiser in terms of prediction potential materials for quantum technologies.
 
@@
 In the evaluation of the machine learning models for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
-Four different evaluation metrics are applied to each of the four algorithms for each approach.
+Due to imbalanced training data, we apply four different evaluation metrics to each of the four algorithms for each approach.
 
-For random forests, gradient boosting, and decision trees, we found that by adjusting most of the available parameters, X responded to severe overfitting.
+The implementation of the machine learning models was done through the open library of Scikit-learn.
+By adjusting the majority of the hyperparameters in Sciki-learn, we experienced severe overfitting for random forest, gradient boosting, and decision trees.
 Therefore, most parameters are the default values defined by Scikit-learn.
@@
 
-\begin{table}[b]
+\begin{table}[t]
 \centering
@@
 % composition 
-as calculated by OQMD.
+as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
 
@@
 In order of importance, we observe that the second component's largest values correspond to the electronegativity, ionic property, and covalence radius among the elements in the composition.
-The aggregations are either calculated as minimum, mean, standard deviation, or maximum.
+The data originiates from elemental calculatinos from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum.
 While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
@@
 Lastly, we turn to the intuitive approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set, which was again somewhat imbalanced.
-However, in contrast to the two training sets discussaed above, the majority of the entries was in this case labeled as unsuitable candidates.
+However, in contrast to the two training sets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
 
@@
 This is part of the reason why we experience a large accuracy for only a single feature, as seen in Figure~\ref{fig:03-pca}.
-The first principal component's corresponding features are challenging to explain due to small variations of values.
-However, it differs when it comes to which top features the first principal component describes, which includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+The first principal component's corresponding features are challenging to explain due to small variations of values, but we see it including
+%However, it differs when it comes to which top features the first principal component describes, which includes 
+bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 
@@
 
+\subsection*{Feature analysis}
+%Or important features for QT 
+Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML models in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
+The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
+Several observations can be made based on the histograms.
+Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
+
+Firstly, we find that the ...
+
+%histograms 
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ElementProperty_MagpieData range CovalentRadius_count_075.pdf}
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MaximumPackingEfficiency_max packing efficiency_count_075.pdf}
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.pdf}
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.pdf}
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.pdf}
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.pdf} 
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.pdf} 
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_count_075.pdf} 
+    \caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
+Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
+The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
+The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right.
+All panels were taken for a $0.75$ cut-off.
+}
+    \label{fig:histograms_supp}
+\end{figure}
+
+\newpage
+
 \bibliography{apssamp}% Produces the bibliography via BibTeX.

### 2022-01-17 paper_v2.tex
Updates from Overleaf

@@
 Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
-Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
+%Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
 
@@
     \centering
-    \begin{subfigure}{0.7\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.7\textwidth}
+    \begin{subfigure}{0.9\textwidth}
         \centering
@@
     \end{subfigure}
-
     \begin{subfigure}{0.4\textwidth}
@@
 
-%MB !! Keep this here or move below??  !!
-To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors.
-The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca}.
+To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors, labeled E1 and E2.
+The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca} for the three approaches, and the training data of each approach is visualized according to the same model.
+Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of centering the data.
+
 Green squares and red triangles represent suitable and unsuitable candidates, respectively.
@@
 Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-%Nonetheless, we note that the unsuitable candidates appear to be restricted to a certain parameter space while the suitable candidates extend much further.  
 We expect therefore that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
@@
 In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates (green, blue, yellow and black symbols). 
-Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue symbols), silicon carbide (black symbols) and silicon (yellow symbols) are grouped together but each material class is separated in its own region.
+Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
 The unsuitable candidates (red squares) are similarly restricted to the lower right corner and there appears to be a clear barrier between the two (suitable and unsuitable), albeit with some exceptions.
@@
 The information from this data set has then been converted into nearly $5000$ physics-informed features.
-After these steps with fine-tuning and selection of entries for our training sets we are now ready to apply the machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
+After selecting and fine-tuning the entries for our training sets we are now ready to apply the machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
 
@@
 This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+%
+In order to deduce how the different material features are weighted by the four ML models when classifying materials into suitable and unsuitable candidates for QT, we perform a principal component analysis (PCA) for each of the three approaches.
+First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
+Next, machine learning if performed. 
+% 
 In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter  combinations. 
-\textbf{Principal components were found by ...} 
-The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents}. 
+%
+The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
 Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four ML models are shown in the Supplementary Material at \cite{supplementary}.
-
-Fig.~\ref{fig:PComponents} displays the principal components as they are sorted in descending order by the explained variance.
-For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-Importantly, we observe that the single most important feature for all models in the Ferrenti approach is the fifth principal component.
-Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
-The second component's largest values correspond to the
-%electronegativity, ionic property, and covalence radius 
-covalent radius, ionic character and packing efficiency 
-among the elements in the composition. 
-The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
-While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
 
@@
 \end{figure}
+
+Fig.~\ref{fig:PComponents} displays the principal components as they are sorted in descending order by the explained variance.
+For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
+Importantly, we observe that the single most important feature for all models in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
+The second most important PC for the Ferrenti approach is the second one, PC2. 
+The second component's largest values correspond to the 
+%electronegativity, ionic property, and covalence radius 
+covalent radius, ionic character and packing efficiency  
+among the elements in the composition. 
+The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
+While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
 
@@
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
-Secondly, we find that the first principal component is by far the most important feature for all models in the empirical approach, as visualized in Fig.~\ref{fig:PComponents}(b).
+Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in Fig.~\ref{fig:PComponents}(b). 
 This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} fur further details).
@@
 
-Considering the principal components that are deemed important by the three approaches, we find several intriguing differences.
-The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding to matter.
-This is interesting as these features were used as guidance in the initial selection process when forming the training sets.
-The machine learning models appear to recognize at least some of the expected features as important.
+The principal components that are deemed important by the three approaches are distinct on multiple levels.
+The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
+Interestingly, these features were used as guidance in the initial selection process when forming the training sets.
+The machine learning models appear to preserve the criteria imposed in the Ferrenti approaches.
 Intriguingly, for the empirical approach, other properties dominate.
-While, e.g., the band gap may still be important, the ML models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+Rather than focusing on, e.g., the band gap, the ML models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
 In this case, we did not guide the selection process in terms of specific properties, as was done in the Ferrenti based approaches.
-Instead, the ML models appear to be inferring that the common trend among the materials that are empirically known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Instead, the ML models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 We first consider the machine learning classification of the test set derived in the Ferrenti approach.
-The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is contained in Figure~6 of the Supplementary Material at \cite{supplementary} for each of the three approaches.
+The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
 %MEB We can take this out, I suppose, if we need more space, and put it in Supplementary (I put fig 5 there) 
@@
 All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off of a prediction to (e.g.) $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
+If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see  Table~\ref{tab:qt-materials}) that were present in the training set. 
@@
 indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the PC analysis revealing the band gap as an important feature for the ML classification in the Ferrenti approach.
-%This cut-off value was imposed on the training data because small band gaps could make it challenging to facilitate deep level defects \cite{Weber2010}. 
 On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
@@
 Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
-Unfortunately, the ML methods also yield predictions that do not match with what one would expect from physics informed  considerations.
-All four ML algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which we believe is unlikely due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+% rewrite?? 
+However, the ML methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter. 
+% 
+All four ML algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
@@
 Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
-As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we are not aware of.
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.50\textwidth]{figures/vesta-images/cubic-5-structures.png}
-    \includegraphics[width=0.23\textwidth]{figures/vesta-images/hex-CdSe-CuI.png}
-    \includegraphics[width=0.16\textwidth]{figures/vesta-images/BC2N.png}
-    \caption{Illustrations of the crystal structures of the $9$ materials predicted by the empirical approach to $0.85$ confidence.
-Three different symmetry categories are clearly observable: (a) cubic, (b) hexagonal and (c) \textit{weird} (orthorombic top, chalcopyrite bottom).
-}
-    \label{fig:vesta-empirical-0p85}
-\end{figure}
+As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we did not anticipate.
 
@@
 
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.85\textwidth]{figures/vesta-images/fig6-all.png}
+    \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to.
+Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
+}
+    \label{fig:crystalsystems}
+\end{figure}
+
+\begin{table}[b]
+    \centering 
+    \caption{Grouping of predicted materials (above $0.75$ confidence) into the four appearing crystal systems.
+The $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$) are considered.
+}
+    \begin{tabular}{c|c c c c}
+      & Cubic & Hexagonal & Tetragonal & Orthorombic \\
+    \hline 
+    Empirical approach & CuI (mp-$22895$) & CuI (mp-$569346$) & BC$_2$N (mp-$1008523$) & BC$_2$N (mp-$629458$) \\
+    to $0.85$ confidence & CdSe (mp-$2691$) & CdSe (mp-$1070$) & & \\
+     & BN (mp-$1639$) & & & \\
+     & InAs (mp-$20305$) & & & \\
+     & ZnCd$_3$Se$_4$ (mp-$1078597$) & & & \\
+    \hline 
+    All approaches & InP (mp-$20351$) & InP (mp-$966800$) & ZnGeAs$_2$ (mp-$4008$) & \\ 
+    to $0.75$ confidence & GeSe (mp-$10759$) & & CdSnP$_2$ (mp-$5213$) & \\ 
+     & SiSn (mp-$1009813$) & & & \\
+    \end{tabular}
+    \label{tab:crystalsystems}
+\end{table}
+
 Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
-%include this? 
-The crystal structures of these materials are schematically drawn in Figure~\ref{fig:vesta-empirical-0p85} and grouped into three categories according to whether they are (a) cubic, (b) hexagonal or (c) other.
-%  
-The compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this a partial explanation for why the models recognize BN  as a suitable candidate with high probability.
+The nine materials each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
+Figure~\ref{fig:vesta-empirical-0p85} visualizes the four different crystal systems by means of examples and Table~\ref{tab:crystalsystems} categorizes each material according to its point group as listed in the MP database.
+Interestingly, we find that all nine materials are four-fold coordinated, and that the first two lattice vector are identical in all nine cases whereas $c$ may differ.  
+There appears to be a high degree of symmetry present for all materials but we find no elemental and perfectly symmetric semiconductors in the list.
+
+Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this a partial explanation for why the models recognize BN as a suitable candidate with high probability.
 Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
 %The element S resides in the same group as Se, and 
-The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.  
-Comparing to experiment, ... 
+The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively. Comparing to experiment, ... 
 %high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}.
@@
 
-In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the chalcopyrite structured (mp-$1008523$) BC$_2$N.
+In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the tetragonally structured (mp-$1008523$) BC$_2$N.
 The former takes on a polar space group while the latter does not.
@@
 It is unknown at this time whether any potential quantum compatible properties of CuI would originate from deep level defects or nanostructuring (e.g., quantum dots).
-Note that NaCl was not predicted as suitable for QT in the empirical approach.
+NaCl was not predicted as suitable for QT in the empirical approach.
 
 Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials for the empirical approach.  
-The full list of these $66$ listings is contained in the Supplementary Material at \cite{supplementary}. 
+The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
 The list of predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$, in addition to elemental and binary semiconductors, and the nine materials listed above.
 For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
-Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
+Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
 In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
@@
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
+% MB Do we want to emphasize Ge, as we are downplaying the importance of elemental semiconductors? Or, it could contain an impurity
 Ge has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
 Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
+%
 Similar considerations could be made for the case of GeC. 
@@
 BP is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
-
-Lastly, we will discuss the prediction of InP (mp-$966800$) as a suitable candidate.
+Lastly, InP (mp-$966800$) was also predicted as a suitable candidate to $0.75$ confidence.
 The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
@@
 
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.85\textwidth]{figures/vesta-images/all-together-vesta-6-mat-all.png}
-    \caption{Illustrations of the crystal structure of the $6$ materials predicted by all approaches to $0.75$ confidence.
-Three different symmetry categories are clearly observable: (a) cubic, (b) hexagonal and (c) tetragonal.
-}
-    \label{fig:vesta-all-0p75}
-\end{figure}
-
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
@@
 We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
-%\oliver{Maybe also see if other compounds that were present in training set are present in their 541 hosts. }
 
@@
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where eight are elementary (unary), $29$ binary, and $10$ tertiary
+All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
 (see the Supplementary Material at \cite{supplementary} for the full list). 
@@
 
-Importantly, there are six materials that all approaches and methods agree on to a $0.75$ confidence level.
-These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$), and their crystal structures are visualized in Figure~\ref{fig:vesta-all-0p75}.
-Again, we can distinguish three groupings in crystal structure; cubic, hexagonal and tetragonal. 
+Importantly, there are $6$ materials that all approaches and methods agree on to a $0.75$ confidence level.
+These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$).
+Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (see Fig.~\ref{fig:crystalsystems} and Table~\ref{tab:crystalsystems}).
+Some similar trends as for the $9$ materials from the empirical approach are maintained here as well (e.g., the same space groups, only binary or tertiary compounds, $a=b$ for all materials), but fourfold coordination and the bond angle trends are not maintained for all materials.
 We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
@@
 Indeed, this is in contrast to the expectations that guided the formulation of the training sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered instead.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well.
 
@@
 For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond have exhibited single-photon emission or controllable spin coherence.
-Instead, we find that QT effects often appear after impurities are introduced, as evidenced by the phosphorous impurity in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy an lead-vacancy centers in diamond [REF].
+Instead, we find that QT effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy an lead-vacancy centers in diamond [REF].
 For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 

### 2022-01-17 supplementary.tex
Updates from Overleaf

@@
   \end{subfigure}
-
   \begin{subfigure}[b]{0.5\textwidth}
@@
   \end{subfigure}
-  \caption{{Four figures displaying hyperparameter search for the Ferrenti approach.
+  \caption{Four figures displaying hyperparameter search for the Ferrenti approach.
 The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
@@
 Precision, recall, and F$1$ scores are based on the test set.
-The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}}
+The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
   \label{fig:01-pca}
@@
   \end{subfigure}%
-
   \begin{subfigure}[b]{0.5\textwidth}
@@
   \end{subfigure}%
-
   \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the intuitive approach.

### 2022-01-17 paper_v2.tex
Updates from Overleaf

@@
 We find that the Ferrenti approach and the extended Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the empirical approach, which relies exclusively on findings from the literature, predicted substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave a more precise prediction of substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
 All four machine learning (ML) methods applied to the training set derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
-All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
+All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
 of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for futher material explorations towards quantum technology.
@@
 The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and ML methods.
+The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
 %(to a $0.5$ cut-off)  
@@
 
-The information stream in this work can be regarded as many modular parts 
-%connected in logical pieces. 
-%MHJ What do we mean with logical pieces? 
-that are connected. 
-The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}. 
+The information stream in this work can be regarded as many modular parts that are connected. 
+The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}. Moreover, Jupyter notebooks containing the full
+workflow in Python can be found at \cite{Ohebbi2021}.
 Initially, we start by extracting all entries in the Materials Project (MP) database that match a specific query. 
@@
 %experimental data 
-the Inorganic Crystal Structure Database (ICSD) database and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+the Inorganic Crystal Structure Database (ICSD) and have a band gap wider than $0.1$~eV to exclude metallic compounds.
 The ICSD is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.
@@
 The $39$ featurizers selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
-The selection of features was kept rather wide as we do not precisely know which features best describe a solid state material platform for quantum technology.
+The selection of features was kept rather wide as we do not want to make ex-ante assumptions on which features best describe a solid state material platform for quantum technology.
 
@@
 After compiling a data set from the procedure outlined above, we must define a training set for the machine learning algorithms. This is challenging for two reasons.  
-Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures, relatively few candidate materials are known to be suitable.
+Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures [REFS], relatively few candidate materials are known to be suitable.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
@@
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
-        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism, Ru and Os are also removed because they only exist in the data as complex cluster structures.
+        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism, Ru and Os are also excluded because they only exist in the data as complex cluster structures.
     \end{itemize}
@@
 
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD \cite{Allen1987,Zagorac2019} 
 that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database,
+        \item are present in the ICSD,
         \item are calculated to be nonmagnetic. 
@@
     \item Select candidate materials that match the formulas in  Table~\ref{tab:qt-materials}, or the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS \cite{Weber2010} and SiGe \cite{Hardy2019}, as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling.
-    \item Ensure that the candidates are present in the ICSD database.  
+    \item Ensure that the candidates are present in the ICSD.  
     \item Perform a manual screening for appropriate crystallographic structures. 
@@
     \caption{Two-dimensional scatter plots for the three different approaches.
-We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components (PC1 and PC2) of the initial data from the Materials Project query.
+We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
 Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots.
@@
 
-To further illustrate the complexity of the training sets, we have identified the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transformed the training sets according to the corresponding two eigenvectors, labeled E1 and E2.
-The resulting scatter plots are depicted in Figure~\ref{fig:2dscatterplotpca} for the three approaches, and the training data of each approach is visualized according to the same model.
+To illustrate the composition of the training sets we perform a principal component analysis.
+We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transform the training sets according to the corresponding two eigenvectors.
+In essence, we reduce the dimensionality of the training sets in order to visualize them on a piece of paper.
+The result of this procedure is visualized in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
+For the three approaches, and the training data of each approach is visualized according to the same manner.
 Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of centering the data.
@@
 %
-In order to deduce how the different material features are weighted by the four ML models when classifying materials into suitable and unsuitable candidates for QT, we perform a principal component analysis (PCA) for each of the three approaches.
+In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT, we perform a principal component analysis (PCA) for each of the three approaches.
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
-Next, machine learning if performed. 
+Next, we apply the machine learning models. 
 % 
@@
 The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
-Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four ML models are shown in the Supplementary Material at \cite{supplementary}.
+Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four machine learning models are shown in the Supplementary Material at \cite{supplementary}.
 
@@
 Importantly, we observe that the single most important feature for all models in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
-Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
-The second most important PC for the Ferrenti approach is the second one, PC2. 
+Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
+The second most important principal component for the Ferrenti approach is the second one, PC2. 
 The second component's largest values correspond to the 
@@
 %empirical approach
-In the case of the empirical approach, in contrast to the Ferrenti based ones, the decision trees and random forests models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger PC values.
+In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger principal component values.
 Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components.
@@
 The machine learning models appear to preserve the criteria imposed in the Ferrenti approaches.
-Intriguingly, for the empirical approach, other properties dominate.
-Rather than focusing on, e.g., the band gap, the ML models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+For the empirical approach, other properties dominate.
+Rather than focusing on, e.g., the band gap, the machine learning models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
 In this case, we did not guide the selection process in terms of specific properties, as was done in the Ferrenti based approaches.
-Instead, the ML models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Instead, the machine learning models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 After training the machine learning models using the three data mining approaches the models were employed on the test sets.
-An overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree is summarized in Table~\ref{tab:probabilites}.
+An overview of the number of predicted suitable candidates as a function of machine learning model confidence when the four models in an approach agree is summarized in Table~\ref{tab:probabilites}.
 
@@
     \centering 
-    \caption{Overview of the number of predicted suitable candidates as a function of ML model confidence when the four models in an approach agree.
+    \caption{Overview of the number of predicted suitable candidates as a function of machine learning model confidence when the four models in an approach agree.
 A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
@@
 From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.7$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
-We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see  Table~\ref{tab:qt-materials}) that were present in the training set. 
-This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our ML methods. 
-For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
+All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.7$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
+We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see  Table~\ref{tab:qt-materials}) that were present in the training set.
+This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our machine learning methods. 
+For example, the machine learning methods do not perpetuate the band gap restriction from the training set definition. 
 Based on the restrictions we defined initially, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated 
 %for a cut-off set to above $0.5$ 
-after applying the ML algorithms.  
+after applying the machine learning algorithms.  
 Although this is expected behavior based on the training set, the trend is not carried over to the predicted data.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
-indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the PC analysis revealing the band gap as an important feature for the ML classification in the Ferrenti approach.
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four machine learning methods employed herein,
+indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the principal component analysis revealing the band gap as an important feature for the machine learning classification in the Ferrenti approach.
 On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
@@
 than the Ferrenti approach.  
-The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a total of $9227$ predicted suitable candidates.
+The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
 % rewrite?? 
-However, the ML methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter. 
-% 
-All four ML algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+However, the machine learning methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter.
+% 
+All four machine learning algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
-As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we did not anticipate.
+Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented machine learning methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the machine learning methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
+As we based this band gap restriction on assumptions for important material parameters in the QT context, the machine learning methods might be picking up on something we did not anticipate.
 
 \subsubsection*{The empirical approach}
-The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
+The machine learning methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four ML methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
-Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
+All the four machine learning methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
+Although this is comparable to the probability of a coin toss, the agreement of the four machine learning algorithms lends support to the suitability of the $214$ materials. 
 Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$. 
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$.
 The nine materials each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML models after training on the data set resulting from the empirical approach.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning models after training on the data set resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
+We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all machine learning methods in the extended Ferrenti approach.
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
+All approaches and their corresponding machine learning methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
 (see the Supplementary Material at \cite{supplementary} for the full list). 
@@
 %Turning to why the specific materials were chosen ... 
-The analysis of the principal components extracted from the ML models revealed that principal component number five was dominant for both the Ferrenti and extended Ferrenti approach.
-This PC includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-On the other hand, the band gap related features were not important in the dominant PC in the empirical approach, i.e., PC number 1.
-However, Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of MP band gap, and reveals that all approaches predicted a substantial amount of materials with a low band gap.
-Moreover, the distribution of materials that was identified as suitable is broader with respect to the band gap for the Ferrenti approaches as compared to that of the empirical approach; the empirical approach exhibits a sharper peak around $2.5$~eV.
+The analysis of the principal components extracted from the machine learning models revealed that principal component number five was dominant for both the Ferrenti and extended Ferrenti approaches.
+This principal component includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
+On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach, i.e., principal component number 1.
+Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of MP band gap, and reveals that all approaches predicted a substantial amount of materials with a low band gap as suitable.
+Moreover, the distribution of materials that was identified as suitable is rather broad with the Ferrenti based approaches exhibiting a peak around $2.5$~eV.
 Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV at the PBE level. 
-
-%Took this out, not correct
-%As mentioned above, the PBE functional employed by the Materials Project calculations is known to underestimate the band gap of many semiconductors \cite{Freysoldt2014}. 
-%It is therefore possible that the band gap is erroneously not considered an important parameter by the ML methods - or, we may be overestimating the importance of this criterion. 
-%Indeed, we did not find that the band gap was prominent in the principal components, although the band gap could be correlated with other more important features. 
-%Thus, one can argue that the ML methods are finding other patterns that represent a better distinction between suitable and unsuitable candidates in the training sets, resulting in the band gap being redundant.
-%In this context, we also note that the patterns recognized by the ML algorithms are challenging to discern.
-Thus, while we intend for the methods to predict materials for QT, we cannot be certain that this is happening.
-%However, the large degree admittance of materials present in the training set of all three approaches (Ferrenti, extended Ferrenti and empirical) through to the predictions indicates that at least some of the intended parameters are being recognized as important.
-
-The secondmost important principal component in the Ferrenti approach, PC nr.
+The empirical approach shows more scattered data with local maxima around $1$-$2$ and $4$~eV.
+
+The secondmost important principal component in the Ferrenti approach, principal component nr.
 2, encompasses properties such as the covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of these features).
@@
 
-The machine learning models in the empirical approach consistently identified the first PC as the predominant one.
-Identifying the single most important feature in this PC proved challenging as it is the combined impact of several features that is important in PC1.
+The machine learning models in the empirical approach consistently identified the first principal component as the predominant one.
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
 Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact, as it appears four times in different forms in the top ten list over dominating features.
 One configuration of the standard deviation of the RDF is demonstrated in  Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
-Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
-
-The standard deviation (std) of the RDF and average bond length for the three approaches reveals important information about the criteria followed by the ML methods when selecting suitable QT candidates.
+Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+
+The standard deviation (std) of the RDF and average bond length for the three approaches reveals important information about the criteria followed by the machine learning methods when selecting suitable QT candidates.
 We interpret this feature such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
@@
 Intriguingly, the peaks in the distributions of the predicted materials are not found for perfectly symmetric materials with identical bond lengths; instead, some variation in the bond and wavefunction distributions is found to be optimal for a material to be suitable for QT.
-We note that the peaks seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
+%This is in keeping with no elemental semiconductors being present in the top lists of predicted materials above the $0.75$ confidence level. 
+We note that the maxima  in the histograms in Fig.~\ref{fig:histogram_new} seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
 The exact degree and type of symmetry is still open to debate and should be studied further.
 
-We note that out of all the feature distributions visualized herein, the largest difference between the Ferrenti approaches and the empirical approach is found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
+We note that out of all the feature distributions visualized herein, the perhaps largest difference between the Ferrenti approaches and the empirical approach is found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
 This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a clear peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
+For the empirical approach, there is a sharp peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
 
@@
 At most three different elements are present, but the emphasis is clearly on binary compounds.
-This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists, where some variations throughout the crystal in (e.g.) bond length and symmetry, for a material to manifest QT compatible properties.
-Indeed, this is in contrast to the expectations that guided the formulation of the training sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well.
-
-Considering our findings in light of the specific defect centers we know to be quantum compatible, we find a fascinating agreement.
-None of the known quantum emitters or spin centers appear in completely uniform systems.
+This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in (e.g.) bond length and symmetry.
+Indeed, this is
+%in contrast 
+not precisely as expected according 
+to the expectations that guided the formulation of the training sets in the Ferrenti and extended Ferrenti approaches.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered
+%as well. 
+instead.
+
+Considering our findings in light of the specific defect centers we know to be quantum compatible reveals fascinating characteristics.
+None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
 For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond have exhibited single-photon emission or controllable spin coherence.
@@
 Two main routes can be followed to exploit the results.
-One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four ML methods.
+One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four machine learning methods.
 Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest.
@@
 Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap.
-The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
+The accuracy is validated by a five-fold cross-validation process for each machine learning method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
 This work utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
@@
 No. PHY-1404159 and PHY-2013047.
+The work of SGWL and ØSS was supported by the Norwegian Directorate for International Cooperation and Quality Enhancement in Higher Education (DIKU) which supports the Center for Computing in Science Education (CCSE).
 

### 2022-01-19 paper_v2.tex
Updates from Overleaf

@@
 \subsection*{Data Mining}
-
-After compiling a data set from the procedure outlined above, we must define a training set for the machine learning algorithms. This is challenging for two reasons.  
+The complete data set consists of $25.000$ materials.
+A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
+The labeled data are then grouped intro training, test and validation sets for the machine learning models.
+
+Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
 Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures [REFS], relatively few candidate materials are known to be suitable.
@@
 Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
-We follow three separate procedures for defining training sets consisting of materials that are labeled as both suitable and unsuitable candidates for QT.
+We follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
 
@@
 %, and exhibit comparable properties. 
-To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized. 
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, and the MP database lists it as decomposing into ZnSe and CdSe (in the list with two entries). 
 Self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
@@
 NaCl was not predicted as suitable for QT in the empirical approach.
+
+Out of these nine materials we note that both instances of CuI are stated in the MP database to decompose into trigonal CuI, which was not present in our predictions.
+Hexagonal CdSe decomposes into cubic CdSe, the cubic BN decomposes to hexagonal BN (mp-$984$, not in tte predictions), and ZnCd$_3$Se$_4$ decomposes to ZnSe $+$ CdSe.
+Finally, both compounds of the BC$_2$N structure are listed to decompose into hexagonal BN $+$ C.
 
@@
 \subsubsection*{Comparing the approaches}
-Comparing the three approaches (see Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
+Comparing the three approaches (see Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
 The Ferrenti approach also admits a large amount of materials through from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manually verification is achievable.
@@
 Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (see Fig.~\ref{fig:crystalsystems} and Table~\ref{tab:crystalsystems}).
-Some similar trends as for the $9$ materials from the empirical approach are maintained here as well (e.g., the same space groups, only binary or tertiary compounds, $a=b$ for all materials), but fourfold coordination and the bond angle trends are not maintained for all materials.
+We note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
+Some similar trends as for the $9$ materials from the empirical approach are maintained here as well (e.g., the same space groups, only binary or tertiary compounds, $a=b$ for all materials), but fourfold coordination and the bond angle trends are not maintained for all materials (GeSe is sixfold coordinated).
 We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
@@
 
-We note that out of all the feature distributions visualized herein, the perhaps largest difference between the Ferrenti approaches and the empirical approach is found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
+%MB 
+Also discuss max packing efficiencies. Now in Supplementary. Two clear peaks for empirical approach.
+
+We note that out of all the feature distributions visualized herein, the perhaps largest discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
 This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.

### 2022-01-19 supplementary.tex
Updates from Overleaf

@@
   \end{subfigure}%
+
   \begin{subfigure}[b]{0.5\textwidth}
@@
   \end{subfigure}%
+
   \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the intuitive approach.
@@
 
+The empirical approach predicted $9$ materials to a $0.85$ confidence level while all approaches and all ML models agreed on $6$ materials to a degree of $0.75$. 
+A more detailed glance at the features of these materials as listed in the MP database is contained in Table~\ref{tab:materialproperties}. 
+\begin{table}[t]
+    \centering 
+    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$).
+}
+    \begin{tabular}{c|c c c c c c c }
+      & Material & Crystal structure & MP code & Density (g/cm$^3$) & Band gap (eV) & a, b, c (\AA) & $\alpha,\beta,\gamma$ ($^\circ$) \\
+    \hline 
+    Empirical & CdSe & Hexagonal & mp-$1070$ & $5.3$ & $0.6$ & $4.4,4.4,7.2$ & $90,90,120$ \\
+    approach  & CuI & Hexagonal & mp-$569346$ & $5.8$ & $1.2$ & $4.3,4.3,7.0$ & $90,90,120$ \\ 
+    to $0.85$  & CuI & Cubic & mp-$22895$ & $5.8$ & $1.2$ & $4.3,4.3,4.3$ & $60,60,60$  \\ 
+    confidence & CdSe & Cubic & mp-$2691$ & $5.3$ & $0.5$ & $4.4,4.4,4.4$ & $60,60,60$  \\
+     & BN & Cubic & mp-$1639$ & $3.5$ & $4.6$ & $2.6,2.6,2.6$ & $60,60,60$  \\
+     & InAs & Cubic & mp-$20305$ & $5.3$ & $0.3$ & $4.4,4.4,4.4$ & $60,60,60$ \\
+     & ZnCd$_3$Se$_4$ & Cubic & mp-$1078597$ & $5.3$ & $1.7$ & $6.1,6.1,6.1$ & $90,90,90$ \\
+     & BC$_2$N & Tetragonal & mp-$1008523$ & $3.3$ & $1.6$ & $2.62.6,3.7$ & $90,90,90$ \\
+     & BC$_2$N & Orthorombic & mp-$629458$ & $3.4$ & $1.8$ & $2.5,2.6,3.6$ & $90,90,90$ \\
+    \hline 
+    All & CdSnP$_2$ & Tetragonal & mp-$5213$ & $4.6$ & $0.7$ & $7.2,7.2,7.2$ & $131.1,131.1,71.7$ \\
+    approaches & GeSe & Cubic & mp-$10759$ & $5.5$ & $0.4$ & $4.0,4.0,4.0$ & $60,60,60$ \\
+    to $0.75$  & InP & Cubic & mp-$20351$ & $4.6$ & $0.5$ & $4.2,4.2,4.2$ &  $60,60,60$\\ 
+    confidence & InP & Hexagonal & mp-$966800$ & $4.6$ & $0.5$ & $4.2,4.2,6.9$ & $90,90,120$ \\ 
+     & SiSn & Cubic & mp-$1009813$ & $4.4$ & $0.4$ & $4.3,4.3,4.3$ & $60,60,60$ \\
+     & ZnGeAs$_2$ & Tetragonal & mp-$4008$ & $5.2$ & $0.6$ & $7.0,7.0,7.0$ & $131.4,131.4,71.2$ \\
+    \end{tabular}
+    \label{tab:materialproperties}
+\end{table}
+
 \subsection*{Feature analysis}
@@
 Several observations can be made based on the histograms.
-Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
+Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.
 
-Firstly, we find that the ...
+Firstly, we find that the covalent radii of the materials (see Fig.~\ref{fig:histograms_supp}a) distribute with two peaks in the data in all approaches.
+The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar.
+The trend of two data peaks is repeated for the maximum packing efficiency (see Fig.~\ref{fig:histograms_supp}b) but is much more prominent for the empirical approach.
+This indicates that the material density, or in other words the bond length, is an important parameter for QT suitability.
 
@@
     \includegraphics[width=0.4\textwidth]{figures/histograms/new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.pdf} 
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_count_075.pdf} 
+    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_normalized_databackgrund_075.pdf} 
     \caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.

### 2022-01-20 paper_v2.tex
Updates from Overleaf

@@
 We find that the Ferrenti approach and the extended Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave a more precise prediction of substantially fewer candidates, and provided a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+In contrast to the machine learning (ML) methods based on Ferrenti and extended Ferrenti approach that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution.
 All four machine learning (ML) methods applied to the training set derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
-of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for futher material explorations towards quantum technology.
+of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
 
@@
 The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders especially for quantum communication purposes due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
-However, defect based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
+However, semiconductor based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
 Furthermore, we lack a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties,  
@@
 
-The fourth science paradigm of big data driven science presents a significant improvement over the third paradigm focusing on computational science, for instance via density functional theory calculations of different materials properties.
-Instead, the fourth paradigm introduces the potential of targeted search for promising material systems in which to expect QT compatible properties.
-Rather than searching through a host of signals for those that match our criteria, we are now able to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
+The fourth science paradigm of big data driven science cover the potential of targeted search for promising material systems in which to expect QT compatible properties. \textit{referanse her} 
+Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing material properties for a wide range of different systems.
@@
 
-In this work we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
-In this context, we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
+Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
+\textit{En setning om discovery her??}
+In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
 The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data are available.
@@
 We find that the former two methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
-The third approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
+The third and empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
 The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+Importantly, the approach emphasize features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
 %(to a $0.5$ cut-off)  
@@
 Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
-Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures [REFS], relatively few candidate materials are known to be suitable.
+Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures \cite{Bathen2021}[ I.
+Aharonovich, D.
+Englund, M.
+Toth, Nat.
+Photonics 2016, 10, 631], relatively few candidate materials are known to be suitable.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
-Secondly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
+Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
 We follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
@@
 \subsubsection*{The Ferrenti approach}
-The first approach to defining a training set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
-They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials from the Materials Project.
+The first approach to labeling a selection of materials in the data set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project.
 In this framework, we label \textbf{suitable} candidates by the following steps:
@@
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
-        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism, Ru and Os are also excluded because they only exist in the data as complex cluster structures.
+        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism; Ru and Os are also excluded because they only exist in the data set as complex cluster structures.
     \end{itemize}
@@
 Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon photon emission, non-polar materials are assumed to be preferable.
-%The inclusion criteria listed above are based on the work of \citeauthor{Weber2010} \cite{Weber2010}.
 
@@
 In this context, also the symmetry of the crystalline host may be important.
-Therefore, only phases which take on non-polar space groups are considered in this approach.
+Therefore, only phases which take on non-polar space groups are considered as suitable in this approach.
 The energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
@@
 that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
-The resulting complete training set contains $1581$ materials where $35 \ \%$
+The resulting complete set of labeled materials contains $1581$ materials where $35 \ \%$
 are labeled as unsuitable and 
@@
 
-The following steps constitute the process of choosing \textbf{suitable} candidates in the \emph{extended Ferrenti approach}:
+The following steps constitute the process of labeling \textbf{suitable} candidates in the \emph{extended Ferrenti approach}:
 \begin{enumerate}
@@
     \item Only keep materials that have a band gap larger than $1.5$~eV in the MP database.
-The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid including an unfeasible number of candidate materials in the training set.
+The higher band gap requirement (as compared to the Ferrenti approach) is included here %to avoid including an unfeasible number of candidate materials in the training set.
+    to avoid labeling an unfeasibly large number of materials. 
     \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
@@
 For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
-The result is a somewhat unbalanced training set, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the training set is $78 \ \%$ larger than for the Ferrenti approach consisting of  $2141$ suitable and $684$ unsuitable materials.
+The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
+However, the labeled data encompasses $78 \ \%$ more materials than for the Ferrenti approach,  consisting of $2141$ suitable and $684$ unsuitable materials.
 
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of having a training set that is too narrow in scope, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of ending up with too small data sets for training, testing and validation of the machine learning models, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
 These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
-We include all of the $202$ structures except for C (mp-$568410$) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
+We include all of the $202$ structures apart from C (mp-$568410$) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
 
@@
 We add these as suitable candidates.
-Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies, see discussion below.
+Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies.
 For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
@@
 We want to avoid discriminating based on the number of elements in a compound, and therefore we remove the feature that describes the number of elements in a compound. 
-Since the training set constituting suitable candidates in the third approach contains rather few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
+Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
 These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
@@
 %MB copied from above  
-Considering the materials present in the training sets of the first two approaches more closely, we find that  carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
-Interestingly, in the training set from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are labeled as suitable as well.
+%Ferrenti 
+Considering the materials present in the labeled data sets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
+Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
 All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing from the training set.
+Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
+% from the training set. 
 Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.  
@@
 In the training set of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The training set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
-
-The training data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+The labeled data set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the data,
+
+The labeled data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
 The green and red polylines represent suitable and unsuitable candidates, respectively.
-
-The Ferrenti approach and the extended Ferrenti approach share several similarities. 
-Interestingly, we observe that the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
-The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
-
-The most striking difference is found for the empirical approach.
-The entries labeled as suitable candidates do not exhibit any magnetization, even though the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti-based approaches.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
-Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
-%Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
 
@@
 
-To illustrate the composition of the training sets we perform a principal component analysis.
-We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transform the training sets according to the corresponding two eigenvectors.
-In essence, we reduce the dimensionality of the training sets in order to visualize them on a piece of paper.
-The result of this procedure is visualized in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
-For the three approaches, and the training data of each approach is visualized according to the same manner.
+The Ferrenti approach and the extended Ferrenti approach share several similarities.
+For example, the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
+The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
+Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
+
+The most striking difference is found for the empirical approach.
+The entries labeled as suitable candidates do not exhibit any magnetization, and the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti-based approaches.
+Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
+Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
+Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
+%Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
+
+To illustrate the composition of the labeled data we perform a principal component analysis.
+We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transform the three labeled data sets according to the corresponding two eigenvectors.
+In essence, we reduce the dimensionality of the labeled data in order to visualize them.
+The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
 Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of centering the data.
-
-Green squares and red triangles represent suitable and unsuitable candidates, respectively.
+Red triangles represent unsuitable candidates while colored symbols (green, blue, black and yellow) represent suitable candidates. 
 Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the extended Ferrenti approaches are largely overlapping. 
@@
 
-In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates (green, blue, yellow and black symbols). 
+In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates (green, blue, yellow and black symbols), while the unsuitable candidates (red triangles) are similarly restricted to the lower right corner, albeit with some exceptions.
 Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
-The unsuitable candidates (red squares) are similarly restricted to the lower right corner and there appears to be a clear barrier between the two (suitable and unsuitable), albeit with some exceptions.
 This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain a suitable training set for the machine learning methods.
+Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable data sets for training, testing and validation of the machine learning methods.
 
@@
 The information from this data set has then been converted into nearly $5000$ physics-informed features.
-After selecting and fine-tuning the entries for our training sets we are now ready to apply the machine learning methods on the test set in order to classify materials as potential candidates for quantum technology applications.
+After selecting and fine-tuning the entries for our labeled data sets we are now ready to train the ML methods and apply them to the test set in order to classify materials as potential candidates for quantum technology applications.
 
@@
 %
-The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
+Figure~\ref{fig:PComponents} visualizes different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
+%The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
 Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four machine learning models are shown in the Supplementary Material at \cite{supplementary}.
 
+Fig.~\ref{fig:PComponents}(a) displays the principal components as they are sorted in descending order by the explained variance.
+For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
+For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$ (not shown).
+In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger principal component values.
+Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components.
+
 \begin{figure}[t]
     \centering
-    %\includegraphics[width=0.9\textwidth]{figures/PC_Ferrenti_intuitive.png}
-    \includegraphics[width=0.9\textwidth]{figures/PCcomponents.pdf}
-    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by the explained variance for (a) the Ferrenti approach and (b) the empirical approach.
-Upper panels show the gradient boosting coefficients and the lower panels show the explained variance that is retained by choosing each of the eigenvectors.
-%\textit{Placeholder figure.}
+    \includegraphics[width=0.9\textwidth]{figures/PC_Ferrenti_empirical.png}
+    %\includegraphics[width=0.9\textwidth]{figures/PCcomponents.pdf}
+    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
+    \textit{Placeholder figure.} 
     }
@@
 
-Fig.~\ref{fig:PComponents} displays the principal components as they are sorted in descending order by the explained variance.
-For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-Importantly, we observe that the single most important feature for all models in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Fig.~\ref{fig:PComponents}(b) reveals that the single most important feature for all models in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
@@
 %extended Ferrenti 
-For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
 The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
@@
 %empirical approach
-In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger principal component values.
-Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components.
-
-The gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
 The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
-Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
+Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
+We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
-Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in Fig.~\ref{fig:PComponents}(b). 
+Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b). 
 This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} fur further details).
-The first principal component's corresponding features are challenging to explain due to small variations of values, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 The standard deviation of the radial distribution function appears multiple times in the list of features and appears to be of particular importance. 
@@
 The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
-Interestingly, these features were used as guidance in the initial selection process when forming the training sets.
-The machine learning models appear to preserve the criteria imposed in the Ferrenti approaches.
-For the empirical approach, other properties dominate.
+Notably, these features were used as guidance in the initial selection process when forming the training sets.
+Thus, the machine learning models appear to preserve the criteria imposed in the Ferrenti approaches.
+For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate.
 Rather than focusing on, e.g., the band gap, the machine learning models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In this case, we did not guide the selection process in terms of specific properties, as was done in the Ferrenti based approaches.
-Instead, the machine learning models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+In this approach, the machine learning models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 %In this section, 
-After training the machine learning models using the three data mining approaches the models were employed on the test sets.
+After training the machine learning models using parts of the data labeled during the three data mining approaches, the models were employed on the test sets. 
+The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
 An overview of the number of predicted suitable candidates as a function of machine learning model confidence when the four models in an approach agree is summarized in Table~\ref{tab:probabilites}.
 
-\begin{table}[b]
+\begin{table}[t]
     \centering 
@@
 We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
-The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
-%MEB We can take this out, I suppose, if we need more space, and put it in Supplementary (I put fig 5 there) 
-From the training set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
+From the labeled data set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
 All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
 If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.7$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
-We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see  Table~\ref{tab:qt-materials}) that were present in the training set.
-This can allow materials with unfortunate structures to be labeled as suitable candidates by all of our machine learning methods. 
+We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
+This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our machine learning methods. 
 For example, the machine learning methods do not perpetuate the band gap restriction from the training set definition. 
@@
 after applying the machine learning algorithms.  
-Although this is expected behavior based on the training set, the trend is not carried over to the predicted data.
+Although this is expected behavior based on the data labeling process, the trend is not carried over to the predicted data.
 We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four machine learning methods employed herein,
-indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the principal component analysis revealing the band gap as an important feature for the machine learning classification in the Ferrenti approach.
+indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
 On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
@@
 Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger 
-%amount of materials 
-data set 
+amount of labeled data  
 than the Ferrenti approach.  
-The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the training set, where they all agree on a total of $9227$ predicted suitable candidates.
-Comparing to the training set reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
+The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled data set, where they all agree on a total of $9227$ predicted suitable candidates.
+Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
 % rewrite?? 
@@
 % 
-All four machine learning algorithms confidently (to confidences of $0.83$ and $0.60$ for two different configurations) predict NaCl as a suitable candidate, which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+All four machine learning algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations,  which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
@@
 Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
+Increasing the confidence cut-off to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
 
@@
 Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
+The viewpoints for all materials are down along the $c$ axis.
 }
@@
 
+%\begin{table}[b]
+ %   \centering 
+ %   \caption{Grouping of predicted materials (above $0.75$ confidence) into the four appearing crystal systems.
+The $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$) are considered.
+}
+ %   \begin{tabular}{c|c c c c}
+ %     & Cubic & Hexagonal & Tetragonal & Orthorombic \\
+ %   \hline 
+ %   Empirical approach & CuI (mp-$22895$) & CuI (mp-$569346$) & BC$_2$N (mp-$1008523$) & BC$_2$N (mp-$629458$) \\
+ %   to $0.85$ confidence & CdSe (mp-$2691$) & CdSe (mp-$1070$) & & \\
+ %    & BN (mp-$1639$) & & & \\
+ %    & InAs (mp-$20305$) & & & \\
+ %    & ZnCd$_3$Se$_4$ (mp-$1078597$) & & & \\
+ %   \hline 
+ %   All approaches & InP (mp-$20351$) & InP (mp-$966800$) & ZnGeAs$_2$ (mp-$4008$) & \\ 
+ %   to $0.75$ confidence & GeSe (mp-$10759$) & & CdSnP$_2$ (mp-$5213$) & \\ 
+ %    & SiSn (mp-$1009813$) & & & \\
+ %   \end{tabular}
+ %   \label{tab:crystalsystems}
+%\end{table}
+
 \begin{table}[b]
     \centering 
-    \caption{Grouping of predicted materials (above $0.75$ confidence) into the four appearing crystal systems.
-The $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$) are considered.
-}
-    \begin{tabular}{c|c c c c}
-      & Cubic & Hexagonal & Tetragonal & Orthorombic \\
+    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$).
+Compounds marked by an asterix are marked as unstable upon tranformation into other phases in the Materials Project database.
+}
+    \begin{tabular}{c|c c c c c c c }
+      & Material & Crystal structure & MP code & Density (g/cm$^3$) & Band gap (eV) & a, b, c (\AA) & $\alpha,\beta,\gamma$ ($^\circ$) \\
     \hline 
-    Empirical approach & CuI (mp-$22895$) & CuI (mp-$569346$) & BC$_2$N (mp-$1008523$) & BC$_2$N (mp-$629458$) \\
-    to $0.85$ confidence & CdSe (mp-$2691$) & CdSe (mp-$1070$) & & \\
-     & BN (mp-$1639$) & & & \\
-     & InAs (mp-$20305$) & & & \\
-     & ZnCd$_3$Se$_4$ (mp-$1078597$) & & & \\
+    Empirical & CdSe & Hexagonal & mp-$1070$ & $5.3$ & $0.6$ & $4.4,4.4,7.2$ & $90,90,120$ \\
+    approach  & CuI & Hexagonal & mp-$569346$ & $5.8$ & $1.2$ & $4.3,4.3,7.0$ & $90,90,120$ \\ 
+    to $0.85$  & CuI & Cubic & mp-$22895$ & $5.8$ & $1.2$ & $4.3,4.3,4.3$ & $60,60,60$  \\ 
+    confidence & CdSe & Cubic & mp-$2691$ & $5.3$ & $0.5$ & $4.4,4.4,4.4$ & $60,60,60$  \\
+     & BN & Cubic & mp-$1639$ & $3.5$ & $4.6$ & $2.6,2.6,2.6$ & $60,60,60$  \\
+     & InAs & Cubic & mp-$20305$ & $5.3$ & $0.3$ & $4.4,4.4,4.4$ & $60,60,60$ \\
+     & ZnCd$_3$Se$_4$ & Cubic & mp-$1078597$ & $5.3$ & $1.7$ & $6.1,6.1,6.1$ & $90,90,90$ \\
+     & BC$_2$N & Tetragonal & mp-$1008523$ & $3.3$ & $1.6$ & $2.6,2.6,3.7$ & $90,90,90$ \\
+     & BC$_2$N & Orthorombic & mp-$629458$ & $3.4$ & $1.8$ & $2.5,2.6,3.6$ & $90,90,90$ \\
     \hline 
-    All approaches & InP (mp-$20351$) & InP (mp-$966800$) & ZnGeAs$_2$ (mp-$4008$) & \\ 
-    to $0.75$ confidence & GeSe (mp-$10759$) & & CdSnP$_2$ (mp-$5213$) & \\ 
-     & SiSn (mp-$1009813$) & & & \\
+    All & CdSnP$_2$ & Tetragonal & mp-$5213$ & $4.6$ & $0.7$ & $7.2,7.2,7.2$ & $131.1,131.1,71.7$ \\
+    approaches & GeSe & Cubic & mp-$10759$ & $5.5$ & $0.4$ & $4.0,4.0,4.0$ & $60,60,60$ \\
+    to $0.75$  & InP & Cubic & mp-$20351$ & $4.6$ & $0.5$ & $4.2,4.2,4.2$ &  $60,60,60$\\ 
+    confidence & InP & Hexagonal & mp-$966800$ & $4.6$ & $0.5$ & $4.2,4.2,6.9$ & $90,90,120$ \\ 
+     & SiSn & Cubic & mp-$1009813$ & $4.4$ & $0.4$ & $4.3,4.3,4.3$ & $60,60,60$ \\
+     & ZnGeAs$_2$ & Tetragonal & mp-$4008$ & $5.2$ & $0.6$ & $7.0,7.0,7.0$ & $131.4,131.4,71.2$ \\
     \end{tabular}
-    \label{tab:crystalsystems}
+    \label{tab:materialproperties}
 \end{table}
@@
 The nine materials each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
-Figure~\ref{fig:vesta-empirical-0p85} visualizes the four different crystal systems by means of examples and Table~\ref{tab:crystalsystems} categorizes each material according to its point group as listed in the MP database.
-Interestingly, we find that all nine materials are four-fold coordinated, and that the first two lattice vector are identical in all nine cases whereas $c$ may differ.  
-There appears to be a high degree of symmetry present for all materials but we find no elemental and perfectly symmetric semiconductors in the list.
+Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems using examples and  Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
+Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
+There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.
 
@@
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of downloading and is therefore not included in our data set.
+We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our data set.
 
@@
 %, and exhibit comparable properties. 
-To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, and the MP database lists it as decomposing into ZnSe and CdSe (in the list with two entries). 
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized. 
+%, and the MP database lists it as unstable upon decomposition into ZnSe and CdSe (in the list with two entries). 
 Self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
@@
 Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the data set than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
-It seems that ionic character alone is not an obstacle for a material to be quantum compatible if the prediction of CuI proves to be merited.
+The presence of CuI in two configurations  proposes that ionic character alone is not an obstacle for a material to be quantum compatible if the prediction of CuI proves to be merited.
 It is unknown at this time whether any potential quantum compatible properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
@@
 Out of these nine materials we note that both instances of CuI are stated in the MP database to decompose into trigonal CuI, which was not present in our predictions.
-Hexagonal CdSe decomposes into cubic CdSe, the cubic BN decomposes to hexagonal BN (mp-$984$, not in tte predictions), and ZnCd$_3$Se$_4$ decomposes to ZnSe $+$ CdSe.
+Hexagonal CdSe decomposes into cubic CdSe (in the list of $9$), the cubic BN decomposes to hexagonal BN (mp-$984$, not in the predictions), and ZnCd$_3$Se$_4$ decomposes to ZnSe $+$ CdSe (in the list).
 Finally, both compounds of the BC$_2$N structure are listed to decompose into hexagonal BN $+$ C.
@@
 
-Among the $66$ materials that all models in the empirical approach agreed on to a $0.75$ confidence level, we emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
+Among the $66$ materials that all models in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
 Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
@@
 
-It is worth mentioning that all models agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates ($0.75$ cut-off) in the Supplementary Material.
+We note that all ML models in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ cut-off.
 Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
@@
 Its band gap is $2.0$~eV in the MP database with the experimental value being reported from $2.45$~eV (optical band gap) \cite{Ubale2014} up to as large as $5.6$~eV \cite{SaumGeorge1959}.
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by  \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} Ref.~\cite{Ferrenti2020}.
-We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as a promising host material in this respect.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by  \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as another promising host material in this respect.
 
@@
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding machine learning methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
+All approaches and their corresponding machine learning models agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
 (see the Supplementary Material at \cite{supplementary} for the full list). 
@@
 These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$).
-Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (see Fig.~\ref{fig:crystalsystems} and Table~\ref{tab:crystalsystems}).
-We note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
-Some similar trends as for the $9$ materials from the empirical approach are maintained here as well (e.g., the same space groups, only binary or tertiary compounds, $a=b$ for all materials), but fourfold coordination and the bond angle trends are not maintained for all materials (GeSe is sixfold coordinated).
+Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal.
+See Fig.~\ref{fig:crystalsystems} for illustration of the crystal systems and Table~\ref{tab:materialproperties} for an overview of the corresponding material properties.
+Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
+We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are present, the materials take on only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP (unstable).
+However, four-fold coordination and the bond angle trends are not maintained for all materials (GeSe is six-fold coordinated).
 We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
@@
 %Turning to why the specific materials were chosen ... 
-The analysis of the principal components extracted from the machine learning models revealed that principal component number five was dominant for both the Ferrenti and extended Ferrenti approaches.
+The analysis of the principal components extracted from the machine learning models revealed that eigenvector number five was dominant for both the Ferrenti and extended Ferrenti approaches.
 This principal component includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach, i.e., principal component number 1.
-Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of MP band gap, and reveals that all approaches predicted a substantial amount of materials with a low band gap as suitable.
+On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach, i.e., principal component number one.
+Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of  band gap (as listen in the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap as suitable.
 Moreover, the distribution of materials that was identified as suitable is rather broad with the Ferrenti based approaches exhibiting a peak around $2.5$~eV.
 Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV at the PBE level. 
-The empirical approach shows more scattered data with local maxima around $1$-$2$ and $4$~eV.
-
-The secondmost important principal component in the Ferrenti approach, principal component nr.
-2, encompasses properties such as the covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of these features).
-The maximum ionic character is also deemed an important part of PC2.
-Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionicities for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+The empirical approach exhibits a more scattered data distribution with local maxima around $1$-$2$ and $4$~eV.
+
+The secondmost important principal component in the Ferrenti approach, principal component number 2, encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
+%The maximum ionic character is also deemed an important part of PC2. 
+Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters  for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+Moreover, we find that the covalent radii of the materials (see the Supplementary Material) distribute with two peaks in the data in all approaches. 
+%The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar. 
+The trend of two data peaks is repeated for the maximum packing efficiency  but is much more prominent for the empirical approach.
+This indicates that the material density, or in other words the bond length, is an important parameter for QT suitability.
 
 The machine learning models in the empirical approach consistently identified the first principal component as the predominant one.
-Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important, as discussed above.
 Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact, as it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in  Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
-Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
-
-The standard deviation (std) of the RDF and average bond length for the three approaches reveals important information about the criteria followed by the machine learning methods when selecting suitable QT candidates.
-We interpret this feature such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
+One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material \cite{supplementary}.
+Notably, substantial discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation in the radial distribution function.
+This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.
+For the empirical approach, there is a sharp peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
+
+We interpret the standard deviation (std) of the RDF such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
 Similarly, zero std in the average bond length would mean that all bonds are identical throughout the crystal.
@@
 %This is in keeping with no elemental semiconductors being present in the top lists of predicted materials above the $0.75$ confidence level. 
-We note that the maxima  in the histograms in Fig.~\ref{fig:histogram_new} seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
+Note that the maxima  in the histograms in Fig.~\ref{fig:histogram_new} seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
 The exact degree and type of symmetry is still open to debate and should be studied further.
 
-%MB 
-Also discuss max packing efficiencies. Now in Supplementary. Two clear peaks for empirical approach.
-
-We note that out of all the feature distributions visualized herein, the perhaps largest discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation in the radial distribution function (see Fig.~\ref{fig:histogram_new}c).
-This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a sharp peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
-
-Returning to the predicted materials above, an interesting observation can be made.
-None of the nine materials predicted by the empirical approach with $0.85$ confidence, nor of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
+Interestingly, none of the nine materials predicted by the empirical approach with $0.85$ confidence, nor of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
 At most three different elements are present, but the emphasis is clearly on binary compounds.
@@
 not precisely as expected according 
-to the expectations that guided the formulation of the training sets in the Ferrenti and extended Ferrenti approaches.
+to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
 Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered
@@
 
+%MB 
+%Also discuss max packing efficiencies. Now in Supplementary. Two clear peaks for empirical approach.
+
+Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+
 Considering our findings in light of the specific defect centers we know to be quantum compatible reveals fascinating characteristics.
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
-For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond have exhibited single-photon emission or controllable spin coherence.
+For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
 Instead, we find that QT effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy an lead-vacancy centers in diamond [REF].
@@
 
-%NB
-
 \section*{Discussion} 
@@
 Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
-Three distinct training sets were defined for four different machine learning algorithms (logistic regression, decision trees, random forests and gradient boosting).
+Three distinct sets of labeled data were defined for training, testing and validation of four different machine learning algorithms (logistic regression, decision trees, random forests and gradient boosting).
 
@@
 Moreover, the smaller number of materials predicted for the empirical approach permits manual verification.
-%Our results show that including impractical materials (e.g., toxic, radioactive and without spin-zero isotopes) in the training set is vital for defining a suitable training set. 
-% MHJ paragraph not concluded \textbf{This manifests in the ML predictions as ...} 
-%Such materials can be eliminated based on practical considerations at a later stage but should be included initially in order to provide the ML methods with optimal conditions to divine physics based trends.
+
+Discuss the new findings from the ML here, related to features. Perhaps move down from above.
+
+%NB 
+Discuss suitability of ML methods here.
 
@@
 \subsection*{Databases}
-The Materials Project \cite{Jain2013, Jain2018} is an open-source project based on the Vienna Ab Initio Package (VASP) \cite{Kresse1996}.
+The Materials Project \cite{Jain2013, Jain2018} is an open-source project containing ground state properties of materials calculated using Density functional theory (DFT) [REF] as implemented in the Vienna Ab initio Simulation Package (VASP) \cite{Kresse1996}.
 The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional is used to calculate band structures, while for transition metals, a $+U$ correction is applied to correct for correlation effects \cite{Wang2006}.
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
-Data extraction from Materials Project was performed in december of $2020$ for the Ferrenti and extended Ferrenti approach, while in march $2021$ for the empirical approach.
+Data extraction from Materials Project was performed in December of $2020$ for the Ferrenti and extended Ferrenti approach, and in March $2021$ for the empirical approach.
 Therefore, the two former approaches includes $77$ more materials due to deprecated entries in the Materials Project database.
@@
 The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than $600.000$  materials.
-The calculations are performed with the VASP software whereas the electron exchange and correlation are described with the PBE functional.
+The calculations are performed with the VASP software and the electron exchange and correlation are described with the PBE functional.
 The $+U$ extension is included for several calculations considering specific elements \cite{Stevanovic2012}.
@@
 
-JARVIS-DFT \cite{Choudhary2020} is an open database based on the VASP software and consists of roughly $40.000$ three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
+JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly $40.000$ three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
 Structures included in the database are originally taken from the Materials
@@
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
-Data extraction from JARVIS-DFT was done in january of $2021$, were we utilized the version made available 30.04.2021 at \url{figshare.com}.
+Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available 30.04.2021 at \url{figshare.com}.
 
@@
 %with projector-extended wave (PAW) potentials 
-to relax twice and optimize the ICSD-structure. Data-extraction was done in the period of January-February of $2021$.
+to relax and optimize the ICSD-structure.  Data-extraction was done in the period of January-February of $2021$.
 
@@
 The accuracy is validated by a five-fold cross-validation process for each machine learning method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
-This work utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
+In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
 We extract the crystallographic information file (CIF) of the crystals from Materials Project, and then use this as input to AFLOW-ML, which then returns an anticipated band gap.

### 2022-01-21 figures/feature-importance/01-ferrenti-approach-PC-v2.tex
Updates from Overleaf

--- 2022-01-07 figures/feature-importance/01-ferrenti-approachPC-final.tex
@@
 \begin{axis}[
-height=1.4222438079424382in,
+height=1.6222438079424382in,
 legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
@@
 tick pos=left,
-width=2.8444876158848764in,
+width=3.0444876158848764in,
 x grid style={white!69.0196078431373!black},
-xlabel={Principal components},
 xmajorgrids,
@@
 yticklabels={, 0, , 0.1},
+title={Explained variance},
 legend style={font=\footnotesize},
@@
 \addlegendimage{semithick, color=white!53.3333333333333!black};
-\addlegendentry{Explained variance};
+\addlegendentry{Ferrenti approach};
 \end{axis}

### 2022-01-21 figures/feature-importance/03-empirical-approach-GB-v2.tex
Updates from Overleaf

--- 2022-01-07 figures/feature-importance/03-insightful-approachGB-final-2.tex
@@
 \begin{axis}[
-height=1.4222438079424382in,
+height=1.6222438079424382in,
 tick align=outside,
 tick pos=left,
-width=2.8444876158848764in,
+width=3.0444876158848764in,
 x grid style={white!69.0196078431373!black},
@@
 xmin=0.5, xmax=15.5,
+xlabel={Principal components},
 xtick style={color=black},
-xticklabels={,,},
 y grid style={white!69.0196078431373!black},
@@
 \addlegendimage{semithick, color=color0};
-\addlegendentry{Gradient boost};
+\addlegendentry{Empirical approach};
 \end{axis}

### 2022-01-21 paper_twocolumn.tex
Updates from Overleaf

--- 2022-01-20 paper_v2.tex
@@
 %pra,
-%prb,
+ prb,
+ twocolumn,
 %rmp,
@@
 The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to the machine learning (ML) methods based on Ferrenti and extended Ferrenti approach that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution.
+In contrast to the machine learning (ML) methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
 All four machine learning (ML) methods applied to the training set derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
@@
 %Figure 1 introduction schematic 
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
@@
     \label{fig:ht-workflow}
-\end{figure}
+\end{figure*}
 
@@
 Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
-\textit{En setning om discovery her??}
+%\textit{En setning om discovery her??} 
+Analyzing the output of the machine learning methods reveals that, given a suitable initial data set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
-Importantly, the approach emphasize features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
+Importantly, the empirical approach emphasizes features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
 %(to a $0.5$ cut-off)  
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
@@
     \label{fig:flowchart}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[t] %!htp
-    \centering
-    \begin{subfigure}{0.9\textwidth}
+\begin{figure}%[t] %!htp
+    \centering
+    \begin{subfigure}{0.9\columnwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
+    \begin{subfigure}{0.9\columnwidth}
         \centering
@@
     \centering
-    \begin{subfigure}{0.3\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v3.pdf}
+    \begin{subfigure}{0.45\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{figures/pca-2d-plots/01-ferrenti-approach-v3.pdf}
     \end{subfigure}%
-    \begin{subfigure}{0.3\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach-v2.pdf}
+    \begin{subfigure}{0.45\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach-v2.pdf}
     \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v3.pdf}
+    \begin{subfigure}{0.9\columnwidth}
+        \centering
+        \includegraphics[width=1\columnwidth]{figures/pca-2d-plots/03-insightful-approach-v3.pdf}
     \end{subfigure}
@@
 
-\subsection*{Important features for QT}
+\section*{Discussion}
+%\subsection*{Important features for QT}
 
@@
 %Turning to why the specific materials were chosen ... 
+Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we find important differences between the three labeling approaches, and can start to discern the driving forces for manifestation of quantum compatible properties in semiconductors.
 The analysis of the principal components extracted from the machine learning models revealed that eigenvector number five was dominant for both the Ferrenti and extended Ferrenti approaches.
 This principal component includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
+In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process, thus, little new information is gained. 
 On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach, i.e., principal component number one.  
@@
 The exact degree and type of symmetry is still open to debate and should be studied further.
+Similarly symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are also influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
@@
 %in contrast 
-not precisely as expected according 
-to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
+contrary to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
 Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered
@@
 
-Additionally, the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
-
-Considering our findings in light of the specific defect centers we know to be quantum compatible reveals fascinating characteristics.
+Considering the trends in machine learning selectivity in light of the specific defect centers we know to be quantum compatible reveals fascinating characteristics.
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
@@
 
-\section*{Discussion} 
-We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25.000$ materials.
+%\section*{Discussion} 
+%MB I removed the initial discussion here, as it was a bit repetitive 
+%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25.000$ materials.
 Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
@@
 
-We find that the formulation of the training sets for the Ferrenti and extended Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
-The stringent restrictions set for the empirical approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
+%NB 
+%Morten, kan ta en titt her? 
+Discuss suitability of ML methods here.
+
+To summarize, the data extraction tools developed herein resulted in a data set of over $25.000$ materials and more than $4800$ physics-informed features.
+Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four machine learning algorithms.
+We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti based ones. 
+Additionally, much fewer principal components are needed for obtaining optimal performance of the machine learning algorithms for the empirical approach, indicating a simpler model. 
+The principal component analyses of the ML model's performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
+Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions instead without being guided by assumptions.
+%that the formulation of the training sets for the Ferrenti and extended Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
+%The stringent restrictions set for the empirical approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
 Moreover, the smaller number of materials predicted for the empirical approach permits manual verification.
 
-Discuss the new findings from the ML here, related to features. Perhaps move down from above.
-
-%NB 
-Discuss suitability of ML methods here.
-
-In short, the findings presented herein firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
+The findings presented herein firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
 Herein, we focus on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.

### 2022-01-24 paper_v2.tex
Updates from Overleaf

@@
 % \usepackage{longtable}
-
+\usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
+\pgfplotsset{compat=newest}
+
+\usepackage{sansmath}
+\tikzset{>=stealth,
+OptimumStyle/.style={align=center,anchor=east,rotate=90,font=\scriptsize}
+}
+\pgfplotsset{%samples=101,
+axis lines = left,
+every axis plot/.append style={line width=2pt},
+}
 \usepackage{forest}
@@
 \author{Oliver Lerst{\o}l Hebnes}
-\affiliation{Your new job} 
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
     \centering
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-        \input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}
+    \begin{subfigure}{1\textwidth}
+        \centering
+        \scalebox{0.85}{\input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}}
     \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-          \input{figures/parallel-coordinates-plots/02-augmented-ferrenti-approach-v2.pgf}
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
     \end{subfigure}
-    \begin{subfigure}{0.9\textwidth}
-        \centering
-          \input{figures/parallel-coordinates-plots/03-insightful-approach-v2.pgf}
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/03-empirical-approach-v3.pgf}}
     \end{subfigure}
-    %\vspace*{10mm}
     \caption{Parallel coordinate plots for the different approaches.
@@
     \centering
-    \begin{subfigure}{0.3\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach-v3.pdf}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
     \end{subfigure}%
-    \begin{subfigure}{0.3\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach-v2.pdf}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach-v3.pdf}
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
     \end{subfigure}
-    %\vspace*{-95mm}
     \caption{Two-dimensional scatter plots for the three different approaches.
@@
 The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
-Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of centering the data.
+Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of
+removing the mean and scaling to unit variance.
+%centering the data. 
 Red triangles represent unsuitable candidates while colored symbols (green, blue, black and yellow) represent suitable candidates. 
@@
 These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above.
-This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
-%
-In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT, we perform a principal component analysis (PCA) for each of the three approaches.
+%This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+
+In order to reduce the dimensionality while preserving most of the variance in the data,
+%In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT,
+we perform a principal component analysis (PCA) for each of the three approaches.
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
@@
 %
-Figure~\ref{fig:PComponents} visualizes different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
+Figure~\ref{fig:PComponents} visualizes different parameters for the 
+%$25$ 
+most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
 %The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
@@
 For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$ (not shown).
-In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger principal component values.
+In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting
+%for larger principal component values. 
+when involving more principal components.
+
 Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components. 
-
-\begin{figure}[t]
-    \centering
-    \includegraphics[width=0.9\textwidth]{figures/PC_Ferrenti_empirical.png}
-    %\includegraphics[width=0.9\textwidth]{figures/PCcomponents.pdf}
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \input{figures/feature-importance/01-ferrenti-approach-PC-v2.tex}
+        \label{fig:01-fi-e}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \input{figures/feature-importance/01-ferrenti-approach-GB-v2.tex}
+        \label{fig:01-fi-d}
+    \end{subfigure}%
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \input{figures/feature-importance/03-empirical-approach-PC-v2.tex}
+        \label{fig:03-fi-e}
+        \subcaption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \input{figures/feature-importance/03-empirical-approach-GB-v2.tex}
+        \label{fig:03-fi-d}
+        \subcaption{}
+    \end{subfigure}
     \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-    \textit{Placeholder figure.} 
     }
@@
 All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.7$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
+If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
 We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
@@
 
-\subsection*{Important features for QT}
+\section*{Discussion}
+%\subsection*{Important features for QT}
 
 %histograms 
-\begin{figure}[t]
-    \includegraphics[width=0.45\textwidth]{figures/histograms/new/MP_Eg_count_075.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/histograms/new/IonProperty_max ionic char_count_075.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.pdf}
-    \includegraphics[width=0.45\textwidth]{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.pdf}
-    \caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function and (d) standard deviation of the average bond length.
+\begin{figure}[ht]
+    \begin{subfigure}[b]{1\textwidth}
+    \centering
+    \input{figures/histograms/new/legend.tex}
+  \end{subfigure}
+  \par\bigskip
+\begin{subfigure}[b]{0.45\textwidth}
+    \input{figures/histograms/new/MP_Eg_count_075.tex}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \input{figures/histograms/new/IonProperty_max ionic char_count_075.tex}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.45\textwidth}
+    \input{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \input{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.tex}
+    \subcaption{}
+\end{subfigure}
+\caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
 The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.

### 2022-01-24 supplementary.tex
Updates from Overleaf

@@
 \sisetup{separate-uncertainty}
-\pgfplotsset{%samples=101,
-axis lines = left,
-every axis plot/.append style={line width=2pt},
-}
 
@@
 
-\subsubsection*{Augmented Ferrenti approach}
+\subsubsection*{Extended Ferrenti approach}
 
-For the augmented Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
+For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
 All models experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which is a ratio of $75:25 \ \%$.
@@
 \centering
-\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the augmented Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
 \label{tab:02-pc}
@@
 
-Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the augmented Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
+Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
 Logistic regression performs optimally for many principal components, and is the only model that continues to improve with an increasing number of components.
@@
   \end{subfigure}
-  \caption{{Four figures displaying hyperparameter search for the augmented Ferrenti approach.
+  \caption{{Four figures displaying hyperparameter search for the extended Ferrenti approach.
 The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
@@
 
-The interpretation of feature importance for the augmented Ferrenti approach is substantially more difficult than in the Ferrenti approach.
+The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation due to a large variety of accuracy.
@@
 
-\subsubsection*{Intuitive approach}
+\subsubsection*{Empirical approach}
 
-Lastly, we turn to the intuitive approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set, which was again somewhat imbalanced.
+Lastly, we turn to the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set, which was again somewhat imbalanced.
 However, in contrast to the two training sets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
@@
 \centering
-\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the intuitive approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
+\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
 \label{tab:03-pca}
@@
 
-  \caption{{Four figures displaying hyperparameter search for the intuitive approach.
+  \caption{{Four figures displaying hyperparameter search for the empirical approach.
 The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
@@
 
-  \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the intuitive approach.
+  \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the empirical approach.
 The panels show the logistic regression coefficients, decision trees feature importance, random forests feature importance, gradient boosting feature importance, and explained variance that is retained by including each of the eigenvectors.
@@
 
-The intuitive approach differs in many aspects from the Ferrenti and augmented Ferrenti approaches.
-Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and augmented Ferrenti approach, respectively.
+The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches.
+Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approach, respectively.
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
@@
 
-Thirdly, the intuitive approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the augmented Ferrenti approach.
+Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
 We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
@@
 
-Figure~\ref{fig:predictions} provides a visualization of the number of predicted material candidates from the (a) Ferrenti, (b) augmented Ferrenti and (c) intuitive approaches.
+Figure~\ref{fig:predictions} provides a visualization of the number of predicted material candidates from the (a) Ferrenti, (b) extended Ferrenti and (c) empirical approaches.
 Suitable and unsuitable candidates are marked in green and red, respectively.
-We observe that the number of predicted suitable candidates is similar for the Ferrenti and augmented Ferrenti approaches, albeit higher in the case of the latter, for all four ML models, while the intuitive approach results in a substantially narrower selection of contender materials.
+We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML models, while the empirical approach results in a substantially narrower selection of contender materials.
 Note that the confidence cut-off was set to $0.5$.
@@
 
-The perhaps more liberal augmented Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
 Due to the less stringent restrictions compared to the Ferrenti approach, we find the large amount of $9227$ entries that the four models agree on.
 
-The four models predict radically fewer suitable candidates for the intuitive approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The four models predict radically fewer suitable candidates for the empirical approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
 The large majority of the unsuitable candidates are predicted with high probability except for the random forests model due to the ensemble of trees.
@@
 
-Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning models, using the training set derived in the intuitive approach, agreed on with a confidence cut-off set to $0.75$.
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning models, using the training set derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
@@
 %histograms 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ElementProperty_MagpieData range CovalentRadius_count_075.pdf}
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MaximumPackingEfficiency_max packing efficiency_count_075.pdf}
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.pdf}
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.pdf}
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.pdf}
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.pdf} 
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.pdf} 
-    \includegraphics[width=0.4\textwidth]{figures/histograms/new/MP_Eg_normalized_databackgrund_075.pdf} 
+\begin{figure}[!ht]
+\begin{subfigure}[t]{1\textwidth}
+    \input{figures/histograms/new/legend.tex}
+\end{subfigure}
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ElementProperty_MagpieData range CovalentRadius_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MaximumPackingEfficiency_max packing efficiency_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.47\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MP_Eg_normalized_databackgrund_075.tex}}
+    \subcaption{}
+\end{subfigure}
 \caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
-Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
+Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function.
+Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
 The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
@@
 }
-    \label{fig:histograms_supp}
 \end{figure}

### 2022-01-26 paper_v2.tex
Updates from Overleaf

@@
 Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, scouring these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
+However, %scouring
+searching 
+these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
 Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods.
@@
 %Marianne I have now changed augmented Ferrenti to extended Ferrenti 
-\emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
-We find that the former two methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
-The third and empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets where then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+\emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}. We find that the %former 
+two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}. The  
+%third and 
+empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
+The three training sets were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
 Importantly, the empirical approach emphasizes features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
@@
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped intro training, test and validation sets for the machine learning models.
+The labeled data are then grouped into training, test and validation sets for the machine learning models.
 
@@
 In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
-Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon photon emission, non-polar materials are assumed to be preferable.
+Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission, non-polar materials are assumed to be preferable.
 

### 2022-01-31 paper_v2.tex
Updates from Overleaf

@@
 The labeled data set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the data,
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
 
@@
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
+
 Next, we apply the machine learning models.
-% 
 In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
-%
-Figure~\ref{fig:PComponents} visualizes different parameters for the 
-%$25$ 
-most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-%The extracted principal components after applying the gradient boosting model for the training sets from the Ferrenti and empirical approaches are shown in Figure~\ref{fig:PComponents} in decreasing order of eigenvalue size.
+We note that all four machine learning models have high evaluation metrics for the optimal hyperparameters.
 Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four machine learning models are shown in the Supplementary Material at \cite{supplementary}.
 
-Fig.~\ref{fig:PComponents}(a) displays the principal components as they are sorted in descending order by the explained variance.
+%OH: Downsides. Could also be moved to methods?
+We note that there are several potential pitfalls of using the chosen dimensionality reduction and machine learning techniques in this paper.
+PCA is a trivial algorithm that only accounts for linear correlation between features, where other algorithms, such as Kernel PCA, can facilitate non-linear dimensionality reduction but with higher computational demand.
+Additionally, by using a trivial PCA, we make an assumption of orthogonality, since the eigenvectors are orthogonal to each other.
+However, there might exist an non-orthogonal basis which captures the non-orthogonal data in the dataset better.
+
+%OH: Øyvind og Seb: 
+%Comment on pitfalls of ML metods
+%Comment on pitfalls on data size.
+
+Figure~\ref{fig:PComponents} visualizes different parameters for the most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
+This differs from Figure \ref{fig:2dscatterplotpca}, where we visualize the two most important eigenvectors for all approaches that originates from the same covariance matrix.
+%Fig.~\ref{fig:PComponents}(a) displays the principal components as they are sorted in descending order by the explained variance. 
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$ (not shown).
+For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$.
+
 In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting
 %for larger principal component values. 
-when involving more principal components.
-
-Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components. 
+when involving more principal components. Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components. 
 \begin{figure}[ht]
@@
 All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to (e.g.) $0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
+If we were to raise the minimum confidence cut-off for a prediction to e.g.
+$0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
 We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
@@
     \centering
-    \input{figures/histograms/new/legend.tex}
+    \input{figures/histograms/new/LegendHistPaper.tex}
   \end{subfigure}
@@
 At most three different elements are present, but the emphasis is clearly on binary compounds.
-This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in (e.g.) bond length and symmetry.
+This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in e.g.
+bond length and symmetry.
 Indeed, this is
@@
 %mhj: ref to materials project is missing
-Project, and then re-optimized using the OPT functional.
-Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
+Project \cite{Jain2013, Jain2018}, and then re-optimized using the OPT functional.
+Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals \cite{Tran2009} is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
 Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available 30.04.2021 at \url{figshare.com}.
@@
 
-Pymatgen, a robust, open-source Python library for materials analysis \cite{pymatgen}, was also employed.
+Pymatgen, a robust, open-source Python library for materials analysis \cite{pymatgen}, was also employed to extract and generate features for several of the databases mentioned above.
 

### 2022-02-03 paper_v2.tex
Updates from Overleaf

@@
 These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above.
-%This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
 
@@
 
-%OH: Øyvind og Seb: 
-%Comment on pitfalls of ML metods
-%Comment on pitfalls on data size.
+%Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
+The three approaches define labelled data of varying size, where the smallest is from the empirical approach.
+For small datasets, it is proven beneficial to repeat the cross-validation, as this is a method that allows us to measure the stability of the predictions given against pertubations (i.e.
+few different entries) of the training data \cite{Beleites2008}.
 
@@
 %empirical approach
+% OH: This paragraph is a duplicate from supplementary
 The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
-Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
-We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
+%Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
+Firstly, We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
 Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b). 
-This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} fur further details).
+This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details).
 The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.

### 2022-02-09 supplementary.tex
Updates from Overleaf

@@
 
-The implementation of the machine learning models was done through the open library of Scikit-learn.
+The implementation of the machine learning models was done through the open library of Scikit-learn \cite{Pedregosa2012}.
 By adjusting the majority of the hyperparameters in Sciki-learn, we experienced severe overfitting for random forest, gradient boosting, and decision trees.
@@
 
-The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches.
+%OH: Commented out the three next paragraphs, since this is mentioned in main text.
+%The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches.
 Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approach, respectively.
@@
 
-Secondly, we find that the first principal component is by far the most important feature for all models, as visualized in Figure~\ref{fig:03-fi}.
+%Secondly, we find that the first principal component is by far the most important feature for all models, as visualized in Figure~\ref{fig:03-fi}.
 This is part of the reason why we experience a large accuracy for only a single feature, as seen in Figure~\ref{fig:03-pca}.
@@
 %However, it differs when it comes to which top features the first principal component describes, which includes 
-bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+%bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 
-Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
+%Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
 We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.

### 2022-02-22 paper_v2.tex
Updates from Overleaf

@@
 \author{Oliver Lerst{\o}l Hebnes}
+\affiliation{Sopra Steria, Information Technology and Services, N-4020 Stavanger, Norway}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 \affiliation{Advanced Power Semiconductor Laboratory, ETH Z{\"u}rich, 8092  Z{\"u}rich,  Switzerland}
-\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning models; BN, CdSe, BC$_2$N, InAs, CuI, and ZnCd$_3$Se$_4$.
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning models; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
 The nine materials each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.

### 2022-02-22 paper_v2.tex
Updates from Overleaf

@@
 
-Data extraction tools have been developed for a number of materials science databases resulting in a data set consisting of over $25.000$ materials.
+Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25.000$ materials.
 The information from the databases was converted into nearly $5000$ physics-informed features.
 Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
-The three approaches define distinct training sets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
+The three approaches define distinct datasets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
 
@@
 In contrast to the machine learning (ML) methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
-All four machine learning (ML) methods applied to the training set derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
+All four machine learning (ML) methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
@@
 
-The fourth science paradigm of big data driven science cover the potential of targeted search for promising material systems in which to expect QT compatible properties. \textit{referanse her} 
+The fourth science paradigm of big data driven science cover the potential of targeted search for promising material systems in which to expect QT compatible properties, see for example Ref.~\cite{Acin2018}.
 Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
@@
 %\textit{En setning om discovery her??} 
-Analyzing the output of the machine learning methods reveals that, given a suitable initial data set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
+Analyzing the output of the machine learning methods reveals that, given a suitable initial dataset of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important aspect of our work is the database building and pertinent development of the training sets for machine learning methods.
+An important aspect of our work is the database building and pertinent development of the datasets for machine learning methods.
 We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii)
@@
 empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+The three training sets were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
 Importantly, the empirical approach emphasizes features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
@@
 The MP database contains ground state properties of different materials that are computed using density functional theory (DFT).
-The DFT calculations in the database were performed using the Vienna ab initio simulation package (VASP) \cite{Kresse1996} and the Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996} exchange-correlation functional to calculate the electronic structure of the materials.
+The DFT calculations in the database were performed using the Vienna {\em ab initio} simulation package (VASP) \cite{Kresse1996} and the Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996} exchange-correlation functional to calculate the electronic structure of the materials.
 We note that despite being immensely successful in describing a number of material properties, PBE is widely known for underestimating the band gap of semiconductors \cite{Freysoldt2014}.
@@
     \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
-    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized data set with entries from several other databases.
+    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized dataset with entries from several other databases.
 To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects
@@
 In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the databases OQMD \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
-The results of these steps are combined into a data set for further analysis.
+The results of these steps are combined into a dataset for further analysis.
 
@@
 However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure, therefore, we extend their implementation to facilitate such featurizations.
-A schematic visualizing the featurization process in Matminer is contained in Fig.~\ref{fig:flowchart} 
+A schematic visualization of the featurization process in Matminer is shown in Fig.~\ref{fig:flowchart} 
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ featurizers selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
-The selection of features was kept rather wide as we do not want to make ex-ante assumptions on which features best describe a solid state material platform for quantum technology.
+The $39$ features selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
+The selection of features was kept rather wide as we do not want to make {\em ex ante} assumptions on which features best describe a solid state material platform for quantum technology.
 
 %It is important to note that 
-The constructed data sets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
+The constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
 Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
@@
 Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Therefore, we are dependent on that the Materials Project database contains data with high quality, but we note that some errors are likely present in our data set.
+Thus, our results depend on the Materials Project database containing data with high quality.
 
 \subsection*{Data Mining}
-The complete data set consists of $25.000$ materials.
+The complete dataset consists of $25.000$ materials.
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
@@
 \subsubsection*{The Ferrenti approach}
-The first approach to labeling a selection of materials in the data set is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+The first approach to labeling a selection of materials in the dataset is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project.
@@
         \item exclude any rare-earth metals (because of the difficulty of obtaining pure materials free of isotopes with nuclear spin) and noble gases (due to the lack of stable solid phases),
-        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism; Ru and Os are also excluded because they only exist in the data set as complex cluster structures.
+        \item exclude transition metal elements with unpaired electrons like Fe and Ni because of their paramagnetism; Ru and Os are also excluded because they only exist in the dataset as complex cluster structures.
     \end{itemize}
@@
 
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD \cite{Allen1987,Zagorac2019} 
-that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
+Next, unsuitable candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
+that crystallize in polar space groups, are calculated to be magnetic.
+These candidates have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors).
 The resulting complete set of labeled materials contains $1581$ materials where $35 \ \%$
@@
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
+For unsuitable candidates, we implement the same strategy as for the first Ferrenti approach.
 The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small data sets for training, testing and validation of the machine learning models, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning models, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
-Materials where properties like single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related will also be included in this context.
+We have also included materials where properties like single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related.
 
@@
 %Ferrenti 
-Considering the materials present in the labeled data sets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
+Considering the materials present in the labeled datasets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
 Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
@@
 %Extended Ferrenti 
-In the training set of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The labeled data set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
+In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the labeled dataset.
 
@@
 We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, we have transformed the three training sets resulting from the three approaches and visualized them as scatter plots.
+Then, we have transformed the three datasets resulting from the three approaches and visualized them as scatter plots.
 Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
@@
 
-To illustrate the composition of the labeled data we perform a principal component analysis.
-We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial data set from the Materials Project, and transform the three labeled data sets according to the corresponding two eigenvectors.
+To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
+Principal component analysis falls under the category of unsupervised learning within machine learning methods.
+Here we apply PCA to the labeled datasets in order to figure out if are specific features that stand out.
+In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
+We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the Materials Project, and transform the three labeled datasets according to the corresponding two eigenvectors.
 In essence, we reduce the dimensionality of the labeled data in order to visualize them.
@@
 This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable data sets for training, testing and validation of the machine learning methods.
+Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training, testing and validation of the machine learning methods.
 
@@
 %summary - do we need this? 
-In summary, using various data extraction tools for a number of materials science databases, we have obtained a data set consisting of over $25.000$ materials.
-The information from this data set has then been converted into nearly $5000$ physics-informed features.
-After selecting and fine-tuning the entries for our labeled data sets we are now ready to train the ML methods and apply them to the test set in order to classify materials as potential candidates for quantum technology applications.
+In summary, using various data extraction tools for a number of materials science databases, we have obtained a dataset consisting of over $25.000$ materials.
+The information from this dataset has then been converted into nearly $5000$ physics-informed features.
+After selecting and fine-tuning the entries for our labeled datasets we are now ready to apply the various ML methods discussed earlier.
+We split our labeled datasets into a so-called training set, a validation set and finally a test set which is not included in the training and validation process.
+This process will allow us to classify specific materials as potential candidates for quantum technology applications.
 
 \subsection*{Machine learning and principal component analysis}
-
-Four well-tested machine learning algorithms were employed in this work: logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009}.
-These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above.
+In this work we have applied
+four well-tested machine learning algorithms in order to classify specific materials as candidate systems for QT.
+These are logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
+These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
 This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
@@
 %In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT,
-we perform a principal component analysis (PCA) for each of the three approaches.
+we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches.
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
 
-Next, we apply the machine learning models.
-In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
+Next, we apply the abovementioned machine learning models.
+In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
 We note that all four machine learning models have high evaluation metrics for the optimal hyperparameters.
@@
 %OH: Downsides. Could also be moved to methods?
-We note that there are several potential pitfalls of using the chosen dimensionality reduction and machine learning techniques in this paper.
+%We observe that there are several potential pitfalls of using the chosen dimensionality reduction and machine learning techniques in this paper.
 PCA is a trivial algorithm that only accounts for linear correlation between features, where other algorithms, such as Kernel PCA, can facilitate non-linear dimensionality reduction but with higher computational demand.
@@
 %Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
-The three approaches define labelled data of varying size, where the smallest is from the empirical approach.
+The three approaches define labeled data of varying size, where the smallest is from the empirical approach.
 For small datasets, it is proven beneficial to repeat the cross-validation, as this is a method that allows us to measure the stability of the predictions given against pertubations (i.e.
@@
 Figure~\ref{fig:PComponents} visualizes different parameters for the most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-This differs from Figure \ref{fig:2dscatterplotpca}, where we visualize the two most important eigenvectors for all approaches that originates from the same covariance matrix.
+This differs from Fig.~\ref{fig:2dscatterplotpca}, where we visualize the two most important eigenvectors for all approaches that originates from the same covariance matrix.
+Note also that in Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
+In the ML analysis here the model development is done on the training and validation set.
 %Fig.~\ref{fig:PComponents}(a) displays the principal components as they are sorted in descending order by the explained variance. 
@@
     \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
+Note well that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training and validation sets using gradient boosting \cite{Hastie2009,xgboost2016}.
+The latter shows that for the empirical approach most of the physics is represented by few features (see text for an in depth discussion).
+The results in (b) are similar to those obtained with logistic regression, decision trees and random forests.
     }
@@
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
-The second most important principal component for the Ferrenti approach is the second one, PC2. 
+The second most important principal component for the Ferrenti approach is the second one. 
 The second component's largest values correspond to the 
@@
 Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b).
+Similar conclusions are reached using logistic regression, decisions trees and random forests as classification methods, lending thus support to our main conclusions.
+
 This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details).
 The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
-The standard deviation of the radial distribution function appears multiple times in the list of features and appears to be of particular importance. 
+The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
 Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti  and $11 \ \%$ for the extended Ferrenti approach.
@@
 The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
-An overview of the number of predicted suitable candidates as a function of machine learning model confidence when the four models in an approach agree is summarized in Table~\ref{tab:probabilites}.
+An overview of the number of predicted suitable candidates as a function of machine learning model confidence is summarized in Table~\ref{tab:probabilites}.
 
@@
 We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
-From the labeled data set of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
+From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
 All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
@@
 than the Ferrenti approach.  
-The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled data set, where they all agree on a total of $9227$ predicted suitable candidates.
+The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
@@
 Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning models; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
-The nine materials each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
+The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
 Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems using examples and  Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
@@
 %The element S resides in the same group as Se, and 
-The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively. Comparing to experiment, ... 
+The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.
+
 %high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}.
@@
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our data set.
+We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
 
@@
 CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the data set than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
+Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the dataset than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
 The presence of CuI in two configurations  proposes that ionic character alone is not an obstacle for a material to be quantum compatible if the prediction of CuI proves to be merited.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning models after training on the data set resulting from the empirical approach.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning models after training on the dataset resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 contrary to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results instead reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered
-%as well. 
-instead.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results show that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered.
 
@@
 %MB I removed the initial discussion here, as it was a bit repetitive 
-%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a data set consisting of more than $25.000$ materials.
+%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25.000$ materials.
 Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
@@
 
-To summarize, the data extraction tools developed herein resulted in a data set of over $25.000$ materials and more than $4800$ physics-informed features.
+To summarize, the data extraction tools developed herein resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four machine learning algorithms.
@@
 Machine learning represents the science of giving computers the ability to learn without being explicitly programmed.
-The idea is that there exist generic algorithms which can be used to find patterns in a broad class of data sets without having to write code specifically for each problem.
+The idea is that there exist generic algorithms which can be used to find patterns in a broad class of datasets without having to write code specifically for each problem.
 The algorithm builds its own logic based on the data.
@@
 In supervised learning we know the answer to a problem, and let the computer deduce the logic behind it.
-On the other hand, unsupervised learning is a method for finding patterns and relationship in data sets without any prior knowledge of the system.
+On the other hand, unsupervised learning is a method for finding patterns and relationship in datasets without any prior knowledge of the system.
 Many researchers also operate with a third category, namely reinforcement learning.
@@
 Gradient boosting and random forests use decision trees as weak learners and improve their predictability.
-For random forests this is implemented through a collection of randomized decision trees where a  subset of the features in the data sets are selected randomly when building a decision tree.
+For random forests this is implemented through a collection of randomized decision trees where a  subset of the features in the datasets are selected randomly when building a decision tree.
 Boosting methods like gradient boosting use decision trees as  weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
@@
 \section*{Data availability} 
-The data sets that support the findings of this study are available online at \cite{Ohebbi2021}.
+The datasets that support the findings of this study are available online at \cite{Ohebbi2021}.
 

### 2022-02-22 paper_v2.tex
Updates from Overleaf

@@
 Among the $66$ materials that all models in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
-Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
+The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
 % MB Do we want to emphasize Ge, as we are downplaying the importance of elemental semiconductors? Or, it could contain an impurity
-Ge has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
+Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
 Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
@@
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we find important differences between the three labeling approaches, and can start to discern the driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the machine learning models revealed that eigenvector number five was dominant for both the Ferrenti and extended Ferrenti approaches.
-This principal component includes features related to the band gap and chemical environment, thus, the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process, thus, little new information is gained. 
-On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach, i.e., principal component number one.  
-Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of  band gap (as listen in the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap as suitable.
+The analysis of the principal components extracted from the machine learning models revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
+This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
+In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process and little new information is gained. 
+On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach.
+
+Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of  band gap (as listed in the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap.
 Moreover, the distribution of materials that was identified as suitable is rather broad with the Ferrenti based approaches exhibiting a peak around $2.5$~eV.
@@
 
-The secondmost important principal component in the Ferrenti approach, principal component number 2, encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
+The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
 %The maximum ionic character is also deemed an important part of PC2. 
@@
 The machine learning models in the empirical approach consistently identified the first principal component as the predominant one.
-Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important, as discussed above.
-Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact, as it appears four times in different forms in the top ten list over dominating features.
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
+Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
 One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material \cite{supplementary}.
-Notably, substantial discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation in the radial distribution function.
-This reflects the observations from the principal component analysis where PC1 (most important for the empirical approach) is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a sharp peak in the preferred std value for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
-
-We interpret the standard deviation (std) of the RDF such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
-Similarly, zero std in the average bond length would mean that all bonds are identical throughout the crystal.
+Notably, substantial discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation of the radial distribution function.
+This reflects the observations from the principal component analysis where the first principal component is dominated by the RDF and similarly symmetry related features.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
+
+We interpret the standard deviation  of the RDF such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
+Similarly, zero standard deviation in the average bond length would mean that all bonds are identical throughout the crystal.
 Intriguingly, the peaks in the distributions of the predicted materials are not found for perfectly symmetric materials with identical bond lengths; instead, some variation in the bond and wavefunction distributions is found to be optimal for a material to be suitable for QT.
@@
 The exact degree and type of symmetry is still open to debate and should be studied further.
-Similarly symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), site fingerprint of the chemical environment and bond orientation (see the Supplementary Material) are also influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
-
-Interestingly, none of the nine materials predicted by the empirical approach with $0.85$ confidence, nor of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
+Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+
+Interestingly, none of the nine materials predicted by the empirical approach with $0.85$ confidence, nor any of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
 At most three different elements are present, but the emphasis is clearly on binary compounds.
@@
 bond length and symmetry.
-Indeed, this is
+This is  in
 %in contrast 
-contrary to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results show that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered.
+contrast to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results show that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well.
 
@@
 While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT  compatible properties to manifest in a semiconductor host.
+Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets.
+The methods we have chosen are all well tested, with random forests and gradient boosting methods as those which tend to outperform the other, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
 
@@
 %NB 
-%Morten, kan ta en titt her? 
-Discuss suitability of ML methods here.
-
-To summarize, the data extraction tools developed herein resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
+%Morten, kan ta en titt her?  Se ovenfor.
+
+To summarize, the data extraction tools developed in this work resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four machine learning algorithms.
 We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti based ones. 
-Additionally, much fewer principal components are needed for obtaining optimal performance of the machine learning algorithms for the empirical approach, indicating a simpler model. 
-The principal component analyses of the ML model's performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
-Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions instead without being guided by assumptions.
+Additionally, much fewer principal components are needed for obtaining optimal performance of the machine learning algorithms for the empirical approach.
+The principal component analyses of the ML models' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
+Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.% instead without being guided by assumptions.
 %that the formulation of the training sets for the Ferrenti and extended Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
@@
 
-The findings presented herein firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
-Herein, we focus on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
+The findings presented here firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
+Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
 Two main routes can be followed to exploit the results.

### 2022-02-22 paper_v2.tex
Updates from Overleaf

@@
 One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four machine learning methods.
-Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest.
-Thus can new discoveries in the field of quantum technologies be made.
+Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
 

### 2022-02-25 supplementary.tex
Updates from Overleaf

@@
 Predicting Solid State Material Platforms for Quantum Technologies}
-
 \author{Oliver Lerst{\o}l Hebnes}
+\affiliation{Sopra Steria, Information Technology and Services, N-4020 Stavanger, Norway}
 \affiliation{Department of Physics and Center for Computing in Science Education, University of Oslo, N-0316 Oslo, Norway}
@@
 
-\newpage
-
 \section*{Supplementary methods}
@@
 To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}. 
-Table~\ref{table:featurizers} contains an overview of this work's chosen 39 featurizers from Matminer. The featurization process results in $4876$ descriptors.
+Table~\ref{table:featurizers} contains an overview of the 39  chosen featurizers from Matminer. The featurization process results in $4876$ descriptors.
 
 The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable potential host.
-Therefore, we strive to collect an achievable quantity of descriptors with the hope of getting wiser in terms of prediction potential materials for quantum technologies.
+Therefore, we strive to collect an achievable quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
 
@@
 
-In the evaluation of the machine learning models for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations.
-Due to imbalanced training data, we apply four different evaluation metrics to each of the four algorithms for each approach.
+In the evaluation of the machine learning models for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations, see for example \cite{Hastie2009} for details on the cross-validation procedure.
+Due to imbalanced training data, we apply four different evaluation metrics to each of the four machine learning algorithms discussed in this work.
 
 The implementation of the machine learning models was done through the open library of Scikit-learn \cite{Pedregosa2012}.
-By adjusting the majority of the hyperparameters in Sciki-learn, we experienced severe overfitting for random forest, gradient boosting, and decision trees.
+By adjusting the majority of the hyperparameters in Sciki-learn, we experienced severe overfitting for the random forests, gradient boosting, and decision trees methods.
 Therefore, most parameters are the default values defined by Scikit-learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$ was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$.
+The only parameter that we found that could potentially improve the evaluation metric F$1$  (see \cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$.
 For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
@@
 When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
-Due to a large number of principal components, we end up fitting $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models, just for one arbitrary machine learning algorithm like logistic regression.
+Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models %, just for one arbitrary machine learning algorithm like logistic regression.
 
@@
 The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
-For each principal component, the optimal combination of hyperparameters based on the F$1$-score is visualized.
+For each principal component, we display the optimal combination of hyperparameters based on the F$1$-score.
 
@@
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall, and F$1$ scores are based on the test set.
+Precision, recall, and F$1$ scores are based on the test set \cite{geron2022}.
 The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
@@
 
-In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components, which is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
-The relevant hyperparameters for logistic regression were the maximum iterations, which was set at $400$, and the regularization term, which was found optimal at $0.46$.
-For random forests and decision trees, we find the maximum depth of $7$, while being $4$ for gradient boosting.
-We find the best performing model is logistic regression, but this model is dependent on a large number of principal components.
+In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components.
+The optimal number  is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
+The relevant hyperparameters for logistic regression were the maximum iterations.
+The number of iterations was set at $400$, and the regularization term was given by an optimal of $0.46$.
+For random forests and decision trees, we find the maximum depth of $7$.
+Gradient boosting which uses a weak learner, had a decision tree of depth $4$.
+We find the best performing model to be logistic regression, but this model depends on a large number of principal components.
 
-In Figure~\ref{fig:01-fi}, we visualize how the models interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation.
-To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components needs to be involved.
-We have visualized the first $25$ since this captures the most important information, and we note that most of the important features are found within the first five principal components.
+In Figure~\ref{fig:01-fi}, we visualize how the models interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components were included.
+We have visualized the first $25$ components since these capture the most important information.
+We note that most of the important features are found within the first five principal components.
 
@@
 In order of importance, we observe that the second component's largest values correspond to the electronegativity, ionic property, and covalence radius among the elements in the composition.
-The data originiates from elemental calculatinos from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum.
+The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum.
 While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
@@
 For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
-All models experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which is a ratio of $75:25 \ \%$.
+All models experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75:25 \ \%$.
 This result comes as a consequence of the models being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
@@
 The decision trees model exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
-Random forests exhibits fewer fluctuations compared to the decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve after around $100$ principal components.
+The Random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
 

### 2022-02-27 supplementary.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item \textit{Supplementary methods.} \\   Additional information on the featurization process and optimization of the machine learning models. 
-    \item \textit{Supplementary results.} \\  Statistics and tables over the materials that were predicted by the machine learning models based on the training sets derived using the three different data mining approaches.
+    \item \textit{Supplementary methods.} \\   Additional information on the featurization process and optimization of the machine learning methods. 
+    \item \textit{Supplementary results.} \\  Statistics and tables over the materials that were predicted by the machine learning methods based on the training sets derived using the three different data mining approaches.
     \item \textit{Supplementary references.}  
@@
 The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable potential host.
-Therefore, we strive to collect an achievable quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
+Therefore, we have collected an achievable quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
 
@@
 
-\subsection*{Optimization of machine learning models}
+\subsection*{Optimization of machine learning methods}
 
-In the evaluation of the machine learning models for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations, see for example \cite{Hastie2009} for details on the cross-validation procedure.
+In the evaluation of the machine learning methods for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations, see for example \cite{Hastie2009} for details on the cross-validation procedure.
 Due to imbalanced training data, we apply four different evaluation metrics to each of the four machine learning algorithms discussed in this work.
 
-The implementation of the machine learning models was done through the open library of Scikit-learn \cite{Pedregosa2012}.
-By adjusting the majority of the hyperparameters in Sciki-learn, we experienced severe overfitting for the random forests, gradient boosting, and decision trees methods.
+The implementation of the machine learning methods was done through the machine learning library Scikit-learn \cite{Pedregosa2012}.
+By adjusting the majority of the hyperparameters in Scikit-learn, we experienced severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees.
 Therefore, most parameters are the default values defined by Scikit-learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$  (see \cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown, which we adjusted between $1$ and $8$.
+The only parameter that we found that could potentially improve the evaluation metric F$1$  (see \cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown.
+In our work we adjusted between the depth of the trees to vary from $1$ to $8$.
 For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
@@
 %Ferrenti 
-The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score on the test set as a function of principal components used in the models.
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score (see for example \cite{geron2022} for a definition of various score metrics) on the test set as a function of principal components.
 For each principal component, we display the optimal combination of hyperparameters based on the F$1$-score.
@@
 \centering
-\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:01-pca}.}
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:01-pca}.}
 \label{tab:01-pc}
@@
   \hline
-   Model & PC & Mean test &  Mean precision & Mean recall & mean F1\\
+   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
   \hline
@@
 For random forests and decision trees, we find the maximum depth of $7$.
-Gradient boosting which uses a weak learner, had a decision tree of depth $4$.
-We find the best performing model to be logistic regression, but this model depends on a large number of principal components.
+Gradient boosting, which normally uses a weak learner, had a decision tree of depth $4$.
+We find the best performing method to be logistic regression, but this method depends on a large number of principal components.
 
-In Figure~\ref{fig:01-fi}, we visualize how the models interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+In Figure~\ref{fig:01-fi}, we visualize how the various machine learning methods  interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
 To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components were included.
@@
 Large positive or negative coefficients can be considered increasingly important, where positive (negative) coefficients will contribute to making positive (negative) predictions.
-In the three next panels, namely for the models decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
-Importantly, we observe that the single most important feature for all models is the fifth principal component.
-Interestingly, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the
+In the three next panels, namely for the machine learning methods  decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
+Importantly, we observe that the single most important feature for all ML methods is the fifth principal component.
+Interestingly, by selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the
 compound 
@@
 
-After the first ten principal components, we observe that the models adapt the other principal components with varying degrees.
+After the first ten principal components, we observe that the methods adapt the other principal components with varying degrees.
 The coefficients for the case of logistic regression experience large fluctuations, but the three remaining models find the first and second principal components important in addition to the fifth.
@@
 For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
-All models experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75:25 \ \%$.
-This result comes as a consequence of the models being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
-On the other hand, we find a small precision for the first component since the model predicts many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
+All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75:25 \ \%$.
+This result comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
+On the other hand, we find a small precision for the first component since the ML methods  predict many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
 This trend is revealed when looking at the balanced accuracy score.
@@
 \centering
-\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
 \label{tab:02-pc}
@@
 Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
-Logistic regression performs optimally for many principal components, and is the only model that continues to improve with an increasing number of components.
-The decision trees model exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
+Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
+The decision trees method exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
 The Random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
@@
 The optimal hyperparameters are summarized in Table~\ref{tab:02-pc}.
-We find that the logistic regression model with $175$ principal components performs more or less like a perfect classifier with overall high scores.
-The decision trees and random forests models have similar balanced accuracy scores with $0.69$ and $0.70$, respectively, due to challenges associated with predicting true negative labels for $25$ principal components.
+We find that logistic regression with $175$ principal components performs more or less like a perfect classifier with overall high scores.
+The decision trees and random forests methods have similar balanced accuracy scores with $0.69$ and $0.70$, respectively, due to challenges associated with predicting true negative labels for $25$ principal components.
 Lastly, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
@@
 
-The relevant hyperparameters for the logistic regression model were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
+The relevant hyperparameters for logistic regression were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
 Smaller regularization values resulted in worse scores, while increasing values did not notably alter the results.
@@
 However, we find that random forests and gradient boosting experience the fifth principal component as important.
-Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates the DFT band gap of the elemental solids among the elements in the composition.
+Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
 
@@
 
-Lastly, we turn to the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set, which was again somewhat imbalanced.
+Lastly, we turn to the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set.
+%, which was again somewhat imbalanced. 
 However, in contrast to the two training sets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
@@
 The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca}.
-Interestingly, we find that all models experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
+Interestingly, we find that all ML methods  experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
 %This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
@@
 However, with multiple principal components, we find the largest increase in precision, which is a sign that the one-dimensional representation tends to wrongly predict candidates as suitable when they are in fact unsuitable.
-The decision trees and the random forests models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger values.
+Decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger values.
 Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for a few principal components.
@@
 \centering
-\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML models logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
+\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
 \label{tab:03-pca}
@@
   \hline
-   Model & PC & Mean test & Mean precision & Mean recall  & mean F1\\
+   Method & PC & Mean test & Mean precision & Mean recall  & mean F1\\
   \hline
@@
 
-The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all models exhibit high evaluation metrics.
+The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all Ml methods exhibit high evaluation metrics.
 Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with the F$1$-score of $0.98$.
-The decision trees model uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
+Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
 
@@
 The decision trees uses a maximum depth of $6$, where larger values increased the training accuracy but not any other metric.
-The maximum depth for the random forests model was set to $6$, and gradient boosting was given a value of $4$.
+The maximum depth for  random forests  was set to $6$.
+Fo gradient boosting, which use a weak learner, the depth of the trees was set to  $4$.
 
@@
 Suitable and unsuitable candidates are marked in green and red, respectively.
-We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML models, while the empirical approach results in a substantially narrower selection of contender materials.
+We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML methods, while the empirical approach results in a substantially narrower selection of contender materials.
 Note that the confidence cut-off was set to $0.5$.
@@
 For the Ferrenti approach, logistic regression finds a total of $12.380$ suitable candidates, while decision trees is the most conservative with $11.315$.
-random forests has the most optimistic estimate with $14.278$, while gradient boosting finds $11.835$ suitable candidates.
-The four ML models agree on $6804$ suitable candidates, however, many of the materials
+Random forests has the most optimistic estimate with $14.278$, while gradient boosting finds $11.835$ suitable candidates.
+The four ML methods agree on $6804$ suitable candidates, however, many of the materials
 are predicted with a confidence similar to that of a coin-flip.
 If we were to raise the minimum bar of a prediction to
-$0.7$, the models would only agree on $3000$ suitable candidates
+$0.7$, the four methods would only agree on $3000$ suitable candidates
 
 The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
-Due to the less stringent restrictions compared to the Ferrenti approach, we find the large amount of $9227$ entries that the four models agree on.
+Due to the less stringent restrictions compared to the Ferrenti approach, we find the large amount of $9227$ entries that the four ML methods  agree on.
 
-The four models predict radically fewer suitable candidates for the empirical approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
-The large majority of the unsuitable candidates are predicted with high probability except for the random forests model due to the ensemble of trees.
-All models, however, agree on $214$ suitable candidates.
+The four methods predict radically fewer suitable candidates for the empirical approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The large majority of the unsuitable candidates are predicted with high probability except for random forests  due to the ensemble of trees.
+All methods, however, agree on $214$ suitable candidates.
 
@@
 
-Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning models, using the training set derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training set derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
@@
 
-Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning models and all three approaches agreed upon. 
+Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning methods and all three approaches agreed upon. 
 %To 0.5 cutoff 
@@
 %Or important features for QT 
-Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML models in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
+Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
 The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
@@
 %histograms 
-\begin{figure}[!ht]
+\begin{figure}[!ht]\label{fig:histograms_supp}
 \begin{subfigure}[t]{1\textwidth}

### 2022-02-27 paper_v2.tex
Updates from Overleaf

@@
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training, test and validation sets for the machine learning models.
+The labeled data are then grouped into training, test and validation sets for the machine learning methodss.
 
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning models, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
 
-Next, we apply the abovementioned machine learning models.
-In the evaluation of the machine learning models for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-We note that all four machine learning models have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the machine learning models and the results from the principal component analyses for all four machine learning models are shown in the Supplementary Material at \cite{supplementary}.
+ In the evaluation of the machine learning methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+We note that all four machine learning methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the machine learning methods and the results from the principal component analyses for all four machine learning methods are shown in the Supplementary Material at \cite{supplementary}.
 
@@
 
-In the case of the empirical approach and in contrast to the Ferrenti based approaches, the decision trees and random forest models exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting
+In the case of the empirical approach and in contrast to the Ferrenti based approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting
 %for larger principal component values. 
@@
 
-Fig.~\ref{fig:PComponents}(b) reveals that the single most important feature for all models in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Fig.~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
@@
 Notably, these features were used as guidance in the initial selection process when forming the training sets.
-Thus, the machine learning models appear to preserve the criteria imposed in the Ferrenti approaches.
+Thus, the machine learning methods appear to preserve the criteria imposed in the Ferrenti approaches.
 For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate.
-Rather than focusing on, e.g., the band gap, the machine learning models appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In this approach, the machine learning models appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Rather than focusing on, e.g., the band gap, the machine learning methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In this approach, the machine learning methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 %In this section, 
-After training the machine learning models using parts of the data labeled during the three data mining approaches, the models were employed on the test sets. 
+After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
 The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
-An overview of the number of predicted suitable candidates as a function of machine learning model confidence is summarized in Table~\ref{tab:probabilites}.
+An overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence is summarized in Table~\ref{tab:probabilites}.
 
@@
     \centering 
-    \caption{Overview of the number of predicted suitable candidates as a function of machine learning model confidence when the four models in an approach agree.
+    \caption{Overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence when the four methods in an approach agree.
 A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning models; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
 The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
@@
 
-We note that all ML models in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+We note that all ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
 However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ cut-off.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning models after training on the dataset resulting from the empirical approach.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning methods after training on the dataset resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we find important differences between the three labeling approaches, and can start to discern the driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the machine learning models revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
+The analysis of the principal components extracted from the machine learning approaches revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
@@
 
-The machine learning models in the empirical approach consistently identified the first principal component as the predominant one.
+The machine learning methods in the empirical approach consistently identified the first principal component as the predominant one.
 Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
@@
 Additionally, much fewer principal components are needed for obtaining optimal performance of the machine learning algorithms for the empirical approach.
-The principal component analyses of the ML models' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
+The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
 Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.% instead without being guided by assumptions.

### 2022-02-27 paper_v3_cut.tex
Updates from Overleaf

--- 2022-02-27 paper_v2.tex
@@
 
-%\title{Predicting Solid State Qubit Candidates}
 \title{Predicting Solid State Material Platforms for Quantum Technologies}
@@
 \begin{abstract}
-Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, %scouring
-searching 
-these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
+%MB 
+%Original: 337 words
+%New: 256 words 
+%Wanted: 150 words
+
+%Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
+However, searching these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
 Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods.
 
-Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25.000$ materials.
+%Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25.000$ materials.
 The information from the databases was converted into nearly $5000$ physics-informed features.
-Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
-The three approaches define distinct datasets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
-
-We find that the Ferrenti approach and the extended Ferrenti approach predict a broad range of materials as suitable for quantum technologies.
+Furthermore, we have developed and implemented three different approaches for the data labeling process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
+The three approaches define distinct sets of labeled data for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
+
+%We find that the Ferrenti and extended Ferrenti approaches predict a broad range of materials as suitable for quantum technologies.
 The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
@@
 All four machine learning (ML) methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
-All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
+All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates
+%(to a probability of $>50 \ \%$) 
+%of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
+
+Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
+However, searching these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physcis-informed features.
+Three approaches were devised to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
+We find that of the three, the empirical approach relying exclusively on findings from the literature predicted substantially fewer candidates than the other two approaches with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+In contrast to expectations from the literature and that found for the the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
+All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates 
+%(to a probability of $>50 \ \%$) 
 of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
@@
 An important concern in this context is that of scalability. 
-For example, the best performing quantum computer prototypes available today rely on superconducting electronics, requiring millikelvin temperatures to operate, with challenging fabrication and the stability of interactions between qubits is an issue.
+For example, the best performing quantum computer prototypes available today rely on superconducting electronics that require millikelvin temperatures to operate, with the stability of interactions between qubits being an important issue.
 Instead, semiconductors are emerging as a promising alternative platform, offering competitive characteristics combined with the possibility of room temperature operation and mature and scalable material processing and fabrication.
 
-Quantum technologies based on semiconductors rely on either defects or quantum dots where the latter kind can be of the self-assembled or fabricated type. 
-Semiconductor defects can act as single-photon emitters or spin centers and are compatible with the three main QT categories of computing, communication and sensing.  
-These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap.
+Quantum technologies based on semiconductors rely on either defects or quantum dots where the latter can be of the self-assembled or nanostructured type \cite{Aharonovich_2016}. 
+Semiconductor defects can act as single-photon emitters or spin centers and are compatible with the three main QT categories of computing, communication and sensing \cite{Awschalom_2018}. 
+These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap \cite{Weber2010}.
 So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
-The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders especially for quantum communication purposes due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication \cite{Bathen2021}.
+The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders for quantum communication purposes especially due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication (see, e.g., Refs.~\cite{Castelletto_2015,Son2020,Bathen2021}).
 However, semiconductor based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
 Furthermore, we lack a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties,  
-and the selection of known quantum compatible host materials is slim.
-
-The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of which material requirements must be met for QT compatible characteristics (e.g.
-single-photon emission and manipulable spin states) to manifest.
+and the selection of known quantum compatible host materials is slim \cite{Atatuere2018,Zhang2020}.
+
+The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of which material requirements must be met for QT compatible characteristics like single-photon emission and single spin control to manifest.
 In this context, a framework for dedicated materials search and analysis is needed.
 
-The fourth science paradigm of big data driven science cover the potential of targeted search for promising material systems in which to expect QT compatible properties, see for example Ref.~\cite{Acin2018}.
+The fourth science paradigm of big data driven science reveals the potential of targeted search for promising material systems in which to expect QT compatible properties. 
+%, see for example Ref.~\cite{Acin2018}.
 Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
@@
 In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
-Combined with machine learning methods we provide a path towards precise classification of qubit candidates.
+Combined with machine learning methods we provide a path towards precise classification of candidate materials.
 The inclusion of machine learning methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
@@
 Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
-%\textit{En setning om discovery her??} 
-Analyzing the output of the machine learning methods reveals that, given a suitable initial dataset of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
+Analyzing the output of the machine learning methods reveals that, given a suitable initial set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 
-The approach we have developed relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+The developed approach relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
 An important aspect of our work is the database building and pertinent development of the datasets for machine learning methods.
-We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii)
-%Marianne I have now changed augmented Ferrenti to extended Ferrenti 
-\emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}. We find that the %former 
-two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}. The  
-%third and 
-empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
-Importantly, the empirical approach emphasizes features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
-%(to a $0.5$ cut-off)  
-Example materials include ZnGeP$_2$, MgSe, CdS, BP, BC$_2$N, BP, Ge, GeC, InP, and InAs. 
+We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
+We find that the two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
+The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
+The three resulting sets of labeled data were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+Example materials include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
 Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
+%Write better! 
+Importantly, our findings also reveal which material properties are weighted by the ML methods upon predicting a material as suitable for QT applications, thereby opening up for new  discoveries in the field of quantum technologies.
 
@@
 
-The information stream in this work can be regarded as many modular parts that are connected. 
-The initial step for gathering material data and building features is visualized by the  flowchart in Figure~\ref{fig:flowchart}. Moreover, Jupyter notebooks containing the full
-workflow in Python can be found at \cite{Ohebbi2021}.
-Initially, we start by extracting all entries in the Materials Project (MP) database that match a specific query. 
-The MP database contains ground state properties of different materials that are computed using density functional theory (DFT).
+The information stream in this work can be regarded as many inter-connected modular parts. 
+The initial step for gathering material data and building features is visualized by the outer flowchart in Figure~\ref{fig:flowchart} (Jupyter notebooks containing the full
+workflow can be found at \cite{Ohebbi2021}).
+We start by extracting all entries in the MP database that match a specific query. 
+The MP database contains ground state properties of different materials that are computed using density functional theory.
 The DFT calculations in the database were performed using the Vienna {\em ab initio} simulation package (VASP) \cite{Kresse1996} and the Perdew-Burke-Ernzerhof (PBE) \cite{Perdew1996} exchange-correlation functional to calculate the electronic structure of the materials.
@@
     \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
-    \caption{The data flow of the main project, starting from an initial MP query, and ending with a featurized dataset with entries from several other databases.
-To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects
-    (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) 
-    are obtained through a query to be used in the following featurization steps.
+    \caption{The project workflow starting from an initial MP query, and ending with a featurized dataset with entries from several other databases. 
+    To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
 This process is repeated iteratively until all the data has been featurized.
@@
 
-The conditions for the initial MP query are that the materials must derive from 
-%experimental data 
-the Inorganic Crystal Structure Database (ICSD) and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+The conditions for the initial MP query are that the materials must derive from the Inorganic Crystal Structure Database (ICSD) and have a band gap wider than $0.1$~eV to exclude metallic compounds.
 The ICSD is the world's largest database for completely identified inorganic crystal structures \cite{Allen1987,Zagorac2019}.
-%OH: corrected icsd citation to german one (different from nist)
 In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the databases OQMD  \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
@@
 
-Thereafter, we apply Matminer’s \cite{Ward2018} tools to generate thousands of features from the data. 
-Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
-This transformation is known as generating descriptors
-or features, however, we will in this work adopt the name featurization. 
-The open-source library of Matminer provides many tools to featurize existing features extracted from the Materials Project. 
-%MB I moved the below to methods 
-%To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}, which were used to generate a supervised machine learning framework called the MODnet.
-Their implementation provides featurization for a material's composition, structure and atomic sites.
-However, Matminer also provides featurization tools for a material's density of states (DOS) and band structure, therefore, we extend their implementation to facilitate such featurizations.
+After material extraction we apply tools from the open-source library Matminer \cite{Ward2018} to generate thousands of features from the data.
+We will refer to this process as featurization herein.
 A schematic visualization of the featurization process in Matminer is shown in  Fig.~\ref{fig:flowchart}
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ features selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
+The $39$ featurizers (each generates several features) selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
 The selection of features was kept rather wide as we do not want to make {\em ex ante} assumptions on which features best describe a solid state material platform for quantum technology.
 
-%It is important to note that 
-The constructed datasets encompass compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
+The constructed dataset encompasses compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
 Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
@@
 Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Thus, our results depend on the Materials Project database containing data with high quality.
+Thus, our results depend on the quality of data in the databases we employ.
 
@@
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training, test and validation sets for the machine learning methodss.
+The labeled data are then grouped into training, test and validation sets for the machine learning methods.
 
 Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
-Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures \cite{Bathen2021}[ I.
-Aharonovich, D.
-Englund, M.
-Toth, Nat.
-Photonics 2016, 10, 631], relatively few candidate materials are known to be suitable.
+Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable \cite{Atatuere2018,Zhang2020}.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
@@
 In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
-Additionally, to obtain defect-based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission, non-polar materials are assumed to be preferable.
-
-Transition metal elements are eliminated in this approach if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
-In this context, also the symmetry of the crystalline host may be important.
-Therefore, only phases which take on non-polar space groups are considered as suitable in this approach.
-The energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
-
-Next, unsuitable candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
-that crystallize in polar space groups, are calculated to be magnetic.
-These candidates have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors).
-The resulting complete set of labeled materials contains $1581$ materials where $35 \ \%$
+Moreover, non-polar materials are assumed to be preferable to obtain defect based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission.  
+Transition metal elements are eliminated if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
+Finally, the energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
+
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
+that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
+The resulting set of labeled materials contains $1581$ materials where $35 \ \%$
 are labeled as unsuitable and 
@@
 
-%The training set from the Ferrenti approach reveal that carbon in a diamond-like structure is classified as a suitable candidate, in good agreement with experimental observations, (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
-Interestingly, in the training set from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are labeled as suitable as well.
-All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the 3C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, 4H-SiC, is missing from the training set.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.
-
 \subsubsection*{The extended Ferrenti approach}
-In the second approach, we adjust the former one in order to expand the training set beyond practical considerations. This approach is therefore named \emph{the extended Ferrenti approach}.
-
-In the first approach we included criteria that were 
-%not physically motivated, but instead 
-to some extent based on a practical perspective, such as excluding toxic and radioactive elements.
-Such criteria are not necessarily related to what makes a material suitable for quantum technology - eventually it is up to the experimentalist to decide the feasibility of the material to be employed.
-Consequently, in the extended Ferrenti approach, we remove stage two from the approach above.
+Here, we adjust the Ferrenti approach to expand the data labeling process beyond practical  considerations.
+The second approach is therefore named \emph{the extended Ferrenti approach} and involves removing stage two from the approach above.
 Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
@@
     \item Only keep materials that have a band gap larger than $1.5$~eV in the MP database.
-The higher band gap requirement (as compared to the Ferrenti approach) is included here %to avoid including an unfeasible number of candidate materials in the training set.
-    to avoid labeling an unfeasibly large number of materials. 
+The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid labeling an unfeasibly large number of materials.
     \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
@@
 
-For unsuitable candidates, we implement the same strategy as for the first Ferrenti approach.
+For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
 The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
@@
 
-%MB I moved this down to not confuse the order of information 
-% 
-% In the training set of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The training set includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to restrict the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the training set.
-
 \subsubsection*{The empirical approach}
-The third approach differs substantially from the first two approaches in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Zhang2020,Son2020,Toth2019,Bathen2021} for an overview) to pick our promising material host candidates.
+The third approach differs substantially from the others in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to pick our promising material host candidates.
 In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
 
-Table~\ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics (e.g., single-photon emission and coherent spin manipulation).
+Table~\ref{tab:qt-materials} contains an overview of known semiconductor materials with demonstrated quantum compatible characteristics.
 The table forms the basis for picking suitable candidates for the empirical approach.
@@
 Quantum emission signatures have been assigned to specific defects in both diamond and SiC, but for most other materials, secure identification of the responsible defects or structure related mechanism is still lacking.
-
-%In the empirical approach, we include materials that are known to be quantum compatible as outlined in Table~\ref{tab:qt-materials} in the training set.
-Additionally, we also include materials matching the formulas ZnSe, AlP, GaP, AlAs, ZnTe, CdS and SiGe as these materials have been predicted to behave as suitable quantum hosts based on favorable properties such as a wide band gap and low spin-orbit coupling \cite{Weber2010,Hardy2019}.
 
@@
     \centering 
-    \caption{Overview of materials and defects that have been demonstrated to exhibit QT compatible characteristics such as single-photon emission and coherent spin manipulation.}
+    \caption{Overview of materials and defects that have been demonstrated to exhibit quantum  compatible characteristics such as single-photon emission and coherent spin manipulation.}
     \begin{tabular}{c|c|c|c}
@@
 After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
-These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially above $0.5$~eV.
-We include all of the $202$ structures apart from C (mp-$568410$) which has a PBE-computed band gap of $0.12$~eV; i.e., a metal according to AFLOW-ML and it is therefore labeled as an unsuitable candidate.
+These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than $0.5$~eV.
+We include all of the $202$ structures apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
 
@@
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-We note that only tetrahedrally coordinated structures of the given formulas were included in the training set after imposing a band gap restriction of $0.5$~eV.
-
-After the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set. 
+We note that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of $0.5$~eV.
+
+Following the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set. 
 Notably, the candidates labeled as suitable in the empirical approach contain only compounds that are either elementary (unary) or binary. 
-We want to avoid discriminating based on the number of elements in a compound, and therefore we remove the feature that describes the number of elements in a compound. 
-Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, we add $400$ candidates that are labeled as \emph{unsuitable}.
+Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, we add $400$ candidates that are labeled as \textbf{unsuitable}.
 These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
@@
 Thus, the first approach targets a more narrow prediction space than the second approach does.
-However, perhaps the most restricted approach is the empirical one.
-Since the variety of known suitable materials is substantially smaller than for the two other approaches, we would expect the empirical approach to provide an even narrower prediction space.
-%Here, one should keep in mind that ...
+However, the most restricted approach is the empirical one, relying exclusively on previous findings rather than assuming which material properties are important.
 
@@
 %summary - do we need this? 
-In summary, using various data extraction tools for a number of materials science databases, we have obtained a dataset consisting of over $25.000$ materials.
+%In summary, using various data extraction tools for a number of materials science databases, we have obtained a dataset consisting of over $25.000$ materials.
 The information from this dataset has then been converted into nearly $5000$ physics-informed features.
@@
 This process will allow us to classify specific materials as potential candidates for quantum technology applications.
+
+%Include a discussion on the difficulty of labeling unsuitable candidates. 
+As mentioned above, a
 

### 2022-02-27 paper_v2.tex
Updates from Overleaf

@@
 these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and ML methods.
 
@@
 Furthermore, we have developed and implemented three different approaches for the data mining process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
-The three approaches define distinct datasets for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
+The three approaches define distinct datasets for the supervised ML methods logistic regression, decision trees, random forests and gradient boosting.
 
@@
 In contrast to the machine learning (ML) methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
-All four machine learning (ML) methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
-All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
+All four ML methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates %(to a probability of $>50 \ \%$) 
 of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
@@
 In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
-Combined with machine learning methods we provide a path towards precise classification of qubit candidates.
-The inclusion of machine learning methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
-
-Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
+Combined with ML methods we provide a path towards precise classification of qubit candidates.
+The inclusion of ML methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
+
+Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and ML methods combined with knowledge from the field.
 %\textit{En setning om discovery her??} 
-Analyzing the output of the machine learning methods reveals that, given a suitable initial dataset of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
+Analyzing the output of the ML methods reveals that, given a suitable initial dataset of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important aspect of our work is the database building and pertinent development of the datasets for machine learning methods.
+An important aspect of our work is the database building and pertinent development of the datasets for ML methods.
 We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii)
@@
 empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three training sets were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+The three training sets were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and ML methods.
 Importantly, the empirical approach emphasizes features like the standard deviations  of  the  radial  distribution  function  (RDF) and average bond length as critical features for suitable QT compatible materials.
@@
 Thereafter, we apply Matminer’s \cite{Ward2018} tools to generate thousands of features from the data. 
-Before applying any machine learning algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
+Before applying any ML algorithm, the data was transformed into a numerical representation that reflects the relationship between the input and output data.
 This transformation is known as generating descriptors
@@
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training, test and validation sets for the machine learning methodss.
+The labeled data are then grouped into training, test and validation sets for the ML methods.
 
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training, testing and validation of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects - even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
 Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, we only admit two-dimensional structures.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the machine learning methods that are applied in a later stage.
+For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML methods that are applied in a later stage.
 
@@
 To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
-Principal component analysis falls under the category of unsupervised learning within machine learning methods.
-Here we apply PCA to the labeled datasets in order to figure out if are specific features that stand out.
+Principal component analysis falls under the category of unsupervised learning within ML methods.
+Here we apply PCA to the labeled datasets in order to figure out if there are specific features that stand out.
 In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
@@
 In essence, we reduce the dimensionality of the labeled data in order to visualize them.
-The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
+The result of this procedure is displayed in the scatter plots of Fig.~\ref{fig:2dscatterplotpca}.
 Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of
@@
 This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training, testing and validation of the machine learning methods.
+Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training, testing and validation of the ML methods.
 
@@
 These are logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
+These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
 This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
@@
 %In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT,
-we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches.
+we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
 
- In the evaluation of the machine learning methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-We note that all four machine learning methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the machine learning methods and the results from the principal component analyses for all four machine learning methods are shown in the Supplementary Material at \cite{supplementary}.
+ In the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material at \cite{supplementary}.
 
@@
 %Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
-The three approaches define labeled data of varying size, where the smallest is from the empirical approach.
-For small datasets, it is proven beneficial to repeat the cross-validation, as this is a method that allows us to measure the stability of the predictions given against pertubations (i.e.
-few different entries) of the training data \cite{Beleites2008}.
+The three data set approaches (Ferrenti, extended Ferrenti and empirical) define labeled data of varying size, where the smallest is from the empirical approach.
+For small datasets, it is proven beneficial to repeat the cross-validation analysis \cite{Hastie2009}, as this is a method that allows us to measure the stability of the predictions  against perturbations (i.e.
+few different entries) in the training data \cite{Beleites2008}.
 
@@
 %for larger principal component values. 
-when involving more principal components. Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for just a few principal components. 
+when involving more principal components. Gradient boosting, in contrast to the case for the two Ferrenti  approaches, also experiences the best performance for just a few principal components. 
 \begin{figure}[ht]
@@
 
-Fig.~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Figure~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
-The second most important principal component for the Ferrenti approach is the second one. 
-The second component's largest values correspond to the 
+The second most important principal component for the Ferrenti approach receives significant contributions from the  
 %electronegativity, ionic property, and covalence radius 
-covalent radius, ionic character and packing efficiency  
+covalent radius, the ionic character and the packing efficiency  
 among the elements in the composition. 
 The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
-While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
+While the first principal component encompasses the largest explained variance, it does not provide a clear and  specific information on which features it represents.
 
@@
 The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
-We find, for logistic regression and decision trees, that no feature is different than any other in the cross-validation due to a large variety of accuracy.
-However, we find that random forests and gradient boosting experience the fifth principal component as important.
+We find, for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
+However, we find that random forests and gradient boosting show the importance of  fifth principal component.
 Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
@@
 Notably, these features were used as guidance in the initial selection process when forming the training sets.
-Thus, the machine learning methods appear to preserve the criteria imposed in the Ferrenti approaches.
+Thus, the ML methods appear to preserve the criteria imposed in the Ferrenti approaches.
 For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate.
-Rather than focusing on, e.g., the band gap, the machine learning methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In this approach, the machine learning methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Rather than focusing on, e.g., the band gap, the ML methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In this approach, the ML methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
 An overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence is summarized in Table~\ref{tab:probabilites}.
@@
 From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
 If we were to raise the minimum confidence cut-off for a prediction to e.g.
 $0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
-We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our machine learning methods. 
-For example, the machine learning methods do not perpetuate the band gap restriction from the training set definition. 
+We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data. 
+This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our ML methods. 
+For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
 Based on the restrictions we defined initially, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated 
@@
 Although this is expected behavior based on the data labeling process, the trend is not carried over to the predicted data.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four machine learning methods employed herein,
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
 indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
@@
 than the Ferrenti approach.  
-The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
 % rewrite?? 
-However, the machine learning methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter.
+However, the ML methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter. 
 % 
@@
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented machine learning methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the machine learning methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
-As we based this band gap restriction on assumptions for important material parameters in the QT context, the machine learning methods might be picking up on something we did not anticipate.
+Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
+As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we did not anticipate.
 
 \subsubsection*{The empirical approach}
-The machine learning methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
+The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four machine learning methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
+All the four ML methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
 Although this is comparable to the probability of a coin toss, the agreement of the four machine learning algorithms lends support to the suitability of the $214$ materials. 
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
 The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning methods after training on the dataset resulting from the empirical approach.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods after training on the dataset resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all machine learning methods in the extended Ferrenti approach.
+We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
@@
 
-The machine learning methods in the empirical approach consistently identified the first principal component as the predominant one.
+The ML methods in the empirical approach consistently identified the first principal component as the predominant one.
 Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
@@
 Two main routes can be followed to exploit the results.
-One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four machine learning methods.
+One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four ML methods.
 Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
@@
 
-In this work we have applied four well-known and tested machine learning methods for classification problems, these are (see for example \cite{Hastie2009,Mehta2019} for discussions and applications):
+In this work we have applied four well-known and tested ML methods for classification problems, these are (see for example \cite{Hastie2009,Mehta2019} for discussions and applications):
 \begin{enumerate}
@@
 Boosting methods like gradient boosting use decision trees as  weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under study, leading to a machine learning method that exhibits a high variance.
+Pure decision trees can easily lead to overfitting of the data under study, leading to an ML method that exhibits a high variance.
 Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.

### 2022-02-27 paper_v2.tex
Updates from Overleaf

@@
 
-The principal components that are deemed important by the three approaches are distinct on multiple levels.
-The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
+The principal components that are deemed important by the three approaches exhibit several differences.
+The Ferrenti and extended Ferrenti approaches place particular value on the band gap of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
 Notably, these features were used as guidance in the initial selection process when forming the training sets.
@@
 After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
-An overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence is summarized in Table~\ref{tab:probabilites}.
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}.
 
@@
     \centering 
-    \caption{Overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence when the four methods in an approach agree.
+    \caption{Overview of the number of predicted suitable candidates as a function of a given ML method's confidence when the four methods in an approach agree.
 A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
@@
 The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
-Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems using examples and  Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
+Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems.
+Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
 Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
@@
 
-Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this a partial explanation for why the models recognize BN as a suitable candidate with high probability.
+Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the models recognize BN as a suitable candidate with high probability.
 Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
@@
 %BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN. 
-Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
 Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.

### 2022-02-27 paper_v2.tex
Updates from Overleaf

@@
 Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials for the empirical approach.  
-The full list of these $66$ is contained in the Supplementary Material at \cite{supplementary}. 
+The full list of these $66$ candidates is displayed in the Supplementary Material at \cite{supplementary}. 
 The list of predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$, in addition to elemental and binary semiconductors, and the nine materials listed above.
@@
 
-Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
+Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
 Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods after training on the dataset resulting from the empirical approach.
@@
 \subsubsection*{Comparing the approaches}
-Comparing the three approaches (see Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
-The Ferrenti approach also admits a large amount of materials through from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manually verification is achievable.
+Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence cut-off value.
+The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manual verification is possible.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
-We note that none of these were admitted through for the empirical approach when the confidence cut-off was set to $0.75$ or higher.
+We note that none of these were incluced by the empirical approach when the confidence cut-off was set to $0.75$ or higher.
 

### 2022-02-27 paper_v2.tex
Updates from Overleaf

@@
 
-The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of which material requirements must be met for QT compatible characteristics (e.g.
-single-photon emission and manipulable spin states) to manifest.
+The majority of discoveries of QT compatible characteristics in semiconductors has so far happened by serendipity, and there is an urgent need for a better and more systematic understanding of which material requirements must be met for QT compatible characteristics (e.g., single-photon emission and manipulable spin states) to manifest.
 In this context, a framework for dedicated materials search and analysis is needed.
@@
 All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to e.g.
-$0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
+If we were to raise the minimum confidence cut-off for a prediction to e.g., $0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data. 
@@
 %The maximum ionic character is also deemed an important part of PC2. 
-Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters  for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+Intriguingly, as shown in Fig.~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters  for all three approaches - even peaking at a relatively high ionic character of $0.8$.
 Moreover, we find that the covalent radii of the materials (see the Supplementary Material) distribute with two peaks in the data in all approaches. 
@@
 At most three different elements are present, but the emphasis is clearly on binary compounds.
-This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in e.g.
-bond length and symmetry.
+This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in e.g., bond length and symmetry.
 This is  in

### 2022-02-27 paper_v3_cut.tex
Updates from Overleaf

@@
 However, searching these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning (ML) methods.
 
@@
 Furthermore, we have developed and implemented three different approaches for the data labeling process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
-The three approaches define distinct sets of labeled data for the supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting.
+The three approaches define distinct sets of labeled data for the supervised ML methods logistic regression, decision trees, random forests and gradient boosting.
 
 %We find that the Ferrenti and extended Ferrenti approaches predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to the machine learning (ML) methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
-All four machine learning (ML) methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
+The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the ML methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
+All four ML methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
 All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates
@@
 In contrast to expectations from the literature and that found for the the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
-All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates 
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
 %(to a probability of $>50 \ \%$) 
@@
 In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
-Combined with machine learning methods we provide a path towards precise classification of candidate materials.
-The inclusion of machine learning methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
-
-Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and machine learning methods combined with knowledge from the field.
-Analyzing the output of the machine learning methods reveals that, given a suitable initial set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
+Combined with ML methods we provide a path towards precise classification of candidate materials.
+The inclusion of ML methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
+
+Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and ML methods combined with knowledge from the field.
+Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important aspect of our work is the database building and pertinent development of the datasets for machine learning methods.
+An important aspect of our work is the database building and pertinent development of the datasets for the ML methods.
 We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
@@
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three resulting sets of labeled data were then analyzed with the four supervised machine learning methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and machine learning methods.
+The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and ML methods.
 Example materials include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
@@
 A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training, test and validation sets for the machine learning methods.
+The labeled data are then grouped into training, test and validation sets for the ML methods.
 
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training, testing and validation of the machine learning methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training, testing and validation of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
 %Ferrenti 
-Considering the materials present in the labeled datasets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}) and hence also with the candidates that were manually defined as suitable in the empirical approach.
+Considering the materials present in the labeled datasets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}).
 Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
@@
 Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
-% from the training set. 
 Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.  
@@
 The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the labeled dataset.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the labeled data.
 
@@
     \caption{Parallel coordinate plots for the different approaches.
-To limit the data cluttering, we have randomly collected up to $250$ entries for each class and made the lines transparent.
+To limit data cluttering, we have randomly collected up to $250$ entries for each class.
 For the empirical approach, we have used all the $187$ suitable candidates.
-The axes show total magnetization (mag) taken from the Materials Project (MP) database along with the space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) extracted from MP.}
+The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}
     \label{fig:parallel-coordinates-approaches}
@@
 We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, we have transformed the three datasets resulting from the three approaches and visualized them as scatter plots.
+Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots.
 Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
@@
 The most striking difference is found for the empirical approach.
-The entries labeled as suitable candidates do not exhibit any magnetization, and the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti-based approaches.
+The entries labeled as suitable candidates do not exhibit any magnetization, and the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti approaches.
 Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
@@
 In this work we have applied
-four well-tested machine learning algorithms in order to classify specific materials as candidate systems for QT.
+four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
 These are logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four machine learning methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
+These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
 This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
@@
 In order to reduce the dimensionality while preserving most of the variance in the data,
-%In order to deduce how the different material features are weighted by the four machine learning models when classifying materials into suitable and unsuitable candidates for QT,
-we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches.
+%In order to deduce how the different material features are weighted by the four ML methods when classifying materials into suitable and unsuitable candidates for QT,
+we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value,  resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
 
- In the evaluation of the machine learning methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-We note that all four machine learning methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the machine learning methods and the results from the principal component analyses for all four machine learning methods are shown in the Supplementary Material at \cite{supplementary}.
+ In the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material at \cite{supplementary}.
 
 %OH: Downsides. Could also be moved to methods?
-%We observe that there are several potential pitfalls of using the chosen dimensionality reduction and machine learning techniques in this paper.
+%We observe that there are several potential pitfalls of using the chosen dimensionality reduction and ML techniques in this paper.
 PCA is a trivial algorithm that only accounts for linear correlation between features, where other algorithms, such as Kernel PCA, can facilitate non-linear dimensionality reduction but with higher computational demand.
@@
 %Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
-The three approaches define labeled data of varying size, where the smallest is from the empirical approach.
-For small datasets, it is proven beneficial to repeat the cross-validation, as this is a method that allows us to measure the stability of the predictions given against pertubations (i.e.
-few different entries) of the training data \cite{Beleites2008}.
+The three data labeling approaches (Ferrenti, extended Ferrenti and empirical) define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
+For small datasets, it is proven to be beneficial to repeat the cross-validation analysis \cite{Hastie2009}, as this is a method that allows us to measure the stability of the predictions against perturbations (i.e., few different entries) in the training data \cite{Beleites2008}.
 
@@
 
-Fig.~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Figure~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
-The second most important principal component for the Ferrenti approach is the second one. 
-The second component's largest values correspond to the 
-%electronegativity, ionic property, and covalence radius 
-covalent radius, ionic character and packing efficiency  
-among the elements in the composition. 
+The second most important principal component for the Ferrenti approach receives significant contributions from the covalent radius, the ionic character and the packing efficiency among the elements in the composition.
 The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
-While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
+While the first principal component encompasses the largest explained variance, it does not provide a clear and specific information on which features it represents.
 
@@
 The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
-We find, for logistic regression and decision trees, that no feature is different than any other in the cross-validation due to a large variety of accuracy.
-However, we find that random forests and gradient boosting experience the fifth principal component as important.
+We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
+However, we find that random forests and gradient boosting show the importance of the fifth principal component.
 Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
@@
 
-The principal components that are deemed important by the three approaches are distinct on multiple levels.
-The Ferrenti and extended Ferrenti approaches place particular value on the band gap, of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
+The principal components that are deemed important by the three approaches exhibit several differences.
+The Ferrenti and extended Ferrenti approaches place particular value on the band gap of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
 Notably, these features were used as guidance in the initial selection process when forming the training sets.
-Thus, the machine learning methods appear to preserve the criteria imposed in the Ferrenti approaches.
+Thus, the ML methods appear to preserve the criteria imposed in the Ferrenti approaches.
 For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate.
-Rather than focusing on, e.g., the band gap, the machine learning methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In this approach, the machine learning methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Rather than focusing on, e.g., the band gap, the ML methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In this approach, the ML methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
@@
 %In this section, 
-After training the machine learning approaches using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four machine learning methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches.
-An overview of the number of predicted suitable candidates as a function of a given machine learning approach's confidence is summarized in Table~\ref{tab:probabilites}.
+After training the ML algorithms using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}.
 
@@
 From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four machine learning methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to e.g.
-$0.75$ instead of $0.5$, the above machine learning algorithms would only agree on $1784$ suitable candidates.
-We find that all four machine learning methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our machine learning methods. 
-For example, the machine learning methods do not perpetuate the band gap restriction from the training set definition. 
+All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
+We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data. 
+This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our ML methods. 
+For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
 Based on the restrictions we defined initially, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated 
 %for a cut-off set to above $0.5$ 
-after applying the machine learning algorithms.  
+after applying the ML algorithms.  
 Although this is expected behavior based on the data labeling process, the trend is not carried over to the predicted data.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four machine learning methods employed herein,
-indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the machine learning algorithms --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
+We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
+indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
 On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
@@
 than the Ferrenti approach.  
-The four machine learning methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
 % rewrite?? 
-However, the machine learning methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter.
+However, the ML methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter. 
 % 
-All four machine learning algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations,  which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
+All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations,  which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
 Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented machine learning methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the machine learning methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
-As we based this band gap restriction on assumptions for important material parameters in the QT context, the machine learning methods might be picking up on something we did not anticipate.
+Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
+As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we did not anticipate.
 
 \subsubsection*{The empirical approach}
-The machine learning methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
+The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
-All the four machine learning methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
-Although this is comparable to the probability of a coin toss, the agreement of the four machine learning algorithms lends support to the suitability of the $214$ materials. 
+All the four ML methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
+Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
 Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four machine learning methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
+Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
 The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
-Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems using examples and  Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
+Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems.
+Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
 Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
@@
 The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
-%BC$_2$N is known as heterodiamond and is a hybrid of diamond and BN. 
-Both structures exhibit, as expected, strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
 Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.
@@
 
-Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggests a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four machine learning methods after training on the dataset resulting from the empirical approach.
+Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods after training on the dataset resulting from the empirical approach.
 This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
@@
 \subsubsection*{Comparing the approaches}
-Comparing the three approaches (see Table~\ref{tab:probabilites}), we observe  that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries through to the predictions regardless of the confidence cut-off value.
-The Ferrenti approach also admits a large amount of materials through from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manually verification is achievable.
+Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence cut-off value.
+The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manual verification is possible.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all machine learning methods in the extended Ferrenti approach.
+We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
-All approaches and their corresponding machine learning models agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
+All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
 (see the Supplementary Material at \cite{supplementary} for the full list). 
@@
 However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
-We note that none of these were admitted through for the empirical approach when the confidence cut-off was set to $0.75$ or higher.
+We note that none of these were included by the empirical approach when the confidence cut-off was set to $0.75$ or higher.
 
@@
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we find important differences between the three labeling approaches, and can start to discern the driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the machine learning approaches revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
@@
 The exact degree and type of symmetry is still open to debate and should be studied further.
-Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the machine learning algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
@@
 At most three different elements are present, but the emphasis is clearly on binary compounds.
-This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in e.g.
-bond length and symmetry.
+This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in, e.g., bond length and symmetry.
 This is  in
@@
 Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
-Three distinct sets of labeled data were defined for training, testing and validation of four different machine learning algorithms (logistic regression, decision trees, random forests and gradient boosting).
+Three distinct sets of labeled data were defined for training, testing and validation of four different ML algorithms (logistic regression, decision trees, random forests and gradient boosting).
 
@@
 To summarize, the data extraction tools developed in this work resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
-Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four machine learning algorithms.
-We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti based ones. 
-Additionally, much fewer principal components are needed for obtaining optimal performance of the machine learning algorithms for the empirical approach.
+Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four ML algorithms.
+We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
+Additionally, much fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach.
 The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
@@
 Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap.
-The accuracy is validated by a five-fold cross-validation process for each machine learning method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
+The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
 In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
@@
 Boosting methods like gradient boosting use decision trees as  weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under study, leading to a machine learning method that exhibits a high variance.
+Pure decision trees can easily lead to overfitting of the data under study, leading to a ML method that exhibits a high variance.
 Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.

### 2022-03-01 paper_v3_cut.tex
Updates from Overleaf

@@
 For example, the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
-The two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
-
+Moreover, two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
+%Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
 The most striking difference is found for the empirical approach.
-The entries labeled as suitable candidates do not exhibit any magnetization, and the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti approaches.
+Again, the entries labeled as suitable candidates do not exhibit any magnetization, but now the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti approaches.
 Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
@@
 Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
-%Identification of the features that promote quantum compatible  characteristics could be crucial for targeted quantum device design based on careful material selection, nanostructuring and defect engineering.
 
 To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
-Principal component analysis falls under the category of unsupervised learning within ML methods.
+Principal component analyses fall  under the category of unsupervised learning within ML  methods.
 Here we apply PCA to the labeled datasets in order to figure out if there are specific features that stand out.
@@
 In essence, we reduce the dimensionality of the labeled data in order to visualize them.
-The result of this procedure is displayed in the scatter plots of Fig.~\ref{fig:2dscatterplotpca}.
-Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of
-removing the mean and scaling to unit variance.
-%centering the data. 
+The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
+Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of removing the mean and scaling to unit variance.
 Red triangles represent unsuitable candidates while colored symbols (green, blue, black and yellow) represent suitable candidates.
@@
 Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-We expect therefore that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
+We therefore expect that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
 
@@
 
-%This paragraph is very diffuse and do not really say anything. I propsoe we remove it.
-%It seems probable that the differences in Fig.~\ref{fig:2dscatterplotpca} can be attributed to the specific choices made when extracting data in each of the three approaches.
-Where the empirical approach takes advantage of the experimental and theoretical knowledge that is available in the literature, the Ferrenti and extended Ferrenti schemes rely on assumptions for which material properties are responsible for the desired quantum effects.
-An additional factor to consider is the use of practical considerations (e.g., toxic materials or the availability of spin zero isotopes) when restricting the parameter space for material choice.
-%Intriguingly, a much clearer separation is observed for the empirical approach, where no restrictions were imposed in terms of specific characteristics for the materials, as compared to the two others.
-%These observations constitute an important finding of our work, as we show that it is possible to distinguish between suitable and unsuitable material candidates for QT based on a principal components analysis.
-The manual approach for selecting suitable candidates based on experimental findings yields strong indications that a trend does exist and thus is possible to identify.
-%This will be an important goal of a future work. 
-%Importantly, the methodology for selecting candidates as implemented in the empirical approach can be adapted also to other material systems where a specific set of properties is desired (and observed or predicted for a sufficient number of materials) but the specific mechanisms behind them are unknown.
+%Include a discussion on the difficulty of labeling unsuitable candidates.
 
@@
 
-%Include a discussion on the difficulty of labeling unsuitable candidates. 
-As mentioned above, a
-
 \subsection*{Machine learning and principal component analysis}
-In this work we have applied
-four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
-These are logistic regression, decision trees, and ensemble methods like random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets).
-This yielded twelve sets of materials that were predicted as suitable material hosts for QT applications.
+In this work we have applied four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
+These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
+These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets), yielding twelve sets of materials that were predicted as suitable material hosts for QT applications.
 
 In order to reduce the dimensionality while preserving most of the variance in the data, 
-%In order to deduce how the different material features are weighted by the four ML methods when classifying materials into suitable and unsuitable candidates for QT,
-we have performed a principal component analysis (PCA) \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+we have performed a principal component analysis  \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
-
- In the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+%
+Next, in the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
 We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
 Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material at \cite{supplementary}.
-
-%OH: Downsides. Could also be moved to methods?
-%We observe that there are several potential pitfalls of using the chosen dimensionality reduction and ML techniques in this paper.
-PCA is a trivial algorithm that only accounts for linear correlation between features, where other algorithms, such as Kernel PCA, can facilitate non-linear dimensionality reduction but with higher computational demand.
-Additionally, by using a trivial PCA, we make an assumption of orthogonality, since the eigenvectors are orthogonal to each other.
-However, there might exist an non-orthogonal basis which captures the non-orthogonal data in the dataset better.
-
-%Beneficial to use simple ML-methods for small datasets, since more advanced methods need (ALOT) more data to perform good
+%
 The three data labeling approaches (Ferrenti, extended Ferrenti and empirical) define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
@@
 Note also that in  Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
-In the ML analysis here the model development is done on the training and validation set.
-%Fig.~\ref{fig:PComponents}(a) displays the principal components as they are sorted in descending order by the explained variance. 
+In the ML analysis here the model development is done on the training and validation sets.
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$.
-
-In the case of the empirical approach and in contrast to the Ferrenti based approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting
-%for larger principal component values. 
-when involving more principal components. Gradient boosting, in contrast to the case for the two Ferrenti  approaches, also experiences the best performance for just a few principal components. 
-\begin{figure}[ht]
+For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components.
+%
+In the case of the empirical approach and in contrast to the Ferrenti approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
+Gradient boosting
+%, in contrast to the case for the two Ferrenti  approaches, 
+also experiences the best performance for just a few principal components.
+
+\begin{figure}[t]
     \centering
@@
     \end{subfigure}
-    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-Note well that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training and validation sets using gradient boosting \cite{Hastie2009,xgboost2016}.
-The latter shows that for the empirical approach most of the physics is represented by few features (see text for an in depth discussion).
+    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
+Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training and validation sets using gradient boosting \cite{Hastie2009,xgboost2016}.
+The latter shows that for the empirical approach most of the physics is represented by a few features.
 The results in (b) are similar to those obtained with logistic regression, decision trees and random forests.
@@
 
-Figure~\ref{fig:PComponents}(b) reveals that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
-Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
-The second most important principal component for the Ferrenti approach receives significant contributions from the covalent radius, the ionic character and the packing efficiency among the elements in the composition.
+Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
+The second most important principal component for the Ferrenti approach exhibits significant contributions from the covalent radius, the ionic character and the packing efficiency among the elements in the composition.
 The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
@@
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
-However, we find that random forests and gradient boosting show the importance of the fifth principal component.
+However, we find that random forests and gradient boosting both mark the fifth principal component as important.
 Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
@@
 %empirical approach 
-% OH: This paragraph is a duplicate from supplementary
 The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
-%Firstly, for the empirical approach, the gradient boosting model performs optimally at $13$ principal components with a mean F$1$-score of $0.96$. 
-Firstly, We find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
+Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
 Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b).
-Similar conclusions are reached using logistic regression, decisions trees and random forests as classification methods, lending thus support to our main conclusions.
-
-This is part of the reason why we experience a large accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details).
+Similar conclusions are reached when using logistic regression, decisions trees and random forests as classification methods, lending support to our observations.
+The distinct importance of the first principal component partly explains why we experience a high accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details).
 The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
-Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti  and $11 \ \%$ for the extended Ferrenti approach.
+Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
 We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
 
-The principal components that are deemed important by the three approaches exhibit several differences.
-The Ferrenti and extended Ferrenti approaches place particular value on the band gap of both the predicted compounds and the elemental solids, as well as features such as the ionic or covalent character of the bonding.
-Notably, these features were used as guidance in the initial selection process when forming the training sets.
-Thus, the ML methods appear to preserve the criteria imposed in the Ferrenti approaches.
-For the empirical approach, we did not guide the selection process in terms of specific properties, thus, other properties dominate.
-Rather than focusing on, e.g., the band gap, the ML methods appear to be informed by other characteristics more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In this approach, the ML methods appear to be inferring that the common trend among the materials that are suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+Intriguingly, the principal components that are deemed important by the three approaches differ substantially.
+The Ferrenti and extended Ferrenti approaches place particular value on the material's band gap and the ionic or covalent character of the bonding.
+Indeed, precisely these features were used as guidance in the data labeling process.
+Thus, the ML methods are preserving the criteria imposed in the Ferrenti approaches and perpetuate our initial biases on which material properties to look for.
+For the empirical approach, on the other hand, we did not guide the selection process in terms of specific properties.
+Here, the ML methods appear to be informed by other  characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In the empirical approach, the ML methods appear to be inferring that the common trend among the materials that are known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
 
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology} 
-%In this section, 
 After training the ML algorithms using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
@@
 An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in  Table~\ref{tab:probabilites}.
+
+\subsubsection*{The Ferrenti approach}
+
+We first consider the machine learning classification of the test set derived in the Ferrenti approach.
+From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
+All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
+We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
+This can allow materials with unfortunate structures to be labeled as suitable candidates.
+Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than $0.5$~eV were eliminated.
+This trend is not carried over to the predicted data. Indeed, we find that many entries with band gaps lower than $0.5$~eV are predicted as suitable candidates by all four ML methods employed herein 
+%indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
+--- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.  
+On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
 
@@
 
-\subsubsection*{The Ferrenti approach}
-
-We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
-From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
-We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data. 
-This can allow materials with unfortunate structures to be labeled as suitable candidates. %by all of our ML methods. 
-For example, the ML methods do not perpetuate the band gap restriction from the training set definition. 
-Based on the restrictions we defined initially, we would expect that all materials with band gaps lower than $0.5$~eV would be eliminated 
-%for a cut-off set to above $0.5$ 
-after applying the ML algorithms.  
-Although this is expected behavior based on the data labeling process, the trend is not carried over to the predicted data.
-We find that many entries with band gaps lower than $0.5$~eV are predicted as both suitable and unsuitable candidates by all four ML methods employed herein,
-indicating that the exact cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
-On the other hand, due to the known underestimation of band gaps by the PBE functional, the band gaps could in reality be larger for many of the materials.
-
 \subsubsection*{The extended Ferrenti approach}
 Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger 
-amount of labeled data  
-than the Ferrenti approach.  
+amount of labeled data than the Ferrenti approach.  
 The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
-% rewrite?? 
-However, the ML methods also yield predictions that do not match with the expectation that we are looking for a covalently bonded semiconductor to host a sharp and bright quantum emitter. 
-% 
-All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations,  which was unexpected due to the strong electrostatic interactions between Na and Cl and the ionic character of their bonding (see, e.g., Ref.~\cite{Weber2010}).
-Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Moreover, despite enforcing an even more conservative band gap restriction of $1.5$~eV for the training set as compared to the Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
-Clearly, the ML methods are not adhering rigidly to our imposed band gap restriction when classifying the materials. 
-As we based this band gap restriction on assumptions for important material parameters in the QT context, the ML methods might be picking up on something we did not anticipate.
+However, the ML methods also predict materials as suitable that we would not expect according to, e.g., \citeauthor{Weber2010} \cite{Weber2010}. 
+All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+%Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
+Furthermore, although we enforced a conservative band gap restriction of $1.5$~eV for the data labeling in the extended Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+As seen above, the ML methods applied to data labeled in the Ferrenti and extended Ferrenti approach are recognizing the band gap and bonding character as important, but the resulting predicted materials do not strictly follow the anticipated guidelines.
 
@@
 All the four ML methods agree on a total of $214$ suitable candidates to $0.5$ confidence.
-Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
+%Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
 Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
-Increasing the confidence cut-off to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
+Increasing the threshold to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
+
+Consider the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
+The nine materials (considering different crystal structures) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
+Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems while Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as reported in the MP database.
+Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
+There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.
 
@@
 
-%\begin{table}[b]
- %   \centering 
- %   \caption{Grouping of predicted materials (above $0.75$ confidence) into the four appearing crystal systems.
-The $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$) are considered.
-}
- %   \begin{tabular}{c|c c c c}
- %     & Cubic & Hexagonal & Tetragonal & Orthorombic \\
- %   \hline 
- %   Empirical approach & CuI (mp-$22895$) & CuI (mp-$569346$) & BC$_2$N (mp-$1008523$) & BC$_2$N (mp-$629458$) \\
- %   to $0.85$ confidence & CdSe (mp-$2691$) & CdSe (mp-$1070$) & & \\
- %    & BN (mp-$1639$) & & & \\
- %    & InAs (mp-$20305$) & & & \\
- %    & ZnCd$_3$Se$_4$ (mp-$1078597$) & & & \\
- %   \hline 
- %   All approaches & InP (mp-$20351$) & InP (mp-$966800$) & ZnGeAs$_2$ (mp-$4008$) & \\ 
- %   to $0.75$ confidence & GeSe (mp-$10759$) & & CdSnP$_2$ (mp-$5213$) & \\ 
- %    & SiSn (mp-$1009813$) & & & \\
- %   \end{tabular}
- %   \label{tab:crystalsystems}
-%\end{table}
-
-\begin{table}[b]
+Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the models recognize BN as a suitable candidate with high probability.
+Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
+The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.
+
+In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the tetragonally structured (mp-$1008523$) BC$_2$N.
+The former takes on a polar space group while the latter does not.
+The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
+Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.
+By creating a boron vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
+Whether this is also possible for BC$_2$N remains to be seen.
+We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
+
+The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, while self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
+CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
+Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the dataset than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
+The prediction of CuI in two configurations indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
+It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
+NaCl was not predicted as suitable for QT in the empirical approach.
+
+Out of the nine predicted materials (threshold of $0.85$) we note that both instances of CuI are stated in the MP database to decompose into trigonal CuI, which was not present in our predictions.
+Hexagonal CdSe decomposes into cubic CdSe (in the list of $9$), the cubic BN decomposes to hexagonal BN (mp-$984$, not in the predictions), and ZnCd$_3$Se$_4$ decomposes to ZnSe $+$ CdSe (in the list).
+Finally, both compounds of the BC$_2$N structure are listed to decompose into hexagonal BN $+$ C.
+
+Lowering the cut-off requirement from $0.85$ to $0.75$ for all ML methods results in $66$ candidate materials for the empirical approach.  
+The full list of these $66$ candidates is displayed in the Supplementary Material at \cite{supplementary}. 
+In addition to the nine materials discussed above and some elemental and binary semiconductors, the list of $66$ predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$.
+For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
+Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
+In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
+We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
+
+\begin{table}[t]
     \centering 
     \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$).
-Compounds marked by an asterix are marked as unstable upon tranformation into other phases in the Materials Project database.
+Compounds marked by an asterisk are predicted to be unstable to tranformation into other phases in MP.
 }
@@
 
-Consider now the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
-The nine materials (considering different crystal structures, see Table~\ref{tab:materialproperties}) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
-Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems.
-Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as listed in the MP database.
-Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
-There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.
-
-Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the models recognize BN as a suitable candidate with high probability.
-Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
-%The element S resides in the same group as Se, and 
-The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.
-
-%high quality nanocrystals of CdS have been synthesized and studied for use as quantum dots since the nanocrystals emit in the visible range with a direct band gap of $2.5$-$2.6$~eV \cite{BanerjeeR2000Eots,CelebiSerdar2007SaCo,Qutub2012}.
-%Bulk CdS has a slightly lower reported band gap of $2.4$~eV \cite{Qutub2012}.
-
-In the case of BC$_2$N we find two compositions with the same chemical formula; the orthorhombically coordinated (mp-$629458$) and the tetragonally structured (mp-$1008523$) BC$_2$N.
-The former takes on a polar space group while the latter does not.
-The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
-Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.
-By creating a boron (B) vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
-Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
-
-The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
-%, and exhibit comparable properties. 
-To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized. 
-%, and the MP database lists it as unstable upon decomposition into ZnSe and CdSe (in the list with two entries). 
-Self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
-CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the dataset than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
-The presence of CuI in two configurations  proposes that ionic character alone is not an obstacle for a material to be quantum compatible if the prediction of CuI proves to be merited.
-It is unknown at this time whether any potential quantum compatible properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
-NaCl was not predicted as suitable for QT in the empirical approach.
-
-Out of these nine materials we note that both instances of CuI are stated in the MP database to decompose into trigonal CuI, which was not present in our predictions.
-Hexagonal CdSe decomposes into cubic CdSe (in the list of $9$), the cubic BN decomposes to hexagonal BN (mp-$984$, not in the predictions), and ZnCd$_3$Se$_4$ decomposes to ZnSe $+$ CdSe (in the list).
-Finally, both compounds of the BC$_2$N structure are listed to decompose into hexagonal BN $+$ C.
-
-Lowering the cut-off requirement from $0.85$ to $0.75$ for all models results in $66$ candidate materials for the empirical approach.  
-The full list of these $66$ candidates is displayed in the Supplementary Material at \cite{supplementary}. 
-The list of predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$, in addition to elemental and binary semiconductors, and the nine materials listed above.
-For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
-Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
-In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
-ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
-Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
-
-Among the $66$ materials that all models in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
+Among the $66$ materials that all ML methods in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
 The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
-% MB Do we want to emphasize Ge, as we are downplaying the importance of elemental semiconductors? Or, it could contain an impurity
 Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
 Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
-%
 Similar considerations could be made for the case of GeC. 
-Data from the Materials Project database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
-Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities to SiC.
-
-The compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures.
-The indirect band gaps of the different structures are calculated at $1.5$~eV and $1.1$~eV, respectively, as reported in the MP database.
-Both configurations of BP are nonmagnetic and share several properties with the entries mentioned above; including ...
-BP is non-toxic and has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
+Data from the MP database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
+Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities with SiC. 
+Next, the compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at $1.5$~eV and $1.1$~eV, respectively.
+Both configurations of BP are nonmagnetic, non-toxic and BP has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
 Lastly, InP (mp-$966800$) was also predicted as a suitable candidate to $0.75$ confidence.
@@
 InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-We underline the possibility of using InP-based quantum dots for QT applications as well.
+We underline the possibility of using InP-based quantum dots for QT applications.
 
 We note that all ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ cut-off.
+However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
 Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods after training on the dataset resulting from the empirical approach.
-This material is the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
-Its band gap is $2.0$~eV in the MP database with the experimental value being reported from $2.45$~eV (optical band gap) \cite{Ubale2014} up to as large as $5.6$~eV \cite{SaumGeorge1959}.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
+The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported from $2.45$~eV (optical band gap) \cite{Ubale2014} up to as large as $5.6$~eV \cite{SaumGeorge1959}.
 MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
-We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as another promising host material in this respect.
+We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as another promising host material in this regard.
 
 \subsubsection*{Comparing the approaches}
-Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence cut-off value.
-The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates where manual verification is possible.
+Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
+The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (when the cut-off is set to $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
+We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
 Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
@@
 (see the Supplementary Material at \cite{supplementary} for the full list). 
-Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, BP, GeC, InP and Ge.
-However, we also find certain materials that can be classified neither as semiconductors nor solid-state, such as P, I, N$_2$ and H$_2$.
-We note that none of these were included by the empirical approach when the confidence cut-off was set to $0.75$ or higher.
-
-Importantly, there are $6$ materials that all approaches and methods agree on to a $0.75$ confidence level.
+Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
+However, we also find certain materials that cannot be classified as semiconductors, such as P, I, N$_2$ and H$_2$.
+We note that none of these were included by the empirical approach when the threshold was set to $0.75$ or above.
+
+Importantly, there are $6$ materials that all approaches (Ferrenti, extended Ferrenti and empirical) and ML methods agree on above a $0.75$ threshold.
 These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$).
-Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal.
-See Fig.~\ref{fig:crystalsystems} for illustration of the crystal systems and Table~\ref{tab:materialproperties} for an overview of the corresponding material properties.
+Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (illustrated in Fig.~\ref{fig:crystalsystems}).
+The relevant material properties are summarized in the lower part of Table~\ref{tab:materialproperties}.
 Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
-We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are present, the materials take on only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP (unstable).
-However, four-fold coordination and the bond angle trends are not maintained for all materials (GeSe is six-fold coordinated).
-We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental study.
+We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP (unstable).
+However, consistent four-fold coordination and the bond angle trends we observed for the first $9$ materials are not maintained as GeSe is six-fold coordinated.
+We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental studies.
 
 \section*{Discussion}
-%\subsection*{Important features for QT}
 
@@
 %Turning to why the specific materials were chosen ... 
-Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we find important differences between the three labeling approaches, and can start to discern the driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the ML methods revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches, includes features related to the band gap and chemical environment.
+Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches encompasses features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process and little new information is gained. 
-On the other hand, the band gap related features were not important in the dominant principal component in the empirical approach.
-
-Figure~\ref{fig:histogram_new}(a) contains histograms of the number of predicted suitable materials for all approaches as a function of  band gap (as listed in the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap.
-Moreover, the distribution of materials that was identified as suitable is rather broad with the Ferrenti based approaches exhibiting a peak around $2.5$~eV.
-Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV at the PBE level. 
+In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process.
+For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.
+
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials for all approaches as a function of band gap (from the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
+Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti approaches exhibiting a peak around a $2.5$~eV band gap.
+Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV using PBE. 
 The empirical approach exhibits a more scattered data distribution with local maxima around $1$-$2$ and $4$~eV.
@@
 The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
-%The maximum ionic character is also deemed an important part of PC2. 
-Intriguingly, as shown in Fig.~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters  for all three approaches - even peaking at a relatively high ionic character of $0.8$.
-Moreover, we find that the covalent radii of the materials (see the Supplementary Material) distribute with two peaks in the data in all approaches. 
-%The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar. 
+Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+We note that this may be a result of the distribution of the initial dataset of $25.000$ materials that peaks around a similar value (not shown).
+The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach, extended Ferrenti approach nor the overall data distribution.
+For comparison, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
+Further, we find that the covalent radii of the materials (see the Supplementary Material) distribute with two peaks in the data for all approaches. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material \cite{supplementary}.
-Notably, substantial discrepancies between the Ferrenti approaches and the empirical approach are found for the standard deviation of the radial distribution function.
+One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
+Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti approaches and the empirical approach.
 This reflects the observations from the principal component analysis where the first principal component is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti and augmented Ferrenti approaches experience a more even distribution across a broader range.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti and extended Ferrenti approaches display an even distribution across a broader range.
 
@@
 Intriguingly, the peaks in the distributions of the predicted materials are not found for perfectly symmetric materials with identical bond lengths; instead, some variation in the bond and wavefunction distributions is found to be optimal for a material to be suitable for QT.
-%This is in keeping with no elemental semiconductors being present in the top lists of predicted materials above the $0.75$ confidence level. 
-Note that the maxima  in the histograms in Fig.~\ref{fig:histogram_new} seem to appear for moderate standard deviations in the RDF and average bond length, indicating that a certain degree of symmetry is likely necessary for a material to act as a good QT host.
-The exact degree and type of symmetry is still open to debate and should be studied further.
+Note that the maxima in Fig.~\ref{fig:histogram_new}(c) seem to appear for moderate standard deviations in the RDF, indicating that a certain degree of symmetry is likely necessary for a material to act as a suitable QT host.
+The exact degree and type of symmetry is still open to debate and merits further study.
 Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
-Interestingly, none of the nine materials predicted by the empirical approach with $0.85$ confidence, nor any of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
+Interestingly, none of the nine materials predicted by the empirical approach above a $0.85$ threshold, nor of the six materials predicted by all approaches to $0.75$ confidence, are elemental.
 At most three different elements are present, but the emphasis is clearly on binary compounds.
-This resonates strongly with the observations from the principal component analysis: an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but retaining some variations throughout the crystal in, e.g., bond length and symmetry.
-This is  in
-%in contrast 
-contrast to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to be a good quantum host, our results show that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well.
-
-%MB 
-%Also discuss max packing efficiencies. Now in Supplementary. Two clear peaks for empirical approach.
+This resonates with the observations from the principal component analysis; an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but some variations throughout the crystal in, e.g., bond length and symmetry are needed.
+This is in contrast to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well and may be more important.
 
@@
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
-For example, in the symmetric materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
-Instead, we find that QT effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy an lead-vacancy centers in diamond [REF].
+For example, in the high symmetry materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
+Instead, we find that quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond [REF].
 For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
@@
 Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets.
-The methods we have chosen are all well tested, with random forests and gradient boosting methods as those which tend to outperform the other, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
-
-%\section*{Discussion} 
-%MB I removed the initial discussion here, as it was a bit repetitive 
-%We have developed data extraction tools for numerous material science databases, and constructed over $4800$ physics-informed features for a dataset consisting of more than $25.000$ materials.
-Furthermore, three approaches to data mining for QT applications were developed; (i) the Ferrenti approach, (ii) the extended Ferrenti approach, and (iii) the empirical approach.
-Three distinct sets of labeled data were defined for training, testing and validation of four different ML algorithms (logistic regression, decision trees, random forests and gradient boosting).
-
-%NB 
-%Morten, kan ta en titt her?  Se ovenfor.
+The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
 
@@
 The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
-Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.% instead without being guided by assumptions.
-%that the formulation of the training sets for the Ferrenti and extended Ferrenti approaches was broad, and hence multiple dimensions would be required for distinguishing between materials labeled as suitable and unsuitable for QT in the two training sets.
-%The stringent restrictions set for the empirical approach, on the other hand, proved to give a distinct difference between suitable and unsuitable candidates by visualizing the two main principal components of the covariance matrix.
-Moreover, the smaller number of materials predicted for the empirical approach permits manual verification.
+Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.
 
@@
 Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
-Two main routes can be followed to exploit the results.
-One aspect is the pursuit of experimental verification of QT compatible effect in the materials predicted as suitable by the four ML methods.
-Another, perhaps even more important, is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
+We suggest two possible paths to further exploit our findings.
+One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by the four ML methods.
+Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
 
@@
 \subsection*{Databases}
-The Materials Project \cite{Jain2013, Jain2018} is an open-source project containing ground state properties of materials calculated using Density functional theory (DFT) [REF] as implemented in the Vienna Ab initio Simulation Package (VASP) \cite{Kresse1996}.
+The Materials Project \cite{Jain2013, Jain2018} is an open-source project containing ground state properties of materials calculated using density functional theory (DFT) as implemented in the Vienna Ab initio Simulation Package (VASP) \cite{Kresse1996}.
 The Perdew-Burke-Ernzerhof \cite{Perdew1996} (PBE) functional is used to calculate band structures, while for transition metals, a $+U$ correction is applied to correct for correlation effects \cite{Wang2006}.
 The project is known as the initiator of materials genomics and offers a variety of calculated properties for over one hundred thousand inorganic crystalline materials, with frequent updates and extensions.
-Data extraction from Materials Project was performed in December of $2020$ for the Ferrenti and extended Ferrenti approach, and in March $2021$ for the empirical approach.
-Therefore, the two former approaches includes $77$ more materials due to deprecated entries in the Materials Project database.
+Data extraction from Materials Project was performed in December of $2020$ for the Ferrenti and extended Ferrenti approaches, and in March $2021$ for the empirical approach.
+Therefore, the initial dataset for the two former approaches includes $77$ more materials than that for the empirical approach due to erroneous entries that have been removed from the Materials Project database.
 
@@
 JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly $40.000$ three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
-Structures included in the database are originally taken from the Materials
-%mhj: ref to materials project is missing
-Project \cite{Jain2013, Jain2018}, and then re-optimized using the OPT functional.
+Structures included in the database are originally taken from the Materials Project \cite{Jain2013, Jain2018}, and then re-optimized using the OPT functional.
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals \cite{Tran2009} is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
-Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available 30.04.2021 at \url{figshare.com}.
+Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on 30.04.2021 at \url{figshare.com}.
 
 The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
-They utilize the PBE functional within VASP
-%with projector-extended wave (PAW) potentials 
-to relax and optimize the ICSD-structure.  Data-extraction was done in the period of January-February of $2021$.
+They utilize the PBE functional within VASP to relax and optimize the structure from the ICSD.
+Data extraction was performed in the period of January to February of $2021$.
 
@@
 In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
-We extract the crystallographic information file (CIF) of the crystals from Materials Project, and then use this as input to AFLOW-ML, which then returns an anticipated band gap.
-The process was done during January of $2021$.
+We extract the crystallographic information files (CIF) for the crystals from Materials Project, use the CIF files as input to AFLOW-ML, which then returns an anticipated band gap.
+This process was executed during January of $2021$.
 
@@
 
-Pymatgen, a robust, open-source Python library for materials analysis \cite{pymatgen}, was also employed to extract and generate features for several of the databases mentioned above.
+Pymatgen, a robust and open-source Python library for material analysis \cite{pymatgen}, was also employed to extract and generate features for several of the databases mentioned above.
 
@@
 Machine learning represents the science of giving computers the ability to learn without being explicitly programmed.
-The idea is that there exist generic algorithms which can be used to find patterns in a broad class of datasets without having to write code specifically for each problem.
+The idea is that generic algorithms exist which can be used to find patterns in a broad class of datasets without having to write code specifically for each problem.
 The algorithm builds its own logic based on the data.
 
-The approaches to machine learning are many, but are often split into two main categories, supervised and unsupervised.
+The approaches to machine learning are many, but are often split into two main categories: supervised and unsupervised.
 In supervised learning we know the answer to a problem, and let the computer deduce the logic behind it.
-On the other hand, unsupervised learning is a method for finding patterns and relationship in datasets without any prior knowledge of the system.
+On the other hand, unsupervised learning is a method for identifying patterns and relationships in datasets without any prior knowledge of the system.
 Many researchers also operate with a third category, namely reinforcement learning.
@@
 \section*{Code availability} 
-The codes employed to develop the machine learning results are available online at 
-%https://github.com/ohebbi/predicting-solid-state-qubit-material-hosts 
-\cite{Ohebbi2021}.
-%Update with new release later).
+The codes employed to develop the machine learning results are available online at \cite{Ohebbi2021}.
 
@@
 The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
-%Some of the computations were performed on resources provided by UNINETT Sigma2 - the National Infrastructure for High Performance Computing and Data Storage in Norway.  
 The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship. 

### 2022-03-01 supplementary.tex
Updates from Overleaf

@@
 
-\title{Supplementary Material \\ 
-%Predicting Solid State Qubit Candidates}
+\title{\textit{Supplementary Material} \\ 
 Predicting Solid State Material Platforms for Quantum Technologies}
+
 \author{Oliver Lerst{\o}l Hebnes}
@@
 \affiliation{Advanced Power Semiconductor Laboratory, ETH Zürich, 8092  Zürich,  Switzerland}
-\affiliation{Department of Physics and Center for Materials Science and Nanotechnology, University of Oslo, N-0316 Oslo, Norway}
 
@@
 
+\newpage
+
 \section*{Supplementary methods}
@@
 To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}. 
-Table~\ref{table:featurizers} contains an overview of the 39  chosen featurizers from Matminer. The featurization process results in $4876$ descriptors.
+Table~\ref{table:featurizers} contains an overview of the 39  chosen featurizers from Matminer. The featurization process results in $4876$ physics informed descriptors.
 
-The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable potential host.
+The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable quantum host material.
 Therefore, we have collected an achievable quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
@@
 
-The implementation of the machine learning methods was done through the machine learning library Scikit-learn \cite{Pedregosa2012}.
-By adjusting the majority of the hyperparameters in Scikit-learn, we experienced severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees.
+The implementation of the machine learning methods was achieved through the machine learning library Scikit-learn \cite{Pedregosa2012}.
+Adjusting many of the hyperparameters in Scikit-learn resulted in severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees.
 Therefore, most parameters are the default values defined by Scikit-learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$  (see \cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown.
-In our work we adjusted between the depth of the trees to vary from $1$ to $8$.
-For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and use either $200$ or $400$ iterations to reach convergence.
+The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown.
+In our work we adjusted
+%between 
+the depth of the trees to vary from $1$ to $8$.
+For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and used either $200$ or $400$ iterations to reach convergence.
 
 When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
-Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models %, just for one arbitrary machine learning algorithm like logistic regression.
+Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models.
+%, just for one arbitrary machine learning algorithm like logistic regression.
 
@@
 %Ferrenti 
-The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score (see for example \cite{geron2022} for a definition of various score metrics) on the test set as a function of principal components.
-For each principal component, we display the optimal combination of hyperparameters based on the F$1$-score.
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score
+%(see for example \cite{geron2022} for a definition of various score metrics) 
+on the test set as a function of the number of principal components. For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score.
 
@@
 \centering
-\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:01-pca}.}
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:01-pca}.}
 \label{tab:01-pc}
@@
 For random forests and decision trees, we find the maximum depth of $7$.
-Gradient boosting, which normally uses a weak learner, had a decision tree of depth $4$.
+Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
 We find the best performing method to be logistic regression, but this method depends on a large number of principal components.
@@
 Importantly, we observe that the single most important feature for all ML methods is the fifth principal component.
-Interestingly, by selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the
-compound 
-% composition 
-as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
+Interestingly, by selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
 
@@
 The coefficients for the case of logistic regression experience large fluctuations, but the three remaining models find the first and second principal components important in addition to the fifth.
-In order of importance, we observe that the second component's largest values correspond to the electronegativity, ionic property, and covalence radius among the elements in the composition.
+In order of importance, we observe that the second component's largest values correspond to the electronegativity, maximum ionic character, and covalent radius among the elements in the composition.
 The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum.
 While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
-
-%While the first principal component has by far the largest explained variance, it does not provide any specific information of which features it represents.
-Some of the features represent the period in the periodic table, structural packing efficiency, and atomic weights of the components.
-However, we are unable to confirm the prominent features due to no significant .
-
-%a variety of features are represented, such as the rows that a composition in the periodic table represents, structural packing efficiency and atomic weights of the components, but we are unable to confirm the prominent features due to small variations.
 
@@
 \subsubsection*{Extended Ferrenti approach}
-
-For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
-All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75:25 \ \%$.
-This result comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
-On the other hand, we find a small precision for the first component since the ML methods  predict many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
-This trend is revealed when looking at the balanced accuracy score.
-For all figures, it remains the lowest score of the evaluation metrics largely due to the inaccuracy of true negatives for the cross-validations.
-%Therefore, one can argue that we should use the balanced accuracy score for evaluation and not the F1 score, but the choice is independent of the evaluation metric since the optimal F1 score is also the optimal balanced accuracy score for all figures.
-
-\begin{table}[b]
-\centering
-\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Figure~\ref{fig:02-pca}.}
-\label{tab:02-pc}
-\noindent\makebox[\textwidth]{
-\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
-  \hline
-  \hline
-   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
-  \hline
-  LOG & $175$ & $0.98(0.008)$ & $0.99(0.004)$ & $0.99(0.004)$ & $0.99(0.003)$ \\
-  DT & $25$   & $0.69(0.034)$ & $0.86(0.015)$ & $0.93(0.021)$ & $0.90(0.008)$ \\
-  RF & $25$   & $0.70(0.028)$ & $0.86(0.011)$ & $1.00(0.003)$ & $0.93(0.006)$ \\
-  GB & $93$   & $0.85(0.025)$ & $0.93(0.011)$ & $0.99(0.004)$ & $0.96(0.007)$ \\
-  \hline
-\end{tabular}
-}
-\end{table}
-
-Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
-Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
-The decision trees method exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
-The Random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
-
-The optimal hyperparameters are summarized in Table~\ref{tab:02-pc}.
-We find that logistic regression with $175$ principal components performs more or less like a perfect classifier with overall high scores.
-The decision trees and random forests methods have similar balanced accuracy scores with $0.69$ and $0.70$, respectively, due to challenges associated with predicting true negative labels for $25$ principal components.
-Lastly, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
 
@@
   \end{subfigure}
-  \caption{{Four figures displaying hyperparameter search for the extended Ferrenti approach.
-The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
+  \caption{Hyperparameter search for the extended Ferrenti approach.
+The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter combination.
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall, and F$1$ scores are based on the test set.
-The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}}
+Precision, recall and F$1$ scores are based on the test set.
+The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}
   \label{fig:02-pca}
@@
 
+For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
+All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75 \ \% : 25 \ \%$.
+This result comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
+%On the other hand, we find a small precision for the first component since the ML methods  predict many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
+On the other hand, we find a small precision for the first component since the ML methods  predict many materials as suitable regardless of whether they were labeled as suitable or unsuitable in the initial data labeling process, and the latter case is particularly numerous.
+This trend is revealed when looking at the balanced accuracy score.
+For all figures, it remains the lowest score of the evaluation metrics largely due to the inaccuracy of true negatives for the cross-validations.
+
+\begin{table}[t]
+\centering
+\caption{Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the extended Ferrenti approach, as visualized by the dash-dotted line in Fig.~\ref{fig:02-pca}.}
+\label{tab:02-pc}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Method & PC & Mean test &  Mean precision & Mean recall & mean F1\\
+  \hline
+  LOG & $175$ & $0.98(0.008)$ & $0.99(0.004)$ & $0.99(0.004)$ & $0.99(0.003)$ \\
+  DT & $25$   & $0.69(0.034)$ & $0.86(0.015)$ & $0.93(0.021)$ & $0.90(0.008)$ \\
+  RF & $25$   & $0.70(0.028)$ & $0.86(0.011)$ & $1.00(0.003)$ & $0.93(0.006)$ \\
+  GB & $93$   & $0.85(0.025)$ & $0.93(0.011)$ & $0.99(0.004)$ & $0.96(0.007)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
+Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
+Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
+The decision trees method exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
+The random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
+
+The optimal hyperparameters are summarized in Table~\ref{tab:02-pc}.
+We find that logistic regression with $175$ principal components performs more or less like a perfect classifier with overall high scores.
+The decision trees and random forests methods have similar balanced accuracy scores with $0.69$ and $0.70$, respectively, due to challenges associated with predicting true negative labels for $25$ principal components.
+Lastly, we find that gradient boosting performs optimally at $93$ principal components with a balanced accuracy score of $0.85$.
+
 The relevant hyperparameters for logistic regression were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
-Smaller regularization values resulted in worse scores, while increasing values did not notably alter the results.
-The decision trees and random forests found an optimal maximum depth of $7$, where smaller values resulted in low precision but high recall.
+Smaller regularization values resulted in worse scores, while increasing values did not noticeably affect the results.
+The decision trees and random forests methods both found an optimal maximum depth of $7$, where smaller values resulted in low precision but high recall.
 Therefore, the choice was made to facilitate a compromise between precision and recall.
@@
 Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
+This means that, if we consider, e.g., the compound SiC, the band gaps of both SiC, Si and C would be considered important by the ML methods.
 
 \subsubsection*{Empirical approach}
-
-Lastly, we turn to the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates in the training set.
-%, which was again somewhat imbalanced. 
-However, in contrast to the two training sets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
-
-The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca}.
-Interestingly, we find that all ML methods  experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
-%This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
-
-Logistic regression experiences improvement of all scores for an increasing number of principal components, yet only up $5 \ \%$ in scores compared to the one-dimensional representation of one principal component.
-Thus, one can argue whether the increase in performance is worthwhile, considering a one-dimensional representation with just a few percentage losses of performance.
-However, with multiple principal components, we find the largest increase in precision, which is a sign that the one-dimensional representation tends to wrongly predict candidates as suitable when they are in fact unsuitable.
-Decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger values.
-Gradient boosting, in contrast to the case for the two Ferrenti based approaches, also experiences the best performance for a few principal components.
-
-\begin{table}[b]
-\centering
-\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Figure~\ref{fig:03-pca}.}
-\label{tab:03-pca}
-\noindent\makebox[\textwidth]{
-\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
-  \hline
-  \hline
-   Method & PC & Mean test & Mean precision & Mean recall  & mean F1\\
-  \hline
-  LOG & $61$  & $0.99(0.011)$ & $0.97(0.032)$ & $0.99(0.016)$ & $0.98(0.018)$ \\
-  DT & $9$    & $0.96(0.019)$ & $0.95(0.040)$ & $0.95(0.033)$ & $0.95(0.026)$ \\
-  RF & $27$   & $0.98(0.020)$ & $0.97(0.033)$ & $0.97(0.031)$ & $0.97(0.026)$ \\
-  GB & $13$   & $0.97(0.016)$ & $0.96(0.036)$ & $0.97(0.029)$ & $0.96(0.022)$ \\
-  \hline
-\end{tabular}
-}
-\end{table}
 
@@
 
-  \caption{{Four figures displaying hyperparameter search for the empirical approach.
+  \caption{{Hyperparameter search for the empirical approach.
 The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
@@
 
-The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all Ml methods exhibit high evaluation metrics.
+Lastly, we turn to the empirical approach to data labeling, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process.
+However, in contrast to the two labeled datasets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
+
+The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca} for the empirical approach.
+Interestingly, we find that all ML methods  experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
+%This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
+
+Logistic regression experiences improvement of all scores for an increasing number of principal components, yet only up $5 \ \%$ in scores compared to the one-dimensional representation of one principal component.
+Thus, one can argue whether the increase in performance is worthwhile, considering a one-dimensional representation with just a few percentage losses of performance.
+However, with multiple principal components, we find the largest increase in precision, which is a sign that the one-dimensional representation tends to wrongly predict candidates as suitable when they are in fact unsuitable.
+Decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting for larger values.
+Gradient boosting, in contrast to the case for the two Ferrenti approaches, also experiences the best performance for a few principal components.
+
+\begin{table}[t]
+\centering
+\caption{ Optimal number of principal components and the respective scores (standard deviation) for each of the four ML methods logistic regression (LOG), decision trees (DT), random forests (RF) and gradient boosting (GB) in the empirical approach, as visualized by the dash-dotted line in Fig.~\ref{fig:03-pca}.}
+\label{tab:03-pca}
+\noindent\makebox[\textwidth]{
+\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+  \hline
+  \hline
+   Method & PC & Mean test & Mean precision & Mean recall  & mean F1\\
+  \hline
+  LOG & $61$  & $0.99(0.011)$ & $0.97(0.032)$ & $0.99(0.016)$ & $0.98(0.018)$ \\
+  DT & $9$    & $0.96(0.019)$ & $0.95(0.040)$ & $0.95(0.033)$ & $0.95(0.026)$ \\
+  RF & $27$   & $0.98(0.020)$ & $0.97(0.033)$ & $0.97(0.031)$ & $0.97(0.026)$ \\
+  GB & $13$   & $0.97(0.016)$ & $0.96(0.036)$ & $0.97(0.029)$ & $0.96(0.022)$ \\
+  \hline
+\end{tabular}
+}
+\end{table}
+
+The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics.
 Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with the F$1$-score of $0.98$.
@@
 
-  \caption{Five figures visualizing different parameters for the $15$ most principal components ranked in descending order by the explained variance for the empirical approach.
+  \caption{Visualization of different parameters for the $15$ most principal components ranked in descending order by the explained variance for the empirical approach.
 The panels show the logistic regression coefficients, decision trees feature importance, random forests feature importance, gradient boosting feature importance, and explained variance that is retained by including each of the eigenvectors.
@@
 Lastly, gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$.
-The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations as $400$.
+The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations at $400$.
 The decision trees uses a maximum depth of $6$, where larger values increased the training accuracy but not any other metric.
 The maximum depth for  random forests was set to $6$.
-Fo gradient boosting, which use a weak learner, the depth of the trees was set to  $4$.
+For gradient boosting, which uses a weak learner, the depth of the trees was set to  $4$.
 
@@
 We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML methods, while the empirical approach results in a substantially narrower selection of contender materials.
-Note that the confidence cut-off was set to $0.5$.
+Note that the confidence threshold was set to $0.5$ in this case.
 
@@
 Random forests has the most optimistic estimate with $14.278$, while gradient boosting finds $11.835$ suitable candidates.
-The four ML methods agree on $6804$ suitable candidates, however, many of the materials
-are predicted with a confidence similar to that of a coin-flip.
+The four ML methods agree on $6804$ suitable candidates,  however, many of the materials are predicted with a confidence similar to that of a coin-flip.
 If we were to raise the minimum bar of a prediction to  
-$0.7$, the four methods would only agree on $3000$ suitable candidates
+%$0.7$, the four methods would only agree on $3000$ suitable candidates
+$0.75$, the four methods would only agree on $1784$ suitable candidates.
 
 The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
-Due to the less stringent restrictions compared to the Ferrenti approach, we find the large amount of $9227$ entries that the four ML methods  agree on.
+Due to the less stringent restrictions compared to the Ferrenti approach, we find a large number ($9227$) of entries that the four ML methods  agree on.
 
-The four methods predict radically fewer suitable candidates for the empirical approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The four ML methods predict radically fewer suitable candidates for the empirical approach as compared to the two former approaches, where only $842$, $1197$, $543$, and $596$ materials are predicted as suitable by logistic regression, decision trees, random forests, and gradient boosting, respectively.
 The large majority of the unsuitable candidates are predicted with high probability except for random forests due to the ensemble of trees.
-All methods, however, agree on $214$ suitable candidates.
+All methods, however, agree on $214$ suitable candidates above a $0.5$ threshold limit.
 
@@
 
-Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training set derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training, test and validation sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
-Note that materials can appear several times  on  the  list due  to  different  structures of the same composition.
+Note that materials can appear several times in the list due  to  different  structures of the same composition.
 The  list  contains $5$ elementary (unary), $46$ binary and  $15$ ternary compounds.
@@
 
-Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning methods and all three approaches agreed upon. 
-%To 0.5 cutoff 
+Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning methods and all three approaches (Ferrenti, extended Ferrenti and empirical) agreed on (to a $0.5$ cut-off value).
 The list contains $8$ elemental, $29$ binary, and $10$ tertiary compounds.
@@
 \subsection*{Feature analysis}
-%Or important features for QT 
+
+%histograms 
+\begin{figure}[t]
+\label{fig:histograms_supp}
+\begin{subfigure}[t]{1\textwidth}
+    \input{figures/histograms/new/legend.tex}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ElementProperty_MagpieData range CovalentRadius_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MaximumPackingEfficiency_max packing efficiency_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.tex}}
+    \subcaption{}
+\end{subfigure}%
+
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\begin{subfigure}[b]{0.45\textwidth}
+    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MP_Eg_normalized_databackgrund_075.tex}}
+    \subcaption{}
+\end{subfigure}
+\caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
+Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function.
+Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
+%The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. 
+The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
+\end{figure}
+
 Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
 The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
-Several observations can be made based on the histograms.
+%Several observations can be made based on the histograms. 
 Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.
@@
 
-%histograms 
-\begin{figure}[!ht]\label{fig:histograms_supp}
-\begin{subfigure}[t]{1\textwidth}
-    \input{figures/histograms/new/legend.tex}
-\end{subfigure}
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ElementProperty_MagpieData range CovalentRadius_count_075.tex}}
-    \subcaption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MaximumPackingEfficiency_max packing efficiency_count_075.tex}}
-    \subcaption{}
-\end{subfigure}%
-
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=2.0 width=1.0_count_075.tex}}
-    \subcaption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/GeneralizedRDF_std_dev Gaussian center=3.0 width=1.0_count_075.tex}}
-    \subcaption{}
-\end{subfigure}%
-
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/ChemEnvSiteFingerprint_GaussianSymmFuncstd_dev G2_20.0_count_075.tex}}
-    \subcaption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/CrystalNNFingerprint_mean tetrahedral CN_4_count_075.tex}}
-    \subcaption{}
-\end{subfigure}%
-
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/OPSiteFingerprint_mean tetrahedral CN_4_count_075.tex}}
-    \subcaption{}
-\end{subfigure}
-\begin{subfigure}[b]{0.47\textwidth}
-    \scalebox{0.85}{\input{figures/histograms/supplementary-new/MP_Eg_normalized_databackgrund_075.tex}}
-    \subcaption{}
-\end{subfigure}
-\caption{Histograms of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
-Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function.
-Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
-The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right.
-All panels were taken for a $0.75$ cut-off.
-}
-\end{figure}
-
-\newpage
-
 \bibliography{apssamp}% Produces the bibliography via BibTeX.

### 2022-03-05 supplementary.tex

@@
 %
-\documentclass[superscriptaddress,unsortedaddress,
+\documentclass[floatfix, superscriptaddress,unsortedaddress,
 %runinaddress,
@@
 \sisetup{separate-uncertainty}
-
+\UseRawInputEncoding
 \usepackage{forest}
@@
 Therefore, most parameters are the default values defined by Scikit-learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum number of depth for the trees grown.
+The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum depth for the trees grown.
 In our work we adjusted
@@
 the depth of the trees to vary from $1$ to $8$.
-For logistic regression, we chose to adjust the regularization strength with seven logarithmic adjusted values from $10^{-3}$ to $10^{5}$, and used either $200$ or $400$ iterations to reach convergence.
+For logistic regression, we chose to adjust the regularization strength with seven logarithmic values ranging from $10^{-3}$ to $10^{5}$, and used either $200$ or $400$ iterations to reach convergence.
 
@@
 \noindent\makebox[\textwidth]{
-\begin{tabular}{M{1.0cm} M{1.0cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
+\begin{tabular}{M{2.0cm} M{1.5cm} M{2.0cm} M{2.0cm}M{2.0cm}M{2.0cm} }
   \hline
@@
 The relevant hyperparameters for logistic regression were the maximum iterations.
-The number of iterations was set at $400$, and the regularization term was given by an optimal of $0.46$.
-For random forests and decision trees, we find the maximum depth of $7$.
+The number of iterations was set at $400$, and the regularization term was found optimal at $0.46$.
+For random forests and decision trees, we find the maximum depth to be $7$.
 Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
@@
 %histograms 
-\begin{figure}[t]
-\label{fig:histograms_supp}
+\begin{figure}[!t]
 \begin{subfigure}[t]{1\textwidth}
@@
 \end{subfigure}
+
 \caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
@@
 The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
+\label{fig:histograms_supp}
 \end{figure}
@@
 
+\clearpage
+
 \bibliography{apssamp}% Produces the bibliography via BibTeX.

### 2022-03-07 paper_v3_cut.tex
Updates from Overleaf

@@
 Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physcis-informed features.
-Three approaches were devised to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
+Three approaches were devised, labeled the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
 We find that of the three, the empirical approach relying exclusively on findings from the literature predicted substantially fewer candidates than the other two approaches with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to expectations from the literature and that found for the the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
+In contrast to expectations from the literature and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
@@
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
-Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate.
+%Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
 We follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
@@
 Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-Where the polarity of the material's space group may be less important than assumed in the Ferrenti based approaches, ionic character and covalent range are distinguished from the other features visualized in Fig.~\ref{fig:parallel-coordinates-approaches}.
+In the empirical approach the polarity of the material's space group may be less important compared to the Ferrenti based approaches, while the accepted values for ionic character and covalent range appear more restricted ( Fig.~\ref{fig:parallel-coordinates-approaches} ).
 
@@
 Principal component analyses fall  under the category of unsupervised learning within ML  methods.
-Here we apply PCA to the labeled datasets in order to figure out if there are specific features that stand out.
+Here we apply PCA to the labeled datasets in order to reveal specific features that stand out.
 In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
@@
 
-%Include a discussion on the difficulty of labeling unsuitable candidates.
-
 %summary - do we need this? 
@@
 \subsection*{Machine learning and principal component analysis}
-In this work we have applied four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
+We have applied four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
 These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
@@
 We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material at \cite{supplementary}.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material \cite{supplementary}.
 %
@@
 %extended Ferrenti 
-The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
+The interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
@@
 For example, in the high symmetry materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
-Instead, we find that quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon [REF] and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond [REF].
+Instead, we find that quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
 For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 

### 2022-03-07 supplementary.tex
Updates from Overleaf

@@
 %
-\documentclass[floatfix, superscriptaddress,unsortedaddress,
+\documentclass[superscriptaddress,unsortedaddress,
 %runinaddress,
@@
 \usepackage{tikz} %draw figures
-
+\usepackage{longtable}
 \usepackage{subcaption} %subcaption
-\usepackage[font=small,labelfont=bf,width=0.9\textwidth]{caption}
+%\usepackage[font=small,labelfont=bf,width=0.9\textwidth]{caption}
 \captionsetup[table]{skip=10pt}
@@
 \usepackage{makecell}
-\usepackage{longtable}
 \usepackage{dcolumn}% Align table columns on decimal point
@@
 However, we find that random forests and gradient boosting experience the fifth principal component as important.
-Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
+%Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
+Similar to the Fererenti approach, the extended Ferrenti finds the DFT band gap of the elemental solids among the elements in the composition important.
+The feature regarding the band gap originates from the highest value from the first principal component.
 This means that, if we consider, e.g., the compound SiC, the band gaps of both SiC, Si and C would be considered important by the ML methods.
@@
 The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca} for the empirical approach.
-Interestingly, we find that all ML methods  experience high scores for just a few principal components, where $1$ principal component earns at least $0.93$ scores for all evaluation metrics.
+Interestingly, we find that all ML methods  experience high scores for just a few principal components, where
+%$1$
+the first
+principal component earns at least $0.93$ scores for all evaluation metrics.
 %This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
@@
 %histograms 
-\begin{figure}[!t]
+\begin{figure}[ht!]
 \begin{subfigure}[t]{1\textwidth}
@@
 \end{subfigure}%
+\end{figure}
 
+Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
+The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
+%Several observations can be made based on the histograms. 
+Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.
+
+\begin{figure}[ht!]\ContinuedFloat
 \begin{subfigure}[b]{0.45\textwidth}
@@
 \end{subfigure}
-
 \caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
@@
 
-Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
-The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
-%Several observations can be made based on the histograms. 
-Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.
-
 Firstly, we find that the covalent radii of the materials (see Fig.~\ref{fig:histograms_supp}a) distribute with two peaks in the data in all approaches.
@@
 
-\clearpage
-
 \bibliography{apssamp}% Produces the bibliography via BibTeX.

### 2022-03-08 appendix/featurizerTable.tex
Updates from Overleaf

@@
 \begin{center}
-\begin{longtable}{M{3.5cm} M{6.5cm} M{2.0cm}}
-\caption{This work's chosen 39 featurizers from matminer.
+\begin{longtable}{M{4.0cm} M{7.5cm} M{2.0cm}}
+\caption{Descriptions of the 39 featurizers from Matminer that have been employed in this work.
 Descriptions are either found from Ref.
@@
 \label{table:featurizers} 
-\hline 
+\\ \hline
 Features & Description & Reference \\
@@
    & and Gaussian window function  & \\ 
-  AverageBond- Agle & Determines the average bond angle of a specific  & \cite{Jong2016}  \\
+  AverageBond- Angle & Determines the average bond angle of a specific  & \cite{Jong2016}  \\
    & site with its nearest neighbors  & \\ 

### 2022-03-08 supplementary.tex
Updates from Overleaf

@@
 The motivation behind the choice of featurizers is that we do not precisely know which features describe a suitable quantum host material.
-Therefore, we have collected an achievable quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
+Therefore, we have collected a large quantity of descriptors in order to reliably  predict potential materials for quantum technologies.
 
@@
 
-The implementation of the machine learning methods was achieved through the machine learning library Scikit-learn \cite{Pedregosa2012}.
-Adjusting many of the hyperparameters in Scikit-learn resulted in severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees.
-Therefore, most parameters are the default values defined by Scikit-learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{geron2022} for a definition of various metrics) was the maximum depth for the trees grown.
+The implementation of the machine learning methods was achieved through the machine learning library Scikit-Learn \cite{Pedregosa2012}.
+Adjusting many of the hyperparameters in Scikit-Learn resulted in severe overfitting for the machine learning methods random forests, gradient boosting, and decision trees.
+Therefore, most parameters are the default values defined by Scikit-Learn.
+The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{sammut2010,geron2022} for a definition of various metrics) was the maximum depth for the decision trees (these are also used as so-called weak learners in ensemble methods like gradient boosting and random forests \cite{geron2022}).
 In our work we adjusted
@@
 %Ferrenti 
-The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Fig.~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score
 %(see for example \cite{geron2022} for a definition of various score metrics) 
-on the test set as a function of the number of principal components. For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score.
+on the test set as a function of the number of principal components.
+For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score \cite{sammut2010,geron2022}.
 
@@
   \caption{Four figures displaying hyperparameter search for the Ferrenti approach.
-The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation, and the dotted lines mark the optimal hyperparameter-combination.
+The best estimator is visualized for all hyperparameters as a function of principal components during a grid search with a $5\times5$ stratified cross-validation.
+The dotted lines mark the optimal hyperparameter-combination.
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall, and F$1$ scores are based on the test set \cite{geron2022}.
+Precision, recall, and F$1$ scores are based on the test set \cite{geron2022,sammut2010}.
 The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
@@
 The relevant hyperparameters for logistic regression were the maximum iterations.
-The number of iterations was set at $400$, and the regularization term was found optimal at $0.46$.
-For random forests and decision trees, we find the maximum depth to be $7$.
-Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
-We find the best performing method to be logistic regression, but this method depends on a large number of principal components.
+The number of iterations was set at $400$, and the optimal regularization term was $0.46$.
+For random forests and decision trees, we found the maximum depth to be seven.
+Gradient boosting, which normally uses a weak learner, had a decision tree depth of four.
+We found the best performing method to be logistic regression, but this method depends on a large number of principal components.
 
-In Figure~\ref{fig:01-fi}, we visualize how the various machine learning methods  interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+In Fig.~\ref{fig:01-fi}, we visualize how the various machine learning methods  interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
 To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components were included.
@@
 In the three next panels, namely for the machine learning methods  decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
-Importantly, we observe that the single most important feature for all ML methods is the fifth principal component.
-Interestingly, by selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
+We observe that the single most important feature for all ML methods is the fifth principal component.
+Selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
 
@@
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall and F$1$ scores are based on the test set.
+Precision, recall and F$1$ scores \cite{geron2022,sammut2010} are based on the test set.
 The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}
@@
 
-Overall, the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
+Overall the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
 Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
@@
 Smaller regularization values resulted in worse scores, while increasing values did not noticeably affect the results.
-The decision trees and random forests methods both found an optimal maximum depth of $7$, where smaller values resulted in low precision but high recall.
+The decision trees and random forests methods both found an optimal maximum depth of seven, where smaller values resulted in low precision but high recall.
 Therefore, the choice was made to facilitate a compromise between precision and recall.
-For gradient boosting, we find the optimal maximum depth as $4$ due to a decline in overall metrics for increasing depth except for training accuracy, which could potentially result in overfitting.
+For gradient boosting, we find the optimal maximum depth as four due to a decline in overall metrics for increasing depth except for training accuracy.
+An increasing depth  could potentially result in overfitting.
 
@@
 %Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
-Similar to the Fererenti approach, the extended Ferrenti finds the DFT band gap of the elemental solids among the elements in the composition important.
+Similar to the Ferrenti approach, the extended Ferrenti approach finds the DFT band gap of the elemental solids among the elements in the composition important.
 The feature regarding the band gap originates from the highest value from the first principal component.
@@
 
-The grid search for the optimal number of principal components is visualized in Figure~\ref{fig:03-pca} for the empirical approach.
+The grid search for the optimal number of principal components is visualized in Fig.~\ref{fig:03-pca} for the empirical approach.
 Interestingly, we find that all ML methods  experience high scores for just a few principal components, where

### 2022-03-08 paper_v3_cut.tex
Updates from Overleaf

@@
 \section*{Introduction}
-Quantum technologies (QT) based on solid state platforms are rapidly gaining in both success and notoriety. 
+Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during the last few years. 
 Among the promising applications that are already available we find important breakthroughs  such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures.
-Quantum computers are in high demand to meet the increasing need for computing power to solve complex many-body problems that are beyond the scope of classical machines.   
-Recent advances have highlighted the potential of quantum information processors to outperform classical systems.
+Quantum computers are in high demand to meet the increasing need for computing power to solve complex and high-dimensional scientific problems. 
+%that are beyond the capability of existing high-performance computing %facilities.   
+Recent advances have highlighted the potential of quantum information processors to outperform state-of-the art high-performance computing facilities.
 Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
@@
 %, see for example Ref.~\cite{Acin2018}.
-Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Figure~\ref{fig:ht-workflow}.
+Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Fig.~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing material properties for a wide range of different systems.
@@
 The information stream in this work can be regarded as many inter-connected modular parts. 
-The initial step for gathering material data and building features is visualized by the outer flowchart in Figure~\ref{fig:flowchart} (Jupyter notebooks containing the full
+The initial step for gathering material data and building features is visualized by the outer flowchart in Fig.~\ref{fig:flowchart} (Jupyter notebooks containing the full
 workflow can be found at \cite{Ohebbi2021}).
@@
 
-The labeled data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+The labeled data for each approach is visualized in Fig.~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
 In essence, we reduce the dimensionality of the labeled data in order to visualize them.
-The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
+The result of this procedure is displayed in the scatter plots of Fig.~\ref{fig:2dscatterplotpca}.
 Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of removing the mean and scaling to unit variance.
@@
 The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+Intriguingly, as shown in Fig.~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
 We note that this may be a result of the distribution of the initial dataset of $25.000$ materials that peaks around a similar value (not shown).
@@
 Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
+One configuration of the standard deviation of the RDF is demonstrated in Fig.~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
 Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti approaches and the empirical approach.
@@
 The exact degree and type of symmetry is still open to debate and merits further study.
-Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+Similar symmetry related features such as the standard deviation of the average bond length (see Fig.~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 

### 2022-03-08 paper_v3_cut.tex
Updates from Overleaf

@@
 Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, searching these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physcis-informed features.
-Three approaches were devised, labeled the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
+However, searching these databases to find promising candidate materials for quantum technology applications
+%among tens of thousands of contenders
+is a major challenge.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physics-informed features.
+Three approaches were devised, named the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
 We find that of the three, the empirical approach relying exclusively on findings from the literature predicted substantially fewer candidates than the other two approaches with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to expectations from the literature and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
+In contrast to expectations from the literature and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
@@
 Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during the last few years. 
-Among the promising applications that are already available we find important breakthroughs  such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures.
+Among the promising applications that are already available we find important breakthroughs such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures \cite{Arute_2019}.
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex and high-dimensional scientific problems. 
@@
 These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap \cite{Weber2010}.
-So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
+So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g.,
+indistinguishable  
+single-photon emission and long spin coherence times. 
 The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders for quantum communication purposes especially due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication (see, e.g., Refs.~\cite{Castelletto_2015,Son2020,Bathen2021}).
@@
 
-The developed approach relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+The developed procedure relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
@@
 The complete dataset consists of $25.000$ materials.
-A subset of these materials will be labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
+A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
 The labeled data are then grouped into training, test and validation sets for the ML methods.
@@
 
-The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131, FriPro ToppForsk-program). 
+The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131) and QuTe (no. 325573). 
 The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship. 

### 2022-03-08 supplementary.tex
Updates from Overleaf

@@
 %Ferrenti 
-The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Fig.~\ref{fig:01-pca}, where we present the mean accuracy on the training set, and the balanced accuracy, precision, recall, and F$1$-score
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Fig.~\ref{fig:01-pca}, where we present the mean accuracy of the four ML models applied to the training set, and the balanced accuracy, precision, recall, and F$1$-score
 %(see for example \cite{geron2022} for a definition of various score metrics) 
-on the test set as a function of the number of principal components.
+for the test set as a function of the number of principal components.
 For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score \cite{sammut2010,geron2022}.
@@
 
-For logistic regression, we have visualized the mean fitted coefficients and the standard variation in the top panel of Fig.~\ref{fig:01-fi}.
+For logistic regression, we have visualized the mean fitted coefficients and the standard deviation in the top panel of Fig.~\ref{fig:01-fi}.
 Large positive or negative coefficients can be considered increasingly important, where positive (negative) coefficients will contribute to making positive (negative) predictions.
@@
 %On the other hand, we find a small precision for the first component since the ML methods  predict many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
-On the other hand, we find a small precision for the first component since the ML methods  predict many materials as suitable regardless of whether they were labeled as suitable or unsuitable in the initial data labeling process, and the latter case is particularly numerous.
+On the other hand, we find a low precision score for the first component since the ML methods  predict many materials as suitable regardless of whether they were labeled as suitable or unsuitable in the initial data labeling process, and the latter case is particularly numerous.
 This trend is revealed when looking at the balanced accuracy score.

### 2022-03-08 paper_v3_cut.tex
Updates from Overleaf

@@
 Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and ML methods combined with knowledge from the field.
-Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training, testing and validation, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
+Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training and testing, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
 In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
@@
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training, test and validation sets for the ML methods.
+The labeled data are then grouped into training and sets for the ML methods.
 
@@
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
-%Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
+Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
 We follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
@@
 We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training, testing and validation of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
+Due to the concern of ending up with too small datasets for training and testing of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
 These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
@@
     \centering 
-    \caption{Overview of materials and defects that have been demonstrated to exhibit quantum  compatible characteristics such as single-photon emission and coherent spin manipulation.}
+    \caption{Overview of materials and defects that have been demonstrated to exhibit quantum  compatible characteristics such as single-photon emission and coherent spin manipulation.
+The subscript denotes lattice site and $V$ refers to a vacancy.
+}
     \begin{tabular}{c|c|c|c}
@@
 Thus, the first approach targets a more narrow prediction space than the second approach does.
-However, the most restricted approach is the empirical one, relying exclusively on previous findings rather than assuming which material properties are important.
+However, the most selective approach is the empirical one, relying exclusively on previous findings rather than assuming which material properties are important.
 
@@
 This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training, testing and validation of the ML methods.
+Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
 
@@
 After selecting and fine-tuning the entries for our labeled datasets we are now ready to apply the various ML methods discussed earlier.
-We split our labeled datasets into a so-called training set, a validation set and finally a test set which is not included in the training and validation process.
+We split our labeled datasets into a so-called training set and a test set which is not included in the training process.
 This process will allow us to classify specific materials as potential candidates for quantum technology applications.
@@
 These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above (recall that the labeled datasets are split into training, validation and test sets), yielding twelve sets of materials that were predicted as suitable material hosts for QT applications.
+These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of materials that were predicted as suitable material hosts for QT applications.
 
@@
 Note also that in  Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
-In the ML analysis here the model development is done on the training and validation sets.
+In the ML analysis here the model development is done on the training set.
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
@@
     \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
-Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training and validation sets using gradient boosting \cite{Hastie2009,xgboost2016}.
+Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
 The latter shows that for the empirical approach most of the physics is represented by a few features.
@@
 
-Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for all ML methods in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+The trend is maintained for all four ML methods (see the Supplementary Material at \cite{supplementary}).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
@@
 
-We first consider the machine learning classification of the test set derived in the Ferrenti approach.
-From the labeled dataset of $23.623$ materials, the four methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
+%We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
+From the predicted dataset of $23.623$ materials, 
+the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
 All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
@@
 amount of labeled data than the Ferrenti approach.  
-The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the labeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
+The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable (see Table~\ref{tab:qt-materials}) are, in fact, predicted as suitable candidates.
@@
 Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
-The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
+%The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
+The Ferrenti approach also admits a large amount of materials as suitable compared to the empirical approach, while the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
+%However, the amount is yet too  The resulting predictions are not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 This resonates with the observations from the principal component analysis; an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but some variations throughout the crystal in, e.g., bond length and symmetry are needed.
-This is in contrast to the expectations that guided the formulation of the test, training and validation sets in the Ferrenti and extended Ferrenti approaches.
+This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti and extended Ferrenti approaches.
 Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well and may be more important.
@@
 While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT compatible properties to manifest in a semiconductor host.
-Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets.
+
+Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabelled materials as suitable, while agreeing on a large part of these materials. 
+%Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets. 
 The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
@@
 To summarize, the data extraction tools developed in this work resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
-Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training, testing and validation of four ML algorithms.
+Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training and testing of four ML algorithms.
 We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
@@
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals \cite{Tran2009} is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
-Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on 30.04.2021 at \url{figshare.com}.
+Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on 30.04.2021 (see Ref.
+\cite{Choudhary2020}).
+%at \url{figshare.com}.
 
@@
 The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
-In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website \url{aflowlib.org}.
+In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website
+(see Ref. \cite{Isayev2017}).
+%\url{aflowlib.org}. 
 We extract the crystallographic information files (CIF) for the crystals from Materials Project, use the CIF files as input to AFLOW-ML, which then returns an anticipated band gap.

### 2022-03-08 supplementary.tex
Updates from Overleaf

@@
 
-Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training, test and validation sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training and test sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.

### 2022-03-10 paper_v3_cut.tex
Updates from Overleaf

@@
 \author{Marianne Etzelm\"uller Bathen}
+\email{bathen@aps.ee.ethz.ch}
 \affiliation{Advanced Power Semiconductor Laboratory, ETH Z{\"u}rich, 8092  Z{\"u}rich,  Switzerland}
@@
 
-The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research project FUNDAMeNT (no. 251131) and QuTe (no. 325573). 
+The work of LV and MEB was supported by the Research Council of Norway and the University of Oslo through the frontier research projects FUNDAMeNT (no. 251131) and QuTe (no. 325573). 
 The work of MEB was supported by an ETH Zurich Postdoctoral Fellowship. 
@@
 \section*{Author contributions}
-Add! 
-%MEB, LV and MHJ conceived the main theme of the work.
-OH developed the programs and performed the bulk of the work.
+MEB, LV and MHJ conceived the main theme of the project.
+OH developed the programs and performed the bulk of the work while MEB lead the writing process.
 All authors have contributed to the writing of the paper and the discussion and analysis of the data.
@@
 \section*{Additional information}
-Correspondence and requests for materials should be addressed to ?
+Correspondence and requests for materials should be addressed to \url{bathen@aps.ee.ethz.ch}.
 

### 2022-03-10 paper_v3_cut.tex
Updates from Overleaf

@@
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
-Simultaneously, the concepts of entanglement and teleportation may eventually facilitate advanced quantum communication protocols such as quantum cryptography and the quantum internet, spurring further investigations into technologies based on quantum mechanics.
+Simultaneously, the concepts of entanglement and teleportation may eventually facilitate advanced quantum communication protocols such as quantum cryptography and the quantum internet \cite{quantum-internet-kimble}, spurring further investigations into technologies based on quantum mechanics.
 
@@
 In this work, the data in question are provided by bulk density functional theory (DFT) calculations to obtain the ground state properties of different elements and compounds.
-Combined with ML methods we provide a path towards precise classification of candidate materials.
+Combined with machine learning (ML) methods we provide a path towards precise classification of candidate materials.
 The inclusion of ML methods follows recent trends in applications of statistical learning, data science and machine learning for scientific discoveries, see for example Refs.~\cite{deiana2021,Carleo2019}.
@@
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training and sets for the ML methods.
+The labeled data are then grouped into training and test sets for the ML methods.
 
 Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
-Firstly, although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable \cite{Atatuere2018,Zhang2020}.
+Although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot (QD) structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable \cite{Atatuere2018,Zhang2020}.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
-Thirdly, defining materials as unsuitable candidates for QT has proven to be surprisingly intricate. 
-We follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
+Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult.
+This is similar to the case for the suitable candidates in that it is not understood which mechanisms break the quantum properties.
+However, we can make some educated guesses and assume that the negation of the criteria we use to select suitable candidates should give unsuitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates (we would assume that most materials are not optimal for the kind of QT we are concerned with in this article).
+We will then find ourselves in a situation with skewed data sets were we have fewer unsuitable than suitable candidates.
+This will not be a perfect method, but it will serve as a starting point and demonstration for how the labeling procedure could be improved.
+Below we follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
 
@@
 $65 \ \%$ as suitable for QT applications.
+Here we see the first example where the criteria for the unsuitable candidates is more restrictive for our data set than the criteria for the suitable candidates.
 
@@
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
-The selected features are found on the x-axis, while the y-axis shows the value of the data.
+The selected features are found on the $x$-axis, while the $y$-axis shows the value of the data.
 Thus, parallel coordinate plots can turn complex many-dimensional data into a compact  two-dimensional representation.
@@
 Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
-The viewpoints for all materials are down along the $c$ axis.
+The viewpoints for all materials are down along the $c$-axis.
 }
@@
 The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right.
+The Ferrenti and extended Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
     }
@@
 
-We interpret the standard deviation  of the RDF such that zero std in the RDF means that there is no variation in the radial symmetry throughout the material.
+We interpret the standard deviation  of the RDF such that zero standard deviation in the RDF means that there is no variation in the radial symmetry throughout the material.
 Similarly, zero standard deviation in the average bond length would mean that all bonds are identical throughout the crystal.
@@
 
-Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabelled materials as suitable, while agreeing on a large part of these materials. 
+Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
 %Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets. 

### 2022-03-10 supplementary.tex
Updates from Overleaf

@@
 \author{Marianne Etzelm\"uller Bathen}
-\affiliation{Advanced Power Semiconductor Laboratory, ETH Zürich, 8092  Zürich,  Switzerland}
+\email{bathen@aps.ee.ethz.ch}
+\affiliation{Advanced Power Semiconductor Laboratory, ETH Z\"urich, 8092  Z\"urich,  Switzerland}
 
@@
 The relevant hyperparameters for logistic regression were the maximum iterations.
-The number of iterations was set at $400$, and the optimal regularization term was $0.46$.
+The number of iterations was set to $400$, and the optimal regularization term was $0.46$.
 For random forests and decision trees, we found the maximum depth to be seven.

### 2022-03-11 supplementary.tex
Updates from Overleaf

@@
 Therefore, the choice was made to facilitate a compromise between precision and recall.
-For gradient boosting, we find the optimal maximum depth as four due to a decline in overall metrics for increasing depth except for training accuracy.
-An increasing depth  could potentially result in overfitting.
+For gradient boosting, we find the optimal maximum depth to be four due to a decline in overall metrics for increasing depth.
+That is, except for the training accuracy, demonstrating a case of potential overfitting.
 
@@
 
-Lastly, we turn to the empirical approach to data labeling, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process.
+Lastly, we turn to the data labeling using the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process.
 However, in contrast to the two labeled datasets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
@@
 The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics.
-Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with the F$1$-score of $0.98$.
+Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with an F$1$-score of $0.98$.
 Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
@@
 The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations at $400$.
-The decision trees uses a maximum depth of $6$, where larger values increased the training accuracy but not any other metric.
+The decision trees uses a maximum depth of $6$, where larger values only increased the training accuracy.
 The maximum depth for  random forests was set to $6$.

### 2022-03-21 paper_v3_cut.tex
Updates from Overleaf

@@
 \begin{abstract}
-%MB 
-%Original: 337 words
-%New: 256 words 
-%Wanted: 150 words
-
-%Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, searching these databases to find promising candidate materials for quantum technology applications among tens of thousands of contenders is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning (ML) methods.
-
-%Data extraction tools have been developed for a number of materials science databases resulting in a dataset consisting of over $25.000$ materials.
-The information from the databases was converted into nearly $5000$ physics-informed features.
-Furthermore, we have developed and implemented three different approaches for the data labeling process: \textit{The Ferrenti approach}, \textit{the extended Ferrenti approach}, and \textit{the empirical approach}.
-The three approaches define distinct sets of labeled data for the supervised ML methods logistic regression, decision trees, random forests and gradient boosting.
-
-%We find that the Ferrenti and extended Ferrenti approaches predict a broad range of materials as suitable for quantum technologies.
-The restrictions set in the empirical approach, which relies exclusively on findings from the literature, gave substantially fewer candidates with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the ML methods based on the Ferrenti and extended Ferrenti approaches that focused on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when labeling a material as suitable for QT.
-All four ML methods applied to the dataset derived using the empirical approach agreed on a set of $214$ predicted candidate materials.
-All three approaches and all four machine learning methods agreed on a subset of $47$ eligible candidates
-%(to a probability of $>50 \ \%$) 
-%of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
 
@@
 However, searching these databases to find promising candidate materials for quantum technology applications
-%among tens of thousands of contenders
 is a major challenge.
@@
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, and yielded $214$ predicted candidates that were common between all approaches and ML methods.
+The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding $214$ predicted candidates that were common between all approaches and ML methods.
 Example materials include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
@@
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ featurizers (each generates several features) selected as material descriptors in this work are summarized and described in the Supplementary Material at \cite{supplementary}.
+The $39$ featurizers (each generates several features) selected as material descriptors in this work are summarized and described in the Supplementary Information at \cite{supplementary}.
 The selection of features was kept rather wide as we do not want to make {\em ex ante} assumptions on which features best describe a solid state material platform for quantum technology.
@@
 Although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot (QD) structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable \cite{Atatuere2018,Zhang2020}.
-An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood, neither for the case of defect- or QD-based quantum technologies.
-Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult.
-This is similar to the case for the suitable candidates in that it is not understood which mechanisms break the quantum properties.
-However, we can make some educated guesses and assume that the negation of the criteria we use to select suitable candidates should give unsuitable candidates.
-A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates (we would assume that most materials are not optimal for the kind of QT we are concerned with in this article).
+An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood.
+Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are also unknown. 
+The strategy for selection of unsuitable candidates is thus that the negation of the criteria we use to select suitable candidates should give unsuitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates. 
 We will then find ourselves in a situation with skewed data sets were we have fewer unsuitable than suitable candidates. 
-This will not be a perfect method, but it will serve as a starting point and demonstration for how the labeling procedure could be improved.
+This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
 Below we follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
@@
 The first approach to labeling a selection of materials in the dataset is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}. 
-They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project.
+They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the MP.
 In this framework, we label \textbf{suitable} candidates by the following steps:
@@
 $65 \ \%$ as suitable for QT applications.
-Here we see the first example where the criteria for the unsuitable candidates is more restrictive for our data set than the criteria for the suitable candidates.
+Here we see the first example of how the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
 
@@
 
-%% OH: Dirty details about suitable materials:
 Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
@@
 Thus, the first approach targets a more narrow prediction space than the second approach does.
-However, the most selective approach is the empirical one, relying exclusively on previous findings rather than assuming which material properties are important.
+However, the most selective approach is the empirical one, relying exclusively on previous findings rather than assuming which material properties are influential.
 
-%MB copied from above  
 %Ferrenti 
@@
 Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the training data.  
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.  
 %Extended Ferrenti 
@@
     \caption{Two-dimensional scatter plots for the three different approaches.
-We have identified the two eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
+We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
 Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots.
@@
 For example, the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
-Moreover, two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-%Moreover, all candidates that were labeled as unsuitable exhibit polar space groups (follows from the definition of the training sets), and the two approaches also share that suitable candidates can consist of up to five different elements.
+Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
 The most striking difference is found for the empirical approach.
@@
 Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-In the empirical approach the polarity of the material's space group may be less important compared to the Ferrenti based approaches, while the accepted values for ionic character and covalent range appear more restricted ( Fig.~\ref{fig:parallel-coordinates-approaches} ).
+In the empirical approach the polarity of the material's space group may be less important compared to the Ferrenti based approaches, while the accepted values for ionic character and covalent range appear more restricted (Fig.~\ref{fig:parallel-coordinates-approaches}).
 
 To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
-Principal component analyses fall  under the category of unsupervised learning within ML  methods.
 Here we apply PCA to the labeled datasets in order to reveal specific features that stand out.
@@
 
-In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of the figure is dominated by suitable candidates (green, blue, yellow and black symbols), while the unsuitable candidates (red triangles) are similarly restricted to the lower right corner, albeit with some exceptions.
+In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable candidates (green, blue, yellow and black symbols), while the unsuitable candidates (red triangles) are similarly restricted to the lower right corner, albeit with some exceptions.
 Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
@@
 
-%summary - do we need this? 
-%In summary, using various data extraction tools for a number of materials science databases, we have obtained a dataset consisting of over $25.000$ materials.
-The information from this dataset has then been converted into nearly $5000$ physics-informed features.
-After selecting and fine-tuning the entries for our labeled datasets we are now ready to apply the various ML methods discussed earlier.
+%MB Repetition, I took this out 
+%After selecting and fine-tuning the entries for our labeled datasets we are now ready to apply the four ML methods discussed earlier.
 We split our labeled datasets into a so-called training set and a test set which is not included in the training process.
@@
 These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four ML methods were applied to the training sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of materials that were predicted as suitable material hosts for QT applications.
+These four ML methods were applied to the labeled data sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
 
@@
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
-%
 Next, in the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
 We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Material \cite{supplementary}.
-%
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Information \cite{supplementary}.
 The three data labeling approaches (Ferrenti, extended Ferrenti and empirical) define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
@@
 Note also that in  Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
-In the ML analysis here the model development is done on the training set.
+Here, the ML analysis is done on the labeled data for each approach.
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
 For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components.
-%
 In the case of the empirical approach and in contrast to the Ferrenti approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
 Gradient boosting
-%, in contrast to the case for the two Ferrenti  approaches, 
 also experiences the best performance for just a few principal components.
@@
     \end{subfigure}
-    \caption{Visualizing different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
+    \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
 Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
@@
 Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
-The trend is maintained for all four ML methods (see the Supplementary Material at \cite{supplementary}).
+The trend is maintained for all four ML methods (see the Supplementary Information at \cite{supplementary}).
 Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
@@
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
-Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b).
-Similar conclusions are reached when using logistic regression, decisions trees and random forests as classification methods, lending support to our observations.
-The distinct importance of the first principal component partly explains why we experience a high accuracy for only a single feature (see also the Supplementary Material at \cite{supplementary} for further details).
+Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
+Similar conclusions are reached when using logistic regression, decisions trees and random forests as classification methods (see the Supplementary Information at \cite{supplementary}).
+The distinct importance of the first principal component partly explains why we experience a high accuracy for only a single feature.
 The first principal component's corresponding features is a complex combination of several material properties, but we find that it includes bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
@@
 Indeed, precisely these features were used as guidance in the data labeling process.
-Thus, the ML methods are preserving the criteria imposed in the Ferrenti approaches and perpetuate our initial biases on which material properties to look for.
+Thus, the ML methods are preserving the criteria imposed in the Ferrenti approaches and perpetuate our initial assumptions on which material properties to look for.
 For the empirical approach, on the other hand, we did not guide the selection process in terms of specific properties.
@@
 After training the ML algorithms using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Material at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
 An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in  Table~\ref{tab:probabilites}.
@@
 
-%We first consider the machine learning classification of the test set derived in the Ferrenti approach. 
-From the predicted dataset of $23.623$ materials, 
+From the predicted dataset of $23.623$ materials 
 the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
@@
     \caption{Overview of the number of predicted suitable candidates as a function of a given ML method's confidence when the four methods in an approach agree.
-A cut-off value of $0.5$ represents the confidence of a coin flip, while $1.0$ is a fully confident prediction.}
+A threshold value of $0.5$ represents the confidence of a coin flip while $1.0$ is a fully confident prediction.}
     \begin{tabular}{c|c|c|c}
@@
 
-Consider the $9$ materials that were classified by the empirical approach as suitable to a confidence of $0.85$ or higher by all four ML methods; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
+Consider the $9$ materials that were classified as suitable to a confidence of $0.85$ or higher by all four ML methods in the empirical approach; BN, CdSe (2 structures), BC$_2$N (2 structures), InAs, CuI (2 structures), and ZnCd$_3$Se$_4$.
 The nine materials (considering different crystal structures) each belong to one of the four crystal systems cubic, hexagonal, tetragonal and orthorombic.
@@
 Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-Importantly, the diamond-like structure of BC$_3$N was recently predicted as a prominent spin qubit material host \cite{Wang2020SpinQB}.
+Importantly, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
 By creating a boron vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
@@
 Finally, both compounds of the BC$_2$N structure are listed to decompose into hexagonal BN $+$ C.
+However, synthesis may still be possible depending on the growth conditions.
 
 Lowering the cut-off requirement from $0.85$ to $0.75$ for all ML methods results in $66$ candidate materials for the empirical approach.  
-The full list of these $66$ candidates is displayed in the Supplementary Material at \cite{supplementary}. 
+The full list of these $66$ candidates is displayed in the Supplementary Information at \cite{supplementary}. 
 In addition to the nine materials discussed above and some elemental and binary semiconductors, the list of $66$ predicted suitable candidates now also includes ternary compounds of the formula ABC$_2$.
@@
     \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$).
-Compounds marked by an asterisk are predicted to be unstable to tranformation into other phases in MP.
+Compounds marked by an asterisk are predicted to be unstable to transformation into other phases in the MP database.
 }
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure.
-The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported from $2.45$~eV (optical band gap) \cite{Ubale2014} up to as large as $5.6$~eV \cite{SaumGeorge1959}.
+Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a $2.0$~eV band gap and decomposes to a similar MgSe configuration.
+%The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported at $2.45$~eV (optical band gap) \cite{Ubale2014}. 
 MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
-We believe that these criteria may favor defects acting as spin centers with qubit potential and MgSe is thus identified as another promising host material in this regard.
+We note that these properties may favor defects acting as spin centers with qubit potential and MgSe is thus identified as an interesting host material in this regard.
 
@@
 Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
-%The Ferrenti approach also admits a large amount of materials from the training set as compared to the empirical approach, but the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
-The Ferrenti approach also admits a large amount of materials as suitable compared to the empirical approach, while the resulting data are otherwise not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
-%However, the amount is yet too  The resulting predictions are not very different from the extended version, whereas the empirical approach predicts fewer suitable candidates that are possible to verify manually.
+The Ferrenti approach also predicts a large amount of materials as suitable compared to the empirical approach, but the resulting data are otherwise not very different from the extended version.
+The empirical approach, on the other hand, predicts fewer suitable candidates that are possible to examine  manually.
 Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
@@
 All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
-(see the Supplementary Material at \cite{supplementary} for the full list). 
+(see the Supplementary Information at \cite{supplementary} for the full list). 
 Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
@@
 
-%Turning to why the specific materials were chosen ... 
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
@@
 
-The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Material at \cite{supplementary} for the predicted material distributions of the latter two features).
+The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
 Intriguingly, as shown in Fig.~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
@@
 For comparison, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
-Further, we find that the covalent radii of the materials (see the Supplementary Material) distribute with two peaks in the data for all approaches. 
+Further, we find that the covalent radii of the materials (see the Supplementary Information) distribute with two peaks in the data for all approaches. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in Fig.~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Material at \cite{supplementary}.
+One configuration of the standard deviation of the RDF is demonstrated in Fig.~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
 Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti approaches and the empirical approach.
@@
 Intriguingly, the peaks in the distributions of the predicted materials are not found for perfectly symmetric materials with identical bond lengths; instead, some variation in the bond and wavefunction distributions is found to be optimal for a material to be suitable for QT.
-Note that the maxima in Fig.~\ref{fig:histogram_new}(c) seem to appear for moderate standard deviations in the RDF, indicating that a certain degree of symmetry is likely necessary for a material to act as a suitable QT host.
+Note that the maxima in Fig.~\ref{fig:histogram_new}(c) seem to appear for moderate standard deviations in the RDF, indicating that a certain degree of symmetry is necessary for a material to act as a suitable QT host.
 The exact degree and type of symmetry is still open to debate and merits further study.
-Similar symmetry related features such as the standard deviation of the average bond length (see Fig.~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Material) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+Similar symmetry related features such as the standard deviation of the average bond length (see Fig.~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Information at \cite{supplementary}) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
@@
 Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
-%Our findings are corroborated by the fact that all four ML methods exhibit similar results for all datasets. 
 The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
@@
 Therefore, we extend their implementation to facilitate such featurizations.
-The features selected for featurization herein are summarized in the Supplementary Material at \cite{supplementary}.
+The features selected for featurization herein are summarized in the Supplementary Information at \cite{supplementary}.
 

### 2022-03-21 supplementary.tex
Updates from Overleaf

@@
 \usepackage[T1]{fontenc}
-\usepackage[sc, osf]{mathpazo}
-\usepackage[euler-digits]{eulervm}
+%\usepackage[sc, osf]{mathpazo}
+%\usepackage[euler-digits]{eulervm}
 \usepackage{booktabs}
@@
 
-\title{\textit{Supplementary Material} \\ 
+\title{\textit{Supplementary Information} \\ 
 Predicting Solid State Material Platforms for Quantum Technologies}
@@
 
-In the evaluation of the machine learning methods for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations, see for example \cite{Hastie2009} for details on the cross-validation procedure.
-Due to imbalanced training data, we apply four different evaluation metrics to each of the four machine learning algorithms discussed in this work.
+In the evaluation of the machine learning methods for the three different approaches, we apply a $5\times 5$ stratified cross-validation when searching for the optimal hyperparameter combinations, see for example Ref.~\cite{Hastie2009} for details on the cross-validation procedure.
+We apply four different evaluation metrics to each of the four machine learning algorithms discussed in this work.
 
@@
 Therefore, most parameters are the default values defined by Scikit-Learn.
-The only parameter that we found that could potentially improve the evaluation metric F$1$  (see Ref.~\cite{sammut2010,geron2022} for a definition of various metrics) was the maximum depth for the decision trees (these are also used as so-called weak learners in ensemble methods like gradient boosting and random forests \cite{geron2022}).
+The only parameter that was found to potentially improve the evaluation metric F$1$  (see Refs.~\cite{sammut2010,geron2022} for a definition of various metrics) was the maximum depth for the decision trees (these are also used as so-called weak learners in ensemble methods like gradient boosting and random forests \cite{geron2022}).
 In our work we adjusted
-%between 
 the depth of the trees to vary from $1$ to $8$.
@@
 Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models.
-%, just for one arbitrary machine learning algorithm like logistic regression.
 
 \subsubsection*{Ferrenti approach}
-%Ferrenti 
 The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Fig.~\ref{fig:01-pca}, where we present the mean accuracy of the four ML models applied to the training set, and the balanced accuracy, precision, recall, and F$1$-score
-%(see for example \cite{geron2022} for a definition of various score metrics) 
-for the test set as a function of the number of principal components.
-For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score \cite{sammut2010,geron2022}.
+for the test set as a function of the number of principal components. For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score.
 
@@
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall, and F$1$ scores are based on the test set \cite{geron2022,sammut2010}.
+Precision, recall, and F$1$ scores are based on the test set.
 The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
@@
 
-\begin{table}[t]
+\begin{table}[b]
 \centering
@@
 The number of iterations was set to $400$, and the optimal regularization term was $0.46$.
-For random forests and decision trees, we found the maximum depth to be seven.
-Gradient boosting, which normally uses a weak learner, had a decision tree depth of four.
+For random forests and decision trees, we found the maximum depth to be $7$.
+Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
 We found the best performing method to be logistic regression, but this method depends on a large number of principal components.
@@
 
-  \caption{Five figures visualizing different parameters for the $25$ most principal components ranked in descending order by the explained variance for the Ferrenti approach.
+  \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by the explained variance for the Ferrenti approach.
 The panels show the logistic regression coefficients, decision trees feature importance, random forests feature importance, gradient boosting feature importance, and explained variance that is retained by choosing each of the eigenvectors.
@@
 Large positive or negative coefficients can be considered increasingly important, where positive (negative) coefficients will contribute to making positive (negative) predictions.
-In the three next panels, namely for the machine learning methods  decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
-We observe that the single most important feature for all ML methods is the fifth principal component.
+In the next three panels we visualize the mean impurity-based feature importance and the standard deviation for the ML methods decision trees, random forests, and gradient boosting, respectively.
+We observe that the single most important feature for all ML methods in the Ferrenti approach is the fifth principal component.
 Selecting the highest values of this eigenvector, we find that the corresponding features originate from the DFT band gap of the elemental solids among the elements in the compound as calculated by Materials Agnostic Platform for Informatics and Exploration (MagPie).
@@
 After the first ten principal components, we observe that the methods adapt the other principal components with varying degrees.
-The coefficients for the case of logistic regression experience large fluctuations, but the three remaining models find the first and second principal components important in addition to the fifth.
+The coefficients for the case of logistic regression experience large fluctuations, but the three remaining models find that the first and second principal components are important in addition to the fifth.
 In order of importance, we observe that the second component's largest values correspond to the electronegativity, maximum ionic character, and covalent radius among the elements in the composition.
@@
 While the first principal component encompasses the largest explained variance, it does not provide any specific information on which features it represents.
-
-%We note that looking at feature importance can be regarded as misleading for data involving correlated features, but we consider the analysis safe due to the projection of the original data to orthogonal vectors, known as principal components, which results in uncorrelated features.
-%OH: Seb or Oyv, is it correct to say uncorrelated?
 
@@
 Train stands for normal training accuracy, while test is the balanced accuracy on the test set.
-Precision, recall and F$1$ scores \cite{geron2022,sammut2010} are based on the test set.
+Precision, recall and F$1$ scores  are based on the test set.
 The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}
@@
 For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
-All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75 \ \% : 25 \ \%$.
-This result comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
-%On the other hand, we find a small precision for the first component since the ML methods  predict many materials, both actually labeled suitable and unsuitable, as suitable candidates, and the latter case is particularly large.
-On the other hand, we find a low precision score for the first component since the ML methods  predict many materials as suitable regardless of whether they were labeled as suitable or unsuitable in the initial data labeling process, and the latter case is particularly numerous.
+All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75 \ \% : 25 \ \%$ (suitable:unsuitable).
+This ratio comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
+On the other hand, we find a low precision score for the first component since the ML methods  predict many materials as suitable regardless of whether they were labeled as suitable or unsuitable in the initial data labeling process.
 This trend is revealed when looking at the balanced accuracy score.
 For all figures, it remains the lowest score of the evaluation metrics largely due to the inaccuracy of true negatives for the cross-validations.
+
+Overall the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
+Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
+The decision trees method exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
+The random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
 
@@
 
-Overall the search for optimal hyperparameters in Fig.~\ref{fig:02-pca} for the extended Ferrenti approach bears resemblance to Fig.~\ref{fig:01-pca} for the Ferrenti approach.
-Logistic regression performs optimally for many principal components, and is the only method that continues to improve with an increasing number of components.
-The decision trees method exhibits a large fluctuation of scores, where the number of false positives is dominating the balanced accuracy score.
-The random forests method exhibits fewer fluctuations compared to decision trees as a consequence of the ensemble decision trees, while gradient boosting does not improve beyond $100$ principal components.
-
-The optimal hyperparameters are summarized in Table~\ref{tab:02-pc}.
+The optimal hyperparameters for the extended Ferrenti approach are summarized in Table~\ref{tab:02-pc}.
 We find that logistic regression with $175$ principal components performs more or less like a perfect classifier with overall high scores.
@@
 
-The relevant hyperparameters for logistic regression were the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
+The relevant hyperparameters for logistic regression are the regularization strength and the maximum iterations, which were set to $0.46$ and $400$, respectively.
 Smaller regularization values resulted in worse scores, while increasing values did not noticeably affect the results.
@@
 However, we find that random forests and gradient boosting experience the fifth principal component as important.
-%Similar to the Ferrenti approach, the corresponding features with the highest value for the first principal component originates from the DFT band gap of the elemental solids among the elements in the composition.
-Similar to the Ferrenti approach, the extended Ferrenti approach finds the DFT band gap of the elemental solids among the elements in the composition important.
+Similar to the Ferrenti approach, the extended Ferrenti approach finds the DFT band gap of the elemental solids among the elements in the composition to be important.
 The feature regarding the band gap originates from the highest value from the first principal component.
@@
 Lastly, we turn to the data labeling using the empirical approach, which resulted in $404$ unsuitable and $202$ suitable candidates through the initial selection process.
-However, in contrast to the two labeled datasets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
+However, in contrast to the two labeled data sets discussed above, the majority of the entries was in this case labeled as unsuitable candidates.
 
 The grid search for the optimal number of principal components is visualized in Fig.~\ref{fig:03-pca} for the empirical approach.
-Interestingly, we find that all ML methods  experience high scores for just a few principal components, where
-%$1$
-the first
-principal component earns at least $0.93$ scores for all evaluation metrics.
-%This information was also revealed for an earlier two-dimensional visualization of a scatter plot showing the two most important principal components in figure \ref{fig:2dscatterplotpca}, and consequently can make the models find the optimal decision boundary more easily.
+Interestingly, we find that all ML methods  experience high scores for just a few principal components, where the first principal component earns at least $0.93$ scores for all evaluation metrics.
 
@@
 \end{table}
-
-The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics.
-Importantly, we find the difference in the number of principal components as most prominent, where logistic regression finds an optimum at $61$ with an F$1$-score of $0.98$.
-Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
 
@@
 
-Lastly, gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$.
+The optimal hyperparameters are summarized in Table~\ref{tab:03-pca}, where all ML methods exhibit high evaluation metrics.
+The difference in the number of optimal principal components is prominent.
+Logistic regression finds an optimum at $61$ with an F$1$-score of $0.98$.
+Decision trees uses only $9$ principal components to achieve an F$1$ score of $0.95$, while random forests needs $27$ principal components to gain an F$1$ score of $0.97$.
+Gradient boosting performs optimally at $13$ principal components with a mean F$1$-score of $0.96$.
 The relevant hyperparameters were the regularization term for logistic regression, which was set to $0.021$, and the maximum number of iterations at $400$.
@@
 
-%OH: Commented out the three next paragraphs, since this is mentioned in main text.
-%The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches.
-Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approach, respectively.
-Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
-
-%Secondly, we find that the first principal component is by far the most important feature for all models, as visualized in Figure~\ref{fig:03-fi}.
-This is part of the reason why we experience a large accuracy for only a single feature, as seen in Figure~\ref{fig:03-pca}.
-The first principal component's corresponding features are challenging to explain due to small variations of values, but we see it including
-%However, it differs when it comes to which top features the first principal component describes, which includes 
-%bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
-
-%Thirdly, the empirical approach differs in how much explained variation is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
-We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
+In Fig.~\ref{fig:03-fi}, we visualize how the four  ML methods in the empirical approach interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+Here, the most important information is captured by the first 15 components. The most important features seem to be found within the first few principal  components. 
+Logistic regression is represented in the top panel of Fig.~\ref{fig:03-fi} where the mean fitted coefficients and the standard deviation are visualized.
+In the three next panels, namely for the ML methods decision trees, random forests, and gradient boosting, we visualize the mean impurity-based feature importance, along with the standard deviation.
+We observe that the single most important feature for all ML methods is the first principal component in the case of the empirical approach.
+Selecting the highest values of this eigenvector, we find that the corresponding features is a complex combination of several material properties, including bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 
@@
 We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML methods, while the empirical approach results in a substantially narrower selection of contender materials.
-Note that the confidence threshold was set to $0.5$ in this case.
+Note that the confidence threshold was set to $0.5$ in this case for all the methods and approaches.
 
@@
 The four ML methods agree on $6804$ suitable candidates,  however, many of the materials are predicted with a confidence similar to that of a coin-flip.
-If we were to raise the minimum bar of a prediction to  
-%$0.7$, the four methods would only agree on $3000$ suitable candidates
-$0.75$, the four methods would only agree on $1784$ suitable candidates.
+If we were to raise the minimum bar of a prediction to $0.75$, the four methods would only agree on $1784$ suitable candidates.
 
@@
 
+\newpage
+
 \input{appendix/tablesof66materials.tex}
 
-Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning methods and all three approaches (Ferrenti, extended Ferrenti and empirical) agreed on (to a $0.5$ cut-off value).
+Table~\ref{tab:04-probability-candidates} displays the $47$ predicted candidates that all four machine learning methods and all three approaches (Ferrenti, extended Ferrenti and empirical) agreed on (to a $0.5$ threshold level).
 The list contains $8$ elemental, $29$ binary, and $10$ tertiary compounds.
@@
 \end{subfigure}%
+\caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
+The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
+\label{fig:histograms_supp1}
 \end{figure}
 
-Figure~\ref{fig:histograms_supp} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
+Figure~\ref{fig:histograms_supp1} displays the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of the (a) covalent radius of the elements in the composition, (b) maximum packing efficiency, and standard deviation of the radial distribution function (RDF) with center at (c) $2.0$ and (d) $3.0$.
 The corresponding figure in the main text shows the standard deviation of the RDF with Gaussian center at $1.0$.
-%Several observations can be made based on the histograms. 
-Panels (e) chemical environment site fingerprint, (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the material band gaps referenced to the normalized mean of the entire data set.
 
-\begin{figure}[ht!]\ContinuedFloat
+We observe that the covalent radii of the materials (see Fig.~\ref{fig:histograms_supp1}a) distribute with two peaks in the data in all approaches.
+The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar.
+The trend of two data peaks is repeated for the maximum packing efficiency (see Fig.~\ref{fig:histograms_supp1}b) but is much more prominent for the empirical approach.
+This indicates that the material density, or in other words the bond length, is an important parameter for QT suitability.
+
+\begin{figure}[ht!]
+\begin{subfigure}[t]{1\textwidth}
+    \input{figures/histograms/new/legend.tex}
+\end{subfigure}
 \begin{subfigure}[b]{0.45\textwidth}
@@
 \end{subfigure}
-\caption{Number of predicted suitable materials as a function of the (a) covalent radius, (b) maximum packing efficiency, and standard deviation of the radial distribution function with center at (c) $2.0$ and (d) $3.0$.
-Panel (e) shows standard deviation of the chemical environment of the gaussian symmetric function.
-Panels (f) crystal fingerprint and (g) OP site fingerprint are related to bond orientational parameters, while (h) shows the band gap referenced to the normalized mean of the entire data set.
-%The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach. 
+\caption{Number of predicted suitable materials as a function of the (a) standard deviation of the chemical environment of the gaussian symmetric function.
+Panels (b) crystal fingerprint and (c) OP site fingerprint are related to bond orientational parameters, while (d) shows the band gap referenced to the normalized mean of the entire data set.
 The Ferrenti and extended Ferrenti approaches refer to the left y-axis and the empirical approach to the right. All panels were taken for a $0.75$ cut-off. }
-\label{fig:histograms_supp}
+\label{fig:histograms_supp2}
 \end{figure}
 
-Firstly, we find that the covalent radii of the materials (see Fig.~\ref{fig:histograms_supp}a) distribute with two peaks in the data in all approaches.
-The maxima are slightly shifted towards the right for the empirical approach compared to the two others but otherwise the data distributions are similar.
-The trend of two data peaks is repeated for the maximum packing efficiency (see Fig.~\ref{fig:histograms_supp}b) but is much more prominent for the empirical approach.
-This indicates that the material density, or in other words the bond length, is an important parameter for QT suitability.
+Figure~\ref{fig:histograms_supp2} shows the number of predicted suitable materials for all approaches (all ML methods in an approach agree to a $0.75$ confidence level) as a function of bond orientational parameters and band gap.
+Panels (a) chemical environment site fingerprint, (b) crystal fingerprint and (c) OP site fingerprint are related to bond orientational parameters, while (d) shows the material band gaps referenced to the normalized mean of the entire data set.
+
+\newpage
 

### 2022-03-28 paper_v3_cut.tex
Updates from Overleaf

@@
 workflow can be found at \cite{Ohebbi2021}).
-We start by extracting all entries in the MP database that match a specific query. 
+We start by extracting all entries in the Materials Project (MP) database  \cite{Jain2013,Jain2018} that match a specific query. 
 The MP database contains ground state properties of different materials that are computed using density functional theory.
@@
     \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
-    \caption{The project workflow starting from an initial MP query, and ending with a featurized dataset with entries from several other databases. 
+    \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
     To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
 This process is repeated iteratively until all the data has been featurized.
-Abbreviations used are Materials Project (MP), density of states (DOS) and electronic band structure (band).
+\emph{DOS} refers to density of states and \emph{band} to the electronic band structure.
     }
@@
 After material extraction we apply tools from the open-source library Matminer \cite{Ward2018} to generate thousands of features from the data.
-We will refer to this process as featurization herein.
+We will refer to this process as featurization.
 A schematic visualization of the featurization process in Matminer is shown in  Fig.~\ref{fig:flowchart}
@@
 The first approach to labeling a selection of materials in the dataset is based on the criteria proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}. 
-They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the MP.
+They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project.
 In this framework, we label \textbf{suitable} candidates by the following steps:
@@
 The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the labeled data encompasses $78 \ \%$ more materials than for the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
+However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
 
@@
 In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
-We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the Materials Project, and transform the three labeled datasets according to the corresponding two eigenvectors.
+We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the MP database, and transform the three labeled datasets according to the corresponding two eigenvectors.
 In essence, we reduce the dimensionality of the labeled data in order to visualize them.
@@
 
-Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Figure~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 The trend is maintained for all four ML methods (see the Supplementary Information at \cite{supplementary}).
@@
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
-Secondly, the first principal component is by far the most important feature for all models in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
+Secondly, the first principal component is by far the most important feature for all ML methods in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
 Similar conclusions are reached when using logistic regression, decisions trees and random forests as classification methods (see the Supplementary Information at \cite{supplementary}).
@@
 %Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
-Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project from PBE-level DFT calculations.
+Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project \cite{Jain2013,Jain2018} from PBE-level DFT calculations.
 Increasing the threshold to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
@@
 
-Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the models recognize BN as a suitable candidate with high probability.
+Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the ML methods recognize BN as a suitable candidate with high probability.
 Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
@@
 The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
-To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, while self-assembled InAs quantum dots are an exciting possible material to use in quantum technology \cite{Liu2018}. 
+To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, while self-assembled InAs quantum dots are  exciting possible materials to use in quantum technology \cite{Liu2018}. 
 CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
@@
 We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
-Similarly, $78$ of the $214$ are also predicted as suitable by all models in the Ferrenti approach.
+Similarly, $78$ of the $214$ materials are also predicted as suitable by all ML methods in the Ferrenti approach.
 All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
@@
 
-Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials for all approaches as a function of band gap (from the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
 Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti approaches exhibiting a peak around a $2.5$~eV band gap.
-Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed in the range around $2.5$~eV using PBE. 
+Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around $2.5$~eV using the PBE functional. 
 The empirical approach exhibits a more scattered data distribution with local maxima around $1$-$2$ and $4$~eV.
@@
 The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in Fig.~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
+Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
 We note that this may be a result of the distribution of the initial dataset of $25.000$ materials that peaks around a similar value (not shown).
@@
 For comparison, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
-Further, we find that the covalent radii of the materials (see the Supplementary Information) distribute with two peaks in the data for all approaches. 
+Further, we find that the covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
-Additionally, much fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
+Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
 The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.

### 2022-03-28 supplementary.tex
Updates from Overleaf

@@
     \item \textit{Supplementary methods.} \\   Additional information on the featurization process and optimization of the machine learning methods. 
-    \item \textit{Supplementary results.} \\  Statistics and tables over the materials that were predicted by the machine learning methods based on the training sets derived using the three different data mining approaches.
+    \item \textit{Supplementary results.} \\ Statistics and tables over the materials that were predicted by the machine learning methods based on the labeled data sets derived using the three different data mining approaches.
+The supplementary results also include feature analyses for the materials predicted by the machine learning methods as suitable for QT.
     \item \textit{Supplementary references.}  

### 2022-03-30 AllFigures/01-ferrenti-approach-GB-v2.tex
update

--- 2022-01-07 figures/feature-importance/01-ferrenti-approachGB-final.tex
@@
 xtick style={color=black},
-xticklabels={,,},
 y grid style={white!69.0196078431373!black},
@@
 yticklabels={,0, 0.1,0.2},
+title={Gradient boosting feature importance},
 legend style={font=\footnotesize},
@@
 \addlegendimage{semithick, color=color0};
-\addlegendentry{Gradient boost};
+\addlegendentry{Ferrenti approach};
 \addplot [semithick, color0, mark=-, mark size=0, mark options={solid}, only marks]

### 2022-03-30 predictingQT.tex
update

--- 2022-03-28 paper_v3_cut.tex
@@
 \usepackage{hyperref}
-% \usepackage{longtable}
+
+%\usepackage{longtable}
 \usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
+    \includegraphics[width=0.9\textwidth]{AllFigures/ht-workflow-new-2.png}
     \caption{Schematic of an example workflow in material informatics.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
+    \includegraphics[width=0.9\textwidth]{AllFigures/flow_chart_2.png}
     \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
@@
         \centering
-        \scalebox{0.85}{\input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}}
+        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
     \end{subfigure}
@@
         \centering
-          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
+          \scalebox{0.85}{\input{AllFigures/02-extended-ferrenti-approach-v3.pgf}}
     \end{subfigure}
@@
         \centering
-          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/03-empirical-approach-v3.pgf}}
+          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{AllFigures/01-ferrenti-approach.pdf}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{AllFigures/02-augmented-ferrenti-approach.pdf}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
+        \includegraphics[width=1\textwidth]{AllFigures/03-insightful-approach.pdf}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/01-ferrenti-approach-PC-v2.tex}
+        \input{AllFigures/01-ferrenti-approach-PC-v2.tex}
         \label{fig:01-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/01-ferrenti-approach-GB-v2.tex}
+        \input{AllFigures/01-ferrenti-approach-GB-v2.tex}
         \label{fig:01-fi-d}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/03-empirical-approach-PC-v2.tex}
+        \input{AllFigures/03-empirical-approach-PC-v2.tex}
         \label{fig:03-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/03-empirical-approach-GB-v2.tex}
+        \input{AllFigures/03-empirical-approach-GB-v2.tex}
         \label{fig:03-fi-d}
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{figures/vesta-images/fig6-all.png}
+    \includegraphics[width=0.85\textwidth]{AllFigures/fig6-all.png}
     \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to.
@@
     \centering
-    \input{figures/histograms/new/LegendHistPaper.tex}
+    \input{AllFigures/LegendHistPaper.tex}
   \end{subfigure}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/MP_Eg_count_075.tex}
+    \input{AllFigures/MP_Eg_count_075.tex}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/IonProperty_max ionic char_count_075.tex}
+% This file was created with tikzplotlib v0.9.16.
+\begin{tikzpicture}
+
+\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
+\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
+\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
+\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}
+
+\begin{axis}[
+height=2.275590092707901in,
+legend cell align={left},
+legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
+tick align=outside,
+tick pos=left,
+title={},
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xlabel={Max ionic character},
+xmin=-0.0460725199741125, xmax=0.967522919456363,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ylabel={},
+ymin=0, ymax=1099.35,
+ytick style={color=black}
+]
+\path [draw=color0, very thick]
+(axis cs:0,0)
+--(axis cs:0,84)
+--(axis cs:0.0484973894464342,84)
+--(axis cs:0.0484973894464342,70)
+--(axis cs:0.0969947788928685,70)
+--(axis cs:0.0969947788928685,72)
+--(axis cs:0.145492168339303,72)
+--(axis cs:0.145492168339303,74)
+--(axis cs:0.193989557785737,74)
+--(axis cs:0.193989557785737,134)
+--(axis cs:0.242486947232171,134)
+--(axis cs:0.242486947232171,93)
+--(axis cs:0.290984336678605,93)
+--(axis cs:0.290984336678605,237)
+--(axis cs:0.33948172612504,237)
+--(axis cs:0.33948172612504,195)
+--(axis cs:0.387979115571474,195)
+--(axis cs:0.387979115571474,183)
+--(axis cs:0.436476505017908,183)
+--(axis cs:0.436476505017908,240)
+--(axis cs:0.484973894464342,240)
+--(axis cs:0.484973894464342,164)
+--(axis cs:0.533471283910777,164)
+--(axis cs:0.533471283910777,464)
+--(axis cs:0.581968673357211,464)
+--(axis cs:0.581968673357211,190)
+--(axis cs:0.630466062803645,190)
+--(axis cs:0.630466062803645,176)
+--(axis cs:0.678963452250079,176)
+--(axis cs:0.678963452250079,314)
+--(axis cs:0.727460841696513,314)
+--(axis cs:0.727460841696513,387)
+--(axis cs:0.775958231142948,387)
+--(axis cs:0.775958231142948,1047)
+--(axis cs:0.824455620589382,1047)
+--(axis cs:0.824455620589382,144)
+--(axis cs:0.872953010035816,144)
+--(axis cs:0.872953010035816,257)
+--(axis cs:0.92145039948225,257)
+--(axis cs:0.92145039948225,0);
+
+\path [draw=color1, very thick]
+(axis cs:0,0)
+--(axis cs:0,21)
+--(axis cs:0.0484973894464342,21)
+--(axis cs:0.0484973894464342,30)
+--(axis cs:0.0969947788928685,30)
+--(axis cs:0.0969947788928685,26)
+--(axis cs:0.145492168339303,26)
+--(axis cs:0.145492168339303,26)
+--(axis cs:0.193989557785737,26)
+--(axis cs:0.193989557785737,59)
+--(axis cs:0.242486947232171,59)
+--(axis cs:0.242486947232171,31)
+--(axis cs:0.290984336678605,31)
+--(axis cs:0.290984336678605,88)
+--(axis cs:0.33948172612504,88)
+--(axis cs:0.33948172612504,77)
+--(axis cs:0.387979115571474,77)
+--(axis cs:0.387979115571474,87)
+--(axis cs:0.436476505017908,87)
+--(axis cs:0.436476505017908,85)
+--(axis cs:0.484973894464342,85)
+--(axis cs:0.484973894464342,67)
+--(axis cs:0.533471283910777,67)
+--(axis cs:0.533471283910777,166)
+--(axis cs:0.581968673357211,166)
+--(axis cs:0.581968673357211,67)
+--(axis cs:0.630466062803645,67)
+--(axis cs:0.630466062803645,77)
+--(axis cs:0.678963452250079,77)
+--(axis cs:0.678963452250079,105)
+--(axis cs:0.727460841696513,105)
+--(axis cs:0.727460841696513,137)
+--(axis cs:0.775958231142948,137)
+--(axis cs:0.775958231142948,406)
+--(axis cs:0.824455620589382,406)
+--(axis cs:0.824455620589382,57)
+--(axis cs:0.872953010035816,57)
+--(axis cs:0.872953010035816,117)
+--(axis cs:0.92145039948225,117)
+--(axis cs:0.92145039948225,0);
+
+\end{axis}
+
+\begin{axis}[
+axis y line=right,
+height=2.275590092707901in,
+tick align=outside,
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xmin=-0.0460725199741125, xmax=0.967522919456363,
+xtick pos=left,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ymin=0, ymax=17.85,
+ytick pos=right,
+ytick style={color=color2},
+yticklabel style={anchor=west, color=color2}
+]
+\path [draw=color3, very thick]
+(axis cs:0,0)
+--(axis cs:0,1)
+--(axis cs:0.0484973894464342,1)
+--(axis cs:0.0484973894464342,2)
+--(axis cs:0.0969947788928685,2)
+--(axis cs:0.0969947788928685,0)
+--(axis cs:0.145492168339303,0)
+--(axis cs:0.145492168339303,0)
+--(axis cs:0.193989557785737,0)
+--(axis cs:0.193989557785737,2)
+--(axis cs:0.242486947232171,2)
+--(axis cs:0.242486947232171,1)
+--(axis cs:0.290984336678605,1)
+--(axis cs:0.290984336678605,4)
+--(axis cs:0.33948172612504,4)
+--(axis cs:0.33948172612504,6)
+--(axis cs:0.387979115571474,6)
+--(axis cs:0.387979115571474,3)
+--(axis cs:0.436476505017908,3)
+--(axis cs:0.436476505017908,1)
+--(axis cs:0.484973894464342,1)
+--(axis cs:0.484973894464342,0)
+--(axis cs:0.533471283910777,0)
+--(axis cs:0.533471283910777,4)
+--(axis cs:0.581968673357211,4)
+--(axis cs:0.581968673357211,3)
+--(axis cs:0.630466062803645,3)
+--(axis cs:0.630466062803645,5)
+--(axis cs:0.678963452250079,5)
+--(axis cs:0.678963452250079,4)
+--(axis cs:0.727460841696513,4)
+--(axis cs:0.727460841696513,4)
+--(axis cs:0.775958231142948,4)
+--(axis cs:0.775958231142948,17)
+--(axis cs:0.824455620589382,17)
+--(axis cs:0.824455620589382,2)
+--(axis cs:0.872953010035816,2)
+--(axis cs:0.872953010035816,10)
+--(axis cs:0.92145039948225,10)
+--(axis cs:0.92145039948225,0);
+\end{axis}
+
+\end{tikzpicture}
+
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
+% This file was created with tikzplotlib v0.9.16.
+\begin{tikzpicture}
+
+\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
+\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
+\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
+\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}
+
+\begin{axis}[
+height=2.275590092707901in,
+legend cell align={left},
+legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
+tick align=outside,
+tick pos=left,
+title={},
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xlabel={Std. dev. RDF},
+xmin=-0.00174896633573773, xmax=0.0367282930504924,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ylabel={Number of materials},
+ymin=0, ymax=413.2,
+ytick style={color=black}
+]
+\path [draw=color0, very thick]
+(axis cs:0,0)
+--(axis cs:0,331)
+--(axis cs:0.0018410171955134,331)
+--(axis cs:0.0018410171955134,291)
+--(axis cs:0.00368203439102681,291)
+--(axis cs:0.00368203439102681,279)
+--(axis cs:0.00552305158654021,279)
+--(axis cs:0.00552305158654021,259)
+--(axis cs:0.00736406878205362,259)
+--(axis cs:0.00736406878205362,231)
+--(axis cs:0.00920508597756702,231)
+--(axis cs:0.00920508597756702,234)
+--(axis cs:0.0110461031730804,234)
+--(axis cs:0.0110461031730804,348)
+--(axis cs:0.0128871203685938,348)
+--(axis cs:0.0128871203685938,355)
+--(axis cs:0.0147281375641072,355)
+--(axis cs:0.0147281375641072,356)
+--(axis cs:0.0165691547596206,356)
+--(axis cs:0.0165691547596206,384)
+--(axis cs:0.018410171955134,384)
+--(axis cs:0.018410171955134,374)
+--(axis cs:0.0202511891506474,374)
+--(axis cs:0.0202511891506474,310)
+--(axis cs:0.0220922063461609,310)
+--(axis cs:0.0220922063461609,255)
+--(axis cs:0.0239332235416743,255)
+--(axis cs:0.0239332235416743,178)
+--(axis cs:0.0257742407371877,178)
+--(axis cs:0.0257742407371877,105)
+--(axis cs:0.0276152579327011,105)
+--(axis cs:0.0276152579327011,68)
+--(axis cs:0.0294562751282145,68)
+--(axis cs:0.0294562751282145,45)
+--(axis cs:0.0312972923237279,45)
+--(axis cs:0.0312972923237279,28)
+--(axis cs:0.0331383095192413,28)
+--(axis cs:0.0331383095192413,23)
+--(axis cs:0.0349793267147547,23)
+--(axis cs:0.0349793267147547,0);
+
+\path [draw=color1, very thick]
+(axis cs:0,0)
+--(axis cs:0,135)
+--(axis cs:0.0018410171955134,135)
+--(axis cs:0.0018410171955134,112)
+--(axis cs:0.00368203439102681,112)
+--(axis cs:0.00368203439102681,101)
+--(axis cs:0.00552305158654021,101)
+--(axis cs:0.00552305158654021,105)
+--(axis cs:0.00736406878205362,105)
+--(axis cs:0.00736406878205362,94)
+--(axis cs:0.00920508597756702,94)
+--(axis cs:0.00920508597756702,117)
+--(axis cs:0.0110461031730804,117)
+--(axis cs:0.0110461031730804,121)
+--(axis cs:0.0128871203685938,121)
+--(axis cs:0.0128871203685938,152)
+--(axis cs:0.0147281375641072,152)
+--(axis cs:0.0147281375641072,147)
+--(axis cs:0.0165691547596206,147)
+--(axis cs:0.0165691547596206,151)
+--(axis cs:0.018410171955134,151)
+--(axis cs:0.018410171955134,131)
+--(axis cs:0.0202511891506474,131)
+--(axis cs:0.0202511891506474,120)
+--(axis cs:0.0220922063461609,120)
+--(axis cs:0.0220922063461609,85)
+--(axis cs:0.0239332235416743,85)
+--(axis cs:0.0239332235416743,61)
+--(axis cs:0.0257742407371877,61)
+--(axis cs:0.0257742407371877,31)
+--(axis cs:0.0276152579327011,31)
+--(axis cs:0.0276152579327011,22)
+--(axis cs:0.0294562751282145,22)
+--(axis cs:0.0294562751282145,15)
+--(axis cs:0.0312972923237279,15)
+--(axis cs:0.0312972923237279,6)
+--(axis cs:0.0331383095192413,6)
+--(axis cs:0.0331383095192413,8)
+--(axis cs:0.0349793267147547,8)
+--(axis cs:0.0349793267147547,0);
+\end{axis}
+
+\begin{axis}[
+axis y line=right,
+height=2.275590092707901in,
+tick align=outside,
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xmin=-0.00174896633573773, xmax=0.0367282930504924,
+xtick pos=left,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ymin=0, ymax=13.65,
+ytick pos=right,
+ytick style={color=color2},
+yticklabel style={anchor=west, color=color2}
+]
+\path [draw=color3, very thick]
+(axis cs:0,0)
+--(axis cs:0,6)
+--(axis cs:0.0018410171955134,6)
+--(axis cs:0.0018410171955134,3)
+--(axis cs:0.00368203439102681,3)
+--(axis cs:0.00368203439102681,5)
+--(axis cs:0.00552305158654021,5)
+--(axis cs:0.00552305158654021,3)
+--(axis cs:0.00736406878205362,3)
+--(axis cs:0.00736406878205362,2)
+--(axis cs:0.00920508597756702,2)
+--(axis cs:0.00920508597756702,2)
+--(axis cs:0.0110461031730804,2)
+--(axis cs:0.0110461031730804,6)
+--(axis cs:0.0128871203685938,6)
+--(axis cs:0.0128871203685938,4)
+--(axis cs:0.0147281375641072,4)
+--(axis cs:0.0147281375641072,5)
+--(axis cs:0.0165691547596206,5)
+--(axis cs:0.0165691547596206,13)
+--(axis cs:0.018410171955134,13)
+--(axis cs:0.018410171955134,4)
+--(axis cs:0.0202511891506474,4)
+--(axis cs:0.0202511891506474,6)
+--(axis cs:0.0220922063461609,6)
+--(axis cs:0.0220922063461609,5)
+--(axis cs:0.0239332235416743,5)
+--(axis cs:0.0239332235416743,1)
+--(axis cs:0.0257742407371877,1)
+--(axis cs:0.0257742407371877,1)
+--(axis cs:0.0276152579327011,1)
+--(axis cs:0.0276152579327011,2)
+--(axis cs:0.0294562751282145,2)
+--(axis cs:0.0294562751282145,0)
+--(axis cs:0.0312972923237279,0)
+--(axis cs:0.0312972923237279,0)
+--(axis cs:0.0331383095192413,0)
+--(axis cs:0.0331383095192413,1)
+--(axis cs:0.0349793267147547,1)
+--(axis cs:0.0349793267147547,0);
+\end{axis}
+
+\end{tikzpicture}
+
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.tex}
+% This file was created with tikzplotlib v0.9.16.
+\begin{tikzpicture}
+
+\definecolor{color0}{rgb}{0.866666666666667,0.8,0.466666666666667}
+\definecolor{color1}{rgb}{0.533333333333333,0.8,0.933333333333333}
+\definecolor{color2}{rgb}{0.83921568627451,0.152941176470588,0.156862745098039}
+\definecolor{color3}{rgb}{0.8,0.4,0.466666666666667}
+
+\begin{axis}[
+height=2.275590092707901in,
+legend cell align={left},
+legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
+tick align=outside,
+tick pos=left,
+title={},
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xlabel={Std. dev. average bond length},
+xmin=-0.0263144046185111, xmax=0.838491250528538,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ylabel={},
+ymin=0, ymax=732.9,
+ytick style={color=black}
+]
+\path [draw=color0, very thick]
+(axis cs:0.0129949433427184,0)
+--(axis cs:0.0129949433427184,28)
+--(axis cs:0.0543732043545389,28)
+--(axis cs:0.0543732043545389,65)
+--(axis cs:0.0957514653663595,65)
+--(axis cs:0.0957514653663595,156)
+--(axis cs:0.13712972637818,156)
+--(axis cs:0.13712972637818,279)
+--(axis cs:0.178507987390001,279)
+--(axis cs:0.178507987390001,403)
+--(axis cs:0.219886248401821,403)
+--(axis cs:0.219886248401821,468)
+--(axis cs:0.261264509413642,468)
+--(axis cs:0.261264509413642,590)
+--(axis cs:0.302642770425462,590)
+--(axis cs:0.302642770425462,698)
+--(axis cs:0.344021031437283,698)
+--(axis cs:0.344021031437283,563)
+--(axis cs:0.385399292449103,563)
+--(axis cs:0.385399292449103,445)
+--(axis cs:0.426777553460924,445)
+--(axis cs:0.426777553460924,340)
+--(axis cs:0.468155814472744,340)
+--(axis cs:0.468155814472744,193)
+--(axis cs:0.509534075484565,193)
+--(axis cs:0.509534075484565,118)
+--(axis cs:0.550912336496385,118)
+--(axis cs:0.550912336496385,52)
+--(axis cs:0.592290597508206,52)
+--(axis cs:0.592290597508206,31)
+--(axis cs:0.633668858520026,31)
+--(axis cs:0.633668858520026,18)
+--(axis cs:0.675047119531847,18)
+--(axis cs:0.675047119531847,11)
+--(axis cs:0.716425380543667,11)
+--(axis cs:0.716425380543667,6)
+--(axis cs:0.757803641555488,6)
+--(axis cs:0.757803641555488,2)
+--(axis cs:0.799181902567308,2)
+--(axis cs:0.799181902567308,0);
+
+\path [draw=color1, very thick]
+(axis cs:0.0129949433427184,0)
+--(axis cs:0.0129949433427184,13)
+--(axis cs:0.0543732043545389,13)
+--(axis cs:0.0543732043545389,36)
+--(axis cs:0.0957514653663595,36)
+--(axis cs:0.0957514653663595,68)
+--(axis cs:0.13712972637818,68)
+--(axis cs:0.13712972637818,111)
+--(axis cs:0.178507987390001,111)
+--(axis cs:0.178507987390001,166)
+--(axis cs:0.219886248401821,166)
+--(axis cs:0.219886248401821,190)
+--(axis cs:0.261264509413642,190)
+--(axis cs:0.261264509413642,243)
+--(axis cs:0.302642770425462,243)
+--(axis cs:0.302642770425462,257)
+--(axis cs:0.344021031437283,257)
+--(axis cs:0.344021031437283,205)
+--(axis cs:0.385399292449103,205)
+--(axis cs:0.385399292449103,143)
+--(axis cs:0.426777553460924,143)
+--(axis cs:0.426777553460924,119)
+--(axis cs:0.468155814472744,119)
+--(axis cs:0.468155814472744,70)
+--(axis cs:0.509534075484565,70)
+--(axis cs:0.509534075484565,29)
+--(axis cs:0.550912336496385,29)
+--(axis cs:0.550912336496385,16)
+--(axis cs:0.592290597508206,16)
+--(axis cs:0.592290597508206,20)
+--(axis cs:0.633668858520026,20)
+--(axis cs:0.633668858520026,7)
+--(axis cs:0.675047119531847,7)
+--(axis cs:0.675047119531847,4)
+--(axis cs:0.716425380543667,4)
+--(axis cs:0.716425380543667,3)
+--(axis cs:0.757803641555488,3)
+--(axis cs:0.757803641555488,0)
+--(axis cs:0.799181902567308,0)
+--(axis cs:0.799181902567308,0);
+
+\end{axis}
+
+\begin{axis}[
+axis y line=right,
+height=2.275590092707901in,
+tick align=outside,
+width=2.8444876158848764in,
+x grid style={white!69.0196078431373!black},
+xmin=-0.0263144046185111, xmax=0.838491250528538,
+xtick pos=left,
+xtick style={color=black},
+y grid style={white!69.0196078431373!black},
+ymin=0, ymax=12.6,
+ytick pos=right,
+ytick style={color=color2},
+yticklabel style={anchor=west, color=color2}
+]
+\path [draw=color3, very thick]
+(axis cs:0.0129949433427184,0)
+--(axis cs:0.0129949433427184,2)
+--(axis cs:0.0543732043545389,2)
+--(axis cs:0.0543732043545389,3)
+--(axis cs:0.0957514653663595,3)
+--(axis cs:0.0957514653663595,1)
+--(axis cs:0.13712972637818,1)
+--(axis cs:0.13712972637818,5)
+--(axis cs:0.178507987390001,5)
+--(axis cs:0.178507987390001,6)
+--(axis cs:0.219886248401821,6)
+--(axis cs:0.219886248401821,10)
+--(axis cs:0.261264509413642,10)
+--(axis cs:0.261264509413642,7)
+--(axis cs:0.302642770425462,7)
+--(axis cs:0.302642770425462,12)
+--(axis cs:0.344021031437283,12)
+--(axis cs:0.344021031437283,7)
+--(axis cs:0.385399292449103,7)
+--(axis cs:0.385399292449103,7)
+--(axis cs:0.426777553460924,7)
+--(axis cs:0.426777553460924,4)
+--(axis cs:0.468155814472744,4)
+--(axis cs:0.468155814472744,4)
+--(axis cs:0.509534075484565,4)
+--(axis cs:0.509534075484565,0)
+--(axis cs:0.550912336496385,0)
+--(axis cs:0.550912336496385,1)
+--(axis cs:0.592290597508206,1)
+--(axis cs:0.592290597508206,0)
+--(axis cs:0.633668858520026,0)
+--(axis cs:0.633668858520026,0)
+--(axis cs:0.675047119531847,0)
+--(axis cs:0.675047119531847,0)
+--(axis cs:0.716425380543667,0)
+--(axis cs:0.716425380543667,0)
+--(axis cs:0.757803641555488,0)
+--(axis cs:0.757803641555488,0)
+--(axis cs:0.799181902567308,0)
+--(axis cs:0.799181902567308,0);
+\end{axis}
+
+\end{tikzpicture}
+
     \subcaption{}
@@
 Correspondence and requests for materials should be addressed to \url{bathen@aps.ee.ethz.ch}.
+Supplementary material is available at \url{https://github.com/mhjensen/PredictingSolidStateQubitCandidates}.
 

### 2022-05-28 response-letter/response-letter.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% LaTeX Template
% Version 2.0 (12/2/17)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{letter} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)

\input{structure.tex} % Include the file that specifies the document structure

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," and date to the left of the page

%----------------------------------------------------------------------------------------
%	YOUR INFORMATION
%----------------------------------------------------------------------------------------

\Who{Prof. Morten Hjorth-Jensen} % Your name

\Title{, PhD} % Your title, leave blank for no title

\authordetails{
	Department of Physics\\ % Your department/institution
	P.O. Box 1048, Blindern\\ % Your address
	N-0316 Oslo, Norway\\ % Your city, zip code, country, etc
	Email: morten.hjorth-jensen@fys.uio.no\\ % Your email address
	Phone: (000) 111-1111\\ % Your phone number
	URL: LaTeXTemplates.com % Your URL
}

%----------------------------------------------------------------------------------------
%	HEADER CONTENTS
%----------------------------------------------------------------------------------------

\logo{UiO_logo.png} % Logo filename, your logo should have square dimensions (i.e. roughly the same width and height), if it does not, you will need to adjust spacing within the HEADER STRUCTURE block in structure.tex (read the comments carefully!)

\headerlineone{UNIVERSITY} % Top header line, leave blank if you only want the bottom line

\headerlinetwo{OF OSLO} % Bottom header line

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

\begin{letter}{
	Dr. Long-Qing Chen\\
	Editor-in-Chief\\
	\textit{npj Computational Materials} \\ 
	npjcompumats@nature.com \\ 
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{}

\begin{center}
   \textbf{Resubmission of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by O.L. Hebnes, et al.}
\end{center}

\noindent
Dear Editor,

Please find enclosed a revised version of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by Oliver L. Hebnes, et al., submitted for publication as an original article in npj Computational Materials. There are two files in all: a Manuscript file and a Supplementary Information file.

Please find detailed responses to reviewer comments below.

\closing{Sincerely,}

%----------------------------------------------------------------------------------------
%	OPTIONAL FOOTNOTE
%----------------------------------------------------------------------------------------

% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}

%----------------------------------------------------------------------------------------

\end{letter}

\newpage

\noindent
\textbf{Associate Editor:}

The main revision I would like to see addressed is the first point of the second reviewer: What is the utility of the machine learning model if it returns the original classification? The other points they bring up around methodological clarity are important, but providing further justification around the need for the use of machine learning would help reinforce the principle of your study.

\textit{Response: }
\begin{itemize}
    \item	Compare empirical to known input. Ferrenti reproduces expectations of literature. Main point is compare that to empirical which gives different result. 
    \item Actually, don’t get exactly what we expect from Ferrenti. Den vektlegger det vi forventer, men returnerer ikke eksakt kriteriene. E.g. band gap, ionic character. 
    \item Wnated to see if ML sees something else than the criteria we introduced. How does this compare to empirical? 
    \item It is a nice start to begin with some general criteria. However, as pointed out, the usefulness is limited. The point is that we actually demonstrate that the Ferrenti approaches are not the best way. 
    \item In some cases it might be useful to impose causality, to see to what extent that works. When we see that it does not work, we let the ML models figure out the connections between materials and QT. We had several hypotheses for why these materials are QT compatible, and therefore forced the causality to verify the assumption. When it did not work, we instead started from no assumptions, and let the ML methods reason out the causality. This proved much more efficient. 
    \item Empirical is main result, Ferrenti is kind of test/validation/benchmark. Highlight more. 
    \item Database of Ferrenti is commonly used, this is benchmark set of materials and information. Compare our method to benchmark. 
    \item We agree; Ferrenti not really useful 
    \item Ferrenti paper is data mining, not ML. We put it in to compare data 
\end{itemize}

\noindent
\textbf{Reviewer \#1: }

In this work, the authors obtained machine learning models (logistic regression, decision trees, random forest, gradient boosting) to predict materials that may be suitable candidates as solid-state semiconductor hosts for quantum emitters and spin centers. The authors used three approaches, one from the literature, one modified from the literature, and one empirical, to label the data. The authors have done thorough analysis on the predicted materials from each method. The article is well-written. The methods used have been described well and the errors from machine learning models have been characterized well. The authors have also made their data and code available through Zenodo. What is lacking is means to prove that at least some of the predicted materials are indeed good candidates. This is understandable as an extensive study would be needed to achieve this. I recommend publication.

\textit{Response: }

\textit{We thank the reviewer for the careful reading of our manuscript and the positive evaluation. We agree that the proof of our findings is a crucial next step for this line of work. However, as pointed out, this requires time-consuming experimental work including material growth, defect creation and advanced characterization, and is outside of the scope of the present work. A follow up project has been started to grow crystalline thin films and investigate the potential presence of quantum compatible defect candidates in selected materials from the list of predictions. }

\noindent
\textbf{Reviewer \#2: }

Reviewer \#2: \\
This work uses a combination of data-mining and machine-learning to search for materials that are suitable for applications in “quantum technologies”, such as quantum computing, cryptography, and sensors. Three different search strategies, named Ferrenti, extended Ferrenti (both based on finding materials with specific properties such as non-magnetic, a minimum band gap, etc.) and empirical (based on searching for materials already used in quantum technologies), were used to search for potential materials in a set of online computational materials databases. The extracted data were then used to train machine-learning models to identify potential materials for quantum technologies applications. However, there are several details in the methodology that are unclear, and as well as other issues regarding the meaningfulness of the results that need to be addressed before the article can be considered for publication.

\textit{Response:}

\textit{We thank the reviewer for the careful reading of our manuscript and the detailed feedback. The reviewer raises several critical points that could have been explained more clearly in the original version of the manuscript. We have attempted to address all concerns raised by the reviewer, and believe that the revised version of the manuscript contains answers that satisfy the reviewer’s concerns. }

Reviewer \#2: \\
In particular, in the Ferrenti and extended Ferrenti searches, the authors define a set of properties of the materials and their component elements that are used to classify materials as either suitable or unsuitable for quantum technologies. They then train machine-learning models based on this classification to classify the same set of materials as suitable or unsuitable. It is unclear to me why this is useful: the machine-learning model will ultimately simply relearn the original classification criteria – the reason that this does not happen explicitly in this case is due to the use of principle component analysis to perform the feature reduction, which combines the training features and thus obscures the relationship between the final model results and the initial classification criteria. It is unclear if there are properties included in the search that are not included in the model training data, where the model could potentially be useful in identifying materials
where certain desired properties are currently unknown. Therefore, the meaningfulness and usefulness of training machine-learning models on a data set constructed in this way is not clear.

\textit{Response:}

\textit{Here ... }

Reviewer \#2: \\
In the machine-learning models trained on the extended Ferrenti approach, the authors note that the models predict unsuitable materials to be suitable, e.g. NaCl. How were these materials categorized by the original extended Ferrenti criteria? It is not necessarily clear that the Ferrenti/extended Ferrenti criteria listed on pages 5 and 6 of this work would reliably categorize ionic materials with cubic symmetry as unsuitable, so it is unsurprising that machine-learning models trained on such data would have these problems.

\textit{Response:} 
% OH: Jeg synes han svarer egentlig på sitt eget spørsmål her. For at et materiale skal bli "predikert" som en god kandidat av maskinlærings-algoritmene, så kan ikke materialet være en del av treningssettet som ML algoritmene blir trent på, ergo så er ikke materiale kategorisert som hverken bra eller dårlig av the original extended ferrenti criteria. Det betyr at materialet er utelukket av the extended ferrenti criteria, altså at den oppfyller ikke kravene for hverken en god eller dårlig kandidat basert på data miningen.
\textit{The material NaCl involves two elements where more than half does not have a natural abundance of spin zero isotopes, and is therefore excluded from being labeled as suitable. In addition, NaCl is excluded from being labeled as unsuitable from the criteria due to its nonmagnetic label in Materials Project. We agree that it is not neccessarily clear that either Ferrenti or extended Ferrenti critera would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process that constitutes the criteria in the data mining. Therefore, NaCl is found unlabeled in the test data, and is predicted as an unsuitable candidate by the ML algorithms.}

\textit{Argument for Ferrenti}

Reviewer \#2: \\
In the Ferrenti and extended Ferrenti searches, the authors also state that they only include materials that have been calculated to be “non-magnetic”. However, it is unclear how this criterion would be implemented in practice: while ferromagnetic materials are usually easy enough to identify, other types of magnetic order such as antiferromagnetism can be more difficult. Many of the automated calculations inside these databases are based on the primitive cell, which might not be large enough to be able to properly represent the antiferromagnetic configuration. Therefore, the authors should clearly define their criteria for determining if a material is non-magnetic, e.g. including checks to see if larger cells have been explored.

\textit{Response:}

\textit{The data regarding a material's magnetic character is extracted from Materials Projects database. Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project perform an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure. As a result, we can find Fe (https://materialsproject.org/materials/mp-13/) labeled as ferromagnetic and NiO (https://materialsproject.org/materials/mp-19009/) as antiferromagnetic in our data .}

\textit{Additionally, Materials Project also include larger structures of the same material. We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.}

\textit{Marianne; The reviewer raises an important issue. As noted, we are in fact mainly probing ferromagnetic ordering in our criteria. This was not sufficiently clear in the original manuscript but has been remedied in the revised version, see the following sentence on page …: 
Exploring larger cells was not done as the links between small and large cells of the same material in MP is not always clear. Therefore, this is an improvement that could be made to our method in a further work. This aspect has now been highlighted in the manuscript on page … 
}

Reviewer \#2: \\
In the empirical approach, the data set is constructed based on the materials that are currently used in quantum technologies. The authors should discuss if there is any intrinsic bias in this data set, e.g. that these materials are selected based on what are readily available to researchers in this field, rather than the materials that are inherently the most suitable.

\textit{Response:}
\textit{We agree with the Reviewer. Availability of affordable and high quality crystals has of course limited the search for quantum compatible defects and solid state effects in semiconductors. Moreover, it is likely that the discovery of single photon emission and spin manipulation for the NV center in diamond has also guided the search for similar properties in other materials, with the search commencing with similar materials to diamond, such as different polytypes of SiC. The criteria of Weber et al are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable. The recent discovery of telecom compatible SPEs in Si, a lower band gap material, show that this may have been a preemptory assumption. We hope that our work can contribute to widening the search for quantum compatible semiconductor platforms. 
A note to this effect has now been added to page …:  
}

Reviewer \#2: \\
The authors use the Materials Project as their primary database to search for ICSD entries. They then search for similar entries in other databases (OQMD, JARVIS-DFT, Citrination, etc.), and combine the data. However, it is unclear what additional data they are extracting from the other databases. How do they identify/define similar materials – are they based on the same ICSD number, on comparing the structures, etc.? If two different databases have different values for the same property, e.g. two different values of the band gap (perhaps due to different U parameters being used), how do they decide which value to use?

\textit{Response:}

\textit{From the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project. This ID is present in AFLOW, AFLOW-ML, JARVIS-DFT and OQMD, and we performed an additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97\%$.}

\textit{For the experimental values from Citrine, we could only verify the chemical formula since the data is lacking structures.}

Reviewer \#2: \\
Other minor issues include the following:

\begin{enumerate}
    \item On page 12, what do the authors mean by “unfortunate structures”? 
    \item The authors use the “.” as the notation to represent both the decimal point and the separator for thousands in large numbers (e.g. writing twenty-five thousand as “25.000”). Generally in English-language publications, “,” is used to separate thousands. \\ 
    \textit{Response}: \\
    \textit{Thank you for pointing out this oversight. This has now been remedied according to the referee's suggestion. } 
    \item The authors should note that AFLOW also uses PBE+U in some calculations as described in Ref. 24 of this work, particularly for materials taken from the ICSD. 
    \item Finally, the article also contains a lot of repetition, making it unnecessarily long. For example, the “Comparing the approaches” subsection on pages 14 and 15 is mainly just repeating the results from the previous subsections - lot of this could be cut, with the remainder incorporated into the Discussion section. 
\end{enumerate}

\end{document}

### 2022-05-28 revision/revised-paper_marked-up.tex

--- 2022-03-28 paper_v3_cut.tex
@@
 
-%\newcommand\abs[1]{\left|#1\right|}
-%\newcommand\bra[1]{\left| #1 \right \rangle}
-%\newcommand\ket[1]{\left \langle #1 \right |}
-
-\newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
-\newcommand{\morten}[1]{\textcolor{green}{#1}}
-\newcommand{\sebastian}[1]{\textcolor{cyan}{#1}}
-\newcommand{\marianne}[1]{\textcolor{blue}{#1}}
-\newcommand{\oyvind}[1]{\textcolor{maroon}{#1}}
-\newcommand{\lasse}[1]{\textcolor{red}{#1}}
+\newcommand{\mrk}[1]{\textcolor{red}{#1}}
 
@@
 is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physics-informed features.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \mrk{$25,000$} materials and nearly $5000$ physics-informed features.
 Three approaches were devised, named the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
@@
 Recent advances have highlighted the potential of quantum information processors to outperform state-of-the art high-performance computing facilities.
-Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
+Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \mrk{$200,000$} core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
@@
 \subsection*{Data Mining}
-The complete dataset consists of $25.000$ materials.
+The complete dataset consists of \mrk{$25,000$} materials.
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
@@
 This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
-Below we follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
+Below we \mrk{follow separate} procedures for labeling materials as suitable or unsuitable candidates for QT.
 
@@
 \subsubsection*{The extended Ferrenti approach}
-Here, we adjust the Ferrenti approach to expand the data labeling process beyond practical  considerations.
+\mrk{The Ferrenti approach was adjusted} to expand the data labeling process beyond practical  considerations.
 The second approach is therefore named \emph{the extended Ferrenti approach} and involves removing stage two from the approach above.
@@
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
+For \textbf{unsuitable} candidates, \mrk{the same strategy as for the first Ferrenti approach was implemented}.
 The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
 However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
+
+\mrk{The findings from both the data mining and machine learning procedures for the extended Ferrenti approach did not differ substantially from those obtained using the Ferrenti approach.
+This is attributed to the similarities in the selection processes.
+Therefore, detailed discussion on the findings from the extended Ferrenti approach can be found in the Supplementary Material at \cite{supplementary}.
+Qualitative conclusions drawn for the Ferrenti approach herein also hold for the extended Ferrenti approach, indicating that the removal of so-called practical considerations did not have a significant impact on the results.
+}
 
@@
 
-\begin{table}[b]
+\begin{table}[t]
     \centering 
@@
 These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than $0.5$~eV.
-We include all of the $202$ structures apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
+\mrk{All of the $202$ structures are included apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
+}
 
 Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
-For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
-Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$~eV) among the data.
-We add these as suitable candidates.
+For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project \mrk{were admitted.} Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$~eV) among the data.
+\mrk{These were added} as suitable candidates.
 Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies.
 For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
-Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, we only admit two-dimensional structures.
+Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, \mrk{only two-dimensional structures were admitted}.
 For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML methods that are applied in a later stage.
@@
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-We note that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of $0.5$~eV.
+\mrk{Note} that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of $0.5$~eV.
 
@@
 \subsubsection*{Comparing the approaches}
-The three different approaches to data mining place a particular emphasis on each of their specific goals.
+%The three different approaches to data mining place a particular emphasis on each of their specific goals.
 The Ferrenti approach relies on choosing only elements with spin zero isotopes and compounds that crystallize in nonpolar spacegroups together with practical filters, while the extended Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
@@
 %Ferrenti 
-Considering the materials present in the labeled datasets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}).
+\mrk{Considering the materials present in the labeled datasets of the Ferrenti approach more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate}, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}).
 Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
@@
 Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.  
-%Extended Ferrenti 
-In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+%Extended Ferrenti - moved 
+%In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
 The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the labeled data.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), there is a more sparse representation of each known chemical formula present in the labeled data.
 
-The labeled data for each approach is visualized in Fig.~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+\mrk{The labeled data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
         \centering
-          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
           \scalebox{0.85}{\input{figures/parallel-coordinates-plots/03-empirical-approach-v3.pgf}}
     \end{subfigure}
-    \caption{Parallel coordinate plots for the different approaches.
+    \caption{Parallel coordinate plots for the two different approaches.
 To limit data cluttering, we have randomly collected up to $250$ entries for each class.
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
-    \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \centering
         \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
     \end{subfigure}
-    \caption{Two-dimensional scatter plots for the three different approaches.
+    \caption{Two-dimensional scatter plots for the two different approaches.
 We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots.
-Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
+Then, we have transformed the sets of labeled data resulting from the two approaches and visualized them as scatter plots.
+Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the right panel, and red triangles represent unsuitable candidates.}
     \label{fig:2dscatterplotpca}
@@
 
-The Ferrenti approach and the extended Ferrenti approach share several similarities.
-For example, the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
-Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
+\mrk{The Ferrenti approach and the extended Ferrenti approach share several similarities with entries that span roughly the same dimensions (not shown).} 
+%For example, the entries in  Figure~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
+%Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
 The most striking difference is found for the empirical approach.
-Again, the entries labeled as suitable candidates do not exhibit any magnetization, but now the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti approaches.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
+\mrk{The entries labeled as suitable candidates do not exhibit any magnetization, which is also the case for the Ferrenti approach, but now the materials crystallize in both polar and non-polar space groups.} Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for \mrk{the former one.}
 Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-In the empirical approach the polarity of the material's space group may be less important compared to the Ferrenti based approaches, while the accepted values for ionic character and covalent range appear more restricted (Fig.~\ref{fig:parallel-coordinates-approaches}).
+In the empirical approach the polarity of the material's space group may be less important compared to the \mrk{Ferrenti approach}, while the accepted values for ionic character and covalent range appear more restricted (Fig.~\ref{fig:parallel-coordinates-approaches}).
 
-To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
-Here we apply PCA to the labeled datasets in order to reveal specific features that stand out.
-In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
+\mrk{To illustrate the composition of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.
+PCA was applied to the labeled datasets in order to reveal specific features that stand out.} In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
 We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the MP database, and transform the three labeled datasets according to the corresponding two eigenvectors.
@@
 Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of removing the mean and scaling to unit variance.
-Red triangles represent unsuitable candidates while colored symbols (green, blue, black and yellow) represent suitable candidates.
-Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the extended Ferrenti approaches are largely overlapping. 
-The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti and extended Ferrenti approaches.
-Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-We therefore expect that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
+Red triangles represent unsuitable candidates while \mrk{otherwise} colored symbols (green, blue, black and yellow) represent suitable candidates.
+Due to the complexity of reducing the large amount of features down to only two, suitable and unsuitable candidates for \mrk{the Ferrenti approach} are largely overlapping. 
+The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti \mrk{approach}.
+Hence, using \mrk{this approach} for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
+We therefore expect that the \mrk{Ferrenti approach} could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
 
@@
 \subsection*{Machine learning and principal component analysis}
-We have applied four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
+\mrk{Four well-tested ML algorithms were applied to the labeled data} to classify specific materials as candidate systems for QT.
 These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
@@
 In order to reduce the dimensionality while preserving most of the variance in the data, 
-we have performed a principal component analysis  \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+\mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
 First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
 Next, in the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Information \cite{supplementary}.
-The three data labeling approaches (Ferrenti, extended Ferrenti and empirical) define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
+\mrk{Note} that all four ML methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four \mrk{ML} methods are shown in the Supplementary Information \cite{supplementary}.
+The \mrk{data labeling approaches} define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
 For small datasets, it is proven to be beneficial to repeat the cross-validation analysis \cite{Hastie2009}, as this is a method that allows us to measure the stability of the predictions against perturbations (i.e., few different entries) in the training data \cite{Beleites2008}.
@@
 Figure~\ref{fig:PComponents} visualizes different parameters for the most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-This differs from Fig.~\ref{fig:2dscatterplotpca}, where we visualize the two most important eigenvectors for all approaches that originates from the same covariance matrix.
-Note also that in  Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
+This differs from Fig.~\ref{fig:2dscatterplotpca}, where \mrk{the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown}.
+Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all data}.
 Here, the ML analysis is done on the labeled data for each approach.
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components.
-In the case of the empirical approach and in contrast to the Ferrenti approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
+\mrk{In the case of the empirical approach and in contrast to the Ferrenti approach}, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
 Gradient boosting
@@
 %extended Ferrenti 
-The interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
+\mrk{Note that the} interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
-However, we find that random forests and gradient boosting both mark the fifth principal component as important.
+However, \mrk{random} forests and gradient boosting both mark the fifth principal component as important.
 Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
@@
 %empirical approach 
-The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
-Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
+The empirical approach differs in many aspects from the Ferrenti \mrk{approach}. 
+Firstly, \mrk{the} number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
 Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
@@
 The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
-Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
+Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach. 
+% and $11 \ \%$ for the extended Ferrenti approach. 
 We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
 
-Intriguingly, the principal components that are deemed important by the three approaches differ substantially.
-The Ferrenti and extended Ferrenti approaches place particular value on the material's band gap and the ionic or covalent character of the bonding.
+Intriguingly, the principal components that are deemed important by \mrk{the approaches differ substantially.
+The Ferrenti approach places}  particular value on the material's band gap and the ionic or covalent character of the bonding.
 Indeed, precisely these features were used as guidance in the data labeling process.
-Thus, the ML methods are preserving the criteria imposed in the Ferrenti approaches and perpetuate our initial assumptions on which material properties to look for.
-For the empirical approach, on the other hand, we did not guide the selection process in terms of specific properties.
-Here, the ML methods appear to be informed by other  characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+\mrk{Thus, the ML methods seem to be perpetuate the criteria imposed in the Ferrenti approach to some extent, and return the initial assumptions on which material properties may be important for QT.
+The ML methods may, however, still be recognizing other patterns than those originally intended in the data selection process.} \mrk{For the empirical approach, on the other hand, the selection process was not guided in terms of specific properties.} Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
 In the empirical approach, the ML methods appear to be inferring that the common trend among the materials that are known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
@@
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology} 
-After training the ML algorithms using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
+After training the ML algorithms using parts of the data labeled during the \mrk{data mining process}, the ML methods were employed on the test sets. 
 The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
@@
 We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with unfortunate structures to be labeled as suitable candidates.
+This can allow materials with \mrk{complex structures (e.g., nanostructures or 2D materials)} to be labeled as suitable candidates.
 Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than $0.5$~eV were eliminated.
-This trend is not carried over to the predicted data. Indeed, we find that many entries with band gaps lower than $0.5$~eV are predicted as suitable candidates by all four ML methods employed herein 
+This trend is not carried over to the predicted data. Indeed, \mrk{many} entries with band gaps lower than $0.5$~eV are predicted as suitable candidates by all four ML methods employed herein 
 %indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
 --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
+\mrk{This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.}
 On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
@@
 
-\subsubsection*{The extended Ferrenti approach}
-Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger 
-amount of labeled data than the Ferrenti approach.  
+%\subsubsection*{The extended Ferrenti approach}
+%Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger amount of labeled data than the Ferrenti approach.
 The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
@@
 All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
-%Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Furthermore, although we enforced a conservative band gap restriction of $1.5$~eV for the data labeling in the extended Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+%%Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
+%Furthermore, although we enforced a conservative band gap restriction of $1.5$~eV for the data labeling in the extended Ferrenti approach, we still find that all four implemented ML methods predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
 As seen above, the ML methods applied to data labeled in the Ferrenti and extended Ferrenti approach are recognizing the band gap and bonding character as important, but the resulting predicted materials do not strictly follow the anticipated guidelines.
@@
 \subsubsection*{The empirical approach}
-The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the other two approaches. 
+The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the \mrk{Ferrenti approach}. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
@@
 Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems while Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as reported in the MP database.
-Interestingly, we find that all nine materials appear to be four-fold coordinated, and that the first two lattice vectors ($a$ and $b$) are identical in all nine cases whereas $c$ may differ.
-There appears to be a high degree of symmetry present for all materials, but we find no elemental and perfectly symmetric semiconductors in the list.
+Interestingly, \mrk{all} nine materials appear to be four-fold coordinated, \mrk{and the first two lattice vectors ($a$ and $b$) are identical in all cases} whereas $c$ may differ.
+There appears to be a high degree of symmetry present for all materials, but \mrk{no elemental and perfectly symmetric semiconductors were found} in the list.
 
@@
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
+\mrk{Note} that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
 
@@
 It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
-NaCl was not predicted as suitable for QT in the empirical approach.
+NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach.
+This underlines that an empirical approach, based on experimental data, may be more suitable for predicting materials for a certain applications and understanding the underlying mechanisms than the assumption-based methodology.}
 
@@
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
+\mrk{ZnGeP$_2$ is therefore identified} as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
 
@@
 Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities with SiC. 
-Next, the compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at $1.5$~eV and $1.1$~eV, respectively.
+Next, the compound BP (mp-$1479$ and mp-$1008559$) is present in \mrk{the} predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at $1.5$~eV and $1.1$~eV, respectively.
 Both configurations of BP are nonmagnetic, non-toxic and BP has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
@@
 InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-We underline the possibility of using InP-based quantum dots for QT applications.
+\mrk{The possibility of using InP-based quantum dots for QT applications should be considered.}
 
-We note that all ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
+\mrk{All} ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+\mrk{However, almost} all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
 Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted sufficiently to admit several oxides as suitable candidates.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a $2.0$~eV band gap and decomposes to a similar MgSe configuration.
+Among these, \mrk{only a single material is present in the list of $66$ candidates predicted by the four ML methods} in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a $2.0$~eV band gap and decomposes to a similar MgSe configuration.
 %The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported at $2.45$~eV (optical band gap) \cite{Ubale2014}. 
@@
 
-\subsubsection*{Comparing the approaches}
-Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
-The Ferrenti approach also predicts a large amount of materials as suitable compared to the empirical approach, but the resulting data are otherwise not very different from the extended version.
+%\subsubsection*{Comparing the approaches}
+\section*{\mrk{Discussion}}
+%Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
+%The Ferrenti approach also predicts a large amount of materials as suitable compared to the empirical approach, but the resulting data are otherwise not very different from the extended version.
 The empirical approach, on the other hand, predicts fewer suitable candidates that are possible to examine  manually.
-Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+\mrk{The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
+The same cannot be said for the Ferrenti (and extended Ferrenti) approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
-Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
+Despite notable differences, as mentioned above, there is \mrk{some overlap of predicted materials between the approaches}. 
+%We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach.
 Similarly, $78$ of the $214$ materials are also predicted as suitable by all ML methods in the Ferrenti approach.
-All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
-(see the Supplementary Information at \cite{supplementary} for the full list). 
+All approaches \mrk{(including the extended Ferrenti approach)} and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary (see the Supplementary Information at \cite{supplementary} for the full list).
 Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
-However, we also find certain materials that cannot be classified as semiconductors, such as P, I, N$_2$ and H$_2$.
+However, \mrk{it also contains} certain materials that cannot be classified as semiconductors, such as P, I, N$_2$ and H$_2$.
 We note that none of these were included by the empirical approach when the threshold was set to $0.75$ or above.
@@
 
-\section*{Discussion}
-
 %histograms 
@@
     \centering
-    \input{figures/histograms/new/LegendHistPaper.tex}
+    \input{figures/histograms/revised/LegendHistogram.tex}
   \end{subfigure}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/MP_Eg_count_075.tex}
+    \input{figures/histograms/revised/MP_Eg_count_075.tex}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/IonProperty_max ionic char_count_075.tex}
+    \input{figures/histograms/revised/IonProperty_max ionic char_count_075.tex}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
+    \input{figures/histograms/revised/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.tex}
+    \input{figures/histograms/revised/AverageBondLength_std_dev Average bond length_count_075.tex}
     \subcaption{}
@@
 \caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
-The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti and extended Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
+The total number of predicted materials is  $6804$ for the Ferrenti approach, and $214$ for the empirical approach.
+The Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
     }

### 2022-05-28 revision/supplementary-revised.tex

--- 2022-03-28 supplementary.tex
@@
 
-\newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
-\newcommand{\morten}[1]{\textcolor{green}{#1}}
-\newcommand{\sebastian}[1]{\textcolor{cyan}{#1}}
-\newcommand{\marianne}[1]{\textcolor{blue}{#1}}
-\newcommand{\oyvind}[1]{\textcolor{maroon}{#1}}
-\newcommand{\lasse}[1]{\textcolor{red}{#1}}
+\newcommand{\mrk}[1]{\textcolor{red}{#1}}
 
@@
 
-\section*{Supplementary methods}
+\section*{Supplementary methodology}
 \subsection*{Featurization}
@@
 \input{appendix/featurizerTable.tex}
+
+\subsection*{\mrk{Data mining: The extended Ferrenti approach}}
+
+\mrk{This section contains the findings from the data mining and feature analysis for the extended Ferrenti approach to complement the discussion in the main text on the Ferrenti and empirical approaches.}
+
+\mrk{In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
+However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), there is a more sparse representation of each known chemical formula present in the labeled data.
+}
+
+\mrk{Figure~\ref{fig:parallel-coordinates-approaches} displays the parallel coordinate plot for the extended Ferrenti approach while Figure~\ref{fig:2dscatterplotpca} contains the two-dimensional scatter plot for the same approach.
+The qualitative behavior of the data set derived during the data mining of the extended Ferrenti approach can be seen to overlap with that of the Ferrenti approach.
+}
+
+\begin{figure}[t] %!htp
+    \centering
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
+    \end{subfigure}
+    \caption{\mrk{Parallel coordinate plot for the extended Ferrenti approach.
+To limit data cluttering, we have randomly collected up to $250$ entries for each class.
+The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}}
+    \label{fig:parallel-coordinates-approaches}
+\end{figure}
+
+\begin{figure}%[h] %!tbp
+    \centering
+    \begin{subfigure}{0.5\textwidth}
+        \centering
+        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+    \end{subfigure}
+    \caption{\mrk{Two-dimensional scatter plot for the extended Ferrenti approach.
+We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
+Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots.
+Green squares display suitable candidates and red triangles represent unsuitable candidates.}}
+    \label{fig:2dscatterplotpca}
+\end{figure}
 
@@
 When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
-Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30.800$ individual models.
+Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30,800$ individual models.
 
@@
 
+\subsection*{\mrk{The extended Ferrenti approach}}
+
+\mrk{The more liberal extended Ferrenti approach results in a $78 \ \%$ larger 
+amount of labeled data than the Ferrenti approach.  
+The four ML methods predict at least $13,000$ materials as suitable candidates out of $22,550$ materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
+Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable are, in fact, predicted as suitable candidates.
+However, the ML methods also predict materials as suitable that are not expected according to, e.g., \citeauthor{Weber2010} \cite{Weber2010}.
+All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+%Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
+Furthermore, although a conservative band gap restriction of $1.5$~eV was enforced for the data labeling in the extended Ferrenti approach, all four implemented ML methods still predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+The ML methods applied to data labeled in the Ferrenti and extended Ferrenti approaches are recognizing the band gap and bonding character as important, but the resulting predicted materials do not strictly follow the anticipated guidelines.
+}
+
 \subsection*{Prediction statistics}
@@
 
-For the Ferrenti approach, logistic regression finds a total of $12.380$ suitable candidates, while decision trees is the most conservative with $11.315$.
-Random forests has the most optimistic estimate with $14.278$, while gradient boosting finds $11.835$ suitable candidates.
+For the Ferrenti approach, logistic regression finds a total of $12,380$ suitable candidates, while decision trees is the most conservative with $11,315$.
+Random forests has the most optimistic estimate with $14,278$, while gradient boosting finds $11,835$ suitable candidates.
 The four ML methods agree on $6804$ suitable candidates,  however, many of the materials are predicted with a confidence similar to that of a coin-flip.
@@
 
-The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14.993$, $14.407$, $15.351$ and $13.788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14,993$, $14,407$, $15,351$ and $13,788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
 Due to the less stringent restrictions compared to the Ferrenti approach, we find a large number ($9227$) of entries that the four ML methods  agree on.

### 2022-05-31 response-letter/response-letter.tex
Updates from Overleaf

@@
 \documentclass[11pt, a4paper]{letter} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
+\usepackage{color}
+\newcommand{\mrk}[1]{\textcolor{red}{#1}}
 
@@
 \textit{Response: }
-\begin{itemize}
-    \item	Compare empirical to known input. Ferrenti reproduces expectations of literature. Main point is compare that to empirical which gives different result. 
-    \item Actually, don’t get exactly what we expect from Ferrenti. Den vektlegger det vi forventer, men returnerer ikke eksakt kriteriene. E.g. band gap, ionic character. 
-    \item Wnated to see if ML sees something else than the criteria we introduced. How does this compare to empirical? 
-    \item It is a nice start to begin with some general criteria.
+
+\textit{We appreciate the consideration of our manuscript and have carefully addressed all reviewer concerns.
+The manuscript has undergone a major revision to facilitate the suggested changes.
+We hope that the methodological clarity has now been improved, and that the logic of the implemented approaches is clear.
+}
+
+\textit{In short (we will revisit this issue below), the Ferrenti approaches are, in fact, not exactly reproducing the original classification.
+Some of the expected features, such as the band gap, are recognized by important by the ML methods trained on the Ferrenti and extended Ferrenti approaches.
+However, other features that were not part of the original selection criteria were also recognized as important (e.g., ...ADD), and the exact band gap criteria (0.5~eV and 1.5~eV) are not reproduced.
+Hence, there is some difference between the training data and the predicted materials.
+This indicates that there are certain patterns that the ML methods are picking up beyond our original definition.
+}
+\textit{Not sufficiently clear; add comment. }
+
+\textit{In some cases it can be useful to impose causality, as done in the Ferrenti approach, to verify whether the expectations are correct.
+However, we find discrepancies between the selection criteria and the predicted materials (e.g., prediction of NaCl and low band gap materials as suitable).
+Hence, the expected properties are not able to capture the full physics of the problem.
+Hence, we instead train the algorithms on knowledge from experiment and let the ML models figure out the connections between materials and QT.
+We had several hypotheses for why these materials are QT compatible, and therefore forced the causality to verify the assumption.
+When it did not work, we instead started from no assumptions, and let the ML methods reason out the causality.
+This proved much more efficient.
+}
+
+\textit{The main purpose of the Ferrenti approaches was to contrast the expectations of the literature (this was the guide for the data mining process) against the results of the empirical approach where the models were allowed to draw their own conclusions from material classifications  based on knowledge from the field.
+However, this contrast was not sufficiently clear;} \textit{add comment.
+}
+
+\textit{A major change to the manuscript that was implemented to highlight the empirical approach as the main finding was to move most of the discussion on the extended Ferrenti approach to the Supplementary.
+The extended Ferrenti approach was included because we wanted to remove the effect of practical considerations from the Ferrenti approach, however, this has no detectable effect on the predictions.
+The same features were recognized as important in the Ferrenti and extended Ferrenti approaches.
+Therefore, the presence of both in the discussion shadows the importance of the empirical approach.
+Hence, we have kept only the Ferrenti and empirical approaches to contrast them against one another.
+}
+
+%\begin{itemize}
+ %   \item	Compare empirical to known input. Ferrenti reproduces expectations of literature. Main point is compare that to empirical which gives different result. 
+ %   \item Actually, don’t get exactly what we expect from Ferrenti. Den vektlegger det vi forventer, men returnerer ikke eksakt kriteriene. E.g. band gap, ionic character. 
+%    \item Wnated to see if ML sees something else than the criteria we introduced. How does this compare to empirical?
+ %   \item It is a nice start to begin with some general criteria.
 However, as pointed out, the usefulness is limited.
 The point is that we actually demonstrate that the Ferrenti approaches are not the best way.
-    \item In some cases it might be useful to impose causality, to see to what extent that works.
+%    \item In some cases it might be useful to impose causality, to see to what extent that works.
 When we see that it does not work, we let the ML models figure out the connections between materials and QT.
@@
 This proved much more efficient.
-    \item Empirical is main result, Ferrenti is kind of test/validation/benchmark. Highlight more. 
-    \item Database of Ferrenti is commonly used, this is benchmark set of materials and information. Compare our method to benchmark. 
-    \item We agree; Ferrenti not really useful 
-    \item Ferrenti paper is data mining, not ML. We put it in to compare data 
-\end{itemize}
+ %   \item Empirical is main result, Ferrenti is kind of test/validation/benchmark. Highlight more. 
+  %  \item Database of Ferrenti is commonly used, this is benchmark set of materials and information. Compare our method to benchmark. 
+   % \item We agree; Ferrenti not really useful 
+    %\item Ferrenti paper is data mining, not ML. We put it in to compare data 
+%\end{itemize}
 
@@
 
+\textit{The Reviewer raises an interesting discussion.
+We agree that there are portions of our work that should be clarified.
+We conceive two main themes in the Reviewer's question: (i) the logic of training and testing on the same data set, and (ii) the logic of using preset criteria to design a data set.}
+
+\textit{Firstly, we would like to point out that the ML methods were not trained and applied to exactly the same data.
+The criteria that were specified in the Ferrenti approaches left many materials without a label altogether.
+We trained the models on only the labeled data, and then performed machine learning on the unlabeled data, that had not been grouped at all.
+The data was hence divided into multiple portions, where some was in the test set, and some in the  training set.
+Therefore, the testing and training was not performed on the same data.
+For the empirical approach, we also put the unlabeled data from the Ferrenti approaches in the test set for ML.}
+
+\textit{Secondly, the ML search does in fact not exactly reproduce the criteria set in the initial selection process.
+For the Ferrenti/Extended Ferrenti approaches, some of the properties we used to guide the labeling are recognized as important by the ML models (e.g., the band gap), but the selection criteria are not fully reproduced.
+For example, many materials are suggested with band gaps below 0.5~eV in the Extended Ferrenti approach, whereas the selection criterion was set to 1.5~eV.
+Hence, the models are recognizing the expected properties as important, but there are differences from expectation.
+The ML models seem to be recognizing some pattern in the data that was not exactly anticipated.
+From a materials science perspective, it seems that the exact value of the band gap is not predominant, although the feature itself is important.
+}
+
+\textit{Finally, as mentioned above, a driving force behind selecting to report on the Ferrenti approaches was the comparison to the Empirical one.
+The literature generally expects the findings from the Ferrenti approach.
+Hence, an analysis from the ML perspective on which features this would entail (i.e., from Matminer) was necessary to compare with the findings from the Empirical approach - the main result of this work.
+Additionally, the agreement in predictions from the three approaches could lend weight to a prediction and merit further experimental studies.
+}
+
+\textit{Importantly, however, the above considerations were not sufficiently clear in the original version of the manuscript. Therefore, we have ... }
+
 Reviewer \#2: \\
@@
 \textit{Response:} 
-% OH: Jeg synes han svarer egentlig på sitt eget spørsmål her.
-For at et materiale skal bli "predikert" som en god kandidat av maskinlærings-algoritmene, så kan ikke materialet være en del av treningssettet som ML algoritmene blir trent på, ergo så er ikke materiale kategorisert som hverken bra eller dårlig av the original extended ferrenti criteria.
-Det betyr at materialet er utelukket av the extended ferrenti criteria, altså at den oppfyller ikke kravene for hverken en god eller dårlig kandidat basert på data miningen.
 \textit{The material NaCl involves two elements where more than half does not have a natural abundance of spin zero isotopes, and is therefore excluded from being labeled as suitable.
@@
 We agree that it is not neccessarily clear that either Ferrenti or extended Ferrenti critera would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process that constitutes the criteria in the data mining.
-Therefore, NaCl is found unlabeled in the test data, and is predicted as an unsuitable candidate by the ML algorithms.}
+Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti alltogether predicts the material as suitable.}
+
+\textit{The following note was added to this effect on page 11:} \\ 
+\mrk{Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the test set.
+For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
+}
 
@@
 
-\textit{The data regarding a material's magnetic character is extracted from Materials Projects database.
-Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project perform an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
-As a result, we can find Fe (https://materialsproject.org/materials/mp-13/) labeled as ferromagnetic and NiO (https://materialsproject.org/materials/mp-19009/) as antiferromagnetic in our data .}
+\textit{The reviewer raises an important issue. 
+The data regarding a material's magnetic character is extracted from the Materials Projects database.
+Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
+As a result, we can find Fe (https://materialsproject.org/materials/mp-13/) labeled as ferromagnetic and NiO (https://materialsproject.org/materials/mp-19009/) as antiferromagnetic in our data set.}
 
-\textit{Additionally, Materials Project also include larger structures of the same material.
-We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.}
+\textit{Materials Project also includes larger structures of the same material.
+We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
+This is an improvement that could be made to our method in a further work.}
 
-\textit{Marianne; The reviewer raises an important issue.
-As noted, we are in fact mainly probing ferromagnetic ordering in our criteria.
-This was not sufficiently clear in the original manuscript but has been remedied in the revised version, see the following sentence on page …:
-Exploring larger cells was not done as the links between small and large cells of the same material in MP is not always clear.
+\textit{These points were not sufficiently clear in the original manuscript which has been remedied in the revised version.
+The following sentence was added to the Data Mining section on page 5 to clarify the part about ferromagnetic ordering: } \\
+\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the present criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
+
+\textit{The following clarifications were added to the Methods section under Databases:} \\ 
+\mrk{The data regarding a material's magnetic character is extracted from the Materials Projects database.
+Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
+As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our data set.}
+
+\mrk{MP includes larger structures of the same material.
+We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
+This is an improvement that could be made to our method in a further work.}
+
+%As noted, we are in fact mainly probing ferromagnetic ordering in our criteria.
+This was not sufficiently clear in the original manuscript but has been remedied in the revised version, see the following sentence on page …: Exploring larger cells was not done as the links between small and large cells of the same material in MP is not always clear.
 Therefore, this is an improvement that could be made to our method in a further work.
 This aspect has now been highlighted in the manuscript on page …
-}
 
@@
 Moreover, it is likely that the discovery of single photon emission and spin manipulation for the NV center in diamond has also guided the search for similar properties in other materials, with the search commencing with similar materials to diamond, such as different polytypes of SiC.
-The criteria of Weber et al are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable.
-The recent discovery of telecom compatible SPEs in Si, a lower band gap material, show that this may have been a preemptory assumption.
+The criteria of Weber \textit{et al.} (Ref.~[8] of the main text) are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable.
+The recent discovery of telecom compatible SPEs in Si (Refs.~[54-55] in the main text), a lower band gap material, show that this may have been a premature assumption.
 We hope that our work can contribute to widening the search for quantum compatible semiconductor platforms.
-A note to this effect has now been added to page …:  
+A discussion on this has now been added to the Discussion section on page 16: } \\ 
+\mrk{One should note that there is a certain degree of bias inherent to the data set labeled in the empirical approach.
+Firstly, experimental searches will always be limited by the availability and cost of materials and processing.
+Secondly, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
+However, the broad range of materials predicted and listed in Table~III and the Supplementary Information at [39] indicates that the ML methods are detecting underlying properties which manifest in materials systems of several kinds.
 }
@@
 \textit{From the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
-This ID is present in AFLOW, AFLOW-ML, JARVIS-DFT and OQMD, and we performed an additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97\%$.}
+This ID is included in the AFLOW, AFLOW-ML, JARVIS-DFT and OQMD databases as well.
 
-\textit{For the experimental values from Citrine, we could only verify the chemical formula since the data is lacking structures.}
+Due to the various different techniques of approximating the bandgap, either demonstrated experimentally or estimated using the DFT-calculations with the functionals PBE or PBE+U, we do not choose one but rather let them all be represented as columns (features) in our data.}
+
+%If two different databases have different values for the same property, we employed the value from ... }
+
+\textit{Furthermore, we performed an additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97 \ \%$, which is close to an ideal match.
+We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
+For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
+space group, symmetry) of the material.}
+
+\textit{We agree with the reviewer that this was not sufficiently clear in the original manuscript.
+To clarify these points, the above information has now been added to the Methods section, under "Databases": } \\
+\mrk{Note that from the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
+This ID is included in the AFLOW,  AFLOW-ML, JARVIS-DFT and OQMD databases as well.
+If two different databases have different values for the same property, such as the band gap, we added both of them as columns (features) to our data to avoid any data cluttering.
+An additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97 \ \%$, which is close to an ideal match.
+We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
+For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
+space group, symmetry) of the material.}
 
@@
 \begin{enumerate}
-    \item On page 12, what do the authors mean by “unfortunate structures”? 
+    \item On page 12, what do the authors mean by “unfortunate structures”? \\ 
+    \textit{Response:} \\ 
+    \textit{This phrase has now been replaced by the following;} \\ 
+    \mrk{Complex structures (e.g., nanostructures or 2D materials)}.  
     \item The authors use the “.” as the notation to represent both the decimal point and the separator for thousands in large numbers (e.g.
@@
     \textit{Thank you for pointing out this oversight. This has now been remedied according to the referee's suggestion. } 
-    \item The authors should note that AFLOW also uses PBE+U in some calculations as described in Ref. 24 of this work, particularly for materials taken from the ICSD. 
+    \item The authors should note that AFLOW also uses PBE+U in some calculations as described in Ref. 24 of this work, particularly for materials taken from the ICSD. \\
+    \textit{Response:} \\ 
+    \textit{Thank you for pointing this out, we have now added the detail to the description of AFLOW in our Methods section; \mrk{with the $+U$ correction}.}
     \item Finally, the article also contains a lot of repetition, making it unnecessarily long.
 For example, the “Comparing the approaches” subsection on pages 14 and 15 is mainly just repeating the results from the previous subsections - lot of this could be cut, with the remainder incorporated into the Discussion section.
+\\
+    \textit{Response:} \\ 
+    \textit{The reviewer makes a good point.
+We have now attempted to shorten the manuscript substantially.
+As mentioned above, much of the discussion on the Extended Ferrenti approach has now been moved to the Supplementary Information.
+Superfluous information has been removed from the main text and in some cases moved to the Methods section.
+The paper is now shorter by a full page.} \\
+    \textit{Regarding the “Comparing the approaches” subsection, we agree that there were many repetitions, which have now been removed.
+However, we elected to keep the subsection itself, as it  contains an important result of the work: a discussion on the $47$ materials that all three approaches and all four ML methods agree on above a $0.5$ threshold, and the $6$ materials likewise agreed upon to $0.75$ confidence.
+These materials were not discussed elsewhere in the text and the portion of Table III displaying their properties was first referenced here.
+Therefore we believe that this subsection should be kept.
+However, since this information got somewhat lost in translation, we have changed the name of the subsection to} \\
+    \mrk{"Overlapping predictions between the approaches"}. 
 \end{enumerate}

### 2022-05-31 revision/revised-paper_marked-up.tex
Updates from Overleaf

@@
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project. 
-In this framework, we label \textbf{suitable} candidates by the following steps:
+\mrk{Note that this data mining process alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
+Nonetheless, we adapt the selection criteria from Ref.~\cite{Ferrenti2020} for the present purposes.}
+In the \mrk{Ferrenti approach} framework, \textbf{suitable} candidates \mrk{are labeled} by the following steps: 
 \begin{enumerate}
@@
 These inclusion criteria are based on the work of \citeauthor{Weber2010} \cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
-In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
+In this context, long spin coherence times are needed, \mrk{necessitating an environment that can be depleted of nuclear spins and permanent magnetism.}
+%and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable. 
 Moreover, non-polar materials are assumed to be preferable to obtain defect based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission.  
@@
 Finally, the energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
+\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
 
@@
 Here we see the first example of how the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
+
+\mrk{Performing machine learning on a data set derived using preconceived notions for which material properties are important is likely to reproduce several of the initial selection criteria.
+Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the other approaches.
+Additionally, one should note that ML methods are capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.}
 
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD,
-        \item are calculated to be nonmagnetic. 
+        \mrk{are present in the ICSD,
+        and are calculated to be nonmagnetic.} 
     \end{itemize}
@@
 
-For \textbf{unsuitable} candidates, \mrk{the same strategy as for the first Ferrenti approach was implemented}.
-The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
+For \textbf{unsuitable} candidates, \mrk{the same strategy as for the Ferrenti approach was implemented}.
+The result is a somewhat unbalanced set of labeled materials with up to $75 \ \%$ of the materials found in the suitable group\mrk{ and $78 \ \%$ more materials than for the Ferrenti approach.}
+%However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
 
@@
 This is attributed to the similarities in the selection processes.
-Therefore, detailed discussion on the findings from the extended Ferrenti approach can be found in the Supplementary Material at \cite{supplementary}.
+Therefore, detailed discussion on the findings from the extended Ferrenti approach can be found in the Supplementary Information at \cite{supplementary}.
 Qualitative conclusions drawn for the Ferrenti approach herein also hold for the extended Ferrenti approach, indicating that the removal of so-called practical considerations did not have a significant impact on the results.
@@
 \subsubsection*{The empirical approach}
-The third approach differs substantially from the others in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to pick our promising material host candidates.
-In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
-We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training and testing of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
-These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
-We have also included materials where properties like single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related.
+%The third approach differs substantially from the others in terms of material labeling, as 
+\mrk{In the \emph{empirical approach},} we apply knowledge from the field (see for instance  Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to \mrk{guide the search for} promising material \mrk{hosts.}
+In other words, \mrk{the labeled data contains candidates} where quantum compatible properties have been either experimentally demonstrated or theoretically predicted\mrk{, including the materials suggested in Ref.~\cite{Weber2010} as promising deep level defect hosts.}
+%We therefore name this scheme \emph{the empirical approach}. 
+%Due to the concern of ending up with too small datasets for training and testing of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
+%These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}. 
+%\mrk{The theoretical predictions were motivated by the criteria for having deep level defects exhibit quantum compatible properties \cite{Weber2010}.} 
+%material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}. 
+\mrk{Materials where single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related were also included.}
 
@@
 Notably, the candidates labeled as suitable in the empirical approach contain only compounds that are either elementary (unary) or binary. 
-Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, we add $400$ candidates that are labeled as \textbf{unsuitable}.
-These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
+Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, \mrk{$400$ materials were added and labeled as \textbf{unsuitable}}.
+These \mrk{were} picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
 
@@
 From the predicted dataset of $23.623$ materials  
-the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+%the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach. 
+all four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
 If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
@@
 On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
+
+\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
+Indeed, NaCl is predicted as a suitable candidate to minimum confidences of $0.83$ and $0.61$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the test set.
+For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
+}
 
@@
 It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
-NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach.
-This underlines that an empirical approach, based on experimental data, may be more suitable for predicting materials for a certain applications and understanding the underlying mechanisms than the assumption-based methodology.}
+NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach}.
+%This underlines that an empirical approach, based on experimental data, may be more suitable for predicting materials for a certain applications and understanding the underlying mechanisms than the assumption-based methodology.}
 
@@
 %\subsubsection*{Comparing the approaches}
-\section*{\mrk{Discussion}}
+\subsubsection*{Overlapping predictions between the approaches}
+
+%\section*{\mrk{Discussion}}
 %Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
@@
 \mrk{The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
-The same cannot be said for the Ferrenti (and extended Ferrenti) approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+The same cannot be said for the Ferrenti (and extended Ferrenti) approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible\mrk{,} and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
 
@@
 Similarly, $78$ of the $214$ materials are also predicted as suitable by all ML methods in the Ferrenti approach.
-All approaches \mrk{(including the extended Ferrenti approach)} and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary (see the Supplementary Information at \cite{supplementary} for the full list).
+All approaches \mrk{(including the extended Ferrenti approach) and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence 
+%where $8$ are elementary (unary), $29$ binary, and $10$ tertiary 
+(see the Supplementary Information at \cite{supplementary} for the full list).} 
 Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
-However, \mrk{it also contains} certain materials that cannot be classified as semiconductors, such as P, I, N$_2$ and H$_2$.
+However, certain materials that cannot be classified as semiconductors \mrk{are also included}, such as P, I, N$_2$ and H$_2$.
 We note that none of these were included by the empirical approach when the threshold was set to $0.75$ or above.
@@
 These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$).
-Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (illustrated in Fig.~\ref{fig:crystalsystems}).
-The relevant material properties are summarized in the lower part of Table~\ref{tab:materialproperties}.
-Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
-We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP (unstable).
-However, consistent four-fold coordination and the bond angle trends we observed for the first $9$ materials are not maintained as GeSe is six-fold coordinated.
+Here, we can distinguish three groupings in crystal structure: cubic, hexagonal and tetragonal (illustrated in Fig.~\ref{fig:crystalsystems}).
+The relevant material properties are summarized in the lower part of Table~\ref{tab:materialproperties},
+%Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
+\mrk{with comparable trends to those for the $9$ materials predicted by the empirical approach in terms of, e.g., crystal structure.
+The six-fold coordination of GeSe is an outlier as compared to the four-fold coordination of the other materials.
+}
+%We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP.
+%However, consistent four-fold coordination and the bond angle trends  observed for the first $9$ materials are not maintained as GeSe is six-fold coordinated. 
 We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental studies.
@@
 
+\section*{Discussion}
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the ML methods revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches encompasses features related to the band gap and chemical environment.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for \mrk{the Ferrenti approach} encompasses features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process.
+%In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process. 
+\mrk{The Ferrenti approach does not entirely reproduce the logic of the initial selection process however as many low band gap materials were highlighted as suitable by the ML methods. } 
 For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.
 
-Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
-Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti approaches exhibiting a peak around a $2.5$~eV band gap.
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that \mrk{both} approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
+Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti \mrk{approach} exhibiting a peak around a $2.5$~eV band gap. 
 Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around $2.5$~eV using the PBE functional. 
-The empirical approach exhibits a more scattered data distribution with local maxima around $1$-$2$ and $4$~eV.
+The empirical approach exhibits a more scattered data distribution. % with local maxima around $1$-$2$ and $4$~eV.
 
 The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
-We note that this may be a result of the distribution of the initial dataset of $25.000$ materials that peaks around a similar value (not shown).
-The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach, extended Ferrenti approach nor the overall data distribution.
-For comparison, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
-Further, we find that the covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
+Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for \mrk{both the Ferrenti and empirical} approaches - even peaking at a relatively high ionic character of $0.8$.
+We note that this may be a result of the distribution of the initial dataset of \mrk{$25,000$} materials \mrk{with a maximum} around a similar value (not shown).
+The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach \mrk{nor} the overall data distribution.
+For \mrk{reference}, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
+\mrk{Furthermore, the} covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 The ML methods in the empirical approach consistently identified the first principal component as the predominant one.
-Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
-Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in Fig.~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
-Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti approaches and the empirical approach.
-This reflects the observations from the principal component analysis where the first principal component is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti and extended Ferrenti approaches display an even distribution across a broader range.
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that \mrk{matters}.
+Here,\mrk{the} standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
+One configuration of the standard deviation of the RDF is demonstrated in \mrk{Figure}~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
+Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the \mrk{Ferrenti} and the empirical approach.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti \mrk{approach displays} an even distribution across a broader range.
+\mrk{These observations emphasize the importance of symmetry related material properties for QT suitability. }
 
@@
 The exact degree and type of symmetry is still open to debate and merits further study.
-Similar symmetry related features such as the standard deviation of the average bond length (see Fig.~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Information at \cite{supplementary}) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
+Similar symmetry related features such as the standard deviation of the average bond length (see Figure~\ref{fig:histogram_new}d), the site fingerprint of the chemical environment and the bond orientation (see the Supplementary Information at \cite{supplementary}) are also influential in guiding the ML algorithms upon classifying suitable and unsuitable materials for QT in the empirical approach.
 
@@
 This resonates with the observations from the principal component analysis; an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but some variations throughout the crystal in, e.g., bond length and symmetry are needed.
-This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti and extended Ferrenti approaches.
+This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti \mrk{approach}.
 Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well and may be more important.
@@
 For example, in the high symmetry materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
-Instead, we find that quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
+Instead, \mrk{quantum} effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
 For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
@@
 
-Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
-The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
+\mrk{One should note that there is a certain degree of bias inherent to the data set labeled in the empirical approach.
+Firstly, experimental searches will always be limited by the availability and cost of materials and processing.
+Secondly, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
+However, the broad range of materials predicted and listed in Table~\ref{tab:materialproperties} and the Supplementary Information at \cite{supplementary} indicates that the ML methods are detecting underlying properties which manifest in materials systems of several kinds.
+}
 
-To summarize, the data extraction tools developed in this work resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
+To summarize, the data extraction tools developed in this work resulted in a dataset of over \mrk{$25,000$} materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training and testing of four ML algorithms.
-We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
-Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
-The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
-Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.
+\mrk{The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is suitable for performing this type of guided search through materials databases.}
+%We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
+%Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
+The principal component analyses of the ML methods' performance imply that the Ferrenti \mrk{approach with its} strong focus on band gap and bonding character when assessing a material's quantum compatibility \mrk{to some extent reproduces} the specifications of the data labeling process, \mrk{as expected.}
+Valuable insight is gained from \mrk{comparing the important features of the Ferrenti with those for} the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions \mrk{over expected features related to band gap and bonding}.
 
 The findings presented here firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
-Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
-We suggest two possible paths to further exploit our findings.
-One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by the four ML methods.
-Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
+Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the \mrk{developed framework} is suitable for other fields as well.
+\mrk{Two possible paths are suggested to further exploit the findings presented herein.} One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by \mrk{machine learning}.
+Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process\mrk{es} to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
 
@@
 The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
-They utilize the PBE functional within VASP to relax and optimize the structure from the ICSD.
+They utilize the PBE functional \mrk{with the $+U$ correction} within VASP to relax and optimize all structures from the ICSD.
 Data extraction was performed in the period of January to February of $2021$.
@@
 This process was executed during January of $2021$.
+
+\mrk{Note that from the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
+This ID is included in the AFLOW,  AFLOW-ML, JARVIS-DFT and OQMD databases as well.
+If two different databases have different values for the same property, such as the band gap, we added both of them as columns (features) to our data to avoid any data cluttering.
+An additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97 \ \%$, which is close to an ideal match.
+We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
+For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
+space group, symmetry) of the material.}
+
+\mrk{The data regarding a material's magnetic character is extracted from the Materials Projects database.
+Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
+As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our data set.}
+
+\mrk{MP includes larger structures of the same material.
+We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
+This is an improvement that could be made to our method in a further work.}
 
@@
 
+\mrk{Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
+The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.}
+
 \section*{Data availability} 

### 2022-06-03 response-letter/response-letter.tex
Updates from Overleaf

@@
 
+Ferrenti is data mining approach that is new. No ML done on it before. We do it to compare to empirical, which is main result. Expectation is band gap, wnated to check whether this is true.
+
+Actually, Ferrenti does not exactly reproduce. Also, we took out extended Ferrenti.
+
+\begin{itemize}
+    \item Ikke gjenskaper helt. Impose causality. Vi antar band gap er viktigst. Stemmer dette ?
+    \item Ferrenti er data mining, er ikke gjort maskinlaering paa det foer 
+    \item Sammenligne med Ferrenti 
+    \item Filter for Ferrenti, to reduce experimental work. ML is effctive way to reduce dimensionality of problem. 
+\end{itemize}
+
 \textit{In short (we will revisit this issue below), the Ferrenti approaches are, in fact, not exactly reproducing the original classification.
-Some of the expected features, such as the band gap, are recognized by important by the ML methods trained on the Ferrenti and extended Ferrenti approaches.
-However, other features that were not part of the original selection criteria were also recognized as important (e.g., ...ADD), and the exact band gap criteria (0.5~eV and 1.5~eV) are not reproduced.
+Some of the expected features, such as the band gap, are recognized as important by the ML methods trained on the Ferrenti and extended Ferrenti approaches, but the exact band gap criteria (0.5~eV and 1.5~eV) are not reproduced.
+Moreover, other features that were not part of the original selection criteria were also recognized as important \textbf{(e.g., ...ADD)}.
 Hence, there is some difference between the training data and the predicted materials.
-This indicates that there are certain patterns that the ML methods are picking up beyond our original definition.
-}
-\textit{Not sufficiently clear; add comment. }
+This indicates that there are certain patterns that the ML methods are picking up beyond our original definition. } 
+\textbf{Not sufficiently clear; add comment. }
+
+\textit{Use Ferrenti as a filter; the materials that all methods admit.}
 
@@
 However, we find discrepancies between the selection criteria and the predicted materials (e.g., prediction of NaCl and low band gap materials as suitable).
-Hence, the expected properties are not able to capture the full physics of the problem.
-Hence, we instead train the algorithms on knowledge from experiment and let the ML models figure out the connections between materials and QT.
+As such, the expected properties are not able to capture the full physics of the problem.
+Thus we instead train the algorithms on knowledge from experiments and let the ML models figure out the connections between materials and QT. 
 We had several hypotheses for why these materials are QT compatible, and therefore forced the causality to verify the assumption.
 When it did not work, we instead started from no assumptions, and let the ML methods reason out the causality.
-This proved much more efficient.
-}
+This proved much more efficient. }
 
 \textit{The main purpose of the Ferrenti approaches was to contrast the expectations of the literature (this was the guide for the data mining process) against the results of the empirical approach where the models were allowed to draw their own conclusions from material classifications  based on knowledge from the field.
-However, this contrast was not sufficiently clear;} \textit{add comment.
-}
+We agree that this contrast was not sufficiently clear.}
+\textbf{add comment. }
 
-\textit{A major change to the manuscript that was implemented to highlight the empirical approach as the main finding was to move most of the discussion on the extended Ferrenti approach to the Supplementary.
-The extended Ferrenti approach was included because we wanted to remove the effect of practical considerations from the Ferrenti approach, however, this has no detectable effect on the predictions.
+\textit{A major change to the manuscript that was implemented to highlight the empirical approach as the main finding was to move most of the discussion on the extended Ferrenti approach to the Supplementary information.
+The extended Ferrenti approach was included because we wanted to remove the effect of practical considerations from the Ferrenti approach, however, this had no detectable effect on the predictions.
 The same features were recognized as important in the Ferrenti and extended Ferrenti approaches.
 Therefore, the presence of both in the discussion shadows the importance of the empirical approach.
-Hence, we have kept only the Ferrenti and empirical approaches to contrast them against one another.
-}
+Hence, we have kept only the Ferrenti and empirical approaches to contrast them against one another. }
 
@@
 The criteria that were specified in the Ferrenti approaches left many materials without a label altogether.
+In fact, several materials could not be labeled in the Ferrenti approaches because they did not fall into either category, suitable or unsuitable. 
 We trained the models on only the labeled data, and then performed machine learning on the unlabeled data, that had not been grouped at all.
@@
 Hence, the models are recognizing the expected properties as important, but there are differences from expectation.
+The ML models will naturally weight the criteria differently from the specifications as they are not aware of the criteria.
+Causality is not exact.
 The ML models seem to be recognizing some pattern in the data that was not exactly anticipated.
@@
 
-\textit{Finally, as mentioned above, a driving force behind selecting to report on the Ferrenti approaches was the comparison to the Empirical one.
+\textit{Finally, as mentioned above, a driving force behind selecting to report on the Ferrenti approaches was the comparison to the empirical one.
 The literature generally expects the findings from the Ferrenti approach.
 Hence, an analysis from the ML perspective on which features this would entail (i.e., from Matminer) was necessary to compare with the findings from the Empirical approach - the main result of this work.
-Additionally, the agreement in predictions from the three approaches could lend weight to a prediction and merit further experimental studies.
+Thirdly, the agreement in predictions from the three approaches could lend weight to a prediction and merit further experimental studies.
+Use Ferrenti as filter.
 }
@@
 In addition, NaCl is excluded from being labeled as unsuitable from the criteria due to its nonmagnetic label in Materials Project.
-We agree that it is not neccessarily clear that either Ferrenti or extended Ferrenti critera would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process that constitutes the criteria in the data mining.
-Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti alltogether predicts the material as suitable.}
+We agree that it is not necessarily clear that either Ferrenti or extended Ferrenti critera would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process that constitutes the criteria in the data mining.
+Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti altogether predicts the material as suitable.}
 
@@
 \textit{Response:}
+
 \textit{We agree with the Reviewer.
@@
 This ID is included in the AFLOW, AFLOW-ML, JARVIS-DFT and OQMD databases as well.
-
-Due to the various different techniques of approximating the bandgap, either demonstrated experimentally or estimated using the DFT-calculations with the functionals PBE or PBE+U, we do not choose one but rather let them all be represented as columns (features) in our data.}
+Due to the various different techniques of approximating the bandgap, either demonstrated experimentally or estimated using the DFT-calculations with the functionals PBE or PBE+U, and as we do not exactly know which method is most accurate, we do not choose one but rather let them all be represented as columns (features) in our data.}
 
@@
 We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
-For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
+For the experimental values from Citrine, we could only verify the chemical formula since the database is lacking information regarding the structure (e.g.
 space group, symmetry) of the material.}
@@
     \textit{This phrase has now been replaced by the following;} \\ 
-    \mrk{Complex structures (e.g., nanostructures or 2D materials)}.  
+    \mrk{Complex and low-dimensional  structures (e.g., nanostructures) were removed so only 3D or 2D structures remained in the labeled dataset}. 
     \item The authors use the “.” as the notation to represent both the decimal point and the separator for thousands in large numbers (e.g.
@@
     \textit{Response:} \\ 
-    \textit{Thank you for pointing this out, we have now added the detail to the description of AFLOW in our Methods section; \mrk{with the $+U$ correction}.}
+    \textit{Thank you for pointing this out, we have now added the detail to the description of AFLOW in our Methods section;} \mrk{with the $+U$ correction}.
     \item Finally, the article also contains a lot of repetition, making it unnecessarily long.

### 2022-06-03 revision/revised-paper_marked-up.tex
Updates from Overleaf

@@
 \section*{Introduction}
-Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during the last few years. 
+Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during \mrk{recent}  years. 
 Among the promising applications that are already available we find important breakthroughs such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures \cite{Arute_2019}.
@@
 These characteristics are most often found for the case of defects that introduce deep energy levels into the semiconductor band gap \cite{Weber2010}.
-So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g.,
-indistinguishable  
-single-photon emission and long spin coherence times. 
+So-called deep level defects can trap charge carriers in localized states that are essentially isolated from the surroundings, making them highly suitable for QT due to, e.g., indistinguishable single-photon emission and long spin coherence times.
 The most well-known quantum compatible defect is the negatively charged nitrogen-vacancy (NV) center in diamond \cite{Doherty_2013}, but silicon carbide (SiC) and the various quantum emitters therein are strong contenders for quantum communication purposes especially due to the favorable emission wavelength region in the near infrared coupled with more mature material processing and fabrication (see, e.g., Refs.~\cite{Castelletto_2015,Son2020,Bathen2021}).
 However, semiconductor based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
-Furthermore, we lack a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties,  
+Furthermore, a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties \mrk{is lacking},  
 and the selection of known quantum compatible host materials is slim \cite{Atatuere2018,Zhang2020}.
@@
 %, see for example Ref.~\cite{Acin2018}.
-Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures we should target for more detailed studies, following the framework illustrated in Fig.~\ref{fig:ht-workflow}.
+Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures \mrk{should be targeted} for more detailed studies, following the framework illustrated in Fig.~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing material properties for a wide range of different systems.
@@
 
-Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and ML methods combined with knowledge from the field.
+Here we provide a framework for the data mining and automated discovery of promising \mrk{semiconductor hosts for QT} using targeted database search and ML methods combined with knowledge from the field.
 Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training and testing, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
@@
 The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important aspect of our work is the database building and pertinent development of the datasets for the ML methods.
-We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
-We find that the two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
+An important aspect of \mrk{the} work is the database building and pertinent development of the datasets for the ML methods.
+\mrk{Three different approaches to data mining were devised}: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
+\mrk{The} two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding $214$ predicted candidates that were common between all approaches and ML methods.
-Example materials include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
+The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding \mrk{$47$} predicted candidates that were common between all approaches and ML methods.
+Example materials \mrk{among the predictions} include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
 Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
@@
 Therefore, not all properties predicted using the PBE functional are reliable, and the band gaps in particular cannot be trusted in absolute terms.
-Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor properties.
+Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor \mrk{material} properties.
 
@@
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ featurizers (each generates several features) selected as material descriptors in this work are summarized and described in the Supplementary Information at \cite{supplementary}.
-The selection of features was kept rather wide as we do not want to make {\em ex ante} assumptions on which features best describe a solid state material platform for quantum technology.
+The $39$ featurizers (each generates several features) selected as material descriptors in this work are \mrk{described} in the Supplementary Information at \cite{supplementary}.
+The selection of features was kept rather wide \mrk{to avoid making} {\em ex ante} assumptions on which features best describe a solid state material platform for \mrk{QT}.
 
@@
 Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
-Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Thus, our results depend on the quality of data in the databases we employ.
+Unfortunately, if an error has \mrk{occurred} in the first part of the process, the error \mrk{is carried along} and will get increasingly harder to detect.
+Thus, \mrk{the} results depend on the quality of data in the \mrk{employed} databases.
 
@@
 The labeled data are then grouped into training and test sets for the ML methods.
-
-Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
+\mrk{The ML methods are trained using the training set and then evaluated on the test set.}
+\mrk{Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.}
+
+Several challenges accompany the labeling \mrk{process.} 
+%of labeling materials according to their suitability for QT. 
 Although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot (QD) structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable  \cite{Atatuere2018,Zhang2020}.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood.
-Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are also unknown. 
-The strategy for selection of unsuitable candidates is thus that the negation of the criteria we use to select suitable candidates should give unsuitable candidates.
-A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates. 
-We will then find ourselves in a situation with skewed data sets were we have fewer unsuitable than suitable candidates. 
+Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are \mrk{not known either}.
+The strategy for selection of unsuitable candidates is thus that the negation of the criteria \mrk{used} to select suitable candidates should give unsuitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates\mrk{, resulting in} skewed data sets \mrk{with} fewer unsuitable than suitable candidates.
 This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
-Below we \mrk{follow separate} procedures for labeling materials as suitable or unsuitable candidates for QT.
+Below \mrk{three separate procedures for labeling materials as suitable or unsuitable candidates for QT are described}.
 
@@
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project. 
-\mrk{Note that this data mining process alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
+\mrk{Note that the data mining process in Ref.~\cite{Ferrenti2020} alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
 Nonetheless, we adapt the selection criteria from Ref.~\cite{Ferrenti2020} for the present purposes.}
-In the \mrk{Ferrenti approach} framework, \textbf{suitable} candidates \mrk{are labeled} by the following steps: 
+In the \mrk{\emph{Ferrenti approach}} framework, \textbf{suitable} candidates \mrk{are labeled} by the following steps: 
 \begin{enumerate}
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD database, 
+        \item are present in the ICSD\mrk{,} 
         and
@@
 %and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable. 
-Moreover, non-polar materials are assumed to be preferable to obtain defect based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission.  
+Moreover, non-polar materials are assumed to be preferable to obtain \mrk{sharp and indistinguishable single-photon emission from defects}.  
 Transition metal elements are eliminated if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
-Finally, the energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
+Finally, the energy above hull requirement \mrk{ensures} that the selected compounds are thermodynamically stable.
 \mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
 
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
-that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the \mrk{ICSD} that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors).
 The resulting set of labeled materials contains $1581$ materials where $35 \ \%$
 are labeled as unsuitable and 
-$65 \ \%$ as suitable for QT applications.
-Here we see the first example of how the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
+$65 \ \%$ as suitable for QT applications, \mrk{evidencing that} 
+%Here we see the first example of how 
+the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
 
@@
 Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the other approaches.
-Additionally, one should note that ML methods are capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.}
+Additionally, one should note that ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.}
 
@@
 The second approach is therefore named \emph{the extended Ferrenti approach} and involves removing stage two from the approach above.
-Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
-
-The following steps constitute the process of labeling \textbf{suitable} candidates in the \emph{extended Ferrenti approach}:
+Moreover, \mrk{certain} additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes \mrk{are also included}.
+
+The following steps constitute the process of labeling \textbf{suitable} candidates in the \mrk{extended Ferrenti approach}:
 \begin{enumerate}
@@
 For \textbf{unsuitable} candidates, \mrk{the same strategy as for the Ferrenti approach was implemented}.
-The result is a somewhat unbalanced set of labeled materials with up to $75 \ \%$ of the materials found in the suitable group\mrk{ and $78 \ \%$ more materials than for the Ferrenti approach.}
+The result is \mrk{an} unbalanced set of labeled materials with up to $75 \ \%$ of the materials found in the suitable group \mrk{and $78 \ \%$ more materials than for the Ferrenti approach.}
 %However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
@@
 
-\mrk{The labeled data for each approach is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+\mrk{The labeled data for the Ferrenti and empiricial approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes  \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
 This differs from Fig.~\ref{fig:2dscatterplotpca}, where \mrk{the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown}.
-Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all data}.
+Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all the data}.
 Here, the ML analysis is done on the labeled data for each approach.
@@
 Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that \mrk{matters}.
-Here,\mrk{the} standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
+Here, \mrk{the} standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
 One configuration of the standard deviation of the RDF is demonstrated in \mrk{Figure}~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.

### 2022-06-10 response-letter/response-letter.tex
Updates from Overleaf

--- 2022-05-31 response-letter/response-letter.tex
@@
 \usepackage{color}
+\usepackage{siunitx}
 \newcommand{\mrk}[1]{\textcolor{red}{#1}}
@@
 
-\Who{Prof. Morten Hjorth-Jensen} % Your name
+\Who{} % Your name
 
-\Title{, PhD} % Your title, leave blank for no title
+\Title{  } % Your title, leave blank for no title
 
-\authordetails{
+\authordetails{%
+	Morten Hjorth-Jensen \\ 
 	Department of Physics\\ % Your department/institution
@@
 	N-0316 Oslo, Norway\\ % Your city, zip code, country, etc
-	Email: morten.hjorth-jensen@fys.uio.no\\ % Your email address
-	Phone: (000) 111-1111\\ % Your phone number
-	URL: LaTeXTemplates.com % Your URL
+	Email: \\ 
+	morten.hjorth-jensen \\ 
+	@fys.uio.no % Your email address
 }
@@
 \begin{center}
-   \textbf{Resubmission of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by O.L. Hebnes, et al.}
+   \textbf{Resubmission of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by O. L. Hebnes, et al.}
 \end{center}
@@
 Please find enclosed a revised version of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by Oliver L.
-Hebnes, et al., submitted for publication as an original article in npj Computational Materials.
-There are two files in all: a Manuscript file and a Supplementary Information file.
+Hebnes, et al., submitted for publication as an original article in \textit{npj Computational Materials}.
+There are three files in all: a marked-up Manuscript file, a clean Manuscript file and a Supplementary Information file.
+Changes are marked in red in the marked-up Manuscript and the Supplementary Information.
 
-Please find detailed responses to reviewer comments below.
+We appreciate the opportunity to revise our manuscript.
+We would also like to thank the reviewers for their careful reading of our manuscript.
+Their comments point to several places where the manuscript was unclear and have enabled us to substantially improve the paper.
 
-\closing{Sincerely,}
+The manuscript has undergone a major revision.
+Most notable is that we have moved the discussion on the results for the Extended Ferrenti approach from the main text to the Supplementary Information.
+This was done to diminish the emphasis on this data mining approach.
+The Ferrenti approach has been kept for several reasons outlined below, but the reasoning behind utilizing this approach has been emphasized, and its benefits clarified.
+Overall, the text has been shortened wherever possible to address the comment that it was too long, leaving the main text almost a full two pages shorter.
+All changes to the manuscript are highlighted in red in the marked-up version.
+
+Please find detailed responses to the comments of the Reviewers and Editor below.
+
+%\closing{Sincerely,}
+Sincerely,
+
+\noindent Prof. Morten Hjorth-Jensen and Dr. Marianne E. Bathen \\
+On behalf of all the authors
 
@@
 
-\textit{In short (we will revisit this issue below), the Ferrenti approaches are, in fact, not exactly reproducing the original classification.
-Some of the expected features, such as the band gap, are recognized by important by the ML methods trained on the Ferrenti and extended Ferrenti approaches.
-However, other features that were not part of the original selection criteria were also recognized as important (e.g., ...ADD), and the exact band gap criteria (0.5~eV and 1.5~eV) are not reproduced.
-Hence, there is some difference between the training data and the predicted materials.
-This indicates that there are certain patterns that the ML methods are picking up beyond our original definition.
-}
-\textit{Not sufficiently clear; add comment. }
+\textit{We  believe that including the Ferrenti approach is important for several reasons.
+Firstly, by starting with an established data mining approach we can partly verify the reliability of our methodology before we introduce the empirical approach.
+The difference in candidate materials extracted from the Ferrenti and empirical approaches also gives insight into the selection criteria and parameters important for suitable qubit materials.
+Thus, the contrast between the two approaches is important.
+However, we do realize that the Ferrenti and extended Ferrenti approaches combined put too much emphasis on this data mining approach.
+A major change to the manuscript that was implemented in order to highlight the empirical approach as the main finding was therefore to move most of the discussion on the extended Ferrenti approach to the Supplementary information.
+The extended Ferrenti approach was initially included because we wanted to remove the effect of practical considerations from the Ferrenti approach, however, this had few detectable effects on the predictions.
+The same features were recognized as important in the Ferrenti and extended Ferrenti approaches.
+Therefore, the presence of both in the discussion shadows the importance of the empirical approach.
+Hence, we have kept mainly the Ferrenti and empirical approaches as discussion points in the main text.
+Please see the following discussion of this in the main text on page 6, in the Data mining section:} \\
+\mrk{The findings from both the data mining and machine learning procedures for the extended Ferrenti approach did not differ substantially from those obtained using the Ferrenti approach.
+This is attributed to the similarities in the selection processes.
+Therefore, detailed discussion on the findings from the extended Ferrenti approach can be found in the Supplementary Information at [39].
+Qualitative conclusions drawn for the Ferrenti approach herein also hold for the extended Ferrenti approach, indicating that the removal of so-called practical considerations did not have a
+significant impact on the results. Nonetheless, predictions from the extended Ferrenti approach will be employed below to contrast with and filter the findings from the empirical approach.}
 
-\textit{In some cases it can be useful to impose causality, as done in the Ferrenti approach, to verify whether the expectations are correct.
+\textit{Secondly, the data mining approach reported by Ferrenti and co-workers follows established expectations (e.g., as reported by Weber et al.) for quantum friendly materials, but no machine learning (ML) has been applied to data sets extracted by this approach.
+Since ML algorithms are useful for reducing the dimensionality of a data set, it is interesting to see if the ML algorithms recognize the original criteria as the key parameters for labeling the materials.
 However, we find discrepancies between the selection criteria and the predicted materials (e.g., prediction of NaCl and low band gap materials as suitable).
-Hence, the expected properties are not able to capture the full physics of the problem.
-Hence, we instead train the algorithms on knowledge from experiment and let the ML models figure out the connections between materials and QT.
-We had several hypotheses for why these materials are QT compatible, and therefore forced the causality to verify the assumption.
-When it did not work, we instead started from no assumptions, and let the ML methods reason out the causality.
-This proved much more efficient.
+As such, the expected properties are not able to capture the full physics of the problem.
+This is in fact an important finding of our work; that the the problem of QT compatibility is more complex than being related to band gap and bonding character alone, and the contrast between the Ferrenti and empirical approaches was necessary to come to this conclusion.
+However, we realize that this was not sufficiently clear in the original manuscript.
+The following phrase has been added to the Discussion on page 15:} \\
+\mrk{As such, the expected properties are not able to capture the full physics of the problem.
+The contrast between the Ferrenti and empirical approaches reveals that the problem of QT compatibility is more complex than being related to band gap and bonding character alone.
+Based on our findings we propose that the manifestation of quantum effects in semiconductors is related to the crystal structure symmetry and bonding.
 }
 
-\textit{The main purpose of the Ferrenti approaches was to contrast the expectations of the literature (this was the guide for the data mining process) against the results of the empirical approach where the models were allowed to draw their own conclusions from material classifications  based on knowledge from the field.
-However, this contrast was not sufficiently clear;} \textit{add comment.
-}
+\textit{Thirdly, the Ferrenti approach can be employed as a filter on the empirical approach.
+If we consider the materials predicted by both the empirical and Ferrenti approaches as the most suitable, the prediction space is restricted even further.
+The following paragraph was added to the Discussion section on page 15 to better explain our reasoning:} \\
+\mrk{It should be noted that performing machine learning on a dataset derived using preconceived notions for which material properties are important may reproduce several of the initial selection criteria.
+Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the empirical one.
+Additionally, ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.
+Finally, the Ferrenti approaches are employed as a filter on the empirical approach, to provide a better tuned list of candidates for future experimental studies.}
 
-\textit{A major change to the manuscript that was implemented to highlight the empirical approach as the main finding was to move most of the discussion on the extended Ferrenti approach to the Supplementary.
-The extended Ferrenti approach was included because we wanted to remove the effect of practical considerations from the Ferrenti approach, however, this has no detectable effect on the predictions.
-The same features were recognized as important in the Ferrenti and extended Ferrenti approaches.
-Therefore, the presence of both in the discussion shadows the importance of the empirical approach.
-Hence, we have kept only the Ferrenti and empirical approaches to contrast them against one another.
-}
-
-%\begin{itemize}
- %   \item	Compare empirical to known input. Ferrenti reproduces expectations of literature. Main point is compare that to empirical which gives different result. 
- %   \item Actually, don’t get exactly what we expect from Ferrenti. Den vektlegger det vi forventer, men returnerer ikke eksakt kriteriene. E.g. band gap, ionic character. 
-%    \item Wnated to see if ML sees something else than the criteria we introduced. How does this compare to empirical?
- %   \item It is a nice start to begin with some general criteria.
-However, as pointed out, the usefulness is limited.
-The point is that we actually demonstrate that the Ferrenti approaches are not the best way.
-%    \item In some cases it might be useful to impose causality, to see to what extent that works.
-When we see that it does not work, we let the ML models figure out the connections between materials and QT.
-We had several hypotheses for why these materials are QT compatible, and therefore forced the causality to verify the assumption.
-When it did not work, we instead started from no assumptions, and let the ML methods reason out the causality.
-This proved much more efficient.
- %   \item Empirical is main result, Ferrenti is kind of test/validation/benchmark. Highlight more. 
-  %  \item Database of Ferrenti is commonly used, this is benchmark set of materials and information. Compare our method to benchmark. 
-   % \item We agree; Ferrenti not really useful 
-    %\item Ferrenti paper is data mining, not ML. We put it in to compare data 
-%\end{itemize}
-
+\pagebreak
 \noindent
@@
 
+\pagebreak 
 \noindent
@@
 
-\textit{Here ... }
+%\textit{Here ... }
 
@@
 
-\textit{Firstly, we would like to point out that the ML methods were not trained and applied to exactly the same data.
+\textit{Firstly, we would like to clarify that the ML methods were not trained and applied to exactly the same data.
 The criteria that were specified in the Ferrenti approaches left many materials without a label altogether.
-We trained the models on only the labeled data, and then performed machine learning on the unlabeled data, that had not been grouped at all.
-The data was hence divided into multiple portions, where some was in the test set, and some in the  training set.
-Therefore, the testing and training was not performed on the same data.
-For the empirical approach, we also put the unlabeled data from the Ferrenti approaches in the test set for ML.}
+In fact, several materials could not be labeled in the Ferrenti approaches because they did not fall into either of the two categories suitable and unsuitable. 
+The labeled data was divided into training and test sets, on which the training and validation of the ML algorithms were performed, and the machine learning to predict new candidate hosts was performed on unlabeled data.
+Therefore, the training, testing and predicting steps were all performed on different data.
+This process was repeated for all three approaches, and therefore they exhibit independent training and test data sets.}
+\textit{To clarify this point further we have added the following phrasing to the Data Mining section on page 4:} \\ 
+\mrk{The ML methods are trained using the training set and then evaluated on the test
+set. Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.} \\ 
+\textit{The notion is repeated on page 10 in the Predicting Suitable Material Hosts for Quantum Technology section:} \\ 
+\mrk{After training and validating the ML algorithms on the labeled datasets, the ML methods were applied to unlabeled
+data to obtain predictions for suitable QT host materials.}
 
-\textit{Secondly, the ML search does in fact not exactly reproduce the criteria set in the initial selection process.
-For the Ferrenti/Extended Ferrenti approaches, some of the properties we used to guide the labeling are recognized as important by the ML models (e.g., the band gap), but the selection criteria are not fully reproduced.
+\textit{Regarding the second point, a principal component analysis does indeed obscure the relationship between the trained machine learning models and the classification criteria.
+This is one of the reasons why we search for the optimal number of principal components, to observe if any components reveal more information regarding the features.
+Since all of the parameters from the initial classification criteria are present in the data, including several thousand features generated from Matminer's featurizers, we would still expect the band gap criterion to be absolute, and thus that it  would be reflected in both the optimal principal component model and the machine learning models.
+However, this is not the case, as the ML-models are achieving an almost perfect accuracy score during the cross-validation, which strengthens our belief  that there are other dimensions in the data that could explain this behavior.}
+\textit{Indeed, as also mentioned by the reviewer, the original Ferrenti criteria are not exactly reproduced by the ML methods.
+For the Ferrenti and extended Ferrenti approaches, some of the properties we used to guide the labeling are recognized as important by the ML models (e.g., the band gap), but the selection criteria are not fully reproduced.
 For example, many materials are suggested with band gaps below 0.5~eV in the Extended Ferrenti approach, whereas the selection criterion was set to 1.5~eV.
-Hence, the models are recognizing the expected properties as important, but there are differences from expectation.
-The ML models seem to be recognizing some pattern in the data that was not exactly anticipated.
 From a materials science perspective, it seems that the exact value of the band gap is not predominant, although the feature itself is important.
+Furthermore, bases on the criteria set by Weber et al.
+and Ferrenti et al.
+we expected covalent materials to dominate, but NaCl is predicted as suitable in the Ferrenti approach.
+The ML models will naturally weight the criteria differently from the specifications as they are not aware of the criteria, and seem to be recognizing some pattern in the data that was not exactly anticipated.
+We have attempted to emphasize this point in the revised version of the manuscript as also mentioned above, please see the response to the Editor's comment.
+The topic is discussed  in the following paragraph on page 11 in the Predicting Suitable Material Hosts for Quantum Technology  section:} \\
+\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.
+[8].
+Indeed, NaCl is predicted as a suitable candidate to minimum confidences of 0.83 and 0.61 for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.}  \\
+\textit{and in the Discussion section on page 13:} \\ 
+\mrk{Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in
+semiconductors.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for the Ferrenti approach encompasses features related to the band gap and chemical environment.
+This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
+The Ferrenti approach does not entirely reproduce the logic of the initial selection process, however, as several low band gap (< 0.5 eV) materials were highlighted as suitable by the ML methods.
+For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.}
+
+\textit{Thirdly, as mentioned above, a driving force behind selecting to report on the Ferrenti approaches was the comparison to the empirical one.
+The selection criteria for the Ferrenti approach were based on the general  expectations from the field.
+Hence, an analysis from the ML perspective on which features this would entail (i.e., from Matminer) was necessary to compare with the findings from the empirical approach, which consistute the main findings of this work.
+Finally, the agreement in predictions from the three approaches could lend weight to a prediction and merit further experimental studies.
+In other words, the Ferrenti approaches are used as a filter for the empirical one.
 }
 
-\textit{Finally, as mentioned above, a driving force behind selecting to report on the Ferrenti approaches was the comparison to the Empirical one.
-The literature generally expects the findings from the Ferrenti approach.
-Hence, an analysis from the ML perspective on which features this would entail (i.e., from Matminer) was necessary to compare with the findings from the Empirical approach - the main result of this work.
-Additionally, the agreement in predictions from the three approaches could lend weight to a prediction and merit further experimental studies.
-}
-
-\textit{Importantly, however, the above considerations were not sufficiently clear in the original version of the manuscript. Therefore, we have ... }
+\textit{Importantly, the above considerations were not sufficiently clear in the original version of the manuscript.
+Therefore, we have tried to make these three points more clear in the overall text.
+Furthermore, the removal of the extended Ferrenti approach from the main text should hopefully also clarify the juxtaposition of the Ferrenti and empirical approaches.
+Please also see the response to the Editor above and the accompanying changes to the manuscript.}
 
@@
 In addition, NaCl is excluded from being labeled as unsuitable from the criteria due to its nonmagnetic label in Materials Project.
-We agree that it is not neccessarily clear that either Ferrenti or extended Ferrenti critera would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process that constitutes the criteria in the data mining.
-Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti alltogether predicts the material as suitable.}
-
-\textit{The following note was added to this effect on page 11:} \\ 
-\mrk{Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the test set.
+We agree that it is not necessarily clear that either the Ferrenti or the extended Ferrenti approaches would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process.
+Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti altogether predicts the material as suitable.}
+\textit{The following note was added to this effect on page 11 in the Predicting Suitable Material Hosts for Quantum Technology section:} \\ 
+\mrk{Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the unlabeled dataset.
 For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
 }
-
-\textit{Argument for Ferrenti}
 
@@
 We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
-This is an improvement that could be made to our method in a further work.}
+This is an improvement that could be made to our method in future studies.}
 
@@
 The following sentence was added to the Data Mining section on page 5 to clarify the part about ferromagnetic ordering: } \\
-\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the present criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
+\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
 
@@
 Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
-As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our data set.}
-
-\mrk{MP includes larger structures of the same material.
-We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our dataset.
+Furthermore, MP contains structures of varying sizes for the same material.
+We have included all structures and materials from the Materials Project, but we have not checked which materials are represented as a larger cell in our data.
 We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
-This is an improvement that could be made to our method in a further work.}
-
-%As noted, we are in fact mainly probing ferromagnetic ordering in our criteria.
-This was not sufficiently clear in the original manuscript but has been remedied in the revised version, see the following sentence on page …: Exploring larger cells was not done as the links between small and large cells of the same material in MP is not always clear.
-Therefore, this is an improvement that could be made to our method in a further work.
-This aspect has now been highlighted in the manuscript on page …
+This is an improvement that could be made to our method in a future study.}
 
@@
 Moreover, it is likely that the discovery of single photon emission and spin manipulation for the NV center in diamond has also guided the search for similar properties in other materials, with the search commencing with similar materials to diamond, such as different polytypes of SiC.
-The criteria of Weber \textit{et al.} (Ref.~[8] of the main text) are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable.
+The criteria of Weber et al.
+(Ref.~[8] of the main text) are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable.
 The recent discovery of telecom compatible SPEs in Si (Refs.~[54-55] in the main text), a lower band gap material, show that this may have been a premature assumption.
 We hope that our work can contribute to widening the search for quantum compatible semiconductor platforms.
-A discussion on this has now been added to the Discussion section on page 16: } \\ 
-\mrk{One should note that there is a certain degree of bias inherent to the data set labeled in the empirical approach.
-Firstly, experimental searches will always be limited by the availability and cost of materials and processing.
-Secondly, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
-However, the broad range of materials predicted and listed in Table~III and the Supplementary Information at [39] indicates that the ML methods are detecting underlying properties which manifest in materials systems of several kinds.
+A discussion on this has now been added to the Data Mining section on page 7: } \\ 
+\mrk{Note that there is some potential for inherent bias in the dataset, in part due to experimental work being limited by the availability and cost of materials and processing.
+Moreover, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
 }
@@
 This ID is included in the AFLOW, AFLOW-ML, JARVIS-DFT and OQMD databases as well.
-
-Due to the various different techniques of approximating the bandgap, either demonstrated experimentally or estimated using the DFT-calculations with the functionals PBE or PBE+U, we do not choose one but rather let them all be represented as columns (features) in our data.}
+Due to the various different techniques of approximating the bandgap, either demonstrated experimentally or estimated using the DFT-calculations with the functionals PBE or PBE+U, and as we do not exactly know which method is most accurate, we do not choose one but rather let them all be represented as columns (features) in our data.
+%We believe information from other databases should be handled as supplements rather than choosing one. 
+We note that other approaches to this issue  exist, such as letting the same material be represented as two entries (rows) in our data but with different values for the same property.
+However, such replications could substantially increase the size and complexity of the current experiment, while not necessarily resulting in any credible benefits.}
 
@@
 This ID is included in the AFLOW,  AFLOW-ML, JARVIS-DFT and OQMD databases as well.
-If two different databases have different values for the same property, such as the band gap, we added both of them as columns (features) to our data to avoid any data cluttering.
-An additional analysis to uncover any difference in space groups reported from Materials Project and the other databases, where we had an average match of $97 \ \%$, which is close to an ideal match.
+If two different databases contain different values for the same property, such as the band gap, we added both of them as columns (features) to our data to avoid any data cluttering.
+An additional analysis was performed to uncover any differences between the space groups reported in the Materials Project and the other databases, yielding an average match of \SI{97}{\percent}.
 We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
@@
     \textit{This phrase has now been replaced by the following;} \\ 
-    \mrk{Complex structures (e.g., nanostructures or 2D materials)}.  
+    \mrk{complex structures (e.g., nanostructures or 2D materials)}. 
     \item The authors use the “.” as the notation to represent both the decimal point and the separator for thousands in large numbers (e.g.
@@
     \textit{Response}: \\
-    \textit{Thank you for pointing out this oversight. This has now been remedied according to the referee's suggestion. } 
+    \textit{Thank you for pointing out this oversight.
+    This has now been remedied by using the \texttt{siunitx}-package in \LaTeX, which uses a shortened space character to separate thousands.
+    }
+    % This has now been remedied according to the referee's suggestion. } 
     \item The authors should note that AFLOW also uses PBE+U in some calculations as described in Ref. 24 of this work, particularly for materials taken from the ICSD. \\
     \textit{Response:} \\ 
-    \textit{Thank you for pointing this out, we have now added the detail to the description of AFLOW in our Methods section; \mrk{with the $+U$ correction}.}
+    \textit{Thank you for pointing this out, we have now added the detail to the description of AFLOW in our Methods section;} \mrk{(with the $+U$ correction for certain cases)}. 
     \item Finally, the article also contains a lot of repetition, making it unnecessarily long.
@@
 Superfluous information has been removed from the main text and in some cases moved to the Methods section.
-The paper is now shorter by a full page.} \\
+The paper is now shorter by two full pages.} \\
     \textit{Regarding the “Comparing the approaches” subsection, we agree that there were many repetitions, which have now been removed.

### 2022-06-10 revision/revised-paper_marked-up.tex
Updates from Overleaf

@@
 \newcommand{\mrk}[1]{\textcolor{red}{#1}}
+\usepackage[useregional]{datetime2}
 
@@
 Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, searching these databases to find promising candidate materials for quantum technology applications
-is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \mrk{$25,000$} materials and nearly $5000$ physics-informed features.
-Three approaches were devised, named the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
-We find that of the three, the empirical approach relying exclusively on findings from the literature predicted substantially fewer candidates than the other two approaches with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to expectations from the literature and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
+However, searching these databases to find promising candidate materials for quantum technology applications is a major challenge. 
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \mrk{\num{25000}} materials and nearly \num{5000} physics-informed features.
+\mrk{Three different approaches were devised} to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting. 
+We find that \mrk{among these, the} empirical approach relying exclusively on findings from the literature \mrk{exhibited the clearest  distinction}  between \mrk{predicted} suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+In contrast to expectations from the literature  %and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, 
+\mrk{focusing on band gap and ionic character as important features for QT compatibility,}  
+the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
@@
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex and high-dimensional scientific problems.
-%that are beyond the capability of existing high-performance computing %facilities.   
 Recent advances have highlighted the potential of quantum information processors to outperform state-of-the art high-performance computing facilities.
-Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \mrk{$200,000$} core supercomputer \cite{Arute_2019}.
+Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \mrk{\num{200000}} core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
@@
 
-Here we provide a framework for the data mining and automated discovery of promising \mrk{semiconductor hosts for QT} using targeted database search and ML methods combined with knowledge from the field.
+\mrk{Herein, a framework is provided} for the data mining and automated discovery of promising \mrk{semiconductor hosts for QT} using targeted database search and ML methods combined with knowledge from the field.
 Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training and testing, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
-In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
-The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data are available.
-
-The developed procedure relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
-The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
+\mrk{This framework does not} distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
+The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data \mrk{is} available.
+
+The developed procedure relies on data extraction \mrk{from different databases and the subsequent featurization of the data.} 
+%from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+%The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data. 
 An important aspect of \mrk{the} work is the database building and pertinent development of the datasets for the ML methods.
 \mrk{Three different approaches to data mining were devised}: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
-\mrk{The} two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
+\mrk{The} two first \mrk{data extraction protocols are based on} broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
 The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding \mrk{$47$} predicted candidates that were common between all approaches and ML methods.
-Example materials \mrk{among the predictions} include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
-Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
+Example materials \mrk{among the predictions} include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP. Focused theoretical and experimental studies 
+%, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, 
+\mrk{are needed} to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials. 
 %Write better! 
@@
 \subsection*{Information Flow} 
-
 The information stream in this work can be regarded as many inter-connected modular parts. 
@@
     \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
-    To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
+    To limit the memory and computational usage, the data \mrk{is} partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
 This process is repeated iteratively until all the data has been featurized.
@@
 
-The conditions for the initial MP query are that the materials must derive from the Inorganic Crystal Structure Database (ICSD) and have a band gap wider than $0.1$~eV to exclude metallic compounds.
+The conditions for the initial MP query are that the materials must derive from the Inorganic Crystal Structure Database (ICSD) and have a band gap wider than \SI{0.1}{\electronvolt} to exclude metallic compounds.
 The ICSD is the world's largest database for completely identified inorganic crystal structures  \cite{Allen1987,Zagorac2019}.
-In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the databases OQMD  \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
+In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the \mrk{following databases: the Open Quantum Materials Database (OQMD)}  \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
 The results of these steps are combined into a dataset for further analysis.
 
-After material extraction we apply tools from the open-source library Matminer \cite{Ward2018} to generate thousands of features from the data.
+After material extraction \mrk{tools from the open-source library Matminer \cite{Ward2018} were applied} to generate thousands of features from the data.
 We will refer to this process as featurization.
@@
 The constructed dataset encompasses compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
-Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
-Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
-Unfortunately, if an error has \mrk{occurred} in the first part of the process, the error \mrk{is carried along} and will get increasingly harder to detect.
-Thus, \mrk{the} results depend on the quality of data in the \mrk{employed} databases.
+Furthermore, \mrk{the extracted data was}  obtained from high-throughput density functional theory calculations.
+Indeed, there are possible errors associated with every step, starting from an initial calculation, \mrk{adding of data in the database, featurization and preprocessing the data, data mining and labeling, and finally training a model and making a prediction.}  Unfortunately, if an error \mrk{occurrs} in the first part of the process, \mrk{it will be  carried along and get} increasingly harder to detect.
+Thus, \mrk{the output strongly depends}  on the quality of data in the \mrk{employed} databases.
 
 \subsection*{Data Mining}
-The complete dataset consists of \mrk{$25,000$} materials.
+The complete dataset consists of \mrk{\num{25000}} materials.
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training and test sets for the ML methods.
-\mrk{The ML methods are trained using the training set and then evaluated on the test set.}
-\mrk{Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.}
+The labeled data \mrk{is} then grouped into training and test sets for the ML methods.
+\mrk{The ML methods are trained using the training set and then evaluated on the test set.
+Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.}
 
@@
 The strategy for selection of unsuitable candidates is thus that the negation of the criteria \mrk{used} to select suitable candidates should give unsuitable candidates.
-A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates\mrk{, resulting in} skewed data sets \mrk{with} fewer unsuitable than suitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates\mrk{, resulting in} skewed datasets \mrk{with} fewer unsuitable than suitable candidates.
 This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
@@
     \begin{itemize}
-        \item contain elements with more than $50 \ \%$ natural abundance of spin zero isotopes,
-        \item crystallize in non-polar space groups,
-        \item are present in the ICSD\mrk{,} 
-        and
-        \item are calculated to be nonmagnetic. 
+        \item contain elements with more than \SI{50}{\percent} natural abundance of spin zero isotopes,
+        \item crystallize in non-polar space groups, \mrk{are calculated to be nonmagnetic, and 
+        are present in the ICSD.}
     \end{itemize}
@@
     \end{itemize}
-    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional.
-The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations.
-    \item Ensure that the energy above hull is less than $0.2$~eV per atom.
+    \item Include only materials with a band gap larger than \SI{0.5}{\electronvolt} calculated using DFT and the PBE functional.
+    The value of \SI{0.5}{\electronvolt} was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
+    \item Ensure that the energy above hull is less than \SI{0.2}{\electronvolt} per atom.
 \end{enumerate}
 
-These inclusion criteria are based on the work of \citeauthor{Weber2010} \cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
+\mrk{The} inclusion criteria are based on \mrk{Ref.}~\cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
 In this context, long spin coherence times are needed, \mrk{necessitating an environment that can be depleted of nuclear spins and permanent magnetism.}
@@
 
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the \mrk{ICSD} that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors).
-The resulting set of labeled materials contains $1581$ materials where $35 \ \%$
-are labeled as unsuitable and 
-$65 \ \%$ as suitable for QT applications, \mrk{evidencing that} 
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the \mrk{ICSD} that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than \SI{0.1}{\electronvolt} in the MP database (to exclude metals but include lower-band gap semiconductors).
+The resulting set of labeled materials contains $1581$ materials where \SI{35}{\percent}
+are labeled as unsuitable and \SI{65}{\percent} 
+as suitable for QT applications, \mrk{evidencing that} 
 %Here we see the first example of how 
-the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
-
-\mrk{Performing machine learning on a data set derived using preconceived notions for which material properties are important is likely to reproduce several of the initial selection criteria.
-Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the other approaches.
-Additionally, one should note that ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.}
+the criteria for labeling unsuitable candidates are more restrictive than those for the suitable \mrk{ones}.
+
+%Ferrenti 
+\mrk{Considering the materials present in the labeled dataset of the Ferrenti approach more closely, we find that diamond is classified as a suitable candidate, in good agreement with experimental observations.
+Interestingly, carbon in two-dimensional graphite-like structures are marked as suitable as well.
+All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
+Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.}
 
@@
         \item crystallize in non-polar space groups,
-        \mrk{are present in the ICSD,
-        and are calculated to be nonmagnetic.} 
+        \mrk{are calculated to be nonmagnetic and are present in the ICSD} 
     \end{itemize}
-    \item Only keep materials that have a band gap larger than $1.5$~eV in the MP database.
+    \item Only keep materials that have a band gap larger than \SI{1.5}{\electronvolt} in the MP database.
 The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid labeling an unfeasibly large number of materials.
-    \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
+    \item Ensure that the energy above hull is less than \SI{0.2}{\electronvolt} per atom. 
 \end{enumerate}
@@
 For \textbf{unsuitable} candidates, \mrk{the same strategy as for the Ferrenti approach was implemented}.
-The result is \mrk{an} unbalanced set of labeled materials with up to $75 \ \%$ of the materials found in the suitable group \mrk{and $78 \ \%$ more materials than for the Ferrenti approach.}
-%However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
+The result is \mrk{an unbalanced set of labeled materials that is   \SI{78}{\percent} larger than for the Ferrenti approach and having $\sim$\SI{75}{\percent} of the materials found in the suitable group.}
 
@@
 Qualitative conclusions drawn for the Ferrenti approach herein also hold for the extended Ferrenti approach, indicating that the removal of so-called practical considerations did not have a significant impact on the results.
+Nonetheless, predictions from the extended Ferrenti approach will be employed below to contrast with and filter the findings from the empirical approach.
 }
@@
 \subsubsection*{The empirical approach} 
-%The third approach differs substantially from the others in terms of material labeling, as 
 \mrk{In the \emph{empirical approach},} we apply knowledge from the field (see for instance  Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to \mrk{guide the search for} promising material \mrk{hosts.}
@@
     \begin{tabular}{c|c|c|c}
-    Material & Band gap (eV) & Defect candidates & References \\
+    Material & Band gap (\si{\electronvolt}) & Defect candidates & References \\
     \hline
@@
     (2D) \textit{h}-BN & $6.0$ & Unidentified defects & \cite{Tran_2016,Tran_2016b,Hayee_2020} \\ 
-    (2D) MoS$_2$, WSe$_2$, WS$_2$ & $<2.5$~eV & Bound excitons & \cite{Toth2019} \\
+    (2D) MoS$_2$, WSe$_2$, WS$_2$ & $<2.5$ & Bound excitons & \cite{Toth2019} \\
     ZnO & $3.4$ & Unidentified defects & \cite{Morfa2012} \\ 
-    ZnS & $3.6$ (zincblende) & Unidentified defects & \cite{Stewart2019} \\ 
+    ZnS (zincblende) & $3.6$ & Unidentified defects & \cite{Stewart2019} \\ 
     GaAs & $1.4$ & Quantum dots & \cite{Bluhm2010} \\ 
@@
 
-After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
-These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than $0.5$~eV.
-\mrk{All of the $202$ structures are included apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
-}
-
-Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
-For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project \mrk{were admitted.} Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$~eV) among the data.
+After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than \SI{0.4}{\electronvolt}.
+These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than \SI{0.5}{\electronvolt}.
+\mrk{All of the $202$ structures were included in the labeled dataset apart from C (mp-$568410$) which is a metal according to AFLOW-ML. }
+
+\begin{figure}[t] %!htp
+    \centering
+    \begin{subfigure}{1\textwidth}
+        \centering
+        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
+    \end{subfigure}
+    \begin{subfigure}{1\textwidth}
+        \centering
+          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
+    \end{subfigure}
+    \caption{Parallel coordinate plots for the two different approaches. \mrk{To limit data cluttering up to $250$ entries for each class were randomly collected.}  
+    %For the empirical approach, we have used all the $187$ suitable candidates. 
+    The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}
+    \label{fig:parallel-coordinates-approaches}
+\end{figure}
+
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ \mrk{were} manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
+For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the \mrk{MP} \mrk{were admitted.} Additionally, we find several two-dimensional structures of carbon with a large band gap (\mrk{$>\SI{1.5}{\electronvolt}$}) among the data.
 \mrk{These were added} as suitable candidates.
@@
 For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
-Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, \mrk{only two-dimensional structures were admitted}.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML methods that are applied in a later stage.
+Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, \mrk{only two-dimensional structures were admitted.
+Other non-matching structures were moved to the test set to see whether or not they are predicted as suitable by the ML methods applied in a later stage}.
 
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-\mrk{Note} that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of $0.5$~eV.
+\mrk{Note} that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of \SI{0.5}{\electronvolt}.
 
 Following the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set.
-Notably, the candidates labeled as suitable in the empirical approach contain only compounds that are either elementary (unary) or binary. 
-Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, \mrk{$400$ materials were added and labeled as \textbf{unsuitable}}.
+\mrk{Notably, only elementary (unary) and binary materials are labeled as suitable in the empirical approach.} \mrk{To complete the dataset, $400$ materials were added and labeled as \textbf{unsuitable}}.
 These \mrk{were} picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
+
+\mrk{Note that there is some potential for inherent bias in the dataset, in part due to experimental work being limited by the availability and cost of materials and processing.
+Moreover, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
+%However, the broad range of materials predicted and listed in Table~\ref{tab:materialproperties} and the Supplementary Information at \cite{supplementary} indicates that the ML methods are detecting underlying properties which manifest in a broad range of material systems.
+}
 
@@
 
-%Ferrenti 
-\mrk{Considering the materials present in the labeled datasets of the Ferrenti approach more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate}, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}).
-Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
-All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.  
-%Extended Ferrenti - moved 
-%In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), there is a more sparse representation of each known chemical formula present in the labeled data.
-
-\mrk{The labeled data for the Ferrenti and empiricial approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+\mrk{The labeled data for the Ferrenti and empirical approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for \mrk{selected} features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
 
-\begin{figure}[t] %!htp
-    \centering
-    \begin{subfigure}{1\textwidth}
-        \centering
-        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
-          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
-    \end{subfigure}
-    \caption{Parallel coordinate plots for the two different approaches.
-To limit data cluttering, we have randomly collected up to $250$ entries for each class.
-For the empirical approach, we have used all the $187$ suitable candidates.
-The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}
-    \label{fig:parallel-coordinates-approaches}
-\end{figure}
-
 \begin{figure}%[h] %!tbp
@@
     \end{subfigure}
-    \caption{Two-dimensional scatter plots for the two different approaches.
-We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, we have transformed the sets of labeled data resulting from the two approaches and visualized them as scatter plots.
-Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the right panel, and red triangles represent unsuitable candidates.}
+    \caption{Two-dimensional scatter plots for the \mrk{Ferrenti and empirical} approaches.
+\mrk{The eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix were identified}, that is, the two most important principal components of the initial data from the Materials Project query.
+Then, \mrk{the labeled datasets were transformed and visualized as 2D scatter plots.} Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols \mrk{for the empirical approach}, and red triangles represent unsuitable candidates.}
     \label{fig:2dscatterplotpca}
@@
 
-\mrk{The Ferrenti approach and the extended Ferrenti approach share several similarities with entries that span roughly the same dimensions (not shown).} 
+%\mrk{The Ferrenti approach and the extended Ferrenti approach share several similarities with entries that span roughly the same dimensions (not shown).} 
 %For example, the entries in  Figure~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
 %Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-The most striking difference is found for the empirical approach.
-\mrk{The entries labeled as suitable candidates do not exhibit any magnetization, which is also the case for the Ferrenti approach, but now the materials crystallize in both polar and non-polar space groups.} Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for \mrk{the former one.}
-Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-In the empirical approach the polarity of the material's space group may be less important compared to the \mrk{Ferrenti approach}, while the accepted values for ionic character and covalent range appear more restricted (Fig.~\ref{fig:parallel-coordinates-approaches}).
-
-\mrk{To illustrate the composition of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.
-PCA was applied to the labeled datasets in order to reveal specific features that stand out.} In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
+%The most striking difference is found for the empirical approach. 
+\mrk{Several differences are observed between the Ferrenti approach and the empirical approach to data mining.
+While neither case passes materials that exhibit magnetization through as suitable, suitable candidates can crystallize in both polar and non-polar space groups in the empirical approach.} Moreover, \mrk{the ranges}  of covalent radius and maximum ionic character span a substantially smaller parameter space \mrk{for the empirical approach than for the Ferrenti approach (see Fig.~\ref{fig:parallel-coordinates-approaches})}.
+%Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance. 
+%In the empirical approach the polarity of the material's space group may be less important compared to the \mrk{Ferrenti approach}, while the accepted values for ionic character and covalent range appear more restricted .
+\mrk{Overall, there seems to be greater overlap in the distributions in material properties for suitable and unsuitable candidates in the case of the Ferrenti approach as compared to the empirical one.}
+
+\mrk{To reduce the dimensionality of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.} In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
 We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the MP database, and transform the three labeled datasets according to the corresponding two eigenvectors.
-In essence, we reduce the dimensionality of the labeled data in order to visualize them.
-The result of this procedure is displayed in the scatter plots of Fig.~\ref{fig:2dscatterplotpca}.
-Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of removing the mean and scaling to unit variance.
+The result of this procedure is displayed in the scatter plots of \mrk{Figure}~\ref{fig:2dscatterplotpca}.
+Note that some minor differences between the \mrk{approaches} may occur due to the process of removing the mean and scaling to unit variance.
 Red triangles represent unsuitable candidates while \mrk{otherwise} colored symbols (green, blue, black and yellow) represent suitable candidates.
@@
 Hence, using \mrk{this approach} for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-We therefore expect that the \mrk{Ferrenti approach} could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
-
-In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable candidates (green, blue, yellow and black symbols), while the unsuitable candidates (red triangles) are similarly restricted to the lower right corner, albeit with some exceptions.
+We therefore expect that the \mrk{Ferrenti approach} could need supplementary dimensions for further distinguishing between the materials in the two categories\mrk{.} 
+%, or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
+
+In the case of the empirical approach, on the other hand, \mrk{a clear trend can be discerned} where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable  %(green, blue, yellow and black symbols),
+\mrk{candidates while the unsuitable ones} are similarly restricted to the lower right corner, albeit with some exceptions. 
 Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
-This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
+This \mrk{strongly indicates that the empirical approach may be capable of separating materials based on their underlying properties, emphasizing the importance of having a logical framework for the data mining process}.
+%Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
 
@@
 
-\subsection*{Machine learning and principal component analysis}
-\mrk{Four well-tested ML algorithms were applied to the labeled data} to classify specific materials as candidate systems for QT.
-These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four ML methods were applied to the labeled data sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
-
-In order to reduce the dimensionality while preserving most of the variance in the data, 
-\mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
-Next, in the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+\subsection*{Machine Learning and Principal Component Analysis}
+\mrk{Four well-tested ML algorithms were applied to the labeled data} to classify specific materials as candidate systems for QT\mrk{, yielding multiple sets of predicted candidates.
+The ML methods employed herein} are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
+%These four ML methods were applied to the labeled datasets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
+%\mrk{To} reduce the dimensionality while preserving most of the variance in the data, \mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+\mrk{Principal component analysis was again performed, but now on the three training sets separately}\footnote{In the main text we discuss the Ferrenti dataset and the empirical one.
+The corresponding results for the extended Ferrenti set are listed in the supplementary material.}
+% \mrk{A principal component analysis was performed where first the} 
+% eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in \mrk{distinct PCA models for each data labeling approach}
+(as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model). 
+Next, in the evaluation of the \mrk{ML methods we}  
+%for the three different approaches 
+apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
 \mrk{Note} that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four \mrk{ML} methods are shown in the Supplementary Information \cite{supplementary}.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four \mrk{ML} methods are shown in the Supplementary Information \mrk{at} \cite{supplementary}.
 The \mrk{data labeling approaches} define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
@@
 This differs from Fig.~\ref{fig:2dscatterplotpca}, where \mrk{the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown}.
-Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all the data}.
-Here, the ML analysis is done on the labeled data for each approach.
-For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
+%Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all the data}. Here, the ML analysis is done on the labeled data for each approach. 
+For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the \SI{95}{\percent} accumulated explained variance, a total of $144$ principal components must be included.
 \mrk{In the case of the empirical approach and in contrast to the Ferrenti approach}, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
@@
     \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
-Note that in (a) we visualize only the results of the PCA analysis while in (b) there are results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
+\mrk{Note that in (a) only the results of the PCA analysis are visualized, while (b) contains} results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
 The latter shows that for the empirical approach most of the physics is represented by a few features.
@@
 
-Figure~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+\mrk{Fig.}~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 The trend is maintained for all four ML methods (see the Supplementary Information at \cite{supplementary}).
-Moreover, by selecting the highest values in this eigenvector, we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
+\mrk{By selecting the highest values in this eigenvector we} find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
 The second most important principal component for the Ferrenti approach exhibits significant contributions from the covalent radius, the ionic character and the packing efficiency among the elements in the composition.
-The data originates from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
+The data originate from elemental calculations from MagPie and are aggregated as either minimum, mean, standard deviation, or maximum. 
 While the first principal component encompasses the largest explained variance, it does not provide a clear and specific information on which features it represents.
@@
 %extended Ferrenti 
-\mrk{Note that the} interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
+%\mrk{Note that the} interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
@@
 The empirical approach differs in many aspects from the Ferrenti \mrk{approach}. 
-Firstly, \mrk{the} number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
-Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
+Firstly, \mrk{the} number of principal components necessary to obtain \SI{95}{\percent} variance is reduced to \mrk{$103$ from $144$}. 
+%and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively. 
+Thus, the variance of the training set \mrk{is} described with fewer principal components, indicating a simpler model.
 Secondly, the first principal component is by far the most important feature for all ML methods in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
@@
 The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
-Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach. 
+Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is \SI{21}{\percent}, \mrk{compared to} \SI{14}{\percent} for the Ferrenti approach. 
 % and $11 \ \%$ for the extended Ferrenti approach. 
@@
 Indeed, precisely these features were used as guidance in the data labeling process.
-\mrk{Thus, the ML methods seem to be perpetuate the criteria imposed in the Ferrenti approach to some extent, and return the initial assumptions on which material properties may be important for QT.
-The ML methods may, however, still be recognizing other patterns than those originally intended in the data selection process.} \mrk{For the empirical approach, on the other hand, the selection process was not guided in terms of specific properties.} Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In the empirical approach, the ML methods appear to be inferring that the common trend among the materials that are known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+\mrk{Thus, the ML methods seem to perpetuate the criteria imposed in the Ferrenti approach at least to some extent.
+They may, however, still be recognizing other patterns than those originally intended in the data selection process.} \mrk{For the empirical approach, on the other hand, the selection was not guided in terms of specific properties.} Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In the empirical approach, the ML methods \mrk{are recognizing more complex mechanisms in the crystal structure and bonding as common trends among materials that are suitable for QT applications}.
 
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology}
-After training the ML algorithms using parts of the data labeled during the \mrk{data mining process}, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in  Table~\ref{tab:probabilites}.
-
-\subsubsection*{The Ferrenti approach}
-
-From the predicted dataset of $23.623$ materials  
-%the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach. 
-all four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
-We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with \mrk{complex structures (e.g., nanostructures or 2D materials)} to be labeled as suitable candidates.
-Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than $0.5$~eV were eliminated.
-This trend is not carried over to the predicted data. Indeed, \mrk{many} entries with band gaps lower than $0.5$~eV are predicted as suitable candidates by all four ML methods employed herein 
-%indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
---- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
-\mrk{This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.}
-On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
-
-\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
-Indeed, NaCl is predicted as a suitable candidate to minimum confidences of $0.83$ and $0.61$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
-Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the test set.
-For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
-}
-
-\begin{table}[t]
+
+\begin{table}[b]
     \centering 
@@
 
+%After training the ML algorithms using parts of the data labeled during the \mrk{data mining process}, the ML methods were employed on the test sets. 
+\mrk{After training and validating the ML algorithms on the labeled datasets, the ML methods were applied to unlabeled data to obtain predictions for suitable QT host materials.} 
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary}\mrk{.} %for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}\mrk{for the Ferrenti, extended Ferrenti and empirical approaches.
+Note that the Ferrenti approaches are employed as a filter on the predictions of the empirical one.}
+
+\subsubsection*{The Ferrenti approach}
+
+From the predicted dataset of \mrk{\num{23623}} materials  
+%the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach. 
+all four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
+We find that \mrk{the} ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
+This can allow materials with \mrk{complex structures (e.g., nanostructures or 2D materials)} to be labeled as suitable candidates.
+Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than \SI{0.5}{\electronvolt} were eliminated.
+This trend is not carried over to the predicted data.
+Indeed, \mrk{many} entries with band gaps lower than \SI{0.5}{\electronvolt} are predicted as suitable candidates by all four ML methods employed herein
+%indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
+--- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
+\mrk{This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.}
+On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
+
+\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
+Indeed, NaCl is predicted as a suitable candidate to minimum confidences of $0.83$ and $0.61$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the unlabeled dataset.
+For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
+}
+
 %\subsubsection*{The extended Ferrenti approach}
@@
 %Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
-Note that $51$ of these have a band gap of $0.5$~eV or smaller as reported in Materials Project \cite{Jain2013,Jain2018} from PBE-level DFT calculations.
+Note that $51$ of these have a band gap of \SI{0.5}{\electronvolt} \mrk{or smaller}.
 Increasing the threshold to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
@@
     \includegraphics[width=0.85\textwidth]{AllFigures/fig6-all.png}
-    \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to.
+    \caption{\mrk{Example illustrations} of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence\mrk{,} belong to.
 Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
@@
 
-Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the ML methods recognize BN as a suitable candidate with high probability.
-Furthermore, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) have been predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
-The two compounds of CdSe share similar properties with calculated band gaps in the MP database of $0.5$~eV and $0.6$~eV, respectively.
+%Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the ML methods recognize BN as a suitable candidate with high probability.
+\mrk{Turning to each of the individual material predictions, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) are predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.}
+The two compounds of CdSe share similar properties with calculated band gaps in the MP database of \SI{0.5}{\electronvolt} and \SI{0.6}{\electronvolt}, respectively. 
+\mrk{The compound BN (mp-$1639$) was also predicted as suitable possibly due to a different BN crystal structure being present in the training set and labeled as a suitable candidate}.
 
@@
 The former takes on a polar space group while the latter does not.
-The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
-Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-Importantly, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
+The band gaps are listed as \SI{1.9}{\electronvolt} and \SI{1.7}{\electronvolt}, respectively, in the MP database.
+Both structures \mrk{exhibit a} strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+\mrk{Interestingly}, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
 By creating a boron vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
@@
 
-The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
+The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of \SIlist{0.3;1.2;1.2;1.7}{\electronvolt}, respectively.
 To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, while self-assembled InAs quantum dots are  exciting possible materials to use in quantum technology \cite{Liu2018}. 
 CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the dataset than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
-The prediction of CuI in two configurations indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
+Interestingly, the material exhibits a large ionic character
+\mrk{and shares few similarities with known QT compatible hosts such as, e.g.,} Si, SiC and  diamond.
+The prediction of CuI in two configurations \mrk{thus} indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
 It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
-NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach}.
+%NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach}.
 %This underlines that an empirical approach, based on experimental data, may be more suitable for predicting materials for a certain applications and understanding the underlying mechanisms than the assumption-based methodology.}
@@
 For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
-Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
-In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
-ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of \SI{1.2}{\electronvolt} \cite{Zhang2015} as reported in the MP database.
+In comparison, the experimentally reported band gap is somewhat larger at \SI{2.0}{\electronvolt} \cite{Xing1989}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits  \mrk{covalent bonding} and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
@@
     \centering 
-    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$) and the $6$ materials predicted by all approaches ($>0.75$).
-Compounds marked by an asterisk are predicted to be unstable to transformation into other phases in the MP database.
+    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach \mrk{($>0.85$ confidence) and the $6$ materials predicted by all approaches ($>0.75$ confidence).} %Compounds marked by an asterisk are predicted to be unstable to transformation into other phases in the MP database.
     }
     \begin{tabular}{c|c c c c c c c }
-      & Material & Crystal structure & MP code & Density (g/cm$^3$) & Band gap (eV) & a, b, c (\AA) & $\alpha,\beta,\gamma$ ($^\circ$) \\
+      & Material & Crystal structure & MP code & Density (g/cm$^3$) & Band gap (\si{\electronvolt}) & a, b, c (\AA) & $\alpha,\beta,\gamma$ ($^\circ$) \\
     \hline 
@@
 
-Among the $66$ materials that all ML methods in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
-The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
-Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
-Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
+Among the \mrk{list of $66$ we also highlight the predictions} of interesting materials like \mrk{Ge, sharing many characteristics with Si and C in addition to the periodic column number,  %(in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$),
+GeC, BP and InP.}  
+%The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number. 
+%Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
+\mrk{Much} like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.  
 Similar considerations could be made for the case of GeC. 
-Data from the MP database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
+Data from the MP database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of \SI{1.8}{\electronvolt}. 
 Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities with SiC. 
-Next, the compound BP (mp-$1479$ and mp-$1008559$) is present in \mrk{the} predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at $1.5$~eV and $1.1$~eV, respectively.
+Next, \mrk{BP} (mp-$1479$ and mp-$1008559$) is present in \mrk{the} predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at \SI{1.5}{\electronvolt} and \SI{1.1}{\electronvolt}, respectively.
 Both configurations of BP are nonmagnetic, non-toxic and BP has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
-Lastly, InP (mp-$966800$) was also predicted as a suitable candidate to $0.75$ confidence.
-The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
-InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-\mrk{The possibility of using InP-based quantum dots for QT applications should be considered.}
-
-\mrk{All} ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+Lastly, InP (mp-$966800$) 
+%was also predicted as a suitable candidate to $0.75$ confidence. The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra. 
+\mrk{in the hexagonal structure} 
+is reported in the Materials Project to have a direct band gap of \SI{0.5}{\electronvolt} and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
+\mrk{The possibility of using InP-based quantum dots for QT applications should therefore be considered.}
+
+%\mrk{The} ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
 \mrk{However, almost} all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, \mrk{only a single material is present in the list of $66$ candidates predicted by the four ML methods} in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a $2.0$~eV band gap and decomposes to a similar MgSe configuration.
+Among these, \mrk{only a single material is present in the list of $66$ candidates predicted by the four ML methods} in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a \SI{2.0}{\electronvolt} band gap and decomposes to a similar MgSe configuration.
 %The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported at $2.45$~eV (optical band gap) \cite{Ubale2014}. 
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010}\mrk{.}  
+%and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}. 
 We note that these properties may favor defects acting as spin centers with qubit potential and MgSe is thus identified as an interesting host material in this regard.
@@
 \mrk{The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
-The same cannot be said for the Ferrenti (and extended Ferrenti) approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible\mrk{,} and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
-
-Despite notable differences, as mentioned above, there is \mrk{some overlap of predicted materials between the approaches}. 
+The same cannot be said for the Ferrenti approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible\mrk{,} and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+
+Despite notable differences, as mentioned above, there is \mrk{overlap of predicted materials between the approaches}. 
 %We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach.
@@
 %histograms 
-\begin{figure}[ht]
+\begin{figure}[t]
     \begin{subfigure}[b]{1\textwidth}
@@
 \end{subfigure}
-\caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
+\caption{Histograms of predicted suitable materials as a function of the (a) \mrk{band gap}, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
 The total number of predicted materials is  $6804$ for the Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
+The Ferrenti \mrk{approach refers} to the left $y$-axis and the empirical approach to the right.
 }
@@
 \section*{Discussion}
+
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
@@
 %In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process. 
-\mrk{The Ferrenti approach does not entirely reproduce the logic of the initial selection process however as many low band gap materials were highlighted as suitable by the ML methods. } 
+\mrk{The Ferrenti approach does not entirely reproduce the logic of the initial selection process, however, as several low band gap ($<0.5$~eV) materials were highlighted as suitable by the ML methods.}
 For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.
 
-Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that \mrk{both} approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
-Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti \mrk{approach} exhibiting a peak around a $2.5$~eV band gap. 
-Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around $2.5$~eV using the PBE functional. 
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that \mrk{both} approaches predicted a substantial amount of materials with a low band gap (below \SI{0.5}{\electronvolt}).
+Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti \mrk{approach} exhibiting a peak around a \SI{2.5}{\electronvolt} band gap. 
+Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around \SI{2.5}{\electronvolt} using the PBE functional. 
 The empirical approach exhibits a more scattered data distribution. % with local maxima around $1$-$2$ and $4$~eV.
 
-The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for \mrk{both the Ferrenti and empirical} approaches - even peaking at a relatively high ionic character of $0.8$.
-We note that this may be a result of the distribution of the initial dataset of \mrk{$25,000$} materials \mrk{with a maximum} around a similar value (not shown).
+The second most important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
+Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for \mrk{both the Ferrenti and empirical} approaches --- even peaking at a relatively high ionic character of $0.8$.
+We note that this may be a result of the distribution of the initial dataset of \mrk{\num{25000}} materials \mrk{with a maximum} around a similar value (not shown).
 The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach \mrk{nor} the overall data distribution.
@@
 Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the \mrk{Ferrenti} and the empirical approach.
-For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti \mrk{approach displays} an even distribution across a broader range.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation \mrk{of} the RDF, while the Ferrenti \mrk{approach displays} an even distribution across a broader range.
 \mrk{These observations emphasize the importance of symmetry related material properties for QT suitability. }
@@
 This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti \mrk{approach}.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well and may be more important.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered \mrk{equally and may even be more important.}
 
@@
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
-For example, in the high symmetry materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
+For example, in \mrk{high symmetry materials like diamond and silicon}, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
 Instead, \mrk{quantum} effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
-For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
+For \mrk{a binary system like silicon carbide}, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
 While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT compatible properties to manifest in a semiconductor host.
 
-\mrk{One should note that there is a certain degree of bias inherent to the data set labeled in the empirical approach.
-Firstly, experimental searches will always be limited by the availability and cost of materials and processing.
-Secondly, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
-However, the broad range of materials predicted and listed in Table~\ref{tab:materialproperties} and the Supplementary Information at \cite{supplementary} indicates that the ML methods are detecting underlying properties which manifest in materials systems of several kinds.
-}
-
-To summarize, the data extraction tools developed in this work resulted in a dataset of over \mrk{$25,000$} materials and more than $4800$ physics-informed features.
+\mrk{It should be noted that performing machine learning on a dataset derived using preconceived notions for which material properties are important may reproduce several of the initial selection criteria.
+Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the empirical one.
+Additionally, ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.
+Finally, the Ferrenti approaches are employed as a filter on the empirical approach, to provide a better tuned list of candidates for future experimental studies.}
+
+To summarize, \mrk{we have developed data extraction tools and strategies for data mining and labeling to enable the automated search and analysis of host materials for QT.} 
+%the data extraction tools developed in this work resulted in a dataset of over \mrk{\num{25000}} materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training and testing of four ML algorithms.
-\mrk{The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is suitable for performing this type of guided search through materials databases.}
+\mrk{The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is highly suitable for performing this type of guided search through materials databases.}
 %We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
@@
 Valuable insight is gained from \mrk{comparing the important features of the Ferrenti with those for} the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions \mrk{over expected features related to band gap and bonding}.
-
-The findings presented here firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
+\mrk{As such, the expected properties are not able to capture the full physics of the problem.
+The contrast between the Ferrenti and empirical approaches reveals that the problem of QT compatibility is more complex than being related to band gap and bonding character alone.
+Based on our findings we propose that the manifestation of quantum effects in semiconductors is related to the crystal structure symmetry and bonding.
+}
+
+The findings presented here firmly establish that material informatics is a viable and important route to new discoveries in important fields. 
 Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the \mrk{developed framework} is suitable for other fields as well.
@@
 
-The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than $600.000$  materials.
+The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than \mrk{\num{600000}} materials.
 The calculations are performed with the VASP software and the electron exchange and correlation are described with the PBE functional.
@@
 
-JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly $40.000$ three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
+JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly \mrk{\num{40000}} three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
 Structures included in the database are originally taken from the Materials Project \cite{Jain2013, Jain2018}, and then re-optimized using the OPT functional.
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals \cite{Tran2009} is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
-Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on 30.04.2021 (see Ref.
+Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on \mrk{\DTMdisplaydate{2021}{4}{30}{-1}} (see Ref.
 \cite{Choudhary2020}).
@@
 The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
-They utilize the PBE functional \mrk{with the $+U$ correction} within VASP to relax and optimize all structures from the ICSD.
+They utilize the PBE functional \mrk{(with the $+U$ correction for certain cases)} within VASP to relax and optimize all structures from the ICSD.
 Data extraction was performed in the period of January to February of $2021$.
@@
 Initially, the API decides whether a given material is a metal or an insulator, where the latter is confirmed with an additional regression method to predict the band gap.
-The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a $93 \ \%$ prediction success of their initial binary classification method.
+The accuracy is validated by a five-fold cross-validation process for each ML method, where they report a \SI{93}{\percent} prediction success of their initial binary classification method.
 In this work we utilized the Property Labeled Material Fragments (PLMF) openly available at their website
@@
 Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
-As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our data set.}
-
-\mrk{MP includes larger structures of the same material.
-We have included all structures and materials from Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our dataset.
+Furthermore, MP contains structures of varying sizes for the same material.
+We have included all structures and materials from the Materials Project, but we have not checked which materials are represented as a larger cell in our data.
 We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
-This is an improvement that could be made to our method in a further work.}
+This is an improvement that could be made to our method in a future study.}
 
@@
 Boosting methods like gradient boosting use decision trees as weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function  \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under study, leading to a ML method that exhibits a high variance.
+Pure decision trees can easily lead to overfitting of the data under study, leading to an ML method that exhibits a high variance.
 Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.

### 2022-06-10 revision/supplementary-revised.tex
Updates from Overleaf

@@
 \begin{itemize}
-    \item \textit{Supplementary methods.} \\   Additional information on the featurization process and optimization of the machine learning methods. 
-    \item \textit{Supplementary results.} \\ Statistics and tables over the materials that were predicted by the machine learning methods based on the labeled data sets derived using the three different data mining approaches.
-The supplementary results also include feature analyses for the materials predicted by the machine learning methods as suitable for QT.
+    \item \textit{Supplementary methods.}    
+    \subitem Additional information on the featurization process and optimization of the machine learning methods. 
+    \item \textit{Supplementary results.} 
+    \subitem Statistics and tables over the materials that were predicted by the machine learning methods based on the labeled data sets derived using the three different data mining approaches. 
+    \subitem \mrk{Discussion on the Extended Ferrenti approach.} 
+    \subitem The supplementary results also include feature analyses for the materials predicted by the machine learning methods as suitable for quantum technologies (QT). 
     \item \textit{Supplementary references.}  
@@
 To apply Matminer's featurization tools, we extend an existing implementation by \citeauthor{Breuck2021} \cite{Breuck2021}. 
-Table~\ref{table:featurizers} contains an overview of the 39  chosen featurizers from Matminer. The featurization process results in $4876$ physics informed descriptors.
+Table~\ref{table:featurizers} contains an overview of the $39$ chosen featurizers from Matminer. The featurization process results in $4876$ physics informed descriptors.
 
@@
 
-\mrk{This section contains the findings from the data mining and feature analysis for the extended Ferrenti approach to complement the discussion in the main text on the Ferrenti and empirical approaches.}
+\mrk{This section contains the findings from the data mining and feature analysis processes for the extended Ferrenti approach to complement the discussion in the main text on the Ferrenti and empirical approaches.}
 
-\mrk{In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
+\mrk{In the labeled dataset from the extended Ferrenti approach we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
 The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), there is a more sparse representation of each known chemical formula present in the labeled data.
+However, since we also included a more stringent band gap restriction of \SI{1.5}{\electronvolt} (to reduce the amount of materials in the training set), there is a more sparse representation of each known chemical formula present in the labeled data.
 }
@@
 \mrk{Figure~\ref{fig:parallel-coordinates-approaches} displays the parallel coordinate plot for the extended Ferrenti approach while  Figure~\ref{fig:2dscatterplotpca} contains the two-dimensional scatter plot for the same approach.
-The qualitative behavior of the data set derived during the data mining of the extended Ferrenti approach can be seen to overlap with that of the Ferrenti approach.
-}
+The qualitative behavior of the data set derived during the data mining for the extended Ferrenti approach can be seen to closely follow that of the Ferrenti approach as presented in the main text.}
 
@@
     \centering
-    \begin{subfigure}{0.5\textwidth}
+    \begin{subfigure}{0.4\textwidth}
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{AllFigures/02-augmented-ferrenti-approach.pdf}
     \end{subfigure}
@@
 When searching for the optimal number of principal components, we iterated over every odd number of principal components from $1$ to the upper restricted number which defines an accumulated variance of $95 \ \%$ from the principal component analysis.
-Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to $30,800$ individual models.
+Due to a large number of principal components, we performed a fit of  $25$ folds for each of the $1232$ parameter combinations, totaling up to \mrk{\num{30800}} individual models.
 
-\subsubsection*{Ferrenti approach}
-The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Fig.~\ref{fig:01-pca}, where we present the mean accuracy of the four ML models applied to the training set, and the balanced accuracy, precision, recall, and F$1$-score
-for the test set as a function of the number of principal components. For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score.
+\subsubsection*{The Ferrenti approach}
+The grid search for the optimal number of principal components for the Ferrenti approach is visualized in Figure~\ref{fig:01-pca}, where we present the mean accuracy of the four ML models applied to the training set, and the balanced accuracy, precision, recall, and F$1$-score for the test set as a function of the number of principal components.
+For each principal component, we display the optimal combination of  hyperparameters based on the F$1$-score.
 
@@
 Precision, recall, and F$1$ scores are based on the test set.
-The number of principal components that explain the $95 \ \%$ accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
+The number of principal components that explain the \SI{95}{\percent} accumulated variance is $144$, while the optimal model is found using the F$1$-score.}
   \label{fig:01-pca}
@@
 \end{table}
-
-In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components.
-The optimal number is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
-The relevant hyperparameters for logistic regression were the maximum iterations.
-The number of iterations was set to $400$, and the optimal regularization term was $0.46$.
-For random forests and decision trees, we found the maximum depth to be $7$.
-Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
-We found the best performing method to be logistic regression, but this method depends on a large number of principal components.
-
-In Fig.~\ref{fig:01-fi}, we visualize how the various machine learning methods  interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
-To reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components were included.
-We have visualized the first $25$ components since these capture the most important information.
-We note that most of the important features are found within the first five principal components.
 
@@
   \end{subfigure}%
-
   \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by the explained variance for the Ferrenti approach.
@@
 \end{figure}
+
+In Table~\ref{tab:01-pc}, we include the precise measurements for each of the evaluation metrics for the optimal number of principal components.
+The optimal number is visualized as dotted lines in Fig.~\ref{fig:01-pca}.
+The relevant hyperparameters for logistic regression were the maximum iterations.
+The number of iterations was set to $400$, and the optimal regularization term was $0.46$.
+For random forests and decision trees, we found the maximum depth to be $7$.
+Gradient boosting, which normally uses a weak learner, had a decision tree depth of $4$.
+We found the best performing method to be logistic regression, but this method depends on a large number of principal components.
+
+In Figure~\ref{fig:01-fi}, we visualize how the various machine learning methods  interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+To reach the \SI{95}{\percent} accumulated explained variance, a total of $144$ principal components were included.
+We have visualized the first $25$ components since these capture the most important information.
+We note that most of the important features are found within the first five principal components.
 
@@
 
-\subsubsection*{Extended Ferrenti approach}
+\subsubsection*{The extended Ferrenti approach}
 
@@
 Precision, recall and F$1$ scores  are based on the test set.
-The number of principal components that explain the $95 \ \%$ accumulated variance is $159$, while the optimal model is found using the F$1$-score.}
+The number of principal components that explain the \SI{95}{\percent} accumulated variance is $159$, while the optimal model is found using the F$1$-score.}
   \label{fig:02-pca}
@@
 For the extended Ferrenti approach, the parameter grid search for principal components is visualized in Figure~\ref{fig:02-pca}.
-All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $75 \ \% : 25 \ \%$ (suitable:unsuitable).
+All methods experience an almost perfect recall score for the first principal component due to the largely imbalanced dataset with $2141$ suitable and $684$ unsuitable candidates, which results in  a ratio of $\SI{75}{\percent} : \SI{25}{\percent}$ (suitable$:$unsuitable).
 This ratio comes as a consequence of the ML methods being able to correctly label many suitable candidates compared to the number of unsuitable candidates.
@@
 
-The interpretation of feature importance for the extended Ferrenti approach is substantially more difficult than in the Ferrenti approach.
-We find for logistic regression and decision trees that no feature is different than any other in the cross-validation due to a large variety of accuracy.
-However, we find that random forests and gradient boosting experience the fifth principal component as important.
-Similar to the Ferrenti approach, the extended Ferrenti approach finds the DFT band gap of the elemental solids among the elements in the composition to be important.
+\mrk{Note that the} interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
+We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
+However, \mrk{random} forests and gradient boosting both mark the fifth principal component as important.
+%Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
+\mrk{Similar to the Ferrenti approach, the extended Ferrenti approach finds the DFT band gap of the elemental solids among the elements in the composition to be important.
 The feature regarding the band gap originates from the highest value from the first principal component.
 This means that, if we consider, e.g., the compound SiC, the band gaps of both SiC, Si and C would be considered important by the ML methods. 
+}
 
-\subsubsection*{Empirical approach}
+\subsubsection*{The empirical approach}
 
@@
 Precision, recall, and F$1$-scores are based on the test set.
-The number of principal components that explain the $95 \ \%$ accumulated variance is $103$, while the optimal model is found using the F$1$-score.}}
+The number of principal components that explain the \SI{95}{\percent} accumulated variance is $103$, while the optimal model is found using the F$1$-score.}}
   \label{fig:03-pca}
@@
 
-Logistic regression experiences improvement of all scores for an increasing number of principal components, yet only up $5 \ \%$ in scores compared to the one-dimensional representation of one principal component.
+Logistic regression experiences improvement of all scores for an increasing number of principal components, yet only up \SI{5}{\percent} in scores compared to the one-dimensional representation of one principal component.
 Thus, one can argue whether the increase in performance is worthwhile, considering a one-dimensional representation with just a few percentage losses of performance.
@@
 
-In Fig.~\ref{fig:03-fi}, we visualize how the four  ML methods in the empirical approach interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
-Here, the most important information is captured by the first 15 components. The most important features seem to be found within the first few principal  components. 
+In Figure~\ref{fig:03-fi}, we visualize how the four  ML methods in the empirical approach interpret the principal components that are sorted in descending order by the explained variance, found through a $5\times 5$ stratified cross-validation approach.
+Here, the most important information is captured by the first $15$ components. The most important features seem to be found within the first few principal  components. 
 Logistic regression is represented in the top panel of Fig.~\ref{fig:03-fi} where the mean fitted coefficients and the standard deviation are visualized.
@@
 We observe that the single most important feature for all ML methods is the first principal component in the case of the empirical approach.
-Selecting the highest values of this eigenvector, we find that the corresponding features is a complex combination of several material properties, including bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
+Selecting the highest values of this eigenvector, we find that the corresponding features are a complex combination of several material properties, including bond orientational parameters, coordination numbers, and the radial distribution function of a compound's crystal system.
 
@@
 
-\mrk{The more liberal extended Ferrenti approach results in a $78 \ \%$ larger 
-amount of labeled data than the Ferrenti approach.  
-The four ML methods predict at least $13,000$ materials as suitable candidates out of $22,550$ materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
+\mrk{The more liberal extended Ferrenti approach results in a \SI{78}{\percent} larger 
+amount of labeled data than the case for the Ferrenti approach.  
+The four ML methods predict at least \mrk{\num{13000}} materials as suitable candidates out of \mrk{\num{22550}} materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
 Comparing to the labeled data reveals that all of the unlabeled candidates that are known to be suitable are, in fact, predicted as suitable candidates.
 However, the ML methods also predict materials as suitable that are not expected according to, e.g., \citeauthor{Weber2010} \cite{Weber2010}.
-All four ML algorithms predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+All four ML algorithms in the extended Ferrenti approach predict NaCl as a suitable candidate to confidences of $0.83$ and $0.60$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
 %Indeed, single-photon emitters with sharp and bright zero-phonon lines are uncommon in materials with a strong ionic character. 
-Furthermore, although a conservative band gap restriction of $1.5$~eV was enforced for the data labeling in the extended Ferrenti approach, all four implemented ML methods still predict suitable candidates that exhibit band gaps substantially lower than $0.5$~eV.
+Furthermore, although a conservative band gap restriction of \SI{1.5}{\electronvolt} was enforced for the data labeling in the extended Ferrenti approach, all four implemented ML methods still predict suitable candidates that exhibit band gaps substantially lower than \SI{0.5}{\electronvolt}.
 The ML methods applied to data labeled in the Ferrenti and extended Ferrenti approaches are recognizing the band gap and bonding character as important, but the resulting predicted materials do not strictly follow the anticipated guidelines.
@@
 Suitable and unsuitable candidates are marked in green and red, respectively.
-We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches, albeit higher in the case of the latter, for all four ML methods, while the empirical approach results in a substantially narrower selection of contender materials.
+\mrk{We observe that the number of predicted suitable candidates is similar for the Ferrenti and extended Ferrenti approaches for all four ML methods, while the empirical approach results in a substantially narrower selection of contender materials.}
 Note that the confidence threshold was set to $0.5$ in this case for all the methods and approaches.
 
-For the Ferrenti approach, logistic regression finds a total of $12,380$ suitable candidates, while decision trees is the most conservative with $11,315$.
-Random forests has the most optimistic estimate with $14,278$, while gradient boosting finds $11,835$ suitable candidates.
+For the Ferrenti approach, logistic regression finds a total of \mrk{\num{12380}} suitable candidates, while decision trees is the most conservative with \mrk{\num{11315}}.
+Random forests has the most optimistic estimate with \mrk{\num{14278}}, while gradient boosting finds \mrk{\num{11835}} suitable candidates.
 The four ML methods agree on $6804$ suitable candidates,  however, many of the materials are predicted with a confidence similar to that of a coin-flip.
@@
 
-The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with $14,993$, $14,407$, $15,351$ and $13,788$ for logistic regression, decision trees, random forests, and gradient boosting, respectively.
+The perhaps more liberal extended Ferrenti approach yields the largest number of predicted candidates with \mrk{\num{14993}, \num{14407}, \num{15351} and \num{13788}} for logistic regression, decision trees, random forests, and gradient boosting, respectively.
 Due to the less stringent restrictions compared to the Ferrenti approach, we find a large number ($9227$) of entries that the four ML methods  agree on.
@@
 
-Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods, using the training and test sets derived in the empirical approach, agreed on with a confidence cut-off set to $0.75$.
+Table~\ref{tab:03-probability-candidates} displays the $66$ predicted candidate materials that all four machine learning methods \mrk{in the empirical approach} agreed on with a confidence cut-off set to $0.75$.
 All band gaps are taken from the Materials Project database as calculated using DFT and the PBE functional.
@@
 
-\newpage
+\mrk{The ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+However, almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
+Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted  sufficiently to admit several oxides as suitable candidates.
+Removing ZnO from the training set for the empirical approach might result in fewer or even no oxide compounds being predicted above a suitability limit of $0.5$ and could be an interesting future pathway for investigation.}
+
+%\newpage
 
@@
 \newpage 
-
+\section*{Supplementary references}
 \bibliography{apssamp}% Produces the bibliography via BibTeX.

### 2022-08-15 response-letter/response-letter.tex
Updates from Overleaf

@@
 As such, the expected properties are not able to capture the full physics of the problem.
-This is in fact an important finding of our work; that the the problem of QT compatibility is more complex than being related to band gap and bonding character alone, and the contrast between the Ferrenti and empirical approaches was necessary to come to this conclusion.
+This is in fact an important finding of our work; that the problem of QT compatibility is more complex than being related to band gap and bonding character alone, and the contrast between the Ferrenti and empirical approaches was necessary to come to this conclusion.
 However, we realize that this was not sufficiently clear in the original manuscript.
@@
 We agree that it is not necessarily clear that either the Ferrenti or the extended Ferrenti approaches would categorize ionic materials with cubic symmetry as unsuitable, but it is clear from these criteria why NaCl is excluded from the labeling process.
-Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both Ferrenti and extended Ferrenti altogether predicts the material as suitable.}
+Therefore, NaCl is found unlabeled in the test data, while the ML algorithms in both the Ferrenti and the extended Ferrenti datasets altogether predict the material as suitable.}
 \textit{The following note was added to this effect on page 11 in the Predicting Suitable Material Hosts for Quantum Technology section:} \\ 
@@
 (Ref.~[8] of the main text) are also interesting to consider in this regard, in particular the assumption that wide band gap materials are preferable.
-The recent discovery of telecom compatible SPEs in Si (Refs.~[54-55] in the main text), a lower band gap material, show that this may have been a premature assumption.
+The recent discovery of single photon emitters that emit in the telecom range in Si (Refs.~[54-55] in the main text), a lower band gap material, show that this may have been a premature assumption.
 We hope that our work can contribute to widening the search for quantum compatible semiconductor platforms.
@@
     \textit{Regarding the “Comparing the approaches” subsection, we agree that there were many repetitions, which have now been removed.
-However, we elected to keep the subsection itself, as it  contains an important result of the work: a discussion on the $47$ materials that all three approaches and all four ML methods agree on above a $0.5$ threshold, and the $6$ materials likewise agreed upon to $0.75$ confidence.
+However, we chose to keep the subsection itself, as it  contains an important result of the work: a discussion on the $47$ materials that all three approaches and all four ML methods agree on above a $0.5$ threshold, and the $6$ materials likewise agreed upon to $0.75$ confidence.
 These materials were not discussed elsewhere in the text and the portion of Table III displaying their properties was first referenced here.

### 2022-08-15 revision-2/revised-paper-2-marked_up.tex
Updates from Overleaf

--- 2022-06-10 revision/revised-paper_marked-up.tex
@@
 %
-\documentclass[superscriptaddress,unsortedaddress,
+\documentclass[superscriptaddress,
 %runinaddress,
 %frontmatterverbose, 
-%preprint,
+preprint,
 %preprintnumbers,
@@
 
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-\usepackage{physics}
-\usepackage{lipsum}
-% \usepackage{subfig} %not compatible with subcaption
-% \usepackage{braket}
 \usepackage{siunitx}
+\usepackage{subcaption}
+\captionsetup[table]{skip=10pt}
+\usepackage{graphicx}
+\usepackage[useregional]{datetime2}
+\usepackage{hyperref}
+
 \usepackage{color}
-% \usepackage{caption}
-\usepackage{subcaption}
-\usepackage{tikz,pgfplots}
-\usepgfplotslibrary{groupplots,dateplot}
-\usetikzlibrary{patterns,shapes.arrows}
-\usepackage{makecell}
-\captionsetup[table]{skip=10pt}
-\pgfplotsset{compat=1.17}
-\sisetup{separate-uncertainty}
-\usepackage{hyperref} 
-% \usepackage{longtable}
-\usetikzlibrary{patterns,shapes.arrows, arrows.meta,bending, shapes,calc,fadings,decorations.pathreplacing,positioning,arrows.meta}
-\pgfplotsset{compat=newest}
-
-\usepackage{sansmath}
-\tikzset{>=stealth,
-OptimumStyle/.style={align=center,anchor=east,rotate=90,font=\scriptsize}
-}
-\pgfplotsset{%samples=101,
-axis lines = left,
-every axis plot/.append style={line width=2pt},
-}
-\usepackage{forest}
-\forestset{
-    .style={
-        for tree={
-            base=bottom,
-            child anchor=north,
-            align=center,
-            s sep+=1cm,
-    straight edge/.style={
-        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
-        (!u.parent anchor) -- (.child anchor);}
-    },
-    if n children={0}
-        {tier=word, draw, thick, rectangle}
-        {draw, diamond, thick, aspect=2},
-    if n=1{%
-        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
-        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {Y};}
-        }{
-        edge path={\noexpand\path[\forestoption{edge},thick,-{Latex}]
-        (!u.parent anchor) -| (.child anchor) node[pos=.2, above] {N};}
-        }
-        }
-    }
-}
-\tikzset{
-  green arrow/.style={
-    midway,green,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
-    allow upside down
-  },
-  yellow arrow/.style={
-    midway,yellow,sloped,fill, minimum height=2cm, single arrow, single arrow head extend=.5cm, single arrow head indent=.25cm,xscale=0.3,yscale=0.15,
-    allow upside down
-  },
-  black arrow/.style 2 args={-stealth, shorten >=#1, shorten <=#2},
-  black arrow/.default={1mm}{1mm},
-  tree box/.style={draw, rounded corners, inner sep=1em},
-  node box/.style={white, draw=white, text=black, rectangle, rounded corners},
-}
-
 \newcommand{\mrk}[1]{\textcolor{red}{#1}}
-\usepackage[useregional]{datetime2}
 
@@
 
-\title{Predicting Solid State Material Platforms for Quantum Technologies}
+\title[Predicting Solid State Material Platforms for Quantum Technologies]{Predicting Solid State Material Platforms for Quantum Technologies}
 
@@
 
-Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
+%Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
 However, searching these databases to find promising candidate materials for quantum technology applications is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \mrk{\num{25000}} materials and nearly \num{5000} physics-informed features.
-\mrk{Three different approaches were devised} to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting. 
-We find that \mrk{among these, the} empirical approach relying exclusively on findings from the literature \mrk{exhibited the clearest  distinction}  between \mrk{predicted} suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to expectations from the literature  %and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, 
-\mrk{focusing on band gap and ionic character as important features for QT compatibility,}  
-the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
-All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
-%(to a probability of $>50 \ \%$) 
-of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \num{25000} materials and nearly \num{5000} physics-informed features.
+Three different approaches were devised to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
+We find that among these, the empirical approach relying exclusively on findings from the literature exhibited the clearest  distinction between predicted suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+In contrast to expectations from the literature focusing on band gap and ionic character as important features for QT compatibility, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
+All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates of $8$ elemental, $29$ binary, and $10$ tertiary compounds, and provide a basis for further material explorations towards quantum technology.
+
+%less than 150 word abstract
+Semiconductor materials provide a compelling platform for quantum technologies (QT).
+However, identifying promising material hosts among the plethora of candidates is a major challenge.
+Therefore, we have developed a framework for the automated discovery of semiconductor platforms for QT using material informatics and machine learning methods.
+Different approaches were implemented to label data for training the supervised machine learning (ML) algorithms logistic regression, decision trees, random forests and gradient boosting.
+We find that an empirical approach relying exclusively on findings from the literature yields a clear separation between predicted suitable and unsuitable candidates.
+In contrast to expectations from the literature focusing on band gap and ionic character as important properties for QT compatibility, the ML methods highlight features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
 
@@
 \section*{Introduction}
-Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during \mrk{recent}  years. 
+Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during recent years. 
 Among the promising applications that are already available we find important breakthroughs such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures \cite{Arute_2019}.
@@
 Recent advances have highlighted the potential of quantum information processors to outperform state-of-the art high-performance computing facilities.
-Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \mrk{\num{200000}} core supercomputer \cite{Arute_2019}.
+Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \num{200000} core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/ht-workflow-new-2.png}
+    \includegraphics[width=0.9\textwidth]{figure1.png}
     \caption{Schematic of an example workflow in material informatics.
@@
 However, semiconductor based QT is still in the early stages, and the issues left to address include identification of suitable host materials and candidate defects, and scalable and reproducible quantum device fabrication.
-Furthermore, a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties \mrk{is lacking},  
+Furthermore, a complete understanding of the requirements for a semiconductor material to manifest quantum compatible properties is lacking,  
 and the selection of known quantum compatible host materials is slim \cite{Atatuere2018,Zhang2020}.
@@
 %, see for example Ref.~\cite{Acin2018}.
-Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures \mrk{should be targeted} for more detailed studies, following the framework illustrated in Fig.~\ref{fig:ht-workflow}.
+Rather than searching through a host of signals for those that match our criteria, we aim to \textit{predict} which materials and signatures should be targeted for more detailed studies, following the framework illustrated in Fig.~\ref{fig:ht-workflow}.
 This is made feasible by the availability of databases containing material properties for a wide range of different systems.
@@
 
-\mrk{Herein, a framework is provided} for the data mining and automated discovery of promising \mrk{semiconductor hosts for QT} using targeted database search and ML methods combined with knowledge from the field.
+Herein, a framework is provided for the data mining and automated discovery of promising semiconductor hosts for QT using targeted database search and ML methods combined with knowledge from the field.
 Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training and testing, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
-\mrk{This framework does not} distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
-The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data \mrk{is} available.
-
-The developed procedure relies on data extraction \mrk{from different databases and the subsequent featurization of the data.} 
+This framework does not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
+The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data is available.
+
+The developed procedure relies on data extraction from different databases and the subsequent featurization of the data. 
 %from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
 %The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data. 
-An important aspect of \mrk{the} work is the database building and pertinent development of the datasets for the ML methods.
-\mrk{Three different approaches to data mining were devised}: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
-\mrk{The} two first \mrk{data extraction protocols are based on} broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
+An important aspect of the work is the database building and pertinent development of the datasets for the ML methods.
+Three different approaches to data mining were devised: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
+The two first data extraction protocols are based on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding \mrk{$47$} predicted candidates that were common between all approaches and ML methods.
-Example materials \mrk{among the predictions} include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP. Focused theoretical and experimental studies 
+The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding \num{47} predicted candidates that were common between all approaches and ML methods.
+Example materials among the predictions include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP. Focused theoretical and experimental studies 
 %, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, 
-\mrk{are needed} to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials. 
+are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials. 
 %Write better! 
@@
 Therefore, not all properties predicted using the PBE functional are reliable, and the band gaps in particular cannot be trusted in absolute terms.
-Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor \mrk{material} properties.
+Nonetheless, the functional is in wide use due to the combination of reasonable accuracy and high computational throughput, and is usually considered to be reliable for large-scale trends in semiconductor material properties.
 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
+    \includegraphics[width=0.9\textwidth]{figure2.png}
     \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
-    To limit the memory and computational usage, the data \mrk{is} partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
+    To limit the memory and computational usage, the data is partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
 This process is repeated iteratively until all the data has been featurized.
@@
 The ICSD is the world's largest database for completely identified inorganic crystal structures  \cite{Allen1987,Zagorac2019}.
-In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the \mrk{following databases: the Open Quantum Materials Database (OQMD)}  \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
+In a parallel step, entries that are deemed similar to the entries from the initial query are extracted from the following databases: the Open Quantum Materials Database (OQMD) \cite{Saal2013,Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015}, AFLOW-ML \cite{Isayev2017} and the Citrination platform \cite{OMaraJordan2016MDIA}.
 The results of these steps are combined into a dataset for further analysis.
 
-After material extraction \mrk{tools from the open-source library Matminer \cite{Ward2018} were applied} to generate thousands of features from the data.
+After material extraction tools from the open-source library Matminer \cite{Ward2018} were applied to generate thousands of features from the data.
 We will refer to this process as featurization.
@@
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ featurizers (each generates several features) selected as material descriptors in this work are \mrk{described} in the Supplementary Information at \cite{supplementary}.
-The selection of features was kept rather wide \mrk{to avoid making} {\em ex ante} assumptions on which features best describe a solid state material platform for \mrk{QT}.
+The $39$ featurizers (each generates several features) selected as material descriptors in this work are described in the Supplementary Information at \cite{supplementary}.
+The selection of features was kept rather wide to avoid making {\em ex ante} assumptions on which features best describe a solid state material platform for QT.
 
 The constructed dataset encompasses compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
-Furthermore, \mrk{the extracted data was}  obtained from high-throughput density functional theory calculations.
-Indeed, there are possible errors associated with every step, starting from an initial calculation, \mrk{adding of data in the database, featurization and preprocessing the data, data mining and labeling, and finally training a model and making a prediction.}  Unfortunately, if an error \mrk{occurrs} in the first part of the process, \mrk{it will be  carried along and get} increasingly harder to detect.
-Thus, \mrk{the output strongly depends}  on the quality of data in the \mrk{employed} databases.
+Furthermore, the extracted data was obtained from high-throughput density functional theory calculations.
+Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, featurization and preprocessing the data, data mining and labeling, and finally training a model and making a prediction.
+Unfortunately, if an error \mrk{occurs} in the first part of the process, it will be  carried along and get increasingly harder to detect.
+Thus, the output strongly depends on the quality of data in the employed databases.
 
 \subsection*{Data Mining}
-The complete dataset consists of \mrk{\num{25000}} materials.
+The complete dataset consists of \num{25000} materials.
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data \mrk{is} then grouped into training and test sets for the ML methods.
-\mrk{The ML methods are trained using the training set and then evaluated on the test set.
-Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.}
-
-Several challenges accompany the labeling \mrk{process.} 
+The labeled data is then grouped into training and test sets for the ML methods.
+The ML methods are trained using the training set and then evaluated on the test set.
+Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.
+
+Several challenges accompany the labeling process. 
 %of labeling materials according to their suitability for QT. 
@@
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood.
-Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are \mrk{not known either}.
-The strategy for selection of unsuitable candidates is thus that the negation of the criteria \mrk{used} to select suitable candidates should give unsuitable candidates.
-A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates\mrk{, resulting in} skewed datasets \mrk{with} fewer unsuitable than suitable candidates.
+Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are not known either.  
+The strategy for selection of unsuitable candidates is thus that the negation of the criteria used to select suitable candidates should give unsuitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates, resulting in skewed datasets with fewer unsuitable than suitable candidates.
 This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
-Below \mrk{three separate procedures for labeling materials as suitable or unsuitable candidates for QT are described}.
+Below three separate procedures for labeling materials as suitable or unsuitable candidates for QT are described.
 
@@
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project. 
-\mrk{Note that the data mining process in Ref.~\cite{Ferrenti2020} alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
-Nonetheless, we adapt the selection criteria from Ref.~\cite{Ferrenti2020} for the present purposes.}
-In the \mrk{\emph{Ferrenti approach}} framework, \textbf{suitable} candidates \mrk{are labeled} by the following steps: 
+Note that the data mining process in Ref.~\cite{Ferrenti2020} alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
+Nonetheless, we adapt the selection criteria from Ref.~\cite{Ferrenti2020} for the present purposes.
+In the \emph{Ferrenti approach} framework, \textbf{suitable} candidates are labeled by the following steps: 
 \begin{enumerate}
@@
         \item contain elements with more than \SI{50}{\percent} natural abundance of spin zero isotopes,
-        \item crystallize in non-polar space groups, \mrk{are calculated to be nonmagnetic, and 
-        are present in the ICSD.}
+        \item crystallize in non-polar space groups, are calculated to be nonmagnetic, and 
+        are present in the ICSD.
     \end{itemize}
@@
 
-\mrk{The} inclusion criteria are based on \mrk{Ref.}~\cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
-In this context, long spin coherence times are needed, \mrk{necessitating an environment that can be depleted of nuclear spins and permanent magnetism.}
+The inclusion criteria are based on Ref.~\cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
+In this context, long spin coherence times are needed, necessitating an environment that can be depleted of nuclear spins and permanent magnetism.
 %and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable. 
-Moreover, non-polar materials are assumed to be preferable to obtain \mrk{sharp and indistinguishable single-photon emission from defects}.  
+Moreover, non-polar materials are assumed to be preferable to obtain sharp and indistinguishable single-photon emission from defects.  
 Transition metal elements are eliminated if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
-Finally, the energy above hull requirement \mrk{ensures} that the selected compounds are thermodynamically stable.
-\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
-
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the \mrk{ICSD} that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than \SI{0.1}{\electronvolt} in the MP database (to exclude metals but include lower-band gap semiconductors).
+Finally, the energy above hull requirement ensures that the selected compounds are thermodynamically stable.
+Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.
+
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than \SI{0.1}{\electronvolt} in the MP database (to exclude metals but include lower-band gap semiconductors).
+\mrk{Crucially, only materials that satisfy \emph{all} of the reverse requirements are labeled unsuitable.
+In other words, unlabeled materials will satisfy some of the selection criteria, but not all.}
 The resulting set of labeled materials contains $1581$ materials where \SI{35}{\percent}
 are labeled as unsuitable and \SI{65}{\percent} 
-as suitable for QT applications, \mrk{evidencing that} 
+as suitable for QT applications, evidencing that 
 %Here we see the first example of how 
-the criteria for labeling unsuitable candidates are more restrictive than those for the suitable \mrk{ones}.
+the criteria for labeling unsuitable candidates are more restrictive than those for the suitable ones.
+\mrk{However, there could still be potential suitable materials among the remaining $23500$ unlabeled materials, yet impractical to manually identify them.
+This serves as the main motivation behind using ML-methods for predicting suitable or unsuitable materials for QT applications.}
 
 %Ferrenti 
-\mrk{Considering the materials present in the labeled dataset of the Ferrenti approach more closely, we find that diamond is classified as a suitable candidate, in good agreement with experimental observations.
+Considering the materials present in the labeled dataset of the Ferrenti approach more closely, we find that diamond is classified as a suitable candidate, in good agreement with experimental observations.
 Interestingly, carbon in two-dimensional graphite-like structures are marked as suitable as well.
@@
 Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.}
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.
 
 \subsubsection*{The extended Ferrenti approach}
-\mrk{The Ferrenti approach was adjusted} to expand the data labeling process beyond practical  considerations.
+The Ferrenti approach was adjusted to expand the data labeling process beyond practical  considerations.
 The second approach is therefore named \emph{the extended Ferrenti approach} and involves removing stage two from the approach above.
-Moreover, \mrk{certain} additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes \mrk{are also included}.
-
-The following steps constitute the process of labeling \textbf{suitable} candidates in the \mrk{extended Ferrenti approach}:
+Moreover, certain additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes are also included.
+
+The following steps constitute the process of labeling \textbf{suitable} candidates in the extended Ferrenti approach:
 \begin{enumerate}
@@
         \item crystallize in non-polar space groups,
-        \mrk{are calculated to be nonmagnetic and are present in the ICSD} 
+        are calculated to be nonmagnetic and are present in the ICSD\mrk{.}
     \end{itemize}
@@
 
-For \textbf{unsuitable} candidates, \mrk{the same strategy as for the Ferrenti approach was implemented}.
-The result is \mrk{an unbalanced set of labeled materials that is   \SI{78}{\percent} larger than for the Ferrenti approach and having $\sim$\SI{75}{\percent} of the materials found in the suitable group.}
-
-\mrk{The findings from both the data mining and machine learning procedures for the extended Ferrenti approach did not differ substantially from those obtained using the Ferrenti approach.
+For \textbf{unsuitable} candidates, the same strategy as for the Ferrenti approach was implemented.
+The result is an unbalanced set of labeled materials that is   \SI{78}{\percent} larger than for the Ferrenti approach and having $\sim$\SI{75}{\percent} of the materials found in the suitable group.
+
+The findings from both the data mining and machine learning procedures for the extended Ferrenti approach did not differ substantially from those obtained using the Ferrenti approach.
 This is attributed to the similarities in the selection processes.
@@
 Nonetheless, predictions from the extended Ferrenti approach will be employed below to contrast with and filter the findings from the empirical approach.
-}
 
 \subsubsection*{The empirical approach} 
-\mrk{In the \emph{empirical approach},} we apply knowledge from the field (see for instance  Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to \mrk{guide the search for} promising material \mrk{hosts.}
-In other words, \mrk{the labeled data contains candidates} where quantum compatible properties have been either experimentally demonstrated or theoretically predicted\mrk{, including the materials suggested in Ref.~\cite{Weber2010} as promising deep level defect hosts.}
+In the \emph{empirical approach}, we apply knowledge from the field (see for instance  Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to guide the search for promising material hosts.
+In other words, the labeled data contains candidates where quantum compatible properties have been either experimentally demonstrated or theoretically predicted, including the materials suggested in Ref.~\cite{Weber2010} as promising deep level defect hosts.
 %We therefore name this scheme \emph{the empirical approach}. 
@@
 %material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}. 
-\mrk{Materials where single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related were also included.}
+Materials where single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related were also included.
 
@@
 These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than \SI{0.5}{\electronvolt}.
-\mrk{All of the $202$ structures were included in the labeled dataset apart from C (mp-$568410$) which is a metal according to AFLOW-ML. }
+All of the $202$ structures were included in the labeled dataset apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
 
@@
     \centering
-    \begin{subfigure}{1\textwidth}
-        \centering
-        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
-          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
-    \end{subfigure}
-    \caption{Parallel coordinate plots for the two different approaches. \mrk{To limit data cluttering up to $250$ entries for each class were randomly collected.}  
+    %\begin{subfigure}{1\textwidth}
+    %    \centering
+    %    \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
+    %\end{subfigure}
+    %\begin{subfigure}{1\textwidth}
+     %   \centering
+     %     \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
+    %\end{subfigure}
+    \includegraphics[width=0.8\textwidth]{figure3.pdf}
+    \caption{Parallel coordinate plots for the two different approaches. To limit data cluttering up to $250$ entries for each class were randomly collected.  
     %For the empirical approach, we have used all the $187$ suitable candidates. 
@@
 
-Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ \mrk{were} manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
-For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the \mrk{MP} \mrk{were admitted.} Additionally, we find several two-dimensional structures of carbon with a large band gap (\mrk{$>\SI{1.5}{\electronvolt}$}) among the data.
-\mrk{These were added} as suitable candidates.
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
+For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the MP were admitted.
+Additionally, we find several two-dimensional structures of carbon with a large band gap ($>\SI{1.5}{\electronvolt}$) among the data.
+These were added as suitable candidates.
 Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies.
 For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
-Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, \mrk{only two-dimensional structures were admitted.
-Other non-matching structures were moved to the test set to see whether or not they are predicted as suitable by the ML methods applied in a later stage}.
+Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, only two-dimensional structures were admitted.
+Other non-matching structures were moved to the test set to see whether or not they are predicted as suitable by the ML methods applied in a later stage.
 
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-\mrk{Note} that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of \SI{0.5}{\electronvolt}.
+Note that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of \SI{0.5}{\electronvolt}.
 
 Following the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set.
-\mrk{Notably, only elementary (unary) and binary materials are labeled as suitable in the empirical approach.} \mrk{To complete the dataset, $400$ materials were added and labeled as \textbf{unsuitable}}.
-These \mrk{were} picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
-
-\mrk{Note that there is some potential for inherent bias in the dataset, in part due to experimental work being limited by the availability and cost of materials and processing.
+Notably, only elementary (unary) and binary materials are labeled as suitable in the empirical approach.
+To complete the dataset, $400$ materials were added and labeled as \textbf{unsuitable}.
+These were picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
+
+Note that there is some potential for inherent bias in the dataset, in part due to experimental work being limited by the availability and cost of materials and processing.
 Moreover, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
 %However, the broad range of materials predicted and listed in Table~\ref{tab:materialproperties} and the Supplementary Information at \cite{supplementary} indicates that the ML methods are detecting underlying properties which manifest in a broad range of material systems.
-}
 
@@
 
-\mrk{The labeled data for the Ferrenti and empirical approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for \mrk{selected} features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+The labeled data for the Ferrenti and empirical approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
         \centering
-        \includegraphics[width=1\textwidth]{AllFigures/01-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{figure4a.pdf}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=1\textwidth]{AllFigures/03-insightful-approach.pdf}
+        \includegraphics[width=1\textwidth]{figure4b.pdf}
     \end{subfigure}
-    \caption{Two-dimensional scatter plots for the \mrk{Ferrenti and empirical} approaches.
-\mrk{The eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix were identified}, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, \mrk{the labeled datasets were transformed and visualized as 2D scatter plots.} Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols \mrk{for the empirical approach}, and red triangles represent unsuitable candidates.}
+    \caption{Two-dimensional scatter plots for the Ferrenti and empirical approaches.
+The eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix were identified, that is, the two most important principal components of the initial data from the Materials Project query.
+Then, the labeled datasets were transformed and visualized as 2D scatter plots.
+Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols for the empirical approach, and red triangles represent unsuitable candidates.}
     \label{fig:2dscatterplotpca}
@@
 %The most striking difference is found for the empirical approach. 
-\mrk{Several differences are observed between the Ferrenti approach and the empirical approach to data mining.
-While neither case passes materials that exhibit magnetization through as suitable, suitable candidates can crystallize in both polar and non-polar space groups in the empirical approach.} Moreover, \mrk{the ranges}  of covalent radius and maximum ionic character span a substantially smaller parameter space \mrk{for the empirical approach than for the Ferrenti approach (see Fig.~\ref{fig:parallel-coordinates-approaches})}.
+Several differences are observed between the Ferrenti approach and the empirical approach to data mining.
+While neither case passes materials that exhibit magnetization through as suitable, suitable candidates can crystallize in both polar and non-polar space groups in the empirical approach.
+Moreover, the ranges of covalent radius and maximum ionic character span a substantially smaller parameter space for the empirical approach than for the Ferrenti approach (see Fig.~\ref{fig:parallel-coordinates-approaches}).
 %Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance. 
 %In the empirical approach the polarity of the material's space group may be less important compared to the \mrk{Ferrenti approach}, while the accepted values for ionic character and covalent range appear more restricted .
-\mrk{Overall, there seems to be greater overlap in the distributions in material properties for suitable and unsuitable candidates in the case of the Ferrenti approach as compared to the empirical one.}
-
-\mrk{To reduce the dimensionality of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.} In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
+Overall, there seems to be greater overlap in the distributions in material properties for suitable and unsuitable candidates in the case of the Ferrenti approach as compared to the empirical one.
+
+To reduce the dimensionality of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.
+In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
 We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the MP database, and transform the three labeled datasets according to the corresponding two eigenvectors.
-The result of this procedure is displayed in the scatter plots of \mrk{Figure}~\ref{fig:2dscatterplotpca}.
-Note that some minor differences between the \mrk{approaches} may occur due to the process of removing the mean and scaling to unit variance.
-Red triangles represent unsuitable candidates while \mrk{otherwise} colored symbols (green, blue, black and yellow) represent suitable candidates.
-Due to the complexity of reducing the large amount of features down to only two, suitable and unsuitable candidates for \mrk{the Ferrenti approach} are largely overlapping. 
-The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti \mrk{approach}.
-Hence, using \mrk{this approach} for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-We therefore expect that the \mrk{Ferrenti approach} could need supplementary dimensions for further distinguishing between the materials in the two categories\mrk{.} 
+The result of this procedure is displayed in the scatter plots of Figure~\ref{fig:2dscatterplotpca}.
+Note that some minor differences between the approaches may occur due to the process of removing the mean and scaling to unit variance.
+Red triangles represent unsuitable candidates while otherwise colored symbols (green, blue, black and yellow) represent suitable candidates.
+Due to the complexity of reducing the large amount of features down to only two, suitable and unsuitable candidates for the Ferrenti approach are largely overlapping. 
+The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti approach.
+Hence, using this approach for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT. 
+We therefore expect that the Ferrenti approach could need supplementary dimensions for further distinguishing between the materials in the two categories. 
 %, or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
 
-In the case of the empirical approach, on the other hand, \mrk{a clear trend can be discerned} where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable  %(green, blue, yellow and black symbols),
-\mrk{candidates while the unsuitable ones} are similarly restricted to the lower right corner, albeit with some exceptions. 
+In the case of the empirical approach, on the other hand, a clear trend can be discerned where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable  %(green, blue, yellow and black symbols),
+candidates while the unsuitable ones are similarly restricted to the lower right corner, albeit with some exceptions. 
 Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
-This \mrk{strongly indicates that the empirical approach may be capable of separating materials based on their underlying properties, emphasizing the importance of having a logical framework for the data mining process}.
+This strongly indicates that the empirical approach may be capable of separating materials based on their underlying properties, emphasizing the importance of having a logical framework for the data mining process.
 %Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
@@
 \subsection*{Machine Learning and Principal Component Analysis}
-\mrk{Four well-tested ML algorithms were applied to the labeled data} to classify specific materials as candidate systems for QT\mrk{, yielding multiple sets of predicted candidates.
-The ML methods employed herein} are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
+Four well-tested ML algorithms were applied to the labeled data to classify specific materials as candidate systems for QT, yielding multiple sets of predicted candidates.
+The ML methods employed herein are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
 %These four ML methods were applied to the labeled datasets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
 %\mrk{To} reduce the dimensionality while preserving most of the variance in the data, \mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-\mrk{Principal component analysis was again performed, but now on the three training sets separately}\footnote{In the main text we discuss the Ferrenti dataset and the empirical one.
-The corresponding results for the extended Ferrenti set are listed in the supplementary material.}
+Principal component analysis was again performed, but now on the three training sets separately
+%\footnote{In the main text we discuss the Ferrenti dataset and the empirical one. The corresponding results for the extended Ferrenti set are listed in the Supplementary Information.}
 % \mrk{A principal component analysis was performed where first the} 
@@
 (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model). 
-Next, in the evaluation of the \mrk{ML methods we}  
+Next, in the evaluation of the ML methods we  
 %for the three different approaches 
 apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-\mrk{Note} that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four \mrk{ML} methods are shown in the Supplementary Information \mrk{at} \cite{supplementary}.
-The \mrk{data labeling approaches} define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
+Note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four ML methods are shown in the Supplementary Information at \cite{supplementary}.
+The data labeling approaches define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
 For small datasets, it is proven to be beneficial to repeat the cross-validation analysis \cite{Hastie2009}, as this is a method that allows us to measure the stability of the predictions against perturbations (i.e., few different entries) in the training data \cite{Beleites2008}.
@@
 Figure~\ref{fig:PComponents} visualizes different parameters for the most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-This differs from Fig.~\ref{fig:2dscatterplotpca}, where \mrk{the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown}.
+This differs from Fig.~\ref{fig:2dscatterplotpca}, where the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown.
 %Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all the data}. Here, the ML analysis is done on the labeled data for each approach. 
 For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the \SI{95}{\percent} accumulated explained variance, a total of $144$ principal components must be included.
-\mrk{In the case of the empirical approach and in contrast to the Ferrenti approach}, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
+In the case of the empirical approach and in contrast to the Ferrenti approach, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
 Gradient boosting
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{AllFigures/01-ferrenti-approach-PC-v2.tex}
+        \includegraphics{figure5a}
         \label{fig:01-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{AllFigures/01-ferrenti-approach-GB-v2.tex}
+        \includegraphics{figure5b}
         \label{fig:01-fi-d}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{AllFigures/03-empirical-approach-PC-v2.tex}
+        \includegraphics{figure5c}
         \label{fig:03-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{AllFigures/03-empirical-approach-GB-v2.tex}
+        \includegraphics{figure5d}
         \label{fig:03-fi-d}
@@
     \caption{Visualization of different parameters for the $25$ most principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approaches, and (b) the gradient boosting coefficients for the corresponding approaches.
-\mrk{Note that in (a) only the results of the PCA analysis are visualized, while (b) contains} results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
+Note that in (a) only the results of the PCA analysis are visualized, while (b) contains results of the PCA reduced training sets using gradient boosting \cite{Hastie2009,xgboost2016}.
 The latter shows that for the empirical approach most of the physics is represented by a few features.
@@
 
-\mrk{Fig.}~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
+Fig.~\ref{fig:PComponents}(b) reveals that the most important feature for the gradient boosting method in the Ferrenti approach is the fifth principal component (fifth largest eigenvalue).
 The trend is maintained for all four ML methods (see the Supplementary Information at \cite{supplementary}).
-\mrk{By selecting the highest values in this eigenvector we} find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
+By selecting the highest values in this eigenvector we find that the corresponding features originate from the DFT computed band gap of the elemental solids among the elements in the compound as calculated by the Materials Agnostic Platform for Informatics and Exploration (MagPie)~\cite{magpie}.
 The second most important principal component for the Ferrenti approach exhibits significant contributions from the covalent radius, the ionic character and the packing efficiency among the elements in the composition.
@@
 %empirical approach 
-The empirical approach differs in many aspects from the Ferrenti \mrk{approach}. 
-Firstly, \mrk{the} number of principal components necessary to obtain \SI{95}{\percent} variance is reduced to \mrk{$103$ from $144$}. 
+The empirical approach differs in many aspects from the Ferrenti approach. 
+Firstly, the number of principal components necessary to obtain \SI{95}{\percent} variance is reduced to \num{103} from \num{144}. 
 %and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively. 
-Thus, the variance of the training set \mrk{is} described with fewer principal components, indicating a simpler model.
+Thus, the variance of the training set is described with fewer principal components, indicating a simpler model.
 Secondly, the first principal component is by far the most important feature for all ML methods in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
@@
 The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
-Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is \SI{21}{\percent}, \mrk{compared to} \SI{14}{\percent} for the Ferrenti approach. 
+Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is \SI{21}{\percent}, compared to \SI{14}{\percent} for the Ferrenti approach. 
 % and $11 \ \%$ for the extended Ferrenti approach. 
@@
 
-Intriguingly, the principal components that are deemed important by \mrk{the approaches differ substantially.
-The Ferrenti approach places}  particular value on the material's band gap and the ionic or covalent character of the bonding.
+Intriguingly, the principal components that are deemed important by the approaches differ substantially.
+The Ferrenti approach places particular value on the material's band gap and the ionic or covalent character of the bonding.
 Indeed, precisely these features were used as guidance in the data labeling process.
-\mrk{Thus, the ML methods seem to perpetuate the criteria imposed in the Ferrenti approach at least to some extent.
-They may, however, still be recognizing other patterns than those originally intended in the data selection process.} \mrk{For the empirical approach, on the other hand, the selection was not guided in terms of specific properties.} Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In the empirical approach, the ML methods \mrk{are recognizing more complex mechanisms in the crystal structure and bonding as common trends among materials that are suitable for QT applications}.
+Thus, the ML methods seem to perpetuate the criteria imposed in the Ferrenti approach at least to some extent.
+They may, however, still be recognizing other patterns than those originally intended in the data selection process.
+For the empirical approach, on the other hand, the selection was not guided in terms of specific properties.
+Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In the empirical approach, the ML methods are recognizing more complex mechanisms in the crystal structure and bonding as common trends among materials that are suitable for QT applications.
 
@@
 %After training the ML algorithms using parts of the data labeled during the \mrk{data mining process}, the ML methods were employed on the test sets. 
-\mrk{After training and validating the ML algorithms on the labeled datasets, the ML methods were applied to unlabeled data to obtain predictions for suitable QT host materials.} 
-The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary}\mrk{.} %for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}\mrk{for the Ferrenti, extended Ferrenti and empirical approaches.
-Note that the Ferrenti approaches are employed as a filter on the predictions of the empirical one.}
+After training and validating the ML algorithms on the labeled datasets, the ML methods were applied to unlabeled data to obtain predictions for suitable QT host materials. 
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary}.
+%for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}for the Ferrenti, extended Ferrenti and empirical approaches.
+Note that the Ferrenti approaches are employed as a filter on the predictions of the empirical one.
 
@@
 
-From the predicted dataset of \mrk{\num{23623}} materials  
+From the predicted dataset of \num{23623} materials  
 %the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach. 
@@
 If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
-We find that \mrk{the} ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with \mrk{complex structures (e.g., nanostructures or 2D materials)} to be labeled as suitable candidates.
+We find that the ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
+This can allow materials with complex structures (e.g., nanostructures or 2D materials) to be labeled as suitable candidates.
 Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than \SI{0.5}{\electronvolt} were eliminated.
 This trend is not carried over to the predicted data.
-Indeed, \mrk{many} entries with band gaps lower than \SI{0.5}{\electronvolt} are predicted as suitable candidates by all four ML methods employed herein
+Indeed, many entries with band gaps lower than \SI{0.5}{\electronvolt} are predicted as suitable candidates by all four ML methods employed herein
 %indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
 --- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
-\mrk{This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.}
+This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.
 On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
 
-\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
+The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
 Indeed, NaCl is predicted as a suitable candidate to minimum confidences of $0.83$ and $0.61$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
@@
 For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
-}
 
@@
 \subsubsection*{The empirical approach}
-The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the \mrk{Ferrenti approach}. 
+The ML methods that were trained on the data extracted in the empirical approach predict substantially fewer candidates as compared to the Ferrenti approach. 
 A total of $842$, $1197$, $543$ and $596$ materials are classified as suitable candidates by logistic regression, decision trees, random forests and gradient boosting, respectively.
@@
 %Although this is comparable to the probability of a coin toss, the agreement of the four ML algorithms lends support to the suitability of the $214$ materials. 
-Note that $51$ of these have a band gap of \SI{0.5}{\electronvolt} \mrk{or smaller}.
+Note that $51$ of these have a band gap of \SI{0.5}{\electronvolt} or smaller.
 Increasing the threshold to $0.75$ or $0.85$ yields $66$ or $9$ predicted suitable candidate materials in the empirical approach, respectively (see~Table~\ref{tab:probabilites}).
@@
 Figure~\ref{fig:crystalsystems} visualizes the four different crystal systems while Table~\ref{tab:materialproperties} lists important material properties of the relevant materials as reported in the MP database.
-Interestingly, \mrk{all} nine materials appear to be four-fold coordinated, \mrk{and the first two lattice vectors ($a$ and $b$) are identical in all cases} whereas $c$ may differ.
-There appears to be a high degree of symmetry present for all materials, but \mrk{no elemental and perfectly symmetric semiconductors were found} in the list.
+Interestingly, all nine materials appear to be four-fold coordinated, and the first two lattice vectors ($a$ and $b$) are identical in all cases whereas $c$ may differ.
+There appears to be a high degree of symmetry present for all materials, but no elemental and perfectly symmetric semiconductors were found in the list.
 
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{AllFigures/fig6-all.png}
-    \caption{\mrk{Example illustrations} of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence\mrk{,} belong to.
+    \includegraphics[width=0.85\textwidth]{figure6.png}
+    \caption{Example illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, belong to.
 Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
@@
 %Turning to each of the individual material predictions, the compound BN (mp-$1639$) was in fact present in the training data as a suitable candidate, and we believe this to be a partial explanation for why the ML methods recognize BN as a suitable candidate with high probability.
-\mrk{Turning to each of the individual material predictions, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) are predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.}
+Turning to each of the individual material predictions, two compositions of CdSe (the cubic mp-$2691$ and the hexagonal mp-$1070$) are predicted as suitable, possibly as a consequence of the similar compound CdS being labeled as a suitable candidate in the training set.
 The two compounds of CdSe share similar properties with calculated band gaps in the MP database of \SI{0.5}{\electronvolt} and \SI{0.6}{\electronvolt}, respectively. 
-\mrk{The compound BN (mp-$1639$) was also predicted as suitable possibly due to a different BN crystal structure being present in the training set and labeled as a suitable candidate}.
+The compound BN (mp-$1639$) was also predicted as suitable possibly due to a different BN crystal structure being present in the training set and labeled as a suitable candidate.
 
@@
 The band gaps are listed as \SI{1.9}{\electronvolt} and \SI{1.7}{\electronvolt}, respectively, in the MP database.
-Both structures \mrk{exhibit a} strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-\mrk{Interestingly}, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
+Both structures exhibit a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+Interestingly, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
 By creating a boron vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
 Whether this is also possible for BC$_2$N remains to be seen.
-\mrk{Note} that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
+Note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
 
@@
 Interestingly, the material exhibits a large ionic character
-\mrk{and shares few similarities with known QT compatible hosts such as, e.g.,} Si, SiC and  diamond.
-The prediction of CuI in two configurations \mrk{thus} indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
+and shares few similarities with known QT compatible hosts such as, e.g., Si, SiC and  diamond.
+The prediction of CuI in two configurations thus indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
 It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
@@
 In comparison, the experimentally reported band gap is somewhat larger at \SI{2.0}{\electronvolt} \cite{Xing1989}.
-ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits  \mrk{covalent bonding} and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits covalent bonding and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-\mrk{ZnGeP$_2$ is therefore identified} as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
+ZnGeP$_2$ is therefore identified as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
 
@@
     \centering 
-    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach \mrk{($>0.85$ confidence) and the $6$ materials predicted by all approaches ($>0.75$ confidence).} %Compounds marked by an asterisk are predicted to be unstable to transformation into other phases in the MP database.
+    \caption{Overview of material properties as listed in the MP database for the $9$ materials predicted by the empirical approach ($>0.85$ confidence) and the $6$ materials predicted by all approaches ($>0.75$ confidence).
+%Compounds marked by an asterisk are predicted to be unstable to transformation into other phases in the MP database.
     }
@@
 
-Among the \mrk{list of $66$ we also highlight the predictions} of interesting materials like \mrk{Ge, sharing many characteristics with Si and C in addition to the periodic column number,  %(in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$),
-GeC, BP and InP.}  
+Among the list of $66$ we also highlight the predictions of interesting materials like Ge, sharing many characteristics with Si and C in addition to the periodic column number,  %(in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$),
+GeC, BP and InP. 
 %The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number. 
 %Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
-\mrk{Much} like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.  
+Much like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.  
 Similar considerations could be made for the case of GeC. 
@@
 Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities with SiC. 
-Next, \mrk{BP} (mp-$1479$ and mp-$1008559$) is present in \mrk{the} predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at \SI{1.5}{\electronvolt} and \SI{1.1}{\electronvolt}, respectively.
+Next, BP (mp-$1479$ and mp-$1008559$) is present in the predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at \SI{1.5}{\electronvolt} and \SI{1.1}{\electronvolt}, respectively.
 Both configurations of BP are nonmagnetic, non-toxic and BP has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
@@
 %was also predicted as a suitable candidate to $0.75$ confidence. The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra. 
-\mrk{in the hexagonal structure} 
+in the hexagonal structure 
 is reported in the Materials Project to have a direct band gap of \SI{0.5}{\electronvolt} and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-\mrk{The possibility of using InP-based quantum dots for QT applications should therefore be considered.}
+The possibility of using InP-based quantum dots for QT applications should therefore be considered.
 
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, \mrk{only a single material is present in the list of $66$ candidates predicted by the four ML methods} in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a \SI{2.0}{\electronvolt} band gap and decomposes to a similar MgSe configuration.
+Among these, only a single material is present in the list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a \SI{2.0}{\electronvolt} band gap and decomposes to a similar MgSe configuration.
 %The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported at $2.45$~eV (optical band gap) \cite{Ubale2014}. 
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010}\mrk{.}  
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010}.  
 %and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}. 
@@
 The empirical approach, on the other hand, predicts fewer suitable candidates that are possible to examine  manually.
-\mrk{The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
-The same cannot be said for the Ferrenti approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible\mrk{,} and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
-
-Despite notable differences, as mentioned above, there is \mrk{overlap of predicted materials between the approaches}. 
+The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
+The same cannot be said for the Ferrenti approach, however, as seen from Table~\ref{tab:probabilites}.
+Manual verification through a literature survey will often not be possible, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+
+Despite notable differences, as mentioned above, there is overlap of predicted materials between the approaches. 
 %We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach.
 Similarly, $78$ of the $214$ materials are also predicted as suitable by all ML methods in the Ferrenti approach.
-All approaches \mrk{(including the extended Ferrenti approach) and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence 
+All approaches (including the extended Ferrenti approach) and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence 
 %where $8$ are elementary (unary), $29$ binary, and $10$ tertiary 
-(see the Supplementary Information at \cite{supplementary} for the full list).} 
+(see the Supplementary Information at \cite{supplementary} for the full list). 
 Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
-However, certain materials that cannot be classified as semiconductors \mrk{are also included}, such as P, I, N$_2$ and H$_2$.
+However, certain materials that cannot be classified as semiconductors are also included, such as P, I, N$_2$ and H$_2$.
 We note that none of these were included by the empirical approach when the threshold was set to $0.75$ or above.
@@
 %Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
-\mrk{with comparable trends to those for the $9$ materials predicted by the empirical approach in terms of, e.g., crystal structure.
+with comparable trends to those for the $9$ materials predicted by the empirical approach in terms of, e.g., crystal structure.
 The six-fold coordination of GeSe is an outlier as compared to the four-fold coordination of the other materials.
-}
 %We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP.
@@
     \centering
-    \input{figures/histograms/revised/LegendHistogram.tex}
+    \includegraphics{figure7-legend.pdf}
   \end{subfigure}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/revised/MP_Eg_count_075.tex}
+    \includegraphics{figure7a.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/revised/IonProperty_max ionic char_count_075.tex}
+    \includegraphics{figure7b.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/revised/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
+    \includegraphics{figure7c.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/revised/AverageBondLength_std_dev Average bond length_count_075.tex}
+    \includegraphics{figure7d.pdf}
     \subcaption{}
 \end{subfigure}
-\caption{Histograms of predicted suitable materials as a function of the (a) \mrk{band gap}, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
+\caption{Histograms of predicted suitable materials as a function of the (a) band gap, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
 The total number of predicted materials is  $6804$ for the Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti \mrk{approach refers} to the left $y$-axis and the empirical approach to the right.
+The Ferrenti approach refers to the left $y$-axis and the empirical approach to the right.
 }
@@
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the ML methods revealed that the most important principal component for \mrk{the Ferrenti approach} encompasses features related to the band gap and chemical environment.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for the Ferrenti approach encompasses features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
 %In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process. 
-\mrk{The Ferrenti approach does not entirely reproduce the logic of the initial selection process, however, as several low band gap ($<0.5$~eV) materials were highlighted as suitable by the ML methods.}
+The Ferrenti approach does not entirely reproduce the logic of the initial selection process, however, as several low band gap ($ < \SI{0.5}{\electronvolt}$) materials were highlighted as suitable by the ML methods.
 For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.
 
-Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that \mrk{both} approaches predicted a substantial amount of materials with a low band gap (below \SI{0.5}{\electronvolt}).
-Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti \mrk{approach} exhibiting a peak around a \SI{2.5}{\electronvolt} band gap. 
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that both approaches predicted a substantial amount of materials with a low band gap (below \SI{0.5}{\electronvolt}).
+Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti approach exhibiting a peak around a \SI{2.5}{\electronvolt} band gap. 
 Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around \SI{2.5}{\electronvolt} using the PBE functional. 
@@
 The second most important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for \mrk{both the Ferrenti and empirical} approaches --- even peaking at a relatively high ionic character of $0.8$.
-We note that this may be a result of the distribution of the initial dataset of \mrk{\num{25000}} materials \mrk{with a maximum} around a similar value (not shown).
-The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach \mrk{nor} the overall data distribution.
-For \mrk{reference}, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
-\mrk{Furthermore, the} covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
+Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for both the Ferrenti and empirical approaches --- even peaking at a relatively high ionic character of $0.8$.
+We note that this may be a result of the distribution of the initial dataset of \num{25000} materials with a maximum around a similar value (not shown).
+The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach nor the overall data distribution.
+For reference, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
+Furthermore, the covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 The ML methods in the empirical approach consistently identified the first principal component as the predominant one.
-Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that \mrk{matters}.
-Here, \mrk{the} standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in \mrk{Figure}~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
-Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the \mrk{Ferrenti} and the empirical approach.
-For the empirical approach, there is a sharp peak in the preferred value for the standard deviation \mrk{of} the RDF, while the Ferrenti \mrk{approach displays} an even distribution across a broader range.
-\mrk{These observations emphasize the importance of symmetry related material properties for QT suitability. }
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that matters.
+Here, the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
+One configuration of the standard deviation of the RDF is demonstrated in Figure~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
+Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti and the empirical approach.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation of the RDF, while the Ferrenti approach displays an even distribution across a broader range.
+These observations emphasize the importance of symmetry related material properties for QT suitability.
 
@@
 This resonates with the observations from the principal component analysis; an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but some variations throughout the crystal in, e.g., bond length and symmetry are needed.
-This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti \mrk{approach}.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered \mrk{equally and may even be more important.}
+This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti approach.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered equally and may even be more important.
 
@@
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
-For example, in \mrk{high symmetry materials like diamond and silicon}, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
-Instead, \mrk{quantum} effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
-For \mrk{a binary system like silicon carbide}, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
+For example, in high symmetry materials like diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
+Instead, quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
+For a binary system like silicon carbide, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
 While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT compatible properties to manifest in a semiconductor host.
 
-\mrk{It should be noted that performing machine learning on a dataset derived using preconceived notions for which material properties are important may reproduce several of the initial selection criteria.
+It should be noted that performing machine learning on a dataset derived using preconceived notions for which material properties are important may reproduce several of the initial selection criteria.
 Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the empirical one.
 Additionally, ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.
-Finally, the Ferrenti approaches are employed as a filter on the empirical approach, to provide a better tuned list of candidates for future experimental studies.}
-
-To summarize, \mrk{we have developed data extraction tools and strategies for data mining and labeling to enable the automated search and analysis of host materials for QT.} 
+Finally, the Ferrenti approaches are employed as a filter on the empirical approach, to provide a better tuned list of candidates for future experimental studies.
+
+To summarize, we have developed data extraction tools and strategies for data mining and labeling to enable the automated search and analysis of host materials for QT. 
 %the data extraction tools developed in this work resulted in a dataset of over \mrk{\num{25000}} materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training and testing of four ML algorithms.
-\mrk{The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is highly suitable for performing this type of guided search through materials databases.}
+The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is highly suitable for performing this type of guided search through materials databases.
 %We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
 %Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
-The principal component analyses of the ML methods' performance imply that the Ferrenti \mrk{approach with its} strong focus on band gap and bonding character when assessing a material's quantum compatibility \mrk{to some extent reproduces} the specifications of the data labeling process, \mrk{as expected.}
-Valuable insight is gained from \mrk{comparing the important features of the Ferrenti with those for} the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions \mrk{over expected features related to band gap and bonding}.
-\mrk{As such, the expected properties are not able to capture the full physics of the problem.
+The principal component analyses of the ML methods' performance imply that the Ferrenti approach with its strong focus on band gap and bonding character when assessing a material's quantum compatibility to some extent reproduces the specifications of the data labeling process, as expected.
+Valuable insight is gained from comparing the important features of the Ferrenti with those for the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions over expected features related to band gap and bonding.
+As such, the expected properties are not able to capture the full physics of the problem.
 The contrast between the Ferrenti and empirical approaches reveals that the problem of QT compatibility is more complex than being related to band gap and bonding character alone.
 Based on our findings we propose that the manifestation of quantum effects in semiconductors is related to the crystal structure symmetry and bonding.
-}
 
 The findings presented here firmly establish that material informatics is a viable and important route to new discoveries in important fields. 
-Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the \mrk{developed framework} is suitable for other fields as well.
-\mrk{Two possible paths are suggested to further exploit the findings presented herein.} One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by \mrk{machine learning}.
-Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process\mrk{es} to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
+Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the developed framework is suitable for other fields as well.
+Two possible paths are suggested to further exploit the findings presented herein.
+One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by machine learning.
+Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction processes to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
 
@@
 
-The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than \mrk{\num{600000}} materials.
+The Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015} contains thermodynamic and structural properties of more than \num{600000} materials.
 The calculations are performed with the VASP software and the electron exchange and correlation are described with the PBE functional.
@@
 
-JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly \mrk{\num{40000}} three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
+JARVIS-DFT \cite{Choudhary2020} is an open-source database based on the VASP software and consists of roughly \num{40000} three-dimensional materials using the vdW-DF-OptB88 (OPT) functional \cite{Thonhauser2007, Klimes2011}.
 Structures included in the database are originally taken from the Materials Project \cite{Jain2013, Jain2018}, and then re-optimized using the OPT functional.
 Finally, the combination of the OPT and modified Becke-Johnson (mBJ) functionals \cite{Tran2009} is used to obtain a representative band gap for each structure \cite{Choudhary2018a}.
-Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on \mrk{\DTMdisplaydate{2021}{4}{30}{-1}} (see Ref.
+Data extraction from JARVIS-DFT was done in January of $2021$, were we utilized the version made available on \DTMdisplaydate{2021}{4}{30}{-1} (see Ref.
 \cite{Choudhary2020}).
@@
 The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
-They utilize the PBE functional \mrk{(with the $+U$ correction for certain cases)} within VASP to relax and optimize all structures from the ICSD.
+They utilize the PBE functional (with the $+U$ correction for certain cases) within VASP to relax and optimize all structures from the ICSD.
 Data extraction was performed in the period of January to February of $2021$.
@@
 
-\mrk{Note that from the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
+Note that from the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
 This ID is included in the AFLOW,  AFLOW-ML, JARVIS-DFT and OQMD databases as well.
@@
 For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
-space group, symmetry) of the material.}
-
-\mrk{The data regarding a material's magnetic character is extracted from the Materials Projects database.
+space group, symmetry) of the material.
+
+The data regarding a material's magnetic character is extracted from the Materials Projects database.
 Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
@@
 We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
-This is an improvement that could be made to our method in a future study.}
+This is an improvement that could be made to our method in a future study.
 
@@
 
-\mrk{Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
-The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.}
+Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
+The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
 
@@
 The codes employed to develop the machine learning results are available online at \cite{Ohebbi2021}.
-
-\bibliography{apssamp}
 
@@
 
+\bibliographystyle{naturemag}
+\bibliography{apssamp}
+
 \section*{Additional information}
-Correspondence and requests for materials should be addressed to \url{bathen@aps.ee.ethz.ch}.
+Correspondence and requests for materials should be addressed to
+\mrk{\href{mailto:bathen@aps.ee.ethz.ch}{bathen@aps.ee.ethz.ch}}.
+
+\listoffigures
 

### 2022-08-15 revision/revised-paper_clean.tex
Updates from Overleaf

--- 2022-03-28 paper_v3_cut.tex
@@
 
-%\newcommand\abs[1]{\left|#1\right|}
-%\newcommand\bra[1]{\left| #1 \right \rangle}
-%\newcommand\ket[1]{\left \langle #1 \right |}
-
-\newcommand{\oliver}[1]{\textcolor{violet}{#1}} 
-\newcommand{\morten}[1]{\textcolor{green}{#1}}
-\newcommand{\sebastian}[1]{\textcolor{cyan}{#1}}
-\newcommand{\marianne}[1]{\textcolor{blue}{#1}}
-\newcommand{\oyvind}[1]{\textcolor{maroon}{#1}}
-\newcommand{\lasse}[1]{\textcolor{red}{#1}}
+\newcommand{\mrk}[1]{\textcolor{black}{#1}}
+\usepackage[useregional]{datetime2}
 
@@
 Semiconductor materials provide a compelling platform for quantum technologies (QT), and the properties of a vast amount of materials can be found in databases containing information from both experimental and theoretical explorations.
-However, searching these databases to find promising candidate materials for quantum technology applications
-is a major challenge.
-Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over $25.000$ materials and nearly $5000$ physics-informed features.
-Three approaches were devised, named the Ferrenti, extended Ferrenti and the empirical approach,  to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting.
-We find that of the three, the empirical approach relying exclusively on findings from the literature predicted substantially fewer candidates than the other two approaches with a clear distinction between suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
-In contrast to expectations from the literature and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
+However, searching these databases to find promising candidate materials for quantum technology applications is a major challenge. 
+Therefore, we have developed a framework for the automated discovery of semiconductor host platforms for QT using material informatics and machine learning methods, resulting in a dataset consisting of over \mrk{\num{25000}} materials and nearly \num{5000} physics-informed features.
+\mrk{Three different approaches were devised} to label data for the supervised machine learning (ML) methods logistic regression, decision trees, random forests and gradient boosting. 
+We find that \mrk{among these, the} empirical approach relying exclusively on findings from the literature \mrk{exhibited the clearest  distinction}  between \mrk{predicted} suitable and unsuitable candidates when comparing the two largest eigenvalues in the covariance matrix.
+In contrast to expectations from the literature  %and that found for the Ferrenti and extended Ferrenti approaches focusing on band gap and ionic character, 
+\mrk{focusing on band gap and ionic character as important features for QT compatibility,}  
+the ML methods from the empirical approach highlighted features related to symmetry and crystal structure, including bond length, orientation and radial distribution, as influential when predicting a material as suitable for QT.
 All three approaches and all four ML methods agreed on a subset of $47$ eligible candidates 
@@
 \section*{Introduction}
-Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during the last few years. 
+Quantum technologies (QT) based on solid state platforms have attracted a lot of attention during \mrk{recent}  years. 
 Among the promising applications that are already available we find important breakthroughs such as in vivo sensing of magnetic fields in cells \cite{Lesage_2013}, secure communication over large distances by separation of entangled photons \cite{Ursin2007} and, notably, various quantum information processing prototypes and architectures \cite{Arute_2019}.
 Quantum computers are in high demand to meet the increasing need for computing power to solve complex and high-dimensional scientific problems.
-%that are beyond the capability of existing high-performance computing %facilities.   
 Recent advances have highlighted the potential of quantum information processors to outperform state-of-the art high-performance computing facilities.
-Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a $200.000$ core supercomputer \cite{Arute_2019}.
+Indeed, Google's $53$ qubit quantum computer based on superconducting electronics solved a computational problem that was beyond the capabilities of a \mrk{\num{200000}} core supercomputer \cite{Arute_2019}.
 Most recently, IBM announced its $127$ qubit quantum processor~\cite{IBM2021}.
@@
 
-Here we provide a framework for the data mining and automated discovery of promising solid-state semiconductor hosts for quantum emitters and spin centers using targeted database search and ML methods combined with knowledge from the field.
+\mrk{Herein, a framework is provided} for the data mining and automated discovery of promising \mrk{semiconductor hosts for QT} using targeted database search and ML methods combined with knowledge from the field.
 Analyzing the output of the ML methods reveals that, given a suitable initial set of labeled materials for training and testing, it is possible to discern the physical mechanisms that govern a material's suitability for quantum applications.
-In this framework we do not distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
-The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data are available.
-
-The developed procedure relies on data extraction from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
-The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data.
-An important aspect of our work is the database building and pertinent development of the datasets for the ML methods.
-We have developed three different approaches to data mining: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
-We find that the two first methodologies base their data extraction protocols on broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
+\mrk{This framework does not} distinguish between the specific mechanism giving rise to properties such as single-photon emission and long spin coherence times (e.g., semiconductor defects or quantum dots); instead, we attempt to target all materials that may accommodate the desired characteristics.
+The methodology developed herein can be modified for other material types and application areas provided that high quality databases containing relevant theoretical and/or experimental data \mrk{is} available.
+
+The developed procedure relies on data extraction \mrk{from different databases and the subsequent featurization of the data.} 
+%from the databases Materials Project \cite{Jain2013,Jain2018}, the Open Quantum Materials Database (OQMD) \cite{Saal2013, Kirklin2015}, JARVIS-DFT \cite{Choudhary2020}, AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} and AFLOW-ML \cite{Isayev2017}.
+%The Matminer Python library for data mining \cite{Ward2018} was then used for material analysis to featurize the extracted data. 
+An important aspect of \mrk{the} work is the database building and pertinent development of the datasets for the ML methods.
+\mrk{Three different approaches to data mining were devised}: (i) \emph{the Ferrenti approach} which is similar to that proposed by \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, (ii) \emph{the extended Ferrenti approach} and (iii) \emph{the empirical approach}.
+\mrk{The} two first \mrk{data extraction protocols are based on} broad material descriptors, leading to large sets of potentially suitable candidates \cite{Mehta2019,Hastie2009}.
 The empirical approach, on the other hand, relies on including materials with experimentally proven advantageous characteristics in the training set and therefore yields a narrower set of possible candidates.
-The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding $214$ predicted candidates that were common between all approaches and ML methods.
-Example materials include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP.
-Focused theoretical and experimental studies, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, are needed to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials.
+The three resulting sets of labeled data were then analyzed with the four supervised ML methods logistic regression, decision trees, random forests and gradient boosting \cite{Hastie2009,Murphy2012}, yielding \mrk{$47$} predicted candidates that were common between all approaches and ML methods.
+Example materials \mrk{among the predictions} include ZnGeP$_2$, CdS, BP, BC$_2$N, GeC and InP. Focused theoretical and experimental studies 
+%, using methods such as, e.g., density functional theory, photoluminescence spectroscopy and optically detected magnetic resonance, 
+\mrk{are needed} to verify the predictions that quantum properties may manifest as a result of defects or nanostructures in the above listed materials. 
 %Write better! 
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
+    \includegraphics[width=0.9\textwidth]{figure2.png}
     \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
-    To limit the memory and computational usage, the data are partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
+    To limit the memory and computational usage, the data \mrk{is} partitioned into smaller subsets where the respective Pymatgen objects (Pymatgen is a robust, open-source Python library for materials analysis \cite{pymatgen}) are obtained through a query to be used in the following featurization steps.
 This process is repeated iteratively until all the data has been featurized.
@@
 and focuses on a material's composition,  structure, atomic sites, density of states and band structure. 
-The $39$ featurizers (each generates several features) selected as material descriptors in this work are summarized and described in the Supplementary Information at \cite{supplementary}.
-The selection of features was kept rather wide as we do not want to make {\em ex ante} assumptions on which features best describe a solid state material platform for quantum technology.
+The $39$ featurizers (each generates several features) selected as material descriptors in this work are \mrk{described} in the Supplementary Information at \cite{supplementary}.
+The selection of features was kept rather wide \mrk{to avoid making} {\em ex ante} assumptions on which features best describe a solid state material platform for \mrk{QT}.
 
 The constructed dataset encompasses compounds formed by a plethora of combinations of surfaces, interfaces, nanostructures, compositions and structures, but this complexity is not necessarily reflected in the material descriptors.
-Furthermore, we have utilized data obtained from high-throughput density functional theory calculations.
-Indeed, there are possible errors associated with every step, starting from an initial calculation, adding of data in the database, gathering of data, featurization of data, preprocessing of data, data mining, and finally training a model and making a prediction.
-Unfortunately, if an error has happened in the first part of the process, the error follows the entire process and will get increasingly harder to detect.
-Thus, our results depend on the quality of data in the databases we employ.
+Furthermore, \mrk{the extracted data was}  obtained from high-throughput density functional theory calculations.
+Indeed, there are possible errors associated with every step, starting from an initial calculation, \mrk{adding of data in the database, featurization and preprocessing the data, data mining and labeling, and finally training a model and making a prediction.}  Unfortunately, if an error \mrk{occurrs} in the first part of the process, \mrk{it will be  carried along and get} increasingly harder to detect.
+Thus, \mrk{the output strongly depends}  on the quality of data in the \mrk{employed} databases.
 
 \subsection*{Data Mining}
-The complete dataset consists of $25.000$ materials.
+The complete dataset consists of \mrk{\num{25000}} materials.
 A subset of these materials is labeled into either suitable or unsuitable candidates for QT while the remainder will stay unlabeled.
-The labeled data are then grouped into training and test sets for the ML methods.
-
-Several challenges accompany the labeling process of labeling materials according to their suitability for QT. 
+The labeled data \mrk{is} then grouped into training and test sets for the ML methods.
+\mrk{The ML methods are trained using the training set and then evaluated on the test set.
+Finally, the ML methods are applied to the unlabeled data for which predictions of QT suitability are made.}
+
+Several challenges accompany the labeling \mrk{process.} 
+%of labeling materials according to their suitability for QT. 
 Although QT compatible properties are becoming increasingly well studied for the case of, e.g., nitrogen-vacancy centers in diamond, single-photon emitters in silicon carbide and quantum dot (QD) structures \cite{Doherty_2013,Bathen2021,Aharonovich_2016}, relatively few candidate materials are known to be suitable  \cite{Atatuere2018,Zhang2020}.
 An additional consideration is that the physical mechanisms promoting favorable properties are not fully understood.
-Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are also unknown. 
-The strategy for selection of unsuitable candidates is thus that the negation of the criteria we use to select suitable candidates should give unsuitable candidates.
-A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates. 
-We will then find ourselves in a situation with skewed data sets were we have fewer unsuitable than suitable candidates. 
+Conversely, defining materials as unsuitable candidates for QT is in many ways equally difficult, as the mechanisms preventing quantum compatible characteristics to manifest are \mrk{not known either}.
+The strategy for selection of unsuitable candidates is thus that the negation of the criteria \mrk{used} to select suitable candidates should give unsuitable candidates.
+A side-effect of this selection is that the criteria for unsuitable candidates can become equally, or more, restrictive compared to the criteria for suitable candidates\mrk{, resulting in} skewed datasets \mrk{with} fewer unsuitable than suitable candidates.
 This method for selecting unsuitable candidates has shortcomings but will serve as a starting point and demonstration for how the labeling procedure could be improved. 
-Below we follow three separate procedures for labeling materials as suitable or unsuitable candidates for QT.
+Below \mrk{three separate procedures for labeling materials as suitable or unsuitable candidates for QT are described}.
 
@@
 They suggest a data mining process consisting of four stages by systematically evaluating the suitability of host materials taken from the Materials Project. 
-In this framework, we label \textbf{suitable} candidates by the following steps:
+\mrk{Note that the data mining process in Ref.~\cite{Ferrenti2020} alone was intended for further experimental studies and not necessarily for a targeted machine learning search.
+Nonetheless, we adapt the selection criteria from Ref.~\cite{Ferrenti2020} for the present purposes.}
+In the \mrk{\emph{Ferrenti approach}} framework, \textbf{suitable} candidates \mrk{are labeled} by the following steps: 
 \begin{enumerate}
@@
     \begin{itemize}
-        \item contain elements with more than $50 \ \%$ natural abundance of spin zero isotopes,
-        \item crystallize in non-polar space groups,
-        \item are present in the ICSD database, 
-        and
-        \item are calculated to be nonmagnetic. 
+        \item contain elements with more than \SI{50}{\percent} natural abundance of spin zero isotopes,
+        \item crystallize in non-polar space groups, \mrk{are calculated to be nonmagnetic, and 
+        are present in the ICSD.}
     \end{itemize}
@@
     \end{itemize}
-    \item Include only materials with a band gap larger than $0.5$~eV calculated using DFT and the PBE functional.
-The value of $0.5$~eV was chosen to match that typically predicted for silicon by PBE-level DFT calculations.
-    \item Ensure that the energy above hull is less than $0.2$~eV per atom.
+    \item Include only materials with a band gap larger than \SI{0.5}{\electronvolt} calculated using DFT and the PBE functional.
+    The value of \SI{0.5}{\electronvolt} was chosen to match that typically predicted for silicon by PBE-level DFT calculations. 
+    \item Ensure that the energy above hull is less than \SI{0.2}{\electronvolt} per atom.
 \end{enumerate}
 
-These inclusion criteria are based on the work of \citeauthor{Weber2010} \cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
-In this context, long spin coherence times are needed, and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable.
-Moreover, non-polar materials are assumed to be preferable to obtain defect based single-photon emitters with sharp zero-phonon lines and indistinguishable single-photon emission.  
+\mrk{The} inclusion criteria are based on \mrk{Ref.}~\cite{Weber2010} and targeted primarily at semiconductors that can host deep level defects with spin qubit capabilities.
+In this context, long spin coherence times are needed, \mrk{necessitating an environment that can be depleted of nuclear spins and permanent magnetism.}
+%and the possibility of having an environment free of nuclear spins and permanent magnetism is therefore desirable. 
+Moreover, non-polar materials are assumed to be preferable to obtain \mrk{sharp and indistinguishable single-photon emission from defects}.  
 Transition metal elements are eliminated if they have unpaired electrons because the presence of permanent electric dipole moments may have a detrimental impact on the optical coherence of defect emission.
-Finally, the energy above hull requirement is included to ensure that the selected compounds are thermodynamically stable.
-
-Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the ICSD database \cite{Allen1987,Zagorac2019} 
-that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than $0.1$~eV in the MP database (to exclude metals but include lower-band gap semiconductors). 
-The resulting set of labeled materials contains $1581$ materials where $35 \ \%$
-are labeled as unsuitable and 
-$65 \ \%$ as suitable for QT applications.
-Here we see the first example of how the criteria for labeling unsuitable candidates are more restrictive than those for the suitable candidates.
+Finally, the energy above hull requirement \mrk{ensures} that the selected compounds are thermodynamically stable.
+\mrk{Note that larger cells are sometimes needed to verify antiferromagnetic ordering so the criteria mainly target ferromagnetic ordering under the labels magnetic/non-magnetic.}
+
+Next, \textbf{unsuitable} candidates are labeled according to the reverse requirements of the above; as materials in the \mrk{ICSD} that crystallize in polar space groups, are calculated to be magnetic and have a band gap larger than \SI{0.1}{\electronvolt} in the MP database (to exclude metals but include lower-band gap semiconductors).
+The resulting set of labeled materials contains $1581$ materials where \SI{35}{\percent}
+are labeled as unsuitable and \SI{65}{\percent} 
+as suitable for QT applications, \mrk{evidencing that} 
+%Here we see the first example of how 
+the criteria for labeling unsuitable candidates are more restrictive than those for the suitable \mrk{ones}.
+
+%Ferrenti 
+\mrk{Considering the materials present in the labeled dataset of the Ferrenti approach more closely, we find that diamond is classified as a suitable candidate, in good agreement with experimental observations.
+Interestingly, carbon in two-dimensional graphite-like structures are marked as suitable as well.
+All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
+Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
+Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.}
 
 \subsubsection*{The extended Ferrenti approach}
-Here, we adjust the Ferrenti approach to expand the data labeling process beyond practical  considerations.
+\mrk{The Ferrenti approach was adjusted} to expand the data labeling process beyond practical  considerations.
 The second approach is therefore named \emph{the extended Ferrenti approach} and involves removing stage two from the approach above.
-Moreover, we include a few additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes.
-
-The following steps constitute the process of labeling \textbf{suitable} candidates in the \emph{extended Ferrenti approach}:
+Moreover, \mrk{certain} additional elements that have shown promising properties but were initially excluded due to the lack of spin zero isotopes \mrk{are also included}.
+
+The following steps constitute the process of labeling \textbf{suitable} candidates in the \mrk{extended Ferrenti approach}:
 \begin{enumerate}
@@
         \item crystallize in non-polar space groups,
-        \item are present in the ICSD,
-        \item are calculated to be nonmagnetic. 
+        \mrk{are calculated to be nonmagnetic and are present in the ICSD} 
     \end{itemize}
-    \item Only keep materials that have a band gap larger than $1.5$~eV in the MP database.
+    \item Only keep materials that have a band gap larger than \SI{1.5}{\electronvolt} in the MP database.
 The higher band gap requirement (as compared to the Ferrenti approach) is included here to avoid labeling an unfeasibly large number of materials.
-    \item Ensure that the energy above hull is less than $0.2$~eV per atom. 
+    \item Ensure that the energy above hull is less than \SI{0.2}{\electronvolt} per atom. 
 \end{enumerate}
 
-For \textbf{unsuitable} candidates, we implement the same strategy as for the first Ferrenti approach.
-The result is a somewhat unbalanced set of labeled materials, with up to $75 \ \%$ of the materials found in the suitable group.
-However, the labeled data encompasses $78 \ \%$ more materials than  the Ferrenti approach, consisting of $2141$ suitable and $684$ unsuitable materials.
+For \textbf{unsuitable} candidates, \mrk{the same strategy as for the Ferrenti approach was implemented}.
+The result is \mrk{an unbalanced set of labeled materials that is   \SI{78}{\percent} larger than for the Ferrenti approach and having $\sim$\SI{75}{\percent} of the materials found in the suitable group.}
+
+\mrk{The findings from both the data mining and machine learning procedures for the extended Ferrenti approach did not differ substantially from those obtained using the Ferrenti approach.
+This is attributed to the similarities in the selection processes.
+Therefore, detailed discussion on the findings from the extended Ferrenti approach can be found in the Supplementary Information at \cite{supplementary}.
+Qualitative conclusions drawn for the Ferrenti approach herein also hold for the extended Ferrenti approach, indicating that the removal of so-called practical considerations did not have a significant impact on the results.
+Nonetheless, predictions from the extended Ferrenti approach will be employed below to contrast with and filter the findings from the empirical approach.
+}
 
 \subsubsection*{The empirical approach} 
-The third approach differs substantially from the others in terms of material labeling, as we apply knowledge from the field (see for instance Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to pick our promising material host candidates.
-In other words, we restrict ourselves to materials where quantum compatible properties have been either experimentally demonstrated or theoretically predicted. 
-We therefore name this scheme \emph{the empirical approach}.
-Due to the concern of ending up with too small datasets for training and testing of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
-These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}.
-We have also included materials where properties like single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related.
+\mrk{In the \emph{empirical approach},} we apply knowledge from the field (see for instance  Refs.~\cite{Atatuere2018,Toth2019,Zhang2020,Son2020} for an overview) to \mrk{guide the search for} promising material \mrk{hosts.}
+In other words, \mrk{the labeled data contains candidates} where quantum compatible properties have been either experimentally demonstrated or theoretically predicted\mrk{, including the materials suggested in Ref.~\cite{Weber2010} as promising deep level defect hosts.}
+%We therefore name this scheme \emph{the empirical approach}. 
+%Due to the concern of ending up with too small datasets for training and testing of the ML methods, we will also include some  materials that are promising in the sense that they have suitable properties for accommodating deep level defects that can potentially exhibit quantum effects --- even though such effects may not yet have been shown.
+%These material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}. 
+%\mrk{The theoretical predictions were motivated by the criteria for having deep level defects exhibit quantum compatible properties \cite{Weber2010}.} 
+%material choices were motivated by the criteria and predictions for QT compatible deep level defects defined by \citeauthor{Weber2010} \cite{Weber2010}. 
+\mrk{Materials where single-photon emission and spin manipulation have been observed but attributed to excitonic effects or quantum dots (formed by self-assembly or lithographic structuring) rather than being defect related were also included.}
 
@@
 
-After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than $0.4$~eV.
-These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than $0.5$~eV.
-We include all of the $202$ structures apart from C (mp-$568410$) which is a metal according to AFLOW-ML.
-
-Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ (quantum compatible characteristics have been demonstrated) were manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
-For carbon, we admit three-dimensional diamond-like structures as explicitly stated in the column tags from the Materials Project.
-Additionally, we find several two-dimensional structures of carbon with a large band gap ($>1.5$~eV) among the data.
-We add these as suitable candidates.
+After the first stage of picking candidates we are left with a list of $202$ matching formulas which includes $12$ entries that have a band gap of less than \SI{0.4}{\electronvolt}.
+These $12$ entries are calculated to be thermodynamically unstable in terms of the energy above hull, and will decompose into other materials in the list --- incidentally, the resulting structures all have calculated band gaps that are substantially larger than \SI{0.5}{\electronvolt}.
+\mrk{All of the $202$ structures were included in the labeled dataset apart from C (mp-$568410$) which is a metal according to AFLOW-ML. }
+
+\begin{figure}[t] %!htp
+    \centering
+    %\begin{subfigure}{1\textwidth}
+    %    \centering
+    %    \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
+    %\end{subfigure}
+    %\begin{subfigure}{1\textwidth}
+     %   \centering
+     %     \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
+    %\end{subfigure}
+    \includegraphics[width=0.8\textwidth]{figure3.pdf}
+    \caption{Parallel coordinate plots for the two different approaches. \mrk{To limit data cluttering up to $250$ entries for each class were randomly collected.}  
+    %For the empirical approach, we have used all the $187$ suitable candidates. 
+    The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}
+    \label{fig:parallel-coordinates-approaches}
+\end{figure}
+
+Entries matching the formulas C, SiC, BN, MoS$_2$, WSe$_2$ and WS$_2$ \mrk{were} manually screened to see whether they have a matching structure to the respective candidates discussed earlier and summarized in Table~\ref{tab:qt-materials}.
+For carbon, three-dimensional diamond-like structures as explicitly stated in the column tags from the \mrk{MP} \mrk{were admitted.} Additionally, we find several two-dimensional structures of carbon with a large band gap (\mrk{$>\SI{1.5}{\electronvolt}$}) among the data.
+\mrk{These were added} as suitable candidates.
 Complex structures (e.g., C$_{28}$, C$_{48}$ and C$_{60}$) were moved to the test set in our machine learning studies.
 For SiC we admitted all entries which included the $2$H, $3$C, $4$H, $6$H and $15$R polytypes.
-Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, we only admit two-dimensional structures.
-For non-matching structures not mentioned so far, we move them to the test set to see if they will be predicted as suitable or not by the ML methods that are applied in a later stage.
+Concerning BN, MoS$_2$, WSe$_2$ and WS$_2$, \mrk{only two-dimensional structures were admitted.
+Other non-matching structures were moved to the test set to see whether or not they are predicted as suitable by the ML methods applied in a later stage}.
 
 The materials AlP, GaP, AlAs, ZnTe and CdS were manually screened for tetrahedrally coordinated structures, and have been included since \citeauthor{Weber2010} \cite{Weber2010} identified them as potentially promising candidates due to suitable material properties.
-We note that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of $0.5$~eV.
+\mrk{Note} that only tetrahedrally coordinated structures of the given formulas were labeled as suitable after imposing a band gap restriction of \SI{0.5}{\electronvolt}.
 
 Following the three screening steps in the empirical approach, a total of $187$ entries were labeled as suitable candidates for the training set.
-Notably, the candidates labeled as suitable in the empirical approach contain only compounds that are either elementary (unary) or binary. 
-Since the set of labeled data constituting suitable candidates in the empirical approach contains rather few entries, we add $400$ candidates that are labeled as \textbf{unsuitable}.
-These are picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
+\mrk{Notably, only elementary (unary) and binary materials are labeled as suitable in the empirical approach.} \mrk{To complete the dataset, $400$ materials were added and labeled as \textbf{unsuitable}}.
+These \mrk{were} picked at random from the pool of unsuitable candidates from the two previous approaches, in addition to those that were marked as unsuitable during the manual screening process.
+
+\mrk{Note that there is some potential for inherent bias in the dataset, in part due to experimental work being limited by the availability and cost of materials and processing.
+Moreover, the discovery of the quantum compatible properties of the NV center in diamond naturally led early searchers to comparable materials such as silicon carbide.
+%However, the broad range of materials predicted and listed in Table~\ref{tab:materialproperties} and the Supplementary Information at \cite{supplementary} indicates that the ML methods are detecting underlying properties which manifest in a broad range of material systems.
+}
 
 \subsubsection*{Comparing the approaches}
-The three different approaches to data mining place a particular emphasis on each of their specific goals.
+%The three different approaches to data mining place a particular emphasis on each of their specific goals.
 The Ferrenti approach relies on choosing only elements with spin zero isotopes and compounds that crystallize in nonpolar spacegroups together with practical filters, while the extended Ferrenti approach allows a larger variety of elements and removes the practical reasons for excluding candidate materials.
@@
 
-%Ferrenti 
-Considering the materials present in the labeled datasets of the first two approaches more closely, we find that carbon in a diamond-like structure is classified as a suitable candidate in the Ferrenti approach, in good agreement with experimental observations (see Table~\ref{tab:qt-materials}).
-Interestingly, in the labeled data from the Ferrenti approach, we find that carbon in two-dimensional graphite-like structures are marked as suitable as well.
-All structures of silicon are also labeled as suitable together with one entry of silicon carbide.
-Note that this is the $3$C polytype of SiC, meaning that the most well-established quantum compatible SiC polytype, $4$H-SiC, is missing.
-Among other potentially suitable candidates we find ZnS, ZnSe, ZnO and ZnTe present in the labeled data from the Ferrenti approach.  
-%Extended Ferrenti 
-In the labeled dataset of the extended Ferrenti approach, we find a single entry for each of SiC, Si, GaN, ZnS, GaP, AlAs and AlP, carbon in both diamond- and graphite-like structures, and AlN in three different configurations.
-The labeled dataset includes a larger variety of materials that are known to be quantum compatible as compared to the Ferrenti approach due to admitting more elements in the initial selection process.
-However, since we also included a more stringent band gap restriction of $1.5$~eV (to reduce the amount of materials in the training set), we find a more sparse representation of each known chemical formula present in the labeled data.
-
-The labeled data for each approach is visualized in Fig.~\ref{fig:parallel-coordinates-approaches} as parallel coordinate plots for a few selected features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
+\mrk{The labeled data for the Ferrenti and empirical approaches is visualized in Figure~\ref{fig:parallel-coordinates-approaches}} as parallel coordinate plots for \mrk{selected} features informed by the criteria proposed by \citeauthor{Weber2010} \cite{Weber2010}.
 Parallel coordinate schemes \cite{Inselberga1990, Inselberg1985} represent a multi-dimensional data tuple as one polyline crossing a parallel axis.
@@
 
-\begin{figure}[t] %!htp
-    \centering
-    \begin{subfigure}{1\textwidth}
-        \centering
-        \scalebox{0.85}{\input{figures/parallel-coordinates-plots/01-ferrenti-approach-v2.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
-          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/02-extended-ferrenti-approach-v3.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
-          \scalebox{0.85}{\input{figures/parallel-coordinates-plots/03-empirical-approach-v3.pgf}}
-    \end{subfigure}
-    \caption{Parallel coordinate plots for the different approaches.
-To limit data cluttering, we have randomly collected up to $250$ entries for each class.
-For the empirical approach, we have used all the $187$ suitable candidates.
-The axes show total magnetization (mag), space group (SG), ionic character (ionic char), covalent range (cov range) as calculated from elemental properties, number of elements (num elements) and energy gap (Eg) as extracted from the MP database.}
-    \label{fig:parallel-coordinates-approaches}
-\end{figure}
-
 \begin{figure}%[h] %!tbp
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/01-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{figure4a.pdf}
     \end{subfigure}%
@@
         \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/02-augmented-ferrenti-approach.pdf}
+        \includegraphics[width=1\textwidth]{figure4b.pdf}
     \end{subfigure}
-    \begin{subfigure}{0.4\textwidth}
-        \centering
-        \includegraphics[width=1\textwidth]{figures/pca-2d-plots/03-insightful-approach.pdf}
-    \end{subfigure}
-    \caption{Two-dimensional scatter plots for the three different approaches.
-We have identified the eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix, that is, the two most important principal components of the initial data from the Materials Project query.
-Then, we have transformed the sets of labeled data resulting from the three approaches and visualized them as scatter plots.
-Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols in the bottom panel, and red triangles represent unsuitable candidates.}
+    \caption{Two-dimensional scatter plots for the \mrk{Ferrenti and empirical} approaches.
+\mrk{The eigenvectors corresponding to the two largest eigenvalues of the covariance-matrix were identified}, that is, the two most important principal components of the initial data from the Materials Project query.
+Then, \mrk{the labeled datasets were transformed and visualized as 2D scatter plots.} Green squares display suitable candidates, along with the black (SiC), blue (diamond) and yellow (Si) symbols \mrk{for the empirical approach}, and red triangles represent unsuitable candidates.}
     \label{fig:2dscatterplotpca}
@@
 
-The Ferrenti approach and the extended Ferrenti approach share several similarities.
-For example, the entries in  Fig.~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
-Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
-The most striking difference is found for the empirical approach.
-Again, the entries labeled as suitable candidates do not exhibit any magnetization, but now the materials crystallize in both polar and non-polar space groups --- contrarily to the two Ferrenti approaches.
-Moreover, we observe that the range of covalent radius and maximum ionic character span a substantially smaller parameter space in the case of the empirical approach than for the two former ones.
-Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance.
-In the empirical approach the polarity of the material's space group may be less important compared to the Ferrenti based approaches, while the accepted values for ionic character and covalent range appear more restricted (Fig.~\ref{fig:parallel-coordinates-approaches}).
-
-To illustrate the composition of the labeled data we perform a principal component analysis (PCA) \cite{Jolliffe2002}.
-Here we apply PCA to the labeled datasets in order to reveal specific features that stand out.
-In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
+%\mrk{The Ferrenti approach and the extended Ferrenti approach share several similarities with entries that span roughly the same dimensions (not shown).} 
+%For example, the entries in  Figure~\ref{fig:parallel-coordinates-approaches} span roughly the same dimensions for the Ferrenti and extended Ferrenti approaches, despite the more restricted nature of the former.
+%Moreover, the two approaches' upper limits for ionic character and covalent range are very similar in the case of candidates labeled as both suitable and unsuitable.   
+%The most striking difference is found for the empirical approach. 
+\mrk{Several differences are observed between the Ferrenti approach and the empirical approach to data mining.
+While neither case passes materials that exhibit magnetization through as suitable, suitable candidates can crystallize in both polar and non-polar space groups in the empirical approach.} Moreover, \mrk{the ranges}  of covalent radius and maximum ionic character span a substantially smaller parameter space \mrk{for the empirical approach than for the Ferrenti approach (see Fig.~\ref{fig:parallel-coordinates-approaches})}.
+%Here, we can begin to deduce some trends, if the findings from the empirical approach are taken as guidance. 
+%In the empirical approach the polarity of the material's space group may be less important compared to the \mrk{Ferrenti approach}, while the accepted values for ionic character and covalent range appear more restricted .
+\mrk{Overall, there seems to be greater overlap in the distributions in material properties for suitable and unsuitable candidates in the case of the Ferrenti approach as compared to the empirical one.}
+
+\mrk{To reduce the dimensionality of the labeled data a principal component analysis (PCA) was performed \cite{Jolliffe2002}.} In its standard  form, PCA relates the variance of the features with the eigenvalues of the covariance matrix \cite{Jolliffe2002,Murphy2012,Hastie2009}.
 We identify the two largest eigenvalues of the covariance matrix \cite{Hastie2009} of the complete initial dataset from the MP database, and transform the three labeled datasets according to the corresponding two eigenvectors.
-In essence, we reduce the dimensionality of the labeled data in order to visualize them.
-The result of this procedure is displayed in the scatter plots of Fig.~\ref{fig:2dscatterplotpca}.
-Note that some minor differences between the three panels in Fig.~\ref{fig:2dscatterplotpca} may occur due to the process of removing the mean and scaling to unit variance.
-Red triangles represent unsuitable candidates while colored symbols (green, blue, black and yellow) represent suitable candidates.
-Due to the complexity of reducing the large amount of features down to only two, both suitable and unsuitable candidates for the Ferrenti and the extended Ferrenti approaches are largely overlapping. 
-The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti and extended Ferrenti approaches.
-Hence, using these approaches for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
-We therefore expect that the two Ferrenti approaches could need supplementary dimensions for further distinguishing between the materials in the two categories (suitable and unsuitable), or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
-
-In the case of the empirical approach, on the other hand, we can discern a trend where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable candidates (green, blue, yellow and black symbols), while the unsuitable candidates (red triangles) are similarly restricted to the lower right corner, albeit with some exceptions.
+The result of this procedure is displayed in the scatter plots of \mrk{Figure}~\ref{fig:2dscatterplotpca}.
+Note that some minor differences between the \mrk{approaches} may occur due to the process of removing the mean and scaling to unit variance.
+Red triangles represent unsuitable candidates while \mrk{otherwise} colored symbols (green, blue, black and yellow) represent suitable candidates.
+Due to the complexity of reducing the large amount of features down to only two, suitable and unsuitable candidates for \mrk{the Ferrenti approach} are largely overlapping. 
+The logic behind categorizing materials in two classes (suitable and unsuitable) appears to not translate into a distinct separation, at least not in the representation of Fig.~\ref{fig:2dscatterplotpca} for the Ferrenti \mrk{approach}.
+Hence, using \mrk{this approach} for predicting QT material hosts could prove challenging for any model that would try to glean a clear-cut boundary between materials that are and are not suitable for QT.
+We therefore expect that the \mrk{Ferrenti approach} could need supplementary dimensions for further distinguishing between the materials in the two categories\mrk{.} 
+%, or that it may prove challenging to find a generalized model based on the training sets that were defined according to the above discussion.
+
+In the case of the empirical approach, on the other hand, \mrk{a clear trend can be discerned} where the upper left part of Fig.~\ref{fig:2dscatterplotpca} is dominated by suitable  %(green, blue, yellow and black symbols),
+\mrk{candidates while the unsuitable ones} are similarly restricted to the lower right corner, albeit with some exceptions. 
 Interestingly, we observe that different configurations of the famously quantum compatible materials of diamond (blue), silicon carbide (black) and silicon (yellow) are grouped together but each material class is separated in its own region.
-This indicates that the empirical approach may be capable of separating materials based on their underlying properties.
-Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
+This \mrk{strongly indicates that the empirical approach may be capable of separating materials based on their underlying properties, emphasizing the importance of having a logical framework for the data mining process}.
+%Thus, devising a logical framework for the data mining process is likely important in order to obtain suitable datasets for training and testing of the ML methods.
 
@@
 
-\subsection*{Machine learning and principal component analysis}
-We have applied four well-tested ML algorithms in order to classify specific materials as candidate systems for QT.
-These are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
-These four ML methods were applied to the labeled data sets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
-
-In order to reduce the dimensionality while preserving most of the variance in the data, 
-we have performed a principal component analysis  \cite{Jolliffe2002} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-First, the eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in three distinct PCA models (as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model).
-Next, in the evaluation of the ML methods for the three different approaches we apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
-We note that all four ML methods have high evaluation metrics for the optimal hyperparameters.
-Further details on the evaluation of the ML methods and the results from the principal component analyses for all four methods are shown in the Supplementary Information \cite{supplementary}.
-The three data labeling approaches (Ferrenti, extended Ferrenti and empirical) define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
+\subsection*{Machine Learning and Principal Component Analysis}
+\mrk{Four well-tested ML algorithms were applied to the labeled data} to classify specific materials as candidate systems for QT\mrk{, yielding multiple sets of predicted candidates.
+The ML methods employed herein} are logistic regression, decision trees, and the ensemble methods random forests and gradient boosting \cite{Mehta2019,Hastie2009,Murphy2012}.
+%These four ML methods were applied to the labeled datasets that were optimized using each of the three approaches (Ferrenti, extended Ferrenti and empirical) outlined above, yielding twelve sets of candidates that were predicted as suitable material hosts for QT applications.
+%\mrk{To} reduce the dimensionality while preserving most of the variance in the data, \mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+\mrk{Principal component analysis was again performed, but now on the three training sets separately} \footnote{In the main text we discuss the Ferrenti dataset and the empirical one.
+The corresponding results for the extended Ferrenti set are listed in the Supplementary Information.}
+% \mrk{A principal component analysis was performed where first the} 
+% eigenvalues of the covariance matrices of the three training sets are identified in order of decreasing value, resulting in \mrk{distinct PCA models for each data labeling approach}
+(as opposed to the case of Fig.~\ref{fig:2dscatterplotpca} where all panels are based on the same model). 
+Next, in the evaluation of the \mrk{ML methods we}  
+%for the three different approaches 
+apply a $5\times 5$ stratified cross-validation \cite{Hastie2009} when searching for the optimal hyperparameter combinations.
+\mrk{Note} that all four ML methods have high evaluation metrics for the optimal hyperparameters.
+Further details on the evaluation of the ML methods and the results from the principal component analyses for all four \mrk{ML} methods are shown in the Supplementary Information \mrk{at} \cite{supplementary}.
+The \mrk{data labeling approaches} define sets of labeled data of varying sizes, where the smallest is from the empirical approach.
 For small datasets, it is proven to be beneficial to repeat the cross-validation analysis \cite{Hastie2009}, as this is a method that allows us to measure the stability of the predictions against perturbations (i.e., few different entries) in the training data \cite{Beleites2008}.
@@
 Figure~\ref{fig:PComponents} visualizes different parameters for the most important principal components ranked in descending order by (a) the explained variance for the Ferrenti (upper panel) and empirical (lower panel) approach, and (b) the gradient boosting coefficients for the corresponding approaches.
-This differs from Fig.~\ref{fig:2dscatterplotpca}, where we visualize the two most important eigenvectors for all approaches that originates from the same covariance matrix.
-Note also that in  Fig.~\ref{fig:2dscatterplotpca} we performed a PCA analysis on all data.
-Here, the ML analysis is done on the labeled data for each approach.
-For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the $95 \ \%$ accumulated explained variance, a total of $144$ principal components must be included.
-For the extended Ferrenti approach, we find that gradient boosting performs optimally at $93$ principal components.
-In the case of the empirical approach and in contrast to the Ferrenti approaches, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
+This differs from Fig.~\ref{fig:2dscatterplotpca}, where \mrk{the two most important eigenvectors for all approaches that originate from the same covariance matrix are shown}.
+%Note also that in  Fig.~\ref{fig:2dscatterplotpca} \mrk{a PCA analysis was performed on all the data}. Here, the ML analysis is done on the labeled data for each approach. 
+For the Ferrenti approach (Fig.~\ref{fig:PComponents}a) to reach the \SI{95}{\percent} accumulated explained variance, a total of $144$ principal components must be included.
+\mrk{In the case of the empirical approach and in contrast to the Ferrenti approach}, decision trees and random forests exhibit the best performance for just a few principal components, and experience a considerable degree of overfitting when involving more principal components.
 Gradient boosting
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/01-ferrenti-approach-PC-v2.tex}
+        \includegraphics{figure5a}
         \label{fig:01-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/01-ferrenti-approach-GB-v2.tex}
+        \includegraphics{figure5b}
         \label{fig:01-fi-d}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/03-empirical-approach-PC-v2.tex}
+        \includegraphics{figure5c}
         \label{fig:03-fi-e}
@@
     \begin{subfigure}[b]{0.45\textwidth}
-        \input{figures/feature-importance/03-empirical-approach-GB-v2.tex}
+        \includegraphics{figure5d}
         \label{fig:03-fi-d}
@@
 %extended Ferrenti 
-The interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
+%\mrk{Note that the} interpretation of feature importance for the extended Ferrenti approach is substantially more challenging than in the Ferrenti approach.
 We find for logistic regression and decision trees that no feature is different than any other in the cross-validation, mainly due to a large variety of accuracy.
-However, we find that random forests and gradient boosting both mark the fifth principal component as important.
+However, \mrk{random} forests and gradient boosting both mark the fifth principal component as important.
 Similar to the Ferrenti approach, the corresponding features with the highest value for the fifth principal component originate from the DFT computed band gap of the elemental solids among the elements in the composition.
@@
 %empirical approach 
-The empirical approach differs in many aspects from the Ferrenti and extended Ferrenti approaches. 
-Firstly, we find that the number of principal components necessary to obtain $95 \ \%$ variance is reduced to $103$ components, which is $41$ and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively.
-Thus, the variance of the training set is found to be described with fewer principal components, indicating a simpler model.
+The empirical approach differs in many aspects from the Ferrenti \mrk{approach}. 
+Firstly, \mrk{the} number of principal components necessary to obtain \SI{95}{\percent} variance is reduced to \mrk{$103$ from $144$}. 
+%and $56$ less than the Ferrenti and extended Ferrenti approaches, respectively. 
+Thus, the variance of the training set \mrk{is} described with fewer principal components, indicating a simpler model.
 Secondly, the first principal component is by far the most important feature for all ML methods in the empirical approach, as visualized in the lower panel of Fig.~\ref{fig:PComponents}(b) for gradient boosting.
@@
 The standard deviation of the radial distribution function appears multiple times in the list of features and is of particular importance. 
-Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is $21 \ \%$, while it is $14 \ \%$ for the Ferrenti approach and $11 \ \%$ for the extended Ferrenti approach.
+Thirdly, the empirical approach differs in how much explained variance is retained by the first component, which is \SI{21}{\percent}, \mrk{compared to} \SI{14}{\percent} for the Ferrenti approach. 
+% and $11 \ \%$ for the extended Ferrenti approach. 
 We find the difference striking considering that the approaches share the same ultimate goal, but where the training sets apparently exhibit large and significant variations.
 
-Intriguingly, the principal components that are deemed important by the three approaches differ substantially.
-The Ferrenti and extended Ferrenti approaches place particular value on the material's band gap and the ionic or covalent character of the bonding.
+Intriguingly, the principal components that are deemed important by \mrk{the approaches differ substantially.
+The Ferrenti approach places}  particular value on the material's band gap and the ionic or covalent character of the bonding.
 Indeed, precisely these features were used as guidance in the data labeling process.
-Thus, the ML methods are preserving the criteria imposed in the Ferrenti approaches and perpetuate our initial assumptions on which material properties to look for.
-For the empirical approach, on the other hand, we did not guide the selection process in terms of specific properties.
-Here, the ML methods appear to be informed by other  characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
-In the empirical approach, the ML methods appear to be inferring that the common trend among the materials that are known to be suitable for QT is related to more complex mechanisms in the crystal structure and bonding.
+\mrk{Thus, the ML methods seem to perpetuate the criteria imposed in the Ferrenti approach at least to some extent.
+They may, however, still be recognizing other patterns than those originally intended in the data selection process.} \mrk{For the empirical approach, on the other hand, the selection was not guided in terms of specific properties.} Here, the ML methods appear to be informed by other characteristics than band gap and ionic character that are more related to symmetry and crystal structure, based on the repeated appearance of bond length, orientation and radial distribution in the first principal component.
+In the empirical approach, the ML methods \mrk{are recognizing more complex mechanisms in the crystal structure and bonding as common trends among materials that are suitable for QT applications}.
 
 \subsection*{Predicting Suitable Material Hosts for Quantum Technology}
-After training the ML algorithms using parts of the data labeled during the three data mining approaches, the ML methods were employed on the test sets. 
-The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in  Table~\ref{tab:probabilites}.
-
-\subsubsection*{The Ferrenti approach}
-
-From the predicted dataset of $23.623$ materials 
-the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach.
-All four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
-If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
-We find that all four ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
-This can allow materials with unfortunate structures to be labeled as suitable candidates.
-Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than $0.5$~eV were eliminated.
-This trend is not carried over to the predicted data. Indeed, we find that many entries with band gaps lower than $0.5$~eV are predicted as suitable candidates by all four ML methods employed herein 
-%indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
---- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.  
-On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
-
-\begin{table}[t]
+
+\begin{table}[b]
     \centering 
@@
 
-\subsubsection*{The extended Ferrenti approach}
-Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger 
-amount of labeled data than the Ferrenti approach.  
+%After training the ML algorithms using parts of the data labeled during the \mrk{data mining process}, the ML methods were employed on the test sets. 
+\mrk{After training and validating the ML algorithms on the labeled datasets, the ML methods were applied to unlabeled data to obtain predictions for suitable QT host materials.} 
+The number of candidates predicted by each of the four ML methods logistic regression, decision trees, random forests and gradient boosting is visualized in the Supplementary Information at \cite{supplementary}\mrk{.} %for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
+An overview of the number of predicted suitable candidates as a function of a given ML algorithm's confidence is summarized in Table~\ref{tab:probabilites}\mrk{for the Ferrenti, extended Ferrenti and empirical approaches.
+Note that the Ferrenti approaches are employed as a filter on the predictions of the empirical one.}
+
+\subsubsection*{The Ferrenti approach}
+
+From the predicted dataset of \mrk{\num{23623}} materials  
+%the four ML methods consistently predict at least $11.000$ materials as promising candidates in the case of the Ferrenti approach. 
+all four ML methods agree on a total of $6804$ suitable candidates, however, many of these materials are predicted with an incidence similar to that of a coin flip.
+If we were to raise the minimum confidence cut-off for a prediction to, e.g., $0.75$ instead of $0.5$, the above ML algorithms would only agree on $1784$ suitable candidates.
+We find that \mrk{the} ML methods admit almost all materials with a chemical formula matching the known suitable candidates (see Table~\ref{tab:qt-materials}) that were present in the labeled data.
+This can allow materials with \mrk{complex structures (e.g., nanostructures or 2D materials)} to be labeled as suitable candidates.
+Notably, the ML methods do not maintain the band gap restriction from the training set definition, where all materials with band gaps lower than \SI{0.5}{\electronvolt} were eliminated.
+This trend is not carried over to the predicted data.
+Indeed, \mrk{many} entries with band gaps lower than \SI{0.5}{\electronvolt} are predicted as suitable candidates by all four ML methods employed herein
+%indicating that the cut-off value we set for the band gap ($0.5$~eV for the Ferrenti approach) is not recognized by the ML algorithms 
+--- despite the principal component analysis revealing that the band gap is an important feature for the machine learning classification in the Ferrenti approach.
+\mrk{This indicates that the ML methods are not exactly recognizing the initial selection criteria, instead finding other patterns in the dataset.}
+On the other hand, due to the known  underestimation of band gaps by the PBE  functional, the band gaps could in reality be larger for many of the materials.
+
+\mrk{The ML methods predict materials as suitable that are not expected according to, e.g., Ref.~\cite{Weber2010}.
+Indeed, NaCl is predicted as a suitable candidate to minimum confidences of $0.83$ and $0.61$ for two different configurations, despite the strong electrostatic interactions between Na and Cl and the ionic character of their bonding.
+Note that NaCl was excluded from being labeled as both unsuitable and suitable in the Ferrenti approach and was therefore found in the unlabeled dataset.
+For the empirical approach, NaCl was included in the labeled data in the training set as an unsuitable candidate.
+}
+
+%\subsubsection*{The extended Ferrenti approach}
+%Next, we turn to the more liberal extended Ferrenti approach containing a $78 \ \%$ larger amount of labeled data than the Ferrenti approach.
 The four ML methods predict at least $13.000$ materials as suitable candidates out of $22.550$ materials in the unlabeled dataset, where they all agree on a total of $9227$ predicted suitable candidates.
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{figures/vesta-images/fig6-all.png}
-    \caption{Illustrations of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence, may belong to.
+    \includegraphics[width=0.85\textwidth]{figure6.png}
+    \caption{\mrk{Example illustrations} of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence\mrk{,} belong to.
 Four different symmetry categories are observed; cubic, hexagonal, tetragonal and orthorombic.
@@
 The former takes on a polar space group while the latter does not.
-The band gaps are listed as $1.9$~eV and $1.7$~eV, respectively, in the MP database.
-Both structures exhibit, as expected, a strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
-Importantly, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
+The band gaps are listed as \SI{1.9}{\electronvolt} and \SI{1.7}{\electronvolt}, respectively, in the MP database.
+Both structures \mrk{exhibit a} strong covalent character and have been studied for applications as nanostructures for electronic devices \cite{Gao2017}, hydrogen storage \cite{Cai2017} and superhard materials \cite{Li2017, Jiang2020}.
+\mrk{Interestingly}, the diamond-like structure of BC$_3$N was recently predicted as a promising  spin qubit material host \cite{Wang2020SpinQB}.
 By creating a boron vacancy one can in theory obtain a defect center with similar properties to those found for the NV center in diamond.
 Whether this is also possible for BC$_2$N remains to be seen.
-We note that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
-
-The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of $0.3$, $1.2$, $1.2$ and $1.7$~eV, respectively.
+\mrk{Note} that BC$_3$N was not represented in the MP database at the time of data extraction and is therefore not included in our dataset.
+
+The compounds InAs (cubic, mp-$20305$), CuI (cubic, mp-$22895$ and hexagonal, mp-$569346$) and ZnCd$_3$Se$_4$ (cubic, mp-$1078597$) are listed in the MP database with band gaps of \SIlist{0.3;1.2;1.2;1.7}{\electronvolt}, respectively.
 To the best of our knowledge, ZnCd$_3$Se$_4$ has yet to be synthesized, while self-assembled InAs quantum dots are  exciting possible materials to use in quantum technology \cite{Liu2018}. 
 CuI has recently been synthesized as single-crystal epitaxial films and was shown to exhibit remarkable optoelectronic properties \cite{Ahn2020}.
-Interestingly, the material exhibits a large ionic character with more similarities to some of the oxide compounds in the dataset than, e.g., the materials that are more covalent in character like Si, SiC and  diamond.
-The prediction of CuI in two configurations indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
+Interestingly, the material exhibits a large ionic character
+\mrk{and shares few similarities with known QT compatible hosts such as, e.g.,} Si, SiC and  diamond.
+The prediction of CuI in two configurations \mrk{thus} indicates that ionic character alone is not an obstacle for a material to be quantum compatible.
 It is unknown at this time whether any potentially favorable properties of CuI would originate from deep level defects or  nanostructuring (e.g., quantum dots).
-NaCl was not predicted as suitable for QT in the empirical approach.
+%NaCl was not predicted as suitable for QT in the empirical approach\mrk{, in contrast to the Ferrenti (and extended Ferenti) approach}.
+%This underlines that an empirical approach, based on experimental data, may be more suitable for predicting materials for a certain applications and understanding the underlying mechanisms than the assumption-based methodology.}
 
@@
 For the ABC$_2$ structures, the elements Ga, Cd, In and Zn can occupy the A-site, Cu, Sn, Ag and Ge take the B-site, while S, Se, Te, P or As may reside at the C site.
-Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of $1.2$~eV \cite{Zhang2015} as reported in the MP database.
-In comparison, the experimentally reported band gap is somewhat larger at $2.0$~eV \cite{Xing1989}.
-ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits strongly covalent bonds, and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
+Most of the predicted compounds include at least one toxic element with one exception: ZnGeP$_2$ (mp-$4524$) in a chalcopyrite-like tetragonal crystal structure with an indirect band gap of \SI{1.2}{\electronvolt} \cite{Zhang2015} as reported in the MP database.
+In comparison, the experimentally reported band gap is somewhat larger at \SI{2.0}{\electronvolt} \cite{Xing1989}.
+ZnGeP$_2$ crystallizes in a non-polar space group, possesses no magnetic moment, exhibits  \mrk{covalent bonding} and has been reported as an excellent mid-IR transparent crystal material that is suitable for nonlinear optical applications \cite{Zhang2015}.
 Importantly, it is possible to integrate sources of photon quantum states based on nonlinear optics with ZnGeP$_2$ \cite{Caspani2017}.
-We therefore identify ZnGeP$_2$ as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
+\mrk{ZnGeP$_2$ is therefore identified} as an eligible candidate material for QT, but it remains to be seen whether the candidate can facilitate, e.g., the isolated deep energy levels often associated with defects exhibiting quantum compatible properties, or instead be a candidate for nanostructure based QT.
 
@@
 
-Among the $66$ materials that all ML methods in the empirical approach agreed on to a $0.75$ confidence level, we also emphasize the presence of interesting materials like Ge (in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$), GeC, BP and InP.
-The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number.
-Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
-Furthermore, like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.
+Among the \mrk{list of $66$ we also highlight the predictions} of interesting materials like \mrk{Ge, sharing many characteristics with Si and C in addition to the periodic column number,  %(in three configurations mp-$137$, mp-$1067619$ and mp-$1198022$),
+GeC, BP and InP.}  
+%The element Ge in the cubic structure (mp-$1198022$) shares many properties with Si and C in addition to the periodic column number. 
+%Germanium has the highest hole mobility of all semiconductors at room temperature, and is therefore considered a key material for the process of extending the chip performance in classical computers beyond the limits imposed by miniaturization \cite{Scappucci2020}.
+\mrk{Much} like SiC, device design based on Ge can take advantage of the mature large-scale fabrication of silicon due to the material's comparable properties.  
 Similar considerations could be made for the case of GeC. 
-Data from the MP database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of $1.8$~eV. 
+Data from the MP database suggests that the cubic compound GeC (mp-$1002164$) is a covalently bonded semiconductor having a band gap of \SI{1.8}{\electronvolt}. 
 Consequently, with SiC being widely known as a highly suitable host material for QT compatible defects, we encourage further research on GeC due to its similarities with SiC. 
-Next, the compound BP (mp-$1479$ and mp-$1008559$) is present in our predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at $1.5$~eV and $1.1$~eV, respectively.
+Next, \mrk{BP} (mp-$1479$ and mp-$1008559$) is present in \mrk{the} predictions in both the cubic and hexagonal structures, with indirect band gaps calculated at \SI{1.5}{\electronvolt} and \SI{1.1}{\electronvolt}, respectively.
 Both configurations of BP are nonmagnetic, non-toxic and BP has been synthesized with a potential for large-scale production \cite{MukhanovVladimirA2016Umso}.
-Lastly, InP (mp-$966800$) was also predicted as a suitable candidate to $0.75$ confidence.
-The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra.
-InP is reported in the Materials Project to have a direct band gap of $0.5$~eV and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
-We underline the possibility of using InP-based quantum dots for QT applications.
-
-We note that all ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
-However, we find that almost all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
+Lastly, InP (mp-$966800$) 
+%was also predicted as a suitable candidate to $0.75$ confidence. The compound inhabits the hexagonal structure with corner-sharing InP$_4$ tetrahedra. 
+\mrk{in the hexagonal structure} 
+is reported in the Materials Project to have a direct band gap of \SI{0.5}{\electronvolt} and is considered as one of the most promising candidates to compete with Cd- or Pb- based QDs for, e.g., display and lighting applications  \cite{Zhang2020a, Won2019}.
+\mrk{The possibility of using InP-based quantum dots for QT applications should therefore be considered.}
+
+%\mrk{The} ML methods in the empirical approach agree on several oxides being potential candidates when the prediction cut-off is set low enough (but still above $0.5$).
+\mrk{However, almost} all the oxide compounds fall between the decision boundary defining suitable and unsuitable candidates, and none are present in the list containing the $66$ suitable candidates using a $0.75$ threshold.
 Due to the labeling of ZnO as a suitable candidate in the training set, we believe that the boundary was shifted  sufficiently to admit several oxides as suitable candidates.
@@
 Comparing to the work of \citeauthor{Ferrenti2020} \cite{Ferrenti2020}, they suggest a list of $541$ viable hosts after the data mining procedure.  
-Among these, we find only a single material present in our list of $66$ candidates predicted by the four ML methods in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a $2.0$~eV band gap and decomposes to a similar MgSe configuration.
+Among these, \mrk{only a single material is present in the list of $66$ candidates predicted by the four ML methods} in the empirical approach: the nontoxic compound MgSe (mp-$10760$) which crystallizes in the rock-salt structure, is expected to have a \SI{2.0}{\electronvolt} band gap and decomposes to a similar MgSe configuration.
 %The band gap of MgSe is listed as $2.0$~eV in the MP database with the experimental value being reported at $2.45$~eV (optical band gap) \cite{Ubale2014}. 
-MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010} and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}.
+MgSe is notable for its available spin-zero isotopes in accordance with the criteria set by \citeauthor{Weber2010} \cite{Weber2010}\mrk{.}  
+%and \citeauthor{Ferrenti2020} \cite{Ferrenti2020}. 
 We note that these properties may favor defects acting as spin centers with qubit potential and MgSe is thus identified as an interesting host material in this regard.
 
-\subsubsection*{Comparing the approaches}
-Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
-The Ferrenti approach also predicts a large amount of materials as suitable compared to the empirical approach, but the resulting data are otherwise not very different from the extended version.
+%\subsubsection*{Comparing the approaches}
+\subsubsection*{Overlapping predictions between the approaches}
+
+%\section*{\mrk{Discussion}}
+%Comparing the three approaches Ferrenti, extended Ferrenti and empirical (see also Table~\ref{tab:probabilites}), we observe that the extended Ferrenti approach is the least restricted also for the predicted materials and admits the largest number of entries regardless of the confidence threshold.
+%The Ferrenti approach also predicts a large amount of materials as suitable compared to the empirical approach, but the resulting data are otherwise not very different from the extended version.
 The empirical approach, on the other hand, predicts fewer suitable candidates that are possible to examine  manually.
-Manual verification through a literature survey will often not be possible, however, and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
-
-Despite notable differences, as mentioned above, there is substantial overlap of predicted materials between the three approaches. 
-We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach. 
+\mrk{The amount of materials predicted by the empirical approach is restricted enough to enable close scrutiny of the various suggested candidates.
+The same cannot be said for the Ferrenti approach, however, as seen from Table~\ref{tab:probabilites}.} Manual verification through a literature survey will often not be possible\mrk{,} and perfecting automatic data mining and analysis is therefore an important goal of material informatics \cite{rickman2019}.
+
+Despite notable differences, as mentioned above, there is \mrk{overlap of predicted materials between the approaches}. 
+%We find that $119$ of the $214$ candidates predicted as suitable by the empirical approach (threshold at $0.5$) were also selected by all ML methods in the extended Ferrenti approach.
 Similarly, $78$ of the $214$ materials are also predicted as suitable by all ML methods in the Ferrenti approach.
-All approaches and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence, where $8$ are elementary (unary), $29$ binary, and $10$ tertiary
-(see the Supplementary Information at \cite{supplementary} for the full list). 
+All approaches \mrk{(including the extended Ferrenti approach) and their corresponding ML methods agree on a total of $47$ potential candidates to $0.5$ confidence 
+%where $8$ are elementary (unary), $29$ binary, and $10$ tertiary 
+(see the Supplementary Information at \cite{supplementary} for the full list).} 
 Several interesting materials that were also discussed above for the predictions by the empirical approach are present among these $47$, including BP, CdSe, GeC, InP and Ge.
-However, we also find certain materials that cannot be classified as semiconductors, such as P, I, N$_2$ and H$_2$.
+However, certain materials that cannot be classified as semiconductors \mrk{are also included}, such as P, I, N$_2$ and H$_2$.
 We note that none of these were included by the empirical approach when the threshold was set to $0.75$ or above.
@@
 These are ZnGeAs$_2$ (tetragonal mp-$4008$), CdSnP$_2$ (tetragonal mp-$5213$), GeSe (cubic mp-$10759$), InP (cubic mp-$20351$), InP (hexagonal mp-$966800$) and SiSn (cubic mp-$1009813$).
-Here, we can distinguish three groupings in crystal structure and they agree with those discussed above; cubic, hexagonal and tetragonal (illustrated in Fig.~\ref{fig:crystalsystems}).
-The relevant material properties are summarized in the lower part of Table~\ref{tab:materialproperties}.
-Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
-We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP (unstable).
-However, consistent four-fold coordination and the bond angle trends we observed for the first $9$ materials are not maintained as GeSe is six-fold coordinated.
+Here, we can distinguish three groupings in crystal structure: cubic, hexagonal and tetragonal (illustrated in Fig.~\ref{fig:crystalsystems}).
+The relevant material properties are summarized in the lower part of Table~\ref{tab:materialproperties},
+%Note that hexagonal InP is listed in the MP database as decomposing into cubic InP while SiSn is stated to decompose into Si $+$ Sn. 
+\mrk{with comparable trends to those for the $9$ materials predicted by the empirical approach in terms of, e.g., crystal structure.
+The six-fold coordination of GeSe is an outlier as compared to the four-fold coordination of the other materials.
+}
+%We can deduce a series of similar trends as for the $9$ materials from the empirical approach --- e.g., the same space groups are manifesting, we find only binary or tertiary compounds, and $a=b$ for all materials while $c$ is different for hexagonal InP.
+%However, consistent four-fold coordination and the bond angle trends  observed for the first $9$ materials are not maintained as GeSe is six-fold coordinated. 
 We highlight these six compounds, along with the nine predicted by the empirical approach to $0.85$ confidence, as particularly interesting for future in-depth theoretical and experimental studies.
 
-\section*{Discussion}
-
 %histograms 
-\begin{figure}[ht]
+\begin{figure}[t]
     \begin{subfigure}[b]{1\textwidth}
     \centering
-    \input{figures/histograms/new/LegendHistPaper.tex}
+    \includegraphics{figure7-legend.pdf}
   \end{subfigure}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/MP_Eg_count_075.tex}
+    \includegraphics{figure7a.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/IonProperty_max ionic char_count_075.tex}
+    \includegraphics{figure7b.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/GeneralizedRDF_std_dev Gaussian center=1.0 width=1.0_count_075.tex}
+    \includegraphics{figure7c.pdf}
     \subcaption{}
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/new/AverageBondLength_std_dev Average bond length_count_075.tex}
+    \includegraphics{figure7d.pdf}
     \subcaption{}
 \end{subfigure}
-\caption{Histograms of predicted suitable materials as a function of the (a) PBE-calculated band gap from Materials Project, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
-The total number of predicted materials is  $6804$ for the Ferrenti approach, $9227$ for the extended Ferrenti approach, and $214$ for the empirical approach.
-The Ferrenti and extended Ferrenti approaches refer to the left $y$-axis and the empirical approach to the right.
+\caption{Histograms of predicted suitable materials as a function of the (a) \mrk{band gap}, (b) maximum ionic character, (c) standard deviation of the radial distribution function (RDF) and (d) standard deviation of the average bond length.
+The total number of predicted materials is  $6804$ for the Ferrenti approach, and $214$ for the empirical approach.
+The Ferrenti \mrk{approach refers} to the left $y$-axis and the empirical approach to the right.
 }
@@
 
+\section*{Discussion}
+
 Taking a closer look at the reasoning behind the choices made by the different ML methods during the classification process, we can start to identify important driving forces for manifestation of quantum compatible properties in semiconductors.
-The analysis of the principal components extracted from the ML methods revealed that the most important principal component for both the Ferrenti and extended Ferrenti approaches encompasses features related to the band gap and chemical environment.
+The analysis of the principal components extracted from the ML methods revealed that the most important principal component for \mrk{the Ferrenti approach} encompasses features related to the band gap and chemical environment.
 This means that the band gap criterion imposed in the training set selection is at least somewhat satisfied.
-In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process.
+%In other words, the Ferrenti approaches appear to reproduce the logic of the initial selection process. 
+\mrk{The Ferrenti approach does not entirely reproduce the logic of the initial selection process, however, as several low band gap ($<0.5$~eV) materials were highlighted as suitable by the ML methods.}
 For the empirical approach, on the other hand, band gap related features were not recognized as important in the dominant principal component.
 
-Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that all approaches predicted a substantial amount of materials with a low band gap (below $0.5$~eV).
-Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti approaches exhibiting a peak around a $2.5$~eV band gap.
-Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around $2.5$~eV using the PBE functional. 
-The empirical approach exhibits a more scattered data distribution with local maxima around $1$-$2$ and $4$~eV.
-
-The secondmost important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
-Intriguingly, as shown in Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for all three approaches - even peaking at a relatively high ionic character of $0.8$.
-We note that this may be a result of the distribution of the initial dataset of $25.000$ materials that peaks around a similar value (not shown).
-The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach, extended Ferrenti approach nor the overall data distribution.
-For comparison, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
-Further, we find that the covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
+Figure~\ref{fig:histogram_new}(a) displays the number of predicted suitable materials as a function of band gap (from the MP database), and reveals that \mrk{both} approaches predicted a substantial amount of materials with a low band gap (below \SI{0.5}{\electronvolt}).
+Moreover, the distribution of materials that were identified as suitable is rather broad with the Ferrenti \mrk{approach} exhibiting a peak around a \SI{2.5}{\electronvolt} band gap. 
+Coincidentally, the band gap of, e.g., 4$H$-SiC is usually computed at around \SI{2.5}{\electronvolt} using the PBE functional. 
+The empirical approach exhibits a more scattered data distribution. % with local maxima around $1$-$2$ and $4$~eV.
+
+The second most important principal component in the Ferrenti approach encompasses properties such as the ionic character, covalent radius and maximum packing efficiency (see the Supplementary Information at \cite{supplementary} for the predicted material distributions of the latter two features).
+Intriguingly, as shown in  Figure~\ref{fig:histogram_new}(b), the predicted candidates distribute over a broad range of ionic characters for \mrk{both the Ferrenti and empirical} approaches --- even peaking at a relatively high ionic character of $0.8$.
+We note that this may be a result of the distribution of the initial dataset of \mrk{\num{25000}} materials \mrk{with a maximum} around a similar value (not shown).
+The minor peak in the empirical approach's predicted materials around $0.4$ ionic character is not present for the Ferrenti approach \mrk{nor} the overall data distribution.
+For \mrk{reference}, all SiC entries in the dataset have maximum ionic characters of $\sim 0.1$.
+\mrk{Furthermore, the} covalent radii of the materials (see the Supplementary Information) exhibit two distinct peaks in the data distribution. 
 The trend of two data peaks is repeated for the maximum packing efficiency but is much more prominent for the empirical approach.
@@
 The ML methods in the empirical approach consistently identified the first principal component as the predominant one.
-Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that is important.
-Here, we find that the standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
-One configuration of the standard deviation of the RDF is demonstrated in Fig.~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
-Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the Ferrenti approaches and the empirical approach.
-This reflects the observations from the principal component analysis where the first principal component is dominated by the RDF and similarly symmetry related features.
-For the empirical approach, there is a sharp peak in the preferred value for the standard deviation for the RDF, while the Ferrenti and extended Ferrenti approaches display an even distribution across a broader range.
+Identifying the single most important feature in this principal component proved challenging as it is the combined impact of several features that \mrk{matters}.
+Here, \mrk{the} standard deviation of the radial distribution function (RDF) has a  particularly strong impact since it appears four times in different forms in the top ten list over dominating features.
+One configuration of the standard deviation of the RDF is demonstrated in \mrk{Figure}~\ref{fig:histogram_new}(c), with two others being included in the Supplementary Information at \cite{supplementary}.
+Intriguingly, the standard deviation of the RDF exhibits substantial discrepancies between the \mrk{Ferrenti} and the empirical approach.
+For the empirical approach, there is a sharp peak in the preferred value for the standard deviation \mrk{of} the RDF, while the Ferrenti \mrk{approach displays} an even distribution across a broader range.
+\mrk{These observations emphasize the importance of symmetry related material properties for QT suitability. }
 
@@
 This resonates with the observations from the principal component analysis; an optimal degree of crystalline order likely exists for a material to manifest QT compatible properties, but some variations throughout the crystal in, e.g., bond length and symmetry are needed.
-This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti and extended Ferrenti approaches.
-Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered as well and may be more important.
+This is in contrast to the expectations that guided the formulation of the test and training sets in the Ferrenti \mrk{approach}.
+Where most previous works have highlighted features such as band gap, polarity and ionic character as vital for a semiconductor to manifest quantum compatible features, our results reveal that local variations in the crystal structure related to symmetry and bond angles, length and orientation should be considered \mrk{equally and may even be more important.}
 
@@
 None of the known quantum emitters or spin centers seem to appear in completely uniform systems.
-For example, in the high symmetry materials of diamond and silicon, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
-Instead, we find that quantum effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
-For the binary system of silicon carbide in different polytypes, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
+For example, in \mrk{high symmetry materials like diamond and silicon}, QT compatible defects are not intrinsic; neither the silicon vacancy in silicon nor the carbon vacancy in diamond, for example,  have exhibited single-photon emission or controllable spin coherence.
+Instead, \mrk{quantum} effects often appear after impurities are introduced, as evidenced by the phosphorous and carbon impurities in silicon \cite{He2019,Redjem2020} and the nitrogen-vacancy, germanium-vacancy, tin-vacancy and lead-vacancy centers in diamond \cite{Thiering2020}.
+For \mrk{a binary system like silicon carbide}, on the other hand, intrinsic defects like the silicon vacancy and the divacancy are appropriate for our goals. 
 While these trends have yet to be verified on a grander scale, our findings provide strong indications that local variations in the crystal structure are paramount for QT compatible properties to manifest in a semiconductor host.
 
-Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
-The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.
-
-To summarize, the data extraction tools developed in this work resulted in a dataset of over $25.000$ materials and more than $4800$ physics-informed features.
+\mrk{It should be noted that performing machine learning on a dataset derived using preconceived notions for which material properties are important may reproduce several of the initial selection criteria.
+Nonetheless, the Ferrenti approach was included in the present work to highlight expectations from the literature and contrast them with the findings from the empirical one.
+Additionally, ML methods are often capable of recognizing other patterns than those intended for the data, opening up the possibility that also the Ferrenti approach could yield new insights.
+Finally, the Ferrenti approaches are employed as a filter on the empirical approach, to provide a better tuned list of candidates for future experimental studies.}
+
+To summarize, \mrk{we have developed data extraction tools and strategies for data mining and labeling to enable the automated search and analysis of host materials for QT.} 
+%the data extraction tools developed in this work resulted in a dataset of over \mrk{\num{25000}} materials and more than $4800$ physics-informed features.
 Three different approaches (Ferrenti, extended Ferrenti and empirical) for data labeling were employed for training and testing of four ML algorithms.
-We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
-Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
-The principal component analyses of the ML methods' performance imply that the Ferrenti and extended Ferrenti approaches, with their strong focus on band gap and bonding character when assessing a material's quantum compatibility, largely replicate the specifications of the data labeling process.
-Valuable insight is gained from the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions.
-
-The findings presented here firmly establish that material informatics (from data mining via featurization to machine learning predictions) is a viable and important route to new discoveries in important fields.
-Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the framework we have developed is suitable for other fields as well.
-We suggest two possible paths to further exploit our findings.
-One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by the four ML methods.
-Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
+\mrk{The clear separation between suitable and unsuitable candidates after data labeling, along with the smaller number of principal components needed for obtaining optimal performance of the ML algorithms, indicate that the empirical approach based on findings from the literature is highly suitable for performing this type of guided search through materials databases.}
+%We find a much clearer separation between suitable and unsuitable candidates after data labeling in the empirical approach than for the two Ferrenti ones. 
+%Additionally, substantially fewer principal components are needed for obtaining optimal performance of the ML algorithms for the empirical approach. 
+The principal component analyses of the ML methods' performance imply that the Ferrenti \mrk{approach with its} strong focus on band gap and bonding character when assessing a material's quantum compatibility \mrk{to some extent reproduces} the specifications of the data labeling process, \mrk{as expected.}
+Valuable insight is gained from \mrk{comparing the important features of the Ferrenti with those for} the empirical approach which highlights the importance of symmetry related properties in the bond orientations and wavefunctions \mrk{over expected features related to band gap and bonding}.
+\mrk{As such, the expected properties are not able to capture the full physics of the problem.
+The contrast between the Ferrenti and empirical approaches reveals that the problem of QT compatibility is more complex than being related to band gap and bonding character alone.
+Based on our findings we propose that the manifestation of quantum effects in semiconductors is related to the crystal structure symmetry and bonding.
+}
+
+The findings presented here firmly establish that material informatics is a viable and important route to new discoveries in important fields. 
+Our focus has been on predicting new candidate materials to host single-photon emitters and spin centers for quantum technology applications, but the \mrk{developed framework} is suitable for other fields as well.
+\mrk{Two possible paths are suggested to further exploit the findings presented herein.} One aspect is the pursuit of experimental verification of QT compatible effects in the materials predicted as suitable by \mrk{machine learning}.
+Another, perhaps even more important, route is to use the features and trends identified during the data mining and prediction process\mrk{es} to understand the distinct material characteristics that enable quantum effects to manifest, opening  thereby up for new discoveries in the field of quantum technologies.
 
@@
 The AFLOW \cite{Curtarolo2012, Curtarolo2012a, Calderon2015} repository is an automatic software framework for the calculations of a wide range of inorganic material properties.
-They utilize the PBE functional within VASP to relax and optimize the structure from the ICSD.
+They utilize the PBE functional \mrk{(with the $+U$ correction for certain cases)} within VASP to relax and optimize all structures from the ICSD.
 Data extraction was performed in the period of January to February of $2021$.
@@
 This process was executed during January of $2021$.
+
+\mrk{Note that from the initial criterion, we define that a material is required to have an ICSD identifier (ID) in Materials Project.
+This ID is included in the AFLOW,  AFLOW-ML, JARVIS-DFT and OQMD databases as well.
+If two different databases contain different values for the same property, such as the band gap, we added both of them as columns (features) to our data to avoid any data cluttering.
+An additional analysis was performed to uncover any differences between the space groups reported in the Materials Project and the other databases, yielding an average match of \SI{97}{\percent}.
+We note that the small deviation might arise due to errors in either database, and is not necessarily reflected in the remaining features of the data.
+For the experimental values from Citrine, we could only verify the chemical formula since the experimental data is lacking information regarding the structure (e.g.
+space group, symmetry) of the material.}
+
+\mrk{The data regarding a material's magnetic character is extracted from the Materials Projects database.
+Indeed, the majority of these calculations are based on the primitive cell, however, Materials Project performs an initial relaxation of cell and lattice parameters using a $1000$ / (number of atoms in the cell) k-point mesh to ensure that all properties calculated are representative of the idealized unit cell for each respective structure.
+As a result, we can find, e.g., Fe labeled as ferromagnetic and NiO as antiferromagnetic in our dataset.
+Furthermore, MP contains structures of varying sizes for the same material.
+We have included all structures and materials from the Materials Project, but we have not checked which materials are represented as a larger cell in our data.
+We have thereby not verified whether antiferromagnetic ordering has been investigated for all cases.
+This is an improvement that could be made to our method in a future study.}
 
@@
 Boosting methods like gradient boosting use decision trees as weak learners and improve upon these by an iterative process that involves the estimation of the gradients of the cost/loss function  \cite{Hastie2009}.
-Pure decision trees can easily lead to overfitting of the data under study, leading to a ML method that exhibits a high variance.
+Pure decision trees can easily lead to overfitting of the data under study, leading to an ML method that exhibits a high variance.
 Ensemble methods like random forests and gradient boosting on the other hand tend to soften the overfitting problem, resulting in both a small bias and a reduced variance of the employed method, see for example Refs.~\cite{Hastie2009,Mehta2019} for an in-depth discussion of the bias-variance trade-off in machine learning.
 Gradient boosting implemented through the  XGBoost library \cite{xgboost2016} is widely used by data scientists to achieve state-of-the-art results on many machine learning challenges.
+
+\mrk{Our findings are corroborated by the fact that all four ML methods predict a small set of the unlabeled materials as suitable, while agreeing on a large part of these materials. 
+The methods we have chosen are all well tested, with random forests and gradient boosting methods tending to outperform the others, resulting normally in a small bias and variance \cite{Hastie2009,Mehta2019,Murphy2012}.}
 

### 2022-08-18 response-letter-2/response-letter-2.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Professional Formal Letter
% LaTeX Template
% Version 2.0 (12/2/17)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Brian Moses
% Vel (vel@LaTeXTemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt, a4paper]{letter} % Set the font size (10pt, 11pt and 12pt) and paper size (letterpaper, a4paper, etc)
\usepackage{color}
\usepackage{siunitx}
\newcommand{\mrk}[1]{\textcolor{red}{#1}}

\input{structure.tex} % Include the file that specifies the document structure

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," and date to the left of the page

%----------------------------------------------------------------------------------------
%	YOUR INFORMATION
%----------------------------------------------------------------------------------------

\Who{} % Your name

\Title{  } % Your title, leave blank for no title

\authordetails{%
	Morten Hjorth-Jensen \\ 
	Department of Physics\\ % Your department/institution
	P.O. Box 1048, Blindern\\ % Your address
	N-0316 Oslo, Norway\\ % Your city, zip code, country, etc
	Email: \\ 
	morten.hjorth-jensen \\ 
	@fys.uio.no % Your email address
}

%----------------------------------------------------------------------------------------
%	HEADER CONTENTS
%----------------------------------------------------------------------------------------

\logo{UiO_logo.png} % Logo filename, your logo should have square dimensions (i.e. roughly the same width and height), if it does not, you will need to adjust spacing within the HEADER STRUCTURE block in structure.tex (read the comments carefully!)

\headerlineone{UNIVERSITY} % Top header line, leave blank if you only want the bottom line

\headerlinetwo{OF OSLO} % Bottom header line

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TO ADDRESS
%----------------------------------------------------------------------------------------

\begin{letter}{
	Dr. Long-Qing Chen\\
	Editor-in-Chief\\
	\textit{npj Computational Materials} \\ 
	npjcompumats@nature.com \\ 
}

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------

\opening{}

\begin{center}
   \textbf{Resubmission of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by O. L. Hebnes, et al.}
\end{center}

\noindent
Dear Editor,

Please find enclosed a revised version of the manuscript entitled “Predicting Solid State Material Platforms for Quantum Technologies” by Oliver L. Hebnes, et al., submitted for publication as an original article in \textit{npj Computational Materials}. There are four files in all: the npj checklist, a marked-up Manuscript file, a clean Manuscript file and a Supplementary Information file. Changes are marked in red in the marked-up Manuscript.

The manuscript has undergone a minor revision. The changes outlined by the Editor have been implemented. Furthermore, additional clarification has been added on the Ferrenti approach, as suggested by Reviewer 2. Indeed - only materials that satisfy all of the criteria are labeled as suitable, while only materials that fail all of the criteria are classified as unsuitable. Finally, we have opted to rename the Ferrenti (and extended Ferrenti) approach in the style of the empirical approach, i.e., descriptive of the logic behind the labeling procedure. The Ferrenti and extended Ferrenti approaches have therefore been labeled the criteria-based and extended criteria-based approaches.

Please find detailed responses to the comments of the Reviewer and Editor below.

%\closing{Sincerely,}
Sincerely,

\noindent Prof. Morten Hjorth-Jensen and Dr. Marianne E. Bathen \\
On behalf of all the authors

%----------------------------------------------------------------------------------------
%	OPTIONAL FOOTNOTE
%----------------------------------------------------------------------------------------

% Uncomment the 4 lines below to print a footnote with custom text
%\def\thefootnote{}
%\def\footnoterule{\hrule}
%\footnotetext{\hspace*{\fill}{\footnotesize\em Footnote text}}
%\def\thefootnote{\arabic{footnote}}

%----------------------------------------------------------------------------------------

\end{letter}

\newpage

\noindent
\textbf{Reviewer \#2: }

Reviewer \#2:

In the revised version of this work, the authors address all of the issues raised in the previous round of review, including clarifying methodological details, making the text more concise, clarifying the limitations of fitting to the Ferrenti and empirical data classications, and fixing all of the minor issues. In particular, from the response to the referees, it appears that the Ferrenti approach does not classify the entire data set as either suitable or unsuitable: only materials that satisfy all of the criteria are labeled as suitable, while only materials that fail all of the criteria are classified as unsuitable. Therefore, most of the data set will be unlabeled, consisting of entries that satisfy some criteria but not others. \textcolor{blue}{If this is the case, then the authors should make this explicitly clear in the text of the manuscript itself.}

\textit{Response:}

\textit{... \\
We have added the following clarification to the Data Mining section: \\
\textcolor{red}{Crucially, only materials that satisfy \emph{all} of the reverse requirements are labeled unsuitable.
In other words, unlabeled materials will satisfy some of the selection criteria, but not all.}
}

Reviewer \#2: \\
\textcolor{blue}{They should also clarify if materials that satisfy some Ferrenti criteria but not others would be expected to be suitable or unsuitable – this would help with the interpreting the results, e.g. for NaCl.} The fact that most of the data is unlabeled by the initial Ferrenti classification would help justify the application of machine-learning approaches to this work, and this helps to clarify the purpose of this work.

\textit{Response:}

\textit{Indeed, finding suitable candidates in a pool consisting of thousands of unlabeled materials acts as the main motivation behind using machine-learning methods. Therefore, we have added the following clarification to the Data Mining section:}

\textcolor{red}{However, there could still be potential suitable materials among the remaining $23500$ unlabeled materials, yet impractical to manually identify them. This serves as the main motivation behind using ML-methods for predicting suitable or unsuitable materials for QT applications.}

\newpage

\noindent 
\textbf{Editorial requests:}

\begin{itemize}
    \item TITLE PAGE 
    \begin{itemize}
        \item The affiliations have been corrected.  
        \item The abstract has been shortened to less than 150 words. 
    \end{itemize}
    \item MAIN TEXT 
    \begin{itemize}
        \item The ordering of manuscript components has been correcting according to the specifications. 
        \item Figure captions have been included. 
        \item Results and discussion have been combined. 
        \item The headings have been modified to only include one level of subheadings. 
    \end{itemize}
\end{itemize}

MAIN TEXT
* Please ensure that the manuscript components are ordered as follows: Title page, Abstract, Introduction, Results, Discussion, Methods, Data Availability statement, Code Availability statement, Acknowledgements, Author Contributions, Competing Interests, References, Figure captions. 
Results and Discussion can be combined to be "Results and Discussion". Please modify the headings accordingly.
* We allow only one level of subheadings in the Results section. Please remove secondary subheadings such as “The Ferrenti approach”.

LANGUAGE AND STYLE
* Please remove language such as "new", "novel", "unique", "for the first time", "unprecedented", "excellent", etc. Novelty should be clear from the context.
* Please make sure that mathematical terms throughout your manuscript and Supplementary Information (including in figures, figure axes, and captions) conform strictly to the following guidelines. Equations should be supplied in editable format, and not as images. Scalar variables (e.g. x, V, χ) should be typeset in italic, whereas multi-letter variables should be formatted in roman. Constants (e.g. ħ, G, c) should be typeset in italics (the only exceptions being e, i, π, which should be typeset in Roman) and vectors (such as r, the wavevector k, or the magnetic field vector B) should be typeset in bold without italics. In contrast, subscripts and superscripts should only be italicised if they too are variables or constants. Those that are labels (such as the 'c' in the critical temperature, T_c, the 'F' in the Fermi energy, E_F, or the 'crit' in the critical current, I_crit) should be typeset in roman. To avoid doubt, unit dimensions should be expressed using
negative integers (e.g. kg m^-1 s^-2, not kg/ms^2) or the word 'per'.

END NOTES
* Please ensure the references are in the standard Nature format and follow the sequence: author list, title of paper, name of journal, volume number, initial-final page numbers or article number (year).
* Please use correct abbreviations for the journal names such as ‘Nat. Phys.’ (ref 2) etc. please fix ALL in the references.
* In the case of references with more than six authors, please change to first author et al (ref 1 etc).
* Please provide all required citing information for references, for example, name of journal and volume/page number of ref 4.
* Please update any preprints (e.g. ref 15) in the reference list with details of the published paper, if possible. If the paper has not been published, please cite the preprint in the style: Babichev, S. A., Ries, J. & Lvovsky, A. I. Quantum scissors: teleportation of single-mode optical states by means of a nonlocal single photon. Preprint at http://arXiv.org/quant-ph/0208066 (2002).
* Example of book citation: Meyer, H. A. The Role of Abdominal Fat 2nd edn, Vol. 2 (Academic, 1970).
* Example of books that form part of a series of books: Dupuis, F., Nielsen, J. B. & Salvail, L. Actively secure two-party evaluation of any quantum operation, in Advances in Cryptology – CRYPTO 2012 794–811 (Lecture Notes in Computer Science vol. 7417, Springer, 2012). Please modify references for books accordingly.

DISPLAY ITEMS
* Please check whether your manuscript or Supplementary Information contain third-party images, such as figures from the literature, stock photos, clip art or commercial satellite and map data. We strongly discourage the use or adaptation of previously published images, but if this is unavoidable, please request the necessary rights documentation to re-use such material from the relevant copyright holders and return this to us when you submit your revised manuscript.
* Please ensure that table titles are brief - they should not occupy more than one line in the final proof.
* In each figure (e.g. Figure 5b) where error bars are used, they must be defined. One statement at the end of each figure is sufficient if the error bars are equivalent throughout the figure.
* Figures should be uploaded as a whole, please avoid uploading figure panels.

SUPPLEMENTARY INFORMATION
* We do not edit Supplementary Information files; they will be uploaded with the published article as they are submitted with the final version of your manuscript. Any tracked changes should be removed from the file and the file should be provided as a PDF file. Supplementary Figures do not need to be provided separately.
* The only section headings permitted in the Supplementary Information are Supplementary Figures, Supplementary Tables, Supplementary Methods, Supplementary Notes, Supplementary Discussion, Supplementary References. All other section headings and numbering should be removed or relabelled.
* In the Supplementary Information file and the main manuscript text, supplementary items must be labelled and cited using only the following formats: Supplementary Figure 1, Supplementary Table 1, Supplementary Methods, Supplementary Note 1, Supplementary Discussion, and Supplementary References. Please note the use of "Supplementary" and that we do not use the "S" prefix.
---------------------------------------------------------------------
Please remove tables and figures from the main manuscript text file. All tables and figures must be uploaded as separate files for typesetting.

This revision step provides you with the opportunity to make minor changes to the manuscript. Please edit carefully and re-submit the manuscript files at the below link.

\end{document}

### 2022-08-18 revision/revised-paper_marked-up.tex

@@
     \centering
-    \includegraphics[width=0.9\textwidth]{figures/flow_chart_2.png}
+    \includegraphics[width=0.9\textwidth]{figure2.png}
     \caption{The project workflow starting from an initial Materials Project (MP) query, and ending with a featurized dataset with entries from several other databases. 
@@
     \centering
-    \begin{subfigure}{1\textwidth}
-        \centering
-        \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
-    \end{subfigure}
-    \begin{subfigure}{1\textwidth}
-        \centering
-          \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
-    \end{subfigure}
+    %\begin{subfigure}{1\textwidth}
+    %    \centering
+    %    \scalebox{0.85}{\input{AllFigures/01-ferrenti-approach-v2.pgf}}
+    %\end{subfigure}
+    %\begin{subfigure}{1\textwidth}
+     %   \centering
+     %     \scalebox{0.85}{\input{AllFigures/03-empirical-approach-v3.pgf}}
+    %\end{subfigure}
+    \includegraphics[width=0.8\textwidth]{figure3.pdf}
     \caption{Parallel coordinate plots for the two different approaches. \mrk{To limit data cluttering up to $250$ entries for each class were randomly collected.}  
@@
         \centering
-        \includegraphics[width=1\textwidth]{AllFigures/03-insightful-approach.pdf}
+        \includegraphics[width=1\textwidth]{figure4b.pdf}
     \end{subfigure}
@@
 %\mrk{To} reduce the dimensionality while preserving most of the variance in the data, \mrk{a principal component analysis  \cite{Jolliffe2002} was performed} for each of the three approaches (Ferrenti, extended Ferrenti and empirical).
-\mrk{Principal component analysis was again performed, but now on the three training sets separately}\footnote{In the main text we discuss the Ferrenti dataset and the empirical one.
-The corresponding results for the extended Ferrenti set are listed in the supplementary material.}
+\mrk{Principal component analysis was again performed, but now on the three training sets separately} \footnote{In the main text we discuss the Ferrenti dataset and the empirical one.
+The corresponding results for the extended Ferrenti set are listed in the Supplementary Information.}
 % \mrk{A principal component analysis was performed where first the} 
@@
     \centering
-    \includegraphics[width=0.85\textwidth]{AllFigures/fig6-all.png}
+    \includegraphics[width=0.85\textwidth]{figure6.png}
     \caption{\mrk{Example illustrations} of the crystal systems that the $9$ materials predicted by the empirical approach to $0.85$ confidence, and the $6$ materials predicted by all approaches to $0.75$ confidence\mrk{,} belong to.
@@
 \begin{subfigure}[b]{0.45\textwidth}
-    \input{figures/histograms/revised/AverageBondLength_std_dev Average bond length_count_075.tex}
+    \includegraphics{figure7d.pdf}
     \subcaption{}
